### 2016-01-15 Twitter_Urban_Boundary.tex
init

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% fixltx2e package for \textsubscript
\usepackage{fixltx2e}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
\usepackage{rotating}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\graphicspath{ {/figures/} }
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

\usepackage[section]{placeins}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.35in}

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{Delineate urban boundaries in Great Britain from the network of Twitter user spatial interactions}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Junjun Yin\textsuperscript{1, 2, 3},
Aiman Soliman\textsuperscript{1, 2, 4},
Dandong Yin\textsuperscript{1, 2, 3},
Shaowen Wang\textsuperscript{1, 2, 3, 4, $\ast$}
\\
\bigskip
\bf{1} CyberGIS Center for Advanced Digital and Spatial Studies
\\
\bf{2} CyberInfrastructure and Geospatial Information Laboratory (CIGI)
\\
\bf{3} Department of Geography and Geographic Information Science
\\
\bf{4} National Center for Supercomputing Applications
\\
\bf{} University of Illinois at Urbana-Champaign, 61801, IL, USA
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note

% Current address notes
%\textcurrency a Insert current address of first author with an address update
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

% Deceased author note
%\dag Deceased

% Group/Consortium Author Note
%\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* shaowen@illinois.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Urban regions are discrete urban areas with various social-economic relations and commute patterns of citizens.
Defining boundaries of the urban regions are of great importance for city planning, traffic management and resource allocation.
As existing urban boundaries are usually defined by government political and administrative purposes, it is not clear whether they truly reflect people daily interactions with the urban spaces, such as intra- and inter regional activities?
In this study, we presented a natural way for redrawing the urban boundaries based on human interactions with the physical spaces.
To be specific, we delineated the urban boundaries in Great Britain from a network of large-scale Twitter user spatial interactions, which were inferred from more than 69 million Twitter messages.
Our study provides a first step in connecting human mobility research with defining natural urban boundaries based on Twitter user spatial interactions, which provides a new perspective for understanding the interactions between urban structures with human activities. 
We redrew the natural boundary in a hierarchical fashion based on different range of user physical movements as it was inferred from the collective mobility patterns of the captured Twitter users in Great Britain.
The results of strongly connected urban regions in the form of communities in the network space yielded geographically cohesive, non-overlapping urban areas, which provides a clear delineation of the urban boundaries in Great Britain.
The technique was applied to both national level (Great Britain) and city level (greater London region), while the results corresponded well to the administrative boundaries, some of the unexpected and interesting boundaries were identified.

\linenumbers
\section*{Introduction}
Today’s urban boundaries (i.e. edges and districts) are usually defined by government agencies for political and administrative purposes.
While urban environments are conceptualized as spaces that are recreated and formed by human activities~\cite{schliephake}, a fundamental question for this “top-down” based approach to defining urban boundaries is whether it reflects the empirical humans interactions across space, such as commuting or trading activities between the borders.
Further, urban boundaries that respect how people naturally interact with the space can be of great importance for city planning, traffic management and resource allocation~\cite{lynch1960,jiang2015,liu2015,long2015}.
Many studies have adopted a ``bottom-up” approach for delineating urban boundaries, where the geographic space is partitioned into small units and each unit is modeled as a node in a network.
Then a suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interactions among them~\cite{lancichinetti2009}.
Different social and physical human interaction were considered to establish the edges of the network between nodes.
For example, a large set of telephone call records were used to represent the network of human interaction across space and delineated urban boundaries in Great Britain~\cite{ratti2010}.
Extended the previous method to different countries~\cite{sobolevsky2013}, the authors argue that this method yields cohesive geographic divisions that follow the socio-economic boundaries. 
While~\cite{kallus2015} have used social ties of Twitter users to identify cohesive regions for different countries across the world, where the authors found evidence for dividing due to local conflicts and cross-countries uniting trends to further support the ``bottom-up" approach to mapping natural boundaries.

In this study, we describe a novel approach to delineate urban boundaries based on the Twitter user movements extracted from massive Twitter dataset, with more than 69 million Twitter messages from $1^{st}$ June to $31^{st}$ December, 2014.
Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at a large spatial scale, for example, country level~\cite{hawelka,jurdak2015}.
We argue here that Twitter user mobility patterns provide a different view of natural units based on physical commuting rather than social ties or phone call initiation. 
A unique advantage is to delineate natural urban boundaries in a hierarchical fashion based on different range of user physical movements, which are inferred from the collective mobility patterns of the captured Twitter users in Great Britain. 
In addition, Twitter data are not sensitive to user privacy issues nor have a spatial granularity that is limited to zip code level~\cite{thiemann}, which can only produce sparse delineation.

We delineated the geography of urban boundaries in Great Britain by imposing a virtual fishnet over the islands of Great Britain. 
Twitter user movements were used to establish the connections between the virtual fishnet cells and form the connectivity network, where each cell acts as a node in a network.
We applied the map equation algorithm~\cite{domenico2015} to partition the network,  and associated geographic regions.
The map equation algorithm was selected to avoid the inherent resolution problem~\cite{fortunato2007} of the common modularity maximization method~\cite{newman2006}. 
We found that the collective mobility patterns of Twitter users in Great Britain are divided into several distance ranges starting from short intra-city to inter-city movements with clear distinction points. 
Identifying the connected regions at each of these distance ranges yielded a hierarchical boundaries of  the urban space in Great Britain.
Our study provides a first step in connecting human mobility research with defining natural urban boundaries based on Twitter user spatial interactions. It provides a new perspective for understanding the interactions between human activities with urban structures.

\section*{Materials and Methods}
\subsection*{Overview}
Our motivation of this study is to utilize large-scale Twitter user spatial interactions, which are inferred from the collective mobility patterns of Twitter users, to delineate urban boundaries in Great Britain.
In particular, a Twitter user's movement refers to the individual's relocation or displacement~\cite{gonzalez2008} in the geographic space.
It is not equivalent to a ``trip" took by an individual, for instance, even the time interval between two recorded locations is one month, it still counts as a displacement.
To identify the clusters of urban regional connectedness via large-scale Twitter user movements, we first imposed a virtual fishnet over the islands of Great Britain, where Twitter user movements were used to establish the connections between the virtual fishnet cells and form the connectivity network with each cell acts as a node in a network. 
Finally, by detecting strongly connected clusters in the network space with community detection methods~\cite{coscia2011}, the urban boundaries of these clusters were revealed back in the geographic space. 
An overview of the approach is illustrated in Fig.~\ref{S1_Fig} and the details are presented in the following sections.

\begin{figure}[ht]
\includegraphics[width=1\linewidth]{./figure/PNG/S1_overview_Fig_2}
\caption{{\bf An overview for delineating urban boundaries from Twitter user movements}}
\label{S1_Fig}
\end{figure}

\subsection*{Geo-located Twitter Data}
A geo-located tweet is a Twitter message appended with an additional geo-tag expressed as a pair of geographical coordinates that represents the location from which the tweet was sent.
In this study, the geo-located tweets were collected using the Twitter Streaming API (\url{https://dev.twitter.com/streaming/overview}) by supplying a geographical bounding box as an area-of-interest to retrieve all the contained geo-located tweets.
To ensure complete coverage of Great Britain, we set the bounding box to British Isles using the lower left and upper right coordinates (49.497, -14.854), (61.186, 2.637). This does include the whole of Ireland and part of France.
We have implemented a data crawler and continuously collected 7-months of data ($1^{st}$ June – $31^{st}$ December, 2014) resulting in over 101.8 million tweets at 60 GB in size. 
To showcase the overall spatial coverage of the collected geo-located tweets, a density map of the Twitter user locations in British Isle for July 2014 is shown in Fig.~\ref{S2_Fig}, where the collected points visualization reveals the geography of cities. Notice the clusters with higher densities of tweets (in color red) correspond to the locations of major cities.

\begin{figure}[ht]
\includegraphics[width=0.7\linewidth]{./figure/PNG/S2_twitter_density_Fig_1}
\caption{{\bf The density map of the Twitter user locations for July 2014}}
\label{S2_Fig}
\end{figure}

To verify the collected tweets are from human users, the raw tweets were further filtered by the following steps. 
First we removed the duplicated messages in the dataset.
Next, we removed non-human users based on unusual relocation speed \cite{hawelka,jurdak2015}. 
We adopted a relocation speed threshold of 240 m/s as used in \cite{jurdak2015}. 
We examined all the consecutive locations of each user and excluded those with relocating speed above the threshold.
Because the original location information embedded in the geo-tag is given in units of latitude and longitude, we projected the points into British National Grid (EPSG: 27700) coordinate system for the ease of distance calculations. 
Finally, we used the geographical boundary of Great Britain, which is derived from Office for National Statistics (ONS) of UK (\url{http://www.ons.gov.uk/ons}), to further restrict the remaining tweets to be ``domestic".
Based on these reinforcements, the filtered dataset for the following study contains 69,847,497 tweets from 1,153,891 users.

At this stage, each geo-located tweet is represented as a tuple $\langle user\_id, loc, t, m \rangle$, where $user\_id$ is an anonymous Twitter user’s id; $loc$ is the recorded location of the tweet as a pair of coordinates; $t$ is the timestamp of when the tweet was posted; and $m$ is the actual content of the tweet. 
To protect Twitter users’ privacy, the id field was replaced with a randomly generated unique number. 
Because we are interested in the collective Twitter user movements instead of individual user trajectories, the content of the message was removed. 
This simplifies the geo-located tweets and can be shared with other researchers upon request.

\subsection*{A network of large-scale Twitter user spatial interactions}
Urban regions are discrete urban areas, with various social-economic relations and commute patterns of citizens. 
In this connection, certain urban regions are more strongly connected to other urban regions than others.
Therefore, in this study, a connection is built between two urban regions when one of them is the origin of a Twitter user’s movement and the other is the destination. 
Such connections can be represented by an origin-destination (OD) matrix based on the collective Twitter user movement flux within the time span (i.e., $1^{st}$ June – $31^{st}$ December, 2014). 
This OD matrix is essentially a mathematical representation of a weighted directed graph $G\equiv\langle V, E_{w}\rangle$ where $V$ is a set of spatial nodes corresponding to the underlying urban regions; and $E_{w}$ is a set of edges representing the connections between a pair of nodes and the corresponding weights are assigned as the accumulated volume of Twitter user movement between the two urban regions.

To build such a spatial network at a national level, one must determine the basic units as the spatial nodes for mapping and aggregating the movement flows. 
Previous studies have suggested spatial tessellation as mapping units, which uses voronoi polygons to partition the space based on the collected points~\cite{rinzivillo2012,zhong2014}. 
This approach demonstrates improvements for estimating the locations of mobile phone records based on the cell tower triangulation~\cite{gonzalez2008,qian2013}.
However, it actually decreases the spatial resolution for geo-located tweets, as the location information is usually derived from the embedded GPS in the mobile devices and tends to provide better accuracy~\cite{sakaki2010,zandbergen2009}.
Another popular approach is to partition the space into a grid of spatial pixels~\cite{liuPopMobility,ratti2010}.
However, deciding the size of the cell can potentially encounter the Modifiable Areal Unit Problem (MAUP)~\cite{openshaw1984,wong2009}, where different choices of unit size can lead to significant variant findings.
To compare our investigation with the findings in similar studies but avoiding subjectively deciding the cell size, we performed statistical analysis of Twitter user mobility patterns in Great Britain measured by the distribution of collective Twitter user displacements and radius of gyrations of individuals \cite{gonzalez2008,jurdak2015}.

In particular, as radius of gyration is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008}, which is defined as Eq. \eqref{eq:2}:
\begin{equation} \label{eq:2}
r_{g} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(p_{i} -  p_{centroid})^{2}}, \textrm{where}\hspace{1ex} p_{centroid} = \frac{1}{n}\sum_{i=1}^{n}p_{i}
\end{equation}

\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
By examining the probability distributions of radius of gyrations, also known as the spatial dispersal kernel $P(r_g)$~\cite{brockmann2006}, we chose 10 km as the cell size, which is the value for quantifying the spatial coverage from majority of Twitter users in Great Britain (Fig.~\ref{S4_Fig} - c, with details shown in the next section). 
In this case, we have created a fishnet with 2784 10-km size cells.
The cells within the fishnet act as proxies for representing individuals' spatial coverage areas, which focus more on the inter-connections among cells to identify the strongly connected clusters.

\subsection*{Community structure of the spatial networks}
Based on the derived spatial network, which is a directed weighted graph, we further determined the clusters of strongly connected spatial nodes, also known as communities in the graph space~\cite{coscia2011}. 
There are a variety of community detection algorithms, which can produce different results depending their definition of community in the network~\cite{coscia2011}.
A common usage of community detection is based on modularity maximization~\cite{newman2006}, such as the previous studies in~\cite{hawelka,ratti2010,song2012}.
However, such an approach is often problematic: it is found to have an inherent resolution problem, where small communities are either ignored~\cite{fortunato2007} or assigned with high modularity scores \cite{guimera2004}; it is also found to produce less informative partitions in many empirical networks~\cite{good2010}.
Since our graph is a directed weighted graph, the alternative community detection library found from the literature is Infomap~\cite{domenico2015,rosvall2008}, which was considered to produce better community detections~\cite{lancichinetti2009}.

The Infomap uses the map equation~\cite{rosvall2010} for representing the probability of flow of random walks in information systems.
It finds communities by minimizing the expected description length of the trajectory of a random walker, which is shown below:
\begin{equation} \label{eq:1}
L(M)=qH(Q) + \sum_{i=1}^{m} p_{i}H(p_{i})
\end{equation}

In Eq. \eqref{eq:1} , $L(M)$ consists of two terms: qH(Q) is the entropy of the movements among clusters and $ \sum_{i=1}^{m} p_{i}H(p_{i})$ is the entropy of movements within clusters. 
To be more specific, q is the probability of a random walker jumps from one cluster to another, while $p_i$ is the probability of in-cluster movements in cluster i.
In this regard, this algorithm can be intuitively tailored to describe the context of finding strongly connected clusters of urban regions (i.e., spatial nodes) based on  Twitter user movements.
The detailed literatures and implementations of Infomap can be found from this website (\url{http://mapequation.org}).
Note that Infomap is capable of performing multi-level community detections~\cite{domenico2015}, but we only use the algorithm to produce most detailed community structures
to examine groups of strongly connected urban regions.

\section*{Results and Discussion}
\subsection*{Collective Mobility Patterns of Twitter Users in Great Britain}
We first modeled different aspects of the collective mobility patterns of Twitter user (i.e., number of visited locations per user,  collective user displacements and radius of gyration of individuals) in order to identify natural breaks in the user travel patterns.
Furthermore, we used these natural breaks of mobility patterns to partition the geographic space of Great Britain into a fine-grained cells and establish the connectivity among these cells to redraw natural urban boundaries.

We found that the cumulative distribution function~\cite{clauset2009} of the number of locations visited by each Twitter user during the timespan (1$^{st}$ June – 31$^{st}$ Dec, 2014) follows a two-tier power law distributions (shown in Fig.~\ref{S3_Fig}). 
The majority (the front part) of the distribution follows a truncated power-law distribution $P(X\geq x)\sim x^{-\alpha}e^{-\lambda x}$, where $\alpha = 1.24, \lambda =0.00132$; and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $P(X \geq x)\sim x^{-\alpha}$ with $\alpha$ value is 3.2.
The distribution was found to be consistent over all individual months (June to December, 2014), which has a slight offset in the truncated power-law distribution with the mean $\alpha$ value as 1.26 $ \pm$  0.05 (standard deviation) and the mean $\lambda$ value as 0.00134 $ \pm$  0.0002 (standard deviation).

The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk (a random walk) model~\cite{rhee2011,reynolds2012}, which has also been identified in many human mobility studies using different mobility data~\cite{zhao2015}.
The similarities among the distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which indicates our approach of using Twitter user mobility to delineating urban boundaries is not a snapshot of the whole process.  
In addition, the L\'{e}vy Walk model reveals the diversity regarding the number of visited locations per user, which indicates a level of ``randomness'' in Twitter user movements across space. 
It in turn justifies our choice of using the map equation community detection algorithm~\cite{rosvall2008} to identify the clusters of urban regional connectedness via large-scale Twitter user movements.

\begin{figure}[ht]
\includegraphics[width=1.0\linewidth]{./figure/PNG/S3_visitation}
\caption{{\bf Cumulative distribution of the number of locations visited by each Twitter user during different timespan}}
\label{S3_Fig}
\end{figure}

We further studied two aspects of Twitter user mobility pattern: the distribution of Twitter user displacements and radius of gyration. 
Twitter user displacement refers to the distance between each two consecutive locations in a user’s trajectory using a “crow's fly distance” (i.e., the direct distance); and the radius of gyration describes the deviation of distance from the center of mass in a user’s trajectory.
The probability distributions of the collective user displacements $P(d)$ and radius of gyration $P(r_g)$ are presented in Fig.~\ref{S4_Fig}, where the fitting method for identifying different distance ranges is derived from~\cite{jurdak2015}.
The probability distribution of the collective displacements can be approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10m, 70m] (accounting for 3 $\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [70m, 70km] (93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 70km] (4 $\%$ of the population). 
In particular, the displacement distance between 70m and 100km can be further approximately by two power law distributions with a cutting point at 4km (55$\%$ distances are less than 4km and 40$\%$ distances between 4km and 100km), which indicates the urban movements captured by the geo-located Twitter data reveals two different modes, such as inter- or intra-city movements. 
In summary, these fitting functions suggest the existence of multi-scale or multi-modal urban movements captured from Twitter users in Great Britain, which means the geographically cohesive, non-overlapping urban areas (identified in the next section) are not just a result of short distance movements but naturally emerged from the collective Twitter user mobility pattern.
Note that similar multiphase pattern was observed of Twitter user displacement in Australian but with slightly different distance ranges\cite{jurdak2015}.

Further, we analyzed the distribution of radius of gyration to understand the movement from point of view of individual Twitter users rather than separated displacements.
The distribution of radius of gyration can be approximated by a combination of three functions: $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10m$ from [10 m, 30m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50m, 10km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [10km, 100km], where these three functions account for 92$\%$ of all the users.
This suggests that there are mainly three types of users, where some Twitter users (1) tend to stay at one location or at nearby locations when they tweet, some users (2) tend to move in intra-city scale when they tweet and some users’ (3) movements tend to have a large spatial coverage. 
In particular, (1) and (2) account for approximately 53$\%$ of all users.  
The radius of gyration between 30m and 100km can be further approximately by two power law distributions with a cutting point at 2.5km (35 $\%$ users with radius of gyration less than 2.5km and 57$\%$ users with radius of gyration between 3km and 100km), which suggest two main types of spatial coverage of Twitter user movements in Great Britain. 
Note that the accuracy of these values for defining the distance bound depends on the accuracy of the location information of each geo-located tweet. 
These findings are consistent with the findings in research on human mobilities where the radius of gyration of human movements is bounded to different distance ranges~\cite{brockmann2006,gonzalez2008}.
The distance-decay effects found in both user displacements and radius of gyration show evidences of spatial proximity in Twitter user movements. 
It explains the communities of urban regions in a graph space are geographically close and yet still be able to be separated from other groups, which essentially result in the delineating urban boundaries based on Twitter user spatial interactions.

\begin{figure}[ht]
\includegraphics[width=1.0\linewidth]{./figure/PNG/S4_radius_displacement}
\caption{{\bf The probability distribution of Twitter user displacements and radius of gyration:} (a) The displacement distribution $P(d)$ is approximated by an exponential, a stretched-exponential and a power-law function (b) the distance between [70m, 70km] is approximated by a double power-law functions (c) The distribution of radius of gyration $P(r_g)$ is approximated by the combination of an exponential, a stretched-exponential and a power-law function (d) the distance between [30m, 100 km] is approximated by a double power-law functions}
\label{S4_Fig}
\end{figure}

\subsection*{Redefining Great Britain’s Administrative Boundaries}
The network of Twitter user spatial interaction in this study was constructed by nodes represented by 10 km by 10 km fishnet cells, which provides an adequate resolution for country wide investigation~\cite{ratti2010}.
The edges of this network were derived from the number of directed Twitter user movements/displacements between each pair of cells.
We used the connectivity network as a proxy to partition the space associated with its nodes.
Coherent geographic regions were identified as individual fishnet cells showing more inner transportation compared to transportation with the outside cells.
Fig.~\ref{S5_Fig}  presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4km, greater than 10 km and using all available displacements together compared to the administrative boundaries of Great Britain counties.
One clear observation across the coarse and fine delineations is that most of the geographic divisions are centered around big urban cores with relatively high population.
This results is expected given that most of the tweets originates in urban centers.
However, what is remarkable is the performance of this approach in dividing the remaining space between cities.
We found that restricting the trip distance resulted in different delineations of the travelers catchment area around these centers.
For example, one could explain these effects as a manifestation of the underlying gravity law~\cite{simini2012} and the distance decay effect on attracting travelers~\cite{gonzalez2008}.
Remarkably, our approach performed well in terms of dividing the entire space with minimum gaps.
Empty cells were found in regions with no, or few Twitter users had visited (e.g., forests, agriculture) especially in the case of restricting the analysis to short distance Twitter user displacements.

\begin{figure}[ht]
\includegraphics[width=0.9\linewidth]{./figure/PNG/S5_community}
\caption{{\bf The community structure from collective Twitter user displacements reveals natural urban boundaries} (a) displacements longer than 10 km (b) displacements shorter than 4 km (c) and displacements longer than 4 km (d) The partition of space was done using a 10 km fishnet to map the directed displacements from and to each cell. Each color represents a unique community with more Twitter users displacements among the cells compared to others. Major cities (urban audit functional areas) and NUTS are displayed in black.}
\label{S5_Fig}
\end{figure}

Region boundaries inferred from short distance Twitter user displacements (less than 4 km) exhibited very small and fragmented regions, which is probably related to daily commuting around users’ home location. 
Redrawing the boundaries based on longer distance displacements, yielded a collection of more cohesive large regions.
For example, partition the space based on displacements greater than 10 km created regions that are comparable to the NUTS (Nomenclature of Territorial Units for Statistics - 1) regions (Fig.~\ref{S6_Fig} - a). 
However, the power of this novel mapping technique is not to reproduce the partitions already known rather pointing out to some of the unexpected boundaries.
For example the boundaries between England and wales were found to be more diffusive compared to the abrupt boundaries with Scotland.
Moreover, the city of London has a wider visitor catchment area that extends beyond the authoritative boundaries of the city. 
Increasing the displacement distance has resulted in revealing the large region connected to London (Fig.~\ref{S6_Fig}).

The power of using Twitter user mobility to delineate natural boundaries is the ability to redraw the city at different mobility ranges inferred objectively from the users collective distribution. 
In addition, the distance range of the movements usually could be explained by local socioeconomic factors (e.g., work commuting ), which could provide some specific interpretation of the apparent patterns.
The patterns obtained from Twitter users mobility patterns are comparable to the patterns produced by division the network of landline phone call~\cite{ratti2010}.\
For example, the region of Wales appeared to consists of three communities as found by connectivity of both phone calls and long distance movements. 
However, the regions extracted from the mobility network seems to be more spatially consistent with minimum spatial gaps compared to the partitions extracted from land-line calls networks in Great Britain~\cite{ratti2010}.

\begin{figure}[ht]
\includegraphics[width=0.7\linewidth]{./figure/PNG/S6_community_london}
\caption{{\bf The natural regions inferred from Twitter user displacements greater than 4 km (left) and 10 km (right) in comparison with major cities in England (upper figures) and Scotland (bottom figures).}  Each color represents a unique community. Including short distance movements has increased the power to differentiate the influence of nearby cities such as Glasgow and Edinburgh (lower left), while restricting the analysis to longer distance movements grouped travelers from the two previous cities into the same community (lower right).}
\label{S6_Fig}
\end{figure}

A more detailed study was conducted over the greater London region revealed by the intra-city spatial interaction patterns.
The space partitions derived from a fine grid of 1km and using all available Twitter user trips without any restriction on the trip’ distances yielded geographic boundaries comparable to some of London boroughs administrative boundaries (Fig.~\ref{S7_Fig}).
However, some areas showed to be more cohesive and displayed more spatial interactions across the administrative boundaries like the area of central London.
Although, the results suggest that the travelers seems to be localized over certain areas of the city for most of their time, and some regions showed long distance interaction patterns.
For example, the separate geographic areas in the south of Hillingdon marking the domain of Heathrow Airport exhibits more connectivity to central London than to the surrounding which is explained by usual flight passengers routes.
The technique also reveals some of the emerging communities around  borders as a result of spatial intermingling of both communities across the borders.
For example, East Barnet and West Enfield seems to have higher interaction that resulted in the emerging cohesive zone between the two boroughs.

\begin{figure}[ht]
\includegraphics[width=0.8\linewidth]{./figure/PNG/S7_london}
\caption{{\bf Natural boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.  Each unique color represents a different natural region. Notice that some remote regions like the airport (light green region in south of Hillingdon) share the same class with downtown because it is well connected despite the geographic separation.}
\label{S7_Fig}
\end{figure}

\section*{Conclusion}
In this study,  we delineated the natural urban boundaries in Great Britain from a network of large-scale Twitter user spatial interactions, which are inferred from the collective Twitter user movements extracted from more than 69 million Twitter messages.
In contrast to urban boundaries defined by government agencies with the ``top-down” based approach, we took a ``bottom-up" approach by first imposing a virtual fishnet over the islands of Great Britain, which serves as a proxy to partition the space.
By studying the probability distributions of radius of gyrations of individual Twitters users, we chose 10 km as the cell size, which is the value for quantifying the spatial coverage from majority of Twitter users in Great Britain. 
Twitter user movements were used to establish the connections between the virtual fishnet cells as nodes in a directed weighted network.  
We then applied the map equation algorithm to partition the network,  and associated geographic regions.
The results of strongly connected urban regions in the form of communities in the network space yielded geographically cohesive, non-overlapping urban areas, which provides a clear delineation of the urban boundaries in Great Britain.
By performing statistical analysis of Twitter user mobility patterns in Great Britain, in particular the distribution of collective Twitter user displacements,  we found multi-scale or multi-modal urban movements captured from the Twitter user in Great Britain, which were divided into several distance ranges starting from short intra-city to inter-city movements with clear distinction points.
Identifying the connected regions at each of these distances ranges yielded a hierarchical boundaries of  the urban space in Great Britain.

The power of using Twitter user mobility to delineate natural boundaries is the ability to redraw the city at different mobility ranges inferred objectively from the collective mobility patterns. 
As the urban boundaries are redrawn based on Twitter user movements, which are the physical commuting rather than social ties or phone call initiation, it reflects empirical humans interactions across space.
This study provides a first step in connecting human mobility research with defining natural boundaries, which could assist decision makers regarding resource allocations, political campaigns and urban planning. Finally, as many other mobility datasets, the geo-located twitter data is not able to generalize to the whole population, therefore, the urban regions that do not have any or few Twitter coverage can be missed in the delineation. However, our approach can be still applicable when more detailed mobility data becomes available.

%\subsection*{xx}
%see \nameref{S1_Fig}.
%
%\section*{Supporting Information}
%
%% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
%\subsection*{S1 A scalable data processing framework}
%\label{S1_framework}

\section*{Acknowledgments}
The authors would like to thank Dr. Kun Zhao and Dr. Raja Jurdak from CSIRO, Australia for their suggestions in generating Figure 1 in this paper. 
The research was supported from National Science Foundation grants No. xx ...

\section*{Author Contribution}
Conceived and designed the experiments: JY AS DY SW. Performed the experiments: JY DY. Analyzed the data: JY AS. Contributed reagents/materials/analysis tools: JY AS DY AS. Wrote the paper: JY AS SW.

\nolinenumbers

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
% 
\begin{thebibliography}{10}
\bibitem{schliephake}
Schliephake, C., 2014. Urban Ecologies: City Space, Material Agency, and Environmental Politics in Contemporary Culture. Lexington Books.

\bibitem{lynch1960}
Lynch, K., 1960. The image of the city. MIT press.

\bibitem{jiang2015}
Jiang, B., Miao, Y., 2015. The evolution of natural cities from the perspective of location-based social media. The Professional Geographer, 67(2), 295-306.

\bibitem{long2015}
Long, Y., Han, H., Tu, Y., Shu, X., 2015. Evaluating the effectiveness of urban growth boundaries using human mobility and activity records. Cities, 46, 76-84.

\bibitem{liu2015}
Liu, X., Gong, L., Gong, Y., Liu, Y., 2015. Revealing travel patterns and city structure with taxi trip data. J. Transportation Geography, 43, 78–90. doi:10.1016/j.jtrangeo.2015.01.016

\bibitem{lancichinetti2009}
Lancichinetti, A., Fortunato, S., 2009. Community detection algorithms: A comparative analysis. Physical Review E, 80, 056117. doi:10.1103/PhysRevE.80.056117

\bibitem{ratti2010}
Ratti, C., Sobolevsky, S., Calabrese, F., Andris, C., Reades, J., Martino, M., Claxton, R., Strogatz, S.H., 2010. Redrawing the Map of Great Britain from a Network of Human Interactions. PLoS ONE 5, e14248. doi:10.1371/journal.pone.0014248

\bibitem{sobolevsky2013}
Sobolevsky S, Szell M, Campari R, Couronné T, Smoreda Z, Ratti, C., 2013. Delineating Geographical Regions with Networks of Human Interactions in an Extensive Set of Countries. PLoS ONE 8(12): e81707. doi: 10.1371/journal.pone.0081707

\bibitem{kallus2015}
Kallus Z, Barankai N, Szüle J, Vattay G., 2015 Spatial Fingerprints of Community Structure in Human Interaction Network for an Extensive Set of Large-Scale Regions. PLoS ONE 10(5): e0126713. doi: 10.1371/journal.pone.0126713

\bibitem{hawelka}
Hawelka, B., Sitko, I., Beinat, E., Sobolevsky, S., Kazakopoulos, P., Ratti, C., 2014. Geo-located Twitter as proxy for global mobility patterns. Cartography and Geographic Information Science, 41, 260–271. doi:10.1080/15230406.2014.890072

\bibitem{jurdak2015}
Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D., 2015. Understanding Human Mobility from Twitter. PLoS ONE 10, e0131469. doi:10.1371/journal.pone.0131469

\bibitem{thiemann}
Thiemann, C., Theis, F., Grady, D., Brune, R., Brockmann, D., 2010. The Structure of Borders in a Small World. PLoS ONE 5, e15422. doi:10.1371/journal.pone.0015422

\bibitem{domenico2015}
De Domenico, M., Lancichinetti, A., Arenas, A., Rosvall, M., 2015. Identifying Modular Flows on Multilayer Networks Reveals Highly Overlapping Organization in Interconnected Systems. Physical Review X, 5. doi:10.1103/PhysRevX.5.011027

\bibitem{fortunato2007}
Fortunato, S., Barthélemy, M., 2007. Resolution limit in community detection. Proceedings of the National Academy of Sciences, 104, 36–41. doi:10.1073/pnas.0605965104

\bibitem{newman2006}
Newman, M.E.J., 2006. Modularity and community structure in networks. Proceedings of the National Academy of Sciences, 103, 8577–82. doi:10.1073/pnas.0601602103

\bibitem{gonzalez2008}
González, M.C., Hidalgo, C.A., Barabási, A.-L., 2008. Understanding individual human mobility patterns. Nature, 453, 779–82. doi:10.1038/nature06958

\bibitem{coscia2011}
Coscia, M., Giannotti, F., Pedreschi, D., 2011. A Classification for Community Discovery Methods in Complex Networks. Statistical Analysis and Data Mining, 4, 512–546. doi:10.1002/sam.10133

\bibitem{rinzivillo2012}
Rinzivillo, S., Mainardi, S., Pezzoni, F., Coscia, M., Pedreschi, D., Giannotti, F., 2012. Discovering the Geographical Borders of Human Mobility. KI - Künstl. Intell. 26, 253–260. doi:10.1007/s13218-012-0181-8

\bibitem{zhong2014}
Zhong, C., Arisona, S.M., Huang, X., Batty, M., Schmitt, G., 2014. Detecting the dynamics of urban structure through spatial network analysis. International Journal of Geographical Information Science, 28, 2178–2199. doi:10.1080/13658816.2014.914521

\bibitem{qian2013}
Qian, W., Stanley, K. G., Osgood, N. D., 2013. The impact of spatial resolution and representation on human mobility predictability. In Web and Wireless Geographical Information Systems,  pp. 25-40, Springer Berlin Heidelberg.

\bibitem{sakaki2010}
Sakaki, T., Okazaki, M., Matsuo, Y., 2010. Earthquake Shakes Twitter Users: Real-time Event Detection by Social Sensors, in: Proceedings of the 19th International Conference on World Wide Web, WWW ’10. ACM, New York, NY, USA, pp. 851–860. doi:10.1145/1772690.1772777

\bibitem{zandbergen2009}
Zandbergen, P.A., 2009. Accuracy of iPhone Locations: A Comparison of Assisted GPS, WiFi and Cellular Positioning. Transactions in GIS, 13, 5–25. doi:10.1111/j.1467-9671.2009.01152.x

\bibitem{liuPopMobility}
Liu, J., Zhao, K., Khan, S., Cameron, M., Jurdak, R., 2014. Multi-scale Population and Mobility Estimation with Geo-tagged Tweets. ArXiv14120327 Phys.

\bibitem{openshaw1984}
Openshaw, S., 1984. The modifiable areal unit problem. Geo Abstracts University of East Anglia.

\bibitem{wong2009}
Wong, D., 2009. The modifiable areal unit problem (MAUP). SAGE Publications: London, UK.

\bibitem{brockmann2006}
Brockmann, D., Hufnagel, L., Geisel, T., 2006. The scaling laws of human travel. Nature 439, 462–5. doi:10.1038/nature04292

\bibitem{song2012}
Song, C., Wang, D., Barabási, A.-L., 2012. Connections between human dynamics and network science. ArXiv Prepr. ArXiv12091411.

\bibitem{guimera2004}
Guimerà, R., Sales-Pardo, M., Amaral, L.A.N., 2004. Modularity from fluctuations in random graphs and complex networks. Physical Review E, 70, 025101. doi:10.1103/PhysRevE.70.025101

\bibitem{good2010}
Good, B.H., de Montjoye, Y.-A., Clauset, A., 2010. Performance of modularity maximization in practical contexts. Physical Review E, 81, 046106. doi:10.1103/PhysRevE.81.046106

\bibitem{rosvall2008}
Rosvall, M., Bergstrom, C.T., 2008. Maps of random walks on complex networks reveal community structure. Proceedings of the National Academy of Sciences, 105, 1118–1123.

\bibitem{rosvall2010}
Rosvall, M., Axelsson, D., Bergstrom, C.T., 2010. The map equation. The European Physical Journal Special Topics, 178, 13–23. doi:10.1140/epjst/e2010-01179-1

\bibitem{clauset2009}
Clauset, A., Shalizi, C., Newman, M., 2009. Power-Law Distributions in Empirical Data. Society for Industrial and Applied Mathematics Review. 51, 661–703. doi:10.1137/070710111

\bibitem{rhee2011}
Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S. J., and Chong, S., 2011. On the levy-walk nature of human mobility. IEEE/ACM transactions on networking (TON), 19(3), 630-643.

\bibitem{reynolds2012}
Reynolds, A., 2012. Truncated levy walks are expected beyond the scale of data collection when correlated random walks embody observed movement patterns. Journal of The Royal Society Interface, 9(68), 528-534.

\bibitem{zhao2015}
Zhao, K., Musolesi, M., Hui, P., Rao, W., and Tarkoma, S., 2015. Explaining the power-law distribution of human mobility through transportation modality decomposition. Scientific reports, 5.

\bibitem{simini2012}
Simini, F., González, M. C., Maritan, A., Barabási, A. L., 2012. A universal model for mobility and migration patterns. Nature, 484(7392), 96-100.

%\bibitem{blondel2008}
%Blondel, V.D., Guillaume, J., Lambiotte, R., Lefebvre, E., 2008. Fast unfolding of community hierarchies in large networks. Networks 1–6.
%

\end{thebibliography}
\end{document}

### 2016-01-16 urban_boundaries_gb/Twitter_Urban_Boundary.edits.tex
new edit to be merged

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% fixltx2e package for \textsubscript
\usepackage{fixltx2e}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
\usepackage{rotating}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\graphicspath{ {/figures/} }
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

\usepackage[section]{placeins}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.35in}

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{Delineate urban boundaries in Great Britain from the network of Twitter user spatial interactions}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Junjun Yin\textsuperscript{1, 2, 3},
Aiman Soliman\textsuperscript{1, 2, 4},
Dandong Yin\textsuperscript{1, 2, 3},
Shaowen Wang\textsuperscript{1, 2, 3, 4, $\ast$}
\\
\bigskip
\bf{1} CyberGIS Center for Advanced Digital and Spatial Studies
\\
\bf{2} CyberInfrastructure and Geospatial Information Laboratory (CIGI)
\\
\bf{3} Department of Geography and Geographic Information Science
\\
\bf{4} National Center for Supercomputing Applications
\\
\bf{} University of Illinois at Urbana-Champaign, 61801, IL, USA
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note

% Current address notes
%\textcurrency a Insert current address of first author with an address update
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

% Deceased author note
%\dag Deceased

% Group/Consortium Author Note
%\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* shaowen@illinois.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns.
Defining the boundaries of urban regions is important to city planning, traffic management and resource allocation.
Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's daily interactions with the urban space in their intra- and inter regional activities.
In this study, we presented a method to redraw urban boundaries based upon human interaction with the physical space.
Specifically, we delineated the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million Twitter messages.
Our study connects human mobility research with the delineation of non-administrative anthropographic urban boundaries based on Twitter user spatial interactions, which provides a new understanding of the interactions between urban structure and human activity.
We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
The result of strongly connected urban regions, or communities, in the network space yield geographically cohesive, non-overlapping urban areas that delineate the non-administrative anthropographic urban boundaries of Great Britain.
The technique was applied at the national scale (Great Britain) and the municipal scale (the London metropolis). 
While our results corresponded well to the administrative boundaries, many unexpected and interesting boundaries were identified.

\linenumbers
\section*{Introduction}
Official urban boundaries are defined by government agencies for political and administrative purposes.
Urban environments are conceptualized as spaces that are recreated and formed by human activities~\cite{schliephake}.
A fundamental question when using the administrative, ``top-down'', approach for defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
These interactions can take the form of trade, commerce, social connections, and political activity.
Urban boundaries that respect the human interaction space can be very import to city planning, traffic management and resource allocation~\cite{lynch1960,jiang2015,liu2015,long2015}.
Many studies adopt a ``bottom-up'' approach to urban boundary delineation; where the geographic space is partitioned into small units and each unit is modeled as a node within a network structure.
A suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interaction among the nodes~\cite{lancichinetti2009}.
Different social and physical human interactions were considered to establish the edges of the network connecting the nodes.
For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in the United Kingdom~\cite{ratti2010}.
% does ratti or sobolevsky argue the following... who are "the authors"?
Extending the previous method to different countries~\cite{sobolevsky2013}, the authors argue, yields cohesive geographic divisions that mark the socio-economic boundaries. 
% I think these citations should expand to include the author's names, not just [9].
While~\cite{kallus2015} use social ties of Twitter users to identify cohesive regions for different countries across the world, the authors found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.

In this study, we describe a novel approach to delineate urban boundaries based on the movements of 
Twitter users extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the country level)~\cite{hawelka,jurdak2015}.
We argue here that Twitter user mobility patterns provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation. 
A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in the United Kingdom. 
In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity 
% I think UK calls them postal codes and not zip codes
that is limited to the postal code level~\cite{thiemann}.  % everything has sparsity at some scale...

We delineated the geography of urban boundaries in the United Kingdom by imposing a virtual fishnet over the British Isles. % Great Britain is, itself, an island.
Twitter user movements were used to establish the connections between the fishnet's cells to form a connectivity network, where each cell acts as a node within the network.
We applied the map equation algorithm~\cite{domenico2015} to partition the network and associate geographic regions.
The map equation algorithm was selected to avoid the inherent resolution problem~\cite{fortunato2007} of the common modularity maximization method~\cite{newman2006}. 
We found that the collective mobility patterns of Twitter users in the United Kingdom are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points. 
The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in the United Kingdom.
Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. It provides a new understanding of the interaction between human activity and urban structures. 
%NOTE: I'm not sure how twitter relates to urban structure...

%NOTE: I did not review the figures or figure captions
\section*{Materials and Methods}
\subsection*{Overview}
We use large-scale Twitter user spatial interactions inferred from the collective mobility patterns of Twitter users to delineate urban boundaries in Great Britain.
A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\cite{gonzalez2008}.
This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two recorded locations is one month.
To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the British Isles.
Twitter user movements were then used to establish the connectivity between fishnet cells to form a connectivity network where each cell is considered a node within the network. 
Finally, by detecting strongly connected clusters in the network space using community detection methods~\cite{coscia2011}, we are able to reveal urban boundaries within the geographic space. 
An overview of the approach is illustrated in Fig.~\ref{S1_Fig} and the details are presented in the following sections.

\begin{figure}[ht]
\includegraphics[width=1\linewidth]{./figure/PNG/S1_overview_Fig_2}
\caption{{\bf An overview for delineating urban boundaries from Twitter user movements}}
\label{S1_Fig}
\end{figure}

\subsection*{Geo-located Twitter Data}
A geo-located tweet is a Twitter message with an additional geo-tag expressed as a pair of geographical coordinates that represent the location from which the tweet was sent.
For this study, geo-located tweets were collected using the Twitter Streaming API (\url{https://dev.twitter.com/streaming/overview}) by supplying a geographical bounding box to retrieve all the  geo-located tweets within an area of interest.
% is it the entire UK or the British Isles? It is not Great Britain.
To ensure complete coverage of the United Kingdom, we set the bounding box to the British Isles using the lower left and upper right coordinates (49.497, -14.854), (61.186, 2.637) respectively. This does include part of France.  % ireland is part of the british isles
We implemented a data crawler to continuously collect 7-months of data (June $1^{st}$ -- December $31^{st}$, 2014) resulting in over 101.8 million tweets with a total data volume of 60 GB which we restrict to 69 million based on a process outlined below. 
To showcase the overall spatial coverage of the collected geo-located tweets, a density map of the tweet locations in British Isles for July 2014 is shown in Fig.~\ref{S2_Fig}.
The collected point visualization reveals the geography of cities. Notice the clusters with higher densities of tweets that correspond to the locations of major cities.

\begin{figure}[ht]
\includegraphics[width=0.7\linewidth]{./figure/PNG/S2_twitter_density_Fig_1}
\caption{{\bf A density map of the Twitter user locations for July 2014}}
\label{S2_Fig}
\end{figure}

To verify the collected tweets are from human users, the raw tweets were further filtered using the following steps. 
First we removed the duplicated messages in the dataset.
Next, we removed non-human users based on unusual relocation speed \cite{hawelka,jurdak2015}. 
We adopted a relocation speed threshold of 240 m/s as used by \cite{jurdak2015}. 
We examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold.
Because the original location information embedded in the geo-tag is given in units of latitude and longitude, we projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations. 
Finally, we used the geographical boundary of the United Kingdom, which is derived from Office for National Statistics (ONS) of UK (\url{http://www.ons.gov.uk/ons}), to further restrict the remaining tweets to be ``domestic".
Based on these restrictions, the filtered dataset for the following study contains 69,847,497 tweets made by 1,153,891 twitter users.

At this stage, each geo-located tweet is represented as a tuple $\langle user\_id, loc, t, m \rangle$, where $user\_id$ is an anonymous Twitter user id; $loc$ is the recorded location of the tweet as a coordinate pair; $t$ is the timestamp of the tweet's post; and $m$ is the actual content of the tweet. 
To protect Twitter user privacy, the id field was replaced with a randomly generated unique number. 
Because we are interested in collective Twitter user movement instead of individual user trajectories, the content of the message was removed. 
Our simplified geo-located tweet dataset can be shared with other researchers upon request.

\subsection*{A network of large-scale Twitter user spatial interactions}
Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns. 
Some urban regions are more strongly connected to each other than other urban regions.
Therefore, this study connects urban regions when a twitter user begins in one region and ends in another region.
These connections can be represented by an origin-destination (OD) matrix based on the collective Twitter user displacement within the dataset.
This OD matrix is essentially a mathematical representation of a weighted directed graph $G\equiv\langle V, E_{w}\rangle$ where $V$ is a set of spatial nodes corresponding to the underlying urban regions and $E_{w}$ is a set of edges representing the connections between a pair of nodes and the corresponding weights that are assigned to the accumulated volume of Twitter user movement.

To build our spatial network at the kingdom level, we had to determine the basic units to serve as spatial nodes of the connectivity network of urban regions.
Previous studies have suggested equi-distant spatial tessellation to generate nodes, which uses voronoi polygons to partition the space based on the collected points~\cite{rinzivillo2012,zhong2014}. 
This approach demonstrates improvements for estimating the locations of mobile phone records based on the cell tower triangulation~\cite{gonzalez2008,qian2013}.
However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\cite{sakaki2010,zandbergen2009}.
Another popular approach is to partition the space into a grid of spatial pixels~\cite{liuPopMobility,ratti2010}.
However, the size of the cell can potentially lead to biases due to the Modifiable Area Unit Problem (MAUP)~\cite{openshaw1984,wong2009}. To compare our investigation with the findings of similar studies, and avoid subjectively deciding the cell size, we performed a statistical analysis of Twitter user mobility patterns in the United Kingdom and measured the distribution of collective Twitter user displacements and the radius of gyrations of individuals \cite{gonzalez2008,jurdak2015}.
The radius of gyration is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008}, which is defined as Eq. \eqref{eq:2}:
\begin{equation} \label{eq:2}
r_{g} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(p_{i} -  p_{centroid})^{2}}, \textrm{where}\hspace{1ex} p_{centroid} = \frac{1}{n}\sum_{i=1}^{n}p_{i}
\end{equation}
\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
By examining the probability distributions of the radius of gyration, also known as the spatial dispersal kernel $P(r_g)$~\cite{brockmann2006}, we chose 10 km as the cell size to quantify the spatial coverage of the majority of Twitter users in the United Kingdom (Fig.~\ref{S4_Fig} - c, with details shown in the next section). 
Thus, we created a fishnet with 2784 10-km size cells.
The cells of the fishnet act as proxies to represent individuals' spatial coverage areas to focus more on the inter-connectivity among cells and identify strongly connected cell clusters.

\subsection*{Community structure of the spatial networks}
Based on the derived spatial network, which is a directed weighted graph, we further determined clusters of strongly connected spatial nodes, known as communities, in the graph space~\cite{coscia2011}. 
There are a variety of community detection algorithms that produce different results depending the definition of community within the network~\cite{coscia2011}.
A common community detection method is based on modularity maximization~\cite{newman2006}, seen in previous studies~\cite{hawelka,ratti2010,song2012}.
However, such an approach is often problematic: it is found to have an inherent resolution problem, where small communities are either ignored~\cite{fortunato2007} or assigned with high modularity scores \cite{guimera2004}; and it is found to produce less informative partitions in many empirical networks~\cite{good2010}.
Since our graph is a directed weighted graph, the alternative community detection library documented in the literature is Infomap~\cite{domenico2015,rosvall2008}, which is considered to produce better community detection results~\cite{lancichinetti2009}.

%NOTE: the random walk should be better introduced or defined. This is slightly confusing.
Infomap uses the map equation~\cite{rosvall2010} to represent the probability of flow of random walks within information systems.
It identifies communities by minimizing the expected description length of the trajectory of a random walker, which is shown below:
\begin{equation} \label{eq:1}
L(M)=qH(Q) + \sum_{i=1}^{m} p_{i}H(p_{i})
\end{equation}

In Eq. \eqref{eq:1} , $L(M)$ consists of two terms: qH(Q) is the entropy of the movement among clusters and $ \sum_{i=1}^{m} p_{i}H(p_{i})$ is the entropy of movement within clusters. 
To be more specific, q is the probability that a random walker jumps from one cluster to another, while $p_i$ is the probability of the in-cluster movement of cluster i.
In this regard, this algorithm can be intuitively tailored to describe strongly connected clusters of urban regions based on Twitter user movement.
The detailed literatures and implementations of Infomap can be found on this website (\url{http://mapequation.org}).
Note that Infomap is capable of performing multi-level community detection~\cite{domenico2015}, but we only use the algorithm to produce our most detailed community structures
to examine groups of strongly connected urban regions.

\section*{Results and Discussion}
\subsection*{Collective Mobility Patterns of Twitter Users in Great Britain}
We first modeled different aspects of the collective mobility patterns of Twitter users.
These patterns include: the number of visited locations per user,  the collective user displacements, and the radius of gyration of individuals in order to identify natural breaks in user travel patterns.
We then used these natural breaks within the mobility patterns to partition the geographic space of the United Kingdom into fine-grained cells and established the connectivity among these cells to redraw non-administrative anthropographic urban boundaries.

We found that the cumulative distribution function~\cite{clauset2009} of the number of locations visited by each Twitter user follows a two-tier power law distribution (shown in Fig.~\ref{S3_Fig}). 
The majority of the data distributed follows a truncated power-law distribution $P(X\geq x)\sim x^{-\alpha}e^{-\lambda x}$, where $\alpha = 1.24, \lambda =0.00132$; and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $P(X \geq x)\sim x^{-\alpha}$ with $\alpha$ value is 3.2.
The distribution was found to be consistent over all individual months examined (June to December, 2014), which has a slight offset in the truncated power-law distribution (the mean $\alpha$ value is 1.26 $ \pm$ with a 0.05 $\sigma$ and the mean $\lambda$ value as 0.00134 $ \pm$  with a 0.0002 $\sigma$).

The two-tier power law distribution indicates that the collective behavior of Twitter users visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk (a random walk) model~\cite{rhee2011,reynolds2012}, which has also been identified in many human mobility studies using different mobility data~\cite{zhao2015}.
The similarity among the distributions suggests that the mobility data collected from geo-located tweets is temporally stable, at least at the monthly interval, which indicates that our approach using Twitter user mobility to delineate urban boundaries is viable.  
In addition, the L\'{e}vy Walk model reveals the diversity regarding the number of visited locations per user, which indicates a level of ``randomness'' in Twitter user movement across space. 
It, in turn, justifies our choice of using the map equation community detection algorithm~\cite{rosvall2008} to identify the clusters of urban regional connectedness using large-scale Twitter user movement data.

\begin{figure}[ht]
\includegraphics[width=1.0\linewidth]{./figure/PNG/S3_visitation}
\caption{{\bf Cumulative distribution of the number of locations visited by each Twitter user during different timespan}}
\label{S3_Fig}
\end{figure}

We further studied two aspects of the Twitter user mobility patterns: the distribution of Twitter user displacement and the radius of gyration. 
Twitter user displacement refers to the distance between two consecutive locations in a user's trajectory using a straight-line distance metric.
The radius of gyration describes the deviation of distance from the center of mass in a user's trajectory.
The probability distributions of the collective user displacement $P(d)$ and radius of gyration $P(r_g)$ are presented in Fig.~\ref{S4_Fig}, where the fitting method for identifying different distance ranges is derived from~\cite{jurdak2015}.
The probability distribution of the collective displacements can be approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10m, 70m] (accounting for 3 $\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [70m, 70km] (93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 70km] (4 $\%$ of the population). 
The displacement distance between 70m and 100km can be further approximated by two power law distributions with a cut-off point at 4km (55$\%$ distances are less than 4km and 40$\%$ distances between 4km and 100km), which indicates the urban movement captured by the geo-located Twitter data to reveal two different modes: inter-city and intra-city movement. 
In short, these fitting functions suggest the existence of multi-scale or multi-modal urban movements captured from Twitter users in the United Kingdom, which means the geographically cohesive, non-overlapping urban areas identified in the next section are not just a result of short distance movement but emerge naturally from the broader Twitter user mobility pattern.
Note that a similar multiphase pattern was observed in Twitter user displacements in Australia, but with slightly different distance ranges\cite{jurdak2015}.

Further, we analyzed the distribution of radius of gyration to understand the movement from the point of view of individual Twitter users rather than separate displacements.
The distribution of the radius of gyration can be approximated through a combination of three functions: $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10m$ from [10 m, 30m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50m, 10km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [10km, 100km], where these three functions account for 92$\%$ of all the users.
This suggests that there are three primary types of users that: (1) tend to stay at one location or at nearby locations when they tweet, or (2) tend to move at the intra-city scale when they tweet, or (3)  tend to exhibit a large spatial coverage. 
(1) and (2) account for approximately 53$\%$ of all users.  
The radius of gyration between 30m and 100km can be further approximated by two power law distributions with a cut-off point at 2.5km (35 $\%$ users with radius of gyration less than 2.5km and 57$\%$ users with radius of gyration between 3km and 100km) that suggests two main types of spatial coverage of Twitter user movement within the United Kingdom. 
Note that the accuracy of these values for defining the distance bound depends upon the accuracy of the location information of each geo-located tweet. 
These findings are consistent with the findings in the literature on human mobility, where the radius of gyration of human movement is bounded to different distance ranges~\cite{brockmann2006,gonzalez2008}.
The distance-decay effects found in both user displacements and the radius of gyration shows evidence of spatial proximity in Twitter user movement. 
It explains that the communities of urban regions within the graph space are geographically close, but are able to be separated from other groups, which results in the delineation of urban boundaries based on the spatial interactions of Twitter users.

\begin{figure}[ht]
\includegraphics[width=1.0\linewidth]{./figure/PNG/S4_radius_displacement}
\caption{{\bf The probability distribution of Twitter user displacements and radius of gyration:} (a) The displacement distribution $P(d)$ is approximated by an exponential, a stretched-exponential and a power-law function (b) the distance between [70m, 70km] is approximated by a double power-law functions (c) The distribution of radius of gyration $P(r_g)$ is approximated by the combination of an exponential, a stretched-exponential and a power-law function (d) the distance between [30m, 100 km] is approximated by a double power-law functions}
\label{S4_Fig}
\end{figure}

\subsection*{Redrawing Great Britain’s Urban Boundaries}
The network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells that provide an adequate resolution for a country wide investigation~\cite{ratti2010}.
The edges of this network were derived from the number of directed Twitter user displacements between each pair of cells.
We used this connectivity network as a proxy to partition the space associated with its nodes.
Coherent geographic regions were identified as individual fishnet cells showing more internal user movement compared to user movements across the cell boundaries to neighboring cells.
Fig.~\ref{S5_Fig}  presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4km, greater than 10 km, and using all available displacements together compared to the administrative boundaries of the United Kingdom.
One clear observation across the coarse and fine delineations is that most of the geographic divisions are centered around big urban cores with relatively high populations.
These results are expected given that most of the tweets originate in urban centers.
However, what is remarkable is the performance of this approach in dividing the remaining space between cities.
We found that restricting the trip distance results in different delineations of the catchment area around these centers.
For example, one could explain these effects as a manifestation of the underlying gravity law~\cite{simini2012} and the distance decay effect on attracting movers~\cite{gonzalez2008}.
Remarkably, our approach performed well in terms of dividing the entire space with minimum gaps.
Empty cells were found in regions where no, or few, Twitter users had visited (e.g. forests, agriculture) especially when restricting the analysis to short distance Twitter user displacements.

\begin{figure}[ht]
\includegraphics[width=0.9\linewidth]{./figure/PNG/S5_community}
\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) displacements longer than 10 km (b) displacements shorter than 4 km (c) and displacements longer than 4 km (d) The partition of space was done using a 10 km fishnet to map the directed displacements from and to each cell. Each color represents a unique community with more Twitter users displacements among the cells compared to others. Major cities (urban audit functional areas) and NUTS are displayed in black.}
\label{S5_Fig}
\end{figure}

Regional boundaries inferred from short distance Twitter user displacements (less than 4 km) exhibit very small and fragmented regions, which is probably related to daily commuting around a user's home location. 
Redrawing the boundaries based on longer distance displacements produces more cohesive, large regions.
For example, by partitioning the space based on displacements greater than 10 km created regions that are comparable to the NUTS (Nomenclature of Territorial Units for Statistics - 1) regions (Fig.~\ref{S6_Fig} - a). 
However, the power of this novel mapping technique is not to reproduce the partitions already known, rather it is to point out some of the unexpected boundaries.
For example the boundaries between England and Wales were found to be more diffuse compared to the abrupt boundary of England and Scotland.
Moreover, the city of London has a wider visitor catchment area that extends beyond the authoritative boundaries of the city.
Increasing the displacement distance results in revealing the large region connected to London (Fig.~\ref{S6_Fig}).

Using Twitter user mobility to delineate non-administrative anthropographic boundaries enables the researcher to redraw the city at different mobility ranges inferred objectively from the user's collective distribution. 
In addition, the distance range of the movements is usually explained by local socio-economic factors (e.g., work commuting ) that provide for a specific interpretation of the apparent patterns.
The patterns obtained from Twitter user mobility are comparable to the patterns produced by those of the network of landline phone calls~\cite{ratti2010}.\
For example, the region of Wales appears to consist of three communities as found in the connectivity of both phone calls and long distance movements. 
However, the regions extracted from the mobility network seems to be more spatially consistent with minimal spatial gaps compared to the partitions extracted from land-line call networks in the United Kingcom~\cite{ratti2010}.

\begin{figure}[ht]
\includegraphics[width=0.7\linewidth]{./figure/PNG/S6_community_london}
\caption{{\bf The non-administrative anthropographic regions inferred from Twitter user displacements greater than 4 km (left) and 10 km (right) in comparison with major cities in England (upper figures) and Scotland (bottom figures).}  Each color represents a unique community. Including short distance movements has increased the power to differentiate the influence of nearby cities such as Glasgow and Edinburgh (lower left), while restricting the analysis to longer distance movements grouped travelers from the two previous cities into the same community (lower right).}
\label{S6_Fig}
\end{figure}

A more detailed study was conducted over the greater London region revealing the intra-city spatial interaction patterns.
The spatial partitions derived from a fine grid of 1km using all available Twitter user trips without any restriction on trip distances yields geographic boundaries comparable to some of London's boroughs  (Fig.~\ref{S7_Fig}).
However, some areas are shown to be more cohesive and display greater spatial interactions across the administrative boundaries, for instance, central London.
Although, these results suggest that travelers seem to be localized over certain areas of the city most of the time, some regions do exhibit long distance interaction patterns.
For example, the separate geographic areas in the south of Hillingdon which includes Heathrow Airport exhibits more connectivity to central London than its surrounding areas which is explained by the usual flight passenger routes.
%NOTE: what borders?
The technique also reveals some of the emerging communities around the borders due to the spatial intermingling of both communities.
For example, East Barnet and West Enfield seem to have higher interactions than those resulted from in the emerging cohesive zone between the two boroughs.

\begin{figure}[ht]
\includegraphics[width=0.8\linewidth]{./figure/PNG/S7_london}
\caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.  Each unique color represents a different non-administrative anthropographic region. Notice that some remote regions like the airport (light green region in south of Hillingdon) share the same class with downtown because it is well connected despite the geographic separation.}
\label{S7_Fig}
\end{figure}

\section*{Conclusion}
In this study, we delineated the non-administrative anthropographic urban boundaries within the United Kingdom using a network of Twitter user spatial interactions inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the British Isles to partition the space.
Then by studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell size of 10 km to quantify the spatial coverage of the majority of Twitter users in the United Kingdom. 
Twitter user movements were used to establish a connectivity network of the fishnet cells.
Then we applied the map equation algorithm to partition the network and associated geographic regions.
The strongly connected communities within the network space yields geographically cohesive, non-overlapping urban areas that provides a clear delineation of the urban boundaries of the United Kingdom.
By performing a statistical analysis of Twitter user mobility patterns in the United Kingdom, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
Identifying the connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in the United Kingdom.

The use of Twitter user mobility to delineate non-administrative anthropographic boundaries enables the researcher to redraw the city at different mobility ranges.
Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect the human interaction space.
This study defines non-administrative anthropographic boundaries by investigating human mobility, which could assist in resource allocation, political campaigns and urban planning. However, the geo-located twitter data is not able to generalize to the entire population; therefore, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process. Yet, our approach is still applicable when more detailed mobility data is available.

\section*{Acknowledgments}
The authors would like to thank Dr. Kun Zhao and Dr. Raja Jurdak from CSIRO, Australia for their suggestions in generating Figure 1 in this paper. 
The research was supported from National Science Foundation grants No. xx ...

\section*{Author Contribution}
Conceived and designed the experiments: JY AS DY SW. Performed the experiments: JY DY. Analyzed the data: JY AS. Contributed reagents/materials/analysis tools: JY AS DY AS. Wrote the paper: JY AS SW.

\nolinenumbers

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
% 
\begin{thebibliography}{10}
\bibitem{schliephake}
Schliephake, C., 2014. Urban Ecologies: City Space, Material Agency, and Environmental Politics in Contemporary Culture. Lexington Books.

\bibitem{lynch1960}
Lynch, K., 1960. The image of the city. MIT press.

\bibitem{jiang2015}
Jiang, B., Miao, Y., 2015. The evolution of natural cities from the perspective of location-based social media. The Professional Geographer, 67(2), 295-306.

\bibitem{long2015}
Long, Y., Han, H., Tu, Y., Shu, X., 2015. Evaluating the effectiveness of urban growth boundaries using human mobility and activity records. Cities, 46, 76-84.

\bibitem{liu2015}
Liu, X., Gong, L., Gong, Y., Liu, Y., 2015. Revealing travel patterns and city structure with taxi trip data. J. Transportation Geography, 43, 78–90. doi:10.1016/j.jtrangeo.2015.01.016

\bibitem{lancichinetti2009}
Lancichinetti, A., Fortunato, S., 2009. Community detection algorithms: A comparative analysis. Physical Review E, 80, 056117. doi:10.1103/PhysRevE.80.056117

\bibitem{ratti2010}
Ratti, C., Sobolevsky, S., Calabrese, F., Andris, C., Reades, J., Martino, M., Claxton, R., Strogatz, S.H., 2010. Redrawing the Map of Great Britain from a Network of Human Interactions. PLoS ONE 5, e14248. doi:10.1371/journal.pone.0014248

\bibitem{sobolevsky2013}
Sobolevsky S, Szell M, Campari R, Couronné T, Smoreda Z, Ratti, C., 2013. Delineating Geographical Regions with Networks of Human Interactions in an Extensive Set of Countries. PLoS ONE 8(12): e81707. doi: 10.1371/journal.pone.0081707

\bibitem{kallus2015}
Kallus Z, Barankai N, Szüle J, Vattay G., 2015 Spatial Fingerprints of Community Structure in Human Interaction Network for an Extensive Set of Large-Scale Regions. PLoS ONE 10(5): e0126713. doi: 10.1371/journal.pone.0126713

\bibitem{hawelka}
Hawelka, B., Sitko, I., Beinat, E., Sobolevsky, S., Kazakopoulos, P., Ratti, C., 2014. Geo-located Twitter as proxy for global mobility patterns. Cartography and Geographic Information Science, 41, 260–271. doi:10.1080/15230406.2014.890072

\bibitem{jurdak2015}
Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D., 2015. Understanding Human Mobility from Twitter. PLoS ONE 10, e0131469. doi:10.1371/journal.pone.0131469

\bibitem{thiemann}
Thiemann, C., Theis, F., Grady, D., Brune, R., Brockmann, D., 2010. The Structure of Borders in a Small World. PLoS ONE 5, e15422. doi:10.1371/journal.pone.0015422

\bibitem{domenico2015}
De Domenico, M., Lancichinetti, A., Arenas, A., Rosvall, M., 2015. Identifying Modular Flows on Multilayer Networks Reveals Highly Overlapping Organization in Interconnected Systems. Physical Review X, 5. doi:10.1103/PhysRevX.5.011027

\bibitem{fortunato2007}
Fortunato, S., Barthélemy, M., 2007. Resolution limit in community detection. Proceedings of the National Academy of Sciences, 104, 36–41. doi:10.1073/pnas.0605965104

\bibitem{newman2006}
Newman, M.E.J., 2006. Modularity and community structure in networks. Proceedings of the National Academy of Sciences, 103, 8577–82. doi:10.1073/pnas.0601602103

\bibitem{gonzalez2008}
González, M.C., Hidalgo, C.A., Barabási, A.-L., 2008. Understanding individual human mobility patterns. Nature, 453, 779–82. doi:10.1038/nature06958

\bibitem{coscia2011}
Coscia, M., Giannotti, F., Pedreschi, D., 2011. A Classification for Community Discovery Methods in Complex Networks. Statistical Analysis and Data Mining, 4, 512–546. doi:10.1002/sam.10133

\bibitem{rinzivillo2012}
Rinzivillo, S., Mainardi, S., Pezzoni, F., Coscia, M., Pedreschi, D., Giannotti, F., 2012. Discovering the Geographical Borders of Human Mobility. KI - Künstl. Intell. 26, 253–260. doi:10.1007/s13218-012-0181-8

\bibitem{zhong2014}
Zhong, C., Arisona, S.M., Huang, X., Batty, M., Schmitt, G., 2014. Detecting the dynamics of urban structure through spatial network analysis. International Journal of Geographical Information Science, 28, 2178–2199. doi:10.1080/13658816.2014.914521

\bibitem{qian2013}
Qian, W., Stanley, K. G., Osgood, N. D., 2013. The impact of spatial resolution and representation on human mobility predictability. In Web and Wireless Geographical Information Systems,  pp. 25-40, Springer Berlin Heidelberg.

\bibitem{sakaki2010}
Sakaki, T., Okazaki, M., Matsuo, Y., 2010. Earthquake Shakes Twitter Users: Real-time Event Detection by Social Sensors, in: Proceedings of the 19th International Conference on World Wide Web, WWW ’10. ACM, New York, NY, USA, pp. 851–860. doi:10.1145/1772690.1772777

\bibitem{zandbergen2009}
Zandbergen, P.A., 2009. Accuracy of iPhone Locations: A Comparison of Assisted GPS, WiFi and Cellular Positioning. Transactions in GIS, 13, 5–25. doi:10.1111/j.1467-9671.2009.01152.x

\bibitem{liuPopMobility}
Liu, J., Zhao, K., Khan, S., Cameron, M., Jurdak, R., 2014. Multi-scale Population and Mobility Estimation with Geo-tagged Tweets. ArXiv14120327 Phys.

\bibitem{openshaw1984}
Openshaw, S., 1984. The modifiable areal unit problem. Geo Abstracts University of East Anglia.

\bibitem{wong2009}
Wong, D., 2009. The modifiable areal unit problem (MAUP). SAGE Publications: London, UK.

\bibitem{brockmann2006}
Brockmann, D., Hufnagel, L., Geisel, T., 2006. The scaling laws of human travel. Nature 439, 462–5. doi:10.1038/nature04292

\bibitem{song2012}
Song, C., Wang, D., Barabási, A.-L., 2012. Connections between human dynamics and network science. ArXiv Prepr. ArXiv12091411.

\bibitem{guimera2004}
Guimerà, R., Sales-Pardo, M., Amaral, L.A.N., 2004. Modularity from fluctuations in random graphs and complex networks. Physical Review E, 70, 025101. doi:10.1103/PhysRevE.70.025101

\bibitem{good2010}
Good, B.H., de Montjoye, Y.-A., Clauset, A., 2010. Performance of modularity maximization in practical contexts. Physical Review E, 81, 046106. doi:10.1103/PhysRevE.81.046106

\bibitem{rosvall2008}
Rosvall, M., Bergstrom, C.T., 2008. Maps of random walks on complex networks reveal community structure. Proceedings of the National Academy of Sciences, 105, 1118–1123.

\bibitem{rosvall2010}
Rosvall, M., Axelsson, D., Bergstrom, C.T., 2010. The map equation. The European Physical Journal Special Topics, 178, 13–23. doi:10.1140/epjst/e2010-01179-1

\bibitem{clauset2009}
Clauset, A., Shalizi, C., Newman, M., 2009. Power-Law Distributions in Empirical Data. Society for Industrial and Applied Mathematics Review. 51, 661–703. doi:10.1137/070710111

\bibitem{rhee2011}
Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S. J., and Chong, S., 2011. On the levy-walk nature of human mobility. IEEE/ACM transactions on networking (TON), 19(3), 630-643.

\bibitem{reynolds2012}
Reynolds, A., 2012. Truncated levy walks are expected beyond the scale of data collection when correlated random walks embody observed movement patterns. Journal of The Royal Society Interface, 9(68), 528-534.

\bibitem{zhao2015}
Zhao, K., Musolesi, M., Hui, P., Rao, W., and Tarkoma, S., 2015. Explaining the power-law distribution of human mobility through transportation modality decomposition. Scientific reports, 5.

\bibitem{simini2012}
Simini, F., González, M. C., Maritan, A., Barabási, A. L., 2012. A universal model for mobility and migration patterns. Nature, 484(7392), 96-100.

%\bibitem{blondel2008}
%Blondel, V.D., Guillaume, J., Lambiotte, R., Lefebvre, E., 2008. Fast unfolding of community hierarchies in large networks. Networks 1–6.
%

\end{thebibliography}
\end{document}

### 2016-01-16 urban_boundaries_gb/Twitter_Urban_Boundary.edits.tex
to send out tomorrow

@@
 It provides a new understanding of the interaction between human activity and urban structures.
-%NOTE: I'm not sure how twitter relates to urban structure...
 
-%NOTE: I did not review the figures or figure captions
 \section*{Materials and Methods}
@@
 \section*{Conclusion}
-In this study, we delineated the non-administrative anthropographic urban boundaries within the United Kingdom using a network of Twitter user spatial interactions inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
+In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
 In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the British Isles to partition the space.
@@
 By performing a statistical analysis of Twitter user mobility patterns in the United Kingdom, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
-Identifying the connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in the United Kingdom.
+Identifying the connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in Great Britain.
 

### 2016-01-17 urban_boundaries_gb/Twitter_Urban_Boundary.tex
new version emerged from Austin's edit

--- 2016-01-15 Twitter_Urban_Boundary.tex
@@
 In addition, the distance range of the movements usually could be explained by local socioeconomic factors (e.g., work commuting ), which could provide some specific interpretation of the apparent patterns.
-The patterns obtained from Twitter users mobility patterns are comparable to the patterns produced by division the network of landline phone call~\cite{ratti2010}.\
+The patterns obtained from Twitter users mobility patterns are comparable to the patterns produced by division the network of landline phone call~\cite{ratti2010}.
 For example, the region of Wales appeared to consists of three communities as found by connectivity of both phone calls and long distance movements. 
@@
 
-%\subsection*{xx}
-%see \nameref{S1_Fig}.
-%
-%\section*{Supporting Information}
-%
-%% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
-%\subsection*{S1 A scalable data processing framework}
-%\label{S1_framework}
-
 \section*{Acknowledgments}
@@
 
-%\section*{References}
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here.
-% 
 \begin{thebibliography}{10}

### 2016-02-19 urban_boundaries_gb/IJGIS/Twitter_Urban_Boundary.tex
new

% tGISguide.tex
% v3.4 released April 2009

\documentclass[]{tGIS2e}

\citestyle{tGIS}
\begin{document}

\doi{10.1080/1365881YYxxxxxxxx}
\issn{1362-3087} \issnp{1365-8816} \jvol{00} \jnum{00} \jyear{2009} %\jmonth{February}

\markboth{Taylor \& Francis and I.T. Consultant}{International Journal of Geographical Information Science}

\articletype{GUIDE}

\title{{\itshape International Journal of Geographical Information Science} -- \LaTeXe\ style guide
for authors\newline (Style 2 + References Style V)}

\author{Taylor \& Francis$^{a}$$^{\ast}$\thanks{$^\ast$Corresponding author. Email: latex.helpdesk@tandf.co.uk
\vspace{6pt}} and I.T. Consultant$^{b}$\\\vspace{6pt}  $^{a}${\em{4 Park Square, Milton Park, Abingdon, UK}};
$^{b}${\em{Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t, Freiburg,
Germany}}\\\vspace{6pt}\received{v2.3 released April 2009} }

\maketitle

\begin{abstract}
This guide 
\end{abstract}

\noindent{\bf{Please note that the index following the abstract in this guide is provided for information only. An index is not required in submitted papers.}}

\section{Introduction}

All submissions of manuscripts for possible publication in {\itshape International Journal of Geographical Information Science} ({\it tGIS}\,)  should be made online via the journal's Manuscript Central site ({\tt{http://mc.manuscriptcentral.com/ijgis}}). New users should first create an account. Once logged on to the site, submissions should be made via the Author Centre. Online user guides and access to a helpdesk are available on this website.

{\it tGIS} accepts papers in any standard format, including Microsoft$\circledR$ Word, PostScript and PDF. Files submitted in formats other than PDF will automatically be converted to a PDF for the review process. \LaTeXe\ files should be converted to PDF prior to submission because Manuscript Central is not able to convert \LaTeXe\ files into PDFs directly. This journal does not accept Microsoft Word 2007 documents. Please use Word's `Save As' option to save your document as an older (.doc) file type. For the submission of manuscripts created using \LaTeXe\, see Section~\ref{S1.2}.

The layout design for {\it tGIS} has been implemented as a \LaTeXe\ Class file. The {\it tGIS} Class file is
based on {\tt article.cls}. Commands that differ from the standard \LaTeXe\ interface, or which are provided in
addition to the standard interface, are explained in this guide. This guide is not a substitute for the \LaTeXe\
manual itself.

This guide can be used as a template for composing an article for submission by cutting, pasting, inserting and
deleting text as appropriate, using the LaTeX environments provided (e.g. \verb"\begin{equation}",
\verb"\begin{corollary}").\vspace{6pt}

\subsection{The {\bi tGIS} document style}

The use of \LaTeXe\ document styles allows a simple change of style (or style option) to transform the appearance
of your document. The tGIS2e Class file preserves the standard \LaTeXe\ interface such that any document that can
be produced using the standard \LaTeXe\ {\tt article} style can also be produced with the {\it tGIS} style.
However, the measure (or width of text) is narrower than the default for {\tt article}, therefore line breaks
will change and long equations may need re-formatting.

When your article appears in the print edition of the {\it gPAV} journal (and exactly reproduced in the PDF
version online), it will have been typeset in Monotype Times. As most authors do not own this font, it is inevitable that the page make-up will change with the change of font. For this reason, we ask authors to ignore details such as slightly long lines, page stretching, or figures falling out of synchronization with their citations in the text, because these details will be dealt with during proofing.

\subsection{Submission of \LaTeXe\ articles to the journal}\label{S1.2}

All submissions of manuscripts for possible publication should be made online via the journal's Manuscript Central site ({\tt{http://mc.manuscriptcentral.com/ijgis}}). New users should first create an account. Once logged on to the site, submissions should be made via the Author Centre. Online user guides and access to a helpdesk are available on this website. \LaTeXe\ files should be converted to PDF prior to submission because Manuscript Central is not able to convert \LaTeXe\ files into PDFs directly. The PDF should be uploaded together with the \LaTeXe\ source files and any graphics files.

General Instructions for Authors may be found at
\begin{center}(\nobreak{\tt{http://www.tandf.co.uk/journals/authors/tgisauth.asp}}).\end{center}

Only `open-source' \LaTeXe\ should be used, not proprietary systems such as TCI LaTeX or Scientific WorkPlace. Similarly, Class files such as REVTex4 that produce a document in the style of a different publisher and journal should not be used for preference.

Appropriate gaps should be left for figures, of which original versions and copies should also be supplied.
Authors should ensure that their figures are suitable (in terms of lettering size, etc.) for the reductions they
intend.

Authors who wish to incorporate Encapsulated PostScript artwork directly in their articles can do so by using
Tomas Rokicki's {\tt EPSF} macros (which are supplied with the DVIPS PostScript driver). See Section~\ref{eps},
which also demonstrates how to treat landscape pages. Please remember to supply any additional figure macros you
use with your article in the preamble before \verb"begin{document}". Authors should not attempt to use
implementation-specific \verb"\special"'s directly.

Ensure that any author-defined macros are gathered together in the source file, just before the
\verb"\begin{document}" command.

Please note that, if serious problems are encountered with the coding of a paper (missing author-defined macros,
for example), it may prove necessary to divert the paper to conventional typesetting, i.e. it will be re-keyed.

\section{Using the {\bi tGIS} Class file}

If the file {\tt tGIS2e.cls} is not already in the appropriate system directory for \LaTeXe\ files, either
arrange for it to be put there, or copy it to your working folder. The {\it tGIS} document style is implemented
as a complete document style, {\em not\/} a document style option. In order to use the {\it tGIS} style, replace
{\tt `article'} by {\tt `tGIS2e'} in the \verb"\documentclass" command at the beginning of your document:
%
\begin{verbatim}
\documentclass{article}
\end{verbatim}
%
is replaced by
%
\begin{verbatim}
\documentclass{tGIS2e}
\end{verbatim}
%
In general, the following standard document style options should {\em not\/} be used with the {\it tGIS} style:
%
\begin{enumerate}
   \item {\tt 10pt}, {\tt 11pt}, {\tt 12pt} -- unavailable;
   \item oneside (no associated style file) -- oneside is the default;
   \item {\tt leqno} and {\tt titlepage} -- should not be used;
   \item {\tt singlecolumn} -- is not necessary as it is the default style.
\end{enumerate}
%

\subsection{Landscape pages}\label{eps}

If a table or illustration is too wide to fit the standard measure, it must be turned, with its caption, through
90$^{\circ}$ anticlockwise. Landscape illustrations and/or tables can be produced directly using the tGIS2e style
file using \verb"\usepackage{rotating}" after \verb"\documentclass{tGIS2e}". The following commands can be used
to produce such pages.
%
\begin{verbatim}
\setcounter{figure}{2}
\begin{sidewaysfigure}
\centerline{\epsfbox{fig1.eps}}
\caption{This is an example of figure caption.}
\label{landfig}
\end{sidewaysfigure}
\end{verbatim}
%
\begin{verbatim}
\setcounter{table}{0}
\begin{sidewaystable}
  \tbl{The Largest Optical Telescopes.}
    \begin{tabular}{@{}llllcll}
    .
    .
    .
  \end{tabular}\label{tab1}
\end{sidewaystable}
\end{verbatim}
%
Before any float environment, use the \verb"\setcounter" command
as above to fix the numbering of the caption. Subsequent captions
will then be automatically renumbered accordingly.

\section{Additional features}

In addition to all the standard \LaTeXe\ design elements, {\it tGIS} style includes a separate command for specifying short versions of the authors' names and the journal title for running headlines on the left-hand (verso) and right-hand (recto) pages, respectively (see Section~\ref{markboth}).  In general, once you have used this additional {\tt tGIS2e.cls} feature in your document, do not process it with a standard \LaTeXe\ style file.

\subsection{Footnotes to article titles and authors' names}

On the title page, the \verb"\thanks" control sequence may be used to produce a footnote to either the title or authors' names.

\vspace{6pt}Footnote symbols should be used in the order: $\dagger$
(coded as \verb"\dagger"),\break $\ddagger$ (\verb"\ddagger"), $\S$ (\verb"\S"),
$\P$ (\verb"\P"), $\|$ (\verb"\|"), $\dagger\dagger$
(\verb"\dagger\dagger"),\break $\ddagger\ddagger$
(\verb"\ddagger\ddagger"),  $\S\S$ (\verb"\S\S"), $\P\P$ (\verb"\P\P"),
$\|\|$ (\verb"\|\|").

Note that footnotes to the text will automatically be assigned the superscript
 symbols 1, 2, 3,... by the Class file, beginning afresh on each
page.\footnote{These symbols will be changed to the style of the journal by the
 typesetter during preparation of your proofs.}

The title, author(s) and affiliation(s) should be followed by the {\verb"\maketitle"} command.

\subsection{Abstracts}

At the beginning of your article, the title should be generated in the usual way using the {\verb"\maketitle"}
command. Immediately following the title you should include an abstract. The abstract should be enclosed within
an {\tt abstract} environment. For example, the titles for this guide were produced by the following source code:
%
\begin{verbatim}

\title{{\itshape International Journal of Geographical Information %
Science} -- \LaTeXe\ style guide for authors\newline (Style 2 + %
References Style V)}

\author{Taylor \& Francis$^{a}$$^{\ast}$\thanks{$^\ast$Corresponding %
author. Email: latex.helpdesk@tandf.co.uk \vspace{6pt}} and I.T. %
Consultant$^{b}$\\\vspace{6pt}  $^{a}${\em{4 Park Square, Milton Park, %
Abingdon, UK}}; $^{b}${\em{Institut f\"{u}r Informatik, %
Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany}}\\\vspace{6pt}%
\received{v2.3 released April 2009} }

\maketitle
\begin{abstract}
This guide is for authors who are preparing papers for the Taylor \& %
Francis journal {\em International Journal of Geographical Information %
Science} ({\it tGIS}\,) using the \LaTeXe\ document preparation system %
and the Class file {\tt tGIS2e.cls}, which is available via the journal %
homepage on the Taylor \& Francis website (see Section~\ref{FTP}). %
Authors planning to submit their papers in \LaTeXe\ are advised to %
use {\tt tGIS2e.cls} as early as possible in the creation of their %
files. \end{abstract}

\end{verbatim}

\noindent{\bf{(Please note that the percentage signs at the ends of lines that quote source code in this document are not part of the coding but have been inserted to achieve line wrapping at the appropriate points.)}}

\subsection{Lists}

The {\it tGIS} style provides numbered and unnumbered lists using the {\tt enumerate} environment and bulleted
lists  using the {\tt itemize} environment.

The enumerated list numbers each list item with arabic numerals:
%
\begin{enumerate}
   \item first item
   \item second item
   \item third item
\end{enumerate}
%
Alternative numbering can be achieved by an argument in square brackets, e.g. \verb"\item[(i)] first item".
%
Unnumbered lists are also provided using the {\tt enumerate} environment.
For example,
\begin{enumerate}
   \item[] First unnumbered indented item without label.
   \item[] Second unnumbered item.
   \item[] Third unnumbered item.
\end{enumerate}
was produced by:
%
\begin{verbatim}
\begin{enumerate}
  \item[] First unnumbered indented item...
  \item[] Second unnumbered item.
  \item[] Third unnumbered item.
\end{enumerate}
\end{verbatim}
%
Bulleted lists are provided using the {\tt itemize} environment. For example,
\begin{itemize}
\item First bulleted item
\item Second bulleted item
\item Third bulleted item
\end{itemize}
was produced by:
\begin{verbatim}
  \begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
  \end{itemize}
\end{verbatim}

\section[]{Some guidelines for using standard features}

The following notes may help you achieve the best effects with the tGIS2e Class file.

%\begin{figure}
%\begin{center}
%\vspace{36pt}
%\begin{minipage}{100mm}
%\subfigure[]{
%\resizebox*{5cm}{!}{\includegraphics{senu_gr1.eps}}}%
%\subfigure[]{
%\resizebox*{5cm}{!}{\includegraphics{senu_gr2.eps}}}%
%\caption{Example of a two-part figure with individual %
%sub-captions showing that all lines of figure captions range left.}%
%\label{sample-figure}
%\end{minipage}
%\end{center}
%\end{figure}

\subsection{Acknowledgements}
zz

\subsection{References}\label{refs}
\begin{thebibliography}{9}

\markboth{Taylor \& Francis and I.T. Consultant}{International Journal of Geographical Information Science}

\bibitem[\protect\citeauthoryear{Agutter}{1995}]{Agu95}
Agutter, A.J., 1995. The linguistic significance of current British slang.
  Thesis (PhD). Edinburgh University, UK.

\bibitem[\protect\citeauthoryear{Cutler {\itshape{et~al.}}}{1986}]{cww86}
Cutler, T., Williams, K., and Williams, J., 1986. {\itshape Keynes, Beveridge and
  beyond}. 3rd ed. Twentieth century political economics Vol. II. London:
  Routledge.

\bibitem[\protect\citeauthoryear{Evans}{1994}]{ev94}
Evans, W.A., 1994. Approaches to intelligent information retrieval. {\itshape
  Information Processing and Management}, 7 (2), 147--168.

\bibitem[\protect\citeauthoryear{French}{1988}]{fzf88}
French, F., 1988. English title of a chapter in the translation of a book in a
  foreign language.  {\itshape{In}}: {\itshape Title of a book in another language (Quoted in
  that language)}  [{\itshape English translation}],  translated by P. Smith.
  New York: Dover (original work published 1923).

\bibitem[\protect\citeauthoryear{Glover and Ribeiro}{1951}]{GloRib51}
Glover, F. and Ribeiro, C.C., eds, 1951. {\itshape
Lessons of the British war economy}. 2nd ed. Westport, CT: Greenwood Press, 1--24.

\bibitem[\protect\citeauthoryear{Holland}{2004}]{Holl04}
Holland, M., 2004. {\itshape Guide to citing Internet sources} [online]. Poole, UK: Bournmouth University. Available from:
  http://www.bournemouth.ac.uk/library/using/guide\_to\_citing\_internet\_sourc.%
  html [Accessed 4 November 2004].

\bibitem[\protect\citeauthoryear{Kern}{1997}]{hk97}
Kern, H., 1997. The resurgent Japanese economy and a Japan--United States free trade
  agreement. {\itshape {In}}: C.~Lambert and G.~Holst, eds. {\itshape 4th international conference on the restructuring of the economic and political system in Japan}, Milan, Italy, 21--25 May 1996. Singapore: World Scientific, 147--156.

\bibitem[\protect\citeauthoryear{Korb}{1995}]{Kor95}
Korb, K.B., 1995. Persons and things: book review of Bringsjord on
  robot-consciousness. {\itshape Psycoloquy} [online], 6 (15). Available from: http://psycprints.ecs.soton.ac.uk/archive/00000462/ [Accessed 20 May 2004].

\bibitem[\protect\citeauthoryear{Misner}{1973}]{cwm73}
Misner, C.W., ed., 1973. Efficient algorithms for layer assignment problems. {\itshape{In}}:
  {\itshape Gravitation in a collapsing Universe}. San Francisco, CA:
  Freeman.

\bibitem[\protect\citeauthoryear{Patel}{2002}]{fwp02}
Patel, F.W., 2002. {\itshape Banking technology in an age of cynicism}. Mongraphs on
  technical aspects Vol. XIII. New York: Dover.

\bibitem[\protect\citeauthoryear{Pierce {\itshape{et~al.}}}{1976}]{PeaEtAl76}
Pierce, I.F., {\itshape{et al.}}, 1976. A
  model of output, employment, wages and prices in the UK. {\itshape{In}}: M.~Laguna and
  J.L. Gonz\'{a}les-Velarde, eds. {\itshape Computing tools for modeling, optimization and simulation: interfaces in
  computer science and operations research}. 2nd  ed. Boston, MA: Cambridge University
  Press, 1--24.
\end{thebibliography}

%\markboth{Taylor \& Francis and I.T. Consultant}{International Journal of Geographical Information Science}

\label{lastpage}

\end{document}

### 2016-02-20 urban_boundaries_gb/IJGIS/Paper.tex
new submission

--- 2016-01-16 urban_boundaries_gb/Twitter_Urban_Boundary.edits.tex
@@
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+% tGISguide.tex
+% v3.4 released April 2009
 
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% fixltx2e package for \textsubscript
-\usepackage{fixltx2e}
-
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
+\documentclass[]{tGIS2e}
 % line numbers
@@
 
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% rotating package for sideways tables
-\usepackage{rotating}
-
-% Remove comment for double spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-\date{}
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr,graphicx}
-\graphicspath{ {/figures/} }
-\usepackage{epstopdf}
-\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\sf PLOS}
-
-\usepackage[section]{placeins}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-%% END MACROS SECTION
+%\citestyle{tGIS}
 
 \begin{document}
-\vspace*{0.35in}
 
-% Title must be 250 characters or less.
-% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
-\begin{flushleft}
-{\Large
-\textbf\newline{Delineate urban boundaries in Great Britain from the network of Twitter user spatial interactions}
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Junjun Yin\textsuperscript{1, 2, 3},
-Aiman Soliman\textsuperscript{1, 2, 4},
-Dandong Yin\textsuperscript{1, 2, 3},
-Shaowen Wang\textsuperscript{1, 2, 3, 4, $\ast$}
-\\
-\bigskip
-\bf{1} CyberGIS Center for Advanced Digital and Spatial Studies
-\\
-\bf{2} CyberInfrastructure and Geospatial Information Laboratory (CIGI)
-\\
-\bf{3} Department of Geography and Geographic Information Science
-\\
-\bf{4} National Center for Supercomputing Applications
-\\
-\bf{} University of Illinois at Urbana-Champaign, 61801, IL, USA
-\\
-\bigskip
+%\doi{10.1080/1365881YYxxxxxxxx}
+%\issn{1362-3087} \issnp{1365-8816} \jvol{00} \jnum{00} \jyear{2009} %\jmonth{February}
 
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-% 
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
+%\markboth{Taylor \& Francis and I.T. Consultant}{International Journal of Geographical Information Science}
 
-% Current address notes
-%\textcurrency a Insert current address of first author with an address update
-% \textcurrency b Insert current address of second author with an address update
-% \textcurrency c Insert current address of third author with an address update
+\articletype{RESEARCH ARTICLE}
 
-% Deceased author note
-%\dag Deceased
+\title{{\itshape Delineate urban boundaries in Great Britain from the network of Twitter user spatial interactions} }
+\maketitle
 
-% Group/Consortium Author Note
-%\textpilcrow Membership list can be found in the Acknowledgments section.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* shaowen@illinois.edu
-
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
+\begin{abstract}
 Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns.
@@
 We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
-The result of strongly connected urban regions, or communities, in the network space yield geographically cohesive, non-overlapping urban areas that delineate the non-administrative anthropographic urban boundaries of Great Britain.
-The technique was applied at the national scale (Great Britain) and the municipal scale (the London metropolis). 
+The result of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas that provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
+The technique was applied to both national scale (Great Britain) and municipal scale (the London metropolis). 
 While our results corresponded well to the administrative boundaries, many unexpected and interesting boundaries were identified.
+\newline
 
+\noindent{\bf{Keywords:}} mobility pattern, urban boundary, spatial interaction, spatial network, community structure
+\end{abstract}
 \linenumbers
-\section*{Introduction}
+\section{Introduction}
+\markboth{International Journal of Geographical Information Science}{International Journal of Geographical Information Science}
 Official urban boundaries are defined by government agencies for political and administrative purposes.
-Urban environments are conceptualized as spaces that are recreated and formed by human activities~\cite{schliephake}.
-A fundamental question when using the administrative, ``top-down'', approach for defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
-These interactions can take the form of trade, commerce, social connections, and political activity.
-Urban boundaries that respect the human interaction space can be very import to city planning, traffic management and resource allocation~\cite{lynch1960,jiang2015,liu2015,long2015}.
-Many studies adopt a ``bottom-up'' approach to urban boundary delineation; where the geographic space is partitioned into small units and each unit is modeled as a node within a network structure.
+Urban environments are conceptualized as spaces that are recreated and formed by human activities~\citep{schliephake}.
+A fundamental question when using the administrative, ``top-down'', approach to defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
+These interactions can take the form of trade, commerce, social connections, and political activity across the borders.
+Urban boundaries that respect the human interaction space can be very import to city planning, traffic management and resource allocation~\citep{lynch1960,jiang2015,liu2015,long2015}.
+Many studies adopt a ``bottom-up'' approach to urban boundary delineation, where the geographic space is partitioned into small units and each unit is modeled as a node within a network structure.
 A suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interaction among the nodes~\cite{lancichinetti2009}.
 Different social and physical human interactions were considered to establish the edges of the network connecting the nodes.
-For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in the United Kingdom~\cite{ratti2010}.
-% does ratti or sobolevsky argue the following... who are "the authors"?
-Extending the previous method to different countries~\cite{sobolevsky2013}, the authors argue, yields cohesive geographic divisions that mark the socio-economic boundaries. 
-% I think these citations should expand to include the author's names, not just [9].
-While~\cite{kallus2015} use social ties of Twitter users to identify cohesive regions for different countries across the world, the authors found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.
+For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in Great Britain~\cite{ratti2010}.
+Extending the previous method to different countries~\cite{sobolevsky2013}, the authors argue that this method yields cohesive geographic divisions that follow the socio-economic boundaries.
+While other researchers use social ties of Twitter users to identify cohesive regions for different countries across the world~\cite{kallus2015}, they found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.
 
-In this study, we describe a novel approach to delineate urban boundaries based on the movements of 
+In this study, we describe a novel approach to delineating urban boundaries based on the movements of 
 Twitter users extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
@@
 We argue here that Twitter user mobility patterns provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation. 
-A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in the United Kingdom.
-In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity 
-% I think UK calls them postal codes and not zip codes
-that is limited to the postal code level~\cite{thiemann}.  % everything has sparsity at some scale...
+A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in Great Britain.
+In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity that is limited to the postal code level~\cite{thiemann}.
 
-We delineated the geography of urban boundaries in the United Kingdom by imposing a virtual fishnet over the British Isles. % Great Britain is, itself, an island.
+We delineated the geography of urban boundaries in Great Britain by imposing a virtual fishnet over the islands of Great Britain.
 Twitter user movements were used to establish the connections between the fishnet's cells to form a connectivity network, where each cell acts as a node within the network.
-We applied the map equation algorithm~\cite{domenico2015} to partition the network and associate geographic regions.
-The map equation algorithm was selected to avoid the inherent resolution problem~\cite{fortunato2007} of the common modularity maximization method~\cite{newman2006}. 
-We found that the collective mobility patterns of Twitter users in the United Kingdom are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points.
-The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in the United Kingdom.
+We applied the map equation algorithm~\citep{domenico2015} to partition the network and associate geographic regions.
+The map equation algorithm was selected to avoid the inherent resolution problem~\cite{fortunato2007} of the common modularity maximization method~\citep{newman2006}. 
+We found that the collective mobility patterns of Twitter users in Great Britain are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points.
+The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of the urban space in Great Britain.
 Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. 
-It provides a new understanding of the interaction between human activity and urban structures.
+It provides a new understanding of the interactions between human activity and urban structures.
 
-\section*{Materials and Methods}
-\subsection*{Overview}
+\section{Materials and Methods}
+\subsection{Overview}
 We use large-scale Twitter user spatial interactions inferred from the collective mobility patterns of Twitter users to delineate urban boundaries in Great Britain.
@@
 This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two recorded locations is one month.
-To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the British Isles.
+To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the islands of Great Britain.
 Twitter user movements were then used to establish the connectivity between fishnet cells to form a connectivity network where each cell is considered a node within the network. 
-Finally, by detecting strongly connected clusters in the network space using community detection methods~\cite{coscia2011}, we are able to reveal urban boundaries within the geographic space. 
+Finally, by detecting strongly connected clusters in the network space using community detection methods~\cite{coscia2011}, we were able to reveal urban boundaries within the geographic space. 
 An overview of the approach is illustrated in Fig.~\ref{S1_Fig} and the details are presented in the following sections.
 
+%\begin{figure}[ht]
+%\includegraphics[width=1\linewidth]{./figure/S1_overview_Fig_2}
+%\caption{{\bf An overview for delineating urban boundaries from Twitter user movements}}
+%\label{S1_Fig}
+%\end{figure}
+
 \begin{figure}[ht]
-\includegraphics[width=1\linewidth]{./figure/PNG/S1_overview_Fig_2}
-\caption{{\bf An overview for delineating urban boundaries from Twitter user movements}}
+\begin{center}
+\vspace{36pt}
+\includegraphics[width=1\linewidth]{./figure/S1_overview_Fig_2}
+\caption{\bfseries{An overview for delineating urban boundaries from Twitter user movements}}
 \label{S1_Fig}
+\end{center}
 \end{figure}
 
-\subsection*{Geo-located Twitter Data}
+\subsection{Geo-located Twitter Data}
 A geo-located tweet is a Twitter message with an additional geo-tag expressed as a pair of geographical coordinates that represent the location from which the tweet was sent.
-For this study, geo-located tweets were collected using the Twitter Streaming API (\url{https://dev.twitter.com/streaming/overview}) by supplying a geographical bounding box to retrieve all the  geo-located tweets within an area of interest.
-% is it the entire UK or the British Isles? It is not Great Britain.
-To ensure complete coverage of the United Kingdom, we set the bounding box to the British Isles using the lower left and upper right coordinates (49.497, -14.854), (61.186, 2.637) respectively.
-This does include part of France.
-% ireland is part of the british isles
-We implemented a data crawler to continuously collect 7-months of data (June $1^{st}$ -- December $31^{st}$, 2014) resulting in over 101.8 million tweets with a total data volume of 60 GB which we restrict to 69 million based on a process outlined below.
+For this study, geo-located tweets were collected using the Twitter Streaming API (
+{\tt{https://dev.twitter.com/streaming/overview}}) by supplying a geographical bounding box to retrieve all the  geo-located tweets within an area of interest.
+To ensure complete coverage of Great Britain, we set the bounding box to the British Isles using the lower left and upper right coordinates (49.497, -14.854), (61.186, 2.637) respectively.
+This does include the whole of Ireland part of France.
+We implemented a data crawler to continuously collect 7-months of data (June $1^{st}$ -- December $31^{st}$, 2014) resulting in over 101.8 million tweets with a total data volume of 60 GB, which we restrict to 69 million based on a process outlined below.
 To showcase the overall spatial coverage of the collected geo-located tweets, a density map of the tweet locations in British Isles for July 2014 is shown in Fig.~\ref{S2_Fig}.
-The collected point visualization reveals the geography of cities. Notice the clusters with higher densities of tweets that correspond to the locations of major cities.
+The collected point visualization reveals the geography of cities.
+Notice the clusters with higher densities of tweets correspond to the locations of major cities.
 
 \begin{figure}[ht]
-\includegraphics[width=0.7\linewidth]{./figure/PNG/S2_twitter_density_Fig_1}
-\caption{{\bf A density map of the Twitter user locations for July 2014}}
+\begin{center}
+\includegraphics[width=0.8\linewidth]{./figure/S2_twitter_density_Fig_1}
+\caption{\bfseries{A density map of the Twitter user locations for July 2014}}
 \label{S2_Fig}
+\end{center}
 \end{figure}
@@
 Because the original location information embedded in the geo-tag is given in units of latitude and longitude, we projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations.
-Finally, we used the geographical boundary of the United Kingdom, which is derived from Office for National Statistics (ONS) of UK (\url{http://www.ons.gov.uk/ons}), to further restrict the remaining tweets to be ``domestic".
+Finally, we used the geographical boundary of Great Britain, which is derived from Office for National Statistics (ONS) of UK ({\tt{http://www.ons.gov.uk/ons}}), to further restrict the remaining tweets to be ``domestic".
 Based on these restrictions, the filtered dataset for the following study contains 69,847,497 tweets made by 1,153,891 twitter users.
@@
 
-\subsection*{A network of large-scale Twitter user spatial interactions}
+\subsection{A network of large-scale Twitter user spatial interactions}
 Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns. 
 Some urban regions are more strongly connected to each other than other urban regions.
-Therefore, this study connects urban regions when a twitter user begins in one region and ends in another region.
-These connections can be represented by an origin-destination (OD) matrix based on the collective Twitter user displacement within the dataset.
-This OD matrix is essentially a mathematical representation of a weighted directed graph $G\equiv\langle V, E_{w}\rangle$ where $V$ is a set of spatial nodes corresponding to the underlying urban regions and $E_{w}$ is a set of edges representing the connections between a pair of nodes and the corresponding weights that are assigned to the accumulated volume of Twitter user movement.
+Therefore, this study connects urban regions when a twitter user's movement begins in one region and ends in another region.
+These connections can be represented by an origin-destination (OD) matrix based on the collective Twitter user displacements within the dataset.
+This OD matrix is essentially a mathematical representation of a weighted directed graph $G\equiv\langle V, E_{w}\rangle$, where $V$ is a set of spatial nodes corresponding to the underlying urban regions and $E_{w}$ is a set of edges representing the connections between a pair of nodes and the corresponding weights are assigned by the accumulated volume of Twitter user movements.
 
-To build our spatial network at the kingdom level, we had to determine the basic units to serve as spatial nodes of the connectivity network of urban regions.
+To build our spatial network at a national level, we had to determine the basic units to serve as spatial nodes of the connectivity network of urban regions.
 Previous studies have suggested equi-distant spatial tessellation to generate nodes, which uses voronoi polygons to partition the space based on the collected points~\cite{rinzivillo2012,zhong2014}. 
@@
 Another popular approach is to partition the space into a grid of spatial pixels~\cite{liuPopMobility,ratti2010}.
-However, the size of the cell can potentially lead to biases due to the Modifiable Area Unit Problem (MAUP)~\cite{openshaw1984,wong2009}.
-To compare our investigation with the findings of similar studies, and avoid subjectively deciding the cell size, we performed a statistical analysis of Twitter user mobility patterns in the United Kingdom and measured the distribution of collective Twitter user displacements and the radius of gyrations of individuals \cite{gonzalez2008,jurdak2015}.
+However, the size of the cell can potentially lead to biases due to the Modifiable Area Unit Problem (MAUP)~\cite{openshaw1984,wong2009}, where different choices of unit size can lead to significant variant findings.
+To compare our investigation with the findings of similar studies, and avoid subjectively deciding the cell size, we performed statistical analysis of Twitter user mobility patterns in Great Britain and measured the distribution of collective Twitter user displacements and the radius of gyrations of individuals \cite{gonzalez2008,jurdak2015}.
 The radius of gyration is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008}, which is defined as Eq. \eqref{eq:2}:
+
 \begin{equation} \label{eq:2}
@@
 \end{equation}
+
 \noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
-By examining the probability distributions of the radius of gyration, also known as the spatial dispersal kernel $P(r_g)$~\cite{brockmann2006}, we chose 10 km as the cell size to quantify the spatial coverage of the majority of Twitter users in the United Kingdom (Fig.~\ref{S4_Fig} - c, with details shown in the next section).
+By examining the probability distributions of the radius of gyration, also known as the spatial dispersal kernel $P(r_g)$~\cite{brockmann2006}, we chose 10 km as the cell size to quantify the spatial coverage of the majority of Twitter users in Great Britain (Fig.~\ref{S4_Fig} - c, with details shown in the next section).
 Thus, we created a fishnet with 2784 10-km size cells.
@@
 
-\subsection*{Community structure of the spatial networks}
+\subsection{Community structure of the spatial networks}
 Based on the derived spatial network, which is a directed weighted graph, we further determined clusters of strongly connected spatial nodes, known as communities, in the graph space~\cite{coscia2011}.
@@
 
-%NOTE: the random walk should be better introduced or defined. This is slightly confusing.
-Infomap uses the map equation~\cite{rosvall2010} to represent the probability of flow of random walks within information systems.
+Infomap uses the map equation~\cite{rosvall2010} to represent the probability of flow of random walks within information systems~\cite{rosvall2008}.
 It identifies communities by minimizing the expected description length of the trajectory of a random walker, which is shown below:
+
 \begin{equation} \label{eq:1}
@@
 In this regard, this algorithm can be intuitively tailored to describe strongly connected clusters of urban regions based on Twitter user movement.
-The detailed literatures and implementations of Infomap can be found on this website (\url{http://mapequation.org}).
+The detailed literatures and implementations of Infomap can be found on this website ({\tt{http://mapequation.org}}).
 Note that Infomap is capable of performing multi-level community detection~\cite{domenico2015}, but we only use the algorithm to produce our most detailed community structures
@@
 
-\section*{Results and Discussion}
-\subsection*{Collective Mobility Patterns of Twitter Users in Great Britain}
+\section{Results and Discussion}
+\subsection{Collective Mobility Patterns of Twitter Users in Great Britain}
 We first modeled different aspects of the collective mobility patterns of Twitter users.
 These patterns include: the number of visited locations per user,  the collective user displacements, and the radius of gyration of individuals in order to identify natural breaks in user travel patterns.
-We then used these natural breaks within the mobility patterns to partition the geographic space of the United Kingdom into fine-grained cells and established the connectivity among these cells to redraw non-administrative anthropographic urban boundaries.
+We then used these natural breaks within the mobility patterns to partition the geographic space of Great Britain into fine-grained cells and established the connectivity among these cells to redraw non-administrative anthropographic urban boundaries.
 
@@
 \begin{figure}[ht]
-\includegraphics[width=1.0\linewidth]{./figure/PNG/S3_visitation}
-\caption{{\bf Cumulative distribution of the number of locations visited by each Twitter user during different timespan}}
+\includegraphics[width=1.0\linewidth]{./figure/S3_visitation}
+\caption{ \bfseries{Cumulative distribution of the number of locations visited by each Twitter user during different timespan}}
 \label{S3_Fig}
@@
 The displacement distance between 70m and 100km can be further approximated by two power law distributions with a cut-off point at 4km (55$\%$ distances are less than 4km and 40$\%$ distances between 4km and 100km), which indicates the urban movement captured by the geo-located Twitter data to reveal two different modes: inter-city and intra-city movement.
-In short, these fitting functions suggest the existence of multi-scale or multi-modal urban movements captured from Twitter users in the United Kingdom, which means the geographically cohesive, non-overlapping urban areas identified in the next section are not just a result of short distance movement but emerge naturally from the broader Twitter user mobility pattern.
+In short, these fitting functions suggest the existence of multi-scale or multi-modal urban movements captured from Twitter users in Great Britain, which means the geographically cohesive, non-overlapping urban areas identified in the next section are not just a result of short distance movement but emerge naturally from the broader Twitter user mobility pattern.
 Note that a similar multiphase pattern was observed in Twitter user displacements in Australia, but with slightly different distance ranges\cite{jurdak2015}.
@@
 (1) and (2) account for approximately 53$\%$ of all users.  
-The radius of gyration between 30m and 100km can be further approximated by two power law distributions with a cut-off point at 2.5km (35 $\%$ users with radius of gyration less than 2.5km and 57$\%$ users with radius of gyration between 3km and 100km) that suggests two main types of spatial coverage of Twitter user movement within the United Kingdom.
+The radius of gyration between 30m and 100km can be further approximated by two power law distributions with a cut-off point at 2.5km (35 $\%$ users with radius of gyration less than 2.5km and 57$\%$ users with radius of gyration between 3km and 100km) that suggests two main types of spatial coverage of Twitter user movement within
+Great Britain. 
 Note that the accuracy of these values for defining the distance bound depends upon the accuracy of the location information of each geo-located tweet. 
@@
 \begin{figure}[ht]
-\includegraphics[width=1.0\linewidth]{./figure/PNG/S4_radius_displacement}
+\includegraphics[width=1.0\linewidth]{./figure/S4_radius_displacement}
 \caption{{\bf The probability distribution of Twitter user displacements and radius of gyration:} (a) The displacement distribution $P(d)$ is approximated by an exponential, a stretched-exponential and a power-law function (b) the distance between [70m, 70km] is approximated by a double power-law functions (c) The distribution of radius of gyration $P(r_g)$ is approximated by the combination of an exponential, a stretched-exponential and a power-law function (d) the distance between [30m, 100 km] is approximated by a double power-law functions}
@@
 
-\subsection*{Redrawing Great Britain’s Urban Boundaries}
+\subsection{Redrawing Great Britain’s Urban Boundaries}
 The network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells that provide an adequate resolution for a country wide investigation~\cite{ratti2010}.
@@
 Coherent geographic regions were identified as individual fishnet cells showing more internal user movement compared to user movements across the cell boundaries to neighboring cells.
-Fig.~\ref{S5_Fig}  presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4km, greater than 10 km, and using all available displacements together compared to the administrative boundaries of the United Kingdom.
+Fig.~\ref{S5_Fig}  presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4km, greater than 10 km, and using all available displacements together compared to the administrative boundaries of Great Britain.
 One clear observation across the coarse and fine delineations is that most of the geographic divisions are centered around big urban cores with relatively high populations.
@@
 \begin{figure}[ht]
-\includegraphics[width=0.9\linewidth]{./figure/PNG/S5_community}
+\begin{center}
+\includegraphics[width=0.9\linewidth]{./figure/S5_community}
 \caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) displacements longer than 10 km (b) displacements shorter than 4 km (c) and displacements longer than 4 km (d) The partition of space was done using a 10 km fishnet to map the directed displacements from and to each cell.
@@
 \label{S5_Fig}
+\end{center}
 \end{figure}
@@
 For example, the region of Wales appears to consist of three communities as found in the connectivity of both phone calls and long distance movements. 
-However, the regions extracted from the mobility network seems to be more spatially consistent with minimal spatial gaps compared to the partitions extracted from land-line call networks in the United Kingcom~\cite{ratti2010}.
+However, the regions extracted from the mobility network seems to be more spatially consistent with minimal spatial gaps compared to the partitions extracted from land-line call networks in Great Britain~\cite{ratti2010}.
 
 \begin{figure}[ht]
-\includegraphics[width=0.7\linewidth]{./figure/PNG/S6_community_london}
+\begin{center}
+\includegraphics[width=0.7\linewidth]{./figure/S6_community_london}
 \caption{{\bf The non-administrative anthropographic regions inferred from Twitter user displacements greater than 4 km (left) and 10 km (right) in comparison with major cities in England (upper figures) and Scotland (bottom figures).}  Each color represents a unique community.
@@
 \label{S6_Fig}
+\end{center}
 \end{figure}
@@
 Although, these results suggest that travelers seem to be localized over certain areas of the city most of the time, some regions do exhibit long distance interaction patterns.
-For example, the separate geographic areas in the south of Hillingdon which includes Heathrow Airport exhibits more connectivity to central London than its surrounding areas which is explained by the usual flight passenger routes.
-%NOTE: what borders?
+For example, the separate geographic areas in the south of Hillingdon which includes Heathrow Airport exhibits more connectivity to central London than its surrounding areas, which is explained by the usual flight passenger routes.
 The technique also reveals some of the emerging communities around the borders due to the spatial intermingling of both communities.
@@
 \begin{figure}[ht]
-\includegraphics[width=0.8\linewidth]{./figure/PNG/S7_london}
+\begin{center}
+\includegraphics[width=0.8\linewidth]{./figure/S7_london}
 \caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.
@@
 \label{S7_Fig}
+\end{center}
 \end{figure}
 
-\section*{Conclusion}
-In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
-In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the British Isles to partition the space.
-Then by studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell size of 10 km to quantify the spatial coverage of the majority of Twitter users in the United Kingdom.
+\clearpage
+\section{Conclusion}
+In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
+In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the islands of Great Britain to partition the space.
+By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell size of 10 km to quantify the spatial coverage of the majority of Twitter users in Great Britain.
 Twitter user movements were used to establish a connectivity network of the fishnet cells.
 Then we applied the map equation algorithm to partition the network and associated geographic regions.
-The strongly connected communities within the network space yields geographically cohesive, non-overlapping urban areas that provides a clear delineation of the urban boundaries of the United Kingdom.
-By performing a statistical analysis of Twitter user mobility patterns in the United Kingdom, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
+The strongly connected communities within the network space yields geographically cohesive, non-overlapping urban areas that provides a clear delineation of the urban boundaries in Great Britain.
+By performing a statistical analysis of Twitter user mobility patterns in Great Britain, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
 Identifying the connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in Great Britain.
 
-The use of Twitter user mobility to delineate non-administrative anthropographic boundaries enables the researcher to redraw the city at different mobility ranges.
+The power of using Twitter user mobility to delineate non-administrative anthropographic boundaries is the ability to redraw the city at different mobility ranges inferred objectively from the collective mobility patterns.
 Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect the human interaction space.
-This study defines non-administrative anthropographic boundaries by investigating human mobility, which could assist in resource allocation, political campaigns and urban planning.
+This study provides a first step in connecting human mobility research with defining non-administrative anthropographic boundaries, which could assist in resource allocation, political campaigns and urban planning.
 However, the geo-located twitter data is not able to generalize to the entire population; therefore, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
@@
 
-\section*{Acknowledgments}
-The authors would like to thank Dr. Kun Zhao and Dr. Raja Jurdak from CSIRO, Australia for their suggestions in generating Figure 1 in this paper. 
-The research was supported from National Science Foundation grants No. xx ...
+%\subsection{Acknowledgements}
 
-\section*{Author Contribution}
-Conceived and designed the experiments: JY AS DY SW. Performed the experiments: JY DY. Analyzed the data: JY AS. Contributed reagents/materials/analysis tools: JY AS DY AS. Wrote the paper: JY AS SW.
+\begin{thebibliography}{9}
 
-\nolinenumbers
+\markboth{International Journal of Geographical Information Science}{International Journal of Geographical Information Science}
 
-%\section*{References}
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here.
-% 
-\begin{thebibliography}{10}
-\bibitem{schliephake}
-Schliephake, C., 2014. Urban Ecologies: City Space, Material Agency, and Environmental Politics in Contemporary Culture. Lexington Books.
+\bibitem[\protect\citeauthoryear{Brockmann {\itshape{et~al.}}}{2006}]{brockmann2006}
+Brockmann, D., Hufnagel, L., Geisel, T., 2006. The scaling laws of human travel. Nature 439, 462–5. doi:10.1038/nature04292
 
-\bibitem{lynch1960}
+\bibitem[\protect\citeauthoryear{Clauset {\itshape{et~al.}}}{2009}]{clauset2009}
+Clauset, A., Shalizi, C., Newman, M., 2009. Power-Law Distributions in Empirical Data. Society for Industrial and Applied Mathematics Review. 51, 661–703. doi:10.1137/070710111
+
+\bibitem[\protect\citeauthoryear{Coscia {\itshape{et~al.}}}{2011}]{coscia2011}
+Coscia, M., Giannotti, F., Pedreschi, D., 2011. A Classification for Community Discovery Methods in Complex Networks. Statistical Analysis and Data Mining, 4, 512–546. doi:10.1002/sam.10133
+
+\bibitem[\protect\citeauthoryear{De Domenico {\itshape{et~al.}}}{2015}]{domenico2015}
+De Domenico, M., Lancichinetti, A., Arenas, A., Rosvall, M., 2015.
+Identifying Modular Flows on Multilayer Networks Reveals Highly Overlapping Organization in Interconnected Systems.
+Physical Review X, 5.
+doi:10.1103/PhysRevX.5.011027
+
+\bibitem[\protect\citeauthoryear{Fortunato and Barthélemy}{2007}]{fortunato2007}
+Fortunato, S., Barthélemy, M., 2007. Resolution limit in community detection. Proceedings of the National Academy of Sciences, 104, 36–41. doi:10.1073/pnas.0605965104
+
+\bibitem[\protect\citeauthoryear{González {\itshape{et~al.}}}{2008}]{gonzalez2008}
+González, M.C., Hidalgo, C.A., Barabási, A.-L., 2008. Understanding individual human mobility patterns. Nature, 453, 779–82. doi:10.1038/nature06958
+
+\bibitem[\protect\citeauthoryear{Good {\itshape{et~al.}}}{2010}]{good2010}
+Good, B.H., de Montjoye, Y.-A., Clauset, A., 2010. Performance of modularity maximization in practical contexts. Physical Review E, 81, 046106. doi:10.1103/PhysRevE.81.046106
+
+\bibitem[\protect\citeauthoryear{Guimerà {\itshape{et~al.}}}{2004}]{guimera2004}
+Guimerà, R., Sales-Pardo, M., Amaral, L.A.N., 2004. Modularity from fluctuations in random graphs and complex networks. Physical Review E, 70, 025101. doi:10.1103/PhysRevE.70.025101
+
+\bibitem[\protect\citeauthoryear{Hawelka {\itshape{et~al.}}}{2014}]{hawelka}
+Hawelka, B., Sitko, I., Beinat, E., Sobolevsky, S., Kazakopoulos, P., Ratti, C., 2014.
+Geo-located Twitter as proxy for global mobility patterns.
+Cartography and Geographic Information Science, 41, 260–271.
+doi:10.1080/15230406.2014.890072
+
+\bibitem[\protect\citeauthoryear{Jiang and Miao}{2015}]{jiang2015}
+Jiang, B., Miao, Y., 2015. The evolution of natural cities from the perspective of location-based social media. The Professional Geographer, 67(2), 295-306.
+
+\bibitem[\protect\citeauthoryear{Jurdak {\itshape{et~al.}}}{2015}]{jurdak2015}
+Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D., 2015. Understanding Human Mobility from Twitter. PLoS ONE 10, e0131469. doi:10.1371/journal.pone.0131469
+
+\bibitem[\protect\citeauthoryear{Kallus {\itshape{et~al.}}}{2015}]{kallus2015}
+Kallus Z, Barankai N, Szüle J, Vattay G., 2015.
+Spatial Fingerprints of Community Structure in Human Interaction Network for an Extensive Set of Large-Scale Regions.
+PLoS ONE 10(5): e0126713.
+doi: 10.1371/journal.pone.0126713
+
+\bibitem[\protect\citeauthoryear{Lancichinetti and Fortunato}{2009}]{lancichinetti2009}
+Lancichinetti, A., Fortunato, S., 2009. Community detection algorithms: A comparative analysis. Physical Review E, 80, 056117. doi:10.1103/PhysRevE.80.056117
+
+\bibitem[\protect\citeauthoryear{Liu {\itshape{et~al.}}}{2015}]{liu2015}
+Liu, X., Gong, L., Gong, Y., Liu, Y., 2015. Revealing travel patterns and city structure with taxi trip data. J. Transportation Geography, 43, 78–90. doi:10.1016/j.jtrangeo.2015.01.016
+
+\bibitem[\protect\citeauthoryear{Liu {\itshape{et~al.}}}{2014}]{liuPopMobility}
+Liu, J., Zhao, K., Khan, S., Cameron, M., Jurdak, R., 2014. Multi-scale Population and Mobility Estimation with Geo-tagged Tweets. ArXiv14120327 Phys.
+
+\bibitem[\protect\citeauthoryear{Long {\itshape{et~al.}}}{2015}]{long2015}
+Long, Y., Han, H., Tu, Y., Shu, X., 2015. Evaluating the effectiveness of urban growth boundaries using human mobility and activity records. Cities, 46, 76-84.
+
+\bibitem[\protect\citeauthoryear{Lynch}{1960}]{lynch1960}
 Lynch, K., 1960. The image of the city. MIT press.
 
-\bibitem{jiang2015}
-Jiang, B., Miao, Y., 2015. The evolution of natural cities from the perspective of location-based social media. The Professional Geographer, 67(2), 295-306.
+\bibitem[\protect\citeauthoryear{Newman}{2006}]{newman2006}
+Newman, M.E.J., 2006. Modularity and community structure in networks. Proceedings of the National Academy of Sciences, 103, 8577–82. doi:10.1073/pnas.0601602103
 
-\bibitem{long2015}
-Long, Y., Han, H., Tu, Y., Shu, X., 2015. Evaluating the effectiveness of urban growth boundaries using human mobility and activity records. Cities, 46, 76-84.
+\bibitem[\protect\citeauthoryear{Openshaw}{1984}]{openshaw1984}
+Openshaw, S., 1984. The modifiable areal unit problem. Geo Abstracts University of East Anglia.
 
-\bibitem{liu2015}
-Liu, X., Gong, L., Gong, Y., Liu, Y., 2015. Revealing travel patterns and city structure with taxi trip data. J. Transportation Geography, 43, 78–90. doi:10.1016/j.jtrangeo.2015.01.016
+\bibitem[\protect\citeauthoryear{Qian {\itshape{et~al.}}}{2013}]{qian2013}
+Qian, W., Stanley, K.
+G., Osgood, N.
+D., 2013.
+The impact of spatial resolution and representation on human mobility predictability.
+In Web and Wireless Geographical Information Systems,  pp.
+25-40, Springer Berlin Heidelberg.
 
-\bibitem{lancichinetti2009}
-Lancichinetti, A., Fortunato, S., 2009. Community detection algorithms: A comparative analysis. Physical Review E, 80, 056117. doi:10.1103/PhysRevE.80.056117
-
-\bibitem{ratti2010}
+\bibitem[\protect\citeauthoryear{Ratti {\itshape{et~al.}}}{2010}]{ratti2010}
 Ratti, C., Sobolevsky, S., Calabrese, F., Andris, C., Reades, J., Martino, M., Claxton, R., Strogatz, S.H., 2010.
@@
 
-\bibitem{sobolevsky2013}
-Sobolevsky S, Szell M, Campari R, Couronné T, Smoreda Z, Ratti, C., 2013.
-Delineating Geographical Regions with Networks of Human Interactions in an Extensive Set of Countries.
-PLoS ONE 8(12): e81707.
-doi: 10.1371/journal.pone.0081707
+\bibitem[\protect\citeauthoryear{Reynolds}{2012}]{reynolds2012}
+Reynolds, A., 2012.
+Truncated levy walks are expected beyond the scale of data collection when correlated random walks embody observed movement patterns.
+Journal of The Royal Society Interface, 9(68), 528-534.
 
-\bibitem{kallus2015}
-Kallus Z, Barankai N, Szüle J, Vattay G., 2015 Spatial Fingerprints of Community Structure in Human Interaction Network for an Extensive Set of Large-Scale Regions.
-PLoS ONE 10(5): e0126713.
-doi: 10.1371/journal.pone.0126713
+\bibitem[\protect\citeauthoryear{Rhee {\itshape{et~al.}}}{2011}]{rhee2011}
+Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S. J., and Chong, S., 2011. On the levy-walk nature of human mobility. IEEE/ACM transactions on networking (TON), 19(3), 630-643.
 
-\bibitem{hawelka}
-Hawelka, B., Sitko, I., Beinat, E., Sobolevsky, S., Kazakopoulos, P., Ratti, C., 2014.
-Geo-located Twitter as proxy for global mobility patterns.
-Cartography and Geographic Information Science, 41, 260–271.
-doi:10.1080/15230406.2014.890072
-
-\bibitem{jurdak2015}
-Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D., 2015. Understanding Human Mobility from Twitter. PLoS ONE 10, e0131469. doi:10.1371/journal.pone.0131469
-
-\bibitem{thiemann}
-Thiemann, C., Theis, F., Grady, D., Brune, R., Brockmann, D., 2010. The Structure of Borders in a Small World. PLoS ONE 5, e15422. doi:10.1371/journal.pone.0015422
-
-\bibitem{domenico2015}
-De Domenico, M., Lancichinetti, A., Arenas, A., Rosvall, M., 2015.
-Identifying Modular Flows on Multilayer Networks Reveals Highly Overlapping Organization in Interconnected Systems.
-Physical Review X, 5.
-doi:10.1103/PhysRevX.5.011027
-
-\bibitem{fortunato2007}
-Fortunato, S., Barthélemy, M., 2007. Resolution limit in community detection. Proceedings of the National Academy of Sciences, 104, 36–41. doi:10.1073/pnas.0605965104
-
-\bibitem{newman2006}
-Newman, M.E.J., 2006. Modularity and community structure in networks. Proceedings of the National Academy of Sciences, 103, 8577–82. doi:10.1073/pnas.0601602103
-
-\bibitem{gonzalez2008}
-González, M.C., Hidalgo, C.A., Barabási, A.-L., 2008. Understanding individual human mobility patterns. Nature, 453, 779–82. doi:10.1038/nature06958
-
-\bibitem{coscia2011}
-Coscia, M., Giannotti, F., Pedreschi, D., 2011. A Classification for Community Discovery Methods in Complex Networks. Statistical Analysis and Data Mining, 4, 512–546. doi:10.1002/sam.10133
-
-\bibitem{rinzivillo2012}
+\bibitem[\protect\citeauthoryear{Rinzivillo {\itshape{et~al.}}}{2012}]{rinzivillo2012}
 Rinzivillo, S., Mainardi, S., Pezzoni, F., Coscia, M., Pedreschi, D., Giannotti, F., 2012.
@@
 
-\bibitem{zhong2014}
-Zhong, C., Arisona, S.M., Huang, X., Batty, M., Schmitt, G., 2014.
-Detecting the dynamics of urban structure through spatial network analysis.
-International Journal of Geographical Information Science, 28, 2178–2199.
-doi:10.1080/13658816.2014.914521
+\bibitem[\protect\citeauthoryear{Rosvall {\itshape{et~al.}}}{2010}]{rosvall2010}
+Rosvall, M., Axelsson, D., Bergstrom, C.T., 2010. The map equation. The European Physical Journal Special Topics, 178, 13–23. doi:10.1140/epjst/e2010-01179-1
 
-\bibitem{qian2013}
-Qian, W., Stanley, K.
-G., Osgood, N.
-D., 2013.
-The impact of spatial resolution and representation on human mobility predictability.
-In Web and Wireless Geographical Information Systems,  pp.
-25-40, Springer Berlin Heidelberg.
+\bibitem[\protect\citeauthoryear{Rosvall and Bergstrom}{2008}]{rosvall2008}
+Rosvall, M., Bergstrom, C.T., 2008. Maps of random walks on complex networks reveal community structure. Proceedings of the National Academy of Sciences, 105, 1118–1123.
 
-\bibitem{sakaki2010}
+\bibitem[\protect\citeauthoryear{Sakaki {\itshape{et~al.}}}{2010}]{sakaki2010}
 Sakaki, T., Okazaki, M., Matsuo, Y., 2010.
@@
 
-\bibitem{zandbergen2009}
+\bibitem[\protect\citeauthoryear{schliephake}{2014}]{schliephake}
+Schliephake, C., 2014. Urban Ecologies: City Space, Material Agency, and Environmental Politics in Contemporary Culture. Lexington Books.
+
+\bibitem[\protect\citeauthoryear{Simini {\itshape{et~al.}}}{2012}]{simini2012}
+Simini, F., González, M. C., Maritan, A., Barabási, A. L., 2012. A universal model for mobility and migration patterns. Nature, 484(7392), 96-100.
+
+\bibitem[\protect\citeauthoryear{Sobolevsky {\itshape{et~al.}}}{2013}]{sobolevsky2013}
+Sobolevsky S, Szell M, Campari R, Couronné T, Smoreda Z, Ratti, C., 2013.
+Delineating Geographical Regions with Networks of Human Interactions in an Extensive Set of Countries.
+PLoS ONE 8(12): e81707.
+doi: 10.1371/journal.pone.0081707
+
+\bibitem[\protect\citeauthoryear{Song {\itshape{et~al.}}}{2012}]{song2012}
+Song, C., Wang, D., Barabási, A.-L., 2012. Connections between human dynamics and network science. ArXiv Prepr. ArXiv12091411.
+
+\bibitem[\protect\citeauthoryear{Thiemann {\itshape{et~al.}}}{2010}]{thiemann}
+Thiemann, C., Theis, F., Grady, D., Brune, R., Brockmann, D., 2010. The Structure of Borders in a Small World. PLoS ONE 5, e15422. doi:10.1371/journal.pone.0015422
+
+\bibitem[\protect\citeauthoryear{Wong}{2009}]{wong2009}
+Wong, D., 2009. The modifiable areal unit problem (MAUP). SAGE Publications: London, UK.
+
+\bibitem[\protect\citeauthoryear{Zandbergen}{2009}]{zandbergen2009}
 Zandbergen, P.A., 2009. Accuracy of iPhone Locations: A Comparison of Assisted GPS, WiFi and Cellular Positioning. Transactions in GIS, 13, 5–25. doi:10.1111/j.1467-9671.2009.01152.x
 
-\bibitem{liuPopMobility}
-Liu, J., Zhao, K., Khan, S., Cameron, M., Jurdak, R., 2014. Multi-scale Population and Mobility Estimation with Geo-tagged Tweets. ArXiv14120327 Phys.
-
-\bibitem{openshaw1984}
-Openshaw, S., 1984. The modifiable areal unit problem. Geo Abstracts University of East Anglia.
-
-\bibitem{wong2009}
-Wong, D., 2009. The modifiable areal unit problem (MAUP). SAGE Publications: London, UK.
-
-\bibitem{brockmann2006}
-Brockmann, D., Hufnagel, L., Geisel, T., 2006. The scaling laws of human travel. Nature 439, 462–5. doi:10.1038/nature04292
-
-\bibitem{song2012}
-Song, C., Wang, D., Barabási, A.-L., 2012. Connections between human dynamics and network science. ArXiv Prepr. ArXiv12091411.
-
-\bibitem{guimera2004}
-Guimerà, R., Sales-Pardo, M., Amaral, L.A.N., 2004. Modularity from fluctuations in random graphs and complex networks. Physical Review E, 70, 025101. doi:10.1103/PhysRevE.70.025101
-
-\bibitem{good2010}
-Good, B.H., de Montjoye, Y.-A., Clauset, A., 2010. Performance of modularity maximization in practical contexts. Physical Review E, 81, 046106. doi:10.1103/PhysRevE.81.046106
-
-\bibitem{rosvall2008}
-Rosvall, M., Bergstrom, C.T., 2008. Maps of random walks on complex networks reveal community structure. Proceedings of the National Academy of Sciences, 105, 1118–1123.
-
-\bibitem{rosvall2010}
-Rosvall, M., Axelsson, D., Bergstrom, C.T., 2010. The map equation. The European Physical Journal Special Topics, 178, 13–23. doi:10.1140/epjst/e2010-01179-1
-
-\bibitem{clauset2009}
-Clauset, A., Shalizi, C., Newman, M., 2009. Power-Law Distributions in Empirical Data. Society for Industrial and Applied Mathematics Review. 51, 661–703. doi:10.1137/070710111
-
-\bibitem{rhee2011}
-Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S. J., and Chong, S., 2011. On the levy-walk nature of human mobility. IEEE/ACM transactions on networking (TON), 19(3), 630-643.
-
-\bibitem{reynolds2012}
-Reynolds, A., 2012.
-Truncated levy walks are expected beyond the scale of data collection when correlated random walks embody observed movement patterns.
-Journal of The Royal Society Interface, 9(68), 528-534.
-
-\bibitem{zhao2015}
+\bibitem[\protect\citeauthoryear{Zhao {\itshape{et~al.}}}{2015}]{zhao2015}
 Zhao, K., Musolesi, M., Hui, P., Rao, W., and Tarkoma, S., 2015. Explaining the power-law distribution of human mobility through transportation modality decomposition. Scientific reports, 5.
 
-\bibitem{simini2012}
-Simini, F., González, M. C., Maritan, A., Barabási, A. L., 2012. A universal model for mobility and migration patterns. Nature, 484(7392), 96-100.
-
-%\bibitem{blondel2008}
-%Blondel, V.D., Guillaume, J., Lambiotte, R., Lefebvre, E., 2008. Fast unfolding of community hierarchies in large networks. Networks 1–6.
-%
+\bibitem[\protect\citeauthoryear{Zhong {\itshape{et~al.}}}{2014}]{zhong2014}
+Zhong, C., Arisona, S.M., Huang, X., Batty, M., Schmitt, G., 2014.
+Detecting the dynamics of urban structure through spatial network analysis.
+International Journal of Geographical Information Science, 28, 2178–2199.
+doi:10.1080/13658816.2014.914521
 
 \end{thebibliography}
+
+\bibliographystyle{tGIS}
+%\bibliography{Twitter_Urban_Boundary}
+
+\label{lastpage}
+
 \end{document}

### 2016-02-29 Geo-located_Twitter_Data/latex/Geo_located_tweets.tex
use this channel for editing

\documentclass[a4paper,11pt]{article}

\makeatletter
\renewcommand\@biblabel[1]{#1.}
\makeatother
%makeatletter \def\@biblabel#1{\@ifnotempty{#1}{#1}}

\begin{document}
%\title{A new geographical data source: geo-located Twitter data}
%\title{A scalable geographical data framework for geo-located Twitter data}
%\title{From massive collection of geo-located Tweets to a new geographical data source}
\title{Generating Twitter user mobility data from massive collection of geo-located Tweets}

%\author[1]{Junjun Yin}
%\author[2]{Bin Jiang}
%	\affil[1]
%	{
%	\it CyberGIS Center for Advanced Digital and Spatial Studies
%%	\it Department of Geography and Geographic Information Science
%%	\it	National Center for Supercomputing Applications \authorcr
%	\it	University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA
%	}
%	\affil[2]
%	{
%	\it Department of Technology and Built Environment \authorcr
%	\it University of Gävle, 80176, Sweden
%	}

\maketitle
\section*{Abstract}
geo-located Twitter data is attracting increasing attention from research communities

the increasing popularity of accessing today's pervasive social media platform has enabled a new geographical data.

In this paper, we present an efficient approach for geo-located data management and processing

\section{Introduction}

disseminate

While today's pervasive social media platforms connects people in the virtual space.

The pervasive

The Location Based Social Media (LBSM)

Herewith known as Twitter

In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
LBSM enables users to attach their current location as a geo-tag to the message they will post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters \cite{Jurdak2015}.
A LBSM Big Data emerges when millions social media users constantly posting messages.

\section*{Data collection}
In general, Twitter (http://www.twitter.com) offers two kinds of search API

an alternative way to collect large is through the Twitter Streaming API (application programming interface)

Geo-located tweets can be downloaded using

REST APIs responses are available in JSON.
limitation

Streaming APIs, also known as Twitter Fire

The Streaming APIs give developers low latency access to Twitter’s global stream of Tweet data. 
A proper implementation of a streaming client will be pushed messages indicating Tweets and other events have occurred, without any of the overhead associated with polling a REST endpoint.

If your intention is to conduct singular searches, read user profile information, or post Tweets, consider using the REST APIs instead.

Twitter offers several streaming endpoints, each customized to certain use cases.

\section*{Data management and processing}
\subsection*{Accommodating massive Twitter Dataset with Hadoop}
Apache Hadoop is an open source software framework designed to facilitate data intensive computing on large commodity clusters.
It combines a distributed file system, namely Hadoop Distributed File System(HDFS) with MapReduce programming paradigm, which can be applied to wide range of data-intensive problems.
MapReduce is a programming model and an associated software framework designed to process massive data in a distributed fashion.
MapReduce breaks the entire computation into small tasks and schedule them among different computing nodes.
MapReduce consists of two main stages: map and reduce.
In the map stage, input data is converted into series of intermediate $\langle key, value\rangle$ pairs.
Customized computation will be performed in the reduce stage based on the same intermediate key.
This framework provides parallelization since both map and reduce tasks are considered independent and can be done in parallel. More importantly, it provides scalability in relation to the growth of data size, where Hadoop can scale to more computing nodes in the cluster to maintain the performance.

Our framework benefits from using Hadoop in both data management and processing.
First, since the input data is large it is desirable to store it on multiple machines.
Second, by using Hadoop we can parallelize the computational tasks and make the data processing faster and more efficient.
Further, by adopting the MapReduce computing paradigm, we can model each individual user's trajectory by treating user's unique ID as key, and summarize the movement flows among different spatial units by utilizing the ID of the spatial unit as key. The details will be introduced in the following section.

\section*{Case study}
In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
To ensure the complete coverage over Great Britain, we have set the bounding box to British Isles (lower left coordinates in (latitude, longitude): (49.497, -14.854) and upper right coordinates: (61.186, 2.637)), which also includes the whole area of Ireland and a part of France.
We have implemented a data crawler and continuously collected 7-month data (1st June – 31st December, 2014) with over 101.8 million tweets and 60 GB in size.
During the data collection phase, the data crawler did not encounter any issue regarding whether it exceeds the data quota by the 1$\%$ policy mentioned in (Hawelka et al., 2014).
It means we have managed to download all the geo-located tweets for the given bounding box.
In particular, to showcase the overall spatial coverage of the collected geo-located tweets, a density map of the Twitter user locations in British Isles for July 2014 is shown in Figure 4, where the collected points alone visually reveal the geography of cities and countries, e.g. the clusters with high density of tweets (in color red) correspond to the skeleton of major cities.

\cite{brockmann2006}

\section*{Conclusion}

\begin{thebibliography}{10}

\bibitem{sakaki2010}
Sakaki, T., Okazaki, M., Matsuo, Y., 2010. Earthquake Shakes Twitter Users: Real-time Event Detection by Social Sensors, in: Proceedings of the 19th International Conference on World Wide Web, WWW ’10. ACM, New York, NY, USA, pp. 851–860. doi:10.1145/1772690.1772777

\bibitem{liuPopMobility}
Liu, J., Zhao, K., Khan, S., Cameron, M., Jurdak, R., 2014. Multi-scale Population and Mobility Estimation with Geo-tagged Tweets. ArXiv14120327 Phys.

\bibitem{hawelka}
Hawelka, B., Sitko, I., Beinat, E., Sobolevsky, S., Kazakopoulos, P., Ratti, C., 2014. Geo-located Twitter as proxy for global mobility patterns. Cartography and Geographic Information Science, 41, 260–271. doi:10.1080/15230406.2014.890072

\bibitem{frank2013}
Frank, M.R., Mitchell, L., Dodds, P.S. and Danforth, C.M., 2013. Happiness and the patterns of life: A study of geolocated tweets. Scientific reports, 3. doi:10.1038/srep02625

\bibitem{jurdak2015}
Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D., 2015. Understanding Human Mobility from Twitter. PLoS ONE 10, e0131469. doi:10.1371/journal.pone.0131469

\end{thebibliography}

\end{document}

### 2016-02-29 Geo-located_Twitter_Data/latex/Geo_located_tweets.tex
new edits

@@
 %\title{From massive collection of geo-located Tweets to a new geographical data source}
-\title{Generating Twitter user mobility data from massive collection of geo-located Tweets}
+%\title{Generating Twitter user mobility data from massive collection of geo-located Tweets}
+
+\title{From massive collection of geo-located Tweets to a new geographical data source: Generating Twitter user mobility data from massive collection of geo-located Tweets}
 
@@
 
+Although Twitter data is accessible from its dedicated APIs, the collected data cannot be shared among
+Furthermore, as the data is collected in a continuous fashion, the accumulated data
+
+In this regard, this paper provides a scalable computing framework for efficient data processing.
+In particular, this framework utilizes
+
 \section*{Data collection}
-In general, Twitter (http://www.twitter.com) offers two kinds of search API
+In general, Twitter ({\tt{http://www.twitter.com}}) offers two kinds of search API
 

### 2016-02-29 Geo-located_Twitter_Data/latex/Geo_located_tweets.tex
new edits

@@
 
-\title{From massive collection of geo-located Tweets to a new geographical data source: Generating Twitter user mobility data from massive collection of geo-located Tweets}
+\title{ Harnessing  geo-located Tweets as a new geographical data source: Extracting mobility data from massive collection of geo-located Tweets}
 
@@
 \section{Introduction}
+Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008}, traffic management~\cite{jiang2009}, and even the spatial spread of epidemic diseases~\cite{belik2011}.
+However, the lack of detailed human movements with fine-grained spatial and temporal granularity limits the findings to capture mobility patterns of individuals~\cite{gonzalez2008,jurdak2015}.
 
-disseminate
+Earlier research efforts relied on low resolution mobility data to understand human mobility patterns, such as using census records to understand human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
 
-While today's pervasive social media platforms connects people in the virtual space.
+In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring},
+emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints~\cite{thatcher2014living} in the form of real-world trails and footprints.
+One significant advantage of LBSM data streams is the large spatial coverage, for example, researchers have used geo-located Twitter data for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible by using other mobility datasets (e.g., GPS traces and mobile phone call records).
+In addition, the publicly available LBSM data streams offer unique opportunities for conducting reproducible scientific findings regarding the concerns of infringement on individual privacy, such as using mobile phone call records~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}.
 
-The pervasive
-
-The Location Based Social Media (LBSM)
-
-Herewith known as Twitter
+However, there are some limitations and complexities in directly using the LBSM data for study human mobility patterns.
 
@@
 
+Although Twitter allows users to gain access to the data streams, the obtained data cannot be shared directly with 
+since the content of each Twitter message concerns user privacy. Therefore, when conducting research using Twitter data, one must download the data
+
+The remainder of this paper is organized as follows. Section describes the
+
 \section*{Data collection}
-In general, Twitter ({\tt{http://www.twitter.com}}) offers two kinds of search API
+In general, Twitter ({\tt{http://www.twitter.com}}) provides two kinds of search APIs for retrieving Twitter messages:  REST API and Streaming API ({\tt{http://dev.twitter.com/overview/}}). 
+Twitter REST API is used to search tweets that belong to a particular user account and its followers
+
+If your intention is to conduct singular searches, read user profile information, or post Tweets, consider using the REST APIs instead.
 
@@
 
+\subsection*{Data extraction based on geographical regions}
+
+\subsection*{Constructing Twitter user space-time trajectories}
+
 \section*{Case study}
@@
 \begin{thebibliography}{10}
+\bibitem{zheng2008}
+Zheng, Y., Li, Q., Chen, Y., Xie, X., and Ma, W.-Y. (2008). Understanding mobility based on gps data. In Proceedings of the 10th international conference on Ubiquitous computing, pp. 312-321. ACM.
+
+\bibitem{jiang2009}
+Jiang, B., Yin, J., and Zhao, S. (2009). Characterizing the human mobility pattern in a large street network. Physical Review E, 80(2):021136.
+
+\bibitem{belik2011}
+Belik, V., Geisel, T., and Brockmann, D. (2011). Natural human mobility patterns and spatial spread of infectious diseases. Physical Review X, 1(1):011001.
+
+\bibitem{gonzalez2008}
+Gonzalez, M. C., Hidalgo, C. A., and Barabasi, A.-L. (2008). Understanding individual human mobility patterns. Nature, 453(7196), pp.779-782.
+
+\bibitem{jurdak2015}
+Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D., 2015. Understanding Human Mobility from Twitter. PLoS ONE 10, e0131469. doi:10.1371/journal.pone.0131469
+
+\bibitem{frank2013}
+Frank, M.R., Mitchell, L., Dodds, P.S. and Danforth, C.M., 2013. Happiness and the patterns of life: A study of geolocated tweets. Scientific reports, 3. doi:10.1038/srep02625
 
@@
 
-\bibitem{frank2013}
-Frank, M.R., Mitchell, L., Dodds, P.S. and Danforth, C.M., 2013. Happiness and the patterns of life: A study of geolocated tweets. Scientific reports, 3. doi:10.1038/srep02625
-
-\bibitem{jurdak2015}
-Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D., 2015. Understanding Human Mobility from Twitter. PLoS ONE 10, e0131469. doi:10.1371/journal.pone.0131469
-
 \end{thebibliography}

### 2016-02-29 Geo-located_Twitter_Data/latex/Geo_located_tweets.tex
before lunch

@@
 
-\title{ Harnessing  geo-located Tweets as a new geographical data source: Extracting mobility data from massive collection of geo-located Tweets}
+\title{Harnessing  geo-located Tweets as a new geographical data source: Extracting mobility data from massive collection of geo-located Tweets}
 
@@
 Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008}, traffic management~\cite{jiang2009}, and even the spatial spread of epidemic diseases~\cite{belik2011}.
+Earlier research efforts relied on low resolution mobility data to understand human mobility patterns, such as using census records~\cite{greenwood1985} or questionnaires by asking volunteers to report the trace of bank notes ~\cite{brockmann2006}.
 However, the lack of detailed human movements with fine-grained spatial and temporal granularity limits the findings to capture mobility patterns of individuals~\cite{gonzalez2008,jurdak2015}.
+More recent approaches to collecting detailed mobility data 
+GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring},
 
-Earlier research efforts relied on low resolution mobility data to understand human mobility patterns, such as using census records to understand human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
-
-In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring},
-emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints~\cite{thatcher2014living} in the form of real-world trails and footprints.
+emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital traces in the form of real-world trails and footprints~\cite{thatcher2014}.
 One significant advantage of LBSM data streams is the large spatial coverage, for example, researchers have used geo-located Twitter data for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible by using other mobility datasets (e.g., GPS traces and mobile phone call records).
@@
 
-\section*{Data management and processing}
-\subsection*{Accommodating massive Twitter Dataset with Hadoop}
+\section{Data management and processing}
+\subsection{Accommodating massive Twitter Dataset with Hadoop}
 Apache Hadoop is an open source software framework designed to facilitate data intensive computing on large commodity clusters.
@@
 
-\subsection*{Data extraction based on geographical regions}
+\subsection{Data extraction based on geographical regions}
 
-\subsection*{Constructing Twitter user space-time trajectories}
+\subsection{Constructing Twitter user space-time trajectories}
 
-\section*{Case study}
+\section{Case study}
 In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
@@
 
-\cite{brockmann2006}
-
 \section*{Conclusion}
@@
 \bibitem{zheng2008}
-Zheng, Y., Li, Q., Chen, Y., Xie, X., and Ma, W.-Y. (2008). Understanding mobility based on gps data. In Proceedings of the 10th international conference on Ubiquitous computing, pp. 312-321. ACM.
+Zheng, Y., Li, Q., Chen, Y., Xie, X., and Ma, W.-Y., 2008. Understanding mobility based on gps data. In Proceedings of the 10th international conference on Ubiquitous computing, pp. 312-321. ACM.
 
 \bibitem{jiang2009}
-Jiang, B., Yin, J., and Zhao, S. (2009). Characterizing the human mobility pattern in a large street network. Physical Review E, 80(2):021136.
+Jiang, B., Yin, J., and Zhao, S., 2009. Characterizing the human mobility pattern in a large street network. Physical Review E, 80(2):021136.
 
 \bibitem{belik2011}
-Belik, V., Geisel, T., and Brockmann, D. (2011). Natural human mobility patterns and spatial spread of infectious diseases. Physical Review X, 1(1):011001.
+Belik, V., Geisel, T., and Brockmann, D., 2011. Natural human mobility patterns and spatial spread of infectious diseases. Physical Review X, 1(1):011001.
+
+\bibitem{greenwood1985}
+Greenwood, M. J., 1985. Human migration: Theory, models, and empirical studies. Journal of regional Science, 25(4), pp. 521-544.
+
+\bibitem{brockmann2006}
+Brockmann, D., Hufnagel, L., and Geisel, T., 2006. The scaling laws of human travel. Nature, 439(7075), pp. 462-465.
 
 \bibitem{gonzalez2008}
-Gonzalez, M. C., Hidalgo, C. A., and Barabasi, A.-L. (2008). Understanding individual human mobility patterns. Nature, 453(7196), pp.779-782.
+Gonzalez, M. C., Hidalgo, C. A., and Barabasi, A.-L., 2008. Understanding individual human mobility patterns. Nature, 453(7196), pp.779-782.
 
@@
 Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D., 2015. Understanding Human Mobility from Twitter. PLoS ONE 10, e0131469. doi:10.1371/journal.pone.0131469
+
+\bibitem{thatcher2014}
+Thatcher, J. (2014). Living on fumes: Digital footprints, data fumes, and the limitations of spatial big data. International Journal of Communication, 8, 1765-1783.
 

### 2016-04-08 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
init revision

--- 2016-02-20 urban_boundaries_gb/IJGIS/Paper.tex
@@
 \documentclass[]{tGIS2e}
-% line numbers
-\usepackage[right]{lineno}
-
 %\citestyle{tGIS}
@@
 \end{abstract}
-\linenumbers
+
 \section{Introduction}
-\markboth{International Journal of Geographical Information Science}{International Journal of Geographical Information Science}
 Official urban boundaries are defined by government agencies for political and administrative purposes.
@@
 \begin{center}
-\vspace{36pt}
 \includegraphics[width=1\linewidth]{./figure/S1_overview_Fig_2}
@@
 \begin{center}
-\includegraphics[width=0.7\linewidth]{./figure/S6_community_london}
+\includegraphics[width=0.8\linewidth]{./figure/S6_community_london}
 \caption{{\bf The non-administrative anthropographic regions inferred from Twitter user displacements greater than 4 km (left) and 10 km (right) in comparison with major cities in England (upper figures) and Scotland (bottom figures).}  Each color represents a unique community.
@@
 
-\markboth{International Journal of Geographical Information Science}{International Journal of Geographical Information Science}
+\markboth{}{International Journal of Geographical Information Science}
 

### 2016-04-08 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
new edits

@@
 Specifically, we delineated the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million Twitter messages.
-Our study connects human mobility research with the delineation of non-administrative anthropographic urban boundaries based on Twitter user spatial interactions, which provides a new understanding of the interactions between urban structure and human activity.
+Our study connects human mobility research with the delineation of non-administrative anthropographic urban boundaries based on Twitter user spatial interactions, which provides a new understanding of the interactions between human activity and urban space.
 We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
@@
 These interactions can take the form of trade, commerce, social connections, and political activity across the borders.
-Urban boundaries that respect the human interaction space can be very import to city planning, traffic management and resource allocation~\citep{lynch1960,jiang2015,liu2015,long2015}.
+Urban boundaries that respect the human interaction space can be very important to city planning, traffic management and resource allocation~\citep{lynch1960,jiang2015,liu2015,long2015}.
 Many studies adopt a ``bottom-up'' approach to urban boundary delineation, where the geographic space is partitioned into small units and each unit is modeled as a node within a network structure.
-A suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interaction among the nodes~\cite{lancichinetti2009}.
+A suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interaction among the nodes~\citep{lancichinetti2009}.
 Different social and physical human interactions were considered to establish the edges of the network connecting the nodes.
-For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in Great Britain~\cite{ratti2010}.
-Extending the previous method to different countries~\cite{sobolevsky2013}, the authors argue that this method yields cohesive geographic divisions that follow the socio-economic boundaries.
-While other researchers use social ties of Twitter users to identify cohesive regions for different countries across the world~\cite{kallus2015}, they found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.
+For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in Great Britain~\citep{ratti2010}.
+Extending the previous method to different countries~\citep{sobolevsky2013}, the authors argue that this method yields cohesive geographic divisions that follow the socio-economic boundaries.
+While other researchers use social ties of Twitter users to identify cohesive regions for different countries across the world~\citep{kallus2015}, they found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.
 
@@
 Twitter users extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
-Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the country level)~\cite{hawelka,jurdak2015}.
+Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the country level)~\citep{hawelka,jurdak2015}.
 We argue here that Twitter user mobility patterns provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation. 
 A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in Great Britain.
-In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity that is limited to the postal code level~\cite{thiemann}.
+In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity that is limited to the postal code level~\citep{thiemann}.
 
@@
 We applied the map equation algorithm~\citep{domenico2015} to partition the network and associate geographic regions.
-The map equation algorithm was selected to avoid the inherent resolution problem~\cite{fortunato2007} of the common modularity maximization method~\citep{newman2006}. 
+The map equation algorithm was selected to avoid the inherent resolution problem~\citep{fortunato2007} of the common modularity maximization method~\citep{newman2006}. 
 We found that the collective mobility patterns of Twitter users in Great Britain are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points.
@@
 
+\section{Related Work}
+
 \section{Materials and Methods}
@@
 We use large-scale Twitter user spatial interactions inferred from the collective mobility patterns of Twitter users to delineate urban boundaries in Great Britain.
-A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\cite{gonzalez2008}.
+A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\citep{gonzalez2008}.
 This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two recorded locations is one month.
@@
 Twitter user movements were then used to establish the connectivity between fishnet cells to form a connectivity network where each cell is considered a node within the network. 
-Finally, by detecting strongly connected clusters in the network space using community detection methods~\cite{coscia2011}, we were able to reveal urban boundaries within the geographic space. 
+Finally, by detecting strongly connected clusters in the network space using community detection methods~\citep{coscia2011}, we were able to reveal urban boundaries within the geographic space. 
 An overview of the approach is illustrated in Fig.~\ref{S1_Fig} and the details are presented in the following sections.
@@
 First we removed the duplicated messages in the dataset.
-Next, we removed non-human users based on unusual relocation speed \cite{hawelka,jurdak2015}. 
-We adopted a relocation speed threshold of 240 m/s as used by \cite{jurdak2015}. 
+Next, we removed non-human users based on unusual relocation speed \citep{hawelka,jurdak2015}. 
+We adopted a relocation speed threshold of 240 m/s as used by \citep{jurdak2015}. 
 We examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold.
@@
 To build our spatial network at a national level, we had to determine the basic units to serve as spatial nodes of the connectivity network of urban regions.
-Previous studies have suggested equi-distant spatial tessellation to generate nodes, which uses voronoi polygons to partition the space based on the collected points~\cite{rinzivillo2012,zhong2014}. 
+Previous studies have suggested equi-distant spatial tessellation to generate nodes, which uses voronoi polygons to partition the space based on the collected points~\citep{rinzivillo2012,zhong2014}. 
 This approach demonstrates improvements for estimating the locations of mobile phone records based on the cell tower triangulation~\cite{gonzalez2008,qian2013}.
-However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\cite{sakaki2010,zandbergen2009}.
-Another popular approach is to partition the space into a grid of spatial pixels~\cite{liuPopMobility,ratti2010}.
-However, the size of the cell can potentially lead to biases due to the Modifiable Area Unit Problem (MAUP)~\cite{openshaw1984,wong2009}, where different choices of unit size can lead to significant variant findings.
-To compare our investigation with the findings of similar studies, and avoid subjectively deciding the cell size, we performed statistical analysis of Twitter user mobility patterns in Great Britain and measured the distribution of collective Twitter user displacements and the radius of gyrations of individuals \cite{gonzalez2008,jurdak2015}.
-The radius of gyration is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008}, which is defined as Eq. \eqref{eq:2}:
+However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\citep{sakaki2010,zandbergen2009}.
+Another popular approach is to partition the space into a grid of spatial pixels~\citep{liuPopMobility,ratti2010}.
+However, the size of the cell can potentially lead to biases due to the Modifiable Area Unit Problem (MAUP)~\citep{openshaw1984,wong2009}, where different choices of unit size can lead to significant variant findings.
+To compare our investigation with the findings of similar studies, and avoid subjectively deciding the cell size, we performed statistical analysis of Twitter user mobility patterns in Great Britain and measured the distribution of collective Twitter user displacements and the radius of gyrations of individuals \citep{gonzalez2008,jurdak2015}.
+The radius of gyration is a metric to distinguish mobility patterns of individuals~\citep{gonzalez2008}, which is defined as Eq. \eqref{eq:2}:
 
@@
 \subsection{Community structure of the spatial networks}
-Based on the derived spatial network, which is a directed weighted graph, we further determined clusters of strongly connected spatial nodes, known as communities, in the graph space~\cite{coscia2011}.
-There are a variety of community detection algorithms that produce different results depending the definition of community within the network~\cite{coscia2011}.
-A common community detection method is based on modularity maximization~\cite{newman2006}, seen in previous studies~\cite{hawelka,ratti2010,song2012}.
-However, such an approach is often problematic: it is found to have an inherent resolution problem, where small communities are either ignored~\cite{fortunato2007} or assigned with high modularity scores \cite{guimera2004}; and it is found to produce less informative partitions in many empirical networks~\cite{good2010}.
-Since our graph is a directed weighted graph, the alternative community detection library documented in the literature is Infomap~\cite{domenico2015,rosvall2008}, which is considered to produce better community detection results~\cite{lancichinetti2009}.
+Based on the derived spatial network, which is a directed weighted graph, we further determined clusters of strongly connected spatial nodes, known as communities, in the graph space~\citep{coscia2011}.
+There are a variety of community detection algorithms that produce different results depending the definition of community within the network~\citep{coscia2011}.
+A common community detection method is based on modularity maximization~\citep{newman2006}, seen in previous studies~\citep{hawelka,ratti2010,song2012}.
+However, such an approach is often problematic: it is found to have an inherent resolution problem, where small communities are either ignored~\citep{fortunato2007} or assigned with high modularity scores \citep{guimera2004}; and it is found to produce less informative partitions in many empirical networks~\citep{good2010}.
+Since our graph is a directed weighted graph, the alternative community detection library documented in the literature is Infomap~\citep{domenico2015,rosvall2008}, which is considered to produce better community detection results~\citep{lancichinetti2009}.
 
-Infomap uses the map equation~\cite{rosvall2010} to represent the probability of flow of random walks within information systems~\cite{rosvall2008}.
+Infomap uses the map equation~\citep{rosvall2010} to represent the probability of flow of random walks within information systems~\citep{rosvall2008}.
 It identifies communities by minimizing the expected description length of the trajectory of a random walker, which is shown below:
@@
 
-\section{Results and Discussion}
+\section{Results}
 \subsection{Collective Mobility Patterns of Twitter Users in Great Britain}
@@
 
-We found that the cumulative distribution function~\cite{clauset2009} of the number of locations visited by each Twitter user follows a two-tier power law distribution (shown in Fig.~\ref{S3_Fig}). 
+We found that the cumulative distribution function~\citep{clauset2009} of the number of locations visited by each Twitter user follows a two-tier power law distribution (shown in Fig.~\ref{S3_Fig}). 
 The majority of the data distributed follows a truncated power-law distribution $P(X\geq x)\sim x^{-\alpha}e^{-\lambda x}$, where $\alpha = 1.24, \lambda =0.00132$; and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $P(X \geq x)\sim x^{-\alpha}$ with $\alpha$ value is 3.2.
@@
 
-The two-tier power law distribution indicates that the collective behavior of Twitter users visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk (a random walk) model~\cite{rhee2011,reynolds2012}, which has also been identified in many human mobility studies using different mobility data~\cite{zhao2015}.
+The two-tier power law distribution indicates that the collective behavior of Twitter users visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk (a random walk) model~\citep{rhee2011,reynolds2012}, which has also been identified in many human mobility studies using different mobility data~\citep{zhao2015}.
 The similarity among the distributions suggests that the mobility data collected from geo-located tweets is temporally stable, at least at the monthly interval, which indicates that our approach using Twitter user mobility to delineate urban boundaries is viable.
 In addition, the L\'{e}vy Walk model reveals the diversity regarding the number of visited locations per user, which indicates a level of ``randomness'' in Twitter user movement across space. 
-It, in turn, justifies our choice of using the map equation community detection algorithm~\cite{rosvall2008} to identify the clusters of urban regional connectedness using large-scale Twitter user movement data.
+It, in turn, justifies our choice of using the map equation community detection algorithm~\citep{rosvall2008} to identify the clusters of urban regional connectedness using large-scale Twitter user movement data.
 
@@
 The radius of gyration describes the deviation of distance from the center of mass in a user's trajectory.
-The probability distributions of the collective user displacement $P(d)$ and radius of gyration $P(r_g)$ are presented in Fig.~\ref{S4_Fig}, where the fitting method for identifying different distance ranges is derived from~\cite{jurdak2015}.
+The probability distributions of the collective user displacement $P(d)$ and radius of gyration $P(r_g)$ are presented in Fig.~\ref{S4_Fig}, where the fitting method for identifying different distance ranges is derived from~\citep{jurdak2015}.
 The probability distribution of the collective displacements can be approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10m, 70m] (accounting for 3 $\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [70m, 70km] (93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 70km] (4 $\%$ of the population).
@@
 In short, these fitting functions suggest the existence of multi-scale or multi-modal urban movements captured from Twitter users in Great Britain, which means the geographically cohesive, non-overlapping urban areas identified in the next section are not just a result of short distance movement but emerge naturally from the broader Twitter user mobility pattern.
-Note that a similar multiphase pattern was observed in Twitter user displacements in Australia, but with slightly different distance ranges\cite{jurdak2015}.
+Note that a similar multiphase pattern was observed in Twitter user displacements in Australia, but with slightly different distance ranges~\citep{jurdak2015}.
 
@@
 Note that the accuracy of these values for defining the distance bound depends upon the accuracy of the location information of each geo-located tweet. 
-These findings are consistent with the findings in the literature on human mobility, where the radius of gyration of human movement is bounded to different distance ranges~\cite{brockmann2006,gonzalez2008}.
+These findings are consistent with the findings in the literature on human mobility, where the radius of gyration of human movement is bounded to different distance ranges~\citep{brockmann2006,gonzalez2008}.
 The distance-decay effects found in both user displacements and the radius of gyration shows evidence of spatial proximity in Twitter user movement. 
@@
 \subsection{Redrawing Great Britain’s Urban Boundaries}
-The network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells that provide an adequate resolution for a country wide investigation~\cite{ratti2010}.
+The network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells that provide an adequate resolution for a country wide investigation~\citep{ratti2010}.
 The edges of this network were derived from the number of directed Twitter user displacements between each pair of cells.
@@
 We found that restricting the trip distance results in different delineations of the catchment area around these centers.
-For example, one could explain these effects as a manifestation of the underlying gravity law~\cite{simini2012} and the distance decay effect on attracting movers~\cite{gonzalez2008}.
+For example, one could explain these effects as a manifestation of the underlying gravity law~\citep{simini2012} and the distance decay effect on attracting movers~\citep{gonzalez2008}.
 Remarkably, our approach performed well in terms of dividing the entire space with minimum gaps.
@@
 In addition, the distance range of the movements is usually explained by local socio-economic factors (e.g., work commuting ) that provide for a specific interpretation of the apparent patterns.
-The patterns obtained from Twitter user mobility are comparable to the patterns produced by those of the network of landline phone calls~\cite{ratti2010}.\
+The patterns obtained from Twitter user mobility are comparable to the patterns produced by those of the network of landline phone calls~\citep{ratti2010}.\
 For example, the region of Wales appears to consist of three communities as found in the connectivity of both phone calls and long distance movements. 
-However, the regions extracted from the mobility network seems to be more spatially consistent with minimal spatial gaps compared to the partitions extracted from land-line call networks in Great Britain~\cite{ratti2010}.
+However, the regions extracted from the mobility network seems to be more spatially consistent with minimal spatial gaps compared to the partitions extracted from land-line call networks in Great Britain~\citep{ratti2010}.
 
@@
 \clearpage
-\section{Conclusion}
+\section{Conclusion and Discussion}
 In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
@@
 \bibitem[\protect\citeauthoryear{Coscia {\itshape{et~al.}}}{2011}]{coscia2011}
-Coscia, M., Giannotti, F., Pedreschi, D., 2011. A Classification for Community Discovery Methods in Complex Networks. Statistical Analysis and Data Mining, 4, 512–546. doi:10.1002/sam.10133
-
+Coscia, M., Giannotti, F., Pedreschi, D., 2011. A Classification for Community Discovery Methods in Complex Networks. Statistical Analysis and 
 \bibitem[\protect\citeauthoryear{De Domenico {\itshape{et~al.}}}{2015}]{domenico2015}
@@
 
-\bibitem[\protect\citeauthoryear{schliephake}{2014}]{schliephake}
+\bibitem[\protect\citeauthoryear{Schliephake}{2014}]{schliephake}
 Schliephake, C., 2014. Urban Ecologies: City Space, Material Agency, and Environmental Politics in Contemporary Culture. Lexington Books.

### 2016-04-12 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
edit

@@
 \subsection{Overview}
-We use large-scale Twitter user spatial interactions inferred from the collective mobility patterns of Twitter users to delineate urban boundaries in Great Britain.
+In this research, we use large-scale Twitter user spatial interactions inferred from the collective mobility patterns of Twitter users to delineate urban boundaries in Great Britain.
 A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\citep{gonzalez2008}.
-This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two recorded locations is one month.
+This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two consecutive recorded locations is one month.
 To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the islands of Great Britain.
@@
 We examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold.
+
 Because the original location information embedded in the geo-tag is given in units of latitude and longitude, we projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations.

### 2016-04-13 sq_mobility/sq_mobility_twitter.tex
init

\documentclass[a4paper,11pt]{article}
\begin{document}
\title{Mining sequential mobility patterns from semantic Twitter user trajectories}
%\author{names}
\maketitle

\section*{Abstract}

\section*{Introduction}
Understanding detailed human mobility patterns is great importance for

\section*{Methods and Materials}

\end{document}

### 2016-04-19 sq_mobility/sq_mobility_twitter.tex
add

@@
 \section*{Introduction}
-Understanding detailed human mobility patterns is great importance for
+Understanding detailed human mobility patterns in the urban settings is critical for a wide range applications, such as urban planning, traffic management, and even the spatial spread of disease.
 

### 2016-04-22 sq_mobility/sq_mobility_twitter.tex
new edits

@@
 \documentclass[a4paper,11pt]{article}
+\usepackage[margin=1in]{geometry}
+\usepackage{lastpage,fancyhdr,graphicx}
+\graphicspath{ {/figure/} }
+
 \begin{document}
-\title{Mining sequential mobility patterns from semantic Twitter user trajectories}
-%\author{names}
+%\title{Mining sequential mobility patterns from semantic Twitter user trajectories}
+\title{Sequential mobility patterns in people's daily life}
+\author{Junjun Yin and Chao Zhang}
 \maketitle
@@
 \section*{Abstract}
+Understanding human mobility patterns
 
@@
 
+On the other hand, to get 
+However, the geo-located Twitter Data contains a variety of uncertainties, such spatial sparseness
+To address these issue, this study implements a novel approach for getting the semantic trajectories by integrating detailed land use maps with geo-located Twitter data.
+
+Emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital traces in the form of real-world trails and footprints~\cite{thatcher2014}.
+One significant advantage of LBSM data streams is the large spatial coverage, for example, researchers have used geo-located Twitter data for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible by using other mobility datasets (e.g., GPS traces and mobile phone call records).
+In addition, the publicly available LBSM data streams offer unique opportunities for conducting reproducible scientific findings regarding the concerns of infringement on individual privacy, such as using mobile phone call records~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}.
+
 \section*{Methods and Materials}
+\subsection*{Geo-located Twitter Data}
+In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
+To ensure the complete coverage over Great Britain, we have set the bounding box to British Isles (lower left coordinates in (latitude, longitude): (49.497, -14.854) and upper right coordinates: (61.186, 2.637)), which also includes the whole area of Ireland and a part of France.
+We have implemented a data crawler and continuously collected 7-month data (1st June – 31st December, 2014) with over 101.8 million tweets and 60 GB in size.
+During the data collection phase, the data crawler did not encounter any issue regarding whether it exceeds the data quota by the 1$\%$ policy mentioned in (Hawelka et al., 2014).
+It means we have managed to download all the geo-located tweets for the given bounding box.
+In particular, to showcase the overall spatial coverage of the collected geo-located tweets, a density map of the Twitter user locations in British Isles for July 2014 is shown in Figure 4, where the collected points alone visually reveal the geography of cities and countries, e.g.
+the clusters with high density of tweets (in color red) correspond to the skeleton of major cities.
+
+\subsection*{The shape of human mobility}
+
+\begin{figure}[ht]
+	\includegraphics[width=1.0\linewidth]{./figure/gyration_chicago}
+	\caption{{\bf The density map of the Twitter user locations for July 2014}}
+	\label{Fig_gyration}
+\end{figure}
+
+\begin{figure}[ht]
+	\includegraphics[width=1.0\linewidth]{./figure/Chicago_Shape}
+	\caption{{\bf The density map of the Twitter user locations for July 2014}}
+	\label{Fig_shape}
+\end{figure}
 

### 2016-05-01 sq_mobility/sq_mobility_twitter.tex
new edits

@@
 \graphicspath{ {/figure/} }
+\usepackage{authblk}
 
@@
 \title{Sequential mobility patterns in people's daily life}
-\author{Junjun Yin and Chao Zhang}
+\author[1]{Junjun Yin}
+\author[2]{Chao Zhang}
+\author[1]{Shaowen Wang\thanks{shaowen@illinois.edu}}
+\affil[1]{CyberGIS Center for Advanced Digtial and Spatial Studies}
+\affil[2]{Department of Computer Science}
+\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
+
+\renewcommand\Authands{ and }
+
 \maketitle
 
-\section*{Abstract}
+\section*{\centering Abstract}
 Understanding human mobility patterns
@@
 
+\section*{Related Work}
+
 \section*{Methods and Materials}
+
 \subsection*{Geo-located Twitter Data}
@@
 	\includegraphics[width=1.0\linewidth]{./figure/gyration_chicago}
-	\caption{{\bf The density map of the Twitter user locations for July 2014}}
+	\caption{{\bf The distribution of the radius of gyrations for Twitter users in Chicago}}
 	\label{Fig_gyration}
@@
 	\includegraphics[width=1.0\linewidth]{./figure/Chicago_Shape}
-	\caption{{\bf The density map of the Twitter user locations for July 2014}}
+	\caption{{\bf The shape of Twitter user mobility in Chicago for year 2014}}
 	\label{Fig_shape}
@@
 
+\begin{figure}[ht]
+	\includegraphics[width=1.0\linewidth]{./figure/firsttime}
+	\caption{{\bf The shape of Twitter user mobility in Chicago for year 2014}}
+	\label{Fig_shape}
+\end{figure}
+
+\section*{Results}
+
+\section*{Discussion and Conclusion}
+
 \end{document}

### 2016-05-01 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
new figure
new
edits

@@
 
-\title{{\itshape Delineate urban boundaries in Great Britain from the network of Twitter user spatial interactions} }
+\title{{\itshape The geography of urban boundaries in Great Britain from the network of Twitter user spatial interactions} }
 \maketitle
@@
 \begin{center}
-\includegraphics[width=0.8\linewidth]{./figure/S2_twitter_density_Fig_1}
-\caption{\bfseries{A density map of the Twitter user locations for July 2014}}
+\includegraphics[width=0.8\linewidth]{./figure/usa}
+\caption{\bfseries{Each point corresponds to a geo-located tweet collected for this study. Twitter activity is most apparent in urban areas.}}
 \label{S2_Fig}

### 2016-05-03 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
new line

@@
 
-\section{Related Work}
+\section{Background and Related Work}
 
@@
 \begin{thebibliography}{9}
-
 \markboth{}{International Journal of Geographical Information Science}
@@
 \bibitem[\protect\citeauthoryear{Brockmann {\itshape{et~al.}}}{2006}]{brockmann2006}
-Brockmann, D., Hufnagel, L., Geisel, T., 2006. The scaling laws of human travel. Nature 439, 462–5. doi:10.1038/nature04292
+Brockmann, D., Hufnagel, L., Geisel, T., 2006. The scaling laws of human travel. Nature 439, pp. 462-465. doi:10.1038/nature04292
 
 \bibitem[\protect\citeauthoryear{Clauset {\itshape{et~al.}}}{2009}]{clauset2009}
-Clauset, A., Shalizi, C., Newman, M., 2009. Power-Law Distributions in Empirical Data. Society for Industrial and Applied Mathematics Review. 51, 661–703. doi:10.1137/070710111
+Clauset, A., Shalizi, C., Newman, M., 2009. Power-Law Distributions in Empirical Data. Society for Industrial and Applied Mathematics Review. 51, pp. 661-703. doi:10.1137/070710111
 
 \bibitem[\protect\citeauthoryear{Coscia {\itshape{et~al.}}}{2011}]{coscia2011}
-Coscia, M., Giannotti, F., Pedreschi, D., 2011. A Classification for Community Discovery Methods in Complex Networks. Statistical Analysis and 
+Coscia, M., Giannotti, F. and Pedreschi, D., 2011. A classification for community discovery methods in complex networks. Statistical Analysis and Data Mining, 4(5), pp. 512-546.
+
 \bibitem[\protect\citeauthoryear{De Domenico {\itshape{et~al.}}}{2015}]{domenico2015}
@@
 \bibitem[\protect\citeauthoryear{Fortunato and Barthélemy}{2007}]{fortunato2007}
-Fortunato, S., Barthélemy, M., 2007. Resolution limit in community detection. Proceedings of the National Academy of Sciences, 104, 36–41. doi:10.1073/pnas.0605965104
+Fortunato, S., Barthélemy, M., 2007. Resolution limit in community detection. Proceedings of the National Academy of Sciences, 104, pp. 36-41. doi:10.1073/pnas.0605965104
+
+\bibitem[\protect\citeauthoryear{Gao {\itshape{et~al.}}}{2014}]{gao2014}
+Gao, S., Yang, J.A., Yan, B., Hu, Y., Janowicz, K.
+and McKenzie, G., 2014.
+Detecting Origin-Destination Mobility Flows From Geotagged Tweets in Greater Los Angeles Area.
+In Eighth International Conference on Geographic Information Science (GIScience'14).
 
 \bibitem[\protect\citeauthoryear{González {\itshape{et~al.}}}{2008}]{gonzalez2008}
-González, M.C., Hidalgo, C.A., Barabási, A.-L., 2008. Understanding individual human mobility patterns. Nature, 453, 779–82. doi:10.1038/nature06958
+González, M.C., Hidalgo, C.A., Barabási, A.-L., 2008. Understanding individual human mobility patterns. Nature, 453, pp. 779-782. doi:10.1038/nature06958
 
@@
 Geo-located Twitter as proxy for global mobility patterns.
-Cartography and Geographic Information Science, 41, 260–271.
+Cartography and Geographic Information Science, 41, pp.
+260-271.
 doi:10.1080/15230406.2014.890072
 
+\bibitem[\protect\citeauthoryear{Huang {\itshape{et~al.}}}{2016}]{huang2016}
+Huang, Q.
+and Wong, D.W., 2016.
+Activity patterns, socioeconomic status and urban spatial structure: what can social media data tell us?.
+International Journal of Geographical Information Science, pp.1-26.
+
 \bibitem[\protect\citeauthoryear{Jiang and Miao}{2015}]{jiang2015}
-Jiang, B., Miao, Y., 2015. The evolution of natural cities from the perspective of location-based social media. The Professional Geographer, 67(2), 295-306.
+Jiang, B., Miao, Y., 2015. The evolution of natural cities from the perspective of location-based social media. The Professional Geographer, 67(2), pp. 295-306.
 
@@
 
-\bibitem[\protect\citeauthoryear{Liu {\itshape{et~al.}}}{2015}]{liu2015}
-Liu, X., Gong, L., Gong, Y., Liu, Y., 2015. Revealing travel patterns and city structure with taxi trip data. J. Transportation Geography, 43, 78–90. doi:10.1016/j.jtrangeo.2015.01.016
-
 \bibitem[\protect\citeauthoryear{Liu {\itshape{et~al.}}}{2014}]{liuPopMobility}
@@
 
+\bibitem[\protect\citeauthoryear{Liu {\itshape{et~al.}}}{2015}]{liu2015}
+Liu, X., Gong, L., Gong, Y., Liu, Y., 2015. Revealing travel patterns and city structure with taxi trip data. J. Transportation Geography, 43, pp. 78-90. doi:10.1016/j.jtrangeo.2015.01.016
+
+\bibitem[\protect\citeauthoryear{Liu {\itshape{et~al.}}}{2015}]{liu2014}
+Liu, Y., Sui, Z., Kang, C., Gao, Y., 2014. Uncovering patterns of inter-urban trip and spatial interaction from social media check-in data. PLoS ONE, 9(1), p.e86026.
+
 \bibitem[\protect\citeauthoryear{Long {\itshape{et~al.}}}{2015}]{long2015}
-Long, Y., Han, H., Tu, Y., Shu, X., 2015. Evaluating the effectiveness of urban growth boundaries using human mobility and activity records. Cities, 46, 76-84.
+Long, Y., Han, H., Tu, Y., Shu, X., 2015. Evaluating the effectiveness of urban growth boundaries using human mobility and activity records. Cities, 46, pp. 76-84.
+
+\bibitem[\protect\citeauthoryear{Long {\itshape{et~al.}}}{2015}]{long2015}
+Luo, F., Cao, G., Mulligan, K., Li, X., 2016. Explore spatiotemporal and demographic characteristics of human mobility via Twitter: A case study of Chicago, Applied Geography, 70, pp. 11-25
 
@@
 \bibitem[\protect\citeauthoryear{Newman}{2006}]{newman2006}
-Newman, M.E.J., 2006. Modularity and community structure in networks. Proceedings of the National Academy of Sciences, 103, 8577–82. doi:10.1073/pnas.0601602103
+Newman, M.E.J., 2006. Modularity and community structure in networks. Proceedings of the National Academy of Sciences, 103, pp. 8577-8582. doi:10.1073/pnas.0601602103
 
@@
 Truncated levy walks are expected beyond the scale of data collection when correlated random walks embody observed movement patterns.
-Journal of The Royal Society Interface, 9(68), 528-534.
+Journal of The Royal Society Interface, 9(68), pp.
+528-534.
 
 \bibitem[\protect\citeauthoryear{Rhee {\itshape{et~al.}}}{2011}]{rhee2011}
-Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S. J., and Chong, S., 2011. On the levy-walk nature of human mobility. IEEE/ACM transactions on networking (TON), 19(3), 630-643.
+Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S. J., and Chong, S., 2011. On the levy-walk nature of human mobility. IEEE/ACM transactions on networking (TON), 19(3), pp. 630-643.
 
@@
 KI - Künstl.
-Intell.
-26, 253–260.
+Intelligenz, 26, pp.
+253-260.
 doi:10.1007/s13218-012-0181-8
@@
 \bibitem[\protect\citeauthoryear{Rosvall {\itshape{et~al.}}}{2010}]{rosvall2010}
-Rosvall, M., Axelsson, D., Bergstrom, C.T., 2010. The map equation. The European Physical Journal Special Topics, 178, 13–23. doi:10.1140/epjst/e2010-01179-1
+Rosvall, M., Axelsson, D., Bergstrom, C.T., 2010. The map equation. The European Physical Journal Special Topics, 178, pp. 13–23. doi:10.1140/epjst/e2010-01179-1
 
 \bibitem[\protect\citeauthoryear{Rosvall and Bergstrom}{2008}]{rosvall2008}
-Rosvall, M., Bergstrom, C.T., 2008. Maps of random walks on complex networks reveal community structure. Proceedings of the National Academy of Sciences, 105, 1118–1123.
+Rosvall, M., Bergstrom, C.T., 2008. Maps of random walks on complex networks reveal community structure. Proceedings of the National Academy of Sciences, 105, pp. 1118-1123.
 
@@
 Earthquake Shakes Twitter Users: Real-time Event Detection by Social Sensors, in: Proceedings of the 19th International Conference on World Wide Web, WWW ’10.
-ACM, New York, NY, USA, pp.
-851–860.
-doi:10.1145/1772690.1772777
+ACM, NY, USA, pp.
+851-860
 
@@
 \bibitem[\protect\citeauthoryear{Simini {\itshape{et~al.}}}{2012}]{simini2012}
-Simini, F., González, M. C., Maritan, A., Barabási, A. L., 2012. A universal model for mobility and migration patterns. Nature, 484(7392), 96-100.
+Simini, F., González, M. C., Maritan, A., Barabási, A. L., 2012. A universal model for mobility and migration patterns. Nature, 484(7392), pp. 96-100.
 
@@
 
+\bibitem[\protect\citeauthoryear{Steiger {\itshape{et~al.}}}{2015}]{steiger2015}
+Steiger, E., Westerholt, R., Resch, B.
+and Zipf, A., 2015.
+Twitter as an indicator for whereabouts of people?
+Correlating twitter with uk census data.
+Computers, Environment and Urban Systems, 54, pp.
+255-265.
+
 \bibitem[\protect\citeauthoryear{Thiemann {\itshape{et~al.}}}{2010}]{thiemann}
@@
 \bibitem[\protect\citeauthoryear{Zandbergen}{2009}]{zandbergen2009}
-Zandbergen, P.A., 2009. Accuracy of iPhone Locations: A Comparison of Assisted GPS, WiFi and Cellular Positioning. Transactions in GIS, 13, 5–25. doi:10.1111/j.1467-9671.2009.01152.x
+Zandbergen, P.A., 2009. Accuracy of iPhone Locations: A Comparison of Assisted GPS, WiFi and Cellular Positioning. Transactions in GIS, 13, pp. 5-25. doi:10.1111/j.1467-9671.2009.01152.x
 
@@
 Detecting the dynamics of urban structure through spatial network analysis.
-International Journal of Geographical Information Science, 28, 2178–2199.
-doi:10.1080/13658816.2014.914521
+International Journal of Geographical Information Science, 28, pp.
+2178-2199, doi:10.1080/13658816.2014.914521
 

### 2016-05-03 NY_taxi_Flow/NY_Taxi_Flow_Capacity.tex
init

\documentclass[a4paper,11pt]{article}
\begin{document}
\title{A visual-analytic approach to understand New York taxi data with flow dimension and capacity}
\maketitle

\section*{\centering Abstract}

\section{Introduction}
Talk about origin and destination flow
Migration, traffic management

Hierarchical

In contrast to the network derived from

\section{Related Work}

\section{Methods and Materials}

\end{document}

### 2016-05-04 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
reference

@@
 To protect Twitter user privacy, the id field was replaced with a randomly generated unique number. 
-Because we are interested in collective Twitter user movement instead of individual user trajectories, the content of the message was removed. 
+Because we are interested in collective Twitter user movement instead of individual user trajectories,
+each geo-location of a
+similar to the approach used in
+
+the content of the message was removed. 
 Our simplified geo-located tweet dataset can be shared with other researchers upon request.
@@
 
-\subsection{Redrawing Great Britain’s Urban Boundaries}
+\subsection{Redrawing Great Britain's Urban Boundaries}
 The network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells that provide an adequate resolution for a country wide investigation~\citep{ratti2010}.
@@
 Fortunato, S., Barthélemy, M., 2007. Resolution limit in community detection. Proceedings of the National Academy of Sciences, 104, pp. 36-41. doi:10.1073/pnas.0605965104
+
+\bibitem[\protect\citeauthoryear{Frank {\itshape{et~al.}}}{2013}]{frank2013}
+Frank, M.R., Mitchell, L., Dodds, P.S. and Danforth, C.M., 2013. Happiness and the patterns of life: A study of geolocated tweets. Scientific reports, 3.
 

### 2016-05-08 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
new
change

@@
 Defining the boundaries of urban regions is important to city planning, traffic management and resource allocation.
-Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's daily interactions with the urban space in their intra- and inter regional activities.
+Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter regional activities.
 In this study, we presented a method to redraw urban boundaries based upon human interaction with the physical space.
@@
 
-In this study, we describe a novel approach to delineating urban boundaries based on the movements of 
+In this study, we describe a novel approach to delineating urban boundaries based on the actual movements (i.e., the reallocation in space) of 
 Twitter users extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
@@
 \begin{center}
-\includegraphics[width=0.8\linewidth]{./figure/usa}
-\caption{\bfseries{Each point corresponds to a geo-located tweet collected for this study. Twitter activity is most apparent in urban areas.}}
+\includegraphics[width=0.8\linewidth]{./figure/uk}
+\caption{{\bf The spatial coverage of collected geo-located Twitter messages in Great Britain.} Each point corresponds to a geo-located tweet collected for this study.
+Twitter activity is most apparent in urban areas.}
 \label{S2_Fig}

### 2016-05-08 MovePattern_revision/Twitter_MovementPatterns_VisualAnalytics.tex
test

\documentclass[a4paper, 11pt]{article}
\usepackage{authblk}
\usepackage[round, sort, numbers, authoryear]{natbib}
\usepackage{regexpatch}
\usepackage{graphicx}
\graphicspath{ {/figures/} }
\usepackage[section]{placeins}
\usepackage{setspace}
\usepackage[margin=1in]{geometry}
\usepackage[]{algorithm2e}
\usepackage{caption}
\usepackage{subcaption}
\date{}

\usepackage{lineno}
%\linenumbers
%\bibpunct{(}{)}{;}{a}{,}{,}
%\bibpunct{}{}{,}{s}{,}{,}

\begin{document}
%\input{./Title.tex}
%\title{\itshape Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
\title{\itshape Exploring Multi-scale Spatiotemporal Twitter User Mobility Patterns Using Geo-located Twitter Data}
	\author{}
%	\author[1, 2, 3]{Junjun Yin}
%	\author[1, 2, 3, 4]{Shaowen Wang}	
%%	\author[1, 2, 3, 4, \footnote{Corresponding author: shaowen@illinois.edu}]{Shaowen Wang}
%	
%	\affil[1]{
%	\it	CyberGIS Center for Advanced Digital and Spatial Studies
%	}
%	\affil[2]
%	{
%	\it	CyberInfrastructure and Geospatial Information Laboratory
%	}
%	\affil[3]
%	{
%	\it	Department of Geography and Geographic Information Science
%	}
%	\affil[4]
%	{
%	\it	National Center for Supercomputing Applications \authorcr
%	\it	University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA
%	}

\maketitle

%\makeatletter
%\xpatchcmd{\@@cite}{\def\BCA##1##2{{\@BAstyle ##1}}}{\def\BCA##1##2{{\@BAstyle ##2}}}{}{}
%\makeatother
%
\renewcommand{\baselinestretch}{1.5}
%\renewcommand{\BBAA}{and}  % between authors in parenthetical cites and ref. list
%\renewcommand{\BBAB}{and} % between authors in in-text citation
%\renewcommand{\BAnd}{and}  % for ``Ed. \& Trans.'' in ref. list

\pagenumbering{gobble}
\onehalfspacing
\section*{\begin{center}
Abstract
\end{center}}
Understanding human mobility patterns is of great importance for urban planning, traffic management, and even marketing campaign.
However, the capability of capturing detailed human movements with fine-grained spatial and temporal granularity is still limited.
In this study, we have extracted high-resolution mobility data from a collection of 1.3 billion geo-located Twitter messages to study multi-scale spatiotemporal Twitter user mobility patterns in the United States during the year 2014. 
Regarding the concerns of infringement on individual privacy, such as the mobile phone call data with restricted access, the dataset is collected from publicly accessible Twitter data streams.
In this study, we have developed a scalable visual-analytics framework to deliver efficiency and scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-scale spatiotemporal user mobility patterns.
We have performed a set of statistical analysis to understand Twitter user mobility patterns across multi-level spatial scales and temporal granularity.
In particular, the Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns.
By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
\newline

\noindent\textbf{Keywords:} Geo-located tweets, mobility patterns, multi-scale spatiotemporal analysis, scalable visual-analytics framework\\

Notes: What about randomly choose several states and perform the analysis
\cleardoublepage

\pagenumbering{arabic}
\setcounter{page}{1}
\onehalfspacing

\section{Introduction}
Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\citep{zheng2008understanding}, traffic management~\citep{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\citep{belik2011natural}.
Earlier research efforts relied on low resolution mobility data to understand human mobility patterns, such as using census records to understand human migration patterns~\citep{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\citep{brockmann2006scaling}.
However, the lack of detailed human movements with fine-grained spatial and temporal granularity limits the findings to capture mobility patterns of individuals~\citep{gonzalez2008understanding,Jurdak2015}.
In addition to the mobility data collected by GPS trackers~\citep{zheng2008understanding, rhee2011levy} and mobile phone call records~\citep{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, 
emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints~\citep{thatcher2014living} in the form of real-world trails and footprints.
One significant advantage of LBSM data streams is the large spatial coverage, for example, researchers have used geo-located Twitter data for studying global mobility patterns~\citep{hawelka2014geo}, which is otherwise impossible by using other mobility datasets (e.g., GPS traces and mobile phone call records). 
In addition, the publicly available LBSM data streams offer unique opportunities for conducting reproducible scientific findings regarding the concerns of infringement on individual privacy, such as using mobile phone call records~\citep{giannotti2008mobility,crampton2014collect,Jurdak2015}.

Many studies have adopted the LBSM data streams to study human mobility patterns. For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects~\citep{gonzalez2008understanding} in the collective user movements to reveal different travel modes~\citep{Jurdak2015}, travel demands~\citep{wu2014intra,hasan2013understanding}, and the impact of social connections~\citep{cho2011friendship}.
These studies have provided strong support for using LBSM data as proxies for studying mobility patterns of individuals and valuable insights into human mobility dynamics. 
However, in these studies, the measurements of distances are either fixed in a certain time period or a specific region, where they do not consider the variations of movements in different spatial scales and temporal ranges.
To be more specific, these studies lack examinations of the detailed movements across different geographical scales and temporal granularity, for instances, whether there are temporal (e.g., monthly or seasonal) changes within the movements, and how the mobility patterns vary across different spatial scales (e.g., intra- or inter county, city or country level). 
These insights are critical to advance our understandings of the collective mobility patterns for a variety of applications, such as examining the mobility patterns across different cities~\citep{noulas2012tale}, the spread patterns of disease~\citep{balcan2009multiscale, tamerius2011global} and touristic activities~\citep{hawelka2014geo}.
While the high resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data intensive challenges for developing a multi-scale spatiotemporal analysis framework~\citep{tsou2015} to deal with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales.
In addition, to enable efficient analysis and visualization of the mobility patterns at different spatiotemporal scales, it is essential for such a framework to provide scalability for addressing the data intensive challenges~\citep{cao2014scalable}.

In this paper, we have explored and studied the Twitter user mobility patterns across multi-level spatial scales and temporal granularity in the United States during the year 2014. 
The mobility data is extracted from1.3 billion geo-located Twitter messages (i.e., tweets) from 1$^{st}$ January to 31$^{st}$ December, 2014 in the United States with over 6 million Twitter users and over 1 TB in file size. 
To address the data-intensive challenges embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
This framework is implemented based on high-performance distributed computing environment using Apache Hadoop\footnote{http://hadoop.apache.org/}, which is an open source software framework to enable distributed processing of large datasets across computing clusters.
%We have implemented a set of efficient MapReduce~\citep{dean2008mapreduce} algorithms to deliver scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
With this framework, we have performed a set of statistical analysis to understand the spatiotemporal Twitter user mobility patterns. 
We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions. 
In particular, the Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals~\citep{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\citep{Jurdak2015}.
By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.

The remainder of this paper is organized as follows.
Section 2 describes the related work in the context of studying mobility patterns using LBSM data, in particular, geo-located Twitter data.
We focus on research challenges in visual-analytics methods to enable multi-scale
spatiotemporal analysis with massive movement datasets, including data management, multi-level spatiotemporal user trajectory modeling and visualization.
In particular, we look into high performance distributed computing approach for addressing such challenges.
Section 3 details the processes for extracting, aggregating and summarizing multi-level spatiotemporal Twitter user mobility patterns.
Section 4 presents the case study of performing visual-analytics for seeking Twitter mobility patterns in the United States of year 2014. Section 5 concludes the paper.

\section{Mobility patterns in Location Based Social Media data}
\subsection{Geo-located Twitter data for studying large-scale user movements}
To understand detailed human mobility patterns of individuals, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
However, the low-resolution mobility data collected from census records~\citep{greenwood1985human} is estimated and aggregated at census tract level, while tracking of bank notes~\citep{brockmann2006scaling} is at zip code level and do not necessarily reflecting movements of the same individuals~\citep{gonzalez2008understanding}.
In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\citep{zheng2008understanding}. However, the data is often limited in spatial scale (e.g. within a specific city or region) with a small group of people, for example, 182 and 226 volunteers participated in collecting such mobility data in~\citep{zheng2010geolife} and~\citep{rhee2011levy} respectively. Other than tracking people directly, the vehicle-based GPS data is often tied to a specific vehicle (e.g. taxi), which may only be accessible for a certain group of people~\citep{kung2014exploring}.

Another approach from the literatures for studying human mobility is using mobile phone call data in the form of Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\citep{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}. 
Such a dataset can cover relatively large spatial scale (e.g., country level)~\citep{becker2013human,sobolevsky2013delineating} and a large portion of the population in the study region~\citep{kung2014exploring}. However, due to the concerns of infringement on individual privacy, the mobile phone call data is not publicly accessible, which is not ideal  for conducting reproducible scientific findings, such as validating or extending the existing discoveries.

In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter). 
LBSM enables users to attach their current location as a geo-tag to the message they will post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\citep{Jurdak2015}.
A Big Data scenario emerges when millions social media users constantly posting messages.
However, there are some limitations and complexities in directly using the LBSM data for study human mobility patterns. 
For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place. It has been criticized for the lack of representativeness of the population as not all people use social media or send geo-located messages~\citep{kung2014exploring}. Another research challenge is to identify the users, as a social media account is not equal to a real person in the physical world~\citep{tsou2015}.
Although many studies started to look into the demographic information of LBSM data, in particular Twitter data~\citep{mitchell2013geography,longley2015geotemporal}, these issues certainly require us to pose more strict criteria in filtering and extracting individual movements.

In this study, geo-located Twitter data is chosen as source for studying detailed mobility patterns. Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries. It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\citep{cranshaw2012livehoods, hasan2013understanding}.
In addition, it presents some unique advantages that make it suitable for studying human mobility patterns.
For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\citep{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\citep{hawelka2014geo}, which is almost impossible for other mobility datasets.
More importantly, by continuously monitoring the geo-located Twitter data streams with large volumes of detailed and frequently updated spatiotemporal  records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements).

\subsection{Data-intensive challenges for multi-scale geo-visual analytics}
Mobility data is essentially a collection of spatiotemporal records of people moving from one location to another in the geographic space.
To study mobility patterns of individuals, a space-time trajectory~\citep{hagerstrand1985time} of each individual should be modeled and constructed to quantify the collective movements over space and time.
Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of displacements and radius of gyrations of individuals, to study the mobility dynamics.
At the same time, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\citep{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal granularity.
For example, a geo-visualization approach was used to study human activity patterns, where user trajectories are mapped in a 3D space ordered by timestamps in the third dimension~\citep{kwan2004geovisualization}. While such an approach enables visualization of detailed trajectories, its capability is limited in dealing with large-volume movement datasets~\citep{andrienko2007designing}.
For example, a visual clutter problem is likely to occur when visualizing massive amount of user trajectories, which makes it difficult for capture meaningful mobility patterns.

Instead of directly visualizing individual user trajectories, a space-time cube approach was proposed in analyzing and visualizing the collective trajectories by providing flexibilities in setting up both spatial and temporal ranges, and therefore to study the mobility patterns across different spatial units (e.g. countries, states, and cities, etc.) and identify the changes over space and time~\citep{maceachren2001research, maceachren2004maps}.
In this connection, visual-analytics methods are proposed to help better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\citep{andrienko2007designing,andrienko2007visual}.
Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\citep{andrienko2007designing}.
Also, it is useful to group the subsets of user trajectories based on the shared characteristics for smooth transformations of space and time. For example, a network approach was used to summarize the actual movements in Twitter user trajectories as movement flows among different countries~\citep{hawelka2014geo}.

Employing visual-analytics methods dealing with massive movement datasets is not only beneficial for optimizing visualizations but also provides a great deal of flexibilities for performing statistical analysis in seeking mobility patterns with different level of spatiotemporal details. 
By conveying the findings from statistical analysis, it provides another visualization form regarding the corresponding mobility patterns, in a sense, to avoid the problems of visual clutters.
However, in the context of studying mobility patterns using large volume of geo-located Twitter data, the inherited large data volume poses significant data intensive challenges for these mentioned visual-analytics methods to scale with both the data volume and the computational requirements (e.g., movement extraction and trajectory modeling)~\citep{cao2014scalable}.
For example, in our study, 1.3 billion geo-located tweets were collected with over 1 TB in file size.
To construct a space-time trajectory of an individual, it is necessary to go through the massive dataset to sort and update the trajectory whenever a new location is found. 
Such a task is already computationally demanding, let along breaking the trajectories to construct space-time cube with multiple spatial scale and temporal ranges. 
In particular, developing a multi-scale spatiotemporal analysis framework is identified as one of the research challenges for dealing with social media Big Data~\citep{tsou2015}. 
To address the data-intensive challenges, there is a need to develop a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.

%\subsection{Accommodating LBSM Big Data with Hadoop}
%Apache Hadoop is an open source software framework designed to facilitate data intensive computing on large commodity clusters.
%It combines a distributed file system, namely Hadoop Distributed File System(HDFS)~\citep{shvachko2010hadoop} with MapReduce programming paradigm, which can be applied to wide range of data-intensive problems.
%MapReduce is a programming model and an associated software framework designed to process massive data in a distributed fashion~\citep{dean2008mapreduce}.
%MapReduce breaks the entire computation into small tasks and schedule them among different computing nodes.
%MapReduce consists of two main stages: map and reduce.
%In the map stage, input data is converted into series of intermediate $\langle key, value\rangle$ pairs.
%Customized computation will be performed in the reduce stage based on the same intermediate key.
%This framework provides parallelization since both map and reduce tasks are considered independent and can be done in parallel. More importantly, it provides scalability in relation to the growth of data size, where Hadoop can scale to more computing nodes in the cluster to maintain the performance.
%
%Our framework benefits from using Hadoop in both data management and processing.
%First, since the input data is large it is desirable to store it on multiple machines.
%Second, by using Hadoop we can parallelize the computational tasks and make the data processing faster and more efficient.
%Further, by adopting the MapReduce computing paradigm, we can model each individual user's trajectory by treating user's unique ID as key, and summarize the movement flows among different spatial units by utilizing the ID of the spatial unit as key. The details will be introduced in the following section.

\section{Materials and Methods}
\subsection{Geo-located Twitter data}
Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at. In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it. 
In our case, to ensure the complete coverage over the United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: -167.276413, longitude: 5.499550) and upper right (latitude: -52.233040, longitude: 83.162102).
The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2GB in size) collected per day.
We have collected more than 1.3 billion geo-located tweets from 1$^{st}$ January to 31$^{st}$ December, 2014 with 6,147,430 Twitter users and 1 TB in file size.

As a social media account is not equal to a real person in the physical world~\citep{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed the duplicated messages\footnote{https://support.twitter.com/articles/18311-the-twitter-rules} in the dataset; and then we attempted to remove non-human users based on unusual relocating speed (Hawelka et al., 2014; Jurdak et al., 2015). 
In this case, we adopted the speed limit value as 240 m/s used in (Jurdak et al., 2015), where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit. 
Finally, we used the geographic boundaries of the United States\footnote{https://www.census.gov/geo/maps-data/data/} (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section. Based on these reinforcements, the dataset contains 1,052,861,000 tweets and 4,559,205 unique users.

\subsection{A scalable visual-analytics framework}
To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
The scalable visual-analytics framework consists of two main units: (1) Data collection unit: a Twitter data crawler that continuously collects raw geo-located tweets using the Twitter Streaming API. (2) Data processing unit: a distributed computing environment using Apache Hadoop for modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing the movements at multiple spatiotemproal levels.
An overall system architecture of the framework that chains the three units is shown in Figure 1. The details regarding the function and implementation of each unit are presented in the next sections.

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{./figures/Overall_Architecture222}
\caption{The overall system architecture of the framework}
\label{fig:Arch}
\end{figure}
\FloatBarrier

\subsection{Space-time Twitter user trajectories}
To derive meaningful mobility patterns of individuals, a space-time trajectory of each individual user should be constructed~\citep{hagerstrand1985time}.
Each raw geo-located tweet contains multiple fields of information, such as the created time, country, language code, and location, etc. To construct a space-time trajectory from the data collection, we are interested in the following fields: \textit{User ID, location, timestamp}, which can be represented by a tuple $\left\langle id, loc, t\right\rangle$, where \textit{id} is a unique string representing a Twitter user's id; \textit{loc} is the recorded location of the message represented as a pair of coordinates $\left\langle latitude, longitude\right\rangle$;
and \textit{t} is the timestamp of when the message was posted; A Twitter user's space-time trajectory is defined as follows.
\newline

\noindent\emph{\textbf{Definition 1. Space-time Twitter user trajectory:}} The space-time trajectory of a Twitter user is defined as a collection of recorded geo-locations in the chronological order (i.e., based on the attached timestamp):
\newline

$Trajectory_{user_{id}} \equiv \lbrace \langle id, loc_{1}, t_{1}\rangle, \langle id, loc_{2}, t_{2}\rangle, \langle id, loc_{i}, t_{i}\rangle, ... \langle id, loc_{n}, t_{n}\rangle \rbrace, i = 1, 2, 3...n$
\newline

To remove non-human users based on unusual relocating speed, a user will be removed if the speed between any two consecutive locations in the user's trajectory with $speed$ $(loc_{i} - loc_{i-1}) > 240 m/s $.
\newline

\noindent\emph{\textbf{Definition 2. visitation behavior, displacement and radius of gyration:}} As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers the frequency of a user visiting different locations within a specific time frame.
This metric can provide an overall assessments regarding the diversity and similarity in the collective mobility pattern~\citep{gao2012exploring}.

In particular, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\citep{gonzalez2008understanding}.
The displacement refers to an individual's re-allocation in the geographical space measured in distance, i.e., $distance (loc_{i} - loc_{i-1})$. It is not equivalent to a ``trip" took by an individual, for example, even the time interval between two recorded locations is one month, it will still count as a displacement.  
By studying all the displacements from a group people, it helps to identify the distance bounds associated with different travel modes~\citep{Jurdak2015} or to determine whether movements are random walks~\citep{brockmann2006scaling}.
Radius of gyration is a metric to distinguish mobility patterns of individuals~\citep{gonzalez2008understanding}, which is defined as fellows.   
\newline

$r_{g} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(p_{i} -  p_{centroid})^{2}}$, where $p_{centroid} = \frac{1}{n}\sum_{i=1}^{n}p_{i}$
\newline

\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory. When applying the measurements to all the users, it helps to identify different groups of people and understand the corresponding mobility patterns. Note that both displacements and radius of gyrations are measured by ``crow's fly distance" in this study (i.e., the direct distance between two recorded locations).
Since all these metrics are based on the generated trajectories, by breaking and aggregating the trajectories in multiple spatial scales and temporal granularity, it would enable performing multi-level spatiotemporal analysis of these measurements and studying the corresponding mobility patterns.

\subsection{Multi-level spatiotemporal trajectory aggregation}
An important strategy for visual-analytics methods dealing with massive movement datasets is performing spatial aggregations to provide different levels-of-detail~\citep{andrienko2007designing,andrienko2007visual}.
It is similar to the map generation approach that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest~\citep{buttenfield1991map}.
To enable aggregating Twitter trajectories into multiple spatial levels, we have extended the hierarchical space-time cube model developed in~\citep{cao2014scalable}, where we partitioned the geographic space of the United States into 10 hierarchical spatial layers. 
To be specific, the state boundaries of the United States are treated as the base layer (i.e. level 0) for aggregating state-level Twitter user movements, Alaska and Hawaii are excluded for the consideration of better visualization effects in the mapping interface of the framework. We then created an hierarchical fishnet by diving the study region into regular cells, where the finest level (level 10) consists 1km $\times$ 1km cells. Such a cell size is consistent with the spatial resolution in landscan\footnote{http://web.ornl.gov/sci/landscan/} product for measuring the global population density. In our case, the cell size for level i-1 is twice of the size in level i. Figure 2 illustrates an hierarchical fishnet spatial units for mapping multi-level Twitter user movements. Note that any fine-grained geographic boundaries can be used and appended in this framework to show different level-of-detailed movements (e.g., county-level and census-tract level), in our case, we replaced the level 8 fishnet layer with the US county boundaries.

To perform a multi-level spatial aggregation of the Twitter user trajectories using hierarchical spatial layers, each location in a user's trajectory is redistributed to the corresponding spatial units. A MapReduce algorithm for the spatial aggregation is implemented, where the ID of unit in each spatial layer (e.g., polygon in state and country layer and cell in the rest) is treated as key in the at the map stage. It performs a ``point-in-polygon" process to determine which polygon the point belongs to. If the location does not belong to any polygon, it will be dropped, which is how we used the geographic boundaries of the United States to filer the raw tweet collection and keep the ``domestic" ones. To optimize the ``point-in-polygon" determination without comparing the location with every polygon in the spatial layer, we also created a Quad-Tree~\citep{samet1984quadtree} for each spatial layer to speed up the process. Finally, the reducers generate two data outputs: (1) reconstructed space-time Twitter user trajectories at each spatial level (2) movement flows in the form of in and out volumes among the units. The movement flows are stored in the database for interactive explorations in the web mapping interface, whereas the re-constructed trajectories can be further processed to produce distance measures at different spatial scales, which is illustrated as fellows:
\newline

\noindent $Trajectory_{user_{id}} \equiv \lbrace \langle id, loc_{1}, t_{1}, unit_{1}\rangle, \langle id, loc_{2}, t_{2}, unit_{2}\rangle, \langle id, loc_{i}, t_{i}, unit_{i}\rangle, ... \langle id, loc_{n}, t_{n}, unit_{n}\rangle \rbrace$
where $ i = 1, 2, 3...n$

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{./figures/multilevel}
\caption{Hierarchical spatial layers for aggregating movements in different level-of-details}
\label{fig:multilevel}
\end{figure}
\FloatBarrier

\section{Multi-scale spatiotemporal Twitter user mobility patterns}
%This section is divided into two parts. The first part presents a set of statistical analysis to explore Twitter user mobility patterns (e.g., movement flows, user visiting behavior, displacements and radius of gyrations) across multi-level spatial scales and temporal granularity in the United States during the year 2014, where all the measurements are enabled by the framework.  
%The second part presents the details of the interactive 3D virtual globe web mapping interface for exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements. 
%In particular, the interface provides capability to dynamically visualize the movements and summarize movement flows based on a given spatial scale and time range, which are specified by the users when they are interacting with the web interface.

\subsection{Twitter user population dynamics}
To investigate the overall geographical distribution of the Twitter population in our dataset, we have carried out analysis at both county and state level to test their correlations and stability regarding the census population estimates.
For this study, we have derived the census information of 48 states plus Washington, D.C., and 3108 counties of the United States (i.e., excluding Alaska and Hawaii) of year 2014 from the US census bureau\footnote{http://www.census.gov/}.
For every state and county, the framework summarizes the number of unique users in each unit for the year 2014 (as well as every month). 
The results of the correlations between the number of unique Twitter user and the census population estimates in each state is show in Figure 3. 
\newline

\begin{figure}[h]
\centering
\includegraphics[width=1\linewidth]{./figures/test}
\caption{The correlation between the number of unique Twitter user and the census population estimates in each state (a) based on year 2014 and (b) based on each month of year 2014}
\label{fig:Arch}
\end{figure}
\FloatBarrier

The results show that the number of unique Twitter users is well ($R^{2}=0.92$ and p-value $<$ 0.01) correlated with the state level census population estimates in year 2014 (Figure 3(a)) and it is consistent (with all $R^{2} > 0.95$ and p-value $<$ 0.01) in each month (Figure 3(b)).
However, such correlations are not significant at the county level. 
Interestingly, zero Twitter population were found in  4 (out of 3108) counties (i.e., Manassas Park city, Covington city, Cumberland county, Lipscomb county) throughout the year, which means no geo-located tweets were captured from those areas. 
It is not clear whether people in those 4 counties do not send geo-located tweets at all or the tweets were lost due to 1 \% policy mentioned in~\citep{hawelka2014geo} as both cases are unlikely. Nevertheless, this does show the limitation of directly using Twitter population as proxies of real population. 
In addition,  the dramatic difference between the correlations at state level and the county level could be useful for other researchers when studying population dynamics at a specific spatial scale.

\subsection{Spatiotemporal Twitter user mobility patterns}
The situation of using geo-located tweets to track people's movements is complex as users' tweeting behavior can be significantly different from one to another, in particular the frequency and time-interval between two consecutive tweets. For example, some people may tweet once a day while others do more; some people may tweet regularly while others do not.  
These tweeting behaviors are expected as such human dynamics are also seen in the mobile phone call data~\citep{gonzalez2008understanding}. 
Many studies have carried out data collection within a certain time period (e.g., a year in our case).
However, as the geo-located tweets were collected in a continuous fashion, we need to examine the sensitivities regarding these behaviors to make sure we are not just capturing a random snapshot from the whole data streams.

In this study, we have analyzed the cumulative distribution of the frequency Twitter users visiting different locations in year 2014 (and every month), which uses the methods developed in~\citep{clauset2009power}. 
The frequency is summarized based on the trajectories of individuals extracted in each time range. Note that different groups of Twitter user may exist in each month. 
It appears that the distribution of the collective Twitter user visitation behaviors in year 2014 follows a two-tiered power law distributions (shown in Figure 4), where the majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$ and the $\alpha$ value is 1.32, and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $p(x)\sim x^{-\alpha}$ with $\alpha$ value is 3.5.
This finding is consistent across all 12 months, with the mean $\alpha$ value as 1.34 $ \pm$  0.05 (standard deviation) and the mean $\lambda$ value as 0.00178 $ \pm$  0.0002 (standard deviation).

The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model~\citep{ reynolds2012truncated, rhee2011levy}, which has also been identified in many human mobility studies using different mobility data~\citep{zhao2015explaining}.
The similarities among the cumulative distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which indicates studies collected geo-located tweets in one month can potentially reveal similar findings as the ones collected in multiple months. 
Of course, different spatial scales can effect such findings as we learned that there were no geo-located tweets collected from 4 counties.
In addition, the two-tier power law also reveals the diversity in the Twitter user visiting behaviors: (1) a small group Twitter users visited significantly more locations than the rest (2) within each group, the probability of Twitter user visiting more locations decreases significantly with a power function.

\begin{figure}[h]
\centering
\includegraphics[width=1.0\linewidth]{./figures/visitation2}
\caption{Two-tier power law distribution of the collective Twitter user visitation behaviors}
\label{fig:Arch}
\end{figure}
\FloatBarrier

As it is mentioned earlier, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\citep{gonzalez2008understanding}. In this case, we first gathered the displacements from all the collected Twitter users in the United States (excluding Hawaii and Alaska) in year 2014, where those Twitter users with only one geo-located tweet were filtered out. 
In addition, to investigate the mobility patterns of individuals, we derived the accumulated displacements and the radius of gyrations of each individual Twitter user based on the corresponding space-time trajectories over the one year period.
Note that both displacements and radius of gyrations were measured by ``crow's fly distance", which is the direct distance ($d$) between two consecutively recorded locations in a user's trajectory.

To seek mobility patterns from these measurements, we performed statistical analysis regarding the probability distributions of displacements and radius of gyrations, which is also known as the spatial dispersal kernel $P(d)$~\citep{brockmann2006scaling}. The probability distribution of the user displacements (as well as accumulated displacements) is shown in Figure 5, whereas the probability distribution of radius of gyrations is shown in Figure 6. In this study, we used the fitting methods developed by~\citep{Jurdak2015}. The probability distributions of overall displacements, and the accumulated displacements and radius of gyrations of individuals, can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.

In particular, as it is shown in Figure 5 (a), the probability distributions of overall displacements is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10 m, 70m] (accounting for 2 $\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [100m, 80km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80km] (accounting for 5 $\%$ of the population). In additon, the displacement in the distance bound from 100m and 80km in Figure 5 (b) can be further approximately by two power-law distributions with a cutting point at 5km (53$\%$ distances are less than 5km and 40$\%$ distances between 5km and 80km), which indicates two different travel modes, such as inter- or intra-city movements.
Overall, the fitting functions with different distance bound suggest the existence of multi-scale or multi-modal mobility patterns ~\citep{Jurdak2015} of the Twitter users in the United States, for example the displacements larger than 80km could be related to inter-state travels or travel by flight.

The probability distribution of radius of gyrations of individuals (Figure 6 (a)) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10m$ from [10 m, 50m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50m, 30km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30km]. In particular, the radius of gyration between 50m and 30km can be further approximately by two power law distributions with a cutting point at 6km, which suggest two main types of spatial coverage of from the collected Twitter users in the United States. The distribution shows that around $10\%$ the tweet population has a radius of gyration less than 50 meters, which indicates those twitter users mostly tweet at a particular place, such as home or office;  around 60$\%$ of the population has a radius of gyration less than 30 km, which indicates that most of the collected Twitter user movements are ``short" distances, e.g., within a city locale. Note that the accuracy of these values for defining the distance bound depends on the accuracy of the location information of each geo-located tweet.

\begin{figure}[h]
\centering
\includegraphics[width=1.0\linewidth]{./figures/displacement}
\caption{(a) The probability distribution of the collective Twitter user displacements P(d) (b) the distance between [100m, 80km] is approximated by a double power-law functions (c) The probability distribution of the accumulated displacements of individual Twitter users P(d) (d) The probability distribution of the accumulated displacements of individual Twitter users in 3 different months}
\label{fig:Arch}
\end{figure}\textbf{}
\FloatBarrier

\begin{figure}[h]
\centering
\includegraphics[width=1.0\linewidth]{./figures/gyration}
\caption{ (a) The probability distribution of radius of gyration of individual Twitter users P($r_{g}$) (b) the distance between [50m, 30 km] is approximated by a double power-law functions}
\label{fig:Arch}
\end{figure}
\FloatBarrier

More importantly, as our framework can aggregate Twitter user trajectories within different temporal ranges, we further analyzed the probability distributions of accumulated displacements took places in January, June, and October (Figure 5 (d)) and radius of gyrations within 4 quarters in year 2014 (Figure 7), in order to examine whether there are temporal changes in the mobility patterns. While the probability distributions of accumulated displacements are almost identical in those selected three months,  we do find changes in the probability distributions of radius of gyrations in different quarters of the year. 
The fluctuations in the tails of the distributions indicate that long distance radius of gyrations (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern, which means the increase or decrease of long distance movement activities in the corresponding time period. 
However, it is worthy noting that the overall trends in the Twitter user mobility patterns revealed by radius of gyrations are still consistent.  In summary, by comparing these results with the same measurements in~\citep{Jurdak2015}, (slightly) different distance bounds were identified for describing the Twitter user mobility patterns in the USA and Australia, however the overall similarity and consistence found in using a combination of three functions to approximate the probability distribution functions of displacements and radius of gyrations, clearly provide supports for using geo-located tweets for conducting reproducible human mobility studies.

\begin{figure}[h]
\centering
\includegraphics[width=1.0\linewidth]{./figures/gyration_season}
\caption{The probability distribution of radius of gyration of individual Twitter users in different quarters of year 2014}
\label{fig:Arch}
\end{figure}
\FloatBarrier

The above analysis of Twitter user mobility patterns mainly focus on the temporal aspects where the spatial scale is fixed to the country level.
Our framework provides the flexibility to aggregate and extract Twitter user trajectories in a specific spatial scale and re-produce the analysis. 
In particular, as it is evident from the above analysis that there are multi-scale or multi-modal Twitter user mobility patterns, this framework can help further look into the mobility pattern regarding how Twitter users move across different spatial scales and temporal ranges, which is measured by the movement flows among these spatial regions.  In this case, we demonstrate the inter-state mobility patterns by using the framework to capture the movement flows among the states. Note that the movement flows can be summarized across all the 10 spatial layers in the framework. 
In particular, the movement flows in the state level are summarized and visualized with chord diagrams (illustrated in Figure 10) as part of the interactive mapping interface.
We tested the overall distribution of the movement flows (in the form of weighted in-degree and out-degree of a graph, where each state is treated as a node) among different states in year 2014.  
We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states. It also indicates that although the Twitter population seems to be linearly correlated with the population at state level, it is not proportional to account the movement flux among the states, which may provide some insights for other researchers in studying social-economical aspects of the migration dynamics.

\begin{figure}[h]
\centering
\includegraphics[width=0.8\linewidth]{./figures/degree}
\caption{The distribution of Twitter user movement flows among different states in year 2014 measured in weighted in- and out-degrees}
\label{fig:Arch}
\end{figure}
\FloatBarrier

%\subsection{The interactive 3D virtual globe web mapping interface}
%In addition to providing supports for understanding Twitter user mobility patterns with statistical analysis, our framework integrates a 3D virtual globe web mapping interface to enable users to perform exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements. 
%The 3D virtual globe is developed and extended from the Cesium library\footnote{http://cesiumjs.org/}, which is an open-source WebGL virtual globe and map engine. 
%We customized the map engine to adapt different spatial scales, which correspond to the hierarchical spatial layers,  for aggregating movements in different level-of-details.
%The map interface interprets user's interactions, such as area-of-interest, time window, and zoom levels, etc. as parameters and send to the dedicated visualization servlet on the CyberGIS Gateway\footnote{http://sandbox.cigi.illinois.edu/home/}, which is the leading online cyberGIS environment for a large number of users to perform computing- and data-intensive, and collaborative geospatial problem-solving enabled by advanced cyberinfrastructure~\citep{liu2014cybergis}.
%In return, the map interface visualizes the corresponding movement flows on the virtual globe.
%
%An overview of the web mapping interface is shown in Figure 9. In terms of performing exploratory visual-analytics of Twitter user movement patterns, users can specify the time window to enable the query. 
%When the results are shown, users can hover the mouse over each individual lines on the map to see the value of movement flows for both in and out directions. If the selected criteria keep unchanged, whenever the user zooms in/out, tilt or rotate the globe, the mapping interface will automatically provide the corresponding level-of-details on the fly.
%
%\begin{figure}[h]
%\centering
%\includegraphics[width=0.8\linewidth]{./figures/vocation}
%\caption{An overview of the 3D interactive web mapping interface}
%\label{fig:Web_Interface}
%\end{figure}
%%\FloatBarrier

For state level Twitter user movements, we provide an interactive chord diagram to explicitly illustrate the movement flows among different states (Figure 9). Figure 9 demonstrates the Twitter movement flows among different states in January, 2014. The size of each color patch is proportional to the volume of total incoming movements from other states, which allow us to visually identify those states that dominate the incoming movement flows and which states the flows are generated from.
By interacting with the state names, it will highlight the details of incoming movement flows from other states, in this case California is selected, which has the largest incoming movement flows in January.\newline

\begin{figure}[h]
\centering
\includegraphics[width=0.9\linewidth]{./figures/vaca_flow}
\caption{Chord diagrams for the movement flows among different states in January, 2014}
\label{fig:vaca_movement}
\end{figure}
\FloatBarrier

%%\begin{figure}[h]
%%\centering
%%\includegraphics[width=0.7\linewidth]{./figures/vaca_globe}
%%\caption{3D extruded polygons with heights proportional to the volume of incoming Twitter user movements in each state }
%%\label{fig:vaca_movement}
%%\end{figure}
%%\FloatBarrier

\section{Conclusions and Discussions}
In this study, we have used large volume of geo-located tweets to study Twitter user mobility patterns across multi-level spatial scales and temporal granularity in the United States during the year 2014. 
To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
This framework is implemented based on high-performance distributed computing environment using Apache Hadoop.
It delivers scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.

With this framework, we have found some interesting Twitter user mobility patterns, both statically and visually.
We first examined the Twitter population by exploring the correlations between the number of unique users and the census population estimates at both state and county level (excluding Hawaii and Alaska). 
Although these two correlate well at the state level, there is no significance at the county level. 
Interestingly, no geo-located Twitter messages were found in 4 (out of 3108) counties (i.e., Manassas Park city, Covington city, Cumberland county, Lipscomb county) throughout the year.
We then studied the collective Twitter user visiting behavior regarding the frequency of Twitter users visiting different locations, which was fitted by a two-tier power-law distribution function.
The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model, which has also been identified in many human mobility studies using different mobility data.
The similarities among the cumulative distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which provides supports that we are not just capturing a random snapshot of the whole data stream.

We studied the distance decay effects in the collective Twitter user movements measured by the probability distributions of the displacements and radius of gyrations of individuals. 
These distributions can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function. In particular, distance bounds between different fitting functions in displacement distribution reveals the existence of multi-scale or multi-modal mobility patterns of the Twitter users in the United States, whereas the distribution of radius of gyration reveals different groups of Tweet users with different types of spatial coverages.   
More importantly, we further studied these mobility patterns in different temporal scales to investigate the temporal changes in the mobility patterns. 
We found that the accumulated displacements are almost identical in different months, while the long distance radius of gyration (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern.
In particular, by comparing the mobility patterns revealed by displacements and radius of gyrations of Twitter users in the United States and Australia, there are slightly difference regarding the exact value of distance bounds between different fitting functions. 
However, the fact that these measurements are of people (i.e., Twitter users) in different countries (in this case, continent) and their probability distributions can all be approximated by a combination of three functions, has clearly show the values in using geo-located tweets for conducting reproducible human mobility studies.

%\section*{Acknowledgements}
%Removed for review process.
\cleardoublepage
%\bibliographystyle{apacitex}

\bibliographystyle{apalike}
\bibliography{Ref}

\end{document}

### 2016-05-08 MovePattern_revision/Twitter_MovementPatterns_VisualAnalytics.tex
home

@@
 One significant advantage of LBSM data streams is the large spatial coverage, for example, researchers have used geo-located Twitter data for studying global mobility patterns~\citep{hawelka2014geo}, which is otherwise impossible by using other mobility datasets (e.g., GPS traces and mobile phone call records).
-In addition, the publicly available LBSM data streams offer unique opportunities for conducting reproducible scientific findings regarding the concerns of infringement on individual privacy, such as using mobile phone call records~\citep{giannotti2008mobility,crampton2014collect,Jurdak2015}.
+In addition, the publicly available LBSM data streams offer unique opportunities for conducting replicable scientific findings regarding the concerns of infringement on individual privacy, such as using mobile phone call records~\citep{giannotti2008mobility,crampton2014collect,Jurdak2015}.
 
@@
 Such a dataset can cover relatively large spatial scale (e.g., country level)~\citep{becker2013human,sobolevsky2013delineating} and a large portion of the population in the study region~\citep{kung2014exploring}.
-However, due to the concerns of infringement on individual privacy, the mobile phone call data is not publicly accessible, which is not ideal  for conducting reproducible scientific findings, such as validating or extending the existing discoveries.
+However, due to the concerns of infringement on individual privacy, the mobile phone call data is not publicly accessible, which is not ideal  for conducting replicable scientific findings, such as validating or extending the existing discoveries.
 
@@
 However, it is worthy noting that the overall trends in the Twitter user mobility patterns revealed by radius of gyrations are still consistent.
-In summary, by comparing these results with the same measurements in~\citep{Jurdak2015}, (slightly) different distance bounds were identified for describing the Twitter user mobility patterns in the USA and Australia, however the overall similarity and consistence found in using a combination of three functions to approximate the probability distribution functions of displacements and radius of gyrations, clearly provide supports for using geo-located tweets for conducting reproducible human mobility studies.
+In summary, by comparing these results with the same measurements in~\citep{Jurdak2015}, (slightly) different distance bounds were identified for describing the Twitter user mobility patterns in the USA and Australia, however the overall similarity and consistence found in using a combination of three functions to approximate the probability distribution functions of displacements and radius of gyrations, clearly provide supports for using geo-located tweets for conducting replicable human mobility studies.
 
@@
 In particular, by comparing the mobility patterns revealed by displacements and radius of gyrations of Twitter users in the United States and Australia, there are slightly difference regarding the exact value of distance bounds between different fitting functions.
-However, the fact that these measurements are of people (i.e., Twitter users) in different countries (in this case, continent) and their probability distributions can all be approximated by a combination of three functions, has clearly show the values in using geo-located tweets for conducting reproducible human mobility studies.
+However, the fact that these measurements are of people (i.e., Twitter users) in different countries (in this case, continent) and their probability distributions can all be approximated by a combination of three functions, has clearly show the values in using geo-located tweets for conducting replicable human mobility studies.
 

### 2016-05-11 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
edits
new

@@
 Specifically, we delineated the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million Twitter messages.
+We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
+
 Our study connects human mobility research with the delineation of non-administrative anthropographic urban boundaries based on Twitter user spatial interactions, which provides a new understanding of the interactions between human activity and urban space.
-We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
+
 The result of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas that provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
@@
 
-In this study, we describe a novel approach to delineating urban boundaries based on the actual movements (i.e., the reallocation in space) of 
-Twitter users extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
+Talk about spatial proximity
+
+In this study, we describe a novel approach to delineating urban boundaries based on the actual movements of Twitter users (i.e., the reallocation in space) extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
 Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the country level)~\citep{hawelka,jurdak2015}.
@@
 The map equation algorithm was selected to avoid the inherent resolution problem~\citep{fortunato2007} of the common modularity maximization method~\citep{newman2006}.
+
+While the
+
 We found that the collective mobility patterns of Twitter users in Great Britain are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points.
@@
 \section{Background and Related Work}
+
+Due to rapid urbanization, modern urban environments are evolving with dynamic forms and complex structures.
+
+\subsection{Potential limitation of }
+
+mainly about the intensity of human interactions across the geographical regions, however,
 
@@
 \begin{center}
-\includegraphics[width=0.8\linewidth]{./figure/uk}
-\caption{{\bf The spatial coverage of collected geo-located Twitter messages in Great Britain.} Each point corresponds to a geo-located tweet collected for this study.
+\includegraphics[width=1.0\linewidth]{./figure/uk}
+\caption{{\bf The spatial coverage of collected geo-located Twitter messages in Great Britain (left) and London (right).} Each point corresponds to a geo-located tweet collected for this study.
 Twitter activity is most apparent in urban areas.}
@@
 We examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold.
+
+That is that the time interval between a user's first and last recorded
+
+ agglomeration
 

### 2016-05-30 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
xx
new content

@@
 
-\title{{\itshape The geography of urban boundaries in Great Britain from the network of Twitter user spatial interactions} }
+\title{{\itshape The geography of urban boundaries in Great Britain from the mobility network of Twitter user spatial interactions} }
 \maketitle
@@
 Finally, we used the geographical boundary of Great Britain, which is derived from Office for National Statistics (ONS) of UK ({\tt{http://www.ons.gov.uk/ons}}), to further restrict the remaining tweets to be ``domestic".
-Based on these restrictions, the filtered dataset for the following study contains 69,847,497 tweets made by 1,153,891 twitter users.
+Based on these restrictions, the filtered dataset for the following study contains 69,847,497 tweets made by 1,153,891 Twitter users.
 

### 2016-06-05 backups/MovePattern_revision_06_02_2016/Twitter_MovementPatterns_VisualAnalytics.tex
backup

--- 2016-05-08 MovePattern_revision/Twitter_MovementPatterns_VisualAnalytics.tex
@@
 \noindent\textbf{Keywords:} Geo-located tweets, mobility patterns, multi-scale spatiotemporal analysis, scalable visual-analytics framework\\
-
-Notes: What about randomly choose several states and perform the analysis
 \cleardoublepage
@@
 While such an approach enables visualization of detailed trajectories, its capability is limited in dealing with large-volume movement datasets~\citep{andrienko2007designing}.
-For example, a visual clutter problem is likely to occur when visualizing massive amount of user trajectories, which makes it difficult for capture meaningful mobility patterns.
-
 Instead of directly visualizing individual user trajectories, a space-time cube approach was proposed in analyzing and visualizing the collective trajectories by providing flexibilities in setting up both spatial and temporal ranges, and therefore to study the mobility patterns across different spatial units (e.g.
@@
 
-%\subsection{Accommodating LBSM Big Data with Hadoop}
-%Apache Hadoop is an open source software framework designed to facilitate data intensive computing on large commodity clusters.
-%It combines a distributed file system, namely Hadoop Distributed File System(HDFS)~\citep{shvachko2010hadoop} with MapReduce programming paradigm, which can be applied to wide range of data-intensive problems.
-%MapReduce is a programming model and an associated software framework designed to process massive data in a distributed fashion~\citep{dean2008mapreduce}.
-%MapReduce breaks the entire computation into small tasks and schedule them among different computing nodes.
-%MapReduce consists of two main stages: map and reduce.
-%In the map stage, input data is converted into series of intermediate $\langle key, value\rangle$ pairs.
-%Customized computation will be performed in the reduce stage based on the same intermediate key.
-%This framework provides parallelization since both map and reduce tasks are considered independent and can be done in parallel.
+\subsection{Accommodating LBSM Big Data with Hadoop}
+Apache Hadoop is an open source software framework designed to facilitate data intensive computing on large commodity clusters.
+It combines a distributed file system, namely Hadoop Distributed File System(HDFS)~\citep{shvachko2010hadoop} with MapReduce programming paradigm, which can be applied to wide range of data-intensive problems.
+MapReduce is a programming model and an associated software framework designed to process massive data in a distributed fashion~\citep{dean2008mapreduce}.
+MapReduce breaks the entire computation into small tasks and schedule them among different computing nodes.
+MapReduce consists of two main stages: map and reduce.
+In the map stage, input data is converted into series of intermediate $\langle key, value\rangle$ pairs.
+Customized computation will be performed in the reduce stage based on the same intermediate key.
+This framework provides parallelization since both map and reduce tasks are considered independent and can be done in parallel.
 More importantly, it provides scalability in relation to the growth of data size, where Hadoop can scale to more computing nodes in the cluster to maintain the performance.
-%
-%Our framework benefits from using Hadoop in both data management and processing.
-%First, since the input data is large it is desirable to store it on multiple machines.
-%Second, by using Hadoop we can parallelize the computational tasks and make the data processing faster and more efficient.
-%Further, by adopting the MapReduce computing paradigm, we can model each individual user's trajectory by treating user's unique ID as key, and summarize the movement flows among different spatial units by utilizing the ID of the spatial unit as key.
+
+Our framework benefits from using Hadoop in both data management and processing.
+First, since the input data is large it is desirable to store it on multiple machines.
+Second, by using Hadoop we can parallelize the computational tasks and make the data processing faster and more efficient.
+Further, by adopting the MapReduce computing paradigm, we can model each individual user's trajectory by treating user's unique ID as key, and summarize the movement flows among different spatial units by utilizing the ID of the spatial unit as key.
 The details will be introduced in the following section.
@@
 
-\subsection{Twitter user population dynamics}
+\subsection{An overview of the Twitter user population}
 To investigate the overall geographical distribution of the Twitter population in our dataset, we have carried out analysis at both county and state level to test their correlations and stability regarding the census population estimates.
@@
 \centering
-\includegraphics[width=0.9\linewidth]{./figures/vaca_flow}
+\includegraphics[width=1.0\linewidth]{./figures/vaca_flow}
 \caption{Chord diagrams for the movement flows among different states in January, 2014}

### 2016-06-05 MovePattern_CAGIS/Twitter_MovementPatterns_VisualAnalytics.tex
revision

--- 2016-05-08 MovePattern_revision/Twitter_MovementPatterns_VisualAnalytics.tex
@@
 %\input{./Title.tex}
-%\title{\itshape Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
-\title{\itshape Exploring Multi-scale Spatiotemporal Twitter User Mobility Patterns Using Geo-located Twitter Data}
+\title{\itshape Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
+%\title{\itshape Exploring Multi-scale Spatiotemporal Twitter User Mobility Patterns Using Geo-located Twitter Data}
 	\author{}
 %	\author[1, 2, 3]{Junjun Yin}	
-%	\author[1, 2, 3, 4]{Shaowen Wang}	
-%%	\author[1, 2, 3, 4, \footnote{Corresponding author: shaowen@illinois.edu}]{Shaowen Wang}
-%	
 %	\affil[1]{
@@
 %	{
-%	\it	Department of Geography and Geographic Information Science
-%	}
-%	\affil[4]
-%	{
-%	\it	National Center for Supercomputing Applications \authorcr
+%	\it	Department of Geography and Geographic Information Science\authorcr
 %		\it	University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA
@@
 We have performed a set of statistical analysis to understand Twitter user mobility patterns across multi-level spatial scales and temporal granularity.
-In particular, the Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns.
+In particular, the Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals have revealed multi-scale or multi-modal Twitter user mobility patterns.
 By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
@@
 spatiotemporal analysis with massive movement datasets, including data management, multi-level spatiotemporal user trajectory modeling and visualization.
-In particular, we look into high performance distributed computing approach for addressing such challenges.
 Section 3 details the processes for extracting, aggregating and summarizing multi-level spatiotemporal Twitter user mobility patterns.
@@
 Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\citep{andrienko2007designing}.
-Also, it is useful to group the subsets of user trajectories based on the shared characteristics for smooth transformations of space and time.
-For example, a network approach was used to summarize the actual movements in Twitter user trajectories as movement flows among different countries~\citep{hawelka2014geo}.
 
@@
 In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
-In our case, to ensure the complete coverage over the United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: -167.276413, longitude: 5.499550) and upper right (latitude: -52.233040, longitude: 83.162102).
+In our case, to ensure the complete coverage over the United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
 The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2GB in size) collected per day.
@@
 
-\subsection{Twitter user population dynamics}
-To investigate the overall geographical distribution of the Twitter population in our dataset, we have carried out analysis at both county and state level to test their correlations and stability regarding the census population estimates.
-For this study, we have derived the census information of 48 states plus Washington, D.C., and 3108 counties of the United States (i.e., excluding Alaska and Hawaii) of year 2014 from the US census bureau\footnote{http://www.census.gov/}.
-For every state and county, the framework summarizes the number of unique users in each unit for the year 2014 (as well as every month). 
-The results of the correlations between the number of unique Twitter user and the census population estimates in each state is show in Figure 3. 
-\newline
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=1\linewidth]{./figures/test}
-\caption{The correlation between the number of unique Twitter user and the census population estimates in each state (a) based on year 2014 and (b) based on each month of year 2014}
-\label{fig:Arch}
-\end{figure}
-\FloatBarrier
-
-The results show that the number of unique Twitter users is well ($R^{2}=0.92$ and p-value $<$ 0.01) correlated with the state level census population estimates in year 2014 (Figure 3(a)) and it is consistent (with all $R^{2} > 0.95$ and p-value $<$ 0.01) in each month (Figure 3(b)).
-However, such correlations are not significant at the county level. 
-Interestingly, zero Twitter population were found in  4 (out of 3108) counties (i.e., Manassas Park city, Covington city, Cumberland county, Lipscomb county) throughout the year, which means no geo-located tweets were captured from those areas.
-It is not clear whether people in those 4 counties do not send geo-located tweets at all or the tweets were lost due to 1 \% policy mentioned in~\citep{hawelka2014geo} as both cases are unlikely.
+%\subsection{An overview of the Twitter user population}
+%To investigate the overall geographical distribution of the Twitter population in our dataset, we have carried out analysis at both county and state level to test their correlations and stability regarding the census population estimates.
+%For this study, we have derived the census information of 48 states plus Washington, D.C., and 3108 counties of the United States (i.e., excluding Alaska and Hawaii) of year 2014 from the US census bureau\footnote{http://www.census.gov/}.
+%For every state and county, the framework summarizes the number of unique users in each unit for the year 2014 (as well as every month). 
+%The results of the correlations between the number of unique Twitter user and the census population estimates in each state is show in Figure 3. 
+%\newline
+%
+%
+%\begin{figure}[h]
+%\centering
+%\includegraphics[width=1\linewidth]{./figures/test}
+%\caption{The correlation between the number of unique Twitter user and the census population estimates in each state (a) based on year 2014 and (b) based on each month of year 2014}
+%\label{fig:Arch}
+%\end{figure}
+%\FloatBarrier
+%
+%The results show that the number of unique Twitter users is well ($R^{2}=0.92$ and p-value $<$ 0.01) correlated with the state level census population estimates in year 2014 (Figure 3(a)) and it is consistent (with all $R^{2} > 0.95$ and p-value $<$ 0.01) in each month (Figure 3(b)).
+%However, such correlations are not significant at the county level. 
+%Interestingly, zero Twitter population were found in  4 (out of 3108) counties (i.e., Manassas Park city, Covington city, Cumberland county, Lipscomb county) throughout the year, which means no geo-located tweets were captured from those areas.
+%It is not clear whether people in those 4 counties do not send geo-located tweets at all or the tweets were lost due to 1 \% policy mentioned in~\citep{hawelka2014geo} as both cases are unlikely.
 Nevertheless, this does show the limitation of directly using Twitter population as proxies of real population.
-In addition,  the dramatic difference between the correlations at state level and the county level could be useful for other researchers when studying population dynamics at a specific spatial scale.
+%In addition,  the dramatic difference between the correlations at state level and the county level could be useful for other researchers when studying population dynamics at a specific spatial scale.
 
@@
 
-%\subsection{The interactive 3D virtual globe web mapping interface}
-%In addition to providing supports for understanding Twitter user mobility patterns with statistical analysis, our framework integrates a 3D virtual globe web mapping interface to enable users to perform exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements.
-%The 3D virtual globe is developed and extended from the Cesium library\footnote{http://cesiumjs.org/}, which is an open-source WebGL virtual globe and map engine. 
-%We customized the map engine to adapt different spatial scales, which correspond to the hierarchical spatial layers,  for aggregating movements in different level-of-details.
-%The map interface interprets user's interactions, such as area-of-interest, time window, and zoom levels, etc.
+\subsection{The interactive 3D virtual globe web mapping interface}
+In addition to providing supports for understanding Twitter user mobility patterns with statistical analysis, the framework integrates a 3D virtual globe interface to enable users to perform exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements.
+The 3D virtual globe is developed and extended from the Cesium library\footnote{http://cesiumjs.org/}, which is an open-source WebGL virtual globe and map engine. 
+We customized the map engine to adapt different spatial scales, which correspond to the hierarchical spatial layers,  for aggregating movements in different level-of-details.
+The map interface interprets user's interactions, such as area-of-interest, time window, and zoom levels, etc.
 as parameters and send to the dedicated visualization servlet on the CyberGIS Gateway\footnote{http://sandbox.cigi.illinois.edu/home/}, which is the leading online cyberGIS environment for a large number of users to perform computing- and data-intensive, and collaborative geospatial problem-solving enabled by advanced cyberinfrastructure~\citep{liu2014cybergis}.
-%In return, the map interface visualizes the corresponding movement flows on the virtual globe.
-%
-%An overview of the web mapping interface is shown in Figure 9.
+In return, the map interface visualizes the corresponding movement flows on the virtual globe.
+
+An overview of the web mapping interface is shown in Figure 9.
 In terms of performing exploratory visual-analytics of Twitter user movement patterns, users can specify the time window to enable the query.
-%When the results are shown, users can hover the mouse over each individual lines on the map to see the value of movement flows for both in and out directions.
+When the results are shown, users can hover the mouse over each individual lines on the map to see the value of movement flows for both in and out directions.
 If the selected criteria keep unchanged, whenever the user zooms in/out, tilt or rotate the globe, the mapping interface will automatically provide the corresponding level-of-details on the fly.
-%
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=0.8\linewidth]{./figures/vocation}
-%\caption{An overview of the 3D interactive web mapping interface}
-%\label{fig:Web_Interface}
-%\end{figure}
-%%\FloatBarrier
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.8\linewidth]{./figures/vocation}
+\caption{An overview of the 3D interactive web mapping interface}
+\label{fig:Web_Interface}
+\end{figure}
+%\FloatBarrier
 
@@
 
-\section{Conclusions and Discussions}
+\section{Conclusions}
 In this study, we have used large volume of geo-located tweets to study Twitter user mobility patterns across multi-level spatial scales and temporal granularity in the United States during the year 2014.
@@
 With this framework, we have found some interesting Twitter user mobility patterns, both statically and visually.
-We first examined the Twitter population by exploring the correlations between the number of unique users and the census population estimates at both state and county level (excluding Hawaii and Alaska).
-Although these two correlate well at the state level, there is no significance at the county level. 
-Interestingly, no geo-located Twitter messages were found in 4 (out of 3108) counties (i.e., Manassas Park city, Covington city, Cumberland county, Lipscomb county) throughout the year.
-We then studied the collective Twitter user visiting behavior regarding the frequency of Twitter users visiting different locations, which was fitted by a two-tier power-law distribution function.
+We studied the collective Twitter user visiting behavior regarding the frequency of Twitter users visiting different locations, which was fitted by a two-tier power-law distribution function.
 The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model, which has also been identified in many human mobility studies using different mobility data.
@@
 We found that the accumulated displacements are almost identical in different months, while the long distance radius of gyration (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern.
-In particular, by comparing the mobility patterns revealed by displacements and radius of gyrations of Twitter users in the United States and Australia, there are slightly difference regarding the exact value of distance bounds between different fitting functions.
-However, the fact that these measurements are of people (i.e., Twitter users) in different countries (in this case, continent) and their probability distributions can all be approximated by a combination of three functions, has clearly show the values in using geo-located tweets for conducting replicable human mobility studies.
 

### 2016-06-05 backups/MovePattern_revision/Twitter_MovementPatterns_VisualAnalytics.tex
revision

--- 2016-06-05 MovePattern_CAGIS/Twitter_MovementPatterns_VisualAnalytics.tex
@@
 %	\author[1, 2, 3]{Junjun Yin}
+%	\author[1, 2, 3, 4]{Shaowen Wang}	
+%%	\author[1, 2, 3, 4, \footnote{Corresponding author: shaowen@illinois.edu}]{Shaowen Wang}
+%	
 %	\affil[1]{
@@
 %	{
-%	\it	Department of Geography and Geographic Information Science\authorcr
+%	\it	Department of Geography and Geographic Information Science
+%	}
+%	\affil[4]
+%	{
+%	\it	National Center for Supercomputing Applications \authorcr
 %	\it	University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA
@@
 In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
-In our case, to ensure the complete coverage over the United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
+In our case, to ensure the complete coverage over the United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: -167.276413, longitude: 5.499550) and upper right (latitude: -52.233040, longitude: 83.162102).
 The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2GB in size) collected per day.

### 2016-06-06 MovePattern_CAGIS/Twitter_MovementPatterns_VisualAnalytics.tex
editor comments

@@
 Mobility data is essentially a collection of spatiotemporal records of people moving from one location to another in the geographic space.
-To study mobility patterns of individuals, a space-time trajectory~\citep{hagerstrand1985time} of each individual should be modeled and constructed to quantify the collective movements over space and time.
+To study mobility patterns of individuals, a space-time trajectory of each individual should be modeled and constructed to quantify the collective movements over space and time.
 Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of displacements and radius of gyrations of individuals, to study the mobility dynamics.
@@
 In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
-In our case, to ensure the complete coverage over the United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
+To ensure complete coverage over the United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
 The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2GB in size) collected per day.
@@
 In this case, we adopted the speed limit value as 240 m/s used in (Jurdak et al., 2015), where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
+Note that the original location information embedded in each geo-located tweet is given in units of latitude and longitude.
+To reduce the complexity in calculating distances and performing spatial aggregations directly based on geographical coordinates, we projected the all the points using North America Albers Equal Area Conic (ESRI:102008) coordinate system.
 Finally, we used the geographic boundaries of the United States\footnote{https://www.census.gov/geo/maps-data/data/} (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section.
@@
 Each raw geo-located tweet contains multiple fields of information, such as the created time, country, language code, and location, etc.
-To construct a space-time trajectory from the data collection, we are interested in the following fields: \textit{User ID, location, timestamp}, which can be represented by a tuple $\left\langle id, loc, t\right\rangle$, where \textit{id} is a unique string representing a Twitter user's id; \textit{loc} is the recorded location of the message represented as a pair of coordinates $\left\langle latitude, longitude\right\rangle$;
+To construct a space-time trajectory from the data collection, we are interested in the following fields: \textit{User ID, location, timestamp}, which can be represented by a tuple $\left\langle id, loc, t\right\rangle$, where \textit{id} is a unique string representing a Twitter user's id; \textit{loc} is the recorded location of the message represented as a pair of projected coordinates $\left\langle x, y\right\rangle$;
 and \textit{t} is the timestamp of when the message was posted; A Twitter user's space-time trajectory is defined as follows.
@@
 \section{Multi-scale spatiotemporal Twitter user mobility patterns}
-%This section is divided into two parts.
-The first part presents a set of statistical analysis to explore Twitter user mobility patterns (e.g., movement flows, user visiting behavior, displacements and radius of gyrations) across multi-level spatial scales and temporal granularity in the United States during the year 2014, where all the measurements are enabled by the framework.
-%The second part presents the details of the interactive 3D virtual globe web mapping interface for exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements. 
-%In particular, the interface provides capability to dynamically visualize the movements and summarize movement flows based on a given spatial scale and time range, which are specified by the users when they are interacting with the web interface.
-
-%\subsection{An overview of the Twitter user population}
-%To investigate the overall geographical distribution of the Twitter population in our dataset, we have carried out analysis at both county and state level to test their correlations and stability regarding the census population estimates.
-%For this study, we have derived the census information of 48 states plus Washington, D.C., and 3108 counties of the United States (i.e., excluding Alaska and Hawaii) of year 2014 from the US census bureau\footnote{http://www.census.gov/}.
-%For every state and county, the framework summarizes the number of unique users in each unit for the year 2014 (as well as every month). 
-%The results of the correlations between the number of unique Twitter user and the census population estimates in each state is show in Figure 3. 
-%\newline
-%
-%
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=1\linewidth]{./figures/test}
-%\caption{The correlation between the number of unique Twitter user and the census population estimates in each state (a) based on year 2014 and (b) based on each month of year 2014}
-%\label{fig:Arch}
-%\end{figure}
-%\FloatBarrier
-%
-%The results show that the number of unique Twitter users is well ($R^{2}=0.92$ and p-value $<$ 0.01) correlated with the state level census population estimates in year 2014 (Figure 3(a)) and it is consistent (with all $R^{2} > 0.95$ and p-value $<$ 0.01) in each month (Figure 3(b)).
-%However, such correlations are not significant at the county level. 
-%Interestingly, zero Twitter population were found in  4 (out of 3108) counties (i.e., Manassas Park city, Covington city, Cumberland county, Lipscomb county) throughout the year, which means no geo-located tweets were captured from those areas.
-%It is not clear whether people in those 4 counties do not send geo-located tweets at all or the tweets were lost due to 1 \% policy mentioned in~\citep{hawelka2014geo} as both cases are unlikely.
-Nevertheless, this does show the limitation of directly using Twitter population as proxies of real population.
-%In addition,  the dramatic difference between the correlations at state level and the county level could be useful for other researchers when studying population dynamics at a specific spatial scale.
-
 \subsection{Spatiotemporal Twitter user mobility patterns}
@@
 
-An overview of the web mapping interface is shown in Figure 9.
+An overview of the web mapping interface is shown in Figure 8.
 In terms of performing exploratory visual-analytics of Twitter user movement patterns, users can specify the time window to enable the query.
@@
 \FloatBarrier
-
-%%\begin{figure}[h]
-%%\centering
-%%\includegraphics[width=0.7\linewidth]{./figures/vaca_globe}
-%%\caption{3D extruded polygons with heights proportional to the volume of incoming Twitter user movements in each state }
-%%\label{fig:vaca_movement}
-%%\end{figure}
-%%\FloatBarrier
 

### 2016-06-09 Mobility_Pattern_Twitter_Landuse/main.tex
jia you!!!

\documentclass[fleqn,10pt]{wlscirep}
\title{Scientific Reports Title to see here (20 words or less)}

\author[1,*]{Junjun Yin}
\author[1]{xx}
%\author[1,2,+]{Christine Author}
%\author[2,+]{Derek Author}
\affil[1]{CyberGIS Center for Advanced Digital and Spatial Studies}
\affil[ ]{Department of Geography and Geographic Information Science}
\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}

\affil[*]{jyn@illinois.edu}

%\affil[+]{these authors contributed equally to this work}

%\keywords{Keyword1, Keyword2, Keyword3}

\begin{abstract}
Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. 
\end{abstract}
\begin{document}

\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
\thispagestyle{empty}

\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.

\section*{Introduction}

The Introduction section, of referenced text\cite{Figueredo:2009dg} expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.

\section*{Results}

\begin{figure}[ht]

\centering
\includegraphics[width=\linewidth]{Chicago_Shape}
\caption{Legend (350 words max). Example legend text.}
\label{fig:Chicago_Shape}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{gyration_chicago}
\caption{Legend (350 words max). Example legend text.}
\label{fig:gyration_chicago}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{firsttime}
\caption{Legend (350 words max). Example legend text.}
\label{fig:firsttime}
\end{figure}

\subsection*{Subsection}

Example text under a subsection. Bulleted lists may be used where appropriate, e.g.

\begin{itemize}
\item First item
\item Second item
\end{itemize}

\subsubsection*{Third-level section}

Topical subheadings are allowed.

\section*{Discussion}

The Discussion should be succinct and must not contain subheadings.

\section*{Methods}

Topical subheadings are allowed. Authors must ensure that their Methods section includes adequate experimental and characterization data necessary for others in the field to reproduce their work.

\bibliography{sample}

\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu. Use the cite command for an inline citation, e.g.  \cite{Figueredo:2009dg}.

\section*{Acknowledgements (not compulsory)}

Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.

\section*{Author contributions statement}

Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript.

\section*{Additional information}

To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing financial interests} (mandatory statement).

The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing financial interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
Condition & n & p \\
\hline
A & 5 & 0.1 \\
\hline
B & 10 & 0.01 \\
\hline
\end{tabular}
\caption{\label{tab:example}Legend (350 words max). Example legend text.}
\end{table}

Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.

\end{document}

### 2016-06-15 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
notes

@@
 
-\title{{\itshape The geography of urban boundaries in Great Britain from the mobility network of Twitter user spatial interactions} }
+%\title{{\itshape The geography of urban boundaries in Great Britain from the mobility network of Twitter user spatial interactions} }
+%\title{{\itshape Depict the geography of urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data} }
+\title{{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data} }
 \maketitle
@@
 \begin{abstract}
+Talk about distance-decay effects in human mobility patterns,
+
 Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns.
@@
 \section{Background and Related Work}
+Distance decay effects
+where a city boundary ends and another city boundary emerges.
+Spatial Distribution of City Tweets and Their Densities
 

### 2016-06-21 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
dinner

@@
 \begin{abstract}
-Talk about distance-decay effects in human mobility patterns,
-
 Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns.
@@
 We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
-
-Our study connects human mobility research with the delineation of non-administrative anthropographic urban boundaries based on Twitter user spatial interactions, which provides a new understanding of the interactions between human activity and urban space.
-
 The result of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas that provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
@@
 While our results corresponded well to the administrative boundaries, many unexpected and interesting boundaries were identified.
+
+Our study connects human mobility research with the delineation of non-administrative anthropographic urban boundaries based on Twitter user spatial interactions, which provides a new understanding of the interactions between human activity and urban space.
 \newline
@@
 
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=0.8\linewidth]{./figure/Gravity}
+\caption{{\bf The observed interaction strength versus the estimated ones from the adopted gravity model with $\bf{\beta}$ = 0.8 } Note that }
+\label{S8_Fig}
+\end{center}
+\end{figure}
+
 \clearpage

### 2016-06-23 Mobility_Pattern_Twitter_Landuse/main.tex
xx
hurry up

@@
 \documentclass[fleqn,10pt]{wlscirep}
-\title{Scientific Reports Title to see here (20 words or less)}
+\title{Understanding Human Mobility Patterns from Semantic Twitter User Trajectories}
 
@@
 \begin{abstract}
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
+xx
 \end{abstract}
 \begin{document}
-
 \flushbottom
 \maketitle
-% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
-%
-%  Click the title above to edit the author information and abstract
-%
 \thispagestyle{empty}
 
-\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.
-
 \section*{Introduction}
-
 The Introduction section, of referenced text\cite{Figueredo:2009dg} expands on the background of the work (some overlap with the Abstract is acceptable).
 The introduction should not include subheadings.
+
+The discovery and identifications of Lévy flight distribution, however, the implication of Lévy flight is that the process illustrates randomness.
 
@@
 \section*{Methods}
+Contextualizing the semantic meaning of the geo-located tweets
 
-Topical subheadings are allowed. Authors must ensure that their Methods section includes adequate experimental and characterization data necessary for others in the field to reproduce their work.
+Spatial entropy
 
-\bibliography{sample}
+Spatial dispersion
 
-\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu.
-Use the cite command for an inline citation, e.g.
-\cite{Figueredo:2009dg}.
+Mobility shape
 
-\section*{Acknowledgements (not compulsory)}
+First passage time model
+
+\bibliography{ref}
+
+\section*{Acknowledgements}
 
@@
 Must include all authors, identified by initials, for example:
-A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript.
+J.Y. conceived the experiment(s),  J.Y. conducted the experiment(s), J.Y. analysed the results.  All authors reviewed the manuscript.
 
 \section*{Additional information}
-
-To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing financial interests} (mandatory statement).
-
-The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing financial interests statement} on behalf of all authors of the paper.
-This statement must be included in the submitted article file.
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{|l|l|l|}
-\hline
-Condition & n & p \\
-\hline
-A & 5 & 0.1 \\
-\hline
-B & 10 & 0.01 \\
-\hline
-\end{tabular}
-\caption{\label{tab:example}Legend (350 words max). Example legend text.}
-\end{table}
-
-Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.
-
+The authors declare no competing financial interests.
 \end{document}

### 2016-06-23 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
hurry up

@@
 
-%\begin{figure}[ht]
-%\includegraphics[width=1\linewidth]{./figure/S1_overview_Fig_2}
-%\caption{{\bf An overview for delineating urban boundaries from Twitter user movements}}
-%\label{S1_Fig}
-%\end{figure}
-
 \begin{figure}[ht]
@@
 
-\subsection{Geo-located Twitter Data}
+\subsection{Geo-located Twitter Data and Data Processing}
 A geo-located tweet is a Twitter message with an additional geo-tag expressed as a pair of geographical coordinates that represent the location from which the tweet was sent.
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{./figure/uk}
-\caption{{\bf The spatial coverage of collected geo-located Twitter messages in Great Britain (left) and London (right).} Each point corresponds to a geo-located tweet collected for this study.
+\includegraphics[width=1.0\linewidth]{./figure/S2_twitter_density_Fig_1}
+\caption{{\bf The spatial coverage of collected geo-located Twitter messages in Great Britain (left) and London (right).} Each point corresponds to an individual geo-located tweet collected for this study.
 Twitter activity is most apparent in urban areas.}
@@
 
-To verify the collected tweets are from human users, the raw tweets were further filtered using the following steps.
+To remove tweets of non-human users from the collected database, the raw tweets were further filtered using the following steps.
 First we removed the duplicated messages in the dataset.
 Next, we removed non-human users based on unusual relocation speed \citep{hawelka,jurdak2015}. 
-We adopted a relocation speed threshold of 240 m/s as used by \citep{jurdak2015}. 
-We examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold.
+We examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold of 240 m/s as used by \citep{jurdak2015}.
 
@@
 
-To build our spatial network at a national level, we had to determine the basic units to serve as spatial nodes of the connectivity network of urban regions.
+To build the spatial network at a national level, we had to determine the basic units to serve as spatial nodes of the connectivity network of urban regions.
 Previous studies have suggested equi-distant spatial tessellation to generate nodes, which uses voronoi polygons to partition the space based on the collected points~\citep{rinzivillo2012,zhong2014}. 
@@
 r_{g} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(p_{i} -  p_{centroid})^{2}}, \textrm{where}\hspace{1ex} p_{centroid} = \frac{1}{n}\sum_{i=1}^{n}p_{i}
+\end{equation}
+
+\begin{equation} \label{eq:3}
+<T_{ij}>=k*\dfrac{P_{i} * P_{j}}{f(d_{ij})},  \textrm{and}\hspace{1ex} f(d_{ij}) \sim d_{ij}^{\beta}
 \end{equation}

### 2016-06-25 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
carry on

@@
 In this study, we presented a method to redraw urban boundaries based upon human interaction with the physical space.
-Specifically, we delineated the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million Twitter messages.
+Specifically, we depicted the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million geo-located Twitter messages.
 We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
-The result of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas that provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
+The results of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas that provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
 The technique was applied to both national scale (Great Britain) and municipal scale (the London metropolis).
 While our results corresponded well to the administrative boundaries, many unexpected and interesting boundaries were identified.
-
-Our study connects human mobility research with the delineation of non-administrative anthropographic urban boundaries based on Twitter user spatial interactions, which provides a new understanding of the interactions between human activity and urban space.
+More importantly, as the depicted urban boundaries exhibit a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to justify the distance decay effects in shaping the delineated urban boundaries.
+The well fitted gravity model explains how the geographical distances found in the mobility pattern affecting the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
 \newline

### 2016-06-28 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
continue

@@
 
-Talk about spatial proximity
+In this study, we describe a novel approach to delineating urban boundaries from a mobility network of physical human spatial interactions.
 
-In this study, we describe a novel approach to delineating urban boundaries based on the actual movements of Twitter users (i.e., the reallocation in space) extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
+actual movements of Twitter users (i.e., the reallocation in space) extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
 Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the country level)~\citep{hawelka,jurdak2015}.
@@
 
-While the
-
 We found that the collective mobility patterns of Twitter users in Great Britain are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points.
 The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of the urban space in Great Britain.
+
 Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. 

### 2016-06-28 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
xx

@@
 Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns.
-Defining the boundaries of urban regions is important to city planning, traffic management and resource allocation.
+Defining the boundaries of urban regions is important to a variety of urban planning applications.
 Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter regional activities.
@@
 While our results corresponded well to the administrative boundaries, many unexpected and interesting boundaries were identified.
-More importantly, as the depicted urban boundaries exhibit a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to justify the distance decay effects in shaping the delineated urban boundaries.
+More importantly, as the depicted urban boundaries exhibit a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
 The well fitted gravity model explains how the geographical distances found in the mobility pattern affecting the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
@@
 These interactions can take the form of trade, commerce, social connections, and political activity across the borders.
-Urban boundaries that respect the human interaction space can be very important to city planning, traffic management and resource allocation~\citep{lynch1960,jiang2015,liu2015,long2015}.
+Urban boundaries that respect the human interaction space can be very important to city planning, traffic management and resource allocation~\citep{gao2014, jiang2015,liu2015,long2015}.
 Many studies adopt a ``bottom-up'' approach to urban boundary delineation, where the geographic space is partitioned into small units and each unit is modeled as a node within a network structure.
@@
 While other researchers use social ties of Twitter users to identify cohesive regions for different countries across the world~\citep{kallus2015}, they found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.
+
+A common outcome observed from the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
+The general consensus is that the derived cohesive geographic divisions
+
+In spite of different community with different forms of human interaction, 
+However, there
+
+The notion of distance decay has a close relationship with The First Law of Geography: ‘everything is
+related to everything else, but near things are more related than distant things’ (Tobler
+1970, p. 236). Although highly developed urban areas offer various means of transportation,
+human activity remains to be restricted by a number of factors such as distance and
+accessibility. 
+Many researchers argue that the ‘death of distance’ hypothesis is premature even with today’s technologies (Wang et al. 2003, Rietveld and Vickerman 2004).
 
@@
 
-To remove tweets of non-human users from the collected database, the raw tweets were further filtered using the following steps.
+To reduce the effects from tweets of non-human users,  
+remove tweets of non-human users from the collected database, the raw tweets were further filtered using the following steps.
 First we removed the duplicated messages in the dataset.
@@
 
-\bibitem[\protect\citeauthoryear{Lynch}{1960}]{lynch1960}
-Lynch, K., 1960. The image of the city. MIT press.
-
 \bibitem[\protect\citeauthoryear{Newman}{2006}]{newman2006}

### 2016-06-29 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
xx
jia you

@@
 
-A common outcome observed from the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
-The general consensus is that the derived cohesive geographic divisions
-
-In spite of different community with different forms of human interaction, 
-However, there
-
-The notion of distance decay has a close relationship with The First Law of Geography: ‘everything is
-related to everything else, but near things are more related than distant things’ (Tobler
-1970, p. 236). Although highly developed urban areas offer various means of transportation,
-human activity remains to be restricted by a number of factors such as distance and
-accessibility. 
-Many researchers argue that the ‘death of distance’ hypothesis is premature even with today’s technologies (Wang et al. 2003, Rietveld and Vickerman 2004).
+A common outcome observed from the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive urban areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
+The general consensus is that those geographically cohesive urban areas are instances of spatial proximity effects, where the interaction strength between two urban regions decreases as the geographical distance between them increases~\citep{fotheringham1981}.
+In particular, spatial proximity is closely related to Tobler's First Law of Geography: ``\textit{everything is related to everything else, but near things are more related than distant things}''~\citep{miller2004}.
+While it is intuitively logical, few research efforts were further carried out to quantitatively understand how the spatial interactions shape the forms of connected urban areas (i.e., urban boundaries).
+One of the reason may due to the
+it is not an explicit constraints in these
 
 In this study, we describe a novel approach to delineating urban boundaries from a mobility network of physical human spatial interactions. 
-
 actual movements of Twitter users (i.e., the reallocation in space) extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
@@
 
+\bibitem[\protect\citeauthoryear{Fotheringham}{1981}]{fotheringham1981}
+Fotheringham, A.S., 1981. Spatial structure and distance-decay parameters. Annals of the Association of American Geographers, 71(3), pp.425-436.
+
 \bibitem[\protect\citeauthoryear{Frank {\itshape{et~al.}}}{2013}]{frank2013}
@@
 Newman, M.E.J., 2006. Modularity and community structure in networks. Proceedings of the National Academy of Sciences, 103, pp. 8577-8582. doi:10.1073/pnas.0601602103
+
+\bibitem[\protect\citeauthoryear{Miller}{2004}]{miller2004}
+Miller, H.J., 2004. Tobler's first law and spatial analysis. Annals of the Association of American Geographers, 94(2), pp.284-289.
 

### 2016-06-29 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
chapter 1

@@
 The results of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas that provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
-The technique was applied to both national scale (Great Britain) and municipal scale (the London metropolis).
+The technique was applied to both national (Great Britain) and municipal scale (the London metropolis).
 While our results corresponded well to the administrative boundaries, many unexpected and interesting boundaries were identified.
 More importantly, as the depicted urban boundaries exhibit a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
-The well fitted gravity model explains how the geographical distances found in the mobility pattern affecting the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
+The well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
 \newline
@@
 
-A common outcome observed from the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive urban areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
-The general consensus is that those geographically cohesive urban areas are instances of spatial proximity effects, where the interaction strength between two urban regions decreases as the geographical distance between them increases~\citep{fotheringham1981}.
+A common outcome observed from the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
+The general consensus is that those geographically cohesive areas are instances of spatial proximity effects, where the interaction strength between two urban regions decreases as the geographical distance between them increases~\citep{fotheringham1981}.
 In particular, spatial proximity is closely related to Tobler's First Law of Geography: ``\textit{everything is related to everything else, but near things are more related than distant things}''~\citep{miller2004}.
-While it is intuitively logical, few research efforts were further carried out to quantitatively understand how the spatial interactions shape the forms of connected urban areas (i.e., urban boundaries).
-One of the reason may due to the
-it is not an explicit constraints in these
+While it is intuitively logical, few research efforts were further carried out to quantitatively understand and explain how the spatial interactions shape the forms of connected geographical areas (i.e., urban boundaries).
+One of the major reasons is that geographical distance may affect the interaction strength, it is not an explicitly expressed constraint in the ``virtual'' human interactions, such as social ties or phone call initiation.
+In addition, there is a general lack of exploration regarding the linkages between the spatial proximity effects and the characteristics of the underlying spatial interactions.
 
 In this study, we describe a novel approach to delineating urban boundaries from a mobility network of physical human spatial interactions.
-actual movements of Twitter users (i.e., the reallocation in space) extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
+Specifically, the spatial interactions refer to the actual movements of Twitter users (i.e., the reallocation across the geographical space), which were extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
 Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the country level)~\citep{hawelka,jurdak2015}.
-We argue here that Twitter user mobility patterns provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation. 
+In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity that is limited to the postal code level~\citep{thiemann}. 
+We argue here that by investigating Twitter user mobility patterns, it provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation.
 A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in Great Britain.
-In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity that is limited to the postal code level~\citep{thiemann}.
 
@@
 The map equation algorithm was selected to avoid the inherent resolution problem~\citep{fortunato2007} of the common modularity maximization method~\citep{newman2006}. 
-
 We found that the collective mobility patterns of Twitter users in Great Britain are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points.
 The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of the urban space in Great Britain.
-
+As the depicted urban boundaries exhibit a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
+The well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas. 
 Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. 
@@
 \section{Background and Related Work}
+
 Distance decay effects
@@
 \subsection{Potential limitation of }
+To understand detailed human mobility patterns of individuals, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
+However, the low-resolution mobility data collected from census records~\citep{greenwood1985human} is estimated and aggregated at census tract level, while tracking of bank notes~\citep{brockmann2006scaling} is at zip code level and do not necessarily reflecting movements of the same individuals~\citep{gonzalez2008understanding}.
+In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\citep{zheng2008understanding}.
+However, the data is often limited in spatial scale (e.g.
+within a specific city or region) with a small group of people, for example, 182 and 226 volunteers participated in collecting such mobility data in~\citep{zheng2010geolife} and~\citep{rhee2011levy} respectively.
+Other than tracking people directly, the vehicle-based GPS data is often tied to a specific vehicle (e.g.
+taxi), which may only be accessible for a certain group of people~\citep{kung2014exploring}.
+
+Another approach from the literatures for studying human mobility is using mobile phone call data in the form of Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\citep{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
+Such a dataset can cover relatively large spatial scale (e.g., country level)~\citep{becker2013human,sobolevsky2013delineating} and a large portion of the population in the study region~\citep{kung2014exploring}.
+However, due to the concerns of infringement on individual privacy, the mobile phone call data is not publicly accessible, which is not ideal  for conducting replicable scientific findings, such as validating or extending the existing discoveries.
+
+In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
+LBSM enables users to attach their current location as a geo-tag to the message they will post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\citep{Jurdak2015}.
+A Big Data scenario emerges when millions social media users constantly posting messages.
+However, there are some limitations and complexities in directly using the LBSM data for study human mobility patterns. 
+For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place.
+It has been criticized for the lack of representativeness of the population as not all people use social media or send geo-located messages~\citep{kung2014exploring}.
+Another research challenge is to identify the users, as a social media account is not equal to a real person in the physical world~\citep{tsou2015}.
+Although many studies started to look into the demographic information of LBSM data, in particular Twitter data~\citep{mitchell2013geography,longley2015geotemporal}, these issues certainly require us to pose more strict criteria in filtering and extracting individual movements.
+
+In this study, geo-located Twitter data is chosen as source for studying detailed mobility patterns.
+Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
+It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\citep{cranshaw2012livehoods, hasan2013understanding}.
+In addition, it presents some unique advantages that make it suitable for studying human mobility patterns.
+For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\citep{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\citep{hawelka2014geo}, which is almost impossible for other mobility datasets.
+More importantly, by continuously monitoring the geo-located Twitter data streams with large volumes of detailed and frequently updated spatiotemporal  records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements).
 
@@
 \section{Conclusion and Discussion}
+Talk about interplay between human mobility
+
 In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.

### 2016-06-29 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
chapter 2 to be done

@@
 
+The spatial extent of those places
+
+Official urban boundaries are defined by government agencies for political and administrative purposes. 
+Urban environments are conceptualized as spaces that are recreated and formed by human activities~\citep{schliephake}.
+A fundamental question when using the administrative, ``top-down'', approach to defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
+These interactions can take the form of trade, commerce, social connections, and political activity across the borders.
+
+mainly about the intensity of human interactions across the geographical regions, however,
+
+While government agencies provide a variety of set of boundaries  
+Official urban boundaries are defined by government agencies for political and administrative purposes.
+
+The idea of
+
+Regarding using crowd-sourced data to determine the spatial extent of places
+
 Distance decay effects
@@
 Spatial Distribution of City Tweets and Their Densities
-
-Due to rapid urbanization, modern urban environments are evolving with dynamic forms and complex structures.
 
@@
 More importantly, by continuously monitoring the geo-located Twitter data streams with large volumes of detailed and frequently updated spatiotemporal  records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements).
-
-mainly about the intensity of human interactions across the geographical regions, however,
 
@@
 
-We found that the cumulative distribution function~\citep{clauset2009} of the number of locations visited by each Twitter user follows a two-tier power law distribution (shown in Fig.~\ref{S3_Fig}). 
+We found that the cumulative distribution function of the number of locations visited by each Twitter user follows a two-tier power law distribution (shown in Fig.~\ref{S3_Fig}). 
 The majority of the data distributed follows a truncated power-law distribution $P(X\geq x)\sim x^{-\alpha}e^{-\lambda x}$, where $\alpha = 1.24, \lambda =0.00132$; and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $P(X \geq x)\sim x^{-\alpha}$ with $\alpha$ value is 3.2.
@@
 Brockmann, D., Hufnagel, L., Geisel, T., 2006. The scaling laws of human travel. Nature 439, pp. 462-465. doi:10.1038/nature04292
-
-\bibitem[\protect\citeauthoryear{Clauset {\itshape{et~al.}}}{2009}]{clauset2009}
-Clauset, A., Shalizi, C., Newman, M., 2009. Power-Law Distributions in Empirical Data. Society for Industrial and Applied Mathematics Review. 51, pp. 661-703. doi:10.1137/070710111
 

### 2016-06-30 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
continue

@@
 \section{Background and Related Work}
+In real-world geography, urban regions are discrete individuals, with or without physical boundaries separating them.
+While government agencies define various sets of boundaries to partition the geographical space into  
+However, the spatial extent of these defined unit
+
+Although, their physical boundaries can be adjacent or distant, based on various connections amongst themselves, such as social-economic relations and commute patterns of citizens, certain groups of urban regions are more strongly connected as clusters than others.
+
+how citizens perceive, organize their image of a city and interact with the urban environments.
+On the other hand, today’s urban boundaries (i.e.
+edges and districts) are usually defined by government agencies for political and administrative purposes.
+A fundamental question for this “top-down” based approach to defining urban boundaries is whether it reflects the real situations of humans interacting across space, such as commuting or trading between the borders.
+Further, the urban boundaries that respect how people naturally interact with the space can be in grate importance for decision makers regarding city planning, resource allocation and even marketing campaigns.
 
@@
 
-While government agencies provide a variety of set of boundaries  
 Official urban boundaries are defined by government agencies for political and administrative purposes.

### 2016-06-30 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
before meeting

@@
 In real-world geography, urban regions are discrete individuals, with or without physical boundaries separating them.
-While government agencies define various sets of boundaries to partition the geographical space into  
-However, the spatial extent of these defined unit
+For political and administrative purposes, government agencies define various sets of boundaries to partition the geographical space into units at different spatial scale, for instances, states, counties or census tracts and electoral districts.
+\cite{
+However, the spatial extent of these defined units overlaps via connections of various human activities amongst themselves, such as social-economic relations and commute patterns of citizens, where certain groups of units are more strongly connected as clusters than others.
 
-Although, their physical boundaries can be adjacent or distant, based on various connections amongst themselves, such as social-economic relations and commute patterns of citizens, certain groups of urban regions are more strongly connected as clusters than others.
+agglomeration
 
@@
 
-\subsection{Potential limitation of }
+\subsection{Large-scale mobility network from geo-located Twitter data}
 To understand detailed human mobility patterns of individuals, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
@@
 In this study, geo-located Twitter data is chosen as source for studying detailed mobility patterns.
-Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
-It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\citep{cranshaw2012livehoods, hasan2013understanding}.
-In addition, it presents some unique advantages that make it suitable for studying human mobility patterns.
+Twitter is one of the most popular platforms and is been actively used in many countries.
+It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data.
+It presents some unique advantages that make it suitable for studying human mobility patterns.
 For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\citep{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\citep{hawelka2014geo}, which is almost impossible for other mobility datasets.
@@
 
+\bibitem[\protect\citeauthoryear{Blanford {\itshape{et~al.}}}{2015}]{blanford2015}
+Blanford, J.I., Huang, Z., Savelyev, A. and MacEachren, A.M., 2015. Geo-located tweets. enhancing mobility maps and capturing cross-border movement. PloS one, 10(6), p.e0129202.
+
 \bibitem[\protect\citeauthoryear{Brockmann {\itshape{et~al.}}}{2006}]{brockmann2006}

### 2016-07-02 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
??
Friday

@@
 \begin{abstract}
-Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns.
-Defining the boundaries of urban regions is important to a variety of urban planning applications.
-Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter regional activities.
+Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter-regional activities.
+Defining urban boundaries with considerations of socio-economic relationships and citizen commute patterns is important for many aspects in urban planning.
 In this study, we presented a method to redraw urban boundaries based upon human interaction with the physical space.
@@
 We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
-The results of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas that provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
-The technique was applied to both national (Great Britain) and municipal scale (the London metropolis).
-While our results corresponded well to the administrative boundaries, many unexpected and interesting boundaries were identified.
-More importantly, as the depicted urban boundaries exhibit a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
-The well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
+The results of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas, which provide a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
+The technique was applied to both national (Great Britain) and municipal scales (the London metropolis).
+While our results corresponded well with the administrative boundaries, many unexpected and interesting boundaries were identified.
+More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
+This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
 \newline
@@
 A fundamental question when using the administrative, ``top-down'', approach to defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
-These interactions can take the form of trade, commerce, social connections, and political activity across the borders.
-Urban boundaries that respect the human interaction space can be very important to city planning, traffic management and resource allocation~\citep{gao2014, jiang2015,liu2015,long2015}.
-Many studies adopt a ``bottom-up'' approach to urban boundary delineation, where the geographic space is partitioned into small units and each unit is modeled as a node within a network structure.
+These interactions can take the form of trade, commerce, social connections, and political activity across borders.
+Urban boundaries that respect the human interaction space are important to city planning, traffic management and resource allocation~\citep{gao2014, jiang2015,liu2015,long2015}.
+Many studies adopt a ``bottom-up'' approach to urban boundary delineation, where the geographic space is partitioned into small units and each unit is represented as a node within a network structure.
 A suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interaction among the nodes~\citep{lancichinetti2009}.
@@
 Specifically, the spatial interactions refer to the actual movements of Twitter users (i.e., the reallocation across the geographical space), which were extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
-Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the country level)~\citep{hawelka,jurdak2015}.
+Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the national level)~\citep{hawelka,jurdak2015}.
 In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity that is limited to the postal code level~\citep{thiemann}. 
-We argue here that by investigating Twitter user mobility patterns, it provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation.
+We argue here that by investigating Twitter user mobility patterns, we can provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation.
 A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in Great Britain.
@@
 The map equation algorithm was selected to avoid the inherent resolution problem~\citep{fortunato2007} of the common modularity maximization method~\citep{newman2006}. 
-We found that the collective mobility patterns of Twitter users in Great Britain are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points.
-The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of the urban space in Great Britain.
-As the depicted urban boundaries exhibit a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
+We found that the collective mobility patterns of Twitter users in Great Britain are divided into several distance ranges ranging from short, intra- to inter-city movements with clear distinction points.
+The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of urban spaces in Great Britain.
+As the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
 The well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas. 
 Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. 
-It provides a new understanding of the interactions between human activity and urban structures.
+This provides a new understanding of the interactions between human activity and urban structures.
 
 \section{Background and Related Work}
-In real-world geography, urban regions are discrete individuals, with or without physical boundaries separating them.
+In real-world geography, urban regions are discrete individuals, with or without physical boundaries separating them~\citep{jiang2015}.
 For political and administrative purposes, government agencies define various sets of boundaries to partition the geographical space into units at different spatial scale, for instances, states, counties or census tracts and electoral districts.
-\cite{
-However, the spatial extent of these defined units overlaps via connections of various human activities amongst themselves, such as social-economic relations and commute patterns of citizens, where certain groups of units are more strongly connected as clusters than others.
+However, the spatial extents of these defined units often overlap and agglomerate depending how citizens perceive, organize their image of a city and interact with the urban environments~\citep{lynch1960}.
+Connections are made among these units with various human activities crossing the boarders, such as social-economic relations and commute patterns of citizens. 
+In such cases, certain groups of units are more strongly connected as clusters than others, and the boarders of agglomeration of these units
 
-agglomeration
-
-how citizens perceive, organize their image of a city and interact with the urban environments.
-On the other hand, today’s urban boundaries (i.e.
-edges and districts) are usually defined by government agencies for political and administrative purposes.
-A fundamental question for this “top-down” based approach to defining urban boundaries is whether it reflects the real situations of humans interacting across space, such as commuting or trading between the borders.
-Further, the urban boundaries that respect how people naturally interact with the space can be in grate importance for decision makers regarding city planning, resource allocation and even marketing campaigns.
-
-The spatial extent of those places
+how people naturally interact with the space can be in grate importance for decision makers regarding city planning, resource allocation and even marketing campaigns.
 
@@
 
+\bibitem[\protect\citeauthoryear{Lynch}{1960}]{lynch1960}
+Lynch, K., 1960. The image of the city. MIT press.
+
 \bibitem[\protect\citeauthoryear{Newman}{2006}]{newman2006}

### 2016-07-08 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
home

@@
 However, the spatial extents of these defined units often overlap and agglomerate depending how citizens perceive, organize their image of a city and interact with the urban environments~\citep{lynch1960}.
+
+\citep{vasardani2013}
+\citep{hollenstein2010}
+\citep{stefanidis2013}
+
+For example, empirical studies have utilized 
 Connections are made among these units with various human activities crossing the boarders, such as social-economic relations and commute patterns of citizens. 
 In such cases, certain groups of units are more strongly connected as clusters than others, and the boarders of agglomeration of these units
-
 how people naturally interact with the space can be in grate importance for decision makers regarding city planning, resource allocation and even marketing campaigns.
 
-Official urban boundaries are defined by government agencies for political and administrative purposes. 
-Urban environments are conceptualized as spaces that are recreated and formed by human activities~\citep{schliephake}.
-A fundamental question when using the administrative, ``top-down'', approach to defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
 These interactions can take the form of trade, commerce, social connections, and political activity across the borders.
@@
 mainly about the intensity of human interactions across the geographical regions, however,
-
-Official urban boundaries are defined by government agencies for political and administrative purposes.
 
@@
 
+\bibitem[\protect\citeauthoryear{Hollenstein and Purves}{2010}]{hollenstein2010}
+Hollenstein, L. and Purves, R., 2010. Exploring place through user-generated content: Using Flickr tags to describe city cores. Journal of Spatial Information Science, 2010(1), pp.21-48.
+
 \bibitem[\protect\citeauthoryear{Huang {\itshape{et~al.}}}{2016}]{huang2016}
@@
 
+\bibitem[\protect\citeauthoryear{Stefanidis {\itshape{et~al.}}}{2013}]{stefanidis2013}
+Stefanidis, A., Cotnoir, A., Croitoru, A., Crooks, A., Rice, M.
+and Radzikowski, J., 2013.
+Demarcating new boundaries: mapping virtual polycentric communities through social media content.
+Cartography and Geographic Information Science, 40(2), pp.116-129.
+
 \bibitem[\protect\citeauthoryear{Steiger {\itshape{et~al.}}}{2015}]{steiger2015}
@@
 Thiemann, C., Theis, F., Grady, D., Brune, R., Brockmann, D., 2010. The Structure of Borders in a Small World. PLoS ONE 5, e15422. doi:10.1371/journal.pone.0015422
+
+\bibitem[\protect\citeauthoryear{Vasardani {\itshape{et~al.}}}{2013}]{vasardani2013}
+Vasardani, M., Winter, S. and Richter, K.F., 2013. Locating place names from place descriptions. International Journal of Geographical Information Science, 27(12), pp.2509-2532.
 

### 2016-07-08 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
new

@@
 In real-world geography, urban regions are discrete individuals, with or without physical boundaries separating them~\citep{jiang2015}.
-For political and administrative purposes, government agencies define various sets of boundaries to partition the geographical space into units at different spatial scale, for instances, states, counties or census tracts and electoral districts.
+For political and administrative purposes, government agencies define various sets of boundaries to partition the geographical space into spatial units at different scales, for instances, states, counties or census tracts and electoral districts.
 However, the spatial extents of these defined units often overlap and agglomerate depending how citizens perceive, organize their image of a city and interact with the urban environments~\citep{lynch1960}.
+As connections are made among these units via various human activities crossing the boarders, such as social-economic relations and commute patterns of citizens, certain groups of units are more strongly connected as clusters than others.
+The boundaries of the agglomeration of these units are argued to reflect how people naturally interact with the geographic space, which is important for city planning~\citep{hollenstein2010}, urban growth evaluations~\citep{jiang2015,long2015}, and traffic management~\citep{gao2014}.
+Empirical studies have attempted to delineate such boundaries with different methods and data sets.
+In general, the methods from existing literatures can be summarized into two, spatial clustering and network based, approaches.
+Spatial clustering based approaches determine the boundaries based the intensity of geographic locations related to human activities, for instances, locations of social media check-ins~\citep{jiang2015,sun2016}, place descriptions from crowd-sourced Web content~\citep{vasardani2013} and geo-tagged Flickr data~\citep{stefanidis2013,hu2016}.
+While interesting boundaries of urban areas were captured and delineated, the dynamic connections among different spatial units were not considered in the spatial clustering based approaches, where the results are discrete and independent areas reflecting high intensity of human activities.
 
-\citep{vasardani2013}
-\citep{hollenstein2010}
-\citep{stefanidis2013}
-
-For example, empirical studies have utilized 
-Connections are made among these units with various human activities crossing the boarders, such as social-economic relations and commute patterns of citizens. 
-In such cases, certain groups of units are more strongly connected as clusters than others, and the boarders of agglomeration of these units
-how people naturally interact with the space can be in grate importance for decision makers regarding city planning, resource allocation and even marketing campaigns.
-
-These interactions can take the form of trade, commerce, social connections, and political activity across the borders.
-
-mainly about the intensity of human interactions across the geographical regions, however,
-
-The idea of
-
-Regarding using crowd-sourced data to determine the spatial extent of places
+On the other hand, network based approaches attempt to delineate urban boundaries based on the intensity of human interactions among different spatial units, where each spatial unit is treated as a node and the edge is modeled by human interactions between two nodes.
+Such human interactions can take physical or virtual forms, such as trade, commerce, social connections, and political activity across the borders.
+Regarding virtual networks of human spatial interactions, social ties of Twitter users are used to identify cohesive regions for different countries across the world~\citep{kallus2015}, a map of Great Britain is redrew based the communication network of phone call initiation~\cite{ratti2010},
 
@@
 \subsection{A network of large-scale Twitter user spatial interactions}
-Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns. 
-Some urban regions are more strongly connected to each other than other urban regions.
 Therefore, this study connects urban regions when a twitter user's movement begins in one region and ends in another region.
@@
 In addition, the distance range of the movements is usually explained by local socio-economic factors (e.g., work commuting ) that provide for a specific interpretation of the apparent patterns.
-The patterns obtained from Twitter user mobility are comparable to the patterns produced by those of the network of landline phone calls~\citep{ratti2010}.\
+The patterns obtained from Twitter user mobility are comparable to the patterns produced by those of the network of landline phone calls~\citep{ratti2010}.
 For example, the region of Wales appears to consist of three communities as found in the connectivity of both phone calls and long distance movements. 
@@
 
+\bibitem[\protect\citeauthoryear{Hu {\itshape{et~al.}}}{2016}]{hu2016}
+Hu, Y., Gao, S., Janowicz, K., Yu, B., Li, W.
+and Prasad, S., 2015.
+Extracting and understanding urban areas of interest using geotagged photos.
+Computers, Environment and Urban Systems, 54, pp.240-254.
+
 \bibitem[\protect\citeauthoryear{Huang {\itshape{et~al.}}}{2016}]{huang2016}
@@
 \bibitem[\protect\citeauthoryear{Liu {\itshape{et~al.}}}{2015}]{liu2015}
-Liu, X., Gong, L., Gong, Y., Liu, Y., 2015. Revealing travel patterns and city structure with taxi trip data. J. Transportation Geography, 43, pp. 78-90. doi:10.1016/j.jtrangeo.2015.01.016
+Liu, X., Gong, L., Gong, Y., Liu, Y., 2015. Revealing travel patterns and city structure with taxi trip data. Journal of Transportation Geography, 43, pp. 78-90. doi:10.1016/j.jtrangeo.2015.01.016
 
@@
 
-\bibitem[\protect\citeauthoryear{Long {\itshape{et~al.}}}{2015}]{long2015}
+\bibitem[\protect\citeauthoryear{Luo {\itshape{et~al.}}}{2016}]{luo2016}
 Luo, F., Cao, G., Mulligan, K., Li, X., 2016. Explore spatiotemporal and demographic characteristics of human mobility via Twitter: A case study of Chicago, Applied Geography, 70, pp. 11-25
@@
 doi:10.1371/journal.pone.0014248
+
+\bibitem[\protect\citeauthoryear{Rae}{2009}]{rae2009}
+Rae, A., 2009.
+From spatial interaction data to spatial interaction information?
+Geovisualisation and spatial structures of migration from the 2001 UK census.
+Computers, Environment and Urban Systems, 33(3), pp.161-178.
 
@@
 
+\bibitem[\protect\citeauthoryear{Sun {\itshape{et~al.}}}{2016}]{sun2016}
+Sun, Y., Fan, H., Li, M.
+and Zipf, A., 2016.
+Identifying the city center using human travel flows generated from location-based social networking data.
+Environment and Planning B: Planning and Design, 43(3), pp.480-498.
+
 \bibitem[\protect\citeauthoryear{Thiemann {\itshape{et~al.}}}{2010}]{thiemann}

### 2016-07-09 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
dinner

@@
 
-In this study, we describe a novel approach to delineating urban boundaries from a mobility network of physical human spatial interactions.
+In this study, we describe a novel approach to delineating non-administrative anthropographic urban boundaries from a mobility network of physical human spatial interactions.
 Specifically, the spatial interactions refer to the actual movements of Twitter users (i.e., the reallocation across the geographical space), which were extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
@@
 In general, the methods from existing literatures can be summarized into two, spatial clustering and network based, approaches.
-Spatial clustering based approaches determine the boundaries based the intensity of geographic locations related to human activities, for instances, locations of social media check-ins~\citep{jiang2015,sun2016}, place descriptions from crowd-sourced Web content~\citep{vasardani2013} and geo-tagged Flickr data~\citep{stefanidis2013,hu2016}.
+Spatial clustering based approaches determine the boundaries based the intensity of geographic locations related to human activities, for instances, locations of social media check-ins~\citep{cranshaw2012,jiang2015,sun2016}, place descriptions from crowd-sourced Web content~\citep{vasardani2013} and geo-tagged Flickr data~\citep{stefanidis2013,hu2016}.
 While interesting boundaries of urban areas were captured and delineated, the dynamic connections among different spatial units were not considered in the spatial clustering based approaches, where the results are discrete and independent areas reflecting high intensity of human activities.
@@
 Such human interactions can take physical or virtual forms, such as trade, commerce, social connections, and political activity across the borders.
-Regarding virtual networks of human spatial interactions, social ties of Twitter users are used to identify cohesive regions for different countries across the world~\citep{kallus2015}, a map of Great Britain is redrew based the communication network of phone call initiation~\cite{ratti2010},
+In terms of networks of virtual human spatial interactions, the connections between nodes are formed by virtual human relations, for examples, social ties of Twitter users are used to identify cohesive regions for different countries across the world~\citep{kallus2015}, and a map of Great Britain is redrew based the communication network of phone call initiations~\citep{ratti2010}.
+In contrast, physical human spatial interactions, the connections between nodes are formed by the collections of individuals physically allocating from one node to another, which is refereed as a mobility network of spatial interactions in this study.
+Many existing studies have attempted to extract the mobility network from various data sources, such as census migration data~\citep{rae2009}, GPS recorded vehicle~\citep{rinzivillo2012} and taxi trip records~\citep{liu2015}, mobile phone call data~\citep{sobolevsky2013,zhong2014}, and social media user movements from check-ins~\citep{liu2014} and geo-located Twitter data~\citep{hawelka,gao2014}.
+The networks of human spatial interactions are then further explored to reveal clusters regarding the intensities of the interaction strength, such as applying visual analytics methods~\citep{rae2009} or more popular community detection methods~\citep{coscia2011}.
 
-Distance decay effects
-where a city boundary ends and another city boundary emerges.
-Spatial Distribution of City Tweets and Their Densities
+The clusters of urban regions in the form of communities in the network space yield geographically cohesive areas, in spite of different community detection methods and forms of human spatial interactions were used.
+Researchers argue that those geographically cohesive areas are related to the distance decay effects, where the interaction strength between two urban regions decreases as the geographical distance between them increases.
+However, few research efforts are carried out to explore the linkages between the spatial proximity effects and the characteristics of the underlying spatial interactions, which is critical for explaining how the spatial interactions shape the forms of connected geographical areas (i.e., urban boundaries).
+While geographical distance is not explicitly expressed constraint in the ``virtual'' human interactions, we argue that seeking answers from the mobility network of spatial interactions with the characteristics of underlying mobility patterns can help to explain how distance decay effects affect the interaction strength and the shape of depicted urban boundaries.
 
 \subsection{Large-scale mobility network from geo-located Twitter data}
-To understand detailed human mobility patterns of individuals, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
-However, the low-resolution mobility data collected from census records~\citep{greenwood1985human} is estimated and aggregated at census tract level, while tracking of bank notes~\citep{brockmann2006scaling} is at zip code level and do not necessarily reflecting movements of the same individuals~\citep{gonzalez2008understanding}.
-In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\citep{zheng2008understanding}.
+To construct a large scale mobility network of human spatial interactions, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
+However, the low-resolution mobility data collected from census records~\citep{rae2009} is estimated and aggregated at census tract level and do not necessarily reflecting movements of the same individuals.
+In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\citep{zheng2008}.
 However, the data is often limited in spatial scale (e.g.
-within a specific city or region) with a small group of people, for example, 182 and 226 volunteers participated in collecting such mobility data in~\citep{zheng2010geolife} and~\citep{rhee2011levy} respectively.
+within a specific city or region) with a small group of people, for example, 182 and 226 volunteers participated in collecting such mobility data in~\citep{zheng2008} and~\citep{rhee2011} respectively.
 Other than tracking people directly, the vehicle-based GPS data is often tied to a specific vehicle (e.g.
-taxi), which may only be accessible for a certain group of people~\citep{kung2014exploring}.
+taxi), which may only be accessible for a certain group of people~\citep{kung2014}.
 
@@
 Twitter is one of the most popular platforms and is been actively used in many countries.
-It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data.
+It provides a publicly accessible streaming API ({\tt{https://dev.twitter.com/streaming/overview}}) for easy access to its data.
 It presents some unique advantages that make it suitable for studying human mobility patterns.
-For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\citep{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\citep{hawelka2014geo}, which is almost impossible for other mobility datasets.
+For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\citep{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\citep{hawelka}, which is almost impossible for other mobility datasets.
 More importantly, by continuously monitoring the geo-located Twitter data streams with large volumes of detailed and frequently updated spatiotemporal  records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements).
 
+A geo-located tweet is a Twitter message with an additional geo-tag expressed as a pair of geographical coordinates that represent the location from which the tweet was sent.
+
 \section{Materials and Methods}
-\subsection{Overview}
-In this research, we use large-scale Twitter user spatial interactions inferred from the collective mobility patterns of Twitter users to delineate urban boundaries in Great Britain.
-A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\citep{gonzalez2008}.
-This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two consecutive recorded locations is one month.
-To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the islands of Great Britain.
-Twitter user movements were then used to establish the connectivity between fishnet cells to form a connectivity network where each cell is considered a node within the network. 
-Finally, by detecting strongly connected clusters in the network space using community detection methods~\citep{coscia2011}, we were able to reveal urban boundaries within the geographic space. 
-An overview of the approach is illustrated in Fig.~\ref{S1_Fig} and the details are presented in the following sections.
-
-\begin{figure}[ht]
-\begin{center}
-\includegraphics[width=1\linewidth]{./figure/S1_overview_Fig_2}
-\caption{\bfseries{An overview for delineating urban boundaries from Twitter user movements}}
-\label{S1_Fig}
-\end{center}
-\end{figure}
+%\subsection{Overview}
+%In this research, we use large-scale Twitter user spatial interactions inferred from the collective mobility patterns of Twitter users to delineate urban boundaries in Great Britain.
+%A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\citep{gonzalez2008}.
+%This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two consecutive recorded locations is one month.
+%To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the islands of Great Britain.
+%Twitter user movements were then used to establish the connectivity between fishnet cells to form a connectivity network where each cell is considered a node within the network. 
+%Finally, by detecting strongly connected clusters in the network space using community detection methods~\citep{coscia2011}, we were able to reveal urban boundaries within the geographic space. 
+%An overview of the approach is illustrated in Fig.~\ref{S1_Fig} and the details are presented in the following sections. 
+%
+%\begin{figure}[ht]
+%\begin{center}
+%\includegraphics[width=1\linewidth]{./figure/S1_overview_Fig_2}
+%\caption{\bfseries{An overview for delineating urban boundaries from Twitter user movements}}
+%\label{S1_Fig}
+%\end{center}
+%\end{figure}
 
 \subsection{Geo-located Twitter Data and Data Processing}
-A geo-located tweet is a Twitter message with an additional geo-tag expressed as a pair of geographical coordinates that represent the location from which the tweet was sent.
-For this study, geo-located tweets were collected using the Twitter Streaming API (
-{\tt{https://dev.twitter.com/streaming/overview}}) by supplying a geographical bounding box to retrieve all the  geo-located tweets within an area of interest.
+For this study, geo-located tweets were collected using the Twitter Streaming API by supplying a geographical bounding box to retrieve all the  geo-located tweets within an area of interest.
 To ensure complete coverage of Great Britain, we set the bounding box to the British Isles using the lower left and upper right coordinates (49.497, -14.854), (61.186, 2.637) respectively.
@@
 Previous studies have suggested equi-distant spatial tessellation to generate nodes, which uses voronoi polygons to partition the space based on the collected points~\citep{rinzivillo2012,zhong2014}. 
-This approach demonstrates improvements for estimating the locations of mobile phone records based on the cell tower triangulation~\cite{gonzalez2008,qian2013}.
+This approach demonstrates improvements for estimating the locations of mobile phone records based on the cell tower triangulation~\citep{gonzalez2008,qian2013}.
 However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\citep{sakaki2010,zandbergen2009}.
@@
 The radius of gyration is a metric to distinguish mobility patterns of individuals~\citep{gonzalez2008}, which is defined as Eq. \eqref{eq:2}:
-
 \begin{equation} \label{eq:2}
@@
 \end{equation}
-
 \begin{equation} \label{eq:3}
@@
 \end{equation}
-
 \noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
@@
 It identifies communities by minimizing the expected description length of the trajectory of a random walker, which is shown below:
-
 \begin{equation} \label{eq:1}
@@
 \end{equation}
-
 In Eq. \eqref{eq:1} , $L(M)$ consists of two terms: qH(Q) is the entropy of the movement among clusters and $ \sum_{i=1}^{m} p_{i}H(p_{i})$ is the entropy of movement within clusters. 
@@
 We found that the cumulative distribution function of the number of locations visited by each Twitter user follows a two-tier power law distribution (shown in Fig.~\ref{S3_Fig}). 
-The majority of the data distributed follows a truncated power-law distribution $P(X\geq x)\sim x^{-\alpha}e^{-\lambda x}$, where $\alpha = 1.24, \lambda =0.00132$; and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $P(X \geq x)\sim x^{-\alpha}$ with $\alpha$ value is 3.2.
+The majority of the data follow a truncated power-law distribution $P(X\geq x)\sim x^{-\alpha}e^{-\lambda x}$, where $\alpha = 1.24, \lambda =0.00132$; and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $P(X \geq x)\sim x^{-\alpha}$ with $\alpha$ value is 3.2.
 The distribution was found to be consistent over all individual months examined (June to December, 2014), which has a slight offset in the truncated power-law distribution (the mean $\alpha$ value is 1.26 $ \pm$ with a 0.05 $\sigma$ and the mean $\lambda$ value as 0.00134 $ \pm$  with a 0.0002 $\sigma$).
@@
 \begin{center}
-\includegraphics[width=0.8\linewidth]{./figure/S7_london}
+\includegraphics[width=0.7\linewidth]{./figure/S7_london}
 \caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.
@@
 \begin{center}
-\includegraphics[width=0.8\linewidth]{./figure/Gravity}
+\includegraphics[width=0.7\linewidth]{./figure/Gravity}
 \caption{{\bf The observed interaction strength versus the estimated ones from the adopted gravity model with $\bf{\beta}$ = 0.8 } Note that }
@@
 Coscia, M., Giannotti, F. and Pedreschi, D., 2011. A classification for community discovery methods in complex networks. Statistical Analysis and Data Mining, 4(5), pp. 512-546.
+
+\bibitem[\protect\citeauthoryear{Cranshaw {\itshape{et~al.}}}{2012}]{cranshaw2012}
+Cranshaw, J., Schwartz, R., Hong, J.I.
+and Sadeh, N., 2012.
+The livehoods project: Utilizing social media to understand the dynamics of a city.
+In International AAAI Conference on Weblogs and Social Media p.
+58.
 
@@
 doi: 10.1371/journal.pone.0126713
+
+\bibitem[\protect\citeauthoryear{Kung {\itshape{et~al.}}}{2014}]{kung2014}
+Kung, K.S., Greco, K., Sobolevsky, S. and Ratti, C., 2014. Exploring universal patterns in human home-work commuting from mobile phone data. PloS one, 9(6), p.e96180.
 
@@
 
+\bibitem[\protect\citeauthoryear{Zheng {\itshape{et~al.}}}{2008}]{zheng2008}
+Zheng, Y., Li, Q., Chen, Y., Xie, X.
+and Ma, W.Y., 2008, September.
+Understanding mobility based on GPS data.
+In Proceedings of the 10th international conference on Ubiquitous computing (pp.
+312-321).
+ACM.
+
 \bibitem[\protect\citeauthoryear{Zhong {\itshape{et~al.}}}{2014}]{zhong2014}

### 2016-07-10 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
home

@@
 within a specific city or region) with a small group of people, for example, 182 and 226 volunteers participated in collecting such mobility data in~\citep{zheng2008} and~\citep{rhee2011} respectively.
-Other than tracking people directly, the vehicle-based GPS data is often tied to a specific vehicle (e.g.
-taxi), which may only be accessible for a certain group of people~\citep{kung2014}.
-
-Another approach from the literatures for studying human mobility is using mobile phone call data in the form of Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\citep{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
+Other than tracking people directly, the vehicle-based GPS data is often tied to a specific vehicle (e.g. taxi), which may only be accessible for a certain group of people~\citep{kung2014}. 
+Another popular mobility data source found in the literatures is the mobile phone call data in the form of Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\citep{gonzalez2008,kung2014,zhong2014}.
 Such a dataset can cover relatively large spatial scale (e.g., country level)~\citep{becker2013human,sobolevsky2013delineating} and a large portion of the population in the study region~\citep{kung2014exploring}.

### 2016-07-10 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
saturday

@@
 Another popular mobility data source found in the literatures is the mobile phone call data in the form of Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\citep{gonzalez2008,kung2014,zhong2014}.
-Such a dataset can cover relatively large spatial scale (e.g., country level)~\citep{becker2013human,sobolevsky2013delineating} and a large portion of the population in the study region~\citep{kung2014exploring}.
-However, due to the concerns of infringement on individual privacy, the mobile phone call data is not publicly accessible, which is not ideal  for conducting replicable scientific findings, such as validating or extending the existing discoveries.
+Such a dataset can cover relatively large spatial scale (e.g., country level)~\citep{sobolevsky2013} and a large portion of the population in the study region~\citep{kung2014}. 
+However, due to the concerns of infringement on individual privacy, the mobile phone call data is not publicly accessible, which is not ideal  for conducting replicable scientific findings or comparisons across different regions.
 
 In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
-LBSM enables users to attach their current location as a geo-tag to the message they will post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\citep{Jurdak2015}.
-A Big Data scenario emerges when millions social media users constantly posting messages.
-However, there are some limitations and complexities in directly using the LBSM data for study human mobility patterns. 
-For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place.
-It has been criticized for the lack of representativeness of the population as not all people use social media or send geo-located messages~\citep{kung2014exploring}.
+This is also evident from the related studies mentioned above.
+However, there are some limitations and complexities in directly extracting and using the mobility data from the LBSM data sets. 
+For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located tweet or check-in at a new place.
+It has been criticized for the lack of representativeness of the population as not all people use social media or send geo-located messages~\citep{kung2014}. 
 Another research challenge is to identify the users, as a social media account is not equal to a real person in the physical world~\citep{tsou2015}.
@@
 In this study, geo-located Twitter data is chosen as source for studying detailed mobility patterns.
+A geo-located tweet is a Twitter message with an additional geo-tag expressed as a pair of geographical coordinates that represent the location from which the tweet was sent.
 Twitter is one of the most popular platforms and is been actively used in many countries. 
@@
 It presents some unique advantages that make it suitable for studying human mobility patterns.
-For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\citep{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\citep{hawelka}, which is almost impossible for other mobility datasets.
-More importantly, by continuously monitoring the geo-located Twitter data streams with large volumes of detailed and frequently updated spatiotemporal  records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements).
+For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\citep{jurdak2015}; the large spatial coverage enables to study global mobility patterns~\citep{hawelka}, which is almost impossible for other mobility datasets.
 
-A geo-located tweet is a Twitter message with an additional geo-tag expressed as a pair of geographical coordinates that represent the location from which the tweet was sent.
+The CEUS paper and song gao
 
@@
 \subsection{Geo-located Twitter Data and Data Processing}
-For this study, geo-located tweets were collected using the Twitter Streaming API by supplying a geographical bounding box to retrieve all the  geo-located tweets within an area of interest.
-To ensure complete coverage of Great Britain, we set the bounding box to the British Isles using the lower left and upper right coordinates (49.497, -14.854), (61.186, 2.637) respectively.
+For this study, the geo-located tweets were collected using the Twitter Streaming API by supplying a geographical bounding box to retrieve all the  geo-located tweets within an area of interest.
+To ensure complete coverage of Great Britain, we set the bounding box to the British Isles using the lower left and upper right coordinates (49.49, -14.85), (61.18, 2.63) respectively.
 This does include the whole of Ireland part of France.
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{./figure/S2_twitter_density_Fig_1}
+\includegraphics[width=.8\linewidth]{./figure/S2_twitter_density_Fig_1}
 \caption{{\bf The spatial coverage of collected geo-located Twitter messages in Great Britain (left) and London (right).} Each point corresponds to an individual geo-located tweet collected for this study.
-Twitter activity is most apparent in urban areas.}
+Note that Twitter activities are most apparent in urban areas.}
 \label{S2_Fig}
@@
 \end{equation}
-\begin{equation} \label{eq:3}
-<T_{ij}>=k*\dfrac{P_{i} * P_{j}}{f(d_{ij})},  \textrm{and}\hspace{1ex} f(d_{ij}) \sim d_{ij}^{\beta}
-\end{equation}
 \noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
@@
 to examine groups of strongly connected urban regions.
+
+\subsection{Distance decay effects with a gravity model}
+\begin{equation} \label{eq:3}
+<T_{ij}>=k*\dfrac{P_{i} * P_{j}}{f(d_{ij})},  \textrm{and}\hspace{1ex} f(d_{ij}) \sim d_{ij}^{\beta}
+\end{equation}
 

### 2016-07-10 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
dinner

@@
 \subsection{Large-scale mobility network from geo-located Twitter data}
-To construct a large scale mobility network of human spatial interactions, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
-However, the low-resolution mobility data collected from census records~\citep{rae2009} is estimated and aggregated at census tract level and do not necessarily reflecting movements of the same individuals.
+To construct a large-scale mobility network of human spatial interactions, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
+The low-resolution mobility data collected from census records~\citep{rae2009} is estimated and aggregated at census tract level and do not necessarily reflecting movements of the same individuals.
 In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\citep{zheng2008}.
@@
 Another research challenge is to identify the users, as a social media account is not equal to a real person in the physical world~\citep{tsou2015}.
-Although many studies started to look into the demographic information of LBSM data, in particular Twitter data~\citep{mitchell2013geography,longley2015geotemporal}, these issues certainly require us to pose more strict criteria in filtering and extracting individual movements.
+Many studies started to look into the demographic information of LBSM data, in particular Twitter data~\citep{steiger2015,luo2016}. 
+While the used methods varies, these studies suggest that the mentioned issues require us to pose more strict criteria in filtering and extracting individual movements.
 
-In this study, geo-located Twitter data is chosen as source for studying detailed mobility patterns.
+In this study, geo-located Twitter data are chosen as the source for constructing large-scale mobility networks of human spatial interactions and studying detailed mobility patterns.
 A geo-located tweet is a Twitter message with an additional geo-tag expressed as a pair of geographical coordinates that represent the location from which the tweet was sent.
 Twitter is one of the most popular platforms and is been actively used in many countries. 
-It provides a publicly accessible streaming API ({\tt{https://dev.twitter.com/streaming/overview}}) for easy access to its data.
-It presents some unique advantages that make it suitable for studying human mobility patterns.
-For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\citep{jurdak2015}; the large spatial coverage enables to study global mobility patterns~\citep{hawelka}, which is almost impossible for other mobility datasets.
-
-The CEUS paper and song gao
+It provides a publicly accessible streaming API ({\tt{http://dev.twitter.com/streaming}}) for easy data access.
+The geo-located Twitter data present some unique advantages regarding the purpose of this study, for example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\citep{jurdak2015}; the large spatial coverage enables to study global mobility patterns~\citep{hawelka}, which is almost impossible for other mobility datasets.
+Also, it provides the opportunities for reproducing this study in other countries.
 
@@
 This does include the whole of Ireland part of France.
-We implemented a data crawler to continuously collect 7-months of data (June $1^{st}$ -- December $31^{st}$, 2014) resulting in over 101.8 million tweets with a total data volume of 60 GB, which we restrict to 69 million based on a process outlined below.
-To showcase the overall spatial coverage of the collected geo-located tweets, a density map of the tweet locations in British Isles for July 2014 is shown in Fig.~\ref{S2_Fig}.
+We implemented a data crawler to continuously collect 7-months of data (June $1^{st}$ -- December $31^{st}$, 2014) resulting in over 101.8 million tweets with a total data volume of 60 GB.
+During the data collection phase, the data crawler did not encounter any issue regarding whether it exceeds the data quota by the 1\% policy mentioned in~\citep{hawelka}).
+It means we have managed to download all the geo-located tweets for the given bounding box.
+To showcase the overall spatial coverage of the collected geo-located tweets, the geo-locations of all the collected Tweets are shown in Fig.~\ref{S2_Fig}.
 The collected point visualization reveals the geography of cities.
@@
 \includegraphics[width=.8\linewidth]{./figure/S2_twitter_density_Fig_1}
-\caption{{\bf The spatial coverage of collected geo-located Twitter messages in Great Britain (left) and London (right).} Each point corresponds to an individual geo-located tweet collected for this study.
+\caption{{\bf The spatial coverage of collected geo-located Tweets in Great Britain (left) and London (right).} Each point corresponds to an individual geo-located tweet collected for this study.
 Note that Twitter activities are most apparent in urban areas.}
@@
 \end{figure}
-
-To reduce the effects from tweets of non-human users,  
-remove tweets of non-human users from the collected database, the raw tweets were further filtered using the following steps.
+Because the original location information embedded in the geo-tag is given in units of latitude and longitude, we projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations.
+We used the geographical boundary of Great Britain, which is derived from Office for National Statistics (ONS) of UK ({\tt{http://www.ons.gov.uk/ons}}), to further restrict the remaining tweets to be ``domestic".
+Based on these restrictions, the filtered dataset contains 69,847,497 tweets made by 1,153,891 Twitter users.
+To reduce the effects of tweets from non-human users, the raw tweets were further filtered using the following steps.
 First we removed the duplicated messages in the dataset.
-Next, we removed non-human users based on unusual relocation speed \citep{hawelka,jurdak2015}. 
+We then removed non-human users based on unusual relocation speed \citep{hawelka,jurdak2015}. 
 We examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold of 240 m/s as used by \citep{jurdak2015}.
-
-That is that the time interval between a user's first and last recorded
-
- agglomeration
-
-Because the original location information embedded in the geo-tag is given in units of latitude and longitude, we projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations.
-Finally, we used the geographical boundary of Great Britain, which is derived from Office for National Statistics (ONS) of UK ({\tt{http://www.ons.gov.uk/ons}}), to further restrict the remaining tweets to be ``domestic".
-Based on these restrictions, the filtered dataset for the following study contains 69,847,497 tweets made by 1,153,891 Twitter users.
+Finally, to reflect the spatial interactions of residents rather than tourists, we further impose a condition that the time interval between a user's first and last recorded tweets should be more than 30 days.
+In other words, a user that is identified to have stayed in the study region more than 30 days is considered as a resident.
+The filtered dataset for the following study contains 60,209,778 tweets made by 824,712 Twitter users.
 
 At this stage, each geo-located tweet is represented as a tuple $\langle user\_id, loc, t, m \rangle$, where $user\_id$ is an anonymous Twitter user id; $loc$ is the recorded location of the tweet as a coordinate pair; $t$ is the timestamp of the tweet's post; and $m$ is the actual content of the tweet.
-To protect Twitter user privacy, the id field was replaced with a randomly generated unique number. 
-Because we are interested in collective Twitter user movement instead of individual user trajectories,
-each geo-location of a
-similar to the approach used in
-
-the content of the message was removed. 
+To protect Twitter users’ privacy, the id field was replaced with a randomly generated unique number and the content of the message was removed.
+In addition, the actual location of each geo-located Tweet is only used for distance calculation and determining the corresponding geographic unit it falls in. 
 Our simplified geo-located tweet dataset can be shared with other researchers upon request.
@@
 \subsection{A network of large-scale Twitter user spatial interactions}
-Therefore, this study connects urban regions when a twitter user's movement begins in one region and ends in another region.
+A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\citep{gonzalez2008}.
+This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two consecutive recorded locations is one month.
+To identify the clusters of urban regional connectedness, Twitter user movements are used to establish a connectivity network, where two urban region connects when a twitter user's movement begins in one and ends in another.
 These connections can be represented by an origin-destination (OD) matrix based on the collective Twitter user displacements within the dataset.
@@
 The radius of gyration is a metric to distinguish mobility patterns of individuals~\citep{gonzalez2008}, which is defined as Eq. \eqref{eq:2}:
+
 \begin{equation} \label{eq:2}
@@
 \end{equation}
+
 \noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
-By examining the probability distributions of the radius of gyration, also known as the spatial dispersal kernel $P(r_g)$~\cite{brockmann2006}, we chose 10 km as the cell size to quantify the spatial coverage of the majority of Twitter users in Great Britain (Fig.~\ref{S4_Fig} - c, with details shown in the next section).
+By examining the probability distributions of the radius of gyration, also known as the spatial dispersal kernel $P(r_g)$~\citep{brockmann2006}, we chose 10 km as the cell size at the national level of Great Britain (Fig.~\ref{S4_Fig} - c, with details shown in the next section).
+More importantly, as 10 km is the distinct geographic distance for separating two main groups of Twitter users in terms of the spatial coverage in Great Britain, a 10-km size cell serves as a mask to partitioning the space.
+In this way, we can focus on the inter-connections among different urban regions with less attention to movements around a user's neighborhood (i.e., within 10 km radius), such as home or work places.
 Thus, we created a fishnet with 2784 10-km size cells.
@@
 
-\subsection{Community structure of the spatial networks}
-Based on the derived spatial network, which is a directed weighted graph, we further determined clusters of strongly connected spatial nodes, known as communities, in the graph space~\citep{coscia2011}.
+\subsection{Community structure of the network of spatial interactions}
+Based on the derived mobility network of spatial interactions, which is a directed weighted graph, we further determined clusters of strongly connected spatial nodes, known as communities, in the graph space~\citep{coscia2011}.
 There are a variety of community detection algorithms that produce different results depending the definition of community within the network~\citep{coscia2011}.
@@
 \subsection{Distance decay effects with a gravity model}
+As it is mentioned above, the clusters of urban regions in the form of communities in the network space often yield geographically cohesive urban areas. 
+This phenomenon is speculated to be related to the distance decay effects, where the interaction strength between two urban regions decreases as the geographical distance between them increases.
+A gravity model is often used to express such relations, as is shown in Eq.
+\eqref{eq:3}, where $<T_{ij}>$ and $d_{ij}$ denote the interaction from i to j and distance between two places, $K$ is a constant, and $P_{i}$ and $P_{j}$ are the population size of place $i$ and $j$ respectively.
+The interaction strength decreases with respect to the geographic distance is expressed by the distance decay function, $f(d_{ij})$, where the parameter $\beta$ reveals the distance impact on interaction strength.
+A greater $\beta$ indicates faster decay effects and the interaction strength is more influenced by distance~\citep{liu2014}.
+While it is suggested that population size may be an accurate indicator to describe the repulsion or attractiveness between places, the gravity model is usually fit by using observed interaction strength and the distance between geographical entities~\citep{liu2014}.
 \begin{equation} \label{eq:3}
@@
 \end{equation}
+
+In this study, the main purpose for adopting the gravity model is not to find the best $\beta$ value to estimate the potential interaction strength among depicted urban areas.
+Interestingly, the distance decay effects are also found in human mobility patterns~\citep{zhao2016}, the authors argue that it is due to the constraints of complex urban structure.
+In this study, in line with the idea that urban environments are conceptualized spaces that are recreated and formed by human activities~\citep{schliephake}, we speculate that the distance decay effects in affecting the interaction strength of two geographic regions and ultimately depicting the urban structures (e.g., urban boundaries), is contributed by (or related to) the distance decay parameters found in the underlying mobility patterns.
+In particular, since we have used a mobility network of spatial interactions, if our hypothesis stands, it will provide strong support that the depicted urban boundaries are not random artifacts but indeed reflect how people move across geographic regions.
 
@@
 \begin{center}
-\includegraphics[width=0.8\linewidth]{./figure/S6_community_london}
+\includegraphics[width=0.7\linewidth]{./figure/S6_community_london}
 \caption{{\bf The non-administrative anthropographic regions inferred from Twitter user displacements greater than 4 km (left) and 10 km (right) in comparison with major cities in England (upper figures) and Scotland (bottom figures).}  Each color represents a unique community.
@@
 Yet, our approach is still applicable when more detailed mobility data is available.
+
+The purpose of trip
+contextualizing
 
@@
 
+\bibitem[\protect\citeauthoryear{Tsou}{2015}]{tsou2015}
+Tsou, M.H., 2015. Research challenges and opportunities in mapping social media and Big Data. Cartography and Geographic Information Science, 42(sup1), pp.70-74.
+
 \bibitem[\protect\citeauthoryear{Vasardani {\itshape{et~al.}}}{2013}]{vasardani2013}
@@
 Zhao, K., Musolesi, M., Hui, P., Rao, W., and Tarkoma, S., 2015. Explaining the power-law distribution of human mobility through transportation modality decomposition. Scientific reports, 5.
+
+\bibitem[\protect\citeauthoryear{Zhao {\itshape{et~al.}}}{2016}]{zhao2016}
+Zhao, Z., Shaw, S.L., Xu, Y., Lu, F., Chen, J.
+and Yin, L., 2016.
+Understanding the bias of call detail records in human mobility research.
+International Journal of Geographical Information Science, 30(9), pp.1738-1762.
 

### 2016-07-11 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
home

@@
 In this study, in line with the idea that urban environments are conceptualized spaces that are recreated and formed by human activities~\citep{schliephake}, we speculate that the distance decay effects in affecting the interaction strength of two geographic regions and ultimately depicting the urban structures (e.g., urban boundaries), is contributed by (or related to) the distance decay parameters found in the underlying mobility patterns.
-In particular, since we have used a mobility network of spatial interactions, if our hypothesis stands, it will provide strong support that the depicted urban boundaries are not random artifacts but indeed reflect how people move across geographic regions.
+In particular, since we have used a mobility network of spatial interactions, if this hypothesis stands, it will provide strong support that the depicted urban boundaries are not random artifacts but indeed reflect how people move across geographic regions.
 
@@
 
-We found that the cumulative distribution function of the number of locations visited by each Twitter user follows a two-tier power law distribution (shown in Fig.~\ref{S3_Fig}). 
+We found that the cumulative distribution function of the number of locations visited by each Twitter user follows a two-tier power law distribution (Fig.~\ref{S3_Fig}). 
 The majority of the data follow a truncated power-law distribution $P(X\geq x)\sim x^{-\alpha}e^{-\lambda x}$, where $\alpha = 1.24, \lambda =0.00132$; and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $P(X \geq x)\sim x^{-\alpha}$ with $\alpha$ value is 3.2.
@@
 
-We further studied two aspects of the Twitter user mobility patterns: the distribution of Twitter user displacement and the radius of gyration. 
+We then studied two aspects of the Twitter user mobility patterns: the distribution of Twitter user displacement and the radius of gyration. 
 Twitter user displacement refers to the distance between two consecutive locations in a user's trajectory using a straight-line distance metric.
@@
 (1) and (2) account for approximately 53$\%$ of all users.  
-The radius of gyration between 30m and 100km can be further approximated by two power law distributions with a cut-off point at 2.5km (35 $\%$ users with radius of gyration less than 2.5km and 57$\%$ users with radius of gyration between 3km and 100km) that suggests two main types of spatial coverage of Twitter user movement within
-Great Britain. 
 Note that the accuracy of these values for defining the distance bound depends upon the accuracy of the location information of each geo-located tweet. 
@@
 \begin{figure}[ht]
-\includegraphics[width=1.0\linewidth]{./figure/S4_radius_displacement}
-\caption{{\bf The probability distribution of Twitter user displacements and radius of gyration:} (a) The displacement distribution $P(d)$ is approximated by an exponential, a stretched-exponential and a power-law function (b) the distance between [70m, 70km] is approximated by a double power-law functions (c) The distribution of radius of gyration $P(r_g)$ is approximated by the combination of an exponential, a stretched-exponential and a power-law function (d) the distance between [30m, 100 km] is approximated by a double power-law functions}
+\includegraphics[width=0.9\linewidth]{./figure/S4_radius_displacement}
+\caption{{\bf The probability distribution of Twitter user displacements and radius of gyration:} (a) $P(d)$ is approximated by an exponential, a stretched-exponential and a power-law function (b) the distance between [70m, 70km] is approximated by a double power-law functions (c) $P(r_g)$ is approximated by the combination of an exponential, a stretched-exponential and a power-law function.
+(The green patch shows the distance range)}
 \label{S4_Fig}
@@
 \subsection{Redrawing Great Britain's Urban Boundaries}
-The network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells that provide an adequate resolution for a country wide investigation~\citep{ratti2010}.
+The mobility network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells, where 10 km is the distinct geographic distance for separating two main groups of Twitter users in terms of the spatial coverage (i.e., radius of gyration) in Great Britain.
+The cells of the fishnet act as proxies to represent individuals' spatial coverage areas to focus more on the inter-connectivity among cells and identify strongly connected cell clusters.
+It provides an adequate resolution for a country wide investigation~\citep{ratti2010}.
 The edges of this network were derived from the number of directed Twitter user displacements between each pair of cells.
@@
 
+\subsection{Explaining the Distance decay effects with the gravity model}
+The results of strongly connected urban regions in the form of communities in the mobility network of Twitter user spatial interactions yield geographically cohesive, non-overlapping urban areas. 
+While it provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain, the reasons on why they are geographically cohesive and non-overlapping or why the boundaries stop/emerge at certain spatial extend that leads to different size of the urban areas are not clear.
+As the depicted urban boundaries exhibited a strong instance of spatial proximity, we adopt the gravity model (Eq.
+\eqref{eq:3}) to explain how distance decay effects found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas.
+
+In this case, the distance between two derived urban areas is measured by the geodetic distance between the centroid locations of the two.
+
 \begin{figure}[ht]
@@
 \includegraphics[width=0.7\linewidth]{./figure/Gravity}
-\caption{{\bf The observed interaction strength versus the estimated ones from the adopted gravity model with $\bf{\beta}$ = 0.8 } Note that }
+\caption{{\bf The observed interaction strength versus the estimated ones from the adopted gravity model with $\bf{\beta}$ = 0.8 } Note that the $\beta$ value is taken from the probability density function of radius of gyration when $r_{g} > 10 km$.
+The red dash line indicate strong linear correlation between the estimated and observed interaction strength with $R^{2}$ = 0.89 and $p-value < 0.01$.}
 \label{S8_Fig}

### 2016-07-11 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
good night

@@
 The results of strongly connected urban regions in the form of communities in the mobility network of Twitter user spatial interactions yield geographically cohesive, non-overlapping urban areas. 
-While it provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain, the reasons on why they are geographically cohesive and non-overlapping or why the boundaries stop/emerge at certain spatial extend that leads to different size of the urban areas are not clear.
-As the depicted urban boundaries exhibited a strong instance of spatial proximity, we adopt the gravity model (Eq.
-\eqref{eq:3}) to explain how distance decay effects found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas.
+While it provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain, the reasons on why they are geographically cohesive and non-overlapping or why the boundaries stop/emerge at certain spatial extent that leads to different size of the urban areas are not clear.
+As the depicted urban boundaries exhibit a strong instance of spatial proximity, the gravity model is employed (Eq.
+\eqref{eq:3}) to explain how distance decay effects found in the mobility patterns affect the interaction strength among non-administrative anthropographic urban areas.
 
-In this case, the distance between two derived urban areas is measured by the geodetic distance between the centroid locations of the two.
+In this model, the distance between two derived urban areas is measured by the geodetic distance between the centroid locations of the two.
+As it is mentioned above,  $P_{i}$ and $P_{j}$  are the observed interaction between urban area $i$ and $j$, which are measured by the aggregation of movement flux in each urban area.
+In particular, we set the distance decay parameter $\beta$ value as 0.8: (1) As we hypothesize that the distance decay parameters found in the underlying mobility patterns potentially contribute to $\beta$ in the gravity model (2) and we have chosen the 10-km cell size based on the collective Twitter user mobility pattern regarding radius of gyration, where the distance decay parameter is 0.8 when radius of gyration $r_{g} > 10 km$ (Fig.~\ref{S4_Fig}(c)).
+We found that the gravity model indicates strong linear correlation between the observed versus the estimated interaction strength with $R^{2}$ = 0.89 and $p-value < 0.01$.
+This confirms that the depicted urban areas are results of spatial proximity effects, where the strength of human (in this case, Twitter user) spatial interaction between two urban regions decreases as the geographic distance between them increases.
+More importantly, since we have used a mobility network to delineate the boundaries, the distance decay effects are well related and explained by the underlying mobility patterns.
+In return, the well fitted gravity model provides support that the depicted urban areas are not random artifacts but indeed reflect how people move across geographic regions.
 
@@
 \section{Conclusion and Discussion}
-Talk about interplay between human mobility
-
 In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
@@
 
-The purpose of trip
-contextualizing
+%Talk about interplay between human mobility 
+%The purpose of trip
+%contextualizing
 

### 2016-07-13 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
docx

@@
 Many studies started to look into the demographic information of LBSM data, in particular Twitter data~\citep{steiger2015,luo2016}. 
-While the used methods varies, these studies suggest that the mentioned issues require us to pose more strict criteria in filtering and extracting individual movements.
+While the used methods vary, these studies suggest that the mentioned issues require us to pose stricter criteria in filtering and extracting individual movements.
 
@@
 The detailed literatures and implementations of Infomap can be found on this website ({\tt{http://mapequation.org}}).
-Note that Infomap is capable of performing multi-level community detection~\cite{domenico2015}, but we only use the algorithm to produce our most detailed community structures
+Note that Infomap is capable of performing multi-level community detection~\citep{domenico2015}, but we only use the algorithm to produce our most detailed community structures
 to examine groups of strongly connected urban regions.

### 2016-07-22 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
xx
images

@@
 \begin{abstract}
-Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter-regional activities.
-Defining urban boundaries with considerations of socio-economic relationships and citizen commute patterns is important for many aspects in urban planning.
-In this study, we presented a method to redraw urban boundaries based upon human interaction with the physical space.
+Existing urban boundaries are usually defined by government agencies for political and administrative purposes.
+However, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter-regional activities.
+Defining urban boundaries which consider socio-economic relationships and citizen commute patterns is important for many aspects of urban planning.
+In this study, we presented a method to redraw urban boundaries based upon human interactions with the physical space.
 Specifically, we depicted the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million geo-located Twitter messages.
@@
 
-A common outcome observed from the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
-The general consensus is that those geographically cohesive areas are instances of spatial proximity effects, where the interaction strength between two urban regions decreases as the geographical distance between them increases~\citep{fotheringham1981}.
+A common outcome observed in the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
+A general consensus is that those geographically cohesive areas are instances of the effects on spatial proximity, where the interaction strength between two urban regions decreases as the geographical distance between them increases~\citep{fotheringham1981}.
 In particular, spatial proximity is closely related to Tobler's First Law of Geography: ``\textit{everything is related to everything else, but near things are more related than distant things}''~\citep{miller2004}.
-While it is intuitively logical, few research efforts were further carried out to quantitatively understand and explain how the spatial interactions shape the forms of connected geographical areas (i.e., urban boundaries).
+While it is perhaps intuitively logical, few research efforts, which seek to quantitatively understand and explain how the spatial interactions shape the forms of connected geographical areas (i.e., urban boundaries), have been carried out.
 One of the major reasons is that geographical distance may affect the interaction strength, it is not an explicitly expressed constraint in the ``virtual'' human interactions, such as social ties or phone call initiation.
@@
 \section{Background and Related Work}
-In real-world geography, urban regions are discrete individuals, with or without physical boundaries separating them~\citep{jiang2015}.
-For political and administrative purposes, government agencies define various sets of boundaries to partition the geographical space into spatial units at different scales, for instances, states, counties or census tracts and electoral districts.
-However, the spatial extents of these defined units often overlap and agglomerate depending how citizens perceive, organize their image of a city and interact with the urban environments~\citep{lynch1960}.
-As connections are made among these units via various human activities crossing the boarders, such as social-economic relations and commute patterns of citizens, certain groups of units are more strongly connected as clusters than others.
-The boundaries of the agglomeration of these units are argued to reflect how people naturally interact with the geographic space, which is important for city planning~\citep{hollenstein2010}, urban growth evaluations~\citep{jiang2015,long2015}, and traffic management~\citep{gao2014}.
+In real-world geography, urban regions are discrete components in a greater set of regions, with or without physical boundaries separating them~\citep{jiang2015}.
+For political and administrative purposes, government agencies define various sets of boundaries to partition the geographical space into spatial units at different scales, for instance: states, counties, census tracts, and electoral districts.
+However, the spatial extents of these units often overlap and agglomerate depending how citizens perceive, organize their image of a city, and interact with the urban environments~\citep{lynch1960}.
+As connections are made between these units via various human activities crossing boarders, such as social-economic relations and commute patterns of citizens, certain groups of units become more strongly connected than others.
+The boundaries of the agglomeration of these units are argued to reflect how people naturally interact with their geographical environment, which is important for city planning~\citep{hollenstein2010}, urban growth evaluations~\citep{jiang2015,long2015}, and traffic management~\citep{gao2014}.
+
 Empirical studies have attempted to delineate such boundaries with different methods and data sets.
-In general, the methods from existing literatures can be summarized into two, spatial clustering and network based, approaches.
-Spatial clustering based approaches determine the boundaries based the intensity of geographic locations related to human activities, for instances, locations of social media check-ins~\citep{cranshaw2012,jiang2015,sun2016}, place descriptions from crowd-sourced Web content~\citep{vasardani2013} and geo-tagged Flickr data~\citep{stefanidis2013,hu2016}.
-While interesting boundaries of urban areas were captured and delineated, the dynamic connections among different spatial units were not considered in the spatial clustering based approaches, where the results are discrete and independent areas reflecting high intensity of human activities.
+In general, the methods from existing literature can be summarized into two classes: spatial clustering and network based approaches.
+Spatial-clustering based approaches determine the boundaries based the intensity of geographic locations related to human activities, for instance: locations of social media check-ins~\citep{cranshaw2012,jiang2015,sun2016}, place descriptions from crowd-sourced Web content~\citep{vasardani2013}, and geo-tagged Flickr data~\citep{stefanidis2013,hu2016}.
+While notable boundaries of urban areas were identified and delineated, the dynamic connections between different spatial units were neglected in the spatial clustering based approaches, where the results are discrete and independent areas reflect a high intensity of human activities.
 
-On the other hand, network based approaches attempt to delineate urban boundaries based on the intensity of human interactions among different spatial units, where each spatial unit is treated as a node and the edge is modeled by human interactions between two nodes.
+On the other hand, network based approaches delineate urban boundaries based on the intensity of human interactions between different spatial units, where each spatial unit is treated as a node and the edge is modeled by human interactions between two nodes.
 Such human interactions can take physical or virtual forms, such as trade, commerce, social connections, and political activity across the borders.
-In terms of networks of virtual human spatial interactions, the connections between nodes are formed by virtual human relations, for examples, social ties of Twitter users are used to identify cohesive regions for different countries across the world~\citep{kallus2015}, and a map of Great Britain is redrew based the communication network of phone call initiations~\citep{ratti2010}.
-In contrast, physical human spatial interactions, the connections between nodes are formed by the collections of individuals physically allocating from one node to another, which is refereed as a mobility network of spatial interactions in this study.
-Many existing studies have attempted to extract the mobility network from various data sources, such as census migration data~\citep{rae2009}, GPS recorded vehicle~\citep{rinzivillo2012} and taxi trip records~\citep{liu2015}, mobile phone call data~\citep{sobolevsky2013,zhong2014}, and social media user movements from check-ins~\citep{liu2014} and geo-located Twitter data~\citep{hawelka,gao2014}.
-The networks of human spatial interactions are then further explored to reveal clusters regarding the intensities of the interaction strength, such as applying visual analytics methods~\citep{rae2009} or more popular community detection methods~\citep{coscia2011}.
+In terms of networks of virtual human spatial interactions, the connections between nodes are formed by virtual human relations, for example: social ties of Twitter users are used to identify cohesive regions for different countries across the world~\citep{kallus2015}, and a map of Great Britain is redrawn based the communication network of phone call initiations~\citep{ratti2010}.
+In contrast, physical human spatial interactions form the connections between nodes by the collections of individuals physically allocating from one node to another, which is referred to as a mobility network of spatial interactions in this study.
+Many existing studies have attempted to extract the mobility network from various data sources, such as census migration data~\citep{rae2009}, GPS recorded vehicle~\citep{rinzivillo2012} and taxi trip records~\citep{liu2015}, mobile phone call data~\citep{sobolevsky2013,zhong2014}, social media check-ins~\citep{liu2014}, and geo-located Twitter data~\citep{hawelka,gao2014}.
+These networks of human spatial interactions are then further explored to reveal clusters regarding the intensities of the interaction strength, for example, by applying visual analytics methods~\citep{rae2009} or community detection methods~\citep{coscia2011}.
 
 The clusters of urban regions in the form of communities in the network space yield geographically cohesive areas, in spite of different community detection methods and forms of human spatial interactions were used.
-Researchers argue that those geographically cohesive areas are related to the distance decay effects, where the interaction strength between two urban regions decreases as the geographical distance between them increases.
-However, few research efforts are carried out to explore the linkages between the spatial proximity effects and the characteristics of the underlying spatial interactions, which is critical for explaining how the spatial interactions shape the forms of connected geographical areas (i.e., urban boundaries).
+Researchers argue that those geographically cohesive areas are related to the distance decay effects, which implies that the interaction strength between two urban regions decreases as the geographical distance between them increases.
+However, few research efforts are carried out to explore the linkages between the spatial proximity effects and the characteristics of the underlying spatial interactions, which is critical for explaining how the spatial interactions affect the shapes of connected geographical areas (i.e., urban boundaries).
 While geographical distance is not explicitly expressed constraint in the ``virtual'' human interactions, we argue that seeking answers from the mobility network of spatial interactions with the characteristics of underlying mobility patterns can help to explain how distance decay effects affect the interaction strength and the shape of depicted urban boundaries.
@@
 To construct a large-scale mobility network of human spatial interactions, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
-The low-resolution mobility data collected from census records~\citep{rae2009} is estimated and aggregated at census tract level and do not necessarily reflecting movements of the same individuals.
-In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\citep{zheng2008}.
+The low-resolution mobility data collected from census records~\citep{rae2009} is estimated and aggregated at census tract level and does not necessarily reflect movements of the same individuals.
+In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce the most accurate records of individuals' movements, which means a high degree of recording accuracy of user locations and update frequency~\citep{zheng2008}.
 However, the data is often limited in spatial scale (e.g.
 within a specific city or region) with a small group of people, for example, 182 and 226 volunteers participated in collecting such mobility data in~\citep{zheng2008} and~\citep{rhee2011} respectively.
-Other than tracking people directly, the vehicle-based GPS data is often tied to a specific vehicle (e.g. taxi), which may only be accessible for a certain group of people~\citep{kung2014}. 
-Another popular mobility data source found in the literatures is the mobile phone call data in the form of Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\citep{gonzalez2008,kung2014,zhong2014}.
-Such a dataset can cover relatively large spatial scale (e.g., country level)~\citep{sobolevsky2013} and a large portion of the population in the study region~\citep{kung2014}. 
-However, due to the concerns of infringement on individual privacy, the mobile phone call data is not publicly accessible, which is not ideal  for conducting replicable scientific findings or comparisons across different regions.
+Other than tracking people directly, the vehicle-based GPS data is often tied to a specific vehicle (e.g. taxi), which may only be accessible to a limited group of people~\citep{kung2014}. 
+Another popular mobility data source found in academic literature is the mobile phone call data in the form of Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\citep{gonzalez2008,kung2014,zhong2014}.
+Such a dataset can cover relatively large spatial scale (e.g., national level)~\citep{sobolevsky2013} and a large portion of the population in the study region~\citep{kung2014}. 
+However, due to the concerns of infringement on individual privacy, the mobile phone call data is not publicly accessible, which is not ideal for the replicability in scientific findings or comparisons across different regions.
 
-In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
+On the other hand, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from the Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
 This is also evident from the related studies mentioned above.
@@
 For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located tweet or check-in at a new place.
-It has been criticized for the lack of representativeness of the population as not all people use social media or send geo-located messages~\citep{kung2014}. 
-Another research challenge is to identify the users, as a social media account is not equal to a real person in the physical world~\citep{tsou2015}.
-Many studies started to look into the demographic information of LBSM data, in particular Twitter data~\citep{steiger2015,luo2016}. 
+LBSM data have also been criticized for lacking of representativeness of the population, as not all people use social media or send geo-located messages~\citep{kung2014}. 
+Another research challenge is to identify the users, as a social media account is not equivalent to a real person in the physical world~\citep{tsou2015}.
+Many studies have started to look into the demographic aspect of LBSM data, in particular Twitter data~\citep{steiger2015,luo2016}. 
 While the used methods vary, these studies suggest that the mentioned issues require us to pose stricter criteria in filtering and extracting individual movements.
@@
 \section{Materials and Methods}
-%\subsection{Overview}
-%In this research, we use large-scale Twitter user spatial interactions inferred from the collective mobility patterns of Twitter users to delineate urban boundaries in Great Britain.
-%A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\citep{gonzalez2008}.
-%This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two consecutive recorded locations is one month.
-%To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the islands of Great Britain.
-%Twitter user movements were then used to establish the connectivity between fishnet cells to form a connectivity network where each cell is considered a node within the network. 
-%Finally, by detecting strongly connected clusters in the network space using community detection methods~\citep{coscia2011}, we were able to reveal urban boundaries within the geographic space. 
-%An overview of the approach is illustrated in Fig.~\ref{S1_Fig} and the details are presented in the following sections. 
-%
-%\begin{figure}[ht]
-%\begin{center}
-%\includegraphics[width=1\linewidth]{./figure/S1_overview_Fig_2}
-%\caption{\bfseries{An overview for delineating urban boundaries from Twitter user movements}}
-%\label{S1_Fig}
-%\end{center}
-%\end{figure}
-
 \subsection{Geo-located Twitter Data and Data Processing}
@@
 \end{figure}
-Because the original location information embedded in the geo-tag is given in units of latitude and longitude, we projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations.
+The original location information embedded in the geo-tag is given in units of latitude and longitude.
+We projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations. 
 We used the geographical boundary of Great Britain, which is derived from Office for National Statistics (ONS) of UK ({\tt{http://www.ons.gov.uk/ons}}), to further restrict the remaining tweets to be ``domestic".
@@
 To reduce the effects of tweets from non-human users, the raw tweets were further filtered using the following steps.
-First we removed the duplicated messages in the dataset.
+First we removed the duplicated messages from the dataset.
 We then removed non-human users based on unusual relocation speed \citep{hawelka,jurdak2015}. 
-We examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold of 240 m/s as used by \citep{jurdak2015}.
+We then examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold of 240 m/s as used by \citep{jurdak2015}.
 Finally, to reflect the spatial interactions of residents rather than tourists, we further impose a condition that the time interval between a user's first and last recorded tweets should be more than 30 days.
@@
 This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two consecutive recorded locations is one month.
-To identify the clusters of urban regional connectedness, Twitter user movements are used to establish a connectivity network, where two urban region connects when a twitter user's movement begins in one and ends in another.
+To identify the clusters of urban regional connectedness, Twitter user movements are used to establish a connectivity network, where two urban regions connect when a Twitter user's movement begins in one and ends in another.
 These connections can be represented by an origin-destination (OD) matrix based on the collective Twitter user displacements within the dataset.
@@
 However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\citep{sakaki2010,zandbergen2009}.
-Another popular approach is to partition the space into a grid of spatial pixels~\citep{liuPopMobility,ratti2010}.
+Another approach is to partition the space into a grid of spatial pixels~\citep{liuPopMobility,ratti2010}.
 However, the size of the cell can potentially lead to biases due to the Modifiable Area Unit Problem (MAUP)~\citep{openshaw1984,wong2009}, where different choices of unit size can lead to significant variant findings.
 To compare our investigation with the findings of similar studies, and avoid subjectively deciding the cell size, we performed statistical analysis of Twitter user mobility patterns in Great Britain and measured the distribution of collective Twitter user displacements and the radius of gyrations of individuals \citep{gonzalez2008,jurdak2015}.
-The radius of gyration is a metric to distinguish mobility patterns of individuals~\citep{gonzalez2008}, which is defined as Eq. \eqref{eq:2}:
+The radius of gyration is a metric to distinguish mobility patterns of individuals~\citep{gonzalez2008}, which is defined as Eq. \eqref{eq:1}:
 
-\begin{equation} \label{eq:2}
+\begin{equation} \label{eq:1}
 r_{g} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(p_{i} -  p_{centroid})^{2}}, \textrm{where}\hspace{1ex} p_{centroid} = \frac{1}{n}\sum_{i=1}^{n}p_{i}
@@
 
-\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
+\noindent This measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
 By examining the probability distributions of the radius of gyration, also known as the spatial dispersal kernel $P(r_g)$~\citep{brockmann2006}, we chose 10 km as the cell size at the national level of Great Britain (Fig.~\ref{S4_Fig} - c, with details shown in the next section).
@@
 \subsection{Community structure of the network of spatial interactions}
-Based on the derived mobility network of spatial interactions, which is a directed weighted graph, we further determined clusters of strongly connected spatial nodes, known as communities, in the graph space~\citep{coscia2011}.
+Based on the derived mobility network of spatial interactions, which is a directed weighted graph, we further determined clusters of strongly connected spatial nodes, known as communities, in the graph space.
 There are a variety of community detection algorithms that produce different results depending the definition of community within the network~\citep{coscia2011}.
@@
 It identifies communities by minimizing the expected description length of the trajectory of a random walker, which is shown below:
-\begin{equation} \label{eq:1}
+\begin{equation} \label{eq:2}
 L(M)=qH(Q) + \sum_{i=1}^{m} p_{i}H(p_{i})
 \end{equation}
-In Eq. \eqref{eq:1} , $L(M)$ consists of two terms: qH(Q) is the entropy of the movement among clusters and $ \sum_{i=1}^{m} p_{i}H(p_{i})$ is the entropy of movement within clusters. 
-To be more specific, q is the probability that a random walker jumps from one cluster to another, while $p_i$ is the probability of the in-cluster movement of cluster i.
-In this regard, this algorithm can be intuitively tailored to describe strongly connected clusters of urban regions based on Twitter user movement.
+In Eq.\eqref{eq:2}, $L(M)$ consists of two terms: qH(Q) is the entropy of the movement among clusters and $ \sum_{i=1}^{m} p_{i}H(p_{i})$ is the entropy of movement within clusters. 
+Specifically, q is the probability that a random walker jumps from one cluster to another, while $p_i$ is the probability of the in-cluster movement of cluster i.
+This algorithm can be intuitively tailored to describe strongly connected clusters of urban regions based on Twitter user movement.
 The detailed literatures and implementations of Infomap can be found on this website ({\tt{http://mapequation.org}}).
-Note that Infomap is capable of performing multi-level community detection~\citep{domenico2015}, but we only use the algorithm to produce our most detailed community structures
-to examine groups of strongly connected urban regions.
+Note that Infomap is capable of performing multi-level community detection~\citep{domenico2015}, but we only use this algorithm to produce our most detailed community structures in order to examine groups of strongly connected urban regions.
 
 \subsection{Distance decay effects with a gravity model}
-As it is mentioned above, the clusters of urban regions in the form of communities in the network space often yield geographically cohesive urban areas. 
+As mentioned above, the clusters of urban regions in the form of communities in the network space often yield geographically cohesive urban areas. 
 This phenomenon is speculated to be related to the distance decay effects, where the interaction strength between two urban regions decreases as the geographical distance between them increases.
@@
 \eqref{eq:3}, where $<T_{ij}>$ and $d_{ij}$ denote the interaction from i to j and distance between two places, $K$ is a constant, and $P_{i}$ and $P_{j}$ are the population size of place $i$ and $j$ respectively.
-The interaction strength decreases with respect to the geographic distance is expressed by the distance decay function, $f(d_{ij})$, where the parameter $\beta$ reveals the distance impact on interaction strength.
-A greater $\beta$ indicates faster decay effects and the interaction strength is more influenced by distance~\citep{liu2014}.
+The interaction strength decreasing with respect to increasing geographic distance is expressed by the distance decay function, $f(d_{ij})$, where the parameter $\beta$ reveals the distance impact on interaction strength.
+A greater $\beta$ indicates stronger decay and the interaction strength is more influenced by distance~\citep{liu2014}.
 While it is suggested that population size may be an accurate indicator to describe the repulsion or attractiveness between places, the gravity model is usually fit by using observed interaction strength and the distance between geographical entities~\citep{liu2014}.
@@
 The majority of the data follow a truncated power-law distribution $P(X\geq x)\sim x^{-\alpha}e^{-\lambda x}$, where $\alpha = 1.24, \lambda =0.00132$; and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $P(X \geq x)\sim x^{-\alpha}$ with $\alpha$ value is 3.2.
-The distribution was found to be consistent over all individual months examined (June to December, 2014), which has a slight offset in the truncated power-law distribution (the mean $\alpha$ value is 1.26 $ \pm$ with a 0.05 $\sigma$ and the mean $\lambda$ value as 0.00134 $ \pm$  with a 0.0002 $\sigma$).
+The distribution was found to be consistent over each month examined (June to December, 2014), which has a slight offset in the truncated power-law distribution (the mean $\alpha$ value is 1.26 $ \pm$ with a 0.05 $\sigma$ and the mean $\lambda$ value as 0.00134 $ \pm$  with a 0.0002 $\sigma$).
 
 The two-tier power law distribution indicates that the collective behavior of Twitter users visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk (a random walk) model~\citep{rhee2011,reynolds2012}, which has also been identified in many human mobility studies using different mobility data~\citep{zhao2015}.
-The similarity among the distributions suggests that the mobility data collected from geo-located tweets is temporally stable, at least at the monthly interval, which indicates that our approach using Twitter user mobility to delineate urban boundaries is viable.
+The similarity among the distributions suggests that the mobility data collected from geo-located tweets is temporally stable, at least at monthly intervals, which indicates that our approach using Twitter user mobility to delineate urban boundaries is viable.
 In addition, the L\'{e}vy Walk model reveals the diversity regarding the number of visited locations per user, which indicates a level of ``randomness'' in Twitter user movement across space. 
@@
 \begin{figure}[ht]
-\includegraphics[width=0.9\linewidth]{./figure/S4_radius_displacement}
-\caption{{\bf The probability distribution of Twitter user displacements and radius of gyration:} (a) $P(d)$ is approximated by an exponential, a stretched-exponential and a power-law function (b) the distance between [70m, 70km] is approximated by a double power-law functions (c) $P(r_g)$ is approximated by the combination of an exponential, a stretched-exponential and a power-law function.
+\includegraphics[width=1.0\linewidth]{./figure/S4_radius_displacement_3}
+\caption{{\bf The probability distribution of Twitter user displacements and radius of gyration:} (a) $P(d)$ is approximated by an exponential, a stretched-exponential and a power-law function (b) the distance between [70m, 70km] is approximated by a double power-law functions (c) $P(r_g)$ of Great Britain is approximated by the combination of an exponential, a stretched-exponential and a power-law function.
+(d) $P(r_g)$ of London is approximated an exponential and a stretched-exponential function.
 (The green patch shows the distance range)}
@@
 Fig.~\ref{S5_Fig}  presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4km, greater than 10 km, and using all available displacements together compared to the administrative boundaries of Great Britain.
-One clear observation across the coarse and fine delineations is that most of the geographic divisions are centered around big urban cores with relatively high populations.
+One clear observation in both the coarse and fine delineations is that most of the geographic divisions are centered around big urban cores with relatively high populations.
 These results are expected given that most of the tweets originate in urban centers.
@@
 
-\clearpage
-\section{Conclusion and Discussion}
+%\clearpage
+\section{Discussions}
+
+\section{Conclusion}
 In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
@@
 \markboth{}{International Journal of Geographical Information Science}
-
 \bibitem[\protect\citeauthoryear{Blanford {\itshape{et~al.}}}{2015}]{blanford2015}
-Blanford, J.I., Huang, Z., Savelyev, A. and MacEachren, A.M., 2015. Geo-located tweets. enhancing mobility maps and capturing cross-border movement. PloS one, 10(6), p.e0129202.
+Blanford, J.I., Huang, Z., Savelyev, A. and MacEachren, A.M., 2015. Geo-located tweets. enhancing mobility maps and capturing cross-border movement. PLoS ONE, 10(6), p.e0129202.
 
 \bibitem[\protect\citeauthoryear{Brockmann {\itshape{et~al.}}}{2006}]{brockmann2006}
-Brockmann, D., Hufnagel, L., Geisel, T., 2006. The scaling laws of human travel. Nature 439, pp. 462-465. doi:10.1038/nature04292
+Brockmann, D., Hufnagel, L., Geisel, T., 2006. The scaling laws of human travel. Nature 439, pp. 462-465.
 
@@
 Physical Review X, 5.
-doi:10.1103/PhysRevX.5.011027
 
 \bibitem[\protect\citeauthoryear{Fortunato and Barthélemy}{2007}]{fortunato2007}
-Fortunato, S., Barthélemy, M., 2007. Resolution limit in community detection. Proceedings of the National Academy of Sciences, 104, pp. 36-41. doi:10.1073/pnas.0605965104
+Fortunato, S., Barthélemy, M., 2007. Resolution limit in community detection. Proceedings of the National Academy of Sciences, 104, pp. 36-41.
 
@@
 
-\bibitem[\protect\citeauthoryear{Frank {\itshape{et~al.}}}{2013}]{frank2013}
-Frank, M.R., Mitchell, L., Dodds, P.S. and Danforth, C.M., 2013. Happiness and the patterns of life: A study of geolocated tweets. Scientific reports, 3.
+%\bibitem[\protect\citeauthoryear{Frank {\itshape{et~al.}}}{2013}]{frank2013}
+%Frank, M.R., Mitchell, L., Dodds, P.S. and Danforth, C.M., 2013. Happiness and the patterns of life: A study of geolocated tweets. Scientific reports, 3.
 
@@
 \bibitem[\protect\citeauthoryear{González {\itshape{et~al.}}}{2008}]{gonzalez2008}
-González, M.C., Hidalgo, C.A., Barabási, A.-L., 2008. Understanding individual human mobility patterns. Nature, 453, pp. 779-782. doi:10.1038/nature06958
+González, M.C., Hidalgo, C.A., Barabási, A.-L., 2008. Understanding individual human mobility patterns. Nature, 453, pp. 779-782.
 
 \bibitem[\protect\citeauthoryear{Good {\itshape{et~al.}}}{2010}]{good2010}
-Good, B.H., de Montjoye, Y.-A., Clauset, A., 2010. Performance of modularity maximization in practical contexts. Physical Review E, 81, 046106. doi:10.1103/PhysRevE.81.046106
+Good, B.H., de Montjoye, Y.-A., Clauset, A., 2010. Performance of modularity maximization in practical contexts. Physical Review E, 81, 046106.
 
 \bibitem[\protect\citeauthoryear{Guimerà {\itshape{et~al.}}}{2004}]{guimera2004}
-Guimerà, R., Sales-Pardo, M., Amaral, L.A.N., 2004. Modularity from fluctuations in random graphs and complex networks. Physical Review E, 70, 025101. doi:10.1103/PhysRevE.70.025101
+Guimerà, R., Sales-Pardo, M., Amaral, L.A.N., 2004. Modularity from fluctuations in random graphs and complex networks. Physical Review E, 70, 025101.
 
@@
 260-271.
-doi:10.1080/15230406.2014.890072
 
@@
 \bibitem[\protect\citeauthoryear{Jurdak {\itshape{et~al.}}}{2015}]{jurdak2015}
-Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D., 2015. Understanding Human Mobility from Twitter. PLoS ONE 10, e0131469. doi:10.1371/journal.pone.0131469
+Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D., 2015. Understanding Human Mobility from Twitter. PLoS ONE 10, e0131469.
 
 \bibitem[\protect\citeauthoryear{Kallus {\itshape{et~al.}}}{2015}]{kallus2015}
-Kallus Z, Barankai N, Szüle J, Vattay G., 2015.
-Spatial Fingerprints of Community Structure in Human Interaction Network for an Extensive Set of Large-Scale Regions.
-PLoS ONE 10(5): e0126713.
-doi: 10.1371/journal.pone.0126713
+Kallus Z, Barankai N, Szüle J, Vattay G., 2015. Spatial Fingerprints of Community Structure in Human Interaction Network for an Extensive Set of Large-Scale Regions. PLoS ONE 10(5): e0126713.
 
 \bibitem[\protect\citeauthoryear{Kung {\itshape{et~al.}}}{2014}]{kung2014}
-Kung, K.S., Greco, K., Sobolevsky, S. and Ratti, C., 2014. Exploring universal patterns in human home-work commuting from mobile phone data. PloS one, 9(6), p.e96180.
+Kung, K.S., Greco, K., Sobolevsky, S. and Ratti, C., 2014. Exploring universal patterns in human home-work commuting from mobile phone data. PLoS ONE, 9(6), p.e96180.
 
 \bibitem[\protect\citeauthoryear{Lancichinetti and Fortunato}{2009}]{lancichinetti2009}
-Lancichinetti, A., Fortunato, S., 2009. Community detection algorithms: A comparative analysis. Physical Review E, 80, 056117. doi:10.1103/PhysRevE.80.056117
+Lancichinetti, A., Fortunato, S., 2009. Community detection algorithms: A comparative analysis. Physical Review E, 80, 056117.
 
@@
 \bibitem[\protect\citeauthoryear{Liu {\itshape{et~al.}}}{2015}]{liu2015}
-Liu, X., Gong, L., Gong, Y., Liu, Y., 2015. Revealing travel patterns and city structure with taxi trip data. Journal of Transportation Geography, 43, pp. 78-90. doi:10.1016/j.jtrangeo.2015.01.016
+Liu, X., Gong, L., Gong, Y., Liu, Y., 2015. Revealing travel patterns and city structure with taxi trip data. Journal of Transportation Geography, 43, pp. 78-90.
 
@@
 \bibitem[\protect\citeauthoryear{Newman}{2006}]{newman2006}
-Newman, M.E.J., 2006. Modularity and community structure in networks. Proceedings of the National Academy of Sciences, 103, pp. 8577-8582. doi:10.1073/pnas.0601602103
+Newman, M.E.J., 2006. Modularity and community structure in networks. Proceedings of the National Academy of Sciences, 103, pp. 8577-8582.
 
@@
 PLoS ONE 5, e14248.
-doi:10.1371/journal.pone.0014248
 
@@
 \bibitem[\protect\citeauthoryear{Rinzivillo {\itshape{et~al.}}}{2012}]{rinzivillo2012}
-Rinzivillo, S., Mainardi, S., Pezzoni, F., Coscia, M., Pedreschi, D., Giannotti, F., 2012.
-Discovering the Geographical Borders of Human Mobility.
-KI - Künstl.
-Intelligenz, 26, pp.
-253-260.
-doi:10.1007/s13218-012-0181-8
+Rinzivillo, S., Mainardi, S., Pezzoni, F., Coscia, M., Pedreschi, D., Giannotti, F., 2012. Discovering the Geographical Borders of Human Mobility. KI - Künstl. Intelligenz, 26, pp. 253-260.
 
 \bibitem[\protect\citeauthoryear{Rosvall {\itshape{et~al.}}}{2010}]{rosvall2010}
-Rosvall, M., Axelsson, D., Bergstrom, C.T., 2010. The map equation. The European Physical Journal Special Topics, 178, pp. 13–23. doi:10.1140/epjst/e2010-01179-1
+Rosvall, M., Axelsson, D., Bergstrom, C.T., 2010. The map equation. The European Physical Journal Special Topics, 178, pp. 13–23.
 
@@
 \bibitem[\protect\citeauthoryear{Sobolevsky {\itshape{et~al.}}}{2013}]{sobolevsky2013}
-Sobolevsky S, Szell M, Campari R, Couronné T, Smoreda Z, Ratti, C., 2013.
-Delineating Geographical Regions with Networks of Human Interactions in an Extensive Set of Countries.
-PLoS ONE 8(12): e81707.
-doi: 10.1371/journal.pone.0081707
+Sobolevsky S, Szell M, Campari R, Couronné T, Smoreda Z, Ratti, C., 2013. Delineating Geographical Regions with Networks of Human Interactions in an Extensive Set of Countries. PLoS ONE 8(12): e81707.
 
@@
 \bibitem[\protect\citeauthoryear{Thiemann {\itshape{et~al.}}}{2010}]{thiemann}
-Thiemann, C., Theis, F., Grady, D., Brune, R., Brockmann, D., 2010. The Structure of Borders in a Small World. PLoS ONE 5, e15422. doi:10.1371/journal.pone.0015422
+Thiemann, C., Theis, F., Grady, D., Brune, R., Brockmann, D., 2010. The Structure of Borders in a Small World. PLoS ONE 5, e15422.
 
@@
 \bibitem[\protect\citeauthoryear{Zandbergen}{2009}]{zandbergen2009}
-Zandbergen, P.A., 2009. Accuracy of iPhone Locations: A Comparison of Assisted GPS, WiFi and Cellular Positioning. Transactions in GIS, 13, pp. 5-25. doi:10.1111/j.1467-9671.2009.01152.x
+Zandbergen, P.A., 2009. Accuracy of iPhone Locations: A Comparison of Assisted GPS, WiFi and Cellular Positioning. Transactions in GIS, 13, pp. 5-25.
 
@@
 International Journal of Geographical Information Science, 28, pp.
-2178-2199, doi:10.1080/13658816.2014.914521
-
+2178-2199.
 \end{thebibliography}

### 2016-07-22 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
discussion part

@@
 Further, we analyzed the distribution of radius of gyration to understand the movement from the point of view of individual Twitter users rather than separate displacements.
-The distribution of the radius of gyration can be approximated through a combination of three functions: $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10m$ from [10 m, 30m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50m, 10km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [10km, 100km], where these three functions account for 92$\%$ of all the users.
+The distribution of the radius of gyration of Twitter users in Great Britain can be approximated through a combination of three functions: $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10m$ from [10 m, 30m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50m, 10km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [10km, 100km], where these three functions account for 92$\%$ of all the users.
 This suggests that there are three primary types of users that: (1) tend to stay at one location or at nearby locations when they tweet, or (2) tend to move at the intra-city scale when they tweet, or (3)  tend to exhibit a large spatial coverage.
@@
 These findings are consistent with the findings in the literature on human mobility, where the radius of gyration of human movement is bounded to different distance ranges~\citep{brockmann2006,gonzalez2008}.
+In particular, the distribution of the radius of gyration of Twitter users over the greater London region can be fitted by similar functions.
+However, as it reflects intra-city level mobility patterns, there is no distinct distance range to indicate large spatial coverage.
 The distance-decay effects found in both user displacements and the radius of gyration shows evidence of spatial proximity in Twitter user movement. 

### 2016-07-23 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
temp

@@
 In this study, we presented a method to redraw urban boundaries based upon human interactions with the physical space.
-Specifically, we depicted the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million geo-located Twitter messages.
+Specifically, we depicted the urban boundaries of Great Britain using a mobility network of Twitter user spatial interactions that was inferred from over 69 million geo-located Twitter messages.
 We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
@@
 \includegraphics[width=0.9\linewidth]{./figure/S5_community}
-\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) displacements longer than 10 km (b) displacements shorter than 4 km (c) and displacements longer than 4 km (d) The partition of space was done using a 10 km fishnet to map the directed displacements from and to each cell.
+\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) all displacements with $L = 7.79$.
+(b) displacements longer than 10 km ($L=xx$) (c) displacements shorter than 4 km ($L=xx$) (d) and displacements longer than 4 km ($L=xx$).The partition of space was done using a 10 km fishnet to map the directed displacements from and to each cell.
 Each color represents a unique community with more Twitter users displacements among the cells compared to others.
@@
 A more detailed study was conducted over the greater London region revealing the intra-city spatial interaction patterns.
+
 The spatial partitions derived from a fine grid of 1km using all available Twitter user trips without any restriction on trip distances yields geographic boundaries comparable to some of London's boroughs  (Fig.~\ref{S7_Fig}).
@@
 \section{Discussions}
+In this study,
 
@@
 \end{thebibliography}
-
 \bibliographystyle{tGIS}
-%\bibliography{Twitter_Urban_Boundary}
-
 \label{lastpage}

### 2016-07-24 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
conclusions and discussions

@@
 \subsection{Redrawing Great Britain's Urban Boundaries}
-The mobility network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells, where 10 km is the distinct geographic distance for separating two main groups of Twitter users in terms of the spatial coverage (i.e., radius of gyration) in Great Britain.
+The mobility network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells, where 10 km is the distinct geographic distance for separating two main groups of Twitter users in terms of the spatial coverage (i.e., radius of gyration) in Great Britain (see Fig.~\ref{S4_Fig} - c).
 The cells of the fishnet act as proxies to represent individuals' spatial coverage areas to focus more on the inter-connectivity among cells and identify strongly connected cell clusters.
@@
 A more detailed study was conducted over the greater London region revealing the intra-city spatial interaction patterns.
-
-The spatial partitions derived from a fine grid of 1km using all available Twitter user trips without any restriction on trip distances yields geographic boundaries comparable to some of London's boroughs  (Fig.~\ref{S7_Fig}).
+Since the captured Twitter user movements were on intra-city level (in comparison to the national level in Fig.~\ref{S4_Fig}-c), there was no distinct distance range to separate Twitter user spatial coverage in terms of radius of gyration (see Fig.~\ref{S4_Fig}-d).
+We chose 1-km cell size as referred from the related literature~\citep{liu2015}, which suggested 1-km cell size is detailed enough to depict urban structures.
+The spatial partitions derived from a fine grid of 1km used all available Twitter user trips without any restriction on trip distances yields geographic boundaries comparable to some of London's boroughs  (Fig.~\ref{S7_Fig}).
 However, some areas are shown to be more cohesive and display greater spatial interactions across the administrative boundaries, for instance, central London.

### 2016-07-24 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
add

@@
 The probability distributions of the collective user displacement $P(d)$ and radius of gyration $P(r_g)$ are presented in Fig.~\ref{S4_Fig}, where the fitting method for identifying different distance ranges is derived from~\citep{jurdak2015}.
-The probability distribution of the collective displacements can be approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10m, 70m] (accounting for 3 $\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [70m, 70km] (93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 70km] (4 $\%$ of the population).
+The probability distribution of the collective displacements can be approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10m, 70m] (accounting for 3$\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [70m, 70km] (93$\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 70km] (4$\%$ of the population).
 The displacement distance between 70m and 100km can be further approximated by two power law distributions with a cut-off point at 4km (55$\%$ distances are less than 4km and 40$\%$ distances between 4km and 100km), which indicates the urban movement captured by the geo-located Twitter data to reveal two different modes: inter-city and intra-city movement.

### 2016-07-26 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
home

@@
 \includegraphics[width=0.9\linewidth]{./figure/S5_community}
-\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) all displacements with $L = 7.79$.
-(b) displacements longer than 10 km ($L=xx$) (c) displacements shorter than 4 km ($L=xx$) (d) and displacements longer than 4 km ($L=xx$).The partition of space was done using a 10 km fishnet to map the directed displacements from and to each cell.
+\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) all displacements with $L = 7.8$.
+(b) displacements longer than 10 km ($L=8.5$) (c) displacements shorter than 4 km ($L=4.5$) (d) and displacements longer than 4 km ($L=8.1$).The partition of space was done using a 10 km fishnet to map the directed displacements from and to each cell.
 Each color represents a unique community with more Twitter users displacements among the cells compared to others.
-Major cities (urban audit functional areas) and NUTS are displayed in black.}
+Major cities (urban audit functional areas) and NUTS are displayed as labels.}
 \label{S5_Fig}
@@
 \includegraphics[width=0.7\linewidth]{./figure/S7_london}
-\caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.
+\caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs ($L=8.1$)}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.
 Each unique color represents a different non-administrative anthropographic region.
-Notice that some remote regions like the airport (light green region in south of Hillingdon) share the same class with downtown because it is well connected despite the geographic separation.}
+Notice that some remote regions like the airport (light purple region in south of Hillingdon) share the same class with downtown because it is well connected despite the geographic separation.}
 \label{S7_Fig}
@@
 
-\subsection{Explaining the Distance decay effects with the gravity model}
+\subsection{Distance decay effects with a gravity model}
 The results of strongly connected urban regions in the form of communities in the mobility network of Twitter user spatial interactions yield geographically cohesive, non-overlapping urban areas. 
 While it provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain, the reasons on why they are geographically cohesive and non-overlapping or why the boundaries stop/emerge at certain spatial extent that leads to different size of the urban areas are not clear.
-As the depicted urban boundaries exhibit a strong instance of spatial proximity, the gravity model is employed (Eq.
+As the depicted urban boundaries exhibit a strong instance of spatial proximity, a gravity model is employed (Eq.
 \eqref{eq:3}) to explain how distance decay effects found in the mobility patterns affect the interaction strength among non-administrative anthropographic urban areas.
@@
 %\clearpage
-\section{Discussions}
-In this study,
+\section{Conclusion and Discussion}
+In this study, we presented a method to delineate the non-administrative anthropographic urban boundaries in Great Britain using a mobility network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
+In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the islands of Great Britain to partition the space.
+To avoid deciding the cell size arbitrarily, we studied the probability distributions of the radius of gyrations of individual Twitters users and selected 10-km as the cell size, which is the distinct geographic distance for separating two main groups of Twitter users in terms of the spatial coverage at the national level.
+In addition, this choice allows us to focus on the inter-connections among different urban regions with less attention to movements around a user's neighborhood (i.e., within 10 km radius), such as home or work places.
 
-\section{Conclusion}
-In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
-In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the islands of Great Britain to partition the space.
-By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell size of 10 km to quantify the spatial coverage of the majority of Twitter users in Great Britain.
+Supplement Materials section 1
+
 Twitter user movements were used to establish a connectivity network of the fishnet cells.

### 2016-07-26 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
Tonight

@@
 %\clearpage
-\section{Conclusion and Discussion}
+\section{Discussion}
+However, the geo-located twitter data is not able to generalize to the entire population; therefore, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
+Yet, our approach is still applicable when more detailed mobility data is available.
+
+\section{Conclusion}
 In this study, we presented a method to delineate the non-administrative anthropographic urban boundaries in Great Britain using a mobility network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
 In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the islands of Great Britain to partition the space.
-To avoid deciding the cell size arbitrarily, we studied the probability distributions of the radius of gyrations of individual Twitters users and selected 10-km as the cell size, which is the distinct geographic distance for separating two main groups of Twitter users in terms of the spatial coverage at the national level.
-In addition, this choice allows us to focus on the inter-connections among different urban regions with less attention to movements around a user's neighborhood (i.e., within 10 km radius), such as home or work places.
-
-Supplement Materials section 1
+To avoid deciding the cell size arbitrarily, we studied the probability distributions of the radius of gyrations of individual Twitters users and selected 10-km as the cell size, which is the distinct geographic distance for separating two main groups of Twitter users in terms of their spatial coverage at the national level.
+In addition, this choice enables us to focus on the inter-connections among different urban regions with less attention to movements around a user's neighborhood (i.e., within 10 km radius), such as home or work places.
+The probability distributions of the radius of gyration for Twitter users in the Great Britain are verified to be consistent across different monthly time span, (see Supplement Materials section 1), which indicates the stability of using such measurements in this study.
+It is worth noting that using
 
@@
 This study provides a first step in connecting human mobility research with defining non-administrative anthropographic boundaries, which could assist in resource allocation, political campaigns and urban planning.
-However, the geo-located twitter data is not able to generalize to the entire population; therefore, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
-Yet, our approach is still applicable when more detailed mobility data is available.
 

### 2016-07-28 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
new

@@
 \articletype{RESEARCH ARTICLE}
-
-%\title{{\itshape The geography of urban boundaries in Great Britain from the mobility network of Twitter user spatial interactions} }
-%\title{{\itshape Depict the geography of urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data} }
 \title{{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data} }
@@
 The original location information embedded in the geo-tag is given in units of latitude and longitude.
+We examined the \textit{``geo"} attribute in each raw tweet and kept the one with location information derived from GPS receiver (with high resolution) rather than from geocoding process~\citep{jurdak2015}.
 We projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations. 
@@
 \section{Discussion}
-However, the geo-located twitter data is not able to generalize to the entire population; therefore, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
+It is worth noting that constructing a mobility network of spatial interaction using geo-located Twitter data has some potential concerns.
+First, the geo-located Twitter data is not able to generalize to the entire population.
+The demographic information of the Twitter users cannot be easily identified, therefore, the result of delineated urban boundaries may not reflect a complete real-world image from human movements.
+The urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
+Related studies have been carried out to examine the demographic information in geo-located Twitter data~\citep{steiger2015,luo2016}, which should be considered in future studies.
+Nevertheless, since this study focus on the connections made through Twitter user movements between urban regions, the concern of spatial sparseness of geo-located Twitter data may cause .
+
+we visualized the mobility flux of Twitter user movements using the method mentioned in~\citep{rae2009}(see Supplement Materials section 1).
+The outcome showed that the Twitter user movements in this study connect most urban areas in Great Britain and clearly exhibited long and short distance movements.
+In this connection, geo-located Twitter data demonstrated its applicability for this study, along with the large spatial coverage and easy data accessibility as mentioned above.
+In addition,
+
+The probability distributions of the radius of gyration for Twitter users in the Great Britain are verified to be consistent across different monthly time span, (see Supplement Materials section 1), which indicates the stability of using such measurements in this study.
+
 Yet, our approach is still applicable when more detailed mobility data is available.
@@
 In addition, this choice enables us to focus on the inter-connections among different urban regions with less attention to movements around a user's neighborhood (i.e., within 10 km radius), such as home or work places.
-The probability distributions of the radius of gyration for Twitter users in the Great Britain are verified to be consistent across different monthly time span, (see Supplement Materials section 1), which indicates the stability of using such measurements in this study.
-It is worth noting that using
 
@@
 This study provides a first step in connecting human mobility research with defining non-administrative anthropographic boundaries, which could assist in resource allocation, political campaigns and urban planning.
-
-%Talk about interplay between human mobility 
-%The purpose of trip
-%contextualizing
+One final remark from this study is that we
 
@@
 
-%\bibitem[\protect\citeauthoryear{Frank {\itshape{et~al.}}}{2013}]{frank2013}
-%Frank, M.R., Mitchell, L., Dodds, P.S. and Danforth, C.M., 2013. Happiness and the patterns of life: A study of geolocated tweets. Scientific reports, 3.
-
 \bibitem[\protect\citeauthoryear{Gao {\itshape{et~al.}}}{2014}]{gao2014}
@@
 
-\bibitem[\protect\citeauthoryear{Huang {\itshape{et~al.}}}{2016}]{huang2016}
+\bibitem[\protect\citeauthoryear{Huang {\itshape{et~al.}}}{2016}]{2016}
 Huang, Q.

### 2016-07-31 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
Conclusion

--- 2016-07-26 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
@@
 \includegraphics[width=0.9\linewidth]{./figure/S5_community}
-\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) all displacements with $L = 7.8$.
-(b) displacements longer than 10 km ($L=8.5$) (c) displacements shorter than 4 km ($L=4.5$) (d) and displacements longer than 4 km ($L=8.1$).The partition of space was done using a 10 km fishnet to map the directed displacements from and to each cell.
+\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) all displacements with $L(M)= 7.8$.
+(b) displacements longer than 10 km ($L(M)=8.5$) (c) displacements shorter than 4 km ($L(M)=4.5$) (d) and displacements longer than 4 km ($L(M)=8.1$).The partition of space was done using a 10 km fishnet for the directed displacements from and to each cell.
 Each color represents a unique community with more Twitter users displacements among the cells compared to others.
@@
 \includegraphics[width=0.7\linewidth]{./figure/S7_london}
-\caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs ($L=8.1$)}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.
+\caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs ($L(M)=8.1$)}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.
 Each unique color represents a different non-administrative anthropographic region.
@@
 \section{Discussion}
-However, the geo-located twitter data is not able to generalize to the entire population; therefore, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
-Yet, our approach is still applicable when more detailed mobility data is available.
+It is worth noting that constructing a mobility network of spatial interaction using geo-located Twitter data has some potential concerns to limit the results from this study.
+First, the geo-located Twitter data is not able to generalize to the entire population.
+As the demographic information of the Twitter users cannot be easily identified, the results of delineated urban boundaries may not reflect a complete real-world image from human movements. 
+The demographics of Twitter users in this study can be an under/over-representation of the all overall population in Great Britain.
+Related studies have been carried out to examine the demographic information in geo-located Twitter data~\citep{steiger2015,luo2016}, which should be carefully considered in future studies.
+Second, regarding the concern of spatial sparseness of geo-located Twitter data~\citep{steiger2015}, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
+To investigate whether this limited the ability to capture the connections made through Twitter user movements between urban regions, we visualized the flows of Twitter user movements using the method mentioned in~\citep{rae2009}(see Supplement Materials section 1).
+The outcome showed that the Twitter user movements in this study connected most urban areas in Great Britain and clearly exhibited long and short distance movements, where was essential for investigating the connection strength between urban regions.
+Third, since the collective radius of gyration was used to determine the cell-size in the network, we examined the temporal stability for the measurement in the geo-located Twitter data.
+The probability distributions of the radius of gyration for Twitter users in the Great Britain are verified to be consistent across different monthly time span, (see Supplement Materials section 2), which indicates the stability of using such measurements in this study.
+Finally, as the geo-located Twitter data offers easy data accessibility, the methods in this study can be reproduced for other countries. 
+Along with the large sample size and spatial coverage, geo-located Twitter data demonstrated its applicability for this study.
+
+A major component in this study was imposing a virtual fishnet to partition the geographic space over Great Britain.
+We should be aware that using different approaches to partitioning the space will produce different mobility networks, and can potentially lead 
+to different delineations of the urban boundaries.
+Indeed, we had used the ward divisions as spatial units for aggregating Twitter user movements, which is the finest administrative boundaries of Great Britain (see Supplement Materials section 3).
+Without looking into the details of the results, the derived communities in the network space are similar to the ones from using fishnet approach.
+The strongly connected communities also yield geographically cohesive, non-overlapping urban areas.
+However, as the ward division is still defined by administrative purpose, the polygonal units tend to be geographically continuous.
+It causes problems to aggregate regions that do not have Twitter coverage into certain clusters.
+Aggregating Twitter user movements at the ward level also imposes more apparent concerns of the mismatch of the overall population, where less populated areas were overly represented and connected into large areas.
+These are the reasons why we chose a virtual fishnet approach for this study.
+
+As it is discussed above, we chose 10 km as the cell-size of the fishnet at national level in this study.
+We also carried out an experiment by arbitrarily setting the cell-size to 5 km at the national level (see Supplement Materials section 4).
+Note that the cell-size could be set to any value, such as 4.9 km or 5.1 km.
+The fishnet with smaller cell-size (i.e., 5 km) produced more and smaller strongly-connected communities within the network space.
+It indicates that the spatial resolution of the fishnet cells does affect the outcome from the community detection method employed in this study, where fishnet with smaller cell-size leads to more discrete and locally connected (i.e., smaller) clusters of urban areas.
+Such an effect can be explained by the probability distributions of the radius of gyrations of individual Twitter users.
+The probability of distance that deviates from a user's center location decays with a stretched-exponential function from [50m, 10km], which means the movements from Twitter users with smaller spatial coverage dominate the delineation of the connected urban areas.
+To avoid arbitrarily deciding the cell-size, we studied the probability distributions of the radius of gyrations of individual Twitter users and selected 10-km as the cell-size, which is the distinct geographic distance for separating two main groups of Twitter users in terms of their spatial coverage at the national level.
+In addition, this choice enabled us to focus on the inter-connections among different urban regions with less attention to movements around a user's neighborhood (i.e., within 10 km radius), such as home or work places.
+
+To apply the map equation algorithm, the mobility network should be organized as a weighted and directed graph, on which we confirmed an undirected graph cannot lead to a meaningful result (see Supplement Materials section 4).
+Since we used different physical movement ranges of users in delineating the urban boundaries, the description length $L(M)$ appeared to get larger when longer movement distances were used, which corresponded to less and larger geographically cohesive, non-overlapping urban areas.
+We believed that different movement ranges of users changed the weights of this graph and affected the interaction strength between two fishnet cells.
+As we have illustrated that the geographically cohesive, non-overlapping urban areas were instances of spatial proximity effects, where the gravity model model employed suggested the interaction strength between two fishnet cells decreases as the geographical distance increases, the longer movement distances were used, the larger $L(M)$ the map equation algorithm can maximize.
 
@@
 In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the islands of Great Britain to partition the space.
-To avoid deciding the cell size arbitrarily, we studied the probability distributions of the radius of gyrations of individual Twitters users and selected 10-km as the cell size, which is the distinct geographic distance for separating two main groups of Twitter users in terms of their spatial coverage at the national level.
-In addition, this choice enables us to focus on the inter-connections among different urban regions with less attention to movements around a user's neighborhood (i.e., within 10 km radius), such as home or work places.
-The probability distributions of the radius of gyration for Twitter users in the Great Britain are verified to be consistent across different monthly time span, (see Supplement Materials section 1), which indicates the stability of using such measurements in this study.
-It is worth noting that using
-
+By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell size of 10 km to quantify the spatial coverage of the majority of Twitter users in Great Britain.
 Twitter user movements were used to establish a connectivity network of the fishnet cells.
@@
 
-%Talk about interplay between human mobility 
-%The purpose of trip
-%contextualizing
+More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
+This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
+
+Yet, our approach is still applicable when more detailed mobility data is available.
+
+A final remark of this research
+
+More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
+This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
 
@@
 Fotheringham, A.S., 1981. Spatial structure and distance-decay parameters. Annals of the Association of American Geographers, 71(3), pp.425-436.
-
-%\bibitem[\protect\citeauthoryear{Frank {\itshape{et~al.}}}{2013}]{frank2013}
-%Frank, M.R., Mitchell, L., Dodds, P.S. and Danforth, C.M., 2013. Happiness and the patterns of life: A study of geolocated tweets. Scientific reports, 3.
 

### 2016-08-01 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
final

@@
 The well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas. 
-Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. 
-This provides a new understanding of the interactions between human activity and urban structures.
+Our study provides a first-step in connecting human mobility research with the delineation of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. 
+This provides a new understanding of the interactions between human activities and urban space.
 
@@
 This confirms that the depicted urban areas are results of spatial proximity effects, where the strength of human (in this case, Twitter user) spatial interaction between two urban regions decreases as the geographic distance between them increases.
-More importantly, since we have used a mobility network to delineate the boundaries, the distance decay effects are well related and explained by the underlying mobility patterns.
+More importantly, since we have used a mobility network to delineate the boundaries, the distance decay effects are well related and explained by the distance decay parameters found in the underlying mobility patterns.
 In return, the well fitted gravity model provides support that the depicted urban areas are not random artifacts but indeed reflect how people move across geographic regions.
@@
 The demographics of Twitter users in this study can be an under/over-representation of the all overall population in Great Britain.
-Related studies have been carried out to examine the demographic information in geo-located Twitter data~\citep{steiger2015,luo2016}, which should be carefully considered in future studies.
+Related studies have been carried out to examine the demographic information in geo-located Twitter data~\citep{steiger2015,luo2016,huang2016}, which should be carefully considered in future studies.
 Second, regarding the concern of spatial sparseness of geo-located Twitter data~\citep{steiger2015}, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
@@
 \section{Conclusion}
-In this study, we presented a method to delineate the non-administrative anthropographic urban boundaries in Great Britain using a mobility network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
-In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the islands of Great Britain to partition the space.
-By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell size of 10 km to quantify the spatial coverage of the majority of Twitter users in Great Britain.
+In this study, we presented a method that connected human mobility research with the delineation of the non-administrative anthropographic urban boundaries in Great Britain using a mobility network of Twitter user spatial interactions.
+In contrast to administrative urban boundaries, our ``bottom-up" approach imposed a virtual fishnet over the islands of Great Britain to partition the space.
+By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell-size of 10 km at the national level and 1 km for the greater London region.
 Twitter user movements were used to establish a connectivity network of the fishnet cells.
@@
 The power of using Twitter user mobility to delineate non-administrative anthropographic boundaries is the ability to redraw the city at different mobility ranges inferred objectively from the collective mobility patterns.
-Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect the human interaction space.
-This study provides a first step in connecting human mobility research with defining non-administrative anthropographic boundaries, which could assist in resource allocation, political campaigns and urban planning.
-
+Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect the human interactions with the geographical space.
 More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
-This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
-
-Yet, our approach is still applicable when more detailed mobility data is available.
-
-A final remark of this research
-
-More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
-This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
-
+This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activities and urban space.
+A final remark from this study for future studies is that geographical distance plays an important role in affecting human mobility patterns and the strength of human spatial interactions across space.
+Our approach can be considered to assist in understanding human spatial interactions from the mobility perspective, which is applicable for detailed geo-located Twitter data in different countries, as well as future mobility datasets with detailed location information of individuals and large spatial coverage.
 %\subsection{Acknowledgements}

### 2016-08-02 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
One more round

@@
 We believed that different movement ranges of users changed the weights of this graph and affected the interaction strength between two fishnet cells.
-As we have illustrated that the geographically cohesive, non-overlapping urban areas were instances of spatial proximity effects, where the gravity model model employed suggested the interaction strength between two fishnet cells decreases as the geographical distance increases, the longer movement distances were used, the larger $L(M)$ the map equation algorithm can maximize.
+As we have illustrated that the geographically cohesive, non-overlapping urban areas were instances of spatial proximity effects, where the gravity model model employed suggested the interaction strength between two fishnet cells decreases as the geographical distance increases, the longer movement distances were used, the larger $L(M)$ the map equation algorithm produces.
 

### 2016-08-05 MovePattern_IJGI/IJGI/Twitter_MovementPatterns_VisualAnalytics.tex
New

--- 2016-06-06 MovePattern_CAGIS/Twitter_MovementPatterns_VisualAnalytics.tex
@@
-\documentclass[a4paper, 11pt]{article}
-\usepackage{authblk}
-\usepackage[round, sort, numbers, authoryear]{natbib}
-\usepackage{regexpatch}
-\usepackage{graphicx}
-\graphicspath{ {/figures/} }
-\usepackage[section]{placeins}
-\usepackage{setspace}
-\usepackage[margin=1in]{geometry}
-\usepackage[]{algorithm2e}
-\usepackage{caption}
-\usepackage{subcaption}
-\date{}
+%  LaTeX support: latex@mdpi.com
+%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
 
-\usepackage{lineno}
-%\linenumbers
-%\bibpunct{(}{)}{;}{a}{,}{,}
-%\bibpunct{}{}{,}{s}{,}{,}
+% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.
 
-\begin{document}
-%\input{./Title.tex}
-\title{\itshape Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
-%\title{\itshape Exploring Multi-scale Spatiotemporal Twitter User Mobility Patterns Using Geo-located Twitter Data}
-	\author{}
-%	\author[1, 2, 3]{Junjun Yin}	
-%	\affil[1]{
-%	\it	CyberGIS Center for Advanced Digital and Spatial Studies
-%	}
-%	\affil[2]
-%	{
-%	\it	CyberInfrastructure and Geospatial Information Laboratory
-%	}
-%	\affil[3]
-%	{
-%	\it	Department of Geography and Geographic Information Science\authorcr
-%		\it	University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA
-%	}
+%=================================================================
+\documentclass[ijgi,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
 
-\maketitle
+%--------------------
+% Class Options:
+%--------------------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% actuators, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, atmosphere, atoms, axioms, batteries, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, challenges, chemosensors, children, chromatography, climate, coatings, computation, computers, condensedmatter, cosmetics, cryptography, crystals, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electronics, energies, entropy, environments, epigenomes, fermentation, fibers, fishes, fluids, foods, forests, futureinternet, galaxies, games, gels, genealogy, genes, geosciences, geriatrics, healthcare, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, inventions, jcdd, jcm, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, lubricants, machines, magnetochemistry, marinedrugs, materials, mathematics, mca, mti, medsci, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, nutrients, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, polymers, processes, proteomes, publications, recycling, religions, remotesensing, resources, risks, robotics, safety, sensors, separations, sexes, sinusitis, socsci, societies, soils, sports, standards, sustainability, symmetry, systems, technologies, toxics, toxins, universe, urbansci, vaccines, vetsci, viruses, water
+%---------
+% article
+%---------
+% The default type of manuscript is article, but can be replaced by: 
+% addendum, article, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimage, letter, newbookreceived, opinion, obituary, projectreport, reply, retraction, review, sciprints, shortnote, supfile, technicalnote
+% supfile = supplementary materials
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g.
+the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. If eps figure are used, remove the option pdftex and use LaTeX and dvi2pdf.
 
-%\makeatletter
-%\xpatchcmd{\@@cite}{\def\BCA##1##2{{\@BAstyle ##1}}}{\def\BCA##1##2{{\@BAstyle ##2}}}{}{}
-%\makeatother
-%
-\renewcommand{\baselinestretch}{1.5}
-%\renewcommand{\BBAA}{and}  % between authors in parenthetical cites and ref. list
-%\renewcommand{\BBAB}{and} % between authors in in-text citation
-%\renewcommand{\BAnd}{and}  % for ``Ed. \& Trans.'' in ref. list
+%=================================================================
+\firstpage{1} 
+\makeatletter 
+\setcounter{page}{\@firstpage} 
+\makeatother 
+\articlenumber{x}
+\doinum{10.3390/------}
+\pubvolume{xx}
+\pubyear{2016}
+\copyrightyear{2016}
+\externaleditor{Academic Editor: name}
+\history{Received: date; Accepted: date; Published: date}
+%------------------------------------------------------------------
+% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
+%\pdfoutput=1
 
-\pagenumbering{gobble}
-\onehalfspacing
-\section*{\begin{center}
-Abstract
-\end{center}}
-Understanding human mobility patterns is of great importance for urban planning, traffic management, and even marketing campaign.
+%=================================================================
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed
+
+%=================================================================
+%% Please use the following mathematics environments:
+ \theoremstyle{mdpi}
+ \newcounter{thm}
+ \setcounter{thm}{0}
+ \newcounter{ex}
+ \setcounter{ex}{0}
+ \newcounter{re}
+ \setcounter{re}{0}
+
+ \newtheorem{Theorem}[thm]{Theorem}
+ \newtheorem{Lemma}[thm]{Lemma}
+ \newtheorem{Corollary}[thm]{Corollary}
+ \newtheorem{Proposition}[thm]{Proposition}
+
+ \theoremstyle{mdpidefinition}
+ \newtheorem{Characterization}[thm]{Characterization}
+ \newtheorem{Property}[thm]{Property}
+ \newtheorem{Problem}[thm]{Problem}
+ \newtheorem{Example}[ex]{Example}
+ \newtheorem{ExamplesandDefinitions}[ex]{Examples and Definitions}
+ \newtheorem{Remark}[re]{Remark}
+ \newtheorem{Definition}[thm]{Definition}
+%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
+
+%=================================================================
+% Full title of the paper (Capitalized)
+\Title{Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
+
+% Authors, for the paper (add full first names)
+\Author{Junjun Yin $^{1}$ and Zhenhong Du $^{2}$*}
+% Authors, for metadata in PDF
+\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}
+
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA ; jyn@illinois.edu\\
+$^{2}$ \quad Key Laboratory of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou, 310028, China; duzhenhong@zju.edu.cn}
+
+% Contact information of the corresponding author
+\corres{Correspondence: duzhenhong@zju.edu.cn; Tel.: +8613819192989}
+
+% Current address and/or shared authorship
+
+% Simple summary
+%\simplesumm{}
+
+% Abstract (Do not use inserted blank lines, i.e. \\) 
+\abstract{Understanding human mobility patterns is of great importance for urban planning, traffic management, and even marketing campaign.
 However, the capability of capturing detailed human movements with fine-grained spatial and temporal granularity is still limited.
@@
 In particular, the Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals have revealed multi-scale or multi-modal Twitter user mobility patterns.
-By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
-\newline
+By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.}
 
-\noindent\textbf{Keywords:} Geo-located tweets, mobility patterns, multi-scale spatiotemporal analysis, scalable visual-analytics framework\\
-\cleardoublepage
+% Keywords
+\keyword{Geo-located tweets, mobility patterns, multi-scale spatiotemporal analysis, scalable visual-analytics framework}
+\begin{document}
 
-\pagenumbering{arabic}
-\setcounter{page}{1}
-\onehalfspacing
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Sections that are not mandatory are listed as such. The section titles given are for Articles. Review papers and other article types have a more flexible structure.
 
+%% Only for the journal Gels: Please place the Experimental Section after the Conclusions
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\citep{zheng2008understanding}, traffic management~\citep{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\citep{belik2011natural}.
+Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\citep{belik2011natural}.
 Earlier research efforts relied on low resolution mobility data to understand human mobility patterns, such as using census records to understand human migration patterns~\citep{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\citep{brockmann2006scaling}.
@@
 \end{figure}
-\FloatBarrier
+%\FloatBarrier
 
@@
 \end{figure}\textbf{}
-\FloatBarrier
+%\FloatBarrier
 
@@
 
-With this framework, we have found some interesting Twitter user mobility patterns, both statically and visually.
+With this framework, we have found some interesting Twitter user mobility patterns, both statistically and visually.
 We studied the collective Twitter user visiting behavior regarding the frequency of Twitter users visiting different locations, which was fitted by a two-tier power-law distribution function.
@@
 
-%\section*{Acknowledgements}
-%Removed for review process.
-\cleardoublepage
-%\bibliographystyle{apacitex}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+\supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
 
-\bibliographystyle{apalike}
-\bibliography{Ref}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\acknowledgments{All sources of funding of the study should be disclosed.
+Please clearly indicate grants that you have received in support of your research work.
+Clearly state if you received funds for covering the costs to publish in open access.}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
+The following statements should be used ``X.X.
+and Y.Y.
+conceived and designed the experiments; X.X.
+performed the experiments; X.X.
+and Y.Y.
+analyzed the data; W.W.
+contributed reagents/materials/analysis tools; Y.Y.
+wrote the paper.'' Authorship must be limited to those who have contributed substantially to the work reported.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\conflictofinterests{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
+Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
+If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliographystyle{mdpi}
+\bibliography{lite}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{document}

### 2016-08-05 MovePattern_IJGI/template.tex
New

--- 2016-08-05 MovePattern_IJGI/IJGI/Twitter_MovementPatterns_VisualAnalytics.tex
@@
 %=================================================================
-\documentclass[ijgi,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
+\documentclass[journal,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
 
@@
 % Full title of the paper (Capitalized)
-\Title{Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
+\Title{Title}
 
 % Authors, for the paper (add full first names)
-\Author{Junjun Yin $^{1}$ and Zhenhong Du $^{2}$*}
+\Author{Firstname Lastname $^{1,\dagger,\ddagger}$, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}
 % Authors, for metadata in PDF
@@
 \address{%
-$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA ; jyn@illinois.edu\\
-$^{2}$ \quad Key Laboratory of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou, 310028, China; duzhenhong@zju.edu.cn}
+$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
+$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}
 
 % Contact information of the corresponding author
-\corres{Correspondence: duzhenhong@zju.edu.cn; Tel.: +8613819192989}
+\corres{Correspondence: e-mail@e-mail.com; Tel.: +x-xxx-xxx-xxxx}
 
 % Current address and/or shared authorship
+\firstnote{Current address: Affiliation 3} 
+\secondnote{These authors contributed equally to this work.}
 
@@
 % Abstract (Do not use inserted blank lines, i.e. \\) 
-\abstract{Understanding human mobility patterns is of great importance for urban planning, traffic management, and even marketing campaign.
-However, the capability of capturing detailed human movements with fine-grained spatial and temporal granularity is still limited.
-In this study, we have extracted high-resolution mobility data from a collection of 1.3 billion geo-located Twitter messages to study multi-scale spatiotemporal Twitter user mobility patterns in the United States during the year 2014.
-Regarding the concerns of infringement on individual privacy, such as the mobile phone call data with restricted access, the dataset is collected from publicly accessible Twitter data streams.
-In this study, we have developed a scalable visual-analytics framework to deliver efficiency and scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-scale spatiotemporal user mobility patterns.
-We have performed a set of statistical analysis to understand Twitter user mobility patterns across multi-level spatial scales and temporal granularity.
-In particular, the Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals have revealed multi-scale or multi-modal Twitter user mobility patterns.
-By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.}
+\abstract{A single paragraph of about 200 words maximum.
+For research articles, abstracts should give a pertinent overview of the work.
+We strongly encourage authors to use the following style of structured abstracts, but without headings: 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations.
+The abstract should be an objective representation of the article: it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}
 
 % Keywords
-\keyword{Geo-located tweets, mobility patterns, multi-scale spatiotemporal analysis, scalable visual-analytics framework}
+\keyword{keyword 1; keyword 2; keyword 3. List three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.}
+
+% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
+%\PACS{J0101}
+%\MSC{}
+%\JEL{}
+
+% If this is an expanded version of a conference paper, please cite it here: enter the full citation of your conference paper, and add $^\S$ in the end of the title of this article.
+%\conference{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Data:
+
+%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
+If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
+In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
+
+%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\setcounter{section}{-1} %% Remove this when starting to work on the template.
+\section{How to Use this Template}
+
+The template details the sections that can be used in a manuscript.
+Sections that are not mandatory are listed as such.
+The section titles given are for Articles.
+Review papers and other article types have a more flexible structure.
+For any questions, please contact the editorial office of the journal or support@mdpi.com.
+For LaTeX related questions please contact Janine Daum at latex-support@mdpi.com.
+
 \section{Introduction}
-Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\citep{belik2011natural}.
-Earlier research efforts relied on low resolution mobility data to understand human mobility patterns, such as using census records to understand human migration patterns~\citep{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\citep{brockmann2006scaling}.
-However, the lack of detailed human movements with fine-grained spatial and temporal granularity limits the findings to capture mobility patterns of individuals~\citep{gonzalez2008understanding,Jurdak2015}.
-In addition to the mobility data collected by GPS trackers~\citep{zheng2008understanding, rhee2011levy} and mobile phone call records~\citep{gonzalez2008understanding,sevtsuk2010does,kung2014exploring},
-emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints~\citep{thatcher2014living} in the form of real-world trails and footprints.
-One significant advantage of LBSM data streams is the large spatial coverage, for example, researchers have used geo-located Twitter data for studying global mobility patterns~\citep{hawelka2014geo}, which is otherwise impossible by using other mobility datasets (e.g., GPS traces and mobile phone call records).
-In addition, the publicly available LBSM data streams offer unique opportunities for conducting replicable scientific findings regarding the concerns of infringement on individual privacy, such as using mobile phone call records~\citep{giannotti2008mobility,crampton2014collect,Jurdak2015}.
 
-Many studies have adopted the LBSM data streams to study human mobility patterns.
-For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects~\citep{gonzalez2008understanding} in the collective user movements to reveal different travel modes~\citep{Jurdak2015}, travel demands~\citep{wu2014intra,hasan2013understanding}, and the impact of social connections~\citep{cho2011friendship}.
-These studies have provided strong support for using LBSM data as proxies for studying mobility patterns of individuals and valuable insights into human mobility dynamics. 
-However, in these studies, the measurements of distances are either fixed in a certain time period or a specific region, where they do not consider the variations of movements in different spatial scales and temporal ranges.
-To be more specific, these studies lack examinations of the detailed movements across different geographical scales and temporal granularity, for instances, whether there are temporal (e.g., monthly or seasonal) changes within the movements, and how the mobility patterns vary across different spatial scales (e.g., intra- or inter county, city or country level).
-These insights are critical to advance our understandings of the collective mobility patterns for a variety of applications, such as examining the mobility patterns across different cities~\citep{noulas2012tale}, the spread patterns of disease~\citep{balcan2009multiscale, tamerius2011global} and touristic activities~\citep{hawelka2014geo}.
-While the high resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data intensive challenges for developing a multi-scale spatiotemporal analysis framework~\citep{tsou2015} to deal with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales.
-In addition, to enable efficient analysis and visualization of the mobility patterns at different spatiotemporal scales, it is essential for such a framework to provide scalability for addressing the data intensive challenges~\citep{cao2014scalable}.
+The introduction should briefly place the study in a broad context and highlight why it is important.
+It should define the purpose of the work and its significance.
+The current state of the research field should be reviewed carefully and key publications should be cited.
+Please highlight controversial and diverging hypotheses when necessary.
+Finally, briefly mention the main aim of the work and highlight the main conclusions.
+As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
+Citing a journal paper \cite{ref-journal}.
+And now citing a book reference \cite{ref-book}.
 
-In this paper, we have explored and studied the Twitter user mobility patterns across multi-level spatial scales and temporal granularity in the United States during the year 2014. 
-The mobility data is extracted from1.3 billion geo-located Twitter messages (i.e., tweets) from 1$^{st}$ January to 31$^{st}$ December, 2014 in the United States with over 6 million Twitter users and over 1 TB in file size.
-To address the data-intensive challenges embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
-This framework is implemented based on high-performance distributed computing environment using Apache Hadoop\footnote{http://hadoop.apache.org/}, which is an open source software framework to enable distributed processing of large datasets across computing clusters.
-%We have implemented a set of efficient MapReduce~\citep{dean2008mapreduce} algorithms to deliver scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
-With this framework, we have performed a set of statistical analysis to understand the spatiotemporal Twitter user mobility patterns. 
-We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions. 
-In particular, the Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals~\citep{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\citep{Jurdak2015}.
-By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
 
-The remainder of this paper is organized as follows.
-Section 2 describes the related work in the context of studying mobility patterns using LBSM data, in particular, geo-located Twitter data.
-We focus on research challenges in visual-analytics methods to enable multi-scale
-spatiotemporal analysis with massive movement datasets, including data management, multi-level spatiotemporal user trajectory modeling and visualization.
-Section 3 details the processes for extracting, aggregating and summarizing multi-level spatiotemporal Twitter user mobility patterns.
-Section 4 presents the case study of performing visual-analytics for seeking Twitter mobility patterns in the United States of year 2014. Section 5 concludes the paper.
+This section may be divided by subheadings.
+It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
 
-\section{Mobility patterns in Location Based Social Media data}
-\subsection{Geo-located Twitter data for studying large-scale user movements}
-To understand detailed human mobility patterns of individuals, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
-However, the low-resolution mobility data collected from census records~\citep{greenwood1985human} is estimated and aggregated at census tract level, while tracking of bank notes~\citep{brockmann2006scaling} is at zip code level and do not necessarily reflecting movements of the same individuals~\citep{gonzalez2008understanding}.
-In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\citep{zheng2008understanding}.
-However, the data is often limited in spatial scale (e.g.
-within a specific city or region) with a small group of people, for example, 182 and 226 volunteers participated in collecting such mobility data in~\citep{zheng2010geolife} and~\citep{rhee2011levy} respectively.
-Other than tracking people directly, the vehicle-based GPS data is often tied to a specific vehicle (e.g.
-taxi), which may only be accessible for a certain group of people~\citep{kung2014exploring}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Subsection}
+\subsubsection{Subsubsection}
 
-Another approach from the literatures for studying human mobility is using mobile phone call data in the form of Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\citep{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
-Such a dataset can cover relatively large spatial scale (e.g., country level)~\citep{becker2013human,sobolevsky2013delineating} and a large portion of the population in the study region~\citep{kung2014exploring}.
-However, due to the concerns of infringement on individual privacy, the mobile phone call data is not publicly accessible, which is not ideal  for conducting replicable scientific findings, such as validating or extending the existing discoveries.
+Bulleted lists look like this:
+\begin{itemize}[leftmargin=*,labelsep=4mm]
+\item	First bullet
+\item	Second bullet
+\item	Third bullet
+\end{itemize}
 
-In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
-LBSM enables users to attach their current location as a geo-tag to the message they will post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\citep{Jurdak2015}.
-A Big Data scenario emerges when millions social media users constantly posting messages.
-However, there are some limitations and complexities in directly using the LBSM data for study human mobility patterns. 
-For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place.
-It has been criticized for the lack of representativeness of the population as not all people use social media or send geo-located messages~\citep{kung2014exploring}.
-Another research challenge is to identify the users, as a social media account is not equal to a real person in the physical world~\citep{tsou2015}.
-Although many studies started to look into the demographic information of LBSM data, in particular Twitter data~\citep{mitchell2013geography,longley2015geotemporal}, these issues certainly require us to pose more strict criteria in filtering and extracting individual movements.
+Numbered lists can be added as follows:
+\begin{enumerate}[leftmargin=*,labelsep=3mm]
+\item	First item
+\item	Second item
+\item	Third item
+\end{enumerate}
 
-In this study, geo-located Twitter data is chosen as source for studying detailed mobility patterns.
-Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
-It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\citep{cranshaw2012livehoods, hasan2013understanding}.
-In addition, it presents some unique advantages that make it suitable for studying human mobility patterns.
-For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\citep{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\citep{hawelka2014geo}, which is almost impossible for other mobility datasets.
-More importantly, by continuously monitoring the geo-located Twitter data streams with large volumes of detailed and frequently updated spatiotemporal  records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements).
+The text continues here.
 
-\subsection{Data-intensive challenges for multi-scale geo-visual analytics}
-Mobility data is essentially a collection of spatiotemporal records of people moving from one location to another in the geographic space.
-To study mobility patterns of individuals, a space-time trajectory of each individual should be modeled and constructed to quantify the collective movements over space and time.
-Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of displacements and radius of gyrations of individuals, to study the mobility dynamics.
-At the same time, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\citep{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal granularity.
-For example, a geo-visualization approach was used to study human activity patterns, where user trajectories are mapped in a 3D space ordered by timestamps in the third dimension~\citep{kwan2004geovisualization}.
-While such an approach enables visualization of detailed trajectories, its capability is limited in dealing with large-volume movement datasets~\citep{andrienko2007designing}.
-Instead of directly visualizing individual user trajectories, a space-time cube approach was proposed in analyzing and visualizing the collective trajectories by providing flexibilities in setting up both spatial and temporal ranges, and therefore to study the mobility patterns across different spatial units (e.g.
-countries, states, and cities, etc.) and identify the changes over space and time~\citep{maceachren2001research, maceachren2004maps}.
-In this connection, visual-analytics methods are proposed to help better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\citep{andrienko2007designing,andrienko2007visual}.
-Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\citep{andrienko2007designing}.
+\subsection{Figures, Tables and Schemes}
 
-Employing visual-analytics methods dealing with massive movement datasets is not only beneficial for optimizing visualizations but also provides a great deal of flexibilities for performing statistical analysis in seeking mobility patterns with different level of spatiotemporal details.
-By conveying the findings from statistical analysis, it provides another visualization form regarding the corresponding mobility patterns, in a sense, to avoid the problems of visual clutters.
-However, in the context of studying mobility patterns using large volume of geo-located Twitter data, the inherited large data volume poses significant data intensive challenges for these mentioned visual-analytics methods to scale with both the data volume and the computational requirements (e.g., movement extraction and trajectory modeling)~\citep{cao2014scalable}.
-For example, in our study, 1.3 billion geo-located tweets were collected with over 1 TB in file size.
-To construct a space-time trajectory of an individual, it is necessary to go through the massive dataset to sort and update the trajectory whenever a new location is found. 
-Such a task is already computationally demanding, let along breaking the trajectories to construct space-time cube with multiple spatial scale and temporal ranges. 
-In particular, developing a multi-scale spatiotemporal analysis framework is identified as one of the research challenges for dealing with social media Big Data~\citep{tsou2015}. 
-To address the data-intensive challenges, there is a need to develop a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
+All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
 
-%\subsection{Accommodating LBSM Big Data with Hadoop}
-%Apache Hadoop is an open source software framework designed to facilitate data intensive computing on large commodity clusters.
-%It combines a distributed file system, namely Hadoop Distributed File System(HDFS)~\citep{shvachko2010hadoop} with MapReduce programming paradigm, which can be applied to wide range of data-intensive problems.
-%MapReduce is a programming model and an associated software framework designed to process massive data in a distributed fashion~\citep{dean2008mapreduce}.
-%MapReduce breaks the entire computation into small tasks and schedule them among different computing nodes.
-%MapReduce consists of two main stages: map and reduce.
-%In the map stage, input data is converted into series of intermediate $\langle key, value\rangle$ pairs.
-%Customized computation will be performed in the reduce stage based on the same intermediate key.
-%This framework provides parallelization since both map and reduce tasks are considered independent and can be done in parallel.
-More importantly, it provides scalability in relation to the growth of data size, where Hadoop can scale to more computing nodes in the cluster to maintain the performance.
-%
-%Our framework benefits from using Hadoop in both data management and processing.
-%First, since the input data is large it is desirable to store it on multiple machines.
-%Second, by using Hadoop we can parallelize the computational tasks and make the data processing faster and more efficient.
-%Further, by adopting the MapReduce computing paradigm, we can model each individual user's trajectory by treating user's unique ID as key, and summarize the movement flows among different spatial units by utilizing the ID of the spatial unit as key.
-The details will be introduced in the following section.
+\begin{figure}[H]
+\centering
+%\includegraphics[width=3cm]{logo-mdpi}
+\caption{This is a figure, Schemes follow the same formatting.
+If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
+(\textbf{b}) Description of what is contained in the second panel.
+Figures should be placed in the main text near to the first time they are cited.
+A caption on a single line should be centered.}
+\end{figure}
 
+\begin{table}[H]
+\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
+\small % Font size can be changed to match table content. Recommend 10 pt.
+\centering
+\begin{tabular}{ccc}
+\toprule
+\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
+\midrule
+entry 1		& data			& data\\
+entry 2		& data			& data\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\subsection{Formatting of Mathematical Components}
+
+This is an example of an equation:
+
+\begin{equation}
+\mathbb{S}
+\end{equation}
+
+%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
+This ensures correct linenumbering.
+The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
+Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
+%% Example of a theorem:
+\begin{Theorem}
+Example text of a theorem.
+\end{Theorem}
+The text continues here. Proofs must be formatted as follows:
+
+%% Example of a proof:
+\begin{proof}[Proof of Theorem 1]
+Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
+\end{proof}
+The text continues here.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+
+This section may be divided by subheadings.
+Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
+The findings and their implications should be discussed in the broadest context possible.
+Future research directions may also be highlighted.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Materials and Methods}
-\subsection{Geo-located Twitter data}
-Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at. 
-In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
-To ensure complete coverage over the United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
-The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2GB in size) collected per day.
-We have collected more than 1.3 billion geo-located tweets from 1$^{st}$ January to 31$^{st}$ December, 2014 with 6,147,430 Twitter users and 1 TB in file size.
 
-As a social media account is not equal to a real person in the physical world~\citep{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed the duplicated messages\footnote{https://support.twitter.com/articles/18311-the-twitter-rules} in the dataset; and then we attempted to remove non-human users based on unusual relocating speed (Hawelka et al., 2014; Jurdak et al., 2015).
-In this case, we adopted the speed limit value as 240 m/s used in (Jurdak et al., 2015), where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
-Note that the original location information embedded in each geo-located tweet is given in units of latitude and longitude.
-To reduce the complexity in calculating distances and performing spatial aggregations directly based on geographical coordinates, we projected the all the points using North America Albers Equal Area Conic (ESRI:102008) coordinate system.
-Finally, we used the geographic boundaries of the United States\footnote{https://www.census.gov/geo/maps-data/data/} (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section.
-Based on these reinforcements, the dataset contains 1,052,861,000 tweets and 4,559,205 unique users.
+This section should be divided by subheadings.
+Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
+Please note that publication of your manuscript implicates that you must make all materials, data, and protocols associated with the publication available to readers.
+Please disclose at the submission stage any restrictions on the availability of materials or information.
+New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
 
-\subsection{A scalable visual-analytics framework}
-To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
-The scalable visual-analytics framework consists of two main units: (1) Data collection unit: a Twitter data crawler that continuously collects raw geo-located tweets using the Twitter Streaming API.
-(2) Data processing unit: a distributed computing environment using Apache Hadoop for modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing the movements at multiple spatiotemproal levels.
-An overall system architecture of the framework that chains the three units is shown in Figure 1. The details regarding the function and implementation of each unit are presented in the next sections.
+Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
+If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
+They must be provided prior to publication.
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.6\linewidth]{./figures/Overall_Architecture222}
-\caption{The overall system architecture of the framework}
-\label{fig:Arch}
-\end{figure}
-%\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions}
 
-\subsection{Space-time Twitter user trajectories}
-To derive meaningful mobility patterns of individuals, a space-time trajectory of each individual user should be constructed~\citep{hagerstrand1985time}.
-Each raw geo-located tweet contains multiple fields of information, such as the created time, country, language code, and location, etc.
-To construct a space-time trajectory from the data collection, we are interested in the following fields: \textit{User ID, location, timestamp}, which can be represented by a tuple $\left\langle id, loc, t\right\rangle$, where \textit{id} is a unique string representing a Twitter user's id; \textit{loc} is the recorded location of the message represented as a pair of projected coordinates $\left\langle x, y\right\rangle$;
-and \textit{t} is the timestamp of when the message was posted; A Twitter user's space-time trajectory is defined as follows.
-\newline
+This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
 
-\noindent\emph{\textbf{Definition 1.
-Space-time Twitter user trajectory:}} The space-time trajectory of a Twitter user is defined as a collection of recorded geo-locations in the chronological order (i.e., based on the attached timestamp):
-\newline
-
-$Trajectory_{user_{id}} \equiv \lbrace \langle id, loc_{1}, t_{1}\rangle, \langle id, loc_{2}, t_{2}\rangle, \langle id, loc_{i}, t_{i}\rangle, ...
-\langle id, loc_{n}, t_{n}\rangle \rbrace, i = 1, 2, 3...n$
-\newline
-
-To remove non-human users based on unusual relocating speed, a user will be removed if the speed between any two consecutive locations in the user's trajectory with $speed$ $(loc_{i} - loc_{i-1}) > 240 m/s $.
-\newline
-
-\noindent\emph{\textbf{Definition 2.
-visitation behavior, displacement and radius of gyration:}} As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers the frequency of a user visiting different locations within a specific time frame.
-This metric can provide an overall assessments regarding the diversity and similarity in the collective mobility pattern~\citep{gao2012exploring}.
-
-In particular, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\citep{gonzalez2008understanding}.
-The displacement refers to an individual's re-allocation in the geographical space measured in distance, i.e., $distance (loc_{i} - loc_{i-1})$.
-It is not equivalent to a ``trip" took by an individual, for example, even the time interval between two recorded locations is one month, it will still count as a displacement.
-By studying all the displacements from a group people, it helps to identify the distance bounds associated with different travel modes~\citep{Jurdak2015} or to determine whether movements are random walks~\citep{brockmann2006scaling}.
-Radius of gyration is a metric to distinguish mobility patterns of individuals~\citep{gonzalez2008understanding}, which is defined as fellows.   
-\newline
-
-$r_{g} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(p_{i} -  p_{centroid})^{2}}$, where $p_{centroid} = \frac{1}{n}\sum_{i=1}^{n}p_{i}$
-\newline
-
-\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
-When applying the measurements to all the users, it helps to identify different groups of people and understand the corresponding mobility patterns.
-Note that both displacements and radius of gyrations are measured by ``crow's fly distance" in this study (i.e., the direct distance between two recorded locations).
-Since all these metrics are based on the generated trajectories, by breaking and aggregating the trajectories in multiple spatial scales and temporal granularity, it would enable performing multi-level spatiotemporal analysis of these measurements and studying the corresponding mobility patterns.
-
-\subsection{Multi-level spatiotemporal trajectory aggregation}
-An important strategy for visual-analytics methods dealing with massive movement datasets is performing spatial aggregations to provide different levels-of-detail~\citep{andrienko2007designing,andrienko2007visual}.
-It is similar to the map generation approach that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest~\citep{buttenfield1991map}.
-To enable aggregating Twitter trajectories into multiple spatial levels, we have extended the hierarchical space-time cube model developed in~\citep{cao2014scalable}, where we partitioned the geographic space of the United States into 10 hierarchical spatial layers.
-To be specific, the state boundaries of the United States are treated as the base layer (i.e.
-level 0) for aggregating state-level Twitter user movements, Alaska and Hawaii are excluded for the consideration of better visualization effects in the mapping interface of the framework.
-We then created an hierarchical fishnet by diving the study region into regular cells, where the finest level (level 10) consists 1km $\times$ 1km cells.
-Such a cell size is consistent with the spatial resolution in landscan\footnote{http://web.ornl.gov/sci/landscan/} product for measuring the global population density.
-In our case, the cell size for level i-1 is twice of the size in level i.
-Figure 2 illustrates an hierarchical fishnet spatial units for mapping multi-level Twitter user movements.
-Note that any fine-grained geographic boundaries can be used and appended in this framework to show different level-of-detailed movements (e.g., county-level and census-tract level), in our case, we replaced the level 8 fishnet layer with the US county boundaries.
-
-To perform a multi-level spatial aggregation of the Twitter user trajectories using hierarchical spatial layers, each location in a user's trajectory is redistributed to the corresponding spatial units.
-A MapReduce algorithm for the spatial aggregation is implemented, where the ID of unit in each spatial layer (e.g., polygon in state and country layer and cell in the rest) is treated as key in the at the map stage.
-It performs a ``point-in-polygon" process to determine which polygon the point belongs to.
-If the location does not belong to any polygon, it will be dropped, which is how we used the geographic boundaries of the United States to filer the raw tweet collection and keep the ``domestic" ones.
-To optimize the ``point-in-polygon" determination without comparing the location with every polygon in the spatial layer, we also created a Quad-Tree~\citep{samet1984quadtree} for each spatial layer to speed up the process.
-Finally, the reducers generate two data outputs: (1) reconstructed space-time Twitter user trajectories at each spatial level (2) movement flows in the form of in and out volumes among the units.
-The movement flows are stored in the database for interactive explorations in the web mapping interface, whereas the re-constructed trajectories can be further processed to produce distance measures at different spatial scales, which is illustrated as fellows:
-\newline
-
-\noindent $Trajectory_{user_{id}} \equiv \lbrace \langle id, loc_{1}, t_{1}, unit_{1}\rangle, \langle id, loc_{2}, t_{2}, unit_{2}\rangle, \langle id, loc_{i}, t_{i}, unit_{i}\rangle, ...
-\langle id, loc_{n}, t_{n}, unit_{n}\rangle \rbrace$
-where $ i = 1, 2, 3...n$
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.6\linewidth]{./figures/multilevel}
-\caption{Hierarchical spatial layers for aggregating movements in different level-of-details}
-\label{fig:multilevel}
-\end{figure}
-%\FloatBarrier
-
-\section{Multi-scale spatiotemporal Twitter user mobility patterns}
-\subsection{Spatiotemporal Twitter user mobility patterns}
-The situation of using geo-located tweets to track people's movements is complex as users' tweeting behavior can be significantly different from one to another, in particular the frequency and time-interval between two consecutive tweets.
-For example, some people may tweet once a day while others do more; some people may tweet regularly while others do not.
-These tweeting behaviors are expected as such human dynamics are also seen in the mobile phone call data~\citep{gonzalez2008understanding}. 
-Many studies have carried out data collection within a certain time period (e.g., a year in our case).
-However, as the geo-located tweets were collected in a continuous fashion, we need to examine the sensitivities regarding these behaviors to make sure we are not just capturing a random snapshot from the whole data streams.
-
-In this study, we have analyzed the cumulative distribution of the frequency Twitter users visiting different locations in year 2014 (and every month), which uses the methods developed in~\citep{clauset2009power}.
-The frequency is summarized based on the trajectories of individuals extracted in each time range. Note that different groups of Twitter user may exist in each month. 
-It appears that the distribution of the collective Twitter user visitation behaviors in year 2014 follows a two-tiered power law distributions (shown in Figure 4), where the majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$ and the $\alpha$ value is 1.32, and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $p(x)\sim x^{-\alpha}$ with $\alpha$ value is 3.5.
-This finding is consistent across all 12 months, with the mean $\alpha$ value as 1.34 $ \pm$  0.05 (standard deviation) and the mean $\lambda$ value as 0.00178 $ \pm$  0.0002 (standard deviation).
-
-The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model~\citep{ reynolds2012truncated, rhee2011levy}, which has also been identified in many human mobility studies using different mobility data~\citep{zhao2015explaining}.
-The similarities among the cumulative distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which indicates studies collected geo-located tweets in one month can potentially reveal similar findings as the ones collected in multiple months.
-Of course, different spatial scales can effect such findings as we learned that there were no geo-located tweets collected from 4 counties.
-In addition, the two-tier power law also reveals the diversity in the Twitter user visiting behaviors: (1) a small group Twitter users visited significantly more locations than the rest (2) within each group, the probability of Twitter user visiting more locations decreases significantly with a power function.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=1.0\linewidth]{./figures/visitation2}
-\caption{Two-tier power law distribution of the collective Twitter user visitation behaviors}
-\label{fig:Arch}
-\end{figure}
-%\FloatBarrier
-
-As it is mentioned earlier, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\citep{gonzalez2008understanding}.
-In this case, we first gathered the displacements from all the collected Twitter users in the United States (excluding Hawaii and Alaska) in year 2014, where those Twitter users with only one geo-located tweet were filtered out.
-In addition, to investigate the mobility patterns of individuals, we derived the accumulated displacements and the radius of gyrations of each individual Twitter user based on the corresponding space-time trajectories over the one year period.
-Note that both displacements and radius of gyrations were measured by ``crow's fly distance", which is the direct distance ($d$) between two consecutively recorded locations in a user's trajectory.
-
-To seek mobility patterns from these measurements, we performed statistical analysis regarding the probability distributions of displacements and radius of gyrations, which is also known as the spatial dispersal kernel $P(d)$~\citep{brockmann2006scaling}.
-The probability distribution of the user displacements (as well as accumulated displacements) is shown in Figure 5, whereas the probability distribution of radius of gyrations is shown in Figure 6.
-In this study, we used the fitting methods developed by~\citep{Jurdak2015}.
-The probability distributions of overall displacements, and the accumulated displacements and radius of gyrations of individuals, can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.
-
-In particular, as it is shown in Figure 5 (a), the probability distributions of overall displacements is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10 m, 70m] (accounting for 2 $\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [100m, 80km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80km] (accounting for 5 $\%$ of the population).
-In additon, the displacement in the distance bound from 100m and 80km in Figure 5 (b) can be further approximately by two power-law distributions with a cutting point at 5km (53$\%$ distances are less than 5km and 40$\%$ distances between 5km and 80km), which indicates two different travel modes, such as inter- or intra-city movements.
-Overall, the fitting functions with different distance bound suggest the existence of multi-scale or multi-modal mobility patterns ~\citep{Jurdak2015} of the Twitter users in the United States, for example the displacements larger than 80km could be related to inter-state travels or travel by flight.
-
-The probability distribution of radius of gyrations of individuals (Figure 6 (a)) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10m$ from [10 m, 50m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50m, 30km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30km].
-In particular, the radius of gyration between 50m and 30km can be further approximately by two power law distributions with a cutting point at 6km, which suggest two main types of spatial coverage of from the collected Twitter users in the United States.
-The distribution shows that around $10\%$ the tweet population has a radius of gyration less than 50 meters, which indicates those twitter users mostly tweet at a particular place, such as home or office;  around 60$\%$ of the population has a radius of gyration less than 30 km, which indicates that most of the collected Twitter user movements are ``short" distances, e.g., within a city locale.
-Note that the accuracy of these values for defining the distance bound depends on the accuracy of the location information of each geo-located tweet.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=1.0\linewidth]{./figures/displacement}
-\caption{(a) The probability distribution of the collective Twitter user displacements P(d) (b) the distance between [100m, 80km] is approximated by a double power-law functions (c) The probability distribution of the accumulated displacements of individual Twitter users P(d) (d) The probability distribution of the accumulated displacements of individual Twitter users in 3 different months}
-\label{fig:Arch}
-\end{figure}\textbf{}
-%\FloatBarrier
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=1.0\linewidth]{./figures/gyration}
-\caption{ (a) The probability distribution of radius of gyration of individual Twitter users P($r_{g}$) (b) the distance between [50m, 30 km] is approximated by a double power-law functions}
-\label{fig:Arch}
-\end{figure}
-%\FloatBarrier
-
-More importantly, as our framework can aggregate Twitter user trajectories within different temporal ranges, we further analyzed the probability distributions of accumulated displacements took places in January, June, and October (Figure 5 (d)) and radius of gyrations within 4 quarters in year 2014 (Figure 7), in order to examine whether there are temporal changes in the mobility patterns.
-While the probability distributions of accumulated displacements are almost identical in those selected three months,  we do find changes in the probability distributions of radius of gyrations in different quarters of the year.
-The fluctuations in the tails of the distributions indicate that long distance radius of gyrations (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern, which means the increase or decrease of long distance movement activities in the corresponding time period.
-However, it is worthy noting that the overall trends in the Twitter user mobility patterns revealed by radius of gyrations are still consistent.
-In summary, by comparing these results with the same measurements in~\citep{Jurdak2015}, (slightly) different distance bounds were identified for describing the Twitter user mobility patterns in the USA and Australia, however the overall similarity and consistence found in using a combination of three functions to approximate the probability distribution functions of displacements and radius of gyrations, clearly provide supports for using geo-located tweets for conducting replicable human mobility studies.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=1.0\linewidth]{./figures/gyration_season}
-\caption{The probability distribution of radius of gyration of individual Twitter users in different quarters of year 2014}
-\label{fig:Arch}
-\end{figure}
-%\FloatBarrier
-
-The above analysis of Twitter user mobility patterns mainly focus on the temporal aspects where the spatial scale is fixed to the country level.
-Our framework provides the flexibility to aggregate and extract Twitter user trajectories in a specific spatial scale and re-produce the analysis. 
-In particular, as it is evident from the above analysis that there are multi-scale or multi-modal Twitter user mobility patterns, this framework can help further look into the mobility pattern regarding how Twitter users move across different spatial scales and temporal ranges, which is measured by the movement flows among these spatial regions.
-In this case, we demonstrate the inter-state mobility patterns by using the framework to capture the movement flows among the states.
-Note that the movement flows can be summarized across all the 10 spatial layers in the framework.
-In particular, the movement flows in the state level are summarized and visualized with chord diagrams (illustrated in Figure 10) as part of the interactive mapping interface.
-We tested the overall distribution of the movement flows (in the form of weighted in-degree and out-degree of a graph, where each state is treated as a node) among different states in year 2014.  
-We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states.
-It also indicates that although the Twitter population seems to be linearly correlated with the population at state level, it is not proportional to account the movement flux among the states, which may provide some insights for other researchers in studying social-economical aspects of the migration dynamics.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.8\linewidth]{./figures/degree}
-\caption{The distribution of Twitter user movement flows among different states in year 2014 measured in weighted in- and out-degrees}
-\label{fig:Arch}
-\end{figure}
-%\FloatBarrier
-
-\subsection{The interactive 3D virtual globe web mapping interface}
-In addition to providing supports for understanding Twitter user mobility patterns with statistical analysis, the framework integrates a 3D virtual globe interface to enable users to perform exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements.
-The 3D virtual globe is developed and extended from the Cesium library\footnote{http://cesiumjs.org/}, which is an open-source WebGL virtual globe and map engine. 
-We customized the map engine to adapt different spatial scales, which correspond to the hierarchical spatial layers,  for aggregating movements in different level-of-details.
-The map interface interprets user's interactions, such as area-of-interest, time window, and zoom levels, etc.
-as parameters and send to the dedicated visualization servlet on the CyberGIS Gateway\footnote{http://sandbox.cigi.illinois.edu/home/}, which is the leading online cyberGIS environment for a large number of users to perform computing- and data-intensive, and collaborative geospatial problem-solving enabled by advanced cyberinfrastructure~\citep{liu2014cybergis}.
-In return, the map interface visualizes the corresponding movement flows on the virtual globe.
-
-An overview of the web mapping interface is shown in Figure 8.
-In terms of performing exploratory visual-analytics of Twitter user movement patterns, users can specify the time window to enable the query.
-When the results are shown, users can hover the mouse over each individual lines on the map to see the value of movement flows for both in and out directions.
-If the selected criteria keep unchanged, whenever the user zooms in/out, tilt or rotate the globe, the mapping interface will automatically provide the corresponding level-of-details on the fly.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.8\linewidth]{./figures/vocation}
-\caption{An overview of the 3D interactive web mapping interface}
-\label{fig:Web_Interface}
-\end{figure}
-%\FloatBarrier
-
-For state level Twitter user movements, we provide an interactive chord diagram to explicitly illustrate the movement flows among different states (Figure 9).
-Figure 9 demonstrates the Twitter movement flows among different states in January, 2014.
-The size of each color patch is proportional to the volume of total incoming movements from other states, which allow us to visually identify those states that dominate the incoming movement flows and which states the flows are generated from.
-By interacting with the state names, it will highlight the details of incoming movement flows from other states, in this case California is selected, which has the largest incoming movement flows in January.\newline
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=1.0\linewidth]{./figures/vaca_flow}
-\caption{Chord diagrams for the movement flows among different states in January, 2014}
-\label{fig:vaca_movement}
-\end{figure}
-%\FloatBarrier
-
-\section{Conclusions}
-In this study, we have used large volume of geo-located tweets to study Twitter user mobility patterns across multi-level spatial scales and temporal granularity in the United States during the year 2014.
-To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
-This framework is implemented based on high-performance distributed computing environment using Apache Hadoop.
-It delivers scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
-
-With this framework, we have found some interesting Twitter user mobility patterns, both statistically and visually.
-We studied the collective Twitter user visiting behavior regarding the frequency of Twitter users visiting different locations, which was fitted by a two-tier power-law distribution function.
-The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model, which has also been identified in many human mobility studies using different mobility data.
-The similarities among the cumulative distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which provides supports that we are not just capturing a random snapshot of the whole data stream.
-
-We studied the distance decay effects in the collective Twitter user movements measured by the probability distributions of the displacements and radius of gyrations of individuals. 
-These distributions can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.
-In particular, distance bounds between different fitting functions in displacement distribution reveals the existence of multi-scale or multi-modal mobility patterns of the Twitter users in the United States, whereas the distribution of radius of gyration reveals different groups of Tweet users with different types of spatial coverages.
-More importantly, we further studied these mobility patterns in different temporal scales to investigate the temporal changes in the mobility patterns. 
-We found that the accumulated displacements are almost identical in different months, while the long distance radius of gyration (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{6pt}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+\abbreviations{The following abbreviations are used in this manuscript:\\
+
+\noindent MDPI: Multidisciplinary Digital Publishing Institute\\
+DOAJ: Directory of open access journals\\
+TLA: Three letter acronym\\
+LD: linear dichroism}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+\appendix
+\section{}
+The appendix is an optional section that can contain details and data supplemental to the main text.
+For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data.
+Mathemtaical proofs of results not central to the paper can be added as an appendix.
+
+\section{}
+All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{mdpi}
-\bibliography{lite}
+
+%=====================================
+% References, variant A: internal bibliography
+%=====================================
+\renewcommand\bibname{References}
+\begin{thebibliography}{999}
+% Reference 1
+\bibitem{ref-journal}
+Lastname, F.; Author, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149.
+% Reference 2
+\bibitem{ref-book}
+Lastname, F.F.; Author, T. The title of the cited contribution. In {\em The Book Title}; Editor, F., Meditor, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58.
+\end{thebibliography}
+
+%=====================================
+% References, variant B: external bibliography
+%=====================================
+%\bibliography{your_external_BibTeX_file}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% optional
+\sampleavailability{Samples of the compounds ...... are available from the authors.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-08-05 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
New

@@
 LBSM data have also been criticized for lacking of representativeness of the population, as not all people use social media or send geo-located messages~\citep{kung2014}. 
-Another research challenge is to identify the users, as a social media account is not equivalent to a real person in the physical world~\citep{tsou2015}.
+Another research challenge is to identify the users, as a social media account is not equivalent to a real person in the physical world.
 Many studies have started to look into the demographic aspect of LBSM data, in particular Twitter data~\citep{steiger2015,luo2016}. 
@@
 At this stage, each geo-located tweet is represented as a tuple $\langle user\_id, loc, t, m \rangle$, where $user\_id$ is an anonymous Twitter user id; $loc$ is the recorded location of the tweet as a coordinate pair; $t$ is the timestamp of the tweet's post; and $m$ is the actual content of the tweet.
+We then constructed a trajectory for each Twitter user by appending all the recorded locations (with the same  $user\_id$) in the chronological order (based on the timestamps).
 To protect Twitter users’ privacy, the id field was replaced with a randomly generated unique number and the content of the message was removed.
@@
 
-\subsection{A network of large-scale Twitter user spatial interactions}
+\subsection{Mobility network of Twitter user spatial interactions}
 A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\citep{gonzalez2008}.
@@
 
-\subsection{Distance decay effects with a gravity model}
+\subsection{Distance decay effect and gravity model}
 As mentioned above, the clusters of urban regions in the form of communities in the network space often yield geographically cohesive urban areas. 
@@
 A greater $\beta$ indicates stronger decay and the interaction strength is more influenced by distance~\citep{liu2014}.
-While it is suggested that population size may be an accurate indicator to describe the repulsion or attractiveness between places, the gravity model is usually fit by using observed interaction strength and the distance between geographical entities~\citep{liu2014}.
+While it is suggested that population size may not be an accurate indicator to describe the repulsion or attractiveness between places, the gravity model is usually fitted by using observed interaction strength and the distance between geographical entities~\citep{liu2014}.
 \begin{equation} \label{eq:3}
@@
 In this study, in line with the idea that urban environments are conceptualized spaces that are recreated and formed by human activities~\citep{schliephake}, we speculate that the distance decay effects in affecting the interaction strength of two geographic regions and ultimately depicting the urban structures (e.g., urban boundaries), is contributed by (or related to) the distance decay parameters found in the underlying mobility patterns.
-In particular, since we have used a mobility network of spatial interactions, if this hypothesis stands, it will provide strong support that the depicted urban boundaries are not random artifacts but indeed reflect how people move across geographic regions.
+In particular, since we have used a mobility network of spatial interactions, if this hypothesis stands, it will provide strong support that the depicted urban boundaries are not random artifacts but indeed reflect how naturally people move across the geographical regions.
 
@@
 \subsection{Collective Mobility Patterns of Twitter Users in Great Britain}
-We first modeled different aspects of the collective mobility patterns of Twitter users.
+We modeled different aspects of the collective mobility patterns of Twitter users.
 These patterns include: the number of visited locations per user,  the collective user displacements, and the radius of gyration of individuals in order to identify natural breaks in user travel patterns.
@@
 
-\subsection{Distance decay effects with a gravity model}
-The results of strongly connected urban regions in the form of communities in the mobility network of Twitter user spatial interactions yield geographically cohesive, non-overlapping urban areas. 
+\subsection{Explaining the distance decay effect with a gravity model}
+The results of strongly connected urban regions in the form of communities, which are derived from the mobility network of Twitter user spatial interactions, yield geographically cohesive, non-overlapping urban areas.
 While it provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain, the reasons on why they are geographically cohesive and non-overlapping or why the boundaries stop/emerge at certain spatial extent that leads to different size of the urban areas are not clear.
 As the depicted urban boundaries exhibit a strong instance of spatial proximity, a gravity model is employed (Eq.
-\eqref{eq:3}) to explain how distance decay effects found in the mobility patterns affect the interaction strength among non-administrative anthropographic urban areas.
+\eqref{eq:3}) to explain how distance decay effects found in the mobility patterns affect the interaction strength between the derived non-administrative anthropographic urban areas.
 
 In this model, the distance between two derived urban areas is measured by the geodetic distance between the centroid locations of the two.
-As it is mentioned above,  $P_{i}$ and $P_{j}$  are the observed interaction between urban area $i$ and $j$, which are measured by the aggregation of movement flux in each urban area.
-In particular, we set the distance decay parameter $\beta$ value as 0.8: (1) As we hypothesize that the distance decay parameters found in the underlying mobility patterns potentially contribute to $\beta$ in the gravity model (2) and we have chosen the 10-km cell size based on the collective Twitter user mobility pattern regarding radius of gyration, where the distance decay parameter is 0.8 when radius of gyration $r_{g} > 10 km$ (Fig.~\ref{S4_Fig}(c)).
+As it is mentioned above,  $P_{i}$ and $P_{j}$  are the observed interaction between urban area $i$ and $j$, which are measured by the aggregation of movement flows in each urban area.
+In particular, we set the distance decay parameter $\beta$ value as 0.8: (1) As we hypothesize that the distance decay parameters found in the underlying mobility patterns potentially contribute to $\beta$ in the gravity model (2) and we chose the 10 km cell-size based on the collective Twitter user mobility pattern regarding radius of gyration, where the distance decay parameter is 0.8 when radius of gyration $r_{g} > 10 km$ (Fig.~\ref{S4_Fig}(c)).
 We found that the gravity model indicates strong linear correlation between the observed versus the estimated interaction strength with $R^{2}$ = 0.89 and $p-value < 0.01$.
-This confirms that the depicted urban areas are results of spatial proximity effects, where the strength of human (in this case, Twitter user) spatial interaction between two urban regions decreases as the geographic distance between them increases.
+This confirms that the depicted urban areas are instances of spatial proximity effects, where the strength of human (in this case, Twitter user) spatial interaction between two urban regions decreases as the geographic distance between them increases.
+The well fitted gravity model provides support that the depicted urban areas are not just random artifacts but reflect how naturally move across geographic regions.
 More importantly, since we have used a mobility network to delineate the boundaries, the distance decay effects are well related and explained by the distance decay parameters found in the underlying mobility patterns.
-In return, the well fitted gravity model provides support that the depicted urban areas are not random artifacts but indeed reflect how people move across geographic regions.
+To elaborate, the spatial interaction strength decreases along with the decay for the probability of longer distance Twitter user movements, and eventually stops at certain spatial extent, which leads to more geographically cohesive cluster of urban regions.
 
@@
 Third, since the collective radius of gyration was used to determine the cell-size in the network, we examined the temporal stability for the measurement in the geo-located Twitter data.
-The probability distributions of the radius of gyration for Twitter users in the Great Britain are verified to be consistent across different monthly time span, (see Supplement Materials section 2), which indicates the stability of using such measurements in this study.
-Finally, as the geo-located Twitter data offers easy data accessibility, the methods in this study can be reproduced for other countries. 
+The probability distributions of the radius of gyration for Twitter users in the Great Britain are verified to be consistent across different monthly time span (see Supplement Materials section 2), which indicates the stability of using such measurements in this study.
+Finally, as the geo-located Twitter data offers easy data accessibility, our methods can be reproduced for other countries. 
 Along with the large sample size and spatial coverage, geo-located Twitter data demonstrated its applicability for this study.
@@
 A major component in this study was imposing a virtual fishnet to partition the geographic space over Great Britain.
-We should be aware that using different approaches to partitioning the space will produce different mobility networks, and can potentially lead 
-to different delineations of the urban boundaries.
-Indeed, we had used the ward divisions as spatial units for aggregating Twitter user movements, which is the finest administrative boundaries of Great Britain (see Supplement Materials section 3).
+Alternatively, we had used the ward divisions as spatial units for aggregating Twitter user movements, which is the finest administrative boundaries of Great Britain (see Supplement Materials section 3).
 Without looking into the details of the results, the derived communities in the network space are similar to the ones from using fishnet approach.
@@
 
+We should be aware that using different fishnet cell-size to partition the space will produce different mobility networks, and can potentially lead to different delineations of the urban boundaries.
 As it is discussed above, we chose 10 km as the cell-size of the fishnet at national level in this study.
@@
 To apply the map equation algorithm, the mobility network should be organized as a weighted and directed graph, on which we confirmed an undirected graph cannot lead to a meaningful result (see Supplement Materials section 4).
-Since we used different physical movement ranges of users in delineating the urban boundaries, the description length $L(M)$ appeared to get larger when longer movement distances were used, which corresponded to less and larger geographically cohesive, non-overlapping urban areas.
+Since we used different physical movement ranges of users in delineating the urban boundaries, the description length $L(M)$ appeared to get larger when longer displacements were used, which corresponded to less and larger geographically cohesive, non-overlapping urban areas.
 We believed that different movement ranges of users changed the weights of this graph and affected the interaction strength between two fishnet cells.
-As we have illustrated that the geographically cohesive, non-overlapping urban areas were instances of spatial proximity effects, where the gravity model model employed suggested the interaction strength between two fishnet cells decreases as the geographical distance increases, the longer movement distances were used, the larger $L(M)$ the map equation algorithm produces.
+As we have illustrated that the geographically cohesive, non-overlapping urban areas were instances of spatial proximity effects, where the employed gravity model model suggested the interaction strength between two fishnet cells decreases as the geographical distance increases, the longer displacements were used, the larger $L(M)$ were produced from the map equation algorithm.
 
@@
 
-\bibitem[\protect\citeauthoryear{Liu {\itshape{et~al.}}}{2015}]{liu2014}
+\bibitem[\protect\citeauthoryear{Liu {\itshape{et~al.}}}{2014}]{liu2014}
 Liu, Y., Sui, Z., Kang, C., Gao, Y., 2014. Uncovering patterns of inter-urban trip and spatial interaction from social media check-in data. PLoS ONE, 9(1), p.e86026.
@@
 
-\bibitem[\protect\citeauthoryear{Tsou}{2015}]{tsou2015}
-Tsou, M.H., 2015. Research challenges and opportunities in mapping social media and Big Data. Cartography and Geographic Information Science, 42(sup1), pp.70-74.
-
 \bibitem[\protect\citeauthoryear{Vasardani {\itshape{et~al.}}}{2013}]{vasardani2013}

### 2016-08-08 MovePattern_IJGI/IJGI/Twitter_MovementPatterns_VisualAnalytics.tex
mac

@@
 \documentclass[ijgi,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
-
-%--------------------
-% Class Options:
-%--------------------
-% journal
-%----------
-% Choose between the following MDPI journals:
-% actuators, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, atmosphere, atoms, axioms, batteries, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, challenges, chemosensors, children, chromatography, climate, coatings, computation, computers, condensedmatter, cosmetics, cryptography, crystals, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electronics, energies, entropy, environments, epigenomes, fermentation, fibers, fishes, fluids, foods, forests, futureinternet, galaxies, games, gels, genealogy, genes, geosciences, geriatrics, healthcare, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, inventions, jcdd, jcm, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, lubricants, machines, magnetochemistry, marinedrugs, materials, mathematics, mca, mti, medsci, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, nutrients, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, polymers, processes, proteomes, publications, recycling, religions, remotesensing, resources, risks, robotics, safety, sensors, separations, sexes, sinusitis, socsci, societies, soils, sports, standards, sustainability, symmetry, systems, technologies, toxics, toxins, universe, urbansci, vaccines, vetsci, viruses, water
-%---------
-% article
-%---------
-% The default type of manuscript is article, but can be replaced by: 
-% addendum, article, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimage, letter, newbookreceived, opinion, obituary, projectreport, reply, retraction, review, sciprints, shortnote, supfile, technicalnote
-% supfile = supplementary materials
-%----------
-% submit
-%----------
-% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
-This will only make changes to the frontpage (e.g.
-the logo of the journal will get visible), the headings, and the copyright information.
-Also, line numbering will be removed.
-Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
-%------------------
-% moreauthors
-%------------------
-% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
-%---------
-% pdftex
-%---------
-% The option pdftex is for use with pdfLaTeX. If eps figure are used, remove the option pdftex and use LaTeX and dvi2pdf.
 
@@
 %=================================================================
+
+\usepackage{placeins}
+
 %% Please use the following mathematics environments:
@@
 \section{Introduction}
-Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\citep{belik2011natural}.
-Earlier research efforts relied on low resolution mobility data to understand human mobility patterns, such as using census records to understand human migration patterns~\citep{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\citep{brockmann2006scaling}.
-However, the lack of detailed human movements with fine-grained spatial and temporal granularity limits the findings to capture mobility patterns of individuals~\citep{gonzalez2008understanding,Jurdak2015}.
-In addition to the mobility data collected by GPS trackers~\citep{zheng2008understanding, rhee2011levy} and mobile phone call records~\citep{gonzalez2008understanding,sevtsuk2010does,kung2014exploring},
-emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints~\citep{thatcher2014living} in the form of real-world trails and footprints.
-One significant advantage of LBSM data streams is the large spatial coverage, for example, researchers have used geo-located Twitter data for studying global mobility patterns~\citep{hawelka2014geo}, which is otherwise impossible by using other mobility datasets (e.g., GPS traces and mobile phone call records).
-In addition, the publicly available LBSM data streams offer unique opportunities for conducting replicable scientific findings regarding the concerns of infringement on individual privacy, such as using mobile phone call records~\citep{giannotti2008mobility,crampton2014collect,Jurdak2015}.
+Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\cite{belik2011natural}.
+Earlier research efforts relied on low resolution mobility data to understand human mobility patterns, such as using census records to understand human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
+However, the lack of detailed human movements with fine-grained spatial and temporal granularity limits the findings to capture mobility patterns of individuals~\cite{gonzalez2008understanding,Jurdak2015}.
+In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring},
+emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints~\cite{thatcher2014living} in the form of real-world trails and footprints.
+One significant advantage of LBSM data streams is the large spatial coverage, for example, researchers have used geo-located Twitter data for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible by using other mobility datasets (e.g., GPS traces and mobile phone call records).
+In addition, the publicly available LBSM data streams offer unique opportunities for conducting replicable scientific findings regarding the concerns of infringement on individual privacy, such as using mobile phone call records~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}.
 
 Many studies have adopted the LBSM data streams to study human mobility patterns.
-For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects~\citep{gonzalez2008understanding} in the collective user movements to reveal different travel modes~\citep{Jurdak2015}, travel demands~\citep{wu2014intra,hasan2013understanding}, and the impact of social connections~\citep{cho2011friendship}.
+For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects~\cite{gonzalez2008understanding} in the collective user movements to reveal different travel modes~\cite{Jurdak2015}, travel demands~\cite{wu2014intra,hasan2013understanding}, and the impact of social connections~\cite{cho2011friendship}.
 These studies have provided strong support for using LBSM data as proxies for studying mobility patterns of individuals and valuable insights into human mobility dynamics. 
@@
 To be more specific, these studies lack examinations of the detailed movements across different geographical scales and temporal granularity, for instances, whether there are temporal (e.g., monthly or seasonal) changes within the movements, and how the mobility patterns vary across different spatial scales (e.g., intra- or inter county, city or country level).
-These insights are critical to advance our understandings of the collective mobility patterns for a variety of applications, such as examining the mobility patterns across different cities~\citep{noulas2012tale}, the spread patterns of disease~\citep{balcan2009multiscale, tamerius2011global} and touristic activities~\citep{hawelka2014geo}.
-While the high resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data intensive challenges for developing a multi-scale spatiotemporal analysis framework~\citep{tsou2015} to deal with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales.
-In addition, to enable efficient analysis and visualization of the mobility patterns at different spatiotemporal scales, it is essential for such a framework to provide scalability for addressing the data intensive challenges~\citep{cao2014scalable}.
+These insights are critical to advance our understandings of the collective mobility patterns for a variety of applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
+While the high resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data intensive challenges for developing a multi-scale spatiotemporal analysis framework~\cite{tsou2015} to deal with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales.
+In addition, to enable efficient analysis and visualization of the mobility patterns at different spatiotemporal scales, it is essential for such a framework to provide scalability for addressing the data intensive challenges~\cite{cao2014scalable}.
 
@@
 This framework is implemented based on high-performance distributed computing environment using Apache Hadoop\footnote{http://hadoop.apache.org/}, which is an open source software framework to enable distributed processing of large datasets across computing clusters.
-%We have implemented a set of efficient MapReduce~\citep{dean2008mapreduce} algorithms to deliver scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
+%We have implemented a set of efficient MapReduce~\cite{dean2008mapreduce} algorithms to deliver scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
 With this framework, we have performed a set of statistical analysis to understand the spatiotemporal Twitter user mobility patterns. 
 We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions. 
-In particular, the Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals~\citep{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\citep{Jurdak2015}.
+In particular, the Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
 By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
@@
 To understand detailed human mobility patterns of individuals, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
-However, the low-resolution mobility data collected from census records~\citep{greenwood1985human} is estimated and aggregated at census tract level, while tracking of bank notes~\citep{brockmann2006scaling} is at zip code level and do not necessarily reflecting movements of the same individuals~\citep{gonzalez2008understanding}.
-In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\citep{zheng2008understanding}.
+However, the low-resolution mobility data collected from census records~\cite{greenwood1985human} is estimated and aggregated at census tract level, while tracking of bank notes~\cite{brockmann2006scaling} is at zip code level and do not necessarily reflecting movements of the same individuals~\cite{gonzalez2008understanding}.
+In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\cite{zheng2008understanding}.
 However, the data is often limited in spatial scale (e.g.
-within a specific city or region) with a small group of people, for example, 182 and 226 volunteers participated in collecting such mobility data in~\citep{zheng2010geolife} and~\citep{rhee2011levy} respectively.
+within a specific city or region) with a small group of people, for example, 182 and 226 volunteers participated in collecting such mobility data in~\cite{zheng2010geolife} and~\cite{rhee2011levy} respectively.
 Other than tracking people directly, the vehicle-based GPS data is often tied to a specific vehicle (e.g.
-taxi), which may only be accessible for a certain group of people~\citep{kung2014exploring}.
+taxi), which may only be accessible for a certain group of people~\cite{kung2014exploring}.
 
-Another approach from the literatures for studying human mobility is using mobile phone call data in the form of Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\citep{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
-Such a dataset can cover relatively large spatial scale (e.g., country level)~\citep{becker2013human,sobolevsky2013delineating} and a large portion of the population in the study region~\citep{kung2014exploring}.
+Another approach from the literatures for studying human mobility is using mobile phone call data in the form of Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
+Such a dataset can cover relatively large spatial scale ~\cite{becker2013human,sobolevsky2013delineating} (e.g., national level) and a large portion of the population in the study region~\cite{kung2014exploring}.
 However, due to the concerns of infringement on individual privacy, the mobile phone call data is not publicly accessible, which is not ideal  for conducting replicable scientific findings, such as validating or extending the existing discoveries.
@@
 In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
-LBSM enables users to attach their current location as a geo-tag to the message they will post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\citep{Jurdak2015}.
+LBSM enables users to attach their current location as a geo-tag to the message they will post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
 A Big Data scenario emerges when millions social media users constantly posting messages.
@@
 For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place.
-It has been criticized for the lack of representativeness of the population as not all people use social media or send geo-located messages~\citep{kung2014exploring}.
-Another research challenge is to identify the users, as a social media account is not equal to a real person in the physical world~\citep{tsou2015}.
-Although many studies started to look into the demographic information of LBSM data, in particular Twitter data~\citep{mitchell2013geography,longley2015geotemporal}, these issues certainly require us to pose more strict criteria in filtering and extracting individual movements.
+It has been criticized for the lack of representativeness of the population as not all people use social media or send geo-located messages~\cite{kung2014exploring}.
+Another research challenge is to identify the users, as a social media account is not equal to a real person in the physical world~\cite{tsou2015}.
+Although many studies started to look into the demographic information of LBSM data, in particular Twitter data~\cite{mitchell2013geography,longley2015geotemporal}, these issues certainly require us to pose more strict criteria in filtering and extracting individual movements.
 
@@
 Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
-It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\citep{cranshaw2012livehoods, hasan2013understanding}.
+It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods, hasan2013understanding}.
 In addition, it presents some unique advantages that make it suitable for studying human mobility patterns.
-For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\citep{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\citep{hawelka2014geo}, which is almost impossible for other mobility datasets.
+For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\cite{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\cite{hawelka2014geo}, which is almost impossible for other mobility datasets.
 More importantly, by continuously monitoring the geo-located Twitter data streams with large volumes of detailed and frequently updated spatiotemporal  records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements).
@@
 Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of displacements and radius of gyrations of individuals, to study the mobility dynamics.
-At the same time, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\citep{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal granularity.
-For example, a geo-visualization approach was used to study human activity patterns, where user trajectories are mapped in a 3D space ordered by timestamps in the third dimension~\citep{kwan2004geovisualization}.
-While such an approach enables visualization of detailed trajectories, its capability is limited in dealing with large-volume movement datasets~\citep{andrienko2007designing}.
+At the same time, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\cite{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal granularity.
+For example, a geo-visualization approach was used to study human activity patterns, where user trajectories are mapped in a 3D space ordered by timestamps in the third dimension~\cite{kwan2004geovisualization}.
+While such an approach enables visualization of detailed trajectories, its capability is limited in dealing with large-volume movement datasets~\cite{andrienko2007designing}.
 Instead of directly visualizing individual user trajectories, a space-time cube approach was proposed in analyzing and visualizing the collective trajectories by providing flexibilities in setting up both spatial and temporal ranges, and therefore to study the mobility patterns across different spatial units (e.g.
-countries, states, and cities, etc.) and identify the changes over space and time~\citep{maceachren2001research, maceachren2004maps}.
-In this connection, visual-analytics methods are proposed to help better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\citep{andrienko2007designing,andrienko2007visual}.
-Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\citep{andrienko2007designing}.
+countries, states, and cities, etc.) and identify the changes over space and time~\cite{maceachren2001research, maceachren2004maps}.
+In this connection, visual-analytics methods are proposed to help better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\cite{andrienko2007designing,andrienko2007visual}.
+Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\cite{andrienko2007designing}.
 
@@
 By conveying the findings from statistical analysis, it provides another visualization form regarding the corresponding mobility patterns, in a sense, to avoid the problems of visual clutters.
-However, in the context of studying mobility patterns using large volume of geo-located Twitter data, the inherited large data volume poses significant data intensive challenges for these mentioned visual-analytics methods to scale with both the data volume and the computational requirements (e.g., movement extraction and trajectory modeling)~\citep{cao2014scalable}.
+However, in the context of studying mobility patterns using large volume of geo-located Twitter data, the inherited large data volume poses significant data intensive challenges for these mentioned visual-analytics methods to scale with both the data volume and the computational requirements (e.g., movement extraction and trajectory modeling)~\cite{cao2014scalable}.
 For example, in our study, 1.3 billion geo-located tweets were collected with over 1 TB in file size.
@@
 Such a task is already computationally demanding, let along breaking the trajectories to construct space-time cube with multiple spatial scale and temporal ranges. 
-In particular, developing a multi-scale spatiotemporal analysis framework is identified as one of the research challenges for dealing with social media Big Data~\citep{tsou2015}. 
+In particular, developing a multi-scale spatiotemporal analysis framework is identified as one of the research challenges for dealing with social media Big Data~\cite{tsou2015}. 
 To address the data-intensive challenges, there is a need to develop a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
@@
 %Apache Hadoop is an open source software framework designed to facilitate data intensive computing on large commodity clusters.
-%It combines a distributed file system, namely Hadoop Distributed File System(HDFS)~\citep{shvachko2010hadoop} with MapReduce programming paradigm, which can be applied to wide range of data-intensive problems.
-%MapReduce is a programming model and an associated software framework designed to process massive data in a distributed fashion~\citep{dean2008mapreduce}.
+%It combines a distributed file system, namely Hadoop Distributed File System(HDFS)~\cite{shvachko2010hadoop} with MapReduce programming paradigm, which can be applied to wide range of data-intensive problems.
+%MapReduce is a programming model and an associated software framework designed to process massive data in a distributed fashion~\cite{dean2008mapreduce}.
 %MapReduce breaks the entire computation into small tasks and schedule them among different computing nodes.
@@
 
-As a social media account is not equal to a real person in the physical world~\citep{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed the duplicated messages\footnote{https://support.twitter.com/articles/18311-the-twitter-rules} in the dataset; and then we attempted to remove non-human users based on unusual relocating speed (Hawelka et al., 2014; Jurdak et al., 2015).
+As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed the duplicated messages\footnote{https://support.twitter.com/articles/18311-the-twitter-rules} in the dataset; and then we attempted to remove non-human users based on unusual relocating speed (Hawelka et al., 2014; Jurdak et al., 2015).
 In this case, we adopted the speed limit value as 240 m/s used in (Jurdak et al., 2015), where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
@@
 \end{figure}
-%\FloatBarrier
+\FloatBarrier
 
 \subsection{Space-time Twitter user trajectories}
-To derive meaningful mobility patterns of individuals, a space-time trajectory of each individual user should be constructed~\citep{hagerstrand1985time}.
+To derive meaningful mobility patterns of individuals, a space-time trajectory of each individual user should be constructed~\cite{hagerstrand1985time}.
 Each raw geo-located tweet contains multiple fields of information, such as the created time, country, language code, and location, etc.
@@
 visitation behavior, displacement and radius of gyration:}} As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers the frequency of a user visiting different locations within a specific time frame.
-This metric can provide an overall assessments regarding the diversity and similarity in the collective mobility pattern~\citep{gao2012exploring}.
+This metric can provide an overall assessments regarding the diversity and similarity in the collective mobility pattern~\cite{gao2012exploring}.
 
-In particular, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\citep{gonzalez2008understanding}.
+In particular, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
 The displacement refers to an individual's re-allocation in the geographical space measured in distance, i.e., $distance (loc_{i} - loc_{i-1})$.
 It is not equivalent to a ``trip" took by an individual, for example, even the time interval between two recorded locations is one month, it will still count as a displacement.
-By studying all the displacements from a group people, it helps to identify the distance bounds associated with different travel modes~\citep{Jurdak2015} or to determine whether movements are random walks~\citep{brockmann2006scaling}.
-Radius of gyration is a metric to distinguish mobility patterns of individuals~\citep{gonzalez2008understanding}, which is defined as fellows.   
+By studying all the displacements from a group people, it helps to identify the distance bounds associated with different travel modes~\cite{Jurdak2015} or to determine whether movements are random walks~\cite{brockmann2006scaling}.
+Radius of gyration is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008understanding}, which is defined as fellows.   
 \newline
@@
 \subsection{Multi-level spatiotemporal trajectory aggregation}
-An important strategy for visual-analytics methods dealing with massive movement datasets is performing spatial aggregations to provide different levels-of-detail~\citep{andrienko2007designing,andrienko2007visual}.
-It is similar to the map generation approach that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest~\citep{buttenfield1991map}.
-To enable aggregating Twitter trajectories into multiple spatial levels, we have extended the hierarchical space-time cube model developed in~\citep{cao2014scalable}, where we partitioned the geographic space of the United States into 10 hierarchical spatial layers.
+An important strategy for visual-analytics methods dealing with massive movement datasets is performing spatial aggregations to provide different levels-of-detail~\cite{andrienko2007designing,andrienko2007visual}.
+It is similar to the map generation approach that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest~\cite{buttenfield1991map}.
+To enable aggregating Twitter trajectories into multiple spatial levels, we have extended the hierarchical space-time cube model developed in~\cite{cao2014scalable}, where we partitioned the geographic space of the United States into 10 hierarchical spatial layers.
 To be specific, the state boundaries of the United States are treated as the base layer (i.e.
@@
 If the location does not belong to any polygon, it will be dropped, which is how we used the geographic boundaries of the United States to filer the raw tweet collection and keep the ``domestic" ones.
-To optimize the ``point-in-polygon" determination without comparing the location with every polygon in the spatial layer, we also created a Quad-Tree~\citep{samet1984quadtree} for each spatial layer to speed up the process.
+To optimize the ``point-in-polygon" determination without comparing the location with every polygon in the spatial layer, we also created a Quad-Tree~\cite{samet1984quadtree} for each spatial layer to speed up the process.
 Finally, the reducers generate two data outputs: (1) reconstructed space-time Twitter user trajectories at each spatial level (2) movement flows in the form of in and out volumes among the units.
@@
 For example, some people may tweet once a day while others do more; some people may tweet regularly while others do not.
-These tweeting behaviors are expected as such human dynamics are also seen in the mobile phone call data~\citep{gonzalez2008understanding}. 
+These tweeting behaviors are expected as such human dynamics are also seen in the mobile phone call data~\cite{gonzalez2008understanding}. 
 Many studies have carried out data collection within a certain time period (e.g., a year in our case).
@@
 
-In this study, we have analyzed the cumulative distribution of the frequency Twitter users visiting different locations in year 2014 (and every month), which uses the methods developed in~\citep{clauset2009power}.
+In this study, we have analyzed the cumulative distribution of the frequency Twitter users visiting different locations in year 2014 (and every month), which uses the methods developed in~\cite{clauset2009power}.
 The frequency is summarized based on the trajectories of individuals extracted in each time range. Note that different groups of Twitter user may exist in each month. 
@@
 
-The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model~\citep{ reynolds2012truncated, rhee2011levy}, which has also been identified in many human mobility studies using different mobility data~\citep{zhao2015explaining}.
+The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model~\cite{ reynolds2012truncated, rhee2011levy}, which has also been identified in many human mobility studies using different mobility data~\cite{zhao2015explaining}.
 The similarities among the cumulative distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which indicates studies collected geo-located tweets in one month can potentially reveal similar findings as the ones collected in multiple months.
@@
 
-As it is mentioned earlier, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\citep{gonzalez2008understanding}.
+As it is mentioned earlier, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
 In this case, we first gathered the displacements from all the collected Twitter users in the United States (excluding Hawaii and Alaska) in year 2014, where those Twitter users with only one geo-located tweet were filtered out.
@@
 
-To seek mobility patterns from these measurements, we performed statistical analysis regarding the probability distributions of displacements and radius of gyrations, which is also known as the spatial dispersal kernel $P(d)$~\citep{brockmann2006scaling}.
+To seek mobility patterns from these measurements, we performed statistical analysis regarding the probability distributions of displacements and radius of gyrations, which is also known as the spatial dispersal kernel $P(d)$~\cite{brockmann2006scaling}.
 The probability distribution of the user displacements (as well as accumulated displacements) is shown in Figure 5, whereas the probability distribution of radius of gyrations is shown in Figure 6.
-In this study, we used the fitting methods developed by~\citep{Jurdak2015}.
+In this study, we used the fitting methods developed by~\cite{Jurdak2015}.
 The probability distributions of overall displacements, and the accumulated displacements and radius of gyrations of individuals, can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.
@@
 In additon, the displacement in the distance bound from 100m and 80km in Figure 5 (b) can be further approximately by two power-law distributions with a cutting point at 5km (53$\%$ distances are less than 5km and 40$\%$ distances between 5km and 80km), which indicates two different travel modes, such as inter- or intra-city movements.
-Overall, the fitting functions with different distance bound suggest the existence of multi-scale or multi-modal mobility patterns ~\citep{Jurdak2015} of the Twitter users in the United States, for example the displacements larger than 80km could be related to inter-state travels or travel by flight.
+Overall, the fitting functions with different distance bound suggest the existence of multi-scale or multi-modal mobility patterns ~\cite{Jurdak2015} of the Twitter users in the United States, for example the displacements larger than 80km could be related to inter-state travels or travel by flight.
 
@@
 \end{figure}\textbf{}
-%\FloatBarrier
+\FloatBarrier
 
@@
 However, it is worthy noting that the overall trends in the Twitter user mobility patterns revealed by radius of gyrations are still consistent.
-In summary, by comparing these results with the same measurements in~\citep{Jurdak2015}, (slightly) different distance bounds were identified for describing the Twitter user mobility patterns in the USA and Australia, however the overall similarity and consistence found in using a combination of three functions to approximate the probability distribution functions of displacements and radius of gyrations, clearly provide supports for using geo-located tweets for conducting replicable human mobility studies.
+In summary, by comparing these results with the same measurements in~\cite{Jurdak2015}, (slightly) different distance bounds were identified for describing the Twitter user mobility patterns in the USA and Australia, however the overall similarity and consistence found in using a combination of three functions to approximate the probability distribution functions of displacements and radius of gyrations, clearly provide supports for using geo-located tweets for conducting replicable human mobility studies.
 
@@
 The map interface interprets user's interactions, such as area-of-interest, time window, and zoom levels, etc.
-as parameters and send to the dedicated visualization servlet on the CyberGIS Gateway\footnote{http://sandbox.cigi.illinois.edu/home/}, which is the leading online cyberGIS environment for a large number of users to perform computing- and data-intensive, and collaborative geospatial problem-solving enabled by advanced cyberinfrastructure~\citep{liu2014cybergis}.
+as parameters and send to the dedicated visualization servlet on the CyberGIS Gateway\footnote{http://sandbox.cigi.illinois.edu/home/}, which is the leading online cyberGIS environment for a large number of users to perform computing- and data-intensive, and collaborative geospatial problem-solving enabled by advanced cyberinfrastructure~\cite{liu2014cybergis}.
 In return, the map interface visualizes the corresponding movement flows on the virtual globe.
@@
 \end{figure}
-%\FloatBarrier
+\FloatBarrier
 

### 2016-08-14 MovePattern_IJGI/IJGI/Twitter_MovementPatterns_VisualAnalytics.tex
new
xx
new drive

@@
 % Full title of the paper (Capitalized)
-\Title{Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
+%\Title{Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
+\Title{Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns with a Visual-Analytics Approach}
 
 % Authors, for the paper (add full first names)
-\Author{Junjun Yin $^{1}$ and Zhenhong Du $^{2}$*}
+\Author{Junjun Yin $^{1}$ and Zhenhong Du $^{2,}$*}
 % Authors, for metadata in PDF
-\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}
+\AuthorNames{Junjun Yin and Zhenhong Du}
 
@@
 However, the capability of capturing detailed human movements with fine-grained spatial and temporal granularity is still limited.
-In this study, we have extracted high-resolution mobility data from a collection of 1.3 billion geo-located Twitter messages to study multi-scale spatiotemporal Twitter user mobility patterns in the United States during the year 2014.
-Regarding the concerns of infringement on individual privacy, such as the mobile phone call data with restricted access, the dataset is collected from publicly accessible Twitter data streams.
-In this study, we have developed a scalable visual-analytics framework to deliver efficiency and scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-scale spatiotemporal user mobility patterns.
-We have performed a set of statistical analysis to understand Twitter user mobility patterns across multi-level spatial scales and temporal granularity.
-In particular, the Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals have revealed multi-scale or multi-modal Twitter user mobility patterns.
-By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.}
+In this study, we extracted high-resolution mobility data from a collection of over 1.3 billion geo-located Twitter messages.
+Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access, the dataset is collected from publicly accessible Twitter data streams.
+In this paper, we employed a visual-analytics approach to studying multi-scale spatiotemporal Twitter user mobility patterns in the contiguous United States during the year 2014.
+Our approach included a scalable visual-analytics framework to deliver efficiency and scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-scale spatiotemporal user mobility patterns.
+We performed a set of statistical analysis to understand Twitter user mobility patterns across multi-level spatial scales and temporal ranges.
+In particular, Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals revealed multi-scale or multi-modal Twitter user mobility patterns.
+By further studying such mobility patterns in different temporal ranges, we identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
+At the same time, our approach provides a geo-visualization unit with an interactive 3D virtual globe web mapping interface for exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements.}
 
@@
 Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\cite{belik2011natural}.
-Earlier research efforts relied on low resolution mobility data to understand human mobility patterns, such as using census records to understand human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
-However, the lack of detailed human movements with fine-grained spatial and temporal granularity limits the findings to capture mobility patterns of individuals~\cite{gonzalez2008understanding,Jurdak2015}.
-In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring},
-emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints~\cite{thatcher2014living} in the form of real-world trails and footprints.
-One significant advantage of LBSM data streams is the large spatial coverage, for example, researchers have used geo-located Twitter data for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible by using other mobility datasets (e.g., GPS traces and mobile phone call records).
-In addition, the publicly available LBSM data streams offer unique opportunities for conducting replicable scientific findings regarding the concerns of infringement on individual privacy, such as using mobile phone call records~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}.
+Earlier research efforts relied on low-resolution mobility data to understand human mobility patterns, such as using census records to study human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
+However, such mobility data do not provide detailed human movements with fine-grained spatial and temporal granularity, which are usually aggregated and therefore are limited to capture mobility patterns of individuals~\cite{gonzalez2008understanding,Jurdak2015}.
+In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints in the form of real-world user trails and footprints~\cite{thatcher2014living}.
+A significant advantage of utilizing LBSM data streams as proxies for studying human mobility patterns is the large spatial coverage.
+For instance, researchers have used geo-located Twitter data for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible for other mobility datasets (e.g., GPS traces and mobile phone call records).
+Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}, the publicly available LBSM data streams offer unique opportunities for conducting reproducible and comparative scientific findings across different geographic regions.
 
-Many studies have adopted the LBSM data streams to study human mobility patterns.
-For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects~\cite{gonzalez2008understanding} in the collective user movements to reveal different travel modes~\cite{Jurdak2015}, travel demands~\cite{wu2014intra,hasan2013understanding}, and the impact of social connections~\cite{cho2011friendship}.
-These studies have provided strong support for using LBSM data as proxies for studying mobility patterns of individuals and valuable insights into human mobility dynamics. 
-However, in these studies, the measurements of distances are either fixed in a certain time period or a specific region, where they do not consider the variations of movements in different spatial scales and temporal ranges.
-To be more specific, these studies lack examinations of the detailed movements across different geographical scales and temporal granularity, for instances, whether there are temporal (e.g., monthly or seasonal) changes within the movements, and how the mobility patterns vary across different spatial scales (e.g., intra- or inter county, city or country level).
-These insights are critical to advance our understandings of the collective mobility patterns for a variety of applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
-While the high resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data intensive challenges for developing a multi-scale spatiotemporal analysis framework~\cite{tsou2015} to deal with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales.
-In addition, to enable efficient analysis and visualization of the mobility patterns at different spatiotemporal scales, it is essential for such a framework to provide scalability for addressing the data intensive challenges~\cite{cao2014scalable}.
+Many recent studies have adopted the LBSM data streams to study human mobility patterns.
+For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects in the collective user movements~\cite{gonzalez2008understanding}, which were used to reveal different travel modes~\cite{Jurdak2015}, travel demands~\cite{wu2014intra,hasan2013understanding}, and the impact of social connections~\cite{cho2011friendship}.
+These studies have provided strong supports for using LBSM data as proxies for studying mobility patterns of individuals and valuable insights into human mobility dynamics.
+However, the variations of movements in different spatial scales and temporal ranges are neglected in these studies, where the measurements of distances are either fixed in a certain time range or to a specific geographic region.
+For instances, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national level), are lacking.
+Such insights are critical to advance our understandings of the collective mobility patterns for various applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
+On the other hand, while the high-resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data-intensive challenges for developing multi-scale spatiotemporal analysis approaches to dealing with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales~\cite{tsou2015}.
 
-In this paper, we have explored and studied the Twitter user mobility patterns across multi-level spatial scales and temporal granularity in the United States during the year 2014. 
-The mobility data is extracted from1.3 billion geo-located Twitter messages (i.e., tweets) from 1$^{st}$ January to 31$^{st}$ December, 2014 in the United States with over 6 million Twitter users and over 1 TB in file size.
-To address the data-intensive challenges embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
+In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
+The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from 1$^{st}$ January to 31$^{st}$ December, 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
+To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
 This framework is implemented based on high-performance distributed computing environment using Apache Hadoop\footnote{http://hadoop.apache.org/}, which is an open source software framework to enable distributed processing of large datasets across computing clusters.
-%We have implemented a set of efficient MapReduce~\cite{dean2008mapreduce} algorithms to deliver scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
-With this framework, we have performed a set of statistical analysis to understand the spatiotemporal Twitter user mobility patterns. 
+Enabled by this framework, we have performed a set of statistical analysis to understand multi-scale spatiotemporal Twitter user mobility patterns. 
 We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions.
-In particular, the Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
+In particular, the Twitter user mobility patterns measured by the user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
 By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
+In particular, our approach provides an interactive 3D virtual globe web mapping interface to enable exploratory geo-visual analytics for understanding the detailed Twitter user movement flows within a given spatial scale and time window.
 
 The remainder of this paper is organized as follows.
-Section 2 describes the related work in the context of studying mobility patterns using LBSM data, in particular, geo-located Twitter data.
-We focus on research challenges in visual-analytics methods to enable multi-scale
-spatiotemporal analysis with massive movement datasets, including data management, multi-level spatiotemporal user trajectory modeling and visualization.
+Section 2 describes the related work in the context of studying mobility patterns using LBSM data, in particular, the geo-located Twitter data.
+We focus on research challenges in using visual-analytics methods to enable multi-scale spatiotemporal analysis with massive movement datasets, including data management, multi-level spatiotemporal user trajectory modeling and visualization.
 Section 3 details the processes for extracting, aggregating and summarizing multi-level spatiotemporal Twitter user mobility patterns.
-Section 4 presents the case study of performing visual-analytics for seeking Twitter mobility patterns in the United States of year 2014. Section 5 concludes the paper.
+Section 4 presents the case study of performing visual-analytics for seeking multi-scale spatiotemporal Twitter mobility patterns in the continuous United States of year 2014.
+Section 5 concludes the paper.
 
@@
 \subsection{Geo-located Twitter data for studying large-scale user movements}
-To understand detailed human mobility patterns of individuals, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
-However, the low-resolution mobility data collected from census records~\cite{greenwood1985human} is estimated and aggregated at census tract level, while tracking of bank notes~\cite{brockmann2006scaling} is at zip code level and do not necessarily reflecting movements of the same individuals~\cite{gonzalez2008understanding}.
+To understand detailed mobility patterns of individuals, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
 In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\cite{zheng2008understanding}.
-However, the data is often limited in spatial scale (e.g.
-within a specific city or region) with a small group of people, for example, 182 and 226 volunteers participated in collecting such mobility data in~\cite{zheng2010geolife} and~\cite{rhee2011levy} respectively.
-Other than tracking people directly, the vehicle-based GPS data is often tied to a specific vehicle (e.g.
-taxi), which may only be accessible for a certain group of people~\cite{kung2014exploring}.
+However, the data are often limited in spatial scale (e.g.
+within a specific city or region) with a small group of people, for example, 226 and 182 volunteers participated in collecting such mobility data in~\cite{rhee2011levy} and~\cite{zheng2010geolife} respectively.
+Other than tracking people directly, the vehicle-based GPS traces are often tied to specific vehicles (e.g.
+taxi), which are only accessible for a certain group of people~\cite{kung2014exploring}.
 
-Another approach from the literatures for studying human mobility is using mobile phone call data in the form of Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
-Such a dataset can cover relatively large spatial scale ~\cite{becker2013human,sobolevsky2013delineating} (e.g., national level) and a large portion of the population in the study region~\cite{kung2014exploring}.
-However, due to the concerns of infringement on individual privacy, the mobile phone call data is not publicly accessible, which is not ideal  for conducting replicable scientific findings, such as validating or extending the existing discoveries.
+Another approach from the literatures for studying human mobility is using mobile phone call data, such as Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
+Such a dataset can cover relatively large spatial scale~\cite{becker2013human,sobolevsky2013delineating} (e.g., national level) and a large portion of the population in the study region~\cite{kung2014exploring}.
+However, due to the concerns of infringement on individual privacy, mobile phone call data are not publicly accessible at all.
+Even such data were obtained in the mentioned studies, they came from various service providers covering different groups of users.
+These issues limit the capability for conducting reproducible scientific findings regarding mobility research, such as validating or extending the existing discoveries.
 
 In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
-LBSM enables users to attach their current location as a geo-tag to the message they will post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
+LBSM enables users to attach their current location as a geo-tag to the message they post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
 A Big Data scenario emerges when millions social media users constantly posting messages.
-However, there are some limitations and complexities in directly using the LBSM data for study human mobility patterns. 
+In this study, geo-located Twitter data are chosen as a source for studying detailed mobility patterns.
+Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
+It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.
+
+However, it is worth noting that there are some limitations and complexities in directly using LBSM data for studying human mobility patterns.
 For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place.
-It has been criticized for the lack of representativeness of the population as not all people use social media or send geo-located messages~\cite{kung2014exploring}.
-Another research challenge is to identify the users, as a social media account is not equal to a real person in the physical world~\cite{tsou2015}.
-Although many studies started to look into the demographic information of LBSM data, in particular Twitter data~\cite{mitchell2013geography,longley2015geotemporal}, these issues certainly require us to pose more strict criteria in filtering and extracting individual movements.
-
-In this study, geo-located Twitter data is chosen as source for studying detailed mobility patterns.
-Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
-It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods, hasan2013understanding}.
-In addition, it presents some unique advantages that make it suitable for studying human mobility patterns.
+There is a potential mismatch regarding the representativeness of the overall population as not all people use social media or send geo-located messages~\cite{kung2014exploring} and the demographic information of the Twitter users cannot be easily identified, the derived mobility patterns may lead to an over or under-representation of the real-world mobility patterns.
+Many studies started to look into the demographic information of LBSM data, in particular Twitter data~\cite{mitchell2013geography,longley2015geotemporal}.
+Although the used methods are still arguable, these issues certainly require us to pose stricter criteria in understanding human mobility patterns using geo-located Twitter data.
+On the other hand, geo-located Twitter dataset presents some unique advantages that make it a valuable proxy for studying human mobility patterns.
 For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\cite{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\cite{hawelka2014geo}, which is almost impossible for other mobility datasets.
-More importantly, by continuously monitoring the geo-located Twitter data streams with large volumes of detailed and frequently updated spatiotemporal  records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements).
+More importantly, by continuously monitoring the geo-located Twitter data streams with large volumes of detailed and frequently updated spatiotemporal records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements), which is one of the motivations for this study.
 
 \subsection{Data-intensive challenges for multi-scale geo-visual analytics}
-Mobility data is essentially a collection of spatiotemporal records of people moving from one location to another in the geographic space.
-To study mobility patterns of individuals, a space-time trajectory of each individual should be modeled and constructed to quantify the collective movements over space and time.
-Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of displacements and radius of gyrations of individuals, to study the mobility dynamics.
-At the same time, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\cite{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal granularity.
+Mobility data are essentially a collection of spatiotemporal records of people moving from one location to another across the geographic space.
+To study mobility patterns of individuals, a space-time trajectory of each individual user should be modeled and constructed to quantify the collective movements over space and time.
+Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of user displacements and radius of gyrations of individuals, to study the mobility dynamics.
+At the same time, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\cite{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal ranges.
 For example, a geo-visualization approach was used to study human activity patterns, where user trajectories are mapped in a 3D space ordered by timestamps in the third dimension~\cite{kwan2004geovisualization}.
-While such an approach enables visualization of detailed trajectories, its capability is limited in dealing with large-volume movement datasets~\cite{andrienko2007designing}.
-Instead of directly visualizing individual user trajectories, a space-time cube approach was proposed in analyzing and visualizing the collective trajectories by providing flexibilities in setting up both spatial and temporal ranges, and therefore to study the mobility patterns across different spatial units (e.g.
+While such an approach enables visualization of individual trajectories, its capability is limited in dealing with large-volume movement datasets~\cite{andrienko2007designing}.
+Instead of directly visualizing individual user trajectories, a space-time cube approach was proposed to analyzing and visualizing the collective trajectories.
+It provides flexibilities in setting up both spatial scales and temporal ranges, and therefore is used to study mobility patterns across different spatial units (e.g.
 countries, states, and cities, etc.) and identify the changes over space and time~\cite{maceachren2001research, maceachren2004maps}.
-In this connection, visual-analytics methods are proposed to help better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\cite{andrienko2007designing,andrienko2007visual}.
+In this regard, visual-analytics methods are proposed to help better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\cite{andrienko2007designing,andrienko2007visual}.
 Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\cite{andrienko2007designing}.
+Employing visual-analytics methods dealing with massive movement datasets is not only beneficial for optimizing visualizations but also provides a great deal of flexibilities for performing statistical analysis in seeking mobility patterns with different level of spatiotemporal details.
 
-Employing visual-analytics methods dealing with massive movement datasets is not only beneficial for optimizing visualizations but also provides a great deal of flexibilities for performing statistical analysis in seeking mobility patterns with different level of spatiotemporal details.
-By conveying the findings from statistical analysis, it provides another visualization form regarding the corresponding mobility patterns, in a sense, to avoid the problems of visual clutters.
-However, in the context of studying mobility patterns using large volume of geo-located Twitter data, the inherited large data volume poses significant data intensive challenges for these mentioned visual-analytics methods to scale with both the data volume and the computational requirements (e.g., movement extraction and trajectory modeling)~\cite{cao2014scalable}.
-For example, in our study, 1.3 billion geo-located tweets were collected with over 1 TB in file size.
+However, in the context of studying mobility patterns using large volume of geo-located Twitter data, the inherited large data volume poses significant data intensive challenges for visual-analytics methods to scale with both the data volume and the computational requirements (e.g., movement extraction and trajectory modeling)~\cite{cao2014scalable}.
+In particular, in our study, 1.3 billion geo-located tweets were collected with over 1 TB in file size.
 To construct a space-time trajectory of an individual, it is necessary to go through the massive dataset to sort and update the trajectory whenever a new location is found.
 Such a task is already computationally demanding, let along breaking the trajectories to construct space-time cube with multiple spatial scale and temporal ranges.
-In particular, developing a multi-scale spatiotemporal analysis framework is identified as one of the research challenges for dealing with social media Big Data~\cite{tsou2015}. 
+Indeed, developing a multi-scale spatiotemporal analysis approach is identified as one of the research challenges for dealing with social media Big Data~\cite{tsou2015}.
 To address the data-intensive challenges, there is a need to develop a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
-
-%\subsection{Accommodating LBSM Big Data with Hadoop}
-%Apache Hadoop is an open source software framework designed to facilitate data intensive computing on large commodity clusters.
-%It combines a distributed file system, namely Hadoop Distributed File System(HDFS)~\cite{shvachko2010hadoop} with MapReduce programming paradigm, which can be applied to wide range of data-intensive problems.
-%MapReduce is a programming model and an associated software framework designed to process massive data in a distributed fashion~\cite{dean2008mapreduce}.
-%MapReduce breaks the entire computation into small tasks and schedule them among different computing nodes.
-%MapReduce consists of two main stages: map and reduce.
-%In the map stage, input data is converted into series of intermediate $\langle key, value\rangle$ pairs.
-%Customized computation will be performed in the reduce stage based on the same intermediate key.
-%This framework provides parallelization since both map and reduce tasks are considered independent and can be done in parallel.
-More importantly, it provides scalability in relation to the growth of data size, where Hadoop can scale to more computing nodes in the cluster to maintain the performance.
-%
-%Our framework benefits from using Hadoop in both data management and processing.
-%First, since the input data is large it is desirable to store it on multiple machines.
-%Second, by using Hadoop we can parallelize the computational tasks and make the data processing faster and more efficient.
-%Further, by adopting the MapReduce computing paradigm, we can model each individual user's trajectory by treating user's unique ID as key, and summarize the movement flows among different spatial units by utilizing the ID of the spatial unit as key.
-The details will be introduced in the following section.
 
@@
 In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
-To ensure complete coverage over the United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
+To ensure complete coverage over the continuous United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
 The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2GB in size) collected per day.
@@
 
-As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed the duplicated messages\footnote{https://support.twitter.com/articles/18311-the-twitter-rules} in the dataset; and then we attempted to remove non-human users based on unusual relocating speed (Hawelka et al., 2014; Jurdak et al., 2015).
-In this case, we adopted the speed limit value as 240 m/s used in (Jurdak et al., 2015), where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
-Note that the original location information embedded in each geo-located tweet is given in units of latitude and longitude.
-To reduce the complexity in calculating distances and performing spatial aggregations directly based on geographical coordinates, we projected the all the points using North America Albers Equal Area Conic (ESRI:102008) coordinate system.
-Finally, we used the geographic boundaries of the United States\footnote{https://www.census.gov/geo/maps-data/data/} (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section.
+As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages\footnote{https://support.twitter.com/articles/18311-the-twitter-rules} in the dataset; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
+In this case, we adopted the speed limit value as 240 m/s used in~\cite{Jurdak2015}, where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
+Note that the original location information embedded in each geo-located tweet is given in units of latitude and longitude, the distance is calculated by the great-circle distance between two points on a sphere with the haversine formula.
+Finally, we used the geographic boundaries of the continuous United States\footnote{https://www.census.gov/geo/maps-data/data/} (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section.
 Based on these reinforcements, the dataset contains 1,052,861,000 tweets and 4,559,205 unique users.
@@
 To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
-The scalable visual-analytics framework consists of two main units: (1) Data collection unit: a Twitter data crawler that continuously collects raw geo-located tweets using the Twitter Streaming API.
-(2) Data processing unit: a distributed computing environment using Apache Hadoop for modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing the movements at multiple spatiotemproal levels.
-An overall system architecture of the framework that chains the three units is shown in Figure 1. The details regarding the function and implementation of each unit are presented in the next sections.
+The scalable visual-analytics framework consists of two main units: (1) Data processing unit: a distributed computing environment using Apache Hadoop for modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing the movements at multiple spatiotemporal scales.
+(2) Geo-visualization unit: an interactive 3D virtual globe web mapping interface for exploratory geo-visual analytics for understanding the detailed Twitter user movement flows across different spatial scales and temporal ranges.
+
+Apache Hadoop combines a distributed file system, namely Hadoop Distributed File System(HDFS)~\cite{shvachko2010hadoop} with MapReduce programming paradigm~\cite{dean2008mapreduce}, which can be applied to a wide range of data-intensive problems.
+Our framework benefits from using Hadoop in both data management and processing.
+First, since the input data is large it is desirable to store it on multiple machines.
+This provides scalability in relation to the growth of data size, where Hadoop can scale to more computing nodes in a cluster to maintain the performance.
+Second, by using Hadoop we can parallelize the computational tasks, where MapReduce breaks the entire computation into small tasks and schedule them among different computing nodes, to make the data processing faster and more efficient.
+An overall system architecture of the framework is shown in Figure~\ref{fig:overall_archi}.
+The details regarding the function and implementation of each unit are presented in the next sections.
 
@@
 \caption{The overall system architecture of the framework}
-\label{fig:Arch}
+\label{fig:overall_archi}
 \end{figure}
@@
 To remove non-human users based on unusual relocating speed, a user will be removed if the speed between any two consecutive locations in the user's trajectory with $speed$ $(loc_{i} - loc_{i-1}) > 240 m/s $.
+Based on this definition for modeling the space-time Twitter user trajectories, we converted the process of extracting trajectories from the raw geo-located Twitter data as a MapReduce task.
+Specifically, each mapper utilizes the unique user id as a key to prepares the records that belong to the same user and send them to reducer.
+Once the reducers receive the $\langle key, value\rangle$ pairs, a Twitter user's space-time trajectory is formed by the sorting the locations in chronological order while considering the speed limit.
 \newline
@@
 visitation behavior, displacement and radius of gyration:}} As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers the frequency of a user visiting different locations within a specific time frame.
-This metric can provide an overall assessments regarding the diversity and similarity in the collective mobility pattern~\cite{gao2012exploring}.
+This metric provides an overall assessment regarding the diversity and similarity in the collective mobility pattern~\cite{gao2012exploring}.
 
 In particular, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
-The displacement refers to an individual's re-allocation in the geographical space measured in distance, i.e., $distance (loc_{i} - loc_{i-1})$.
-It is not equivalent to a ``trip" took by an individual, for example, even the time interval between two recorded locations is one month, it will still count as a displacement.
-By studying all the displacements from a group people, it helps to identify the distance bounds associated with different travel modes~\cite{Jurdak2015} or to determine whether movements are random walks~\cite{brockmann2006scaling}.
-Radius of gyration is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008understanding}, which is defined as fellows.   
+The displacement refers to an individual's re-allocation across the geographic space measured in distance, i.e., $distance (loc_{i} - loc_{i-1})$.
+It is not equivalent to a ``trip'' took by an individual, for example, even the time interval between two recorded locations is one month, it will still count as a displacement.
+By studying the collective displacements from a group people, it helps to identify the distance bounds associated with different travel modes~\cite{Jurdak2015} and to quantitatively differentiate the mobility patterns from random walks~\cite{brockmann2006scaling}.
+On the other hand, radius of gyration is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008understanding}, which is defined as fellows.   
 \newline
@@
 
-\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
-When applying the measurements to all the users, it helps to identify different groups of people and understand the corresponding mobility patterns.
-Note that both displacements and radius of gyrations are measured by ``crow's fly distance" in this study (i.e., the direct distance between two recorded locations).
-Since all these metrics are based on the generated trajectories, by breaking and aggregating the trajectories in multiple spatial scales and temporal granularity, it would enable performing multi-level spatiotemporal analysis of these measurements and studying the corresponding mobility patterns.
+\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, and therefore indicates the individual's spatial coverage, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
+When applying the measurement to the study population, it identifies different groups of people in terms of spatial coverage from their corresponding mobility patterns.
+Note that both displacements and radius of gyrations are measured by ``crow's fly distance'' in this study (i.e., the direct great-circle distance between two recorded locations).
+Since these metrics are based on the generated trajectories, by breaking and aggregating the trajectories in multiple spatial scales and temporal ranges, it enables performing multi-scale spatiotemporal analysis on these measurements and studying the corresponding mobility patterns.
 
@@
 It is similar to the map generation approach that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest~\cite{buttenfield1991map}.
-To enable aggregating Twitter trajectories into multiple spatial levels, we have extended the hierarchical space-time cube model developed in~\cite{cao2014scalable}, where we partitioned the geographic space of the United States into 10 hierarchical spatial layers.
-To be specific, the state boundaries of the United States are treated as the base layer (i.e.
+To enable aggregating Twitter trajectories into multiple spatial scales, we have extended the hierarchical space-time cube model developed in~\cite{cao2014scalable}, where we partitioned the geographic space of the continuous United States into 10 hierarchical spatial layers.
+To be specific, the state boundaries of the continuous United States are treated as the base layer (i.e.
 level 0) for aggregating state-level Twitter user movements, Alaska and Hawaii are excluded for the consideration of better visualization effects in the mapping interface of the framework.
-We then created an hierarchical fishnet by diving the study region into regular cells, where the finest level (level 10) consists 1km $\times$ 1km cells.
+We then created an hierarchical fishnet by diving the study region into regular cells, where the finest level (level 10) consists 1 km $\times$ 1 km cells.
 Such a cell size is consistent with the spatial resolution in landscan\footnote{http://web.ornl.gov/sci/landscan/} product for measuring the global population density.
 In our case, the cell size for level i-1 is twice of the size in level i.
-Figure 2 illustrates an hierarchical fishnet spatial units for mapping multi-level Twitter user movements.
-Note that any fine-grained geographic boundaries can be used and appended in this framework to show different level-of-detailed movements (e.g., county-level and census-tract level), in our case, we replaced the level 8 fishnet layer with the US county boundaries.
+Figure~\ref{fig:multilevel} illustrates an hierarchical fishnet spatial units for mapping multi-level Twitter user movements.
+Note that any predefined geographic boundaries can be used and appended in this framework to show different level-of-detailed movements (e.g., national-level and census-tract level), in our case, we replaced the level 8 fishnet layer with the US county boundaries.
 
@@
 A MapReduce algorithm for the spatial aggregation is implemented, where the ID of unit in each spatial layer (e.g., polygon in state and country layer and cell in the rest) is treated as key in the at the map stage.
-It performs a ``point-in-polygon" process to determine which polygon the point belongs to.
-If the location does not belong to any polygon, it will be dropped, which is how we used the geographic boundaries of the United States to filer the raw tweet collection and keep the ``domestic" ones.
+It performs a ``point-in-polygon" geospatial operation to determine which polygon the point belongs to.
+If the location does not belong to any polygon, it will be dropped, which is how we used the geographic boundaries of the continuous United States to filer the raw tweet collection that initially covered the North America and kept the ``domestic" ones.
 To optimize the ``point-in-polygon" determination without comparing the location with every polygon in the spatial layer, we also created a Quad-Tree~\cite{samet1984quadtree} for each spatial layer to speed up the process.
-Finally, the reducers generate two data outputs: (1) reconstructed space-time Twitter user trajectories at each spatial level (2) movement flows in the form of in and out volumes among the units.
-The movement flows are stored in the database for interactive explorations in the web mapping interface, whereas the re-constructed trajectories can be further processed to produce distance measures at different spatial scales, which is illustrated as fellows:
+Finally, the reducers generate two data outputs: (1) reconstructed space-time Twitter user trajectories at each spatial level (2) movement flows in the form of in and out movement flux between the spatial units.
+The movement flows are stored in the database for interactive explorations in the 3D web mapping interface, whereas the re-constructed trajectories can be further processed to produce distance measures at different spatial scales, which is illustrated as fellows:
 \newline
@@
 \subsection{Spatiotemporal Twitter user mobility patterns}
-The situation of using geo-located tweets to track people's movements is complex as users' tweeting behavior can be significantly different from one to another, in particular the frequency and time-interval between two consecutive tweets.
+The situation of using geo-located tweets as proxies to infer people's movements is complex as users' tweeting behavior can be significantly different from one to another, in particular, the frequency and time-interval between two consecutive tweets.
 For example, some people may tweet once a day while others do more; some people may tweet regularly while others do not.  
@@
 Many studies have carried out data collection within a certain time period (e.g., a year in our case).
-However, as the geo-located tweets were collected in a continuous fashion, we need to examine the sensitivities regarding these behaviors to make sure we are not just capturing a random snapshot from the whole data streams.
+However, as the geo-located tweets were collected in a continuous fashion, it is necessary to examine the sensitivities regarding these behaviors to make sure we are not just capturing a random snapshot from the whole data streams.
 
 In this study, we have analyzed the cumulative distribution of the frequency Twitter users visiting different locations in year 2014 (and every month), which uses the methods developed in~\cite{clauset2009power}.
-The frequency is summarized based on the trajectories of individuals extracted in each time range. Note that different groups of Twitter user may exist in each month. 
-It appears that the distribution of the collective Twitter user visitation behaviors in year 2014 follows a two-tiered power law distributions (shown in Figure 4), where the majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$ and the $\alpha$ value is 1.32, and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $p(x)\sim x^{-\alpha}$ with $\alpha$ value is 3.5.
+The frequency is summarized based on the trajectories of individuals extracted from a monthly time span.
+Note that different groups of Twitter user may exist in each month. 
+It appears that the distribution of the collective Twitter user visitation behaviors in year 2014 follows a two-tiered power law distributions (shown in Figure~\ref{fig:visitation}, where the majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$ and the $\alpha$ value is 1.32, and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $p(x)\sim x^{-\alpha}$ with $\alpha$ value is 3.5.
 This finding is consistent across all 12 months, with the mean $\alpha$ value as 1.34 $ \pm$  0.05 (standard deviation) and the mean $\lambda$ value as 0.00178 $ \pm$  0.0002 (standard deviation).
@@
 The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model~\cite{ reynolds2012truncated, rhee2011levy}, which has also been identified in many human mobility studies using different mobility data~\cite{zhao2015explaining}.
-The similarities among the cumulative distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which indicates studies collected geo-located tweets in one month can potentially reveal similar findings as the ones collected in multiple months.
-Of course, different spatial scales can effect such findings as we learned that there were no geo-located tweets collected from 4 counties.
-In addition, the two-tier power law also reveals the diversity in the Twitter user visiting behaviors: (1) a small group Twitter users visited significantly more locations than the rest (2) within each group, the probability of Twitter user visiting more locations decreases significantly with a power function.
+The similarities among the cumulative distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which indicates the collected geo-located tweets in one month can potentially reveal similar findings as the ones collected in multiple months.
+In addition, the two-tier power law also reveals the diversity in the Twitter user visiting behaviors: (1) a small group Twitter users visited significantly more locations than the others (2) within each group, the probability of Twitter user visiting more locations decreases significantly with a power function.
 
@@
 \caption{Two-tier power law distribution of the collective Twitter user visitation behaviors}
-\label{fig:Arch}
+\label{fig:visitation}
 \end{figure}
-%\FloatBarrier
+\FloatBarrier
 
-As it is mentioned earlier, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
-In this case, we first gathered the displacements from all the collected Twitter users in the United States (excluding Hawaii and Alaska) in year 2014, where those Twitter users with only one geo-located tweet were filtered out.
-In addition, to investigate the mobility patterns of individuals, we derived the accumulated displacements and the radius of gyrations of each individual Twitter user based on the corresponding space-time trajectories over the one year period.
-Note that both displacements and radius of gyrations were measured by ``crow's fly distance", which is the direct distance ($d$) between two consecutively recorded locations in a user's trajectory.
+As it is mentioned above, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
+In this case, we first gathered the displacements from all the collected Twitter users in the continuous United States in year 2014, where those Twitter users with only one geo-located tweet were filtered out.
+To investigate the mobility patterns of individuals, we also derived the accumulated displacements and the radius of gyrations of each individual Twitter user based on the corresponding space-time trajectories over the one year period.
+Note that both displacements and radius of gyrations were calculated by the direct great-circle distance ($d$) between two consecutively recorded locations in a user's trajectory.
 
 To seek mobility patterns from these measurements, we performed statistical analysis regarding the probability distributions of displacements and radius of gyrations, which is also known as the spatial dispersal kernel $P(d)$~\cite{brockmann2006scaling}.
-The probability distribution of the user displacements (as well as accumulated displacements) is shown in Figure 5, whereas the probability distribution of radius of gyrations is shown in Figure 6.
+The probability distribution of the user displacements (as well as accumulated displacements) is shown in Figure~\ref{fig:displacement}, whereas the probability distribution of radius of gyrations is shown in Figure~\ref{fig:gyration}.
 In this study, we used the fitting methods developed by~\cite{Jurdak2015}.
@@
 
-In particular, as it is shown in Figure 5 (a), the probability distributions of overall displacements is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10 m, 70m] (accounting for 2 $\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [100m, 80km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80km] (accounting for 5 $\%$ of the population).
-In additon, the displacement in the distance bound from 100m and 80km in Figure 5 (b) can be further approximately by two power-law distributions with a cutting point at 5km (53$\%$ distances are less than 5km and 40$\%$ distances between 5km and 80km), which indicates two different travel modes, such as inter- or intra-city movements.
-Overall, the fitting functions with different distance bound suggest the existence of multi-scale or multi-modal mobility patterns ~\cite{Jurdak2015} of the Twitter users in the United States, for example the displacements larger than 80km could be related to inter-state travels or travel by flight.
+In particular, as it is shown in Figure~\ref{fig:displacement} (a), the probability distribution of the overall displacements is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10 m, 70 m] (accounting for 2 $\%$ of the population), $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [100 m, 80 km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80 km] (accounting for 5 $\%$ of the population).
+In addition, the displacement in the distance bound from 100 m and 80 km in Figure~\ref{fig:displacement} (b) can be further approximately by two power-law distributions with a cutting point at 5 km (53$\%$ distances are less than 5 km and 40$\%$ distances between 5 km and 80 km), which indicates two different travel modes, such as inter- or intra-city movements.
+Overall, the fitting functions with different distance bounds suggest the existence of multi-scale or multi-modal mobility patterns~\cite{Jurdak2015} of the Twitter users in the continuous United States, for example the displacements larger than 80 km could be related to inter-state travels or travel by flight.
 
-The probability distribution of radius of gyrations of individuals (Figure 6 (a)) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10m$ from [10 m, 50m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50m, 30km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30km].
-In particular, the radius of gyration between 50m and 30km can be further approximately by two power law distributions with a cutting point at 6km, which suggest two main types of spatial coverage of from the collected Twitter users in the United States.
+The probability distribution of radius of gyrations of individuals at the national level (Figure~\ref{fig:gyration} (a)) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10m$ from [10 m, 50 m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50 m, 30 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30 km].
+In particular, the radius of gyration between 50 m and 30 km can be further approximately by two power law distributions with a cutting point at 6 km (Figure~\ref{fig:gyration} (b)), which suggest two main types of spatial coverage of from the collected Twitter users in the continuous United States.
 The distribution shows that around $10\%$ the tweet population has a radius of gyration less than 50 meters, which indicates those twitter users mostly tweet at a particular place, such as home or office;  around 60$\%$ of the population has a radius of gyration less than 30 km, which indicates that most of the collected Twitter user movements are ``short" distances, e.g., within a city locale.
@@
 \includegraphics[width=1.0\linewidth]{./figures/displacement}
-\caption{(a) The probability distribution of the collective Twitter user displacements P(d) (b) the distance between [100m, 80km] is approximated by a double power-law functions (c) The probability distribution of the accumulated displacements of individual Twitter users P(d) (d) The probability distribution of the accumulated displacements of individual Twitter users in 3 different months}
-\label{fig:Arch}
-\end{figure}\textbf{}
+\caption{(a) The probability distribution of the collective Twitter user displacements P(d) (b) the distance between [100 m, 80 km] is approximated by a double power-law functions (c) The probability distribution of the accumulated displacements of individual Twitter users P(d) (d) The probability distribution of the accumulated displacements of individual Twitter users in 3 different months}
+\label{fig:displacement}
+\end{figure}
 \FloatBarrier
+
+We also measured the distribution of the radius of gyration of Twitter users at different spatial scales, specifically, the state level and city level.
+In this study, we selected the state Illinois and California for comparisons at the state level (Figure~\ref{fig:gyration} (c)), whereas we chose Chicago city as an example (Figure~\ref{fig:gyration} (d)) at the city level.
+Interestingly but not surprisingly, the P($r_{g}$) at the state level can also be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.
+We noticed that distance bound of the radius of gyration at the state level is at 10 km instead of 30 km at the national level.
+The distance decay effects in larger spatial coverage [$>$ 30 km] slightly differ, in this case, the P($r_{g}$) decreases faster in smaller size state (i.e., Illinois) than the large size state (i.e., California).
+In particular, the P($r_{g}$) over Chicago city can be fitted by similar functions.
+However, as it reflects intra-city level mobility patterns, there is no distinct distance range to indicate large spatial coverage.
 
@@
 \centering
-\includegraphics[width=1.0\linewidth]{./figures/gyration}
-\caption{ (a) The probability distribution of radius of gyration of individual Twitter users P($r_{g}$) (b) the distance between [50m, 30 km] is approximated by a double power-law functions}
-\label{fig:Arch}
+\includegraphics[width=1.0\linewidth]{./figures/gyration2}
+\caption{ (a) The probability distribution of radius of gyration of individual Twitter users P($r_{g}$) at the national level (b) the distance between [50 m, 30 km] is approximated by a double power-law functions (c) P($r_{g}$) at the state level (Illinois and California) (d) P($r_{g}$) for Chicago city}
+\label{fig:gyration}
 \end{figure}
-%\FloatBarrier
+\FloatBarrier
 
-More importantly, as our framework can aggregate Twitter user trajectories within different temporal ranges, we further analyzed the probability distributions of accumulated displacements took places in January, June, and October (Figure 5 (d)) and radius of gyrations within 4 quarters in year 2014 (Figure 7), in order to examine whether there are temporal changes in the mobility patterns.
+On the other hand, as our framework can aggregate Twitter user trajectories within different temporal ranges, we further analyzed the probability distributions of accumulated displacements took places in January, June, and October (Figure~\ref{fig:displacement} (d)) and radius of gyrations within 4 quarters in year 2014 (Figure~\ref{fig:gyration_season}, in order to examine whether there are temporal changes in the mobility patterns.
 While the probability distributions of accumulated displacements are almost identical in those selected three months,  we do find changes in the probability distributions of radius of gyrations in different quarters of the year.
@@
 However, it is worthy noting that the overall trends in the Twitter user mobility patterns revealed by radius of gyrations are still consistent.
-In summary, by comparing these results with the same measurements in~\cite{Jurdak2015}, (slightly) different distance bounds were identified for describing the Twitter user mobility patterns in the USA and Australia, however the overall similarity and consistence found in using a combination of three functions to approximate the probability distribution functions of displacements and radius of gyrations, clearly provide supports for using geo-located tweets for conducting replicable human mobility studies.
 
-\begin{figure}[h]
+In summary, by comparing these results from different spatial scales and temporal ranges, different distance bounds were identified for describing the spatiotemporal Twitter user mobility patterns.
+However the overall similarity and consistence found in using a combination of three functions to approximate the probability distribution functions of displacements and radius of gyrations, clearly provide supports for using geo-located tweets as useful proxies for understanding human mobility patterns and conducting reproducible findings at multiple spatial scales and temporal ranges.
+
+\begin{figure}[ht]
 \centering
@@
 \caption{The probability distribution of radius of gyration of individual Twitter users in different quarters of year 2014}
-\label{fig:Arch}
+\label{fig:gyration_season}
 \end{figure}
-%\FloatBarrier
+\FloatBarrier
 
-The above analysis of Twitter user mobility patterns mainly focus on the temporal aspects where the spatial scale is fixed to the country level.
+The above analysis of Twitter user mobility patterns mainly focus on the spatiotemporal aspects.
 Our framework provides the flexibility to aggregate and extract Twitter user trajectories in a specific spatial scale and re-produce the analysis. 
-In particular, as it is evident from the above analysis that there are multi-scale or multi-modal Twitter user mobility patterns, this framework can help further look into the mobility pattern regarding how Twitter users move across different spatial scales and temporal ranges, which is measured by the movement flows among these spatial regions.
-In this case, we demonstrate the inter-state mobility patterns by using the framework to capture the movement flows among the states.
+In particular, as it is evident from the above analysis that there are multi-scale or multi-modal Twitter user mobility patterns, this framework can help further look into the mobility pattern regarding how Twitter users move across different spatial scales and temporal ranges, which is measured by the movement flows between these spatial units.
+In this case, we demonstrate the inter-state mobility patterns by using the framework to capture the movement flows between the states.
 Note that the movement flows can be summarized across all the 10 spatial layers in the framework.
-In particular, the movement flows in the state level are summarized and visualized with chord diagrams (illustrated in Figure 10) as part of the interactive mapping interface.
 We tested the overall distribution of the movement flows (in the form of weighted in-degree and out-degree of a graph, where each state is treated as a node) among different states in year 2014.
 We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states.
-It also indicates that although the Twitter population seems to be linearly correlated with the population at state level, it is not proportional to account the movement flux among the states, which may provide some insights for other researchers in studying social-economical aspects of the migration dynamics.
+It indicates that the Twitter population is not proportional to account the movement flux between the states, which may provide some insights for other researchers in studying social-economical aspects of the migration dynamics.
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
@@
 \caption{The distribution of Twitter user movement flows among different states in year 2014 measured in weighted in- and out-degrees}
-\label{fig:Arch}
+\label{fig:state_flow}
 \end{figure}
-%\FloatBarrier
+\FloatBarrier
 
@@
 
-An overview of the web mapping interface is shown in Figure 8.
+An overview of the 3D web mapping interface is shown in Figure~\ref{fig:Web_Interface}.
 In terms of performing exploratory visual-analytics of Twitter user movement patterns, users can specify the time window to enable the query. 
 When the results are shown, users can hover the mouse over each individual lines on the map to see the value of movement flows for both in and out directions.
-If the selected criteria keep unchanged, whenever the user zooms in/out, tilt or rotate the globe, the mapping interface will automatically provide the corresponding level-of-details on the fly.
+If the selected criteria keep unchanged, whenever the user zooms in/out, tilt or rotate the globe, the 3D virtual globe mapping interface will automatically provide the corresponding level-of-details on the fly.
+For example, Figure~\ref{fig:chicago} and Figure~\ref{fig:Chicago_airport} demonstrated the movement flows in different level-of-details around the Chicago city, and between O'Hare International Airport and the city center of Chicago city, where top 20 $\%$ movement flows were shown.
+The URL to access this 3D web mapping interfaces as well as the source code of the visual-analytics framework are available upon request.
 
@@
 \centering
-\includegraphics[width=0.8\linewidth]{./figures/vocation}
+\includegraphics[width=0.8\linewidth]{./figures/all}
 \caption{An overview of the 3D interactive web mapping interface}
@@
 
-For state level Twitter user movements, we provide an interactive chord diagram to explicitly illustrate the movement flows among different states (Figure 9).
-Figure 9 demonstrates the Twitter movement flows among different states in January, 2014.
-The size of each color patch is proportional to the volume of total incoming movements from other states, which allow us to visually identify those states that dominate the incoming movement flows and which states the flows are generated from.
-By interacting with the state names, it will highlight the details of incoming movement flows from other states, in this case California is selected, which has the largest incoming movement flows in January.\newline
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.8\linewidth]{./figures/Chicago}
+\caption{The top 20 $\%$ movement flows around Chicago city}
+\label{fig:chicago}
+\end{figure}
+\FloatBarrier
 
@@
 \centering
-\includegraphics[width=1.0\linewidth]{./figures/vaca_flow}
-\caption{Chord diagrams for the movement flows among different states in January, 2014}
-\label{fig:vaca_movement}
+\includegraphics[width=0.8\linewidth]{./figures/Chicago_airport}
+\caption{The top 20 $\%$ movement flows between O'Hare International Airport and the city center of Chicago city}
+\label{fig:Chicago_airport}
 \end{figure}
@@
 \section{Conclusions}
-In this study, we have used large volume of geo-located tweets to study Twitter user mobility patterns across multi-level spatial scales and temporal granularity in the United States during the year 2014.
-To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
+In this study, we have used large volume of geo-located tweets to study Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States during the year 2014.
+To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-scale spatiotemporal Twitter user mobility patterns.
 This framework is implemented based on high-performance distributed computing environment using Apache Hadoop.
@@
 These distributions can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.
-In particular, distance bounds between different fitting functions in displacement distribution reveals the existence of multi-scale or multi-modal mobility patterns of the Twitter users in the United States, whereas the distribution of radius of gyration reveals different groups of Tweet users with different types of spatial coverages.
-More importantly, we further studied these mobility patterns in different temporal scales to investigate the temporal changes in the mobility patterns. 
+In particular, distance bounds between different fitting functions in displacement distribution reveals the existence of multi-scale or multi-modal mobility patterns of the Twitter users, whereas the distribution of radius of gyration reveals different groups of Tweet users with different types of spatial coverages at multiple spatial scales.
+We further studied these mobility patterns in different temporal ranges to investigate the temporal changes in the mobility patterns. 
 We found that the accumulated displacements are almost identical in different months, while the long distance radius of gyration (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern.
+
+Finally, it is worth noting that the geo-located Twitter data is not able to generalize to the entire population.
+As the demographic information of the Twitter users cannot be easily identified, the results of delineated urban boundaries may not reflect a complete real-world image from human movements, which should be carefully considered in future studies.
+Nevertheless, as we have discussed in this paper that geo-located Twitter data show the advantages regarding the easy data accessibility, the large spatial coverage and massive sample size, our approach showed that such data can be a valuable proxy for understanding human mobility patterns across multiple spatial scales and temporal ranges.
+Also, our approach can be applied to the setting of other countries, which can be used to carry out comparative studies regarding spatiotemporal Twitter user mobility patterns.
 
@@
 %% optional
-\supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
+%\supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{All sources of funding of the study should be disclosed.
-Please clearly indicate grants that you have received in support of your research work.
-Clearly state if you received funds for covering the costs to publish in open access.}
+\acknowledgments{J.Y. would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
+D.Z. would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.
+The work also used the ROGER supercomputer, which is supported by NSF under grant number: 1429699.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``X.X.
-and Y.Y.
-conceived and designed the experiments; X.X.
-performed the experiments; X.X.
-and Y.Y.
-analyzed the data; W.W.
-contributed reagents/materials/analysis tools; Y.Y.
-wrote the paper.'' Authorship must be limited to those who have contributed substantially to the work reported.}
+\authorcontributions{J.Y. conceived and designed the experiments; J.Y. and D.Z. wrote the paper.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictofinterests{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.}
+\conflictofinterests{The authors declare no conflict of interest.
+The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results.}
 

### 2016-08-18 semantic_decomposition_of_twitter_user_locations/paper.tex
xx

\documentclass[a4paper,11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{lastpage,fancyhdr,graphicx}
\graphicspath{ {/figure/} }
\usepackage{authblk}

\begin{document}
\title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
\author[1]{Junjun Yin\thanks{yinjunjun@gmail.com}}
\affil[1]{Department of Geography and Geographic Information Science}
\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
\renewcommand\Authands{ and }
\maketitle

\section*{Abstract}
Today's pervasive Location Based Social Media provide abundant user-generated geographic information
In this paper, we present a scalable data integration 
We analyzed the

\section{Introduction}

\section{Related Work}

\section{Methods and Materials}
\subsection{Geo-located Twitter Data}
Geo-located Twitter data refer to

\section{Results}

\section{Discussions and Conclusions}

\end{document}

### 2016-08-18 sq_mobility/main.tex
template

\documentclass[fleqn,10pt]{wlscirep}
\title{Scientific Reports Title to see here (20 words or less)}

\author[1,*]{Alice Author}
\author[2]{Bob Author}
\author[1,2,+]{Christine Author}
\author[2,+]{Derek Author}
\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}

\affil[*]{corresponding.author@email.example}

\affil[+]{these authors contributed equally to this work}

%\keywords{Keyword1, Keyword2, Keyword3}

\begin{abstract}
Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. 
\end{abstract}
\begin{document}

\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
\thispagestyle{empty}

\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.

\section*{Introduction}

The Introduction section, of referenced text\cite{Figueredo:2009dg} expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.

\section*{Results}

Up to three levels of \textbf{subheading} are permitted. Subheadings should not be numbered.

\subsection*{Subsection}

Example text under a subsection. Bulleted lists may be used where appropriate, e.g.

\begin{itemize}
\item First item
\item Second item
\end{itemize}

\subsubsection*{Third-level section}

Topical subheadings are allowed.

\section*{Discussion}

The Discussion should be succinct and must not contain subheadings.

\section*{Methods}

Topical subheadings are allowed. Authors must ensure that their Methods section includes adequate experimental and characterization data necessary for others in the field to reproduce their work.

\bibliography{ref}

\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu. Use the cite command for an inline citation, e.g.  \cite{Figueredo:2009dg}. \cite{Figueredo:2009dg}

\section*{Acknowledgements (not compulsory)}

Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.

\section*{Author contributions statement}

Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript.

\section*{Additional information}

To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing financial interests} (mandatory statement).

The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing financial interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{stream}
\caption{Legend (350 words max). Example legend text.}
\label{fig:stream}
\end{figure}

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
Condition & n & p \\
\hline
A & 5 & 0.1 \\
\hline
B & 10 & 0.01 \\
\hline
\end{tabular}
\caption{\label{tab:example}Legend (350 words max). Example legend text.}
\end{table}

%Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.

\end{document}

### 2016-08-18 sq_mobility/sq_mobility_twitter.tex
xx
template

@@
-\documentclass[a4paper,11pt]{article}
-\usepackage[margin=1in]{geometry}
-\usepackage{lastpage,fancyhdr,graphicx}
+\documentclass[fleqn,10pt]{wlscirep}
+\usepackage{graphicx}
 \graphicspath{ {/figure/} }
-\usepackage{authblk}
+
+%\title{Mining sequential mobility patterns from semantic Twitter user trajectories}
+%\title{Sequential mobility patterns in people's daily life: Evidence from}
+\title{Preferential Return Behaviors in People's Daily Life: Evidence from semantic enriched geo-located Twitter data}
+\author[1,+]{Junjun  Yin}
+\author[1,2,+]{Myeonghun Jeong}
+\author[2,3,*]{Zhenhong Du}
+\affil[1]{Department of Geography and Geographic Information Science}
+\affil[2]{CyberGIS Center for Advanced Digitial and Spatial Studies}
+\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
+\affil[3]{Zhejiang University}
+\affil[*]{duzhenhong.zju@gmail.com}
+\affil[+]{these authors contributed equally to this work}
+
+%\keywords{Keyword1, Keyword2, Keyword3}
+
+\begin{abstract}
+Example Abstract.
+Abstract must be under 200 words and not include subheadings or citations.
+Example Abstract.
+Abstract must be under 200 words and not include subheadings or citations.
+Example Abstract.
+Abstract must be under 200 words and not include subheadings or citations.
+Example Abstract.
+Abstract must be under 200 words and not include subheadings or citations.
+Example Abstract.
+Abstract must be under 200 words and not include subheadings or citations.
+Example Abstract.
+Abstract must be under 200 words and not include subheadings or citations.
+Example Abstract.
+Abstract must be under 200 words and not include subheadings or citations.
+Example Abstract.
+Abstract must be under 200 words and not include subheadings or citations.
+\end{abstract}
 
 \begin{document}
-%\title{Mining sequential mobility patterns from semantic Twitter user trajectories}
-\title{Sequential mobility patterns in people's daily life}
-\author[1]{Junjun Yin}
-\author[2]{Chao Zhang}
-\author[1]{Shaowen Wang\thanks{shaowen@illinois.edu}}
-\affil[1]{CyberGIS Center for Advanced Digtial and Spatial Studies}
-\affil[2]{Department of Computer Science}
-\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
-
-\renewcommand\Authands{ and }
-
+\flushbottom
 \maketitle
-
-\section*{\centering Abstract}
-Understanding human mobility patterns
 
@@
 	\caption{{\bf The shape of Twitter user mobility in Chicago for year 2014}}
-	\label{Fig_shape}
+	\label{first_time_passage}
 \end{figure}
@@
 
+\bibliography{ref}
+
 \end{document}

### 2016-08-18 sq_mobility/main.tex
ref

@@
 
-The Introduction section, of referenced text\cite{Figueredo:2009dg} expands on the background of the work (some overlap with the Abstract is acceptable).
-The introduction should not include subheadings.
+The Introduction section, of referenced text\cite{hawelka2014geo} expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.
 
@@
 
-\bibliography{ref}
-
 \noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu.
 Use the cite command for an inline citation, e.g.
-\cite{Figueredo:2009dg}.
-\cite{Figueredo:2009dg}
+\cite{padmanabhan2014flumapper}.
 
@@
 %Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.
+\bibliography{ref}
+%\bibliographystyle{ref}
 

### 2016-08-21 semantic_decomposition_of_twitter_user_locations/paper.tex
mac

@@
 \begin{document}
-\title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
-\author[1]{Junjun Yin\thanks{yinjunjun@gmail.com}}
+% \title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
+\title{A tale of two cities: A data synthesis approach for semantic decompositions of Twitter user locations}
+\author[1~\thanks{yinjunjun@gmail.com}]{Junjun Yin}
 \affil[1]{Department of Geography and Geographic Information Science}
@@
 \section*{Abstract}
+
 Today's pervasive Location Based Social Media provide abundant user-generated geographic information
@@
 \section{Introduction}
+Today's pervasive Location Based Social Media (LBSM) are attacting much attention from many researh displines. For example,
 
@@
 
+\subsection{A scalable data synthesis framework}
+
 \section{Results}

### 2016-09-03 MovePattern_IJGI/IJGI_revision/Twitter_MovementPatterns_VisualAnalytics_v2.tex
xxx

--- 2016-08-14 MovePattern_IJGI/IJGI/Twitter_MovementPatterns_VisualAnalytics.tex
@@
 However, such mobility data do not provide detailed human movements with fine-grained spatial and temporal granularity, which are usually aggregated and therefore are limited to capture mobility patterns of individuals~\cite{gonzalez2008understanding,Jurdak2015}.
-In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints in the form of real-world user trails and footprints~\cite{thatcher2014living}.
+In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, emerging as a new mobility data source, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints in the form of real-world user trails and footprints~\cite{thatcher2014living}.
 A significant advantage of utilizing LBSM data streams as proxies for studying human mobility patterns is the large spatial coverage.
@@
 However, the variations of movements in different spatial scales and temporal ranges are neglected in these studies, where the measurements of distances are either fixed in a certain time range or to a specific geographic region.
-For instances, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national level), are lacking.
+For instances, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national levels), are lacking.
 Such insights are critical to advance our understandings of the collective mobility patterns for various applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
@@
 We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions.
-In particular, the Twitter user mobility patterns measured by the user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
+In particular, Twitter user mobility patterns measured by user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
 By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
@@
 \subsection{Geo-located Twitter data for studying large-scale user movements}
-To understand detailed mobility patterns of individuals, the capability of capturing human movements with fine-grained spatial and temporal granularity is critical.
-In terms of collecting detailed mobility data of individuals, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\cite{zheng2008understanding}.
-However, the data are often limited in spatial scale (e.g.
-within a specific city or region) with a small group of people, for example, 226 and 182 volunteers participated in collecting such mobility data in~\cite{rhee2011levy} and~\cite{zheng2010geolife} respectively.
-Other than tracking people directly, the vehicle-based GPS traces are often tied to specific vehicles (e.g.
-taxi), which are only accessible for a certain group of people~\cite{kung2014exploring}.
+To understand detailed mobility patterns of individuals, the capability to capture human movements with fine-grained spatial and temporal granularity is critical.
+In this connection, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\cite{zheng2008understanding}.
+However, such data are often limited in spatial scale (e.g.
+within a specific city or region) from a small group of people, for example, 226 and 182 volunteers participated in collecting such mobility data in~\cite{rhee2011levy} and~\cite{zheng2010geolife} respectively.
+Other than tracking people directly, the vehicle-based GPS traces are often tied to specific vehicles (e.g. taxi), which are only accessible for a certain group of people~\cite{kung2014exploring}.
 
-Another approach from the literatures for studying human mobility is using mobile phone call data, such as Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
+Another approach from the literatures for studying human mobility is using mobile phone call data, such as Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with an accuracy in the order of kilometers~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
 Such a dataset can cover relatively large spatial scale~\cite{becker2013human,sobolevsky2013delineating} (e.g., national level) and a large portion of the population in the study region~\cite{kung2014exploring}.
@@
 Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
-It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy access to its data, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.
+It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy data access, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.
 
@@
 \noindent\emph{\textbf{Definition 2.
-visitation behavior, displacement and radius of gyration:}} As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers the frequency of a user visiting different locations within a specific time frame.
+Visitation behavior, displacement and radius of gyration:}} As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers the frequency of a user visiting different locations within a specific time frame.
 This metric provides an overall assessment regarding the diversity and similarity in the collective mobility pattern~\cite{gao2012exploring}.
@@
 The displacement refers to an individual's re-allocation across the geographic space measured in distance, i.e., $distance (loc_{i} - loc_{i-1})$.
-It is not equivalent to a ``trip'' took by an individual, for example, even the time interval between two recorded locations is one month, it will still count as a displacement.
+It is not equivalent to a ``trip'' took by an individual, for instance, even the time interval between two recorded locations is one month, it will still count as a displacement.
 By studying the collective displacements from a group people, it helps to identify the distance bounds associated with different travel modes~\cite{Jurdak2015} and to quantitatively differentiate the mobility patterns from random walks~\cite{brockmann2006scaling}.
-On the other hand, radius of gyration is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008understanding}, which is defined as fellows.   
+On the other hand, radius of gyration (donated as $r_{g}$) is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008understanding}, which is defined as fellows.
 \newline
@@
 
-\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, and therefore indicates the individual's spatial coverage, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
+\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, and therefore indicates the individual's spatial coverage, where $p_{i}$ and $p_{centroid}$ are the $ith$ location and the geometric center of the user's trajectory, respectively.
 When applying the measurement to the study population, it identifies different groups of people in terms of spatial coverage from their corresponding mobility patterns.
@@
 \subsection{Multi-level spatiotemporal trajectory aggregation}
-An important strategy for visual-analytics methods dealing with massive movement datasets is performing spatial aggregations to provide different levels-of-detail~\cite{andrienko2007designing,andrienko2007visual}.
+An important strategy for visual-analytics methods to deal with massive movement datasets is performing spatial aggregations to provide different levels-of-detail~\cite{andrienko2007designing,andrienko2007visual}.
 It is similar to the map generation approach that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest~\cite{buttenfield1991map}.
@@
 The frequency is summarized based on the trajectories of individuals extracted from a monthly time span.
-Note that different groups of Twitter user may exist in each month. 
+Note that different groups of Twitter users may exist in each month. 
 It appears that the distribution of the collective Twitter user visitation behaviors in year 2014 follows a two-tiered power law distributions (shown in Figure~\ref{fig:visitation}, where the majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$ and the $\alpha$ value is 1.32, and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $p(x)\sim x^{-\alpha}$ with $\alpha$ value is 3.5.
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
-\includegraphics[width=1.0\linewidth]{./figures/visitation2}
+\includegraphics[width=1.0\linewidth]{./figures/visitation}
 \caption{Two-tier power law distribution of the collective Twitter user visitation behaviors}
@@
 
-As it is mentioned above, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
+As it is aforementioned, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
 In this case, we first gathered the displacements from all the collected Twitter users in the continuous United States in year 2014, where those Twitter users with only one geo-located tweet were filtered out.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{J.Y. would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
+\acknowledgments{
+The authors would like to thank the four reviewers of IJGI for their constructive comments that better shaped the paper.
+J.Y. would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
 D.Z. would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.

### 2016-09-07 MovePattern_IJGI/IJGI_revision/Twitter_MovementPatterns_VisualAnalytics_v2.tex
home

@@
 In this connection, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\cite{zheng2008understanding}.
-However, such data are often limited in spatial scale (e.g.
-within a specific city or region) from a small group of people, for example, 226 and 182 volunteers participated in collecting such mobility data in~\cite{rhee2011levy} and~\cite{zheng2010geolife} respectively.
+However, such data are often limited in spatial scale (e.g., within a specific city or region) from a small group of people, for example, 226 and 182 volunteers participated in collecting such mobility data in~\cite{rhee2011levy} and~\cite{zheng2010geolife} respectively.
 Other than tracking people directly, the vehicle-based GPS traces are often tied to specific vehicles (e.g. taxi), which are only accessible for a certain group of people~\cite{kung2014exploring}.
@@
 Even such data were obtained in the mentioned studies, they came from various service providers covering different groups of users.
-These issues limit the capability for conducting reproducible scientific findings regarding mobility research, such as validating or extending the existing discoveries.
+These issues limit the capability for conducting reproducible scientific findings for mobility research, such as validating or extending the existing discoveries.
 
@@
 LBSM enables users to attach their current location as a geo-tag to the message they post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
-A Big Data scenario emerges when millions social media users constantly posting messages.
+A Big Data scenario emerges when millions social media users constantly post messages.
 In this study, geo-located Twitter data are chosen as a source for studying detailed mobility patterns.
 Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
-It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy data access, in fact, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.
+It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy data access.
+Indeed, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.
 
@@
 For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place.
-There is a potential mismatch regarding the representativeness of the overall population as not all people use social media or send geo-located messages~\cite{kung2014exploring} and the demographic information of the Twitter users cannot be easily identified, the derived mobility patterns may lead to an over or under-representation of the real-world mobility patterns.
+There is a potential mismatch regarding the representativeness of the overall population since not all people use social media or send geo-located messages~\cite{kung2014exploring}, the demographic information of the Twitter users cannot be easily identified.
+The derived mobility patterns may lead to an over or under-representation of the real-world human mobility patterns.
 Many studies started to look into the demographic information of LBSM data, in particular Twitter data~\cite{mitchell2013geography,longley2015geotemporal}.
@@
 For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\cite{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\cite{hawelka2014geo}, which is almost impossible for other mobility datasets.
-More importantly, by continuously monitoring the geo-located Twitter data streams with large volumes of detailed and frequently updated spatiotemporal records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements), which is one of the motivations for this study.
+More importantly, by continuously monitoring the geo-located Twitter data streams with large volume of detailed and frequently updated spatiotemporal records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements), which is one of the motivations for this study.
 
 \subsection{Data-intensive challenges for multi-scale geo-visual analytics}
-Mobility data are essentially a collection of spatiotemporal records of people moving from one location to another across the geographic space.
+Mobility data are essentially a collection of spatiotemporal records of people re-allocating across the geographic space.
 To study mobility patterns of individuals, a space-time trajectory of each individual user should be modeled and constructed to quantify the collective movements over space and time.
@@
 countries, states, and cities, etc.) and identify the changes over space and time~\cite{maceachren2001research, maceachren2004maps}.
-In this regard, visual-analytics methods are proposed to help better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\cite{andrienko2007designing,andrienko2007visual}.
+In this regard, visual-analytics methods are proposed to better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\cite{andrienko2007designing,andrienko2007visual}.
 Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\cite{andrienko2007designing}.

### 2016-09-08 MovePattern_IJGI/IJGI_revision/Twitter_MovementPatterns_VisualAnalytics_v2.tex
half

@@
 However, the variations of movements in different spatial scales and temporal ranges are neglected in these studies, where the measurements of distances are either fixed in a certain time range or to a specific geographic region.
-For instances, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national levels), are lacking.
+For instances, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national levels) are lacking.
 Such insights are critical to advance our understandings of the collective mobility patterns for various applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
@@
 To ensure complete coverage over the continuous United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
-The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2GB in size) collected per day.
+The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2 GB in size) collected per day.
 We have collected more than 1.3 billion geo-located tweets from 1$^{st}$ January to 31$^{st}$ December, 2014 with 6,147,430 Twitter users and 1 TB in file size.
@@
 Based on this definition for modeling the space-time Twitter user trajectories, we converted the process of extracting trajectories from the raw geo-located Twitter data as a MapReduce task.
-Specifically, each mapper utilizes the unique user id as a key to prepares the records that belong to the same user and send them to reducer.
+Specifically, each mapper utilizes the unique user id as a key to prepares the records that belong to the same user and send them to a reducer.
 Once the reducers receive the $\langle key, value\rangle$ pairs, a Twitter user's space-time trajectory is formed by the sorting the locations in chronological order while considering the speed limit.
@@
 By studying the collective displacements from a group people, it helps to identify the distance bounds associated with different travel modes~\cite{Jurdak2015} and to quantitatively differentiate the mobility patterns from random walks~\cite{brockmann2006scaling}.
-On the other hand, radius of gyration (donated as $r_{g}$) is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008understanding}, which is defined as fellows.
+On the other hand, radius of gyration (donated as $r_{g}$) is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008understanding}, which is defined as follows.
 \newline
@@
 
-In particular, as it is shown in Figure~\ref{fig:displacement} (a), the probability distribution of the overall displacements is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10 m, 70 m] (accounting for 2 $\%$ of the population), $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [100 m, 80 km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80 km] (accounting for 5 $\%$ of the population).
+In particular, as it is shown in Figure~\ref{fig:displacement} (a), the probability distribution of the overall displacements is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10~m$ from [10 m, 70 m] (accounting for 2 $\%$ of the population), $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min}=100~m$ from [100 m, 80 km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80 km] (accounting for 5 $\%$ of the population).
 In addition, the displacement in the distance bound from 100 m and 80 km in Figure~\ref{fig:displacement} (b) can be further approximately by two power-law distributions with a cutting point at 5 km (53$\%$ distances are less than 5 km and 40$\%$ distances between 5 km and 80 km), which indicates two different travel modes, such as inter- or intra-city movements.
@@
 
-The probability distribution of radius of gyrations of individuals at the national level (Figure~\ref{fig:gyration} (a)) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10m$ from [10 m, 50 m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50 m, 30 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30 km].
+The probability distribution of radius of gyrations of individuals at the national level (Figure~\ref{fig:gyration} (a)) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10~m$ from [10 m, 50 m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50 m, 30 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30 km].
 In particular, the radius of gyration between 50 m and 30 km can be further approximately by two power law distributions with a cutting point at 6 km (Figure~\ref{fig:gyration} (b)), which suggest two main types of spatial coverage of from the collected Twitter users in the continuous United States.
@@
 \subsection{The interactive 3D virtual globe web mapping interface}
-In addition to providing supports for understanding Twitter user mobility patterns with statistical analysis, the framework integrates a 3D virtual globe interface to enable users to perform exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements.
+In addition to providing supports for understanding Twitter user mobility patterns with statistical analysis, the framework integrates a 3D virtual globe interface to enable users to perform exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements\footnote{http://sandbox.cigi.illinois.edu/home/apps.php?app=movepattern}.
 The 3D virtual globe is developed and extended from the Cesium library\footnote{http://cesiumjs.org/}, which is an open-source WebGL virtual globe and map engine. 
@@
 The map interface interprets user's interactions, such as area-of-interest, time window, and zoom levels, etc.
-as parameters and send to the dedicated visualization servlet on the CyberGIS Gateway\footnote{http://sandbox.cigi.illinois.edu/home/}, which is the leading online cyberGIS environment for a large number of users to perform computing- and data-intensive, and collaborative geospatial problem-solving enabled by advanced cyberinfrastructure~\cite{liu2014cybergis}.
+as parameters and send to the dedicated visualization servlet on the CyberGIS Gateway, which is the leading online cyberGIS environment for a large number of users to perform computing- and data-intensive, and collaborative geospatial problem-solving enabled by advanced cyberinfrastructure~\cite{liu2014cybergis}.
 In return, the map interface visualizes the corresponding movement flows on the virtual globe.
@@
 For example, Figure~\ref{fig:chicago} and Figure~\ref{fig:Chicago_airport} demonstrated the movement flows in different level-of-details around the Chicago city, and between O'Hare International Airport and the city center of Chicago city, where top 20 $\%$ movement flows were shown.
-The URL to access this 3D web mapping interfaces as well as the source code of the visual-analytics framework are available upon request.
+The source code of the visual-analytics framework is available upon request.
 
@@
 These distributions can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.
-In particular, distance bounds between different fitting functions in displacement distribution reveals the existence of multi-scale or multi-modal mobility patterns of the Twitter users, whereas the distribution of radius of gyration reveals different groups of Tweet users with different types of spatial coverages at multiple spatial scales.
+In particular, distance bounds between different fitting functions in displacement distribution reveals the existence of multi-scale or multi-modal mobility patterns of the Twitter users, whereas the distribution of radius of gyration reveals different groups of Twitter users with different types of spatial coverages at multiple spatial scales.
 We further studied these mobility patterns in different temporal ranges to investigate the temporal changes in the mobility patterns. 

### 2016-09-09 MovePattern_IJGI/IJGI_revision/Twitter_MovementPatterns_VisualAnalytics_v2.tex
draft

@@
 A significant advantage of utilizing LBSM data streams as proxies for studying human mobility patterns is the large spatial coverage.
-For instance, researchers have used geo-located Twitter data for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible for other mobility datasets (e.g., GPS traces and mobile phone call records).
+For instance, researchers have used geo-located tweets for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible for other mobility datasets (e.g., GPS traces and mobile phone call records).
 Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}, the publicly available LBSM data streams offer unique opportunities for conducting reproducible and comparative scientific findings across different geographic regions.
 
-Many recent studies have adopted the LBSM data streams to study human mobility patterns.
+Many recent studies have adopted LBSM data streams to study human mobility patterns.
 For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects in the collective user movements~\cite{gonzalez2008understanding}, which were used to reveal different travel modes~\cite{Jurdak2015}, travel demands~\cite{wu2014intra,hasan2013understanding}, and the impact of social connections~\cite{cho2011friendship}.
@@
 By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
-In particular, our approach provides an interactive 3D virtual globe web mapping interface to enable exploratory geo-visual analytics for understanding the detailed Twitter user movement flows within a given spatial scale and time window.
+In addition, our approach provides an interactive 3D virtual globe web mapping interface to enable exploratory geo-visual analytics for understanding the detailed Twitter user movement flows within a given spatial scale and time window.
 
@@
 For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place.
-There is a potential mismatch regarding the representativeness of the overall population since not all people use social media or send geo-located messages~\cite{kung2014exploring}, the demographic information of the Twitter users cannot be easily identified.
+Although geo-located tweets tend to provide geo-locations with high position resolution as aforementioned~\cite{Jurdak2015}, the information regarding the quality of the geo-locations is absent in each tweet.
+This will contribute to the uncertainties in calculating the distance of Twitter user movements, especially in densely built environments.   
+There is also a potential mismatch regarding the representativeness of the overall population since not all people use social media or send geo-located messages~\cite{kung2014exploring}, the demographic information of the Twitter users cannot be easily identified.
 The derived mobility patterns may lead to an over or under-representation of the real-world human mobility patterns.
@@
 Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of user displacements and radius of gyrations of individuals, to study the mobility dynamics.
-At the same time, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\cite{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal ranges.
-For example, a geo-visualization approach was used to study human activity patterns, where user trajectories are mapped in a 3D space ordered by timestamps in the third dimension~\cite{kwan2004geovisualization}.
+Indeed, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\cite{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal ranges.
+For example, a geo-visualization approach was used to study human activity patterns, where user trajectories were mapped in a 3D space ordered by timestamps in the third dimension~\cite{kwan2004geovisualization}.
 While such an approach enables visualization of individual trajectories, its capability is limited in dealing with large-volume movement datasets~\cite{andrienko2007designing}.
-Instead of directly visualizing individual user trajectories, a space-time cube approach was proposed to analyzing and visualizing the collective trajectories.
-It provides flexibilities in setting up both spatial scales and temporal ranges, and therefore is used to study mobility patterns across different spatial units (e.g.
-countries, states, and cities, etc.) and identify the changes over space and time~\cite{maceachren2001research, maceachren2004maps}.
+Instead of directly visualizing an individual user's trajectories, a space-time cube approach was proposed to analyzing and visualizing the collective trajectories.
+It provides flexibilities in setting up both spatial scales and temporal ranges, and therefore is used to study mobility patterns across different spatial units (e.g., countries, states, and cities, etc.) and identify the changes over space and time~\cite{maceachren2001research, maceachren2004maps}.
 In this regard, visual-analytics methods are proposed to better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\cite{andrienko2007designing,andrienko2007visual}.
@@
 We have collected more than 1.3 billion geo-located tweets from 1$^{st}$ January to 31$^{st}$ December, 2014 with 6,147,430 Twitter users and 1 TB in file size.
+In particular, this data collection of year 2014 was originally used to map the spatial spread of flu in North America during the time period~\cite{padmanabhan2014flumapper}.
 
@@
 \centering
-\includegraphics[width=0.6\linewidth]{./figures/Overall_Architecture222}
+\includegraphics[width=0.55\linewidth]{./figures/Overall_Architecture222}
 \caption{The overall system architecture of the framework}
@@
 It is similar to the map generation approach that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest~\cite{buttenfield1991map}.
-To enable aggregating Twitter trajectories into multiple spatial scales, we have extended the hierarchical space-time cube model developed in~\cite{cao2014scalable}, where we partitioned the geographic space of the continuous United States into 10 hierarchical spatial layers.
-To be specific, the state boundaries of the continuous United States are treated as the base layer (i.e.
+To enable aggregating Twitter trajectories into multiple spatial scales, we have extended the hierarchical space-time cube model developed in~\cite{cao2014scalable}, where we partitioned the geographic space of the continuous United States into 10 hierarchical spatial layers and each space-time cube is created with a fixed time window of a week interval.
+Specifically, the state boundaries of the continuous United States are treated as the base layer (i.e.
 level 0) for aggregating state-level Twitter user movements, Alaska and Hawaii are excluded for the consideration of better visualization effects in the mapping interface of the framework.
@@
 Such a cell size is consistent with the spatial resolution in landscan\footnote{http://web.ornl.gov/sci/landscan/} product for measuring the global population density.
-In our case, the cell size for level i-1 is twice of the size in level i.
+In our case, the cell width/height for level i-1 is twice of the size in level i.
 Figure~\ref{fig:multilevel} illustrates an hierarchical fishnet spatial units for mapping multi-level Twitter user movements.
@@
 A MapReduce algorithm for the spatial aggregation is implemented, where the ID of unit in each spatial layer (e.g., polygon in state and country layer and cell in the rest) is treated as key in the at the map stage.
-It performs a ``point-in-polygon" geospatial operation to determine which polygon the point belongs to.
-If the location does not belong to any polygon, it will be dropped, which is how we used the geographic boundaries of the continuous United States to filer the raw tweet collection that initially covered the North America and kept the ``domestic" ones.
-To optimize the ``point-in-polygon" determination without comparing the location with every polygon in the spatial layer, we also created a Quad-Tree~\cite{samet1984quadtree} for each spatial layer to speed up the process.
+It performs a ``point-in-polygon'' geospatial operation to determine which polygon the point belongs to.
+If the location does not belong to any polygon, it will be dropped, which is how we used the geographic boundaries of the continuous United States to filer the raw tweet collection that initially covered the North America and kept the ``domestic'' ones.
+To optimize the ``point-in-polygon'' determination without comparing the location with every polygon in the spatial layer, we also created a Quad-Tree~\cite{samet1984quadtree} for each spatial layer to speed up the process.
 Finally, the reducers generate two data outputs: (1) reconstructed space-time Twitter user trajectories at each spatial level (2) movement flows in the form of in and out movement flux between the spatial units.
@@
 Many studies have carried out data collection within a certain time period (e.g., a year in our case).
-However, as the geo-located tweets were collected in a continuous fashion, it is necessary to examine the sensitivities regarding these behaviors to make sure we are not just capturing a random snapshot from the whole data streams.
+However, as the geo-located tweets were collected in a continuous fashion, it is necessary to examine the sensitivities regarding these behaviors to ensure we are not just capturing a random snapshot from the whole data streams.
 
@@
 Note that different groups of Twitter users may exist in each month. 
-It appears that the distribution of the collective Twitter user visitation behaviors in year 2014 follows a two-tiered power law distributions (shown in Figure~\ref{fig:visitation}, where the majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$ and the $\alpha$ value is 1.32, and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $p(x)\sim x^{-\alpha}$ with $\alpha$ value is 3.5.
+It appears that the distribution of the collective Twitter user visitation behaviors in year 2014 follows a two-tiered power law distributions (shown in Figure~\ref{fig:visitation}.
+The majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$, where $x$ is the number of visited locations and the $\alpha$ value is 1.32.
+The tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $p(x)\sim x^{-\alpha}$ with $\alpha$ value is 3.5.
 This finding is consistent across all 12 months, with the mean $\alpha$ value as 1.34 $ \pm$  0.05 (standard deviation) and the mean $\lambda$ value as 0.00178 $ \pm$  0.0002 (standard deviation).
@@
 
-In particular, as it is shown in Figure~\ref{fig:displacement} (a), the probability distribution of the overall displacements is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10~m$ from [10 m, 70 m] (accounting for 2 $\%$ of the population), $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min}=100~m$ from [100 m, 80 km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80 km] (accounting for 5 $\%$ of the population).
+Figure~\ref{fig:displacement} (a) shows the probability distribution of the overall displacements, which is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10~m$ from [10 m, 70 m] (accounting for 2 $\%$ of the population), $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min}=100~m$ from [100 m, 80 km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80 km] (accounting for 5 $\%$ of the population).
 In addition, the displacement in the distance bound from 100 m and 80 km in Figure~\ref{fig:displacement} (b) can be further approximately by two power-law distributions with a cutting point at 5 km (53$\%$ distances are less than 5 km and 40$\%$ distances between 5 km and 80 km), which indicates two different travel modes, such as inter- or intra-city movements.
-Overall, the fitting functions with different distance bounds suggest the existence of multi-scale or multi-modal mobility patterns~\cite{Jurdak2015} of the Twitter users in the continuous United States, for example the displacements larger than 80 km could be related to inter-state travels or travel by flight.
+Overall, the fitting functions with different distance bounds suggest the existence of multi-scale or multi-modal mobility patterns~\cite{Jurdak2015} of the Twitter users in the continuous United States, for example, the displacements larger than 80 km could be related to inter-state travels and stronger distance decay effects are observed in longer distance travels.
 
@@
 In particular, the radius of gyration between 50 m and 30 km can be further approximately by two power law distributions with a cutting point at 6 km (Figure~\ref{fig:gyration} (b)), which suggest two main types of spatial coverage of from the collected Twitter users in the continuous United States.
-The distribution shows that around $10\%$ the tweet population has a radius of gyration less than 50 meters, which indicates those twitter users mostly tweet at a particular place, such as home or office;  around 60$\%$ of the population has a radius of gyration less than 30 km, which indicates that most of the collected Twitter user movements are ``short" distances, e.g., within a city locale.
+The distribution shows that around $10\%$ the tweet population has a radius of gyration less than 50 meters, which indicates those twitter users mostly tweet at a particular place, such as home or office;  around 60$\%$ of the population has a radius of gyration less than 30 km, which indicates that most of the collected Twitter user movements are ``short'' distances, e.g., within a city locale.
 Note that the accuracy of these values for defining the distance bound depends on the accuracy of the location information of each geo-located tweet.
@@
 
-The above analysis of Twitter user mobility patterns mainly focus on the spatiotemporal aspects.
+The above analysis of Twitter user mobility patterns mainly focuses on the spatiotemporal aspects.
 Our framework provides the flexibility to aggregate and extract Twitter user trajectories in a specific spatial scale and re-produce the analysis.
 In particular, as it is evident from the above analysis that there are multi-scale or multi-modal Twitter user mobility patterns, this framework can help further look into the mobility pattern regarding how Twitter users move across different spatial scales and temporal ranges, which is measured by the movement flows between these spatial units.
+The movement flows are obtained by aggregating the movements that started from and ended in the corresponding spatial units within the giving time frame.
 In this case, we demonstrate the inter-state mobility patterns by using the framework to capture the movement flows between the states.
@@
 as parameters and send to the dedicated visualization servlet on the CyberGIS Gateway, which is the leading online cyberGIS environment for a large number of users to perform computing- and data-intensive, and collaborative geospatial problem-solving enabled by advanced cyberinfrastructure~\cite{liu2014cybergis}.
-In return, the map interface visualizes the corresponding movement flows on the virtual globe.
 
 An overview of the 3D web mapping interface is shown in Figure~\ref{fig:Web_Interface}.
+The mapping interface visualizes the corresponding movement flows on the virtual globe, where the number of movement flows are divided by 20 percentiles and categorized by the colors shown in the legend.
 In terms of performing exploratory visual-analytics of Twitter user movement patterns, users can specify the time window to enable the query. 
-When the results are shown, users can hover the mouse over each individual lines on the map to see the value of movement flows for both in and out directions.
+When the results are shown, users can hover the mouse over each individual lines on the map to see the value of movement flows for both in and out directions (highlighted in color green).
 If the selected criteria keep unchanged, whenever the user zooms in/out, tilt or rotate the globe, the 3D virtual globe mapping interface will automatically provide the corresponding level-of-details on the fly.
 For example, Figure~\ref{fig:chicago} and Figure~\ref{fig:Chicago_airport} demonstrated the movement flows in different level-of-details around the Chicago city, and between O'Hare International Airport and the city center of Chicago city, where top 20 $\%$ movement flows were shown.
-The source code of the visual-analytics framework is available upon request.
+The 3D mapping interface facilitates uses to query multi-scale Twitter user movements with a geographical context and in an interactive fashion.
+For example, users can perform comparative studies of Twitter user movements in different cities by simply rotating the globe. 
+More importantly, this mapping interface can be easily customized and extended to accommodate future geo-located Twitter data collection with larger spatial coverages.
+The source code of the visual-analytics framework in this paper is available upon request.
 
@@
 To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-scale spatiotemporal Twitter user mobility patterns.
-This framework is implemented based on high-performance distributed computing environment using Apache Hadoop.
-It delivers scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
+This framework is implemented on high-performance distributed computing environment using Apache Hadoop.
+It provides efficiency in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
 
@@
 
-Finally, it is worth noting that the geo-located Twitter data is not able to generalize to the entire population.
-As the demographic information of the Twitter users cannot be easily identified, the results of delineated urban boundaries may not reflect a complete real-world image from human movements, which should be carefully considered in future studies.
-Nevertheless, as we have discussed in this paper that geo-located Twitter data show the advantages regarding the easy data accessibility, the large spatial coverage and massive sample size, our approach showed that such data can be a valuable proxy for understanding human mobility patterns across multiple spatial scales and temporal ranges.
+Finally, it is worth noting that at the current stage the geo-located Twitter data is not able to generalize to the entire population.
+As the demographic information of the Twitter users cannot be easily identified, the results derived in this study may not reflect a complete real-world image of human movements, which should be carefully considered in future studies.
+Nevertheless, the Twitter user movements provide clear supports to reveal the distance decay effects in human mobility research, which is observed in multiple spatial and temporal scales.
+Due to the large sample size, it is difficult to generalize the mobility pattern found at national level to entire population, city-level mobility pattern may provide better insights for investigating mobility dynamics.
+For example, the results of radius of gyration in Chicago exhibit similar pattern found in larger spatial scale, and with inputs of other mobility dataset that are often available at city-level, such as taxi trip records and mobile phone call data, there is a potential to synthesize these different sources of information and therefore provide a more complete image for understanding human mobility patterns.
+On the other hand, as we have discussed in this paper that geo-located Twitter data show the advantages regarding the easy data accessibility, the large spatial coverage and massive sample size, our approach took advantage of such data source to understand the mobility patterns across multiple spatial scales and temporal ranges.
 Also, our approach can be applied to the setting of other countries, which can be used to carry out comparative studies regarding spatiotemporal Twitter user mobility patterns.

### 2016-09-19 MovePattern_IJGI/IJGI_revision/Twitter_MovementPatterns_VisualAnalytics_v2.tex
revision

@@
 It provides efficiency in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
+For example, we have included an experiment for illustrating the processing time regarding generating Twitter user trajectories across different time span in the supplement material.
 
@@
 \acknowledgments{
-The authors would like to thank the four reviewers of IJGI for their constructive comments that better shaped the paper.
+The authors would like to thank the four anonymous reviewers of IJGI for their constructive comments that better shaped the paper.
 J.Y. would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.

### 2016-09-23 semantic_decomposition_of_twitter_user_locations/paper.tex
speed up please
edittings

--- 2016-08-18 semantic_decomposition_of_twitter_user_locations/paper.tex
@@
 \begin{document}
-\title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
-\author[1]{Junjun Yin\thanks{yinjunjun@gmail.com}}
+% \title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
+\title{A tale of two cities: A GIS based data synthesis approach for semantic decompositions of Twitter user locations}
+\author[1~\thanks{jyn@illinois.edu}]{Junjun Yin}
 \affil[1]{Department of Geography and Geographic Information Science}
@@
 \section{Introduction}
+Modern urban environments are perceived as real-world complex systems, where the embedded urban dynamics are interrelated to various types of human activities that are taking place simultaneously~\cite{jiangyin2014}.
+Throughout the process of urbanization, a fascinating research direction remains open regarding whether the spatial configurations of urban environment confine human activities or the social dynamics embedded in human activities change the functions of urban regions and therefore shape the urban structures.
+Research efforts in understanding the interactions between urban environment and its citizens are of critical importance to urban planing and its applications concerning the characteristics of urban mobility, accessibility and sustainability.
+
+what is it?
+
+why it is important?
+
+why is my solution?
+
+The remainder of this paper is organized as follows. Section 2 introduces the related work 
+Section 3 details the 
+Detailed analysis of the
+Section 5 presents the results
+Section 6 concludes the paper.
 
@@
 \section{Discussions and Conclusions}
+Talk about OpenStreetMap for potential large scale validation
+talk about the limitation of detailed land use maps currently available.
+
+\bibliographystyle{apalike}
+\bibliography{ref}
 

### 2016-10-03 ijgi-148112-for proofreading/Twitter_MovementPatterns_VisualAnalytics.tex
proof reading

--- 2016-09-19 MovePattern_IJGI/IJGI_revision/Twitter_MovementPatterns_VisualAnalytics_v2.tex
@@
 %=================================================================
-\documentclass[ijgi,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
+\documentclass[ijgi,article,accept,moreauthors,pdftex,10pt,a4paper]{mdpi}
 
@@
 \copyrightyear{2016}
-\externaleditor{Academic Editor: name}
-\history{Received: date; Accepted: date; Published: date}
+\externaleditor{Academic Editors: Marguerite Madden and Wolfgang Kainz}
+\history{Received: 15 August 2016; Accepted: 28 September 2016; Published: date}
 %------------------------------------------------------------------
@@
 % Authors, for the paper (add full first names)
-\Author{Junjun Yin $^{1}$ and Zhenhong Du $^{2,}$*}
+\Author{Junjun Yin $^{1,2}$ and Zhenhong Du $^{1,3,}$*}
 % Authors, for metadata in PDF
@@
 \address{%
-$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA ; jyn@illinois.edu\\
-$^{2}$ \quad Key Laboratory of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou, 310028, China; duzhenhong@zju.edu.cn}
+$^{1}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies\\
+$^{2}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA ; jyn@illinois.edu\\
+$^{3}$ \quad Key Laboratory of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou, 310028, China; duzhenhong@zju.edu.cn}
 
@@
 In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
-The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from 1$^{st}$ January to 31$^{st}$ December, 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
+The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from January 1$^{st}$ to December 31$^{st}$, 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
 To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
@@
 Section 3 details the processes for extracting, aggregating and summarizing multi-level spatiotemporal Twitter user mobility patterns.
-Section 4 presents the case study of performing visual-analytics for seeking multi-scale spatiotemporal Twitter mobility patterns in the continuous United States of year 2014.
+Section 4 presents the case study of performing visual-analytics for seeking multi-scale spatiotemporal Twitter mobility patterns in the continuous United States of the year 2014.
 Section 5 concludes the paper.
@@
 The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2 GB in size) collected per day.
-We have collected more than 1.3 billion geo-located tweets from 1$^{st}$ January to 31$^{st}$ December, 2014 with 6,147,430 Twitter users and 1 TB in file size.
-In particular, this data collection of year 2014 was originally used to map the spatial spread of flu in North America during the time period~\cite{padmanabhan2014flumapper}.
+We have collected more than 1.3 billion geo-located tweets from January 1$^{st}$ to December 31$^{st}$, 2014 with 6,147,430 Twitter users and 1 TB in file size.
+In particular, this data collection of the year 2014 was originally used to map the spatial spread of flu in North America during the time period~\cite{padmanabhan2014flumapper}.
 
@@
 The scalable visual-analytics framework consists of two main units: (1) Data processing unit: a distributed computing environment using Apache Hadoop for modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing the movements at multiple spatiotemporal scales.
-(2) Geo-visualization unit: an interactive 3D virtual globe web mapping interface for exploratory geo-visual analytics for understanding the detailed Twitter user movement flows across different spatial scales and temporal ranges.
+(2) Geo-visualization unit: an interactive 3D virtual globe web mapping interface for exploratory geo-visual analytics to understand detailed Twitter user movement flows across different spatial scales and temporal ranges.
 
@@
 Each raw geo-located tweet contains multiple fields of information, such as the created time, country, language code, and location, etc.
-To construct a space-time trajectory from the data collection, we are interested in the following fields: \textit{User ID, location, timestamp}, which can be represented by a tuple $\left\langle id, loc, t\right\rangle$, where \textit{id} is a unique string representing a Twitter user's id; \textit{loc} is the recorded location of the message represented as a pair of projected coordinates $\left\langle x, y\right\rangle$;
+To construct a space-time trajectory from the data collection, we are interested in the following fields: \textit{user ID, location, timestamp}, which can be represented by a tuple $\left\langle id, loc, t\right\rangle$, where \textit{id} is a unique string representing a Twitter user's id; \textit{loc} is the recorded location of the message represented as a pair of projected coordinates $\left\langle x, y\right\rangle$;
 and \textit{t} is the timestamp of when the message was posted; A Twitter user's space-time trajectory is defined as follows.
@@
 \noindent\emph{\textbf{Definition 2.
-Visitation behavior, displacement and radius of gyration:}} As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers the frequency of a user visiting different locations within a specific time frame.
+Visitation behavior, displacement and radius of gyration:}} As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers to the frequency of a user visiting different locations within a specific time frame.
 This metric provides an overall assessment regarding the diversity and similarity in the collective mobility pattern~\cite{gao2012exploring}.
@@
 Many studies have carried out data collection within a certain time period (e.g., a year in our case).
-However, as the geo-located tweets were collected in a continuous fashion, it is necessary to examine the sensitivities regarding these behaviors to ensure we are not just capturing a random snapshot from the whole data streams.
+However, as the geo-located tweets were collected in a continuous fashion, it is necessary to examine the sensitivity regarding these behaviors to ensure we are not just capturing a random snapshot from the whole data streams.
 
-In this study, we have analyzed the cumulative distribution of the frequency Twitter users visiting different locations in year 2014 (and every month), which uses the methods developed in~\cite{clauset2009power}.
+In this study, we have analyzed the cumulative distribution of the frequency Twitter users visiting different locations in the year 2014 (and every month), which uses the methods developed in~\cite{clauset2009power}.
 The frequency is summarized based on the trajectories of individuals extracted from a monthly time span.
 Note that different groups of Twitter users may exist in each month. 
-It appears that the distribution of the collective Twitter user visitation behaviors in year 2014 follows a two-tiered power law distributions (shown in Figure~\ref{fig:visitation}.
+It appears that the distribution of the collective Twitter user visitation behaviors in the year 2014 follows a two-tiered power law distributions (shown in Figure~\ref{fig:visitation}.
 The majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$, where $x$ is the number of visited locations and the $\alpha$ value is 1.32.
@@
 
-As it is aforementioned, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
-In this case, we first gathered the displacements from all the collected Twitter users in the continuous United States in year 2014, where those Twitter users with only one geo-located tweet were filtered out.
+As it is aforementioned, the measurements of displacements and radius of gyrations of individuals are two popular metrics to quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
+In this case, we first gathered the displacements from all the collected Twitter users in the continuous United States in the year 2014, where those Twitter users with only one geo-located tweet were filtered out.
 To investigate the mobility patterns of individuals, we also derived the accumulated displacements and the radius of gyrations of each individual Twitter user based on the corresponding space-time trajectories over the one year period.
@@
 
-We also measured the distribution of the radius of gyration of Twitter users at different spatial scales, specifically, the state level and city level.
+We also measured the distribution of the radius of gyration of Twitter users at different spatial scales, specifically, the state and city level.
 In this study, we selected the state Illinois and California for comparisons at the state level (Figure~\ref{fig:gyration} (c)), whereas we chose Chicago city as an example (Figure~\ref{fig:gyration} (d)) at the city level.
@@
 
-On the other hand, as our framework can aggregate Twitter user trajectories within different temporal ranges, we further analyzed the probability distributions of accumulated displacements took places in January, June, and October (Figure~\ref{fig:displacement} (d)) and radius of gyrations within 4 quarters in year 2014 (Figure~\ref{fig:gyration_season}, in order to examine whether there are temporal changes in the mobility patterns.
+On the other hand, as our framework can aggregate Twitter user trajectories within different temporal ranges, we further analyzed the probability distributions of accumulated displacements took places in January, June, and October (Figure~\ref{fig:displacement} (d)) and radius of gyrations within 4 quarters in the year 2014 (Figure~\ref{fig:gyration_season}, in order to examine whether there are temporal changes in the mobility patterns.
 While the probability distributions of accumulated displacements are almost identical in those selected three months,  we do find changes in the probability distributions of radius of gyrations in different quarters of the year.
@@
 In summary, by comparing these results from different spatial scales and temporal ranges, different distance bounds were identified for describing the spatiotemporal Twitter user mobility patterns.
-However the overall similarity and consistence found in using a combination of three functions to approximate the probability distribution functions of displacements and radius of gyrations, clearly provide supports for using geo-located tweets as useful proxies for understanding human mobility patterns and conducting reproducible findings at multiple spatial scales and temporal ranges.
+However, the overall similarity and consistence found, in using a combination of three functions to approximate the probability distribution functions of displacements and radius of gyrations, clearly provide supports for using geo-located tweets as useful proxies for understanding human mobility patterns and conducting reproducible findings at multiple spatial scales and temporal ranges.
 
@@
 \includegraphics[width=1.0\linewidth]{./figures/gyration_season}
-\caption{The probability distribution of radius of gyration of individual Twitter users in different quarters of year 2014}
+\caption{The probability distribution of radius of gyration of individual Twitter users in different quarters of the year 2014}
 \label{fig:gyration_season}
@@
 Note that the movement flows can be summarized across all the 10 spatial layers in the framework.
-We tested the overall distribution of the movement flows (in the form of weighted in-degree and out-degree of a graph, where each state is treated as a node) among different states in year 2014.
+We tested the overall distribution of the movement flows (in the form of weighted in-degree and out-degree of a graph, where each state is treated as a node) among different states in the year 2014.
 We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states.
@@
 \includegraphics[width=0.8\linewidth]{./figures/degree}
-\caption{The distribution of Twitter user movement flows among different states in year 2014 measured in weighted in- and out-degrees}
+\caption{The distribution of Twitter user movement flows among different states in the year 2014 measured in weighted in- and out-degrees}
 \label{fig:state_flow}
@@
 The 3D virtual globe is developed and extended from the Cesium library\footnote{http://cesiumjs.org/}, which is an open-source WebGL virtual globe and map engine.
-We customized the map engine to adapt different spatial scales, which correspond to the hierarchical spatial layers, for aggregating movements in different level-of-details.
+We customized the map engine to adapt different spatial scales, which correspond to the hierarchical spatial layers, for aggregating movements in different levels-of-detail.
 The map interface interprets user's interactions, such as area-of-interest, time window, and zoom levels, etc.

### 2016-10-08 ijgi-148112-for proofreading/Twitter_MovementPatterns_VisualAnalytics.tex
profreading 2

@@
 % Authors, for the paper (add full first names)
-\Author{Junjun Yin $^{1,2}$ and Zhenhong Du $^{1,3,}$*}
+\Author{Junjun Yin $^{1,3}$ and Zhenhong Du $^{2,3}$*}
 % Authors, for metadata in PDF
@@
 \address{%
-$^{1}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies\\
-$^{2}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA ; jyn@illinois.edu\\
-$^{3}$ \quad Key Laboratory of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou, 310028, China; duzhenhong@zju.edu.cn}
+$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
+$^{2}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou, 310028, China; duzhenhong@zju.edu.cn\\
+$^{3}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA}
 
@@
 To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
-This framework is implemented based on high-performance distributed computing environment using Apache Hadoop\footnote{http://hadoop.apache.org/}, which is an open source software framework to enable distributed processing of large datasets across computing clusters.
+This framework is implemented based on high-performance distributed computing environment using Apache Hadoop (http://hadoop.apache.org/), which is an open source software framework to enable distributed processing of large datasets across computing clusters.
 Enabled by this framework, we have performed a set of statistical analysis to understand multi-scale spatiotemporal Twitter user mobility patterns. 
@@
 Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
-It provides a publicly accessible streaming API\footnote{https://dev.twitter.com/streaming/overview} for easy data access.
+It provides a publicly accessible streaming API (https://dev.twitter.com/streaming/overview) for easy data access.
 Indeed, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.
@@
 
-As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages\footnote{https://support.twitter.com/articles/18311-the-twitter-rules} in the dataset; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
+As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages (https://support.twitter.com/articles/18311-the-twitter-rules) in the dataset; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
 In this case, we adopted the speed limit value as 240 m/s used in~\cite{Jurdak2015}, where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
 Note that the original location information embedded in each geo-located tweet is given in units of latitude and longitude, the distance is calculated by the great-circle distance between two points on a sphere with the haversine formula.
-Finally, we used the geographic boundaries of the continuous United States\footnote{https://www.census.gov/geo/maps-data/data/} (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section.
+Finally, we used the geographic boundaries of the continuous United States (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section.
 Based on these reinforcements, the dataset contains 1,052,861,000 tweets and 4,559,205 unique users.
@@
 We then created an hierarchical fishnet by diving the study region into regular cells, where the finest level (level 10) consists 1 km $\times$ 1 km cells.
-Such a cell size is consistent with the spatial resolution in landscan\footnote{http://web.ornl.gov/sci/landscan/} product for measuring the global population density.
+Such a cell size is consistent with the spatial resolution in landscan (http://web.ornl.gov/sci/landscan) product for measuring the global population density.
 In our case, the cell width/height for level i-1 is twice of the size in level i.
@@
 \subsection{The interactive 3D virtual globe web mapping interface}
-In addition to providing supports for understanding Twitter user mobility patterns with statistical analysis, the framework integrates a 3D virtual globe interface to enable users to perform exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements\footnote{http://sandbox.cigi.illinois.edu/home/apps.php?app=movepattern}.
-The 3D virtual globe is developed and extended from the Cesium library\footnote{http://cesiumjs.org/}, which is an open-source WebGL virtual globe and map engine.
+In addition to providing supports for understanding Twitter user mobility patterns with statistical analysis, the framework integrates a 3D virtual globe interface to enable users to perform exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements(http://sandbox.cigi.illinois.edu/home/apps.php?app=movepattern).
+The 3D virtual globe is developed and extended from the Cesium library (http://cesiumjs.org), which is an open-source WebGL virtual globe and map engine.
 We customized the map engine to adapt different spatial scales, which correspond to the hierarchical spatial layers, for aggregating movements in different levels-of-detail.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{J.Y. conceived and designed the experiments; J.Y. and D.Z. wrote the paper.}
+\authorcontributions{J.Y. conceived and designed the experiments; J.Y. and D.Z. analyzed the results; J.Y. and D.Z. wrote the paper.}
 

### 2016-10-08 ijgi-148112-for proofreading/ijgi-148112-can be published.tex
profreading 2

--- 2016-10-08 ijgi-148112-for proofreading/Twitter_MovementPatterns_VisualAnalytics.tex
@@
 % Authors, for the paper (add full first names)
-\Author{Junjun Yin $^{1,3}$ and Zhenhong Du $^{2,3}$*}
+\Author{Junjun Yin $^{1,3}$ and Zhenhong Du $^{2,3,*}$}
 % Authors, for metadata in PDF
@@
 $^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
-$^{2}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou, 310028, China; duzhenhong@zju.edu.cn\\
+$^{2}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn\\
 $^{3}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA}
@@
 % Contact information of the corresponding author
-\corres{Correspondence: duzhenhong@zju.edu.cn; Tel.: +8613819192989}
+\corres{Correspondence: duzhenhong@zju.edu.cn; Tel.: +86-138-1919-2989}
 
@@
 In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
-The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from January 1$^{st}$ to December 31$^{st}$, 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
+The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from 1st January to 31st December 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
 To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
@@
 
-\section{Mobility patterns in Location Based Social Media data}
-\subsection{Geo-located Twitter data for studying large-scale user movements}
+\section{Mobility Patterns in Location Based Social Media data}
+\subsection{Geo-located Twitter Data for Studying Large-scale User Movements}
 To understand detailed mobility patterns of individuals, the capability to capture human movements with fine-grained spatial and temporal granularity is critical.
@@
 Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
-It provides a publicly accessible streaming API (https://dev.twitter.com/streaming/overview) for easy data access.
+It provides a publicly accessible streaming API for easy data access~\cite{twitterAPI}.
 Indeed, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.
@@
 
-\subsection{Data-intensive challenges for multi-scale geo-visual analytics}
+\subsection{Data-intensive Challenges for Multi-scale Geo-visual Analytics}
 Mobility data are essentially a collection of spatiotemporal records of people re-allocating across the geographic space.
@@
 \section{Materials and Methods}
-\subsection{Geo-located Twitter data}
+\subsection{Geo-located Twitter Data}
 Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at.
@@
 The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2 GB in size) collected per day.
-We have collected more than 1.3 billion geo-located tweets from January 1$^{st}$ to December 31$^{st}$, 2014 with 6,147,430 Twitter users and 1 TB in file size.
+We have collected more than 1.3 billion geo-located tweets from 1 January to 31 December 2014 with 6,147,430 Twitter users and 1 TB in file size.
+
 In particular, this data collection of the year 2014 was originally used to map the spatial spread of flu in North America during the time period~\cite{padmanabhan2014flumapper}.
-
-As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages (https://support.twitter.com/articles/18311-the-twitter-rules) in the dataset; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
+As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages in the dataset~\cite{black2012twitter}; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
 In this case, we adopted the speed limit value as 240 m/s used in~\cite{Jurdak2015}, where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
@@
 \includegraphics[width=0.55\linewidth]{./figures/Overall_Architecture222}
-\caption{The overall system architecture of the framework}
+\caption{The overall system architecture of the framework.}
 \label{fig:overall_archi}
@@
 
-\subsection{Space-time Twitter user trajectories}
+\subsection{Space-time Twitter User Trajectories}
 To derive meaningful mobility patterns of individuals, a space-time trajectory of each individual user should be constructed~\cite{hagerstrand1985time}.
@@
 
-\noindent\emph{\textbf{Definition 1.
-Space-time Twitter user trajectory:}} The space-time trajectory of a Twitter user is defined as a collection of recorded geo-locations in the chronological order (i.e., based on the attached timestamp):
+\noindent\textbf{Definition 1.
+Space-time Twitter user trajectory:} \emph{The space-time trajectory of a Twitter user is defined as a collection of recorded geo-locations in the chronological order (i.e., based on the attached timestamp):}
 \newline
@@
 
-To remove non-human users based on unusual relocating speed, a user will be removed if the speed between any two consecutive locations in the user's trajectory with $speed$ $(loc_{i} - loc_{i-1}) > 240 m/s $.
+To remove non-human users based on unusual relocating speed, a user will be removed if the speed between any two consecutive locations in the user's trajectory with $speed$ $(loc_{i} - loc_{i-1}) > $ 240 m/s.
 Based on this definition for modeling the space-time Twitter user trajectories, we converted the process of extracting trajectories from the raw geo-located Twitter data as a MapReduce task.
-Specifically, each mapper utilizes the unique user id as a key to prepares the records that belong to the same user and send them to a reducer.
+Specifically, each mapper utilizes the unique user id as a key to prepares the records that belong to the same user and send them to reducer.
 Once the reducers receive the $\langle key, value\rangle$ pairs, a Twitter user's space-time trajectory is formed by the sorting the locations in chronological order while considering the speed limit.
@@
 
-\noindent\emph{\textbf{Definition 2.
-Visitation behavior, displacement and radius of gyration:}} As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers to the frequency of a user visiting different locations within a specific time frame.
-This metric provides an overall assessment regarding the diversity and similarity in the collective mobility pattern~\cite{gao2012exploring}.
+\noindent\textbf{Definition 2.
+visitation behavior, displacement and radius of gyration:} \emph{As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers the frequency of a user visiting different locations within a specific time frame.
+This metric provides an overall assessment regarding the diversity and similarity in the collective mobility pattern}~\cite{gao2012exploring}.
 
@@
 \includegraphics[width=0.6\linewidth]{./figures/multilevel}
-\caption{Hierarchical spatial layers for aggregating movements in different level-of-details}
+\caption{Hierarchical spatial layers for aggregating movements in different level-of-details.}
 \label{fig:multilevel}
@@
 
-\section{Multi-scale spatiotemporal Twitter user mobility patterns}
-\subsection{Spatiotemporal Twitter user mobility patterns}
+\section{Multi-scale Spatiotemporal Twitter User Mobility Patterns}
+\subsection{Spatiotemporal Twitter User Mobility Patterns}
 The situation of using geo-located tweets as proxies to infer people's movements is complex as users' tweeting behavior can be significantly different from one to another, in particular, the frequency and time-interval between two consecutive tweets.
@@
 \includegraphics[width=1.0\linewidth]{./figures/visitation}
-\caption{Two-tier power law distribution of the collective Twitter user visitation behaviors}
+\caption{Two-tier power law distribution of the collective Twitter user visitation behaviors.}
 \label{fig:visitation}
@@
 
-Figure~\ref{fig:displacement} (a) shows the probability distribution of the overall displacements, which is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10~m$ from [10 m, 70 m] (accounting for 2 $\%$ of the population), $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min}=100~m$ from [100 m, 80 km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80 km] (accounting for 5 $\%$ of the population).
-In addition, the displacement in the distance bound from 100 m and 80 km in Figure~\ref{fig:displacement} (b) can be further approximately by two power-law distributions with a cutting point at 5 km (53$\%$ distances are less than 5 km and 40$\%$ distances between 5 km and 80 km), which indicates two different travel modes, such as inter- or intra-city movements.
+Figure~\ref{fig:displacement}a shows the probability distribution of the overall displacements, which is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10~m$ from [10 m, 70 m] (accounting for 2 $\%$ of the population), $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min}=100~m$ from [100 m, 80 km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80 km] (accounting for 5 $\%$ of the population).
+In addition, the displacement in the distance bound from 100 m and 80 km in Figure~\ref{fig:displacement}b can be further approximately by two power-law distributions with a cutting point at 5 km (53$\%$ distances are less than 5 km and 40$\%$ distances between 5 km and 80 km), which indicates two different travel modes, such as inter- or intra-city movements.
 Overall, the fitting functions with different distance bounds suggest the existence of multi-scale or multi-modal mobility patterns~\cite{Jurdak2015} of the Twitter users in the continuous United States, for example, the displacements larger than 80 km could be related to inter-state travels and stronger distance decay effects are observed in longer distance travels.
 
-The probability distribution of radius of gyrations of individuals at the national level (Figure~\ref{fig:gyration} (a)) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10~m$ from [10 m, 50 m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50 m, 30 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30 km].
-In particular, the radius of gyration between 50 m and 30 km can be further approximately by two power law distributions with a cutting point at 6 km (Figure~\ref{fig:gyration} (b)), which suggest two main types of spatial coverage of from the collected Twitter users in the continuous United States.
+The probability distribution of radius of gyrations of individuals at the national level (Figure~\ref{fig:gyration}a) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10~m$ from [10 m, 50 m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50 m, 30 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30 km].
+In particular, the radius of gyration between 50 m and 30 km can be further approximately by two power law distributions with a cutting point at 6 km (Figure~\ref{fig:gyration}b), which suggest two main types of spatial coverage of from the collected Twitter users in the continuous United States.
 The distribution shows that around $10\%$ the tweet population has a radius of gyration less than 50 meters, which indicates those twitter users mostly tweet at a particular place, such as home or office;  around 60$\%$ of the population has a radius of gyration less than 30 km, which indicates that most of the collected Twitter user movements are ``short'' distances, e.g., within a city locale.
@@
 \includegraphics[width=1.0\linewidth]{./figures/displacement}
-\caption{(a) The probability distribution of the collective Twitter user displacements P(d) (b) the distance between [100 m, 80 km] is approximated by a double power-law functions (c) The probability distribution of the accumulated displacements of individual Twitter users P(d) (d) The probability distribution of the accumulated displacements of individual Twitter users in 3 different months}
+\caption{({\bf a}) The probability distribution of the collective Twitter user displacements P(d); ({\bf b}) the distance between [100 m, 80 km] is approximated by a double power-law functions; ({\bf c}) The probability distribution of the accumulated displacements of individual Twitter users P(d); ({\bf d}) The probability distribution of the accumulated displacements of individual Twitter users in 3 different months.}
+
 \label{fig:displacement}
@@
 We also measured the distribution of the radius of gyration of Twitter users at different spatial scales, specifically, the state and city level.
-In this study, we selected the state Illinois and California for comparisons at the state level (Figure~\ref{fig:gyration} (c)), whereas we chose Chicago city as an example (Figure~\ref{fig:gyration} (d)) at the city level.
+In this study, we selected the state Illinois and California for comparisons at the state level (Figure~\ref{fig:gyration}c), whereas we chose Chicago city as an example (Figure~\ref{fig:gyration}d) at the city level.
 Interestingly but not surprisingly, the P($r_{g}$) at the state level can also be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.
@@
 \includegraphics[width=1.0\linewidth]{./figures/gyration2}
-\caption{ (a) The probability distribution of radius of gyration of individual Twitter users P($r_{g}$) at the national level (b) the distance between [50 m, 30 km] is approximated by a double power-law functions (c) P($r_{g}$) at the state level (Illinois and California) (d) P($r_{g}$) for Chicago city}
+\caption{ ({\bf a}) The probability distribution of radius of gyration of individual Twitter users P($r_{g}$) at the national level; ({\bf b}) the distance between [50 m, 30 km] is approximated by a double power-law functions; ({\bf c}) P($r_{g}$) at the state level (Illinois and California); ({\bf d}) P($r_{g}$) for Chicago city.}
 \label{fig:gyration}
@@
 
-On the other hand, as our framework can aggregate Twitter user trajectories within different temporal ranges, we further analyzed the probability distributions of accumulated displacements took places in January, June, and October (Figure~\ref{fig:displacement} (d)) and radius of gyrations within 4 quarters in the year 2014 (Figure~\ref{fig:gyration_season}, in order to examine whether there are temporal changes in the mobility patterns.
+On the other hand, as our framework can aggregate Twitter user trajectories within different temporal ranges, we further analyzed the probability distributions of accumulated displacements took places in January, June, and October (Figure~\ref{fig:displacement}d) and radius of gyrations within 4 quarters in the year 2014 (Figure~\ref{fig:gyration_season}, in order to examine whether there are temporal changes in the mobility patterns.
 While the probability distributions of accumulated displacements are almost identical in those selected three months,  we do find changes in the probability distributions of radius of gyrations in different quarters of the year.
@@
 \includegraphics[width=1.0\linewidth]{./figures/gyration_season}
-\caption{The probability distribution of radius of gyration of individual Twitter users in different quarters of the year 2014}
+\caption{The probability distribution of radius of gyration of individual Twitter users in different quarters of the year 2014.}
 \label{fig:gyration_season}
@@
 We tested the overall distribution of the movement flows (in the form of weighted in-degree and out-degree of a graph, where each state is treated as a node) among different states in the year 2014.
-We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states.
+We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states (Figure~\ref{fig:state_flow}).
 It indicates that the Twitter population is not proportional to account the movement flux between the states, which may provide some insights for other researchers in studying social-economical aspects of the migration dynamics.
@@
 \includegraphics[width=0.8\linewidth]{./figures/degree}
-\caption{The distribution of Twitter user movement flows among different states in the year 2014 measured in weighted in- and out-degrees}
+\caption{The distribution of Twitter user movement flows among different states in the year 2014 measured in weighted in- and out-degrees.}
 \label{fig:state_flow}
@@
 
-\subsection{The interactive 3D virtual globe web mapping interface}
-In addition to providing supports for understanding Twitter user mobility patterns with statistical analysis, the framework integrates a 3D virtual globe interface to enable users to perform exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements(http://sandbox.cigi.illinois.edu/home/apps.php?app=movepattern).
+\subsection{The Interactive 3D Virtual Globe Web Mapping Interface}
+In addition to providing supports for understanding Twitter user mobility patterns with statistical analysis, the framework integrates a 3D virtual globe interface to enable users to perform exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements (http://sandbox.cigi.illinois.edu/home).
 The 3D virtual globe is developed and extended from the Cesium library (http://cesiumjs.org), which is an open-source WebGL virtual globe and map engine.
@@
 If the selected criteria keep unchanged, whenever the user zooms in/out, tilt or rotate the globe, the 3D virtual globe mapping interface will automatically provide the corresponding level-of-details on the fly.
-For example, Figure~\ref{fig:chicago} and Figure~\ref{fig:Chicago_airport} demonstrated the movement flows in different level-of-details around the Chicago city, and between O'Hare International Airport and the city center of Chicago city, where top 20 $\%$ movement flows were shown.
+For example, Figure~\ref{fig:chicago} and Figure~\ref{fig:Chicago_airport} demonstrated the movement flows in different level-of-details around the Chicago city, and between O'Hare International Airport and the city center of Chicago city, where top 20$\%$ movement flows were shown.
 The 3D mapping interface facilitates uses to query multi-scale Twitter user movements with a geographical context and in an interactive fashion.
@@
 \includegraphics[width=0.8\linewidth]{./figures/all}
-\caption{An overview of the 3D interactive web mapping interface}
+\caption{An overview of the 3D interactive web mapping interface.}
 \label{fig:Web_Interface}
@@
 \includegraphics[width=0.8\linewidth]{./figures/Chicago}
-\caption{The top 20 $\%$ movement flows around Chicago city}
+\caption{The top 20$\%$ movement flows around Chicago city.}
 \label{fig:chicago}
@@
 \includegraphics[width=0.8\linewidth]{./figures/Chicago_airport}
-\caption{The top 20 $\%$ movement flows between O'Hare International Airport and the city center of Chicago city}
+\caption{The top 20$\%$ movement flows between O'Hare International Airport and the city center of Chicago city.}
 \label{fig:Chicago_airport}
@@
 The authors would like to thank the four anonymous reviewers of IJGI for their constructive comments that better shaped the paper.
-J.Y. would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
-D.Z. would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.
+Junjun Yin would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
+Zhenhong Du would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.
 The work also used the ROGER supercomputer, which is supported by NSF under grant number: 1429699.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{J.Y. conceived and designed the experiments; J.Y. and D.Z. analyzed the results; J.Y. and D.Z. wrote the paper.}
+\authorcontributions{Junjun Yin conceived and designed the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin and Zhenhong Du wrote the paper.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{mdpi}
-\bibliography{lite}
+\renewcommand\bibname{References}
+\begin{thebibliography}{-------}
+\providecommand{\natexlab}[1]{#1}
+
+\bibitem[Zheng \em{et~al.}(2008)Zheng, Li, Chen, Xie, and
+  Ma]{zheng2008understanding}
+Zheng, Y.; Li, Q.; Chen, Y.; Xie, X.; Ma, W.Y.
+\newblock Understanding mobility based on GPS data.
+\newblock  In Proceedings of the 10th International Conference on Ubiquitous
+  Computing, Seoul, South Korea, 21--24 September 2008.
+
+\bibitem[Jiang \em{et~al.}(2009)Jiang, Yin, and Zhao]{jiang2009characterizing}
+Jiang, B.; Yin, J.; Zhao, S.
+\newblock Characterizing the human mobility pattern in a large street network.
+\newblock {\em Phys. Rev. E} {\bf 2009}, doi:10.1103/PhysRevE.80.021136.
+
+\bibitem[Belik \em{et~al.}(2011)Belik, Geisel, and Brockmann]{belik2011natural}
+Belik, V.; Geisel, T.; Brockmann, D.
+\newblock Natural human mobility patterns and spatial spread of infectious
+  diseases.
+\newblock {\em Phys. Rev. X} {\bf 2011}, doi:10.1103/PhysRevX.1.011001.
+
+\bibitem[Greenwood(1985)]{greenwood1985human}
+Greenwood, M.J.
+\newblock Human migration: Theory, models, and empirical studies.
+\newblock {\em J. Reg. Sci.} {\bf 1985}, {\em 25},~521--544.
+
+\bibitem[Brockmann \em{et~al.}(2006)Brockmann, Hufnagel, and
+  Geisel]{brockmann2006scaling}
+Brockmann, D.; Hufnagel, L.; Geisel, T.
+\newblock The scaling laws of human travel.
+\newblock {\em Nature} {\bf 2006}, {\em 439},~462--465.
+
+\bibitem[Gonzalez \em{et~al.}(2008)Gonzalez, Hidalgo, and
+  Barabasi]{gonzalez2008understanding}
+Gonzalez, M.C.; Hidalgo, C.A.; Barabasi, A.L.
+\newblock Understanding individual human mobility patterns.
+\newblock {\em Nature} {\bf 2008}, {\em 453},~779--782.
+
+\bibitem[Jurdak \em{et~al.}(2015)Jurdak, Zhao, Liu, AbouJaoude, Cameron, and
+  Newth]{Jurdak2015}
+Jurdak, R.; Zhao, K.; Liu, J.; AbouJaoude, M.; Cameron, M.; Newth, D.
+\newblock Understanding human mobility from twitter.
+\newblock {\em PLoS One} {\bf 2015}, doi:10.1371/journal.pone.0131469.
+
+\bibitem[Rhee \em{et~al.}(2011)Rhee, Shin, Hong, Lee, Kim, and
+  Chong]{rhee2011levy}
+Rhee, I.; Shin, M.; Hong, S.; Lee, K.; Kim, S.J.; Chong, S.
+\newblock On the levy-walk nature of human mobility.
+\newblock {\em IEEE/ACM Trans. Netw.} {\bf 2011}, {\em
+  19},~630--643.
+
+\bibitem[Sevtsuk and Ratti(2010)]{sevtsuk2010does}
+Sevtsuk, A.; Ratti, C.
+\newblock Does urban mobility have a daily routine? Learning from the aggregate
+  data of mobile networks.
+\newblock {\em J. Urban Technol.} {\bf 2010}, {\em 17},~41--60.
+
+\bibitem[Kung \em{et~al.}(2014)Kung, Greco, Sobolevsky, and
+  Ratti]{kung2014exploring}
+Kung, K.S.; Greco, K.; Sobolevsky, S.; Ratti, C.
+\newblock Exploring universal patterns in human home-work commuting from mobile
+  phone data.
+\newblock {\em PloS One} {\bf 2014}, doi:10.1371/journal.pone.0096180.
+
+\bibitem[Thatcher(2014)]{thatcher2014living}
+Thatcher, J.
+\newblock Living on fumes: Digital footprints, data fumes, and the limitations
+  of spatial big data.
+\newblock {\em Int. J. Commun.} {\bf 2014}, {\em
+  8},~1765--1783.
+
+\bibitem[Hawelka \em{et~al.}(2014)Hawelka, Sitko, Beinat, Sobolevsky,
+  Kazakopoulos, and Ratti]{hawelka2014geo}
+Hawelka, B.; Sitko, I.; Beinat, E.; Sobolevsky, S.; Kazakopoulos, P.; Ratti, C.
+\newblock Geo-located Twitter as proxy for global mobility patterns.
+\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2014}, {\em
+  41},~260--271.
+
+\bibitem[Giannotti and Pedreschi(2008)]{giannotti2008mobility}
+Giannotti, F.; Pedreschi, D.
+\newblock {\em Mobility, Data Mining and Privacy: Geographic Knowledge
+  Discovery}; Springer Science \& Business Media: Berlin, Germany,  2008.
+
+\bibitem[Crampton(2014)]{crampton2014collect}
+Crampton, J.W.
+\newblock Collect it all: National security, Big Data and governance.
+\newblock {\em GeoJournal} {\bf 2014}, {\em 9}, 1--13.
+
+\bibitem[Wu \em{et~al.}(2014)Wu, Zhi, Sui, and Liu]{wu2014intra}
+Wu, L.; Zhi, Y.; Sui, Z.; Liu, Y.
+\newblock Intra-urban human mobility and activity transition: Evidence from
+  social media check-in data.
+\newblock {\em PLoS one} {\bf 2014}, doi:10.1371/journal.pone.0097010.
+
+\bibitem[Hasan \em{et~al.}(2013)Hasan, Zhan, and
+  Ukkusuri]{hasan2013understanding}
+Hasan, S.; Zhan, X.; Ukkusuri, S.V.
+\newblock Understanding urban human activity and mobility patterns using
+  large-scale location-based data from online social media.
+\newblock  In Proceedings of the 2nd ACM SIGKDD International Workshop on Urban
+  Computing, Chicago, IL, USA, 11--14 August 2013.
+
+\bibitem[Cho \em{et~al.}(2011)Cho, Myers, and Leskovec]{cho2011friendship}
+Cho, E.; Myers, S.A.; Leskovec, J.
+\newblock Friendship and mobility: User movement in location-based social
+  networks.
+\newblock  In Proceedings of the 17th ACM SIGKDD International Conference on
+  Knowledge Discovery and Data Mining, San Diego, CA, USA, 21--24 August 2011.
+
+\bibitem[Noulas \em{et~al.}(2012)Noulas, Scellato, Lambiotte, Pontil, and
+  Mascolo]{noulas2012tale}
+Noulas, A.; Scellato, S.; Lambiotte, R.; Pontil, M.; Mascolo, C.
+\newblock A tale of many cities: Universal patterns in human urban mobility.
+\newblock {\em PLoS One} {\bf 2012}, doi:10.1371/journal.pone.0037027.
+
+\bibitem[Balcan \em{et~al.}(2009)Balcan, Colizza, Gon{\c{c}}alves, Hu, Ramasco,
+  and Vespignani]{balcan2009multiscale}
+Balcan, D.; Colizza, V.; Gon{\c{c}}alves, B.; Hu, H.; Ramasco, J.J.;
+  Vespignani, A.
+\newblock Multiscale mobility networks and the spatial spreading of infectious
+  diseases.
+\newblock {\em Proc. Nat. Acad. Sci.} {\bf 2009},
+  {\em 106},~21484--21489.
+
+\bibitem[Tamerius \em{et~al.}(2011)Tamerius, Nelson, Zhou, Viboud, Miller, and
+  Alonso]{tamerius2011global}
+Tamerius, J.; Nelson, M.I.; Zhou, S.Z.; Viboud, C.; Miller, M.A.; Alonso, W.J.
+\newblock Global influenza seasonality: Reconciling patterns across temperate
+  and tropical regions.
+\newblock {\em Environ. Health Perspect.} {\bf 2011}, {\em 119},~439--445.
+
+\bibitem[Tsou(2015)]{tsou2015}
+Tsou, M.H.
+\newblock Research challenges and opportunities in mapping social media and Big
+  Data.
+\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2015}, {\em
+  42},~70--74.
+
+\bibitem[Zheng \em{et~al.}(2010)Zheng, Xie, and Ma]{zheng2010geolife}
+Zheng, Y.; Xie, X.; Ma, W.Y.
+\newblock GeoLife: A collaborative social networking service among user,
+  location and trajectory. {\em IEEE Data(base) Eng. Bulletin} {\bf 2010}, {\em 33}, 32--39.
+
+\bibitem[Becker \em{et~al.}(2013)Becker, C{\'a}ceres, Hanson, Isaacman, Loh,
+  Martonosi, Rowland, Urbanek, Varshavsky, and Volinsky]{becker2013human}
+Becker, R.; C{\'a}ceres, R.; Hanson, K.; Isaacman, S.; Loh, J.M.; Martonosi,
+  M.; Rowland, J.; Urbanek, S.; Varshavsky, A.; Volinsky, C.
+\newblock Human mobility characterization from cellular network data.
+\newblock {\em Commun. ACM} {\bf 2013}, {\em 56},~74--82.
+
+\bibitem[Sobolevsky \em{et~al.}(2013)Sobolevsky, Szell, Campari, Couronn{\'e},
+  Smoreda, and Ratti]{sobolevsky2013delineating}
+Sobolevsky, S.; Szell, M.; Campari, R.; Couronn{\'e}, T.; Smoreda, Z.; Ratti,
+  C.
+\newblock Delineating geographical regions with networks of human interactions
+  in an extensive set of countries.
+\newblock {\em PLoS One} {\bf 2013}, doi:10.1371/journal.pone.0081707.
+
+\bibitem[Twitter (2016)]{twitterAPI}
+Twitter Streaming API
+\newblock available from: https://dev.twitter.com/streaming/overview
+\newblock {\bf 2016}, accessed on October, 2016
+
+\bibitem[Cranshaw \em{et~al.}(2012)Cranshaw, Schwartz, Hong, and
+  Sadeh]{cranshaw2012livehoods}
+Cranshaw, J.; Schwartz, R.; Hong, J.I.; Sadeh, N.M.
+\newblock The livehoods project: Utilizing social media to understand the
+  dynamics of a city.
+\newblock  In Proceedings of the ICWSM 2012, Dublin, Ireland, 4--8 June 2012.
+
+\bibitem[Mitchell \em{et~al.}(2013)Mitchell, Frank, Harris, Dodds, and
+  Danforth]{mitchell2013geography}
+Mitchell, L.; Frank, M.R.; Harris, K.D.; Dodds, P.S.; Danforth, C.M.
+\newblock The geography of happiness: Connecting twitter sentiment and
+  expression, demographics, and objective characteristics of place. {\em PLoS One} {\bf 2013}, doi:10.1371/journal.pone.0064417.
+
+\bibitem[Longley \em{et~al.}(2015)Longley, Adnan, Lansley,
+  et~al.]{longley2015geotemporal}
+Longley, P.A.; Adnan, M.; Lansley, G.
+\newblock The geotemporal demographics of Twitter usage.
+\newblock {\em Environ. Plan. A} {\bf 2015}, {\em 47},~465--484.
+
+\bibitem[H{\"a}gerstrand \em{et~al.}(1985)H{\"a}gerstrand
+  et~al.]{hagerstrand1985time}
+H{\"a}gerstrand, T.
+\newblock Time-geography: Focus on the corporeality of man, society, and
+  environment.
+\newblock In {\em The Science and Praxis of Complexity}; United Nations University: Montpellier, France, 1985; pp. 193--216.
+
+\bibitem[Kwan and Lee(2004)]{kwan2004geovisualization}
+Kwan, M.P.; Lee, J.
+\newblock Geovisualization of human activity patterns using 3D GIS: A
+  time-geographic approach. In 
+\newblock {\em Spatially Integrated Social Science: Examples in Best Practice}; Michael, F.G., Donald, G.J. Eds.; Oxford University Press: Oxford, MI, USA, 2003; Volume 3, pp. 27--51.
+
+\bibitem[Andrienko and Andrienko(2007)]{andrienko2007designing}
+Andrienko, N.; Andrienko, G.
+\newblock Designing visual analytics methods for massive collections of
+  movement data.
+\newblock {\em Cartogr. Int. J. Geogr.
+  Inf. Geovis.} {\bf 2007}, {\em 42},~117--138.
+
+\bibitem[MacEachren and Kraak(2001)]{maceachren2001research}
+MacEachren, A.M.; Kraak, M.J.
+\newblock Research challenges in geovisualization.
+\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2001}, {\em
+  28},~3--12.
+
+\bibitem[MacEachren(2004)]{maceachren2004maps}
+MacEachren, A.M.
+\newblock {\em How Maps Work: Representation, Visualization, and Design};
+  Guilford Press: New York, NY, USA, 2004.
+
+\bibitem[Andrienko \em{et~al.}(2007)Andrienko, Andrienko, and
+  Wrobel]{andrienko2007visual}
+Andrienko, G.; Andrienko, N.; Wrobel, S.
+\newblock Visual analytics tools for analysis of movement data.
+\newblock {\em ACM SIGKDD Explor. Newsl.} {\bf 2007}, {\em 9},~38--46.
+
+\bibitem[Cao \em{et~al.}(2015)Cao, Wang, Hwang, Padmanabhan, Zhang, and
+  Soltani]{cao2014scalable}
+Cao, G.; Wang, S.; Hwang, M.; Padmanabhan, A.; Zhang, Z.; Soltani, K.
+\newblock A scalable framework for spatiotemporal analysis of location-based
+  social media data.
+\newblock {\em Comput. Environ. Urban Syst.} {\bf 2015}, {\em 51}, 70--82.
+
+\bibitem[Padmanabhan \em{et~al.}(2014)Padmanabhan, Wang, Cao, Hwang, Zhang,
+  Gao, Soltani, and Liu]{padmanabhan2014flumapper}
+Padmanabhan, A.; Wang, S.; Cao, G.; Hwang, M.; Zhang, Z.; Gao, Y.; Soltani, K.;
+  Liu, Y.
+\newblock FluMapper: A cyberGIS application for interactive analysis of massive
+  location-based social media.
+\newblock {\em Concurr. Comput. Pract. Exp.} {\bf
+  2014}, doi:10.1002/cpe.3287.
+
+\bibitem[Black \em{et~al.}(2012)Black, A., Mascaro, C., Gallagher, M. and Goggins, S.P.]{black2012twitter}
+Black, A., Mascaro, C., Gallagher, M. and Goggins, S.P.
+\newblock DTwitter zombie: Architecture for capturing, socially transforming and analyzing the Twittersphere
+\newblock In {\em Proceedings of the 17th ACM international conference on Supporting group work} {\bf 2012}, pp. 229-238. ACM.
+
+\bibitem[Shvachko \em{et~al.}(2010)Shvachko, Kuang, Radia, and
+  Chansler]{shvachko2010hadoop}
+Shvachko, K.; Kuang, H.; Radia, S.; Chansler, R.
+\newblock The hadoop distributed file system.
+\newblock  {\em Mass Storage Syst. Technol.}  {\bf 2010}, doi:10.1109/MSST.2010.5496972.
+
+\bibitem[Dean and Ghemawat(2008)]{dean2008mapreduce}
+Dean, J.; Ghemawat, S.
+\newblock MapReduce: Simplified data processing on large clusters.
+\newblock {\em Commun. ACM} {\bf 2008}, {\em 51},~107--113.
+
+\bibitem[Gao \em{et~al.}(2012)Gao, Tang, and Liu]{gao2012exploring}
+Gao, H.; Tang, J.; Liu, H.
+\newblock Exploring social-historical ties on location-based social networks.
+\newblock In Proceedings of the ICWSM 2012, Dublin, Ireland, 4--8 June 2012.
+
+\bibitem[Buttenfield and McMaster(1991)]{buttenfield1991map}
+Buttenfield, B.P.; McMaster, R.B.
+\newblock {\em Map Generalization: Making Rules for Knowledge Representation};
+  Longman Scientific \& Technical: New York, NY, USA, 1991.
+
+\bibitem[Samet(1984)]{samet1984quadtree}
+Samet, H.
+\newblock The quadtree and related hierarchical data structures.
+\newblock {\em ACM Comput. Surv. (CSUR)} {\bf 1984}, {\em 16},~187--260.
+
+\bibitem[Clauset \em{et~al.}(2009)Clauset, Shalizi, and
+  Newman]{clauset2009power}
+Clauset, A.; Shalizi, C.R.; Newman, M.E.
+\newblock Power-law distributions in empirical data.
+\newblock {\em SIAM Rev.} {\bf 2009}, {\em 51},~661--703.
+
+\bibitem[Reynolds(2012)]{reynolds2012truncated}
+Reynolds, A.
+\newblock Truncated L{\'e}vy walks are expected beyond the scale of data
+  collection when correlated random walks embody observed movement patterns.
+\newblock {\em J. Royal Soc. Int.} {\bf 2012}, {\em
+  9},~528--534.
+
+\bibitem[Zhao \em{et~al.}(2015)Zhao, Musolesi, Hui, Rao, and
+  Tarkoma]{zhao2015explaining}
+Zhao, K.; Musolesi, M.; Hui, P.; Rao, W.; Tarkoma, S.
+\newblock Explaining the power-law distribution of human mobility through
+  transportation modality decomposition.
+\newblock {\em Sci. Rep.} {\bf 2015}, doi:10.1038/srep09136.
+
+\bibitem[Liu \em{et~al.}(2014)Liu, Padmanabhan, and Wang]{liu2014cybergis}
+Liu, Y.; Padmanabhan, A.; Wang, S.
+\newblock CyberGIS Gateway for enabling data-rich geospatial research and
+  education.
+\newblock {\em Sci. Gatew. Workshops 2013} {\bf
+  2014}, doi:10.1002/cpe.3256.
+
+\end{thebibliography}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-10-08 ijgi-148112-for proofreading/Twitter_MovementPatterns_VisualAnalytics.tex
to be submitted

@@
 
-As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages (https://support.twitter.com/articles/18311-the-twitter-rules) in the dataset; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
+As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages in the dataset~\cite{black2012twitter}; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
 In this case, we adopted the speed limit value as 240 m/s used in~\cite{Jurdak2015}, where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.

### 2016-10-12 urban_boundaries_gb_ijgis_submission_r2/IJGIS/Paper.tex
figures
round 2

--- 2016-08-05 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
@@
 This approach demonstrates improvements for estimating the locations of mobile phone records based on the cell tower triangulation~\citep{gonzalez2008,qian2013}.
-However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\citep{sakaki2010,zandbergen2009}.
+However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\citep{sakaki2010}.
 Another approach is to partition the space into a grid of spatial pixels~\citep{liuPopMobility,ratti2010}.
@@
 Coherent geographic regions were identified as individual fishnet cells showing more internal user movement compared to user movements across the cell boundaries to neighboring cells.
+To help readers that are not familiar with the geographic context in Great Britain better interpret the derived boundaries,
+we had added two additonal layers (i.e., locations of airport fields and population-wighted-centroids of workplace zones in the Great Britian) in the background of the figures.
 Fig.~\ref{S5_Fig}  presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4km, greater than 10 km, and using all available displacements together compared to the administrative boundaries of Great Britain.
@@
 \caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) all displacements with $L(M)= 7.8$.
-(b) displacements longer than 10 km ($L(M)=8.5$) (c) displacements shorter than 4 km ($L(M)=4.5$) (d) and displacements longer than 4 km ($L(M)=8.1$).The partition of space was done using a 10 km fishnet for the directed displacements from and to each cell.
+(b) displacements longer than 10 km ($L(M)=8.5$), red symbols are the locations of airport fields in the Great Britain (c) displacements shorter than 4 km ($L(M)=4.5$) (d) and displacements longer than 4 km ($L(M)=8.1$).The partition of space was done using a 10 km fishnet for the directed displacements from and to each cell.
 Each color represents a unique community with more Twitter users displacements among the cells compared to others.
@@
 \begin{center}
-\includegraphics[width=0.7\linewidth]{./figure/S6_community_london}
+\includegraphics[width=1.0\linewidth]{./figure/S6_community_london}
 \caption{{\bf The non-administrative anthropographic regions inferred from Twitter user displacements greater than 4 km (left) and 10 km (right) in comparison with major cities in England (upper figures) and Scotland (bottom figures).}  Each color represents a unique community.
-Including short distance movements has increased the power to differentiate the influence of nearby cities such as Glasgow and Edinburgh (lower left), while restricting the analysis to longer distance movements grouped travelers from the two previous cities into the same community (lower right).}
+Including short distance movements has increased the power to differentiate the influence of nearby cities such as Glasgow and Edinburgh (lower left), while restricting the analysis to longer distance movements grouped travelers from the two previous cities into the same community (lower right).
+Red symbols are the locations of airport fields and gray points are the population-wighted-centroids of workplace zones in the Great Britian.}
 \label{S6_Fig}
@@
 \begin{center}
-\includegraphics[width=0.7\linewidth]{./figure/S7_london}
+\includegraphics[width=0.9\linewidth]{./figure/S7_london}
 \caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs ($L(M)=8.1$)}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.
 Each unique color represents a different non-administrative anthropographic region.
-Notice that some remote regions like the airport (light purple region in south of Hillingdon) share the same class with downtown because it is well connected despite the geographic separation.}
+Notice that some remote regions like the airport (light purple region in south of Hillingdon) share the same class with downtown because it is well connected despite the geographic separation.
+Red symbols are the locations of airport fields and gray points are the population-wighted-centroids of workplace zones in London.}
 \label{S7_Fig}
@@
 
-\bibitem[\protect\citeauthoryear{Zandbergen}{2009}]{zandbergen2009}
-Zandbergen, P.A., 2009. Accuracy of iPhone Locations: A Comparison of Assisted GPS, WiFi and Cellular Positioning. Transactions in GIS, 13, pp. 5-25.
-
 \bibitem[\protect\citeauthoryear{Zhao {\itshape{et~al.}}}{2015}]{zhao2015}

### 2016-10-12 urban_boundaries_gb_ijgis_submission_r2/IJGIS/Paper.tex
track_changes

@@
 This approach demonstrates improvements for estimating the locations of mobile phone records based on the cell tower triangulation~\citep{gonzalez2008,qian2013}.
-However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\citep{sakaki2010}.
+However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\citep{zandbergen2009}.
 Another approach is to partition the space into a grid of spatial pixels~\citep{liuPopMobility,ratti2010}.
@@
 We modeled different aspects of the collective mobility patterns of Twitter users.
-These patterns include: the number of visited locations per user,  the collective user displacements, and the radius of gyration of individuals in order to identify natural breaks in user travel patterns.
-We then used these natural breaks within the mobility patterns to partition the geographic space of Great Britain into fine-grained cells and established the connectivity among these cells to redraw non-administrative anthropographic urban boundaries.
+These patterns include: the number of visited locations per user,  the collective user displacements, and the radius of gyration of individuals in order to identify distinct distance ranges in user travel patterns.
+We then used these distance ranges within the mobility patterns to partition the geographic space of Great Britain into fine-grained cells and established the connectivity among these cells to redraw non-administrative anthropographic urban boundaries.
 
@@
 The probability distributions of the collective user displacement $P(d)$ and radius of gyration $P(r_g)$ are presented in Fig.~\ref{S4_Fig}, where the fitting method for identifying different distance ranges is derived from~\citep{jurdak2015}.
-The probability distribution of the collective displacements can be approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10m, 70m] (accounting for 3$\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [70m, 70km] (93$\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 70km] (4$\%$ of the population).
-The displacement distance between 70m and 100km can be further approximated by two power law distributions with a cut-off point at 4km (55$\%$ distances are less than 4km and 40$\%$ distances between 4km and 100km), which indicates the urban movement captured by the geo-located Twitter data to reveal two different modes: inter-city and intra-city movement.
+The probability distribution of the collective displacements can be approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10 m$ from [10 m, 70 m] (accounting for 3$\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [70 m, 70 km] (93$\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 70 km] (4$\%$ of the population).
+The displacement distance between 70 m and 100 km can be further approximated by two power law distributions with a cut-off point at 4 km (55$\%$ distances are less than 4 km and 40$\%$ distances between 4 km and 100 km), which indicates the urban movement captured by the geo-located Twitter data to reveal two different modes: inter-city and intra-city movement.
 In short, these fitting functions suggest the existence of multi-scale or multi-modal urban movements captured from Twitter users in Great Britain, which means the geographically cohesive, non-overlapping urban areas identified in the next section are not just a result of short distance movement but emerge naturally from the broader Twitter user mobility pattern.
@@
 Further, we analyzed the distribution of radius of gyration to understand the movement from the point of view of individual Twitter users rather than separate displacements.
-The distribution of the radius of gyration of Twitter users in Great Britain can be approximated through a combination of three functions: $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10m$ from [10 m, 30m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50m, 10km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [10km, 100km], where these three functions account for 92$\%$ of all the users.
+The distribution of the radius of gyration of Twitter users in Great Britain can be approximated through a combination of three functions: $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}= 10 m$ from [10 m, 30 m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50 m, 10 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [10 km, 100 km], where these three functions account for 92$\%$ of all the users.
 This suggests that there are three primary types of users that: (1) tend to stay at one location or at nearby locations when they tweet, or (2) tend to move at the intra-city scale when they tweet, or (3)  tend to exhibit a large spatial coverage.
@@
 \includegraphics[width=1.0\linewidth]{./figure/S4_radius_displacement_3}
-\caption{{\bf The probability distribution of Twitter user displacements and radius of gyration:} (a) $P(d)$ is approximated by an exponential, a stretched-exponential and a power-law function (b) the distance between [70m, 70km] is approximated by a double power-law functions (c) $P(r_g)$ of Great Britain is approximated by the combination of an exponential, a stretched-exponential and a power-law function.
+\caption{{\bf The probability distribution of Twitter user displacements and radius of gyration:} (a) $P(d)$ is approximated by an exponential, a stretched-exponential and a power-law function (b) the distance between [70 m, 70 km] is approximated by a double power-law functions (c) $P(r_g)$ of Great Britain is approximated by the combination of an exponential, a stretched-exponential and a power-law function.
 (d) $P(r_g)$ of London is approximated an exponential and a stretched-exponential function.
@@
 To help readers that are not familiar with the geographic context in Great Britain better interpret the derived boundaries,
-we had added two additonal layers (i.e., locations of airport fields and population-wighted-centroids of workplace zones in the Great Britian) in the background of the figures.
-Fig.~\ref{S5_Fig}  presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4km, greater than 10 km, and using all available displacements together compared to the administrative boundaries of Great Britain.
+we had added two additional layers (i.e., locations of airport fields and population-wighted-centroids of workplace zones in the Great Britain) in the background of the figures.
+Fig.~\ref{S5_Fig} presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4 km, greater than 10 km, and using all available displacements together compared to the administrative boundaries of Great Britain.
 One clear observation in both the coarse and fine delineations is that most of the geographic divisions are centered around big urban cores with relatively high populations.
@@
 \begin{center}
-\includegraphics[width=0.9\linewidth]{./figure/S5_community}
+\includegraphics[width=0.85\linewidth]{./figure/S5_community}
 \caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) all displacements with $L(M)= 7.8$.
-(b) displacements longer than 10 km ($L(M)=8.5$), red symbols are the locations of airport fields in the Great Britain (c) displacements shorter than 4 km ($L(M)=4.5$) (d) and displacements longer than 4 km ($L(M)=8.1$).The partition of space was done using a 10 km fishnet for the directed displacements from and to each cell.
+(b) displacements longer than 10 km ($L(M)=8.5$), red symbols are the locations of airport fields in Great Britain (c) displacements shorter than 4 km ($L(M)=4.5$) (d) and displacements longer than 4 km ($L(M)=8.1$).The partition of space was done using a 10 km fishnet for the directed displacements from and to each cell.
 Each color represents a unique community with more Twitter users displacements among the cells compared to others.
@@
 Including short distance movements has increased the power to differentiate the influence of nearby cities such as Glasgow and Edinburgh (lower left), while restricting the analysis to longer distance movements grouped travelers from the two previous cities into the same community (lower right).
-Red symbols are the locations of airport fields and gray points are the population-wighted-centroids of workplace zones in the Great Britian.}
+Red symbols are the locations of airport fields and gray points are the population-wighted-centroids of workplace zones in Great Britain.}
 \label{S6_Fig}
@@
 We chose 1-km cell size as referred from the related literature~\citep{liu2015}, which suggested 1-km cell size is detailed enough to depict urban structures.
-The spatial partitions derived from a fine grid of 1km used all available Twitter user trips without any restriction on trip distances yields geographic boundaries comparable to some of London's boroughs  (Fig.~\ref{S7_Fig}).
+The spatial partitions derived from a fine grid of 1 km used all available Twitter user trips without any restriction on trip distances yields geographic boundaries comparable to some of London's boroughs  (Fig.~\ref{S7_Fig}).
 However, some areas are shown to be more cohesive and display greater spatial interactions across the administrative boundaries, for instance, central London.
@@
 \includegraphics[width=0.7\linewidth]{./figure/Gravity}
-\caption{{\bf The observed interaction strength versus the estimated ones from the adopted gravity model with $\bf{\beta}$ = 0.8 } Note that the $\beta$ value is taken from the probability density function of radius of gyration when $r_{g} > 10 km$.
+\caption{{\bf The observed interaction strength versus the estimated ones from the adopted gravity model with $\bf{\beta}$ = 0.8} Note that the $\beta$ value is taken from the probability density function of radius of gyration when $r_{g} > 10 km$.
 The red dash line indicate strong linear correlation between the estimated and observed interaction strength with $R^{2}$ = 0.89 and $p-value < 0.01$.}
@@
 Third, since the collective radius of gyration was used to determine the cell-size in the network, we examined the temporal stability for the measurement in the geo-located Twitter data.
-The probability distributions of the radius of gyration for Twitter users in the Great Britain are verified to be consistent across different monthly time span (see Supplement Materials section 2), which indicates the stability of using such measurements in this study.
+The probability distributions of the radius of gyration for Twitter users in Great Britain are verified to be consistent across different monthly time span (see Supplement Materials section 2), which indicates the stability of using such measurements in this study.
 Finally, as the geo-located Twitter data offers easy data accessibility, our methods can be reproduced for other countries. 
@@
 Such an effect can be explained by the probability distributions of the radius of gyrations of individual Twitter users.
-The probability of distance that deviates from a user's center location decays with a stretched-exponential function from [50m, 10km], which means the movements from Twitter users with smaller spatial coverage dominate the delineation of the connected urban areas.
+The probability of distance that deviates from a user's center location decays with a stretched-exponential function from [50 m, 10 km], which means the movements from Twitter users with smaller spatial coverage dominate the delineation of the connected urban areas.
 To avoid arbitrarily deciding the cell-size, we studied the probability distributions of the radius of gyrations of individual Twitter users and selected 10-km as the cell-size, which is the distinct geographic distance for separating two main groups of Twitter users in terms of their spatial coverage at the national level.
@@
 Twitter user movements were used to establish a connectivity network of the fishnet cells.
-Then we applied the map equation algorithm to partition the network and associated geographic regions.
-The strongly connected communities within the network space yields geographically cohesive, non-overlapping urban areas that provides a clear delineation of the urban boundaries in Great Britain.
+We applied the map equation algorithm to partition the network and associated geographic regions.
+The strongly connected communities within the network space yielded geographically cohesive, non-overlapping urban areas that provided a clear delineation of the urban boundaries in Great Britain.
 By performing a statistical analysis of Twitter user mobility patterns in Great Britain, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
@@
 
-\bibitem[\protect\citeauthoryear{Sakaki {\itshape{et~al.}}}{2010}]{sakaki2010}
-Sakaki, T., Okazaki, M., Matsuo, Y., 2010.
-Earthquake Shakes Twitter Users: Real-time Event Detection by Social Sensors, in: Proceedings of the 19th International Conference on World Wide Web, WWW ’10.
-ACM, NY, USA, pp.
-851-860
-
 \bibitem[\protect\citeauthoryear{Schliephake}{2014}]{schliephake}
@@
 
+\bibitem[\protect\citeauthoryear{Zandbergen}{2009}]{zandbergen2009}
+Zandbergen, P.A., 2009. Accuracy of iPhone Locations: A Comparison of Assisted GPS, WiFi and Cellular Positioning. Transactions in GIS, 13, pp. 5-25.
+
 \bibitem[\protect\citeauthoryear{Zhao {\itshape{et~al.}}}{2015}]{zhao2015}

### 2016-10-15 ijgi-148112-for proofreading/ijgi-148112-can be published.tex
new author list

@@
 % Authors, for the paper (add full first names)
-\Author{Junjun Yin $^{1,3}$ and Zhenhong Du $^{2,3,*}$}
+\Author{Junjun Yin $^{1,2}$, Shaowen Wang $^{1,2,3}$ and Zhenhong Du $^{4,*}$}
 % Authors, for metadata in PDF
-\AuthorNames{Junjun Yin and Zhenhong Du}
+\AuthorNames{Junjun Yin, Shaowen Wang and Zhenhong Du}
 
@@
 \address{%
-$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
-$^{2}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn\\
-$^{3}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA}
+$^{1}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
+$^{2}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
+$^{3}$ \quad National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
+$^{4}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn
+}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Junjun Yin conceived and designed the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin and Zhenhong Du wrote the paper.}
+\authorcontributions{Shaowen Wang conceived and designed the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin, Shaowen Wang and Zhenhong Du wrote the paper.}
 
@@
 \newblock Understanding mobility based on GPS data.
-\newblock  In Proceedings of the 10th International Conference on Ubiquitous
-  Computing, Seoul, South Korea, 21--24 September 2008.
+\newblock  Proceedings of the 10th international conference on Ubiquitous
+  computing. ACM,  2008, pp. 312--321.
 
@@
 \newblock Characterizing the human mobility pattern in a large street network.
-\newblock {\em Phys. Rev. E} {\bf 2009}, doi:10.1103/PhysRevE.80.021136.
+\newblock {\em Physical Review E} {\bf 2009}, {\em 80},~021136.
 
@@
   diseases.
-\newblock {\em Phys. Rev. X} {\bf 2011}, doi:10.1103/PhysRevX.1.011001.
+\newblock {\em Physical Review X} {\bf 2011}, {\em 1},~011001.
 
@@
 \newblock Human migration: Theory, models, and empirical studies.
-\newblock {\em J. Reg. Sci.} {\bf 1985}, {\em 25},~521--544.
+\newblock {\em Journal of regional Science} {\bf 1985}, {\em 25},~521--544.
 
@@
 Jurdak, R.; Zhao, K.; Liu, J.; AbouJaoude, M.; Cameron, M.; Newth, D.
-\newblock Understanding human mobility from twitter.
-\newblock {\em PLoS One} {\bf 2015}, doi:10.1371/journal.pone.0131469.
+\newblock Understanding Human Mobility from Twitter.
+\newblock {\em PLoS ONE} {\bf 2015}, {\em 10},~e0131469.
 
@@
 \newblock On the levy-walk nature of human mobility.
-\newblock {\em IEEE/ACM Trans. Netw.} {\bf 2011}, {\em
+\newblock {\em IEEE/ACM transactions on networking (TON)} {\bf 2011}, {\em
   19},~630--643.
@@
   data of mobile networks.
-\newblock {\em J. Urban Technol.} {\bf 2010}, {\em 17},~41--60.
+\newblock {\em Journal of Urban Technology} {\bf 2010}, {\em 17},~41--60.
 
@@
   phone data.
-\newblock {\em PloS One} {\bf 2014}, doi:10.1371/journal.pone.0096180.
+\newblock {\em PloS one} {\bf 2014}, {\em 9},~e96180.
 
@@
   of spatial big data.
-\newblock {\em Int. J. Commun.} {\bf 2014}, {\em
+\newblock {\em International Journal of Communication} {\bf 2014}, {\em
   8},~1765--1783.
@@
 \newblock Geo-located Twitter as proxy for global mobility patterns.
-\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2014}, {\em
+\newblock {\em Cartography and Geographic Information Science} {\bf 2014}, {\em
   41},~260--271.
@@
 Giannotti, F.; Pedreschi, D.
-\newblock {\em Mobility, Data Mining and Privacy: Geographic Knowledge
-  Discovery}; Springer Science \& Business Media: Berlin, Germany,  2008.
+\newblock {\em Mobility, data mining and privacy: Geographic knowledge
+  discovery}; Springer Science \& Business Media,  2008.
 
@@
 Crampton, J.W.
-\newblock Collect it all: National security, Big Data and governance.
-\newblock {\em GeoJournal} {\bf 2014}, {\em 9}, 1--13.
+\newblock Collect it all: national security, Big Data and governance.
+\newblock {\em GeoJournal} {\bf 2014}, pp. 1--13.
 
@@
   social media check-in data.
-\newblock {\em PLoS one} {\bf 2014}, doi:10.1371/journal.pone.0097010.
+\newblock {\em PloS one} {\bf 2014}, {\em 9},~e97010.
 
@@
   large-scale location-based data from online social media.
-\newblock  In Proceedings of the 2nd ACM SIGKDD International Workshop on Urban
-  Computing, Chicago, IL, USA, 11--14 August 2013.
+\newblock  Proceedings of the 2nd ACM SIGKDD international workshop on urban
+  computing. ACM,  2013, p.~6.
 
@@
 Cho, E.; Myers, S.A.; Leskovec, J.
-\newblock Friendship and mobility: User movement in location-based social
+\newblock Friendship and mobility: user movement in location-based social
   networks.
-\newblock  In Proceedings of the 17th ACM SIGKDD International Conference on
-  Knowledge Discovery and Data Mining, San Diego, CA, USA, 21--24 August 2011.
+\newblock  Proceedings of the 17th ACM SIGKDD international conference on
+  Knowledge discovery and data mining. ACM,  2011, pp. 1082--1090.
 
@@
 Noulas, A.; Scellato, S.; Lambiotte, R.; Pontil, M.; Mascolo, C.
-\newblock A tale of many cities: Universal patterns in human urban mobility.
-\newblock {\em PLoS One} {\bf 2012}, doi:10.1371/journal.pone.0037027.
+\newblock A tale of many cities: universal patterns in human urban mobility.
+\newblock {\em PloS one} {\bf 2012}, {\em 7},~e37027.
 
@@
   diseases.
-\newblock {\em Proc. Nat. Acad. Sci.} {\bf 2009},
+\newblock {\em Proceedings of the National Academy of Sciences} {\bf 2009},
   {\em 106},~21484--21489.
@@
 Tamerius, J.; Nelson, M.I.; Zhou, S.Z.; Viboud, C.; Miller, M.A.; Alonso, W.J.
-\newblock Global influenza seasonality: Reconciling patterns across temperate
+\newblock Global influenza seasonality: reconciling patterns across temperate
   and tropical regions.
-\newblock {\em Environ. Health Perspect.} {\bf 2011}, {\em 119},~439--445.
+\newblock {\em Environmental health perspectives} {\bf 2011}, {\em 119},~439.
 
@@
   Data.
-\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2015}, {\em
+\newblock {\em Cartography and Geographic Information Science} {\bf 2015}, {\em
   42},~70--74.
@@
 Zheng, Y.; Xie, X.; Ma, W.Y.
-\newblock GeoLife: A collaborative social networking service among user,
-  location and trajectory. {\em IEEE Data(base) Eng. Bulletin} {\bf 2010}, {\em 33}, 32--39.
+\newblock GeoLife: A Collaborative Social Networking Service among User,
+  Location and Trajectory. {\bf 2010}.
 
@@
 \newblock Human mobility characterization from cellular network data.
-\newblock {\em Commun. ACM} {\bf 2013}, {\em 56},~74--82.
+\newblock {\em Communications of the ACM} {\bf 2013}, {\em 56},~74--82.
 
@@
   in an extensive set of countries.
-\newblock {\em PLoS One} {\bf 2013}, doi:10.1371/journal.pone.0081707.
+\newblock {\em PLoS One} {\bf 2013}, {\em 8},~e81707.
 
-\bibitem[Twitter (2016)]{twitterAPI}
-Twitter Streaming API
-\newblock available from: https://dev.twitter.com/streaming/overview
-\newblock {\bf 2016}, accessed on October, 2016
+\bibitem[Twitter(2016)]{twitterAPI}
+Twitter.
+\newblock Twitter streaming API.
+\newblock {\em available from: https://dev.twitter.com/streaming/overview} {\bf
+  2016}.
 
@@
 Cranshaw, J.; Schwartz, R.; Hong, J.I.; Sadeh, N.M.
-\newblock The livehoods project: Utilizing social media to understand the
-  dynamics of a city.
-\newblock  In Proceedings of the ICWSM 2012, Dublin, Ireland, 4--8 June 2012.
+\newblock The Livehoods Project: Utilizing Social Media to Understand the
+  Dynamics of a City.
+\newblock  ICWSM,  2012.
 
@@
 \newblock The geography of happiness: Connecting twitter sentiment and
-  expression, demographics, and objective characteristics of place. {\em PLoS One} {\bf 2013}, doi:10.1371/journal.pone.0064417.
+  expression, demographics, and objective characteristics of place {\bf 2013}.
 
@@
   et~al.]{longley2015geotemporal}
-Longley, P.A.; Adnan, M.; Lansley, G.
+Longley, P.A.; Adnan, M.; Lansley, G.; others.
 \newblock The geotemporal demographics of Twitter usage.
-\newblock {\em Environ. Plan. A} {\bf 2015}, {\em 47},~465--484.
+\newblock {\em Environment and Planning A} {\bf 2015}, {\em 47},~465--484.
 
@@
   et~al.]{hagerstrand1985time}
-H{\"a}gerstrand, T.
-\newblock Time-geography: Focus on the corporeality of man, society, and
+H{\"a}gerstrand, T.; others.
+\newblock Time-geography: focus on the corporeality of man, society, and
   environment.
-\newblock In {\em The Science and Praxis of Complexity}; United Nations University: Montpellier, France, 1985; pp. 193--216.
+\newblock {\em The science and praxis of complexity} {\bf 1985}, pp. 193--216.
 
@@
 Kwan, M.P.; Lee, J.
-\newblock Geovisualization of human activity patterns using 3D GIS: A
-  time-geographic approach. In 
-\newblock {\em Spatially Integrated Social Science: Examples in Best Practice}; Michael, F.G., Donald, G.J. Eds.; Oxford University Press: Oxford, MI, USA, 2003; Volume 3, pp. 27--51.
+\newblock Geovisualization of human activity patterns using 3D GIS: a
+  time-geographic approach.
+\newblock {\em Spatially integrated social science} {\bf 2004}, {\em 27}.
 
@@
   movement data.
-\newblock {\em Cartogr. Int. J. Geogr.
-  Inf. Geovis.} {\bf 2007}, {\em 42},~117--138.
+\newblock {\em Cartographica: The International Journal for Geographic
+  Information and Geovisualization} {\bf 2007}, {\em 42},~117--138.
 
@@
 \newblock Research challenges in geovisualization.
-\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2001}, {\em
+\newblock {\em Cartography and Geographic Information Science} {\bf 2001}, {\em
   28},~3--12.
@@
 MacEachren, A.M.
-\newblock {\em How Maps Work: Representation, Visualization, and Design};
-  Guilford Press: New York, NY, USA, 2004.
+\newblock {\em How maps work: representation, visualization, and design};
+  Guilford Press,  2004.
 
@@
 \newblock Visual analytics tools for analysis of movement data.
-\newblock {\em ACM SIGKDD Explor. Newsl.} {\bf 2007}, {\em 9},~38--46.
+\newblock {\em ACM SIGKDD Explorations Newsletter} {\bf 2007}, {\em 9},~38--46.
 
@@
   social media data.
-\newblock {\em Comput. Environ. Urban Syst.} {\bf 2015}, {\em 51}, 70--82.
+\newblock {\em Computers, Environment and Urban Systems} {\bf 2015}, {\em
+  51},~70--82.
 
@@
   location-based social media.
-\newblock {\em Concurr. Comput. Pract. Exp.} {\bf
-  2014}, doi:10.1002/cpe.3287.
+\newblock {\em Concurrency and Computation: Practice and Experience} {\bf
+  2014}.
 
-\bibitem[Black \em{et~al.}(2012)Black, A., Mascaro, C., Gallagher, M. and Goggins, S.P.]{black2012twitter}
-Black, A., Mascaro, C., Gallagher, M. and Goggins, S.P.
-\newblock DTwitter zombie: Architecture for capturing, socially transforming and analyzing the Twittersphere
-\newblock In {\em Proceedings of the 17th ACM international conference on Supporting group work} {\bf 2012}, pp. 229-238. ACM.
+\bibitem[Black \em{et~al.}(2012)Black, Mascaro, Gallagher, and
+  Goggins]{black2012twitter}
+Black, A.; Mascaro, C.; Gallagher, M.; Goggins, S.P.
+\newblock Twitter zombie: Architecture for capturing, socially transforming and
+  analyzing the Twittersphere.
+\newblock  Proceedings of the 17th ACM international conference on Supporting
+  group work. ACM,  2012, pp. 229--238.
 
@@
 \newblock The hadoop distributed file system.
-\newblock  {\em Mass Storage Syst. Technol.}  {\bf 2010}, doi:10.1109/MSST.2010.5496972.
+\newblock  Mass Storage Systems and Technologies (MSST), 2010 IEEE 26th
+  Symposium on. IEEE,  2010, pp. 1--10.
 
@@
 Dean, J.; Ghemawat, S.
-\newblock MapReduce: Simplified data processing on large clusters.
-\newblock {\em Commun. ACM} {\bf 2008}, {\em 51},~107--113.
+\newblock MapReduce: simplified data processing on large clusters.
+\newblock {\em Communications of the ACM} {\bf 2008}, {\em 51},~107--113.
 
@@
 Gao, H.; Tang, J.; Liu, H.
-\newblock Exploring social-historical ties on location-based social networks.
-\newblock In Proceedings of the ICWSM 2012, Dublin, Ireland, 4--8 June 2012.
+\newblock Exploring Social-Historical Ties on Location-Based Social Networks.
+\newblock  ICWSM,  2012.
 
@@
 Buttenfield, B.P.; McMaster, R.B.
-\newblock {\em Map Generalization: Making Rules for Knowledge Representation};
-  Longman Scientific \& Technical: New York, NY, USA, 1991.
+\newblock {\em Map Generalization: Making rules for knowledge representation};
+  Longman Scientific \& Technical New York,  1991.
 
@@
 \newblock The quadtree and related hierarchical data structures.
-\newblock {\em ACM Comput. Surv. (CSUR)} {\bf 1984}, {\em 16},~187--260.
+\newblock {\em ACM Computing Surveys (CSUR)} {\bf 1984}, {\em 16},~187--260.
 
@@
 \newblock Power-law distributions in empirical data.
-\newblock {\em SIAM Rev.} {\bf 2009}, {\em 51},~661--703.
+\newblock {\em SIAM review} {\bf 2009}, {\em 51},~661--703.
 
@@
   collection when correlated random walks embody observed movement patterns.
-\newblock {\em J. Royal Soc. Int.} {\bf 2012}, {\em
+\newblock {\em Journal of The Royal Society Interface} {\bf 2012}, {\em
   9},~528--534.
@@
   transportation modality decomposition.
-\newblock {\em Sci. Rep.} {\bf 2015}, doi:10.1038/srep09136.
+\newblock {\em Scientific reports} {\bf 2015}, {\em 5}.
 
@@
   education.
-\newblock {\em Sci. Gatew. Workshops 2013} {\bf
-  2014}, doi:10.1002/cpe.3256.
+\newblock {\em Concurrency and Computation: Practice and Experience} {\bf
+  2014}.
 

### 2016-10-16 ijgi-148112-for proofreading/ijgi-148112-can be published.tex
hope it works

@@
 $^{2}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
-$^{3}$ \quad National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
+$^{3}$ \quad National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; shaowen@illinois.edu\\
 $^{4}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn

### 2016-10-16 semantic_decomposition_of_twitter_user_locations/paper.tex
hope it works

--- 2016-08-21 semantic_decomposition_of_twitter_user_locations/paper.tex
@@
 % \title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
-\title{A tale of two cities: A data synthesis approach for semantic decompositions of Twitter user locations}
-\author[1~\thanks{yinjunjun@gmail.com}]{Junjun Yin}
+\title{A tale of two cities: A GIS based data synthesis approach to understanding semantic decompositions of Twitter user locations}
+\author{Junjun Yin}
+\author{Shaowen Wang~\thanks{shaowen@illinois.edu}}
 \affil[1]{Department of Geography and Geographic Information Science}
+\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
+\affil[2]{CyberGIS Center for Advanced Digital and Spatial Studies}
+\affil[3]{Department of Geography and Geographic Information Science}
+\affil[4]{National Center for Supercomputing Applications}
 \affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
@@
 \section*{Abstract}
+Semantic Trajectory Mining for Location Prediction
 
 Today's pervasive Location Based Social Media provide abundant user-generated geographic information
-In this paper, we present a scalable data integration 
+In this paper, we present a geographical information system (GIS) based data synthesis approch to understanding semantic decompositions of Twitter user locations.
+Specifically, we implemented a
+This approach 
 We analyzed the
@@
 \section{Introduction}
-Today's pervasive Location Based Social Media (LBSM) are attacting much attention from many researh displines. For example,
+With the advancements in mobile technology, the location information 
+what is it?
+
+why it is important?
+
+why is my solution?
+
+The remainder of this paper is organized as follows. Section 2 introduces the related work 
+Section 3 details the 
+Detailed analysis of the
+Section 5 presents the results
+Section 6 concludes the paper.
 

### 2016-10-17 semantic_decomposition_of_twitter_user_locations/paper.tex
Revert "hope it works"
This reverts commit 43218950806362a5c77e513fb4be43499ad56636.

@@
 \title{A tale of two cities: A GIS based data synthesis approach to understanding semantic decompositions of Twitter user locations}
-\author{Junjun Yin}
-\author{Shaowen Wang~\thanks{shaowen@illinois.edu}}
+% \author~\thanks{yinjunjun@gmail.com]{Junjun Yin}
+\author{Junjun Yin~\thanks{jyn@illinois.edu}}
 \affil[1]{Department of Geography and Geographic Information Science}
-\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
-\affil[2]{CyberGIS Center for Advanced Digital and Spatial Studies}
-\affil[3]{Department of Geography and Geographic Information Science}
-\affil[4]{National Center for Supercomputing Applications}
 \affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
@@
 \section*{Abstract}
-Semantic Trajectory Mining for Location Prediction
-
 Today's pervasive Location Based Social Media provide abundant user-generated geographic information

### 2016-10-17 ijgi-148112-for proofreading/ijgi-148112-can be published.tex
edits

--- 2016-10-15 ijgi-148112-for proofreading/ijgi-148112-can be published.tex
@@
 % Authors, for the paper (add full first names)
-\Author{Junjun Yin $^{1,2}$, Shaowen Wang $^{1,2,3}$ and Zhenhong Du $^{4,*}$}
+\Author{Junjun Yin $^{1,2,*}$ and Zhenhong Du $^{2,3}$}
 % Authors, for metadata in PDF
-\AuthorNames{Junjun Yin, Shaowen Wang and Zhenhong Du}
+\AuthorNames{Junjun Yin and Zhenhong Du}
 
@@
 \address{%
-$^{1}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
-$^{2}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
-$^{3}$ \quad National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
-$^{4}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn
+$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Champaign, IL 61820 U.S.A.;~jyn@illinois.edu;\\ 
+$^{2}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801 U.S.A.\\
+$^{3}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn
 }
@@
 % Contact information of the corresponding author
-\corres{Correspondence: duzhenhong@zju.edu.cn; Tel.: +86-138-1919-2989}
+\corres{Correspondence: jyn@illinois.edu}
 
@@
 However, the capability of capturing detailed human movements with fine-grained spatial and temporal granularity is still limited.
-In this study, we extracted high-resolution mobility data from a collection of over 1.3 billion geo-located Twitter messages.
+In this study, we extracted high-resolution mobility data from a collection of over 1.3 billion geo-located tweets.
 Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access, the dataset is collected from publicly accessible Twitter data streams.
 In this paper, we employed a visual-analytics approach to studying multi-scale spatiotemporal Twitter user mobility patterns in the contiguous United States during the year 2014.
-Our approach included a scalable visual-analytics framework to deliver efficiency and scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-scale spatiotemporal user mobility patterns.
+Our approach included a scalable visual-analytics framework to deliver efficiency and scalability in filtering large volume of geo-located tweets, modeling and generating space-time user trajectories, and summarizing multi-scale spatiotemporal user mobility patterns.
 We performed a set of statistical analysis to understand Twitter user mobility patterns across multi-level spatial scales and temporal ranges.
@@
 By further studying such mobility patterns in different temporal ranges, we identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
-At the same time, our approach provides a geo-visualization unit with an interactive 3D virtual globe web mapping interface for exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements.}
+In addition, our approach provided an interactive 3D virtual globe web mapping interface for performing exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements.}
 
@@
 For instance, researchers have used geo-located tweets for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible for other mobility datasets (e.g., GPS traces and mobile phone call records).
-Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}, the publicly available LBSM data streams offer unique opportunities for conducting reproducible and comparative scientific findings across different geographic regions.
+Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}, the publicly available LBSM data streams offer unique opportunities for conducting reproducible and comparative scientific findings across different geographical regions.
 
@@
 This framework is implemented on high-performance distributed computing environment using Apache Hadoop.
-It provides efficiency in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
-For example, we have included an experiment for illustrating the processing time regarding generating Twitter user trajectories across different time span in the supplement material.
+It provides efficiency in filtering large volume of geo-located tweets, modeling and generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
+For example, we have included an experiment for illustrating the processing time regarding generating Twitter user trajectories across different time span in the supplementary material.
 
@@
 
-Finally, it is worth noting that at the current stage the geo-located Twitter data is not able to generalize to the entire population.
-As the demographic information of the Twitter users cannot be easily identified, the results derived in this study may not reflect a complete real-world image of human movements, which should be carefully considered in future studies.
-Nevertheless, the Twitter user movements provide clear supports to reveal the distance decay effects in human mobility research, which is observed in multiple spatial and temporal scales.
-Due to the large sample size, it is difficult to generalize the mobility pattern found at national level to entire population, city-level mobility pattern may provide better insights for investigating mobility dynamics.
+It is worth noting that at the current stage the geo-located Twitter data is not able to generalize to the entire population.
+As the demographic information of Twitter users cannot be easily identified, the results derived in this study may not reflect a complete real-world image of human movements, which should be carefully considered in future studies.
+Nevertheless, the Twitter user movements provide clear supports for revealing the distance decay effects in human mobility research, which is observed in multiple spatial and temporal scales.
+Due to the large sample size, it is difficult to generalize the mobility pattern found at national level to the entire population, city-level mobility pattern may provide better insights for investigating mobility dynamics.
 For example, the results of radius of gyration in Chicago exhibit similar pattern found in larger spatial scale, and with inputs of other mobility dataset that are often available at city-level, such as taxi trip records and mobile phone call data, there is a potential to synthesize these different sources of information and therefore provide a more complete image for understanding human mobility patterns.
-On the other hand, as we have discussed in this paper that geo-located Twitter data show the advantages regarding the easy data accessibility, the large spatial coverage and massive sample size, our approach took advantage of such data source to understand the mobility patterns across multiple spatial scales and temporal ranges.
+On the other hand, as we have discussed in this paper that geo-located tweets show advantages in terms of easy data accessibility, large spatial coverage and massive sample size, our approach took advantage of such data source to understand the mobility patterns across multiple spatial scales and temporal ranges.
 Also, our approach can be applied to the setting of other countries, which can be used to carry out comparative studies regarding spatiotemporal Twitter user mobility patterns.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Shaowen Wang conceived and designed the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin, Shaowen Wang and Zhenhong Du wrote the paper.}
+\authorcontributions{Junjun Yin conceived and designed the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin and Zhenhong Du wrote the paper.}
 

### 2016-10-17 ijgi-148112-for proofreading/ijgi-148112-can be published_origin.tex
edits

--- 2016-10-15 ijgi-148112-for proofreading/ijgi-148112-can be published.tex
@@
 % Authors, for the paper (add full first names)
-\Author{Junjun Yin $^{1,2}$, Shaowen Wang $^{1,2,3}$ and Zhenhong Du $^{4,*}$}
+\Author{Junjun Yin $^{1,3}$ and Zhenhong Du $^{2,3,*}$}
 % Authors, for metadata in PDF
-\AuthorNames{Junjun Yin, Shaowen Wang and Zhenhong Du}
+\AuthorNames{Junjun Yin and Zhenhong Du}
 
@@
 \address{%
-$^{1}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
-$^{2}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
-$^{3}$ \quad National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
-$^{4}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn
-}
+$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
+$^{2}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn\\
+$^{3}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA}
 

### 2016-10-19 Multi-scale_Mobility_Pattern_CEUS/template-num.tex
init

--- 2016-10-17 ijgi-148112-for proofreading/ijgi-148112-can be published.tex
@@
-%  LaTeX support: latex@mdpi.com
-%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
+% Template article for preprint document class `elsart'
+% SP 2006/04/26
 
-% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.
+\documentclass{elsart}
 
-%=================================================================
-\documentclass[ijgi,article,accept,moreauthors,pdftex,10pt,a4paper]{mdpi}
+% Use the option doublespacing or reviewcopy to obtain double line spacing
+% \documentclass[doublespacing]{elsart}
 
-%=================================================================
-\firstpage{1}
-\makeatletter 
-\setcounter{page}{\@firstpage} 
-\makeatother 
-\articlenumber{x}
-\doinum{10.3390/------}
-\pubvolume{xx}
-\pubyear{2016}
-\copyrightyear{2016}
-\externaleditor{Academic Editors: Marguerite Madden and Wolfgang Kainz}
-\history{Received: 15 August 2016; Accepted: 28 September 2016; Published: date}
-%------------------------------------------------------------------
-% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
-%\pdfoutput=1
+% if you use PostScript figures in your article
+% use the graphics package for simple commands
+% \usepackage{graphics}
+% or use the graphicx package for more complicated commands
+% \usepackage{graphicx}
+% or use the epsfig package if you prefer to use the old commands
+% \usepackage{epsfig}
 
-%=================================================================
-% Add packages and commands here.
-The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed
+% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb}
 
-%=================================================================
+% The lineno packages adds line numbers. Start line numbering with
+% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+% for the whole article with \linenumbers.
+% \usepackage{lineno}
 
-\usepackage{placeins}
-
-%% Please use the following mathematics environments:
- \theoremstyle{mdpi}
- \newcounter{thm}
- \setcounter{thm}{0}
- \newcounter{ex}
- \setcounter{ex}{0}
- \newcounter{re}
- \setcounter{re}{0}
-
- \newtheorem{Theorem}[thm]{Theorem}
- \newtheorem{Lemma}[thm]{Lemma}
- \newtheorem{Corollary}[thm]{Corollary}
- \newtheorem{Proposition}[thm]{Proposition}
-
- \theoremstyle{mdpidefinition}
- \newtheorem{Characterization}[thm]{Characterization}
- \newtheorem{Property}[thm]{Property}
- \newtheorem{Problem}[thm]{Problem}
- \newtheorem{Example}[ex]{Example}
- \newtheorem{ExamplesandDefinitions}[ex]{Examples and Definitions}
- \newtheorem{Remark}[re]{Remark}
- \newtheorem{Definition}[thm]{Definition}
-%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
-
-%=================================================================
-% Full title of the paper (Capitalized)
-%\Title{Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
-\Title{Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns with a Visual-Analytics Approach}
-
-% Authors, for the paper (add full first names)
-\Author{Junjun Yin $^{1,2,*}$ and Zhenhong Du $^{2,3}$}
-% Authors, for metadata in PDF
-\AuthorNames{Junjun Yin and Zhenhong Du}
-
-% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Champaign, IL 61820 U.S.A.;~jyn@illinois.edu;\\ 
-$^{2}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801 U.S.A.\\
-$^{3}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn
-}
-
-% Contact information of the corresponding author
-\corres{Correspondence: jyn@illinois.edu}
-
-% Current address and/or shared authorship
-
-% Simple summary
-%\simplesumm{}
-
-% Abstract (Do not use inserted blank lines, i.e. \\) 
-\abstract{Understanding human mobility patterns is of great importance for urban planning, traffic management, and even marketing campaign.
-However, the capability of capturing detailed human movements with fine-grained spatial and temporal granularity is still limited.
-In this study, we extracted high-resolution mobility data from a collection of over 1.3 billion geo-located tweets.
-Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access, the dataset is collected from publicly accessible Twitter data streams.
-In this paper, we employed a visual-analytics approach to studying multi-scale spatiotemporal Twitter user mobility patterns in the contiguous United States during the year 2014.
-Our approach included a scalable visual-analytics framework to deliver efficiency and scalability in filtering large volume of geo-located tweets, modeling and generating space-time user trajectories, and summarizing multi-scale spatiotemporal user mobility patterns.
-We performed a set of statistical analysis to understand Twitter user mobility patterns across multi-level spatial scales and temporal ranges.
-In particular, Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals revealed multi-scale or multi-modal Twitter user mobility patterns.
-By further studying such mobility patterns in different temporal ranges, we identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
-In addition, our approach provided an interactive 3D virtual globe web mapping interface for performing exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements.}
-
-% Keywords
-\keyword{Geo-located tweets, mobility patterns, multi-scale spatiotemporal analysis, scalable visual-analytics framework}
+% \linenumbers
 \begin{document}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Sections that are not mandatory are listed as such. The section titles given are for Articles. Review papers and other article types have a more flexible structure.
+\begin{frontmatter}
 
-%% Only for the journal Gels: Please place the Experimental Section after the Conclusions
+% Title, authors and addresses
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\cite{belik2011natural}.
-Earlier research efforts relied on low-resolution mobility data to understand human mobility patterns, such as using census records to study human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
-However, such mobility data do not provide detailed human movements with fine-grained spatial and temporal granularity, which are usually aggregated and therefore are limited to capture mobility patterns of individuals~\cite{gonzalez2008understanding,Jurdak2015}.
-In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, emerging as a new mobility data source, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints in the form of real-world user trails and footprints~\cite{thatcher2014living}.
-A significant advantage of utilizing LBSM data streams as proxies for studying human mobility patterns is the large spatial coverage.
-For instance, researchers have used geo-located tweets for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible for other mobility datasets (e.g., GPS traces and mobile phone call records).
-Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}, the publicly available LBSM data streams offer unique opportunities for conducting reproducible and comparative scientific findings across different geographical regions.
+% use the thanksref command within \title, \author or \address for footnotes,
+% use the corauthref command within \author for corresponding author footnotes,
+% use the ead command for the email address,
+% and the form \ead[url] for the home page:
+% \title{Title\thanksref{label1}}
+% \thanks[label1]{}
+% \author{Name\corauthref{cor1}\thanksref{label2}}
+% \ead{email address}
+% \ead[url]{home page}
+% \thanks[label2]{}
+% \corauth[cor1]{}
+% \address{Address\thanksref{label3}}
+% \thanks[label3]{}
 
-Many recent studies have adopted LBSM data streams to study human mobility patterns.
-For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects in the collective user movements~\cite{gonzalez2008understanding}, which were used to reveal different travel modes~\cite{Jurdak2015}, travel demands~\cite{wu2014intra,hasan2013understanding}, and the impact of social connections~\cite{cho2011friendship}.
-These studies have provided strong supports for using LBSM data as proxies for studying mobility patterns of individuals and valuable insights into human mobility dynamics.
-However, the variations of movements in different spatial scales and temporal ranges are neglected in these studies, where the measurements of distances are either fixed in a certain time range or to a specific geographic region.
-For instances, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national levels) are lacking.
-Such insights are critical to advance our understandings of the collective mobility patterns for various applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
-On the other hand, while the high-resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data-intensive challenges for developing multi-scale spatiotemporal analysis approaches to dealing with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales~\cite{tsou2015}.
+\title{}
 
-In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
-The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from 1st January to 31st December 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
-To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
-This framework is implemented based on high-performance distributed computing environment using Apache Hadoop (http://hadoop.apache.org/), which is an open source software framework to enable distributed processing of large datasets across computing clusters.
-Enabled by this framework, we have performed a set of statistical analysis to understand multi-scale spatiotemporal Twitter user mobility patterns. 
-We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions.
-In particular, Twitter user mobility patterns measured by user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
-By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
-In addition, our approach provides an interactive 3D virtual globe web mapping interface to enable exploratory geo-visual analytics for understanding the detailed Twitter user movement flows within a given spatial scale and time window.
+% use optional labels to link authors explicitly to addresses:
+% \author[label1,label2]{}
+% \address[label1]{}
+% \address[label2]{}
 
-The remainder of this paper is organized as follows.
-Section 2 describes the related work in the context of studying mobility patterns using LBSM data, in particular, the geo-located Twitter data.
-We focus on research challenges in using visual-analytics methods to enable multi-scale spatiotemporal analysis with massive movement datasets, including data management, multi-level spatiotemporal user trajectory modeling and visualization.
-Section 3 details the processes for extracting, aggregating and summarizing multi-level spatiotemporal Twitter user mobility patterns.
-Section 4 presents the case study of performing visual-analytics for seeking multi-scale spatiotemporal Twitter mobility patterns in the continuous United States of the year 2014.
-Section 5 concludes the paper.
+\author{}
 
-\section{Mobility Patterns in Location Based Social Media data}
-\subsection{Geo-located Twitter Data for Studying Large-scale User Movements}
-To understand detailed mobility patterns of individuals, the capability to capture human movements with fine-grained spatial and temporal granularity is critical.
-In this connection, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\cite{zheng2008understanding}.
-However, such data are often limited in spatial scale (e.g., within a specific city or region) from a small group of people, for example, 226 and 182 volunteers participated in collecting such mobility data in~\cite{rhee2011levy} and~\cite{zheng2010geolife} respectively.
-Other than tracking people directly, the vehicle-based GPS traces are often tied to specific vehicles (e.g. taxi), which are only accessible for a certain group of people~\cite{kung2014exploring}.
+\address{}
 
-Another approach from the literatures for studying human mobility is using mobile phone call data, such as Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with an accuracy in the order of kilometers~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
-Such a dataset can cover relatively large spatial scale~\cite{becker2013human,sobolevsky2013delineating} (e.g., national level) and a large portion of the population in the study region~\cite{kung2014exploring}.
-However, due to the concerns of infringement on individual privacy, mobile phone call data are not publicly accessible at all.
-Even such data were obtained in the mentioned studies, they came from various service providers covering different groups of users.
-These issues limit the capability for conducting reproducible scientific findings for mobility research, such as validating or extending the existing discoveries.
+\begin{abstract}
+% Text of abstract
+\end{abstract}
 
-In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
-LBSM enables users to attach their current location as a geo-tag to the message they post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
-A Big Data scenario emerges when millions social media users constantly post messages.
-In this study, geo-located Twitter data are chosen as a source for studying detailed mobility patterns.
-Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
-It provides a publicly accessible streaming API for easy data access~\cite{twitterAPI}.
-Indeed, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.
+\begin{keyword}
+% keywords here, in the form: keyword \sep keyword
 
-However, it is worth noting that there are some limitations and complexities in directly using LBSM data for studying human mobility patterns.
-For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place.
-Although geo-located tweets tend to provide geo-locations with high position resolution as aforementioned~\cite{Jurdak2015}, the information regarding the quality of the geo-locations is absent in each tweet.
-This will contribute to the uncertainties in calculating the distance of Twitter user movements, especially in densely built environments.   
-There is also a potential mismatch regarding the representativeness of the overall population since not all people use social media or send geo-located messages~\cite{kung2014exploring}, the demographic information of the Twitter users cannot be easily identified.
-The derived mobility patterns may lead to an over or under-representation of the real-world human mobility patterns.
-Many studies started to look into the demographic information of LBSM data, in particular Twitter data~\cite{mitchell2013geography,longley2015geotemporal}.
-Although the used methods are still arguable, these issues certainly require us to pose stricter criteria in understanding human mobility patterns using geo-located Twitter data.
-On the other hand, geo-located Twitter dataset presents some unique advantages that make it a valuable proxy for studying human mobility patterns.
-For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\cite{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\cite{hawelka2014geo}, which is almost impossible for other mobility datasets.
-More importantly, by continuously monitoring the geo-located Twitter data streams with large volume of detailed and frequently updated spatiotemporal records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements), which is one of the motivations for this study.
+% PACS codes here, in the form: \PACS code \sep code
+\PACS 
+\end{keyword}
+\end{frontmatter}
 
-\subsection{Data-intensive Challenges for Multi-scale Geo-visual Analytics}
-Mobility data are essentially a collection of spatiotemporal records of people re-allocating across the geographic space.
-To study mobility patterns of individuals, a space-time trajectory of each individual user should be modeled and constructed to quantify the collective movements over space and time.
-Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of user displacements and radius of gyrations of individuals, to study the mobility dynamics.
-Indeed, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\cite{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal ranges.
-For example, a geo-visualization approach was used to study human activity patterns, where user trajectories were mapped in a 3D space ordered by timestamps in the third dimension~\cite{kwan2004geovisualization}.
-While such an approach enables visualization of individual trajectories, its capability is limited in dealing with large-volume movement datasets~\cite{andrienko2007designing}.
-Instead of directly visualizing an individual user's trajectories, a space-time cube approach was proposed to analyzing and visualizing the collective trajectories.
-It provides flexibilities in setting up both spatial scales and temporal ranges, and therefore is used to study mobility patterns across different spatial units (e.g., countries, states, and cities, etc.) and identify the changes over space and time~\cite{maceachren2001research, maceachren2004maps}.
-In this regard, visual-analytics methods are proposed to better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\cite{andrienko2007designing,andrienko2007visual}.
-Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\cite{andrienko2007designing}.
-Employing visual-analytics methods dealing with massive movement datasets is not only beneficial for optimizing visualizations but also provides a great deal of flexibilities for performing statistical analysis in seeking mobility patterns with different level of spatiotemporal details.
+% main text
+\section{}
+\label{}
 
-However, in the context of studying mobility patterns using large volume of geo-located Twitter data, the inherited large data volume poses significant data intensive challenges for visual-analytics methods to scale with both the data volume and the computational requirements (e.g., movement extraction and trajectory modeling)~\cite{cao2014scalable}.
-In particular, in our study, 1.3 billion geo-located tweets were collected with over 1 TB in file size.
-To construct a space-time trajectory of an individual, it is necessary to go through the massive dataset to sort and update the trajectory whenever a new location is found.
-Such a task is already computationally demanding, let along breaking the trajectories to construct space-time cube with multiple spatial scale and temporal ranges.
-Indeed, developing a multi-scale spatiotemporal analysis approach is identified as one of the research challenges for dealing with social media Big Data~\cite{tsou2015}.
-To address the data-intensive challenges, there is a need to develop a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
+% The Appendices part is started with the command \appendix,
+% appendix sections are then done as normal sections
+% \appendix
 
-\section{Materials and Methods}
-\subsection{Geo-located Twitter Data}
-Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at.
-In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
-To ensure complete coverage over the continuous United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
-The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2 GB in size) collected per day.
-We have collected more than 1.3 billion geo-located tweets from 1 January to 31 December 2014 with 6,147,430 Twitter users and 1 TB in file size.
+% \section{}
+% \label{}
 
-In particular, this data collection of the year 2014 was originally used to map the spatial spread of flu in North America during the time period~\cite{padmanabhan2014flumapper}.
-As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages in the dataset~\cite{black2012twitter}; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
-In this case, we adopted the speed limit value as 240 m/s used in~\cite{Jurdak2015}, where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
-Note that the original location information embedded in each geo-located tweet is given in units of latitude and longitude, the distance is calculated by the great-circle distance between two points on a sphere with the haversine formula.
-Finally, we used the geographic boundaries of the continuous United States (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section.
-Based on these reinforcements, the dataset contains 1,052,861,000 tweets and 4,559,205 unique users.
-
-\subsection{A scalable visual-analytics framework}
-To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
-The scalable visual-analytics framework consists of two main units: (1) Data processing unit: a distributed computing environment using Apache Hadoop for modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing the movements at multiple spatiotemporal scales.
-(2) Geo-visualization unit: an interactive 3D virtual globe web mapping interface for exploratory geo-visual analytics to understand detailed Twitter user movement flows across different spatial scales and temporal ranges.
-
-Apache Hadoop combines a distributed file system, namely Hadoop Distributed File System(HDFS)~\cite{shvachko2010hadoop} with MapReduce programming paradigm~\cite{dean2008mapreduce}, which can be applied to a wide range of data-intensive problems.
-Our framework benefits from using Hadoop in both data management and processing.
-First, since the input data is large it is desirable to store it on multiple machines.
-This provides scalability in relation to the growth of data size, where Hadoop can scale to more computing nodes in a cluster to maintain the performance.
-Second, by using Hadoop we can parallelize the computational tasks, where MapReduce breaks the entire computation into small tasks and schedule them among different computing nodes, to make the data processing faster and more efficient.
-An overall system architecture of the framework is shown in Figure~\ref{fig:overall_archi}.
-The details regarding the function and implementation of each unit are presented in the next sections.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.55\linewidth]{./figures/Overall_Architecture222}
-\caption{The overall system architecture of the framework.}
-\label{fig:overall_archi}
-\end{figure}
-\FloatBarrier
-
-\subsection{Space-time Twitter User Trajectories}
-To derive meaningful mobility patterns of individuals, a space-time trajectory of each individual user should be constructed~\cite{hagerstrand1985time}.
-Each raw geo-located tweet contains multiple fields of information, such as the created time, country, language code, and location, etc.
-To construct a space-time trajectory from the data collection, we are interested in the following fields: \textit{user ID, location, timestamp}, which can be represented by a tuple $\left\langle id, loc, t\right\rangle$, where \textit{id} is a unique string representing a Twitter user's id; \textit{loc} is the recorded location of the message represented as a pair of projected coordinates $\left\langle x, y\right\rangle$;
-and \textit{t} is the timestamp of when the message was posted; A Twitter user's space-time trajectory is defined as follows.
-\newline
-
-\noindent\textbf{Definition 1.
-Space-time Twitter user trajectory:} \emph{The space-time trajectory of a Twitter user is defined as a collection of recorded geo-locations in the chronological order (i.e., based on the attached timestamp):}
-\newline
-
-$Trajectory_{user_{id}} \equiv \lbrace \langle id, loc_{1}, t_{1}\rangle, \langle id, loc_{2}, t_{2}\rangle, \langle id, loc_{i}, t_{i}\rangle, ...
-\langle id, loc_{n}, t_{n}\rangle \rbrace, i = 1, 2, 3...n$
-\newline
-
-To remove non-human users based on unusual relocating speed, a user will be removed if the speed between any two consecutive locations in the user's trajectory with $speed$ $(loc_{i} - loc_{i-1}) > $ 240 m/s.
-Based on this definition for modeling the space-time Twitter user trajectories, we converted the process of extracting trajectories from the raw geo-located Twitter data as a MapReduce task.
-Specifically, each mapper utilizes the unique user id as a key to prepares the records that belong to the same user and send them to reducer.
-Once the reducers receive the $\langle key, value\rangle$ pairs, a Twitter user's space-time trajectory is formed by the sorting the locations in chronological order while considering the speed limit.
-\newline
-
-\noindent\textbf{Definition 2.
-visitation behavior, displacement and radius of gyration:} \emph{As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers the frequency of a user visiting different locations within a specific time frame.
-This metric provides an overall assessment regarding the diversity and similarity in the collective mobility pattern}~\cite{gao2012exploring}.
-
-In particular, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
-The displacement refers to an individual's re-allocation across the geographic space measured in distance, i.e., $distance (loc_{i} - loc_{i-1})$.
-It is not equivalent to a ``trip'' took by an individual, for instance, even the time interval between two recorded locations is one month, it will still count as a displacement.
-By studying the collective displacements from a group people, it helps to identify the distance bounds associated with different travel modes~\cite{Jurdak2015} and to quantitatively differentiate the mobility patterns from random walks~\cite{brockmann2006scaling}.
-On the other hand, radius of gyration (donated as $r_{g}$) is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008understanding}, which is defined as follows.
-\newline
-
-$r_{g} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(p_{i} - p_{centroid})^{2}}$, where $p_{centroid} = \frac{1}{n}\sum_{i=1}^{n}p_{i}$
-\newline
-
-\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, and therefore indicates the individual's spatial coverage, where $p_{i}$ and $p_{centroid}$ are the $ith$ location and the geometric center of the user's trajectory, respectively.
-When applying the measurement to the study population, it identifies different groups of people in terms of spatial coverage from their corresponding mobility patterns.
-Note that both displacements and radius of gyrations are measured by ``crow's fly distance'' in this study (i.e., the direct great-circle distance between two recorded locations).
-Since these metrics are based on the generated trajectories, by breaking and aggregating the trajectories in multiple spatial scales and temporal ranges, it enables performing multi-scale spatiotemporal analysis on these measurements and studying the corresponding mobility patterns.
-
-\subsection{Multi-level spatiotemporal trajectory aggregation}
-An important strategy for visual-analytics methods to deal with massive movement datasets is performing spatial aggregations to provide different levels-of-detail~\cite{andrienko2007designing,andrienko2007visual}.
-It is similar to the map generation approach that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest~\cite{buttenfield1991map}.
-To enable aggregating Twitter trajectories into multiple spatial scales, we have extended the hierarchical space-time cube model developed in~\cite{cao2014scalable}, where we partitioned the geographic space of the continuous United States into 10 hierarchical spatial layers and each space-time cube is created with a fixed time window of a week interval.
-Specifically, the state boundaries of the continuous United States are treated as the base layer (i.e.
-level 0) for aggregating state-level Twitter user movements, Alaska and Hawaii are excluded for the consideration of better visualization effects in the mapping interface of the framework.
-We then created an hierarchical fishnet by diving the study region into regular cells, where the finest level (level 10) consists 1 km $\times$ 1 km cells.
-Such a cell size is consistent with the spatial resolution in landscan (http://web.ornl.gov/sci/landscan) product for measuring the global population density.
-In our case, the cell width/height for level i-1 is twice of the size in level i.
-Figure~\ref{fig:multilevel} illustrates an hierarchical fishnet spatial units for mapping multi-level Twitter user movements.
-Note that any predefined geographic boundaries can be used and appended in this framework to show different level-of-detailed movements (e.g., national-level and census-tract level), in our case, we replaced the level 8 fishnet layer with the US county boundaries.
-
-To perform a multi-level spatial aggregation of the Twitter user trajectories using hierarchical spatial layers, each location in a user's trajectory is redistributed to the corresponding spatial units.
-A MapReduce algorithm for the spatial aggregation is implemented, where the ID of unit in each spatial layer (e.g., polygon in state and country layer and cell in the rest) is treated as key in the at the map stage.
-It performs a ``point-in-polygon'' geospatial operation to determine which polygon the point belongs to.
-If the location does not belong to any polygon, it will be dropped, which is how we used the geographic boundaries of the continuous United States to filer the raw tweet collection that initially covered the North America and kept the ``domestic'' ones.
-To optimize the ``point-in-polygon'' determination without comparing the location with every polygon in the spatial layer, we also created a Quad-Tree~\cite{samet1984quadtree} for each spatial layer to speed up the process.
-Finally, the reducers generate two data outputs: (1) reconstructed space-time Twitter user trajectories at each spatial level (2) movement flows in the form of in and out movement flux between the spatial units.
-The movement flows are stored in the database for interactive explorations in the 3D web mapping interface, whereas the re-constructed trajectories can be further processed to produce distance measures at different spatial scales, which is illustrated as fellows:
-\newline
-
-\noindent $Trajectory_{user_{id}} \equiv \lbrace \langle id, loc_{1}, t_{1}, unit_{1}\rangle, \langle id, loc_{2}, t_{2}, unit_{2}\rangle, \langle id, loc_{i}, t_{i}, unit_{i}\rangle, ...
-\langle id, loc_{n}, t_{n}, unit_{n}\rangle \rbrace$
-where $ i = 1, 2, 3...n$
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.6\linewidth]{./figures/multilevel}
-\caption{Hierarchical spatial layers for aggregating movements in different level-of-details.}
-\label{fig:multilevel}
-\end{figure}
-\FloatBarrier
-
-\section{Multi-scale Spatiotemporal Twitter User Mobility Patterns}
-\subsection{Spatiotemporal Twitter User Mobility Patterns}
-The situation of using geo-located tweets as proxies to infer people's movements is complex as users' tweeting behavior can be significantly different from one to another, in particular, the frequency and time-interval between two consecutive tweets.
-For example, some people may tweet once a day while others do more; some people may tweet regularly while others do not.  
-These tweeting behaviors are expected as such human dynamics are also seen in the mobile phone call data~\cite{gonzalez2008understanding}. 
-Many studies have carried out data collection within a certain time period (e.g., a year in our case).
-However, as the geo-located tweets were collected in a continuous fashion, it is necessary to examine the sensitivity regarding these behaviors to ensure we are not just capturing a random snapshot from the whole data streams.
-
-In this study, we have analyzed the cumulative distribution of the frequency Twitter users visiting different locations in the year 2014 (and every month), which uses the methods developed in~\cite{clauset2009power}.
-The frequency is summarized based on the trajectories of individuals extracted from a monthly time span.
-Note that different groups of Twitter users may exist in each month. 
-It appears that the distribution of the collective Twitter user visitation behaviors in the year 2014 follows a two-tiered power law distributions (shown in Figure~\ref{fig:visitation}.
-The majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$, where $x$ is the number of visited locations and the $\alpha$ value is 1.32.
-The tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $p(x)\sim x^{-\alpha}$ with $\alpha$ value is 3.5.
-This finding is consistent across all 12 months, with the mean $\alpha$ value as 1.34 $ \pm$  0.05 (standard deviation) and the mean $\lambda$ value as 0.00178 $ \pm$  0.0002 (standard deviation).
-
-The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model~\cite{ reynolds2012truncated, rhee2011levy}, which has also been identified in many human mobility studies using different mobility data~\cite{zhao2015explaining}.
-The similarities among the cumulative distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which indicates the collected geo-located tweets in one month can potentially reveal similar findings as the ones collected in multiple months.
-In addition, the two-tier power law also reveals the diversity in the Twitter user visiting behaviors: (1) a small group Twitter users visited significantly more locations than the others (2) within each group, the probability of Twitter user visiting more locations decreases significantly with a power function.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=1.0\linewidth]{./figures/visitation}
-\caption{Two-tier power law distribution of the collective Twitter user visitation behaviors.}
-\label{fig:visitation}
-\end{figure}
-\FloatBarrier
-
-As it is aforementioned, the measurements of displacements and radius of gyrations of individuals are two popular metrics to quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
-In this case, we first gathered the displacements from all the collected Twitter users in the continuous United States in the year 2014, where those Twitter users with only one geo-located tweet were filtered out.
-To investigate the mobility patterns of individuals, we also derived the accumulated displacements and the radius of gyrations of each individual Twitter user based on the corresponding space-time trajectories over the one year period.
-Note that both displacements and radius of gyrations were calculated by the direct great-circle distance ($d$) between two consecutively recorded locations in a user's trajectory.
-
-To seek mobility patterns from these measurements, we performed statistical analysis regarding the probability distributions of displacements and radius of gyrations, which is also known as the spatial dispersal kernel $P(d)$~\cite{brockmann2006scaling}.
-The probability distribution of the user displacements (as well as accumulated displacements) is shown in Figure~\ref{fig:displacement}, whereas the probability distribution of radius of gyrations is shown in Figure~\ref{fig:gyration}.
-In this study, we used the fitting methods developed by~\cite{Jurdak2015}.
-The probability distributions of overall displacements, and the accumulated displacements and radius of gyrations of individuals, can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.
-
-Figure~\ref{fig:displacement}a shows the probability distribution of the overall displacements, which is approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10~m$ from [10 m, 70 m] (accounting for 2 $\%$ of the population), $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min}=100~m$ from [100 m, 80 km] (accounting for 93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 80 km] (accounting for 5 $\%$ of the population).
-In addition, the displacement in the distance bound from 100 m and 80 km in Figure~\ref{fig:displacement}b can be further approximately by two power-law distributions with a cutting point at 5 km (53$\%$ distances are less than 5 km and 40$\%$ distances between 5 km and 80 km), which indicates two different travel modes, such as inter- or intra-city movements.
-Overall, the fitting functions with different distance bounds suggest the existence of multi-scale or multi-modal mobility patterns~\cite{Jurdak2015} of the Twitter users in the continuous United States, for example, the displacements larger than 80 km could be related to inter-state travels and stronger distance decay effects are observed in longer distance travels.
-
-The probability distribution of radius of gyrations of individuals at the national level (Figure~\ref{fig:gyration}a) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10~m$ from [10 m, 50 m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50 m, 30 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30 km].
-In particular, the radius of gyration between 50 m and 30 km can be further approximately by two power law distributions with a cutting point at 6 km (Figure~\ref{fig:gyration}b), which suggest two main types of spatial coverage of from the collected Twitter users in the continuous United States.
-The distribution shows that around $10\%$ the tweet population has a radius of gyration less than 50 meters, which indicates those twitter users mostly tweet at a particular place, such as home or office;  around 60$\%$ of the population has a radius of gyration less than 30 km, which indicates that most of the collected Twitter user movements are ``short'' distances, e.g., within a city locale.
-Note that the accuracy of these values for defining the distance bound depends on the accuracy of the location information of each geo-located tweet.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=1.0\linewidth]{./figures/displacement}
-\caption{({\bf a}) The probability distribution of the collective Twitter user displacements P(d); ({\bf b}) the distance between [100 m, 80 km] is approximated by a double power-law functions; ({\bf c}) The probability distribution of the accumulated displacements of individual Twitter users P(d); ({\bf d}) The probability distribution of the accumulated displacements of individual Twitter users in 3 different months.}
-
-\label{fig:displacement}
-\end{figure}
-\FloatBarrier
-
-We also measured the distribution of the radius of gyration of Twitter users at different spatial scales, specifically, the state and city level.
-In this study, we selected the state Illinois and California for comparisons at the state level (Figure~\ref{fig:gyration}c), whereas we chose Chicago city as an example (Figure~\ref{fig:gyration}d) at the city level.
-Interestingly but not surprisingly, the P($r_{g}$) at the state level can also be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.
-We noticed that distance bound of the radius of gyration at the state level is at 10 km instead of 30 km at the national level.
-The distance decay effects in larger spatial coverage [$>$ 30 km] slightly differ, in this case, the P($r_{g}$) decreases faster in smaller size state (i.e., Illinois) than the large size state (i.e., California).
-In particular, the P($r_{g}$) over Chicago city can be fitted by similar functions.
-However, as it reflects intra-city level mobility patterns, there is no distinct distance range to indicate large spatial coverage.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=1.0\linewidth]{./figures/gyration2}
-\caption{ ({\bf a}) The probability distribution of radius of gyration of individual Twitter users P($r_{g}$) at the national level; ({\bf b}) the distance between [50 m, 30 km] is approximated by a double power-law functions; ({\bf c}) P($r_{g}$) at the state level (Illinois and California); ({\bf d}) P($r_{g}$) for Chicago city.}
-\label{fig:gyration}
-\end{figure}
-\FloatBarrier
-
-On the other hand, as our framework can aggregate Twitter user trajectories within different temporal ranges, we further analyzed the probability distributions of accumulated displacements took places in January, June, and October (Figure~\ref{fig:displacement}d) and radius of gyrations within 4 quarters in the year 2014 (Figure~\ref{fig:gyration_season}, in order to examine whether there are temporal changes in the mobility patterns.
-While the probability distributions of accumulated displacements are almost identical in those selected three months,  we do find changes in the probability distributions of radius of gyrations in different quarters of the year.
-The fluctuations in the tails of the distributions indicate that long distance radius of gyrations (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern, which means the increase or decrease of long distance movement activities in the corresponding time period.
-However, it is worthy noting that the overall trends in the Twitter user mobility patterns revealed by radius of gyrations are still consistent.
-
-In summary, by comparing these results from different spatial scales and temporal ranges, different distance bounds were identified for describing the spatiotemporal Twitter user mobility patterns.
-However, the overall similarity and consistence found, in using a combination of three functions to approximate the probability distribution functions of displacements and radius of gyrations, clearly provide supports for using geo-located tweets as useful proxies for understanding human mobility patterns and conducting reproducible findings at multiple spatial scales and temporal ranges.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=1.0\linewidth]{./figures/gyration_season}
-\caption{The probability distribution of radius of gyration of individual Twitter users in different quarters of the year 2014.}
-\label{fig:gyration_season}
-\end{figure}
-\FloatBarrier
-
-The above analysis of Twitter user mobility patterns mainly focuses on the spatiotemporal aspects.
-Our framework provides the flexibility to aggregate and extract Twitter user trajectories in a specific spatial scale and re-produce the analysis.
-In particular, as it is evident from the above analysis that there are multi-scale or multi-modal Twitter user mobility patterns, this framework can help further look into the mobility pattern regarding how Twitter users move across different spatial scales and temporal ranges, which is measured by the movement flows between these spatial units.
-The movement flows are obtained by aggregating the movements that started from and ended in the corresponding spatial units within the giving time frame.
-In this case, we demonstrate the inter-state mobility patterns by using the framework to capture the movement flows between the states.
-Note that the movement flows can be summarized across all the 10 spatial layers in the framework.
-We tested the overall distribution of the movement flows (in the form of weighted in-degree and out-degree of a graph, where each state is treated as a node) among different states in the year 2014.
-We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states (Figure~\ref{fig:state_flow}).
-It indicates that the Twitter population is not proportional to account the movement flux between the states, which may provide some insights for other researchers in studying social-economical aspects of the migration dynamics.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.8\linewidth]{./figures/degree}
-\caption{The distribution of Twitter user movement flows among different states in the year 2014 measured in weighted in- and out-degrees.}
-\label{fig:state_flow}
-\end{figure}
-\FloatBarrier
-
-\subsection{The Interactive 3D Virtual Globe Web Mapping Interface}
-In addition to providing supports for understanding Twitter user mobility patterns with statistical analysis, the framework integrates a 3D virtual globe interface to enable users to perform exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements (http://sandbox.cigi.illinois.edu/home).
-The 3D virtual globe is developed and extended from the Cesium library (http://cesiumjs.org), which is an open-source WebGL virtual globe and map engine.
-We customized the map engine to adapt different spatial scales, which correspond to the hierarchical spatial layers, for aggregating movements in different levels-of-detail.
-The map interface interprets user's interactions, such as area-of-interest, time window, and zoom levels, etc.
-as parameters and send to the dedicated visualization servlet on the CyberGIS Gateway, which is the leading online cyberGIS environment for a large number of users to perform computing- and data-intensive, and collaborative geospatial problem-solving enabled by advanced cyberinfrastructure~\cite{liu2014cybergis}.
-
-An overview of the 3D web mapping interface is shown in Figure~\ref{fig:Web_Interface}.
-The mapping interface visualizes the corresponding movement flows on the virtual globe, where the number of movement flows are divided by 20 percentiles and categorized by the colors shown in the legend.
-In terms of performing exploratory visual-analytics of Twitter user movement patterns, users can specify the time window to enable the query. 
-When the results are shown, users can hover the mouse over each individual lines on the map to see the value of movement flows for both in and out directions (highlighted in color green).
-If the selected criteria keep unchanged, whenever the user zooms in/out, tilt or rotate the globe, the 3D virtual globe mapping interface will automatically provide the corresponding level-of-details on the fly.
-For example, Figure~\ref{fig:chicago} and Figure~\ref{fig:Chicago_airport} demonstrated the movement flows in different level-of-details around the Chicago city, and between O'Hare International Airport and the city center of Chicago city, where top 20$\%$ movement flows were shown.
-The 3D mapping interface facilitates uses to query multi-scale Twitter user movements with a geographical context and in an interactive fashion.
-For example, users can perform comparative studies of Twitter user movements in different cities by simply rotating the globe. 
-More importantly, this mapping interface can be easily customized and extended to accommodate future geo-located Twitter data collection with larger spatial coverages.
-The source code of the visual-analytics framework in this paper is available upon request.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.8\linewidth]{./figures/all}
-\caption{An overview of the 3D interactive web mapping interface.}
-\label{fig:Web_Interface}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.8\linewidth]{./figures/Chicago}
-\caption{The top 20$\%$ movement flows around Chicago city.}
-\label{fig:chicago}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.8\linewidth]{./figures/Chicago_airport}
-\caption{The top 20$\%$ movement flows between O'Hare International Airport and the city center of Chicago city.}
-\label{fig:Chicago_airport}
-\end{figure}
-\FloatBarrier
-
-\section{Conclusions}
-In this study, we have used large volume of geo-located tweets to study Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States during the year 2014.
-To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-scale spatiotemporal Twitter user mobility patterns.
-This framework is implemented on high-performance distributed computing environment using Apache Hadoop.
-It provides efficiency in filtering large volume of geo-located tweets, modeling and generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
-For example, we have included an experiment for illustrating the processing time regarding generating Twitter user trajectories across different time span in the supplementary material.
-
-With this framework, we have found some interesting Twitter user mobility patterns, both statistically and visually.
-We studied the collective Twitter user visiting behavior regarding the frequency of Twitter users visiting different locations, which was fitted by a two-tier power-law distribution function.
-The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model, which has also been identified in many human mobility studies using different mobility data.
-The similarities among the cumulative distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which provides supports that we are not just capturing a random snapshot of the whole data stream.
-
-We studied the distance decay effects in the collective Twitter user movements measured by the probability distributions of the displacements and radius of gyrations of individuals. 
-These distributions can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.
-In particular, distance bounds between different fitting functions in displacement distribution reveals the existence of multi-scale or multi-modal mobility patterns of the Twitter users, whereas the distribution of radius of gyration reveals different groups of Twitter users with different types of spatial coverages at multiple spatial scales.
-We further studied these mobility patterns in different temporal ranges to investigate the temporal changes in the mobility patterns. 
-We found that the accumulated displacements are almost identical in different months, while the long distance radius of gyration (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern.
-
-It is worth noting that at the current stage the geo-located Twitter data is not able to generalize to the entire population.
-As the demographic information of Twitter users cannot be easily identified, the results derived in this study may not reflect a complete real-world image of human movements, which should be carefully considered in future studies.
-Nevertheless, the Twitter user movements provide clear supports for revealing the distance decay effects in human mobility research, which is observed in multiple spatial and temporal scales.
-Due to the large sample size, it is difficult to generalize the mobility pattern found at national level to the entire population, city-level mobility pattern may provide better insights for investigating mobility dynamics.
-For example, the results of radius of gyration in Chicago exhibit similar pattern found in larger spatial scale, and with inputs of other mobility dataset that are often available at city-level, such as taxi trip records and mobile phone call data, there is a potential to synthesize these different sources of information and therefore provide a more complete image for understanding human mobility patterns.
-On the other hand, as we have discussed in this paper that geo-located tweets show advantages in terms of easy data accessibility, large spatial coverage and massive sample size, our approach took advantage of such data source to understand the mobility patterns across multiple spatial scales and temporal ranges.
-Also, our approach can be applied to the setting of other countries, which can be used to carry out comparative studies regarding spatiotemporal Twitter user mobility patterns.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%\supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{
-The authors would like to thank the four anonymous reviewers of IJGI for their constructive comments that better shaped the paper.
-Junjun Yin would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
-Zhenhong Du would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.
-The work also used the ROGER supercomputer, which is supported by NSF under grant number: 1429699.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Junjun Yin conceived and designed the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin and Zhenhong Du wrote the paper.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictofinterests{The authors declare no conflict of interest.
-The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\renewcommand\bibname{References}
-\begin{thebibliography}{-------}
-\providecommand{\natexlab}[1]{#1}
-
-\bibitem[Zheng \em{et~al.}(2008)Zheng, Li, Chen, Xie, and
-  Ma]{zheng2008understanding}
-Zheng, Y.; Li, Q.; Chen, Y.; Xie, X.; Ma, W.Y.
+\begin{thebibliography}{00}
+\bibitem{zheng2008understanding}
+Zheng, Y., Li, Q., Chen, Y., Xie, X., Ma, W.Y., 2008
 \newblock Understanding mobility based on GPS data.
 \newblock  Proceedings of the 10th international conference on Ubiquitous
-  computing. ACM,  2008, pp. 312--321.
+  computing. ACM, pp. 312--321.
 
-\bibitem[Jiang \em{et~al.}(2009)Jiang, Yin, and Zhao]{jiang2009characterizing}
-Jiang, B.; Yin, J.; Zhao, S.
+\bibitem{jiang2009characterizing}
+Jiang, B., Yin, J., Zhao, S., 2009
 \newblock Characterizing the human mobility pattern in a large street network.
-\newblock {\em Physical Review E} {\bf 2009}, {\em 80},~021136.
+\newblock {\em Physical Review E}, {\em 80},~021136.
 
-\bibitem[Belik \em{et~al.}(2011)Belik, Geisel, and Brockmann]{belik2011natural}
-Belik, V.; Geisel, T.; Brockmann, D.
+\bibitem{belik2011natural}
+Belik, V., Geisel, T., Brockmann, D.
 \newblock Natural human mobility patterns and spatial spread of infectious
@@
 
-\bibitem[Greenwood(1985)]{greenwood1985human}
+\bibitem{greenwood1985human}
 Greenwood, M.J.
@@
 
-\bibitem[Brockmann \em{et~al.}(2006)Brockmann, Hufnagel, and
-  Geisel]{brockmann2006scaling}
-Brockmann, D.; Hufnagel, L.; Geisel, T.
+\bibitem{brockmann2006scaling}
+Brockmann, D., Hufnagel, L., Geisel, T.
 \newblock The scaling laws of human travel.
@@
 
-\bibitem[Gonzalez \em{et~al.}(2008)Gonzalez, Hidalgo, and
-  Barabasi]{gonzalez2008understanding}
-Gonzalez, M.C.; Hidalgo, C.A.; Barabasi, A.L.
+\bibitem{gonzalez2008understanding}
+Gonzalez, M.C., Hidalgo, C.A., Barabasi, A.L.
 \newblock Understanding individual human mobility patterns.
@@
 
-\bibitem[Jurdak \em{et~al.}(2015)Jurdak, Zhao, Liu, AbouJaoude, Cameron, and
-  Newth]{Jurdak2015}
-Jurdak, R.; Zhao, K.; Liu, J.; AbouJaoude, M.; Cameron, M.; Newth, D.
+\bibitem{Jurdak2015}
+Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D.
 \newblock Understanding Human Mobility from Twitter.
@@
 
-\bibitem[Rhee \em{et~al.}(2011)Rhee, Shin, Hong, Lee, Kim, and
-  Chong]{rhee2011levy}
-Rhee, I.; Shin, M.; Hong, S.; Lee, K.; Kim, S.J.; Chong, S.
+\bibitem{rhee2011levy}
+Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S.J., Chong, S.
 \newblock On the levy-walk nature of human mobility.
@@
 
-\bibitem[Sevtsuk and Ratti(2010)]{sevtsuk2010does}
-Sevtsuk, A.; Ratti, C.
+\bibitem{sevtsuk2010does}
+Sevtsuk, A., Ratti, C.
 \newblock Does urban mobility have a daily routine? Learning from the aggregate
@@
 
-\bibitem[Kung \em{et~al.}(2014)Kung, Greco, Sobolevsky, and
-  Ratti]{kung2014exploring}
-Kung, K.S.; Greco, K.; Sobolevsky, S.; Ratti, C.
+\bibitem{kung2014exploring}
+Kung, K.S., Greco, K., Sobolevsky, S., Ratti, C.
 \newblock Exploring universal patterns in human home-work commuting from mobile
@@
 
-\bibitem[Thatcher(2014)]{thatcher2014living}
+\bibitem{thatcher2014living}
 Thatcher, J.
@@
 
-\bibitem[Hawelka \em{et~al.}(2014)Hawelka, Sitko, Beinat, Sobolevsky,
-  Kazakopoulos, and Ratti]{hawelka2014geo}
-Hawelka, B.; Sitko, I.; Beinat, E.; Sobolevsky, S.; Kazakopoulos, P.; Ratti, C.
+\bibitem{hawelka2014geo}
+Hawelka, B., Sitko, I., Beinat, E., Sobolevsky, S., Kazakopoulos, P., Ratti, C.
 \newblock Geo-located Twitter as proxy for global mobility patterns.
@@
 
-\bibitem[Giannotti and Pedreschi(2008)]{giannotti2008mobility}
-Giannotti, F.; Pedreschi, D.
+\bibitem{giannotti2008mobility}
+Giannotti, F., Pedreschi, D.
 \newblock {\em Mobility, data mining and privacy: Geographic knowledge
-  discovery}; Springer Science \& Business Media,  2008.
+  discovery}, Springer Science \& Business Media,  2008.
 
-\bibitem[Crampton(2014)]{crampton2014collect}
+\bibitem{crampton2014collect}
 Crampton, J.W.
@@
 
-\bibitem[Wu \em{et~al.}(2014)Wu, Zhi, Sui, and Liu]{wu2014intra}
-Wu, L.; Zhi, Y.; Sui, Z.; Liu, Y.
+\bibitem{wu2014intra}
+Wu, L., Zhi, Y., Sui, Z., Liu, Y.
 \newblock Intra-urban human mobility and activity transition: Evidence from
@@
 
-\bibitem[Hasan \em{et~al.}(2013)Hasan, Zhan, and
-  Ukkusuri]{hasan2013understanding}
-Hasan, S.; Zhan, X.; Ukkusuri, S.V.
+\bibitem{hasan2013understanding}
+Hasan, S., Zhan, X., Ukkusuri, S.V.
 \newblock Understanding urban human activity and mobility patterns using
@@
 
-\bibitem[Cho \em{et~al.}(2011)Cho, Myers, and Leskovec]{cho2011friendship}
-Cho, E.; Myers, S.A.; Leskovec, J.
+\bibitem{cho2011friendship}
+Cho, E., Myers, S.A., Leskovec, J.
 \newblock Friendship and mobility: user movement in location-based social
@@
 
-\bibitem[Noulas \em{et~al.}(2012)Noulas, Scellato, Lambiotte, Pontil, and
-  Mascolo]{noulas2012tale}
-Noulas, A.; Scellato, S.; Lambiotte, R.; Pontil, M.; Mascolo, C.
+\bibitem{noulas2012tale}
+Noulas, A., Scellato, S., Lambiotte, R., Pontil, M., Mascolo, C.
 \newblock A tale of many cities: universal patterns in human urban mobility.
@@
 
-\bibitem[Balcan \em{et~al.}(2009)Balcan, Colizza, Gon{\c{c}}alves, Hu, Ramasco,
-  and Vespignani]{balcan2009multiscale}
-Balcan, D.; Colizza, V.; Gon{\c{c}}alves, B.; Hu, H.; Ramasco, J.J.;
+\bibitem{balcan2009multiscale}
+Balcan, D., Colizza, V., Gon{\c{c}}alves, B., Hu, H., Ramasco, J.J.,
   Vespignani, A.
@@
 
-\bibitem[Tamerius \em{et~al.}(2011)Tamerius, Nelson, Zhou, Viboud, Miller, and
-  Alonso]{tamerius2011global}
-Tamerius, J.; Nelson, M.I.; Zhou, S.Z.; Viboud, C.; Miller, M.A.; Alonso, W.J.
+\bibitem{tamerius2011global}
+Tamerius, J., Nelson, M.I., Zhou, S.Z., Viboud, C., Miller, M.A., Alonso, W.J.
 \newblock Global influenza seasonality: reconciling patterns across temperate
@@
 
-\bibitem[Tsou(2015)]{tsou2015}
+\bibitem{tsou2015}
 Tsou, M.H.
@@
 
-\bibitem[Zheng \em{et~al.}(2010)Zheng, Xie, and Ma]{zheng2010geolife}
-Zheng, Y.; Xie, X.; Ma, W.Y.
+\bibitem{zheng2010geolife}
+Zheng, Y., Xie, X., Ma, W.Y.
 \newblock GeoLife: A Collaborative Social Networking Service among User,
@@
 
-\bibitem[Becker \em{et~al.}(2013)Becker, C{\'a}ceres, Hanson, Isaacman, Loh,
-  Martonosi, Rowland, Urbanek, Varshavsky, and Volinsky]{becker2013human}
-Becker, R.; C{\'a}ceres, R.; Hanson, K.; Isaacman, S.; Loh, J.M.; Martonosi,
-  M.; Rowland, J.; Urbanek, S.; Varshavsky, A.; Volinsky, C.
+\bibitem{becker2013human}
+Becker, R., C{\'a}ceres, R., Hanson, K., Isaacman, S., Loh, J.M., Martonosi,
+  M., Rowland, J., Urbanek, S., Varshavsky, A., Volinsky, C.
 \newblock Human mobility characterization from cellular network data.
@@
 
-\bibitem[Sobolevsky \em{et~al.}(2013)Sobolevsky, Szell, Campari, Couronn{\'e},
-  Smoreda, and Ratti]{sobolevsky2013delineating}
-Sobolevsky, S.; Szell, M.; Campari, R.; Couronn{\'e}, T.; Smoreda, Z.; Ratti,
+\bibitem{sobolevsky2013delineating}
+Sobolevsky, S., Szell, M., Campari, R., Couronn{\'e}, T., Smoreda, Z., Ratti,
   C.
@@
 
-\bibitem[Twitter(2016)]{twitterAPI}
+\bibitem{twitterAPI}
 Twitter.
@@
 
-\bibitem[Cranshaw \em{et~al.}(2012)Cranshaw, Schwartz, Hong, and
-  Sadeh]{cranshaw2012livehoods}
-Cranshaw, J.; Schwartz, R.; Hong, J.I.; Sadeh, N.M.
+\bibitem{cranshaw2012livehoods}
+Cranshaw, J., Schwartz, R., Hong, J.I., Sadeh, N.M.
 \newblock The Livehoods Project: Utilizing Social Media to Understand the
@@
 
-\bibitem[Mitchell \em{et~al.}(2013)Mitchell, Frank, Harris, Dodds, and
-  Danforth]{mitchell2013geography}
-Mitchell, L.; Frank, M.R.; Harris, K.D.; Dodds, P.S.; Danforth, C.M.
+\bibitem{mitchell2013geography}
+Mitchell, L., Frank, M.R., Harris, K.D., Dodds, P.S., Danforth, C.M.
 \newblock The geography of happiness: Connecting twitter sentiment and
@@
 
-\bibitem[Longley \em{et~al.}(2015)Longley, Adnan, Lansley,
-  et~al.]{longley2015geotemporal}
-Longley, P.A.; Adnan, M.; Lansley, G.; others.
+\bibitem{longley2015geotemporal}
+Longley, P.A., Adnan, M., Lansley, G., others.
 \newblock The geotemporal demographics of Twitter usage.
@@
 
-\bibitem[H{\"a}gerstrand \em{et~al.}(1985)H{\"a}gerstrand
-  et~al.]{hagerstrand1985time}
-H{\"a}gerstrand, T.; others.
+\bibitem{hagerstrand1985time}
+H{\"a}gerstrand, T., others.
 \newblock Time-geography: focus on the corporeality of man, society, and
@@
 
-\bibitem[Kwan and Lee(2004)]{kwan2004geovisualization}
-Kwan, M.P.; Lee, J.
+\bibitem{kwan2004geovisualization}
+Kwan, M.P., Lee, J.
 \newblock Geovisualization of human activity patterns using 3D GIS: a
@@
 
-\bibitem[Andrienko and Andrienko(2007)]{andrienko2007designing}
-Andrienko, N.; Andrienko, G.
+\bibitem{andrienko2007designing}
+Andrienko, N., Andrienko, G.
 \newblock Designing visual analytics methods for massive collections of
@@
 
-\bibitem[MacEachren and Kraak(2001)]{maceachren2001research}
-MacEachren, A.M.; Kraak, M.J.
+\bibitem{maceachren2001research}
+MacEachren, A.M., Kraak, M.J.
 \newblock Research challenges in geovisualization.
@@
 
-\bibitem[MacEachren(2004)]{maceachren2004maps}
+\bibitem{maceachren2004maps}
 MacEachren, A.M.
-\newblock {\em How maps work: representation, visualization, and design};
+\newblock {\em How maps work: representation, visualization, and design},
   Guilford Press,  2004.
 
-\bibitem[Andrienko \em{et~al.}(2007)Andrienko, Andrienko, and
-  Wrobel]{andrienko2007visual}
-Andrienko, G.; Andrienko, N.; Wrobel, S.
+\bibitem{andrienko2007visual}
+Andrienko, G., Andrienko, N., Wrobel, S.
 \newblock Visual analytics tools for analysis of movement data.
@@
 
-\bibitem[Cao \em{et~al.}(2015)Cao, Wang, Hwang, Padmanabhan, Zhang, and
-  Soltani]{cao2014scalable}
-Cao, G.; Wang, S.; Hwang, M.; Padmanabhan, A.; Zhang, Z.; Soltani, K.
-\newblock A scalable framework for spatiotemporal analysis of location-based
-  social media data.
-\newblock {\em Computers, Environment and Urban Systems} {\bf 2015}, {\em
-  51},~70--82.
-
-\bibitem[Padmanabhan \em{et~al.}(2014)Padmanabhan, Wang, Cao, Hwang, Zhang,
-  Gao, Soltani, and Liu]{padmanabhan2014flumapper}
-Padmanabhan, A.; Wang, S.; Cao, G.; Hwang, M.; Zhang, Z.; Gao, Y.; Soltani, K.;
-  Liu, Y.
-\newblock FluMapper: A cyberGIS application for interactive analysis of massive
-  location-based social media.
-\newblock {\em Concurrency and Computation: Practice and Experience} {\bf
-  2014}.
-
-\bibitem[Black \em{et~al.}(2012)Black, Mascaro, Gallagher, and
-  Goggins]{black2012twitter}
-Black, A.; Mascaro, C.; Gallagher, M.; Goggins, S.P.
+\bibitem{black2012twitter}
+Black, A., Mascaro, C., Gallagher, M., Goggins, S.P.
 \newblock Twitter zombie: Architecture for capturing, socially transforming and
@@
 
-\bibitem[Shvachko \em{et~al.}(2010)Shvachko, Kuang, Radia, and
-  Chansler]{shvachko2010hadoop}
-Shvachko, K.; Kuang, H.; Radia, S.; Chansler, R.
+\bibitem{shvachko2010hadoop}
+Shvachko, K., Kuang, H., Radia, S., Chansler, R.
 \newblock The hadoop distributed file system.
@@
 
-\bibitem[Dean and Ghemawat(2008)]{dean2008mapreduce}
-Dean, J.; Ghemawat, S.
+\bibitem{dean2008mapreduce}
+Dean, J., Ghemawat, S.
 \newblock MapReduce: simplified data processing on large clusters.
@@
 
-\bibitem[Gao \em{et~al.}(2012)Gao, Tang, and Liu]{gao2012exploring}
-Gao, H.; Tang, J.; Liu, H.
+\bibitem{gao2012exploring}
+Gao, H., Tang, J., Liu, H.
 \newblock Exploring Social-Historical Ties on Location-Based Social Networks.
@@
 
-\bibitem[Buttenfield and McMaster(1991)]{buttenfield1991map}
-Buttenfield, B.P.; McMaster, R.B.
-\newblock {\em Map Generalization: Making rules for knowledge representation};
+\bibitem{buttenfield1991map}
+Buttenfield, B.P., McMaster, R.B.
+\newblock {\em Map Generalization: Making rules for knowledge representation},
   Longman Scientific \& Technical New York,  1991.
 
-\bibitem[Samet(1984)]{samet1984quadtree}
+\bibitem{samet1984quadtree}
 Samet, H.
@@
 
-\bibitem[Clauset \em{et~al.}(2009)Clauset, Shalizi, and
-  Newman]{clauset2009power}
-Clauset, A.; Shalizi, C.R.; Newman, M.E.
+\bibitem{clauset2009power}
+Clauset, A., Shalizi, C.R., Newman, M.E.
 \newblock Power-law distributions in empirical data.
@@
 
-\bibitem[Reynolds(2012)]{reynolds2012truncated}
+\bibitem{reynolds2012truncated}
 Reynolds, A.
@@
 
-\bibitem[Zhao \em{et~al.}(2015)Zhao, Musolesi, Hui, Rao, and
-  Tarkoma]{zhao2015explaining}
-Zhao, K.; Musolesi, M.; Hui, P.; Rao, W.; Tarkoma, S.
+\bibitem{zhao2015explaining}
+Zhao, K., Musolesi, M., Hui, P., Rao, W., Tarkoma, S.
 \newblock Explaining the power-law distribution of human mobility through
@@
 
-\bibitem[Liu \em{et~al.}(2014)Liu, Padmanabhan, and Wang]{liu2014cybergis}
-Liu, Y.; Padmanabhan, A.; Wang, S.
-\newblock CyberGIS Gateway for enabling data-rich geospatial research and
-  education.
-\newblock {\em Concurrency and Computation: Practice and Experience} {\bf
-  2014}.
+\end{thebibliography}
 
-\end{thebibliography}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{document}

### 2016-10-19 Multi-scale_Mobility_Pattern_CEUS/template-num.tex
init ref

@@
 
-\title{}
+\title{Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns}
 
@@
 \bibitem{zheng2008understanding}
-Zheng, Y., Li, Q., Chen, Y., Xie, X., Ma, W.Y., 2008
-\newblock Understanding mobility based on GPS data.
-\newblock  Proceedings of the 10th international conference on Ubiquitous
-  computing. ACM, pp. 312--321.
+Zheng, Y., Li, Q., Chen, Y., Xie, X., Ma, W.Y., 2008. Understanding mobility based on GPS data. Proceedings of the 10th international conference on Ubiquitous computing. ACM, pp. 312--321.
 
 \bibitem{jiang2009characterizing}
-Jiang, B., Yin, J., Zhao, S., 2009
-\newblock Characterizing the human mobility pattern in a large street network.
-\newblock {\em Physical Review E}, {\em 80},~021136.
+Jiang, B., Yin, J., Zhao, S., 2009. Characterizing the human mobility pattern in a large street network. {\em Physical Review E}, {\em 80},~021136.
 
 \bibitem{belik2011natural}
-Belik, V., Geisel, T., Brockmann, D.
-\newblock Natural human mobility patterns and spatial spread of infectious
-  diseases.
-\newblock {\em Physical Review X} {\bf 2011}, {\em 1},~011001.
+Belik, V., Geisel, T., Brockmann, D., 2011. Natural human mobility patterns and spatial spread of infectious diseases. {\em Physical Review X}, {\em 1},~011001.
 
 \bibitem{greenwood1985human}
-Greenwood, M.J.
-\newblock Human migration: Theory, models, and empirical studies.
-\newblock {\em Journal of regional Science} {\bf 1985}, {\em 25},~521--544.
+Greenwood, M.J., 1985. Human migration: Theory, models, and empirical studies. {\em Journal of regional Science}, {\em 25}, pp. 521--544.
 
 \bibitem{brockmann2006scaling}
-Brockmann, D., Hufnagel, L., Geisel, T.
-\newblock The scaling laws of human travel.
-\newblock {\em Nature} {\bf 2006}, {\em 439},~462--465.
+Brockmann, D., Hufnagel, L., Geisel, T., 2006. The scaling laws of human travel. {\em Nature}, {\em 439}, pp. 462--465.
 
 \bibitem{gonzalez2008understanding}
-Gonzalez, M.C., Hidalgo, C.A., Barabasi, A.L.
-\newblock Understanding individual human mobility patterns.
-\newblock {\em Nature} {\bf 2008}, {\em 453},~779--782.
+Gonzalez, M.C., Hidalgo, C.A., Barabasi, A.L., 2008. Understanding individual human mobility patterns. {\em Nature}, {\em 453}, pp. 779--782.
 
 \bibitem{Jurdak2015}
-Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D.
-\newblock Understanding Human Mobility from Twitter.
-\newblock {\em PLoS ONE} {\bf 2015}, {\em 10},~e0131469.
+Jurdak, R., Zhao, K., Liu, J., AbouJaoude, M., Cameron, M., Newth, D., 2015. Understanding Human Mobility from Twitter. {\em PLoS ONE}, {\em 10},~e0131469.
 
 \bibitem{rhee2011levy}
-Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S.J., Chong, S.
-\newblock On the levy-walk nature of human mobility.
-\newblock {\em IEEE/ACM transactions on networking (TON)} {\bf 2011}, {\em
-  19},~630--643.
+Rhee, I., Shin, M., Hong, S., Lee, K., Kim, S.J., Chong, S., 2011. On the levy-walk nature of human mobility. {\em IEEE/ACM transactions on networking (TON)}, {\em 19}, pp. 630--643.
 
 \bibitem{sevtsuk2010does}
-Sevtsuk, A., Ratti, C.
-\newblock Does urban mobility have a daily routine? Learning from the aggregate
-  data of mobile networks.
-\newblock {\em Journal of Urban Technology} {\bf 2010}, {\em 17},~41--60.
+Sevtsuk, A., Ratti, C., 2010. Does urban mobility have a daily routine? Learning from the aggregate data of mobile networks. {\em Journal of Urban Technology}, {\em 17}, pp. 41--60.
 
 \bibitem{kung2014exploring}
-Kung, K.S., Greco, K., Sobolevsky, S., Ratti, C.
-\newblock Exploring universal patterns in human home-work commuting from mobile
-  phone data.
-\newblock {\em PloS one} {\bf 2014}, {\em 9},~e96180.
+Kung, K.S., Greco, K., Sobolevsky, S., Ratti, C. 2014. Exploring universal patterns in human home-work commuting from mobile phone data. {\em PLoS ONE}, {\em 9},~e96180.
 
 \bibitem{thatcher2014living}
-Thatcher, J.
-\newblock Living on fumes: Digital footprints, data fumes, and the limitations
-  of spatial big data.
-\newblock {\em International Journal of Communication} {\bf 2014}, {\em
-  8},~1765--1783.
+Thatcher, J., 2014. Living on fumes: Digital footprints, data fumes, and the limitations of spatial big data. {\em International Journal of Communication}, {\em 8}, pp. 1765--1783.
 
 \bibitem{hawelka2014geo}
-Hawelka, B., Sitko, I., Beinat, E., Sobolevsky, S., Kazakopoulos, P., Ratti, C.
-\newblock Geo-located Twitter as proxy for global mobility patterns.
-\newblock {\em Cartography and Geographic Information Science} {\bf 2014}, {\em
-  41},~260--271.
+Hawelka, B., Sitko, I., Beinat, E., Sobolevsky, S., Kazakopoulos, P., Ratti, C., 2014.
+Geo-located Twitter as proxy for global mobility patterns.{\em Cartography and Geographic Information Science}, {\em
+  41}, pp. 260--271.
 
 \bibitem{giannotti2008mobility}
-Giannotti, F., Pedreschi, D.
-\newblock {\em Mobility, data mining and privacy: Geographic knowledge
-  discovery}, Springer Science \& Business Media,  2008.
+Giannotti, F., Pedreschi, D., 2008.{\em Mobility, data mining and privacy: Geographic knowledge discovery}, Springer Science \& Business Media.
 
 \bibitem{crampton2014collect}
-Crampton, J.W.
-\newblock Collect it all: national security, Big Data and governance.
-\newblock {\em GeoJournal} {\bf 2014}, pp. 1--13.
+Crampton, J.W. 2014. Collect it all: national security, Big Data and governance. {\em GeoJournal}, pp. 1--13.
 
 \bibitem{wu2014intra}
-Wu, L., Zhi, Y., Sui, Z., Liu, Y.
-\newblock Intra-urban human mobility and activity transition: Evidence from
-  social media check-in data.
-\newblock {\em PloS one} {\bf 2014}, {\em 9},~e97010.
+Wu, L., Zhi, Y., Sui, Z., Liu, Y., 2014. Intra-urban human mobility and activity transition: Evidence from social media check-in data. {\em PLoS ONE}, {\em 9},~e97010.
 
 \bibitem{hasan2013understanding}
-Hasan, S., Zhan, X., Ukkusuri, S.V.
-\newblock Understanding urban human activity and mobility patterns using
-  large-scale location-based data from online social media.
-\newblock  Proceedings of the 2nd ACM SIGKDD international workshop on urban
-  computing. ACM,  2013, p.~6.
+Hasan, S., Zhan, X., Ukkusuri, S.V., 2013.
+Understanding urban human activity and mobility patterns using large-scale location-based data from online social media.
+Proceedings of the 2nd ACM SIGKDD international workshop on urban computing.
+ACM,  2013, p.~6.
 
@@
 Cho, E., Myers, S.A., Leskovec, J.
-\newblock Friendship and mobility: user movement in location-based social
-  networks.
-\newblock  Proceedings of the 17th ACM SIGKDD international conference on
-  Knowledge discovery and data mining. ACM,  2011, pp. 1082--1090.
+2011, Friendship and mobility: user movement in location-based social networks.
+Proceedings of the 17th ACM SIGKDD international conference on Knowledge discovery and data mining.
+ACM,  2011, pp.
+1082--1090.
 
 \bibitem{noulas2012tale}
-Noulas, A., Scellato, S., Lambiotte, R., Pontil, M., Mascolo, C.
-\newblock A tale of many cities: universal patterns in human urban mobility.
-\newblock {\em PloS one} {\bf 2012}, {\em 7},~e37027.
+Noulas, A., Scellato, S., Lambiotte, R., Pontil, M., Mascolo, C., 2012. A tale of many cities: universal patterns in human urban mobility. {\em PLoS ONE}, {\em 7},~e37027.
 
@@
 Balcan, D., Colizza, V., Gon{\c{c}}alves, B., Hu, H., Ramasco, J.J.,
-  Vespignani, A.
-\newblock Multiscale mobility networks and the spatial spreading of infectious
-  diseases.
-\newblock {\em Proceedings of the National Academy of Sciences} {\bf 2009},
-  {\em 106},~21484--21489.
+  Vespignani, A., 2009. Multiscale mobility networks and the spatial spreading of infectious diseases.{\em Proceedings of the National Academy of Sciences},{\em 106}, pp. 21484--21489.
 
 \bibitem{tamerius2011global}
-Tamerius, J., Nelson, M.I., Zhou, S.Z., Viboud, C., Miller, M.A., Alonso, W.J.
-\newblock Global influenza seasonality: reconciling patterns across temperate
-  and tropical regions.
-\newblock {\em Environmental health perspectives} {\bf 2011}, {\em 119},~439.
+Tamerius, J., Nelson, M.I., Zhou, S.Z., Viboud, C., Miller, M.A., Alonso, W.J., 2011.
+Global influenza seasonality: reconciling patterns across temperate and tropical regions.{\em Environmental health perspectives}, {\em 119},~439.
 
 \bibitem{tsou2015}
-Tsou, M.H.
-\newblock Research challenges and opportunities in mapping social media and Big
-  Data.
-\newblock {\em Cartography and Geographic Information Science} {\bf 2015}, {\em
-  42},~70--74.
+Tsou, M.H., 2015. Research challenges and opportunities in mapping social media and Big Data.{\em Cartography and Geographic Information Science} {\bf 2015}, {\em 42}, pp. 70--74.
 
 \bibitem{zheng2010geolife}
-Zheng, Y., Xie, X., Ma, W.Y.
-\newblock GeoLife: A Collaborative Social Networking Service among User,
-  Location and Trajectory. {\bf 2010}.
+Zheng, Y., Xie, X., Ma, W.Y., 2010. GeoLife: A Collaborative Social Networking Service among User, Location and Trajectory.
 
@@
 Becker, R., C{\'a}ceres, R., Hanson, K., Isaacman, S., Loh, J.M., Martonosi,
-  M., Rowland, J., Urbanek, S., Varshavsky, A., Volinsky, C.
-\newblock Human mobility characterization from cellular network data.
-\newblock {\em Communications of the ACM} {\bf 2013}, {\em 56},~74--82.
+  M., Rowland, J., Urbanek, S., Varshavsky, A., Volinsky, C., 2013. Human mobility characterization from cellular network data.{\em Communications of the ACM}, {\em 56}, pp. 74--82.
 
@@
 Sobolevsky, S., Szell, M., Campari, R., Couronn{\'e}, T., Smoreda, Z., Ratti,
-  C.
-\newblock Delineating geographical regions with networks of human interactions
-  in an extensive set of countries.
-\newblock {\em PLoS One} {\bf 2013}, {\em 8},~e81707.
+  C., 2013. Delineating geographical regions with networks of human interactions in an extensive set of countries.{\em PLoS ONE}, {\em 8},~e81707.
 
 \bibitem{twitterAPI}
-Twitter.
-\newblock Twitter streaming API.
-\newblock {\em available from: https://dev.twitter.com/streaming/overview} {\bf
-  2016}.
+Twitter, 2016. Twitter streaming API.{\em Available from: https://dev.twitter.com/streaming/overview}.
 
 \bibitem{cranshaw2012livehoods}
-Cranshaw, J., Schwartz, R., Hong, J.I., Sadeh, N.M.
-\newblock The Livehoods Project: Utilizing Social Media to Understand the
-  Dynamics of a City.
-\newblock  ICWSM,  2012.
+Cranshaw, J., Schwartz, R., Hong, J.I., Sadeh, N.M., 2012. The Livehoods Project: Utilizing Social Media to Understand the Dynamics of a City. ICWSM.
 
 \bibitem{mitchell2013geography}
-Mitchell, L., Frank, M.R., Harris, K.D., Dodds, P.S., Danforth, C.M.
-\newblock The geography of happiness: Connecting twitter sentiment and
-  expression, demographics, and objective characteristics of place {\bf 2013}.
+Mitchell, L., Frank, M.R., Harris, K.D., Dodds, P.S., Danforth, C.M., 2013.
+The geography of happiness: Connecting twitter sentiment and expression, demographics, and objective characteristics of place.
 
 \bibitem{longley2015geotemporal}
-Longley, P.A., Adnan, M., Lansley, G., others.
-\newblock The geotemporal demographics of Twitter usage.
-\newblock {\em Environment and Planning A} {\bf 2015}, {\em 47},~465--484.
+Longley, P.A., Adnan, M., Lansley, G., others., 2015. The geotemporal demographics of Twitter usage. {\em Environment and Planning A}, {\em 47}, pp. 465--484.
 
 \bibitem{hagerstrand1985time}
-H{\"a}gerstrand, T., others.
-\newblock Time-geography: focus on the corporeality of man, society, and
-  environment.
-\newblock {\em The science and praxis of complexity} {\bf 1985}, pp. 193--216.
+H{\"a}gerstrand, T., others., 1985. Time-geography: focus on the corporeality of man, society, and environment. {\em The science and praxis of complexity}, pp. 193--216.
 
 \bibitem{kwan2004geovisualization}
-Kwan, M.P., Lee, J.
-\newblock Geovisualization of human activity patterns using 3D GIS: a
-  time-geographic approach.
-\newblock {\em Spatially integrated social science} {\bf 2004}, {\em 27}.
+Kwan, M.P., Lee, J., 2004. Geovisualization of human activity patterns using 3D GIS: a time-geographic approach. {\em Spatially integrated social science}, {\em 27}.
 
 \bibitem{andrienko2007designing}
-Andrienko, N., Andrienko, G.
-\newblock Designing visual analytics methods for massive collections of
-  movement data.
-\newblock {\em Cartographica: The International Journal for Geographic
-  Information and Geovisualization} {\bf 2007}, {\em 42},~117--138.
+Andrienko, N., Andrienko, G., 2007.
+Designing visual analytics methods for massive collections of movement data.
+{\em Cartographica: The International Journal for Geographic Information and Geovisualization}, {\em 42}, pp.
+117--138.
 
 \bibitem{maceachren2001research}
-MacEachren, A.M., Kraak, M.J.
-\newblock Research challenges in geovisualization.
-\newblock {\em Cartography and Geographic Information Science} {\bf 2001}, {\em
-  28},~3--12.
+MacEachren, A.M., Kraak, M.J., 2001. Research challenges in geovisualization. {\em Cartography and Geographic Information Science}, {\em
+  28}, pp. 3--12.
 
 \bibitem{maceachren2004maps}
-MacEachren, A.M.
-\newblock {\em How maps work: representation, visualization, and design},
-  Guilford Press,  2004.
+MacEachren, A.M., 2004. {\em How maps work: representation, visualization, and design}, Guilford Press.
 
 \bibitem{andrienko2007visual}
-Andrienko, G., Andrienko, N., Wrobel, S.
-\newblock Visual analytics tools for analysis of movement data.
-\newblock {\em ACM SIGKDD Explorations Newsletter} {\bf 2007}, {\em 9},~38--46.
+Andrienko, G., Andrienko, N., Wrobel, S., 2007. Visual analytics tools for analysis of movement data. {\em ACM SIGKDD Explorations Newsletter}, {\em 9}, pp. 38--46.
 
 \bibitem{black2012twitter}
-Black, A., Mascaro, C., Gallagher, M., Goggins, S.P.
-\newblock Twitter zombie: Architecture for capturing, socially transforming and
-  analyzing the Twittersphere.
-\newblock  Proceedings of the 17th ACM international conference on Supporting
-  group work. ACM,  2012, pp. 229--238.
+Black, A., Mascaro, C., Gallagher, M., Goggins, S.P., 2012.
+Twitter zombie: Architecture for capturing, socially transforming and analyzing the Twittersphere.
+Proceedings of the 17th ACM international conference on Supporting group work.
+ACM, pp.
+229--238.
 
 \bibitem{shvachko2010hadoop}
-Shvachko, K., Kuang, H., Radia, S., Chansler, R.
-\newblock The hadoop distributed file system.
-\newblock  Mass Storage Systems and Technologies (MSST), 2010 IEEE 26th
-  Symposium on. IEEE,  2010, pp. 1--10.
+Shvachko, K., Kuang, H., Radia, S., Chansler, R., 2010. The hadoop distributed file system. Mass Storage Systems and Technologies (MSST), 2010 IEEE 26th Symposium on. IEEE, 2010, pp. 1--10.
 
 \bibitem{dean2008mapreduce}
-Dean, J., Ghemawat, S.
-\newblock MapReduce: simplified data processing on large clusters.
-\newblock {\em Communications of the ACM} {\bf 2008}, {\em 51},~107--113.
+Dean, J., Ghemawat, S., 2008. MapReduce: simplified data processing on large clusters. {\em Communications of the ACM}, {\em 51}, pp. 107--113.
 
 \bibitem{gao2012exploring}
-Gao, H., Tang, J., Liu, H.
-\newblock Exploring Social-Historical Ties on Location-Based Social Networks.
-\newblock  ICWSM,  2012.
+Gao, H., Tang, J., Liu, H., 2012. Exploring Social-Historical Ties on Location-Based Social Networks. ICWSM.
 
 \bibitem{buttenfield1991map}
-Buttenfield, B.P., McMaster, R.B.
-\newblock {\em Map Generalization: Making rules for knowledge representation},
-  Longman Scientific \& Technical New York,  1991.
+Buttenfield, B.P., McMaster, R.B., 1991. {\em Map Generalization: Making rules for knowledge representation}, Longman Scientific \& Technical New York.
 
 \bibitem{samet1984quadtree}
-Samet, H.
-\newblock The quadtree and related hierarchical data structures.
-\newblock {\em ACM Computing Surveys (CSUR)} {\bf 1984}, {\em 16},~187--260.
+Samet, H., 1984. The quadtree and related hierarchical data structures. {\em ACM Computing Surveys (CSUR)}, {\em 16}, pp. 187--260.
 
 \bibitem{clauset2009power}
-Clauset, A., Shalizi, C.R., Newman, M.E.
-\newblock Power-law distributions in empirical data.
-\newblock {\em SIAM review} {\bf 2009}, {\em 51},~661--703.
+Clauset, A., Shalizi, C.R., Newman, M.E., 2009. Power-law distributions in empirical data. {\em SIAM review}, {\em 51}, pp. 661--703.
 
 \bibitem{reynolds2012truncated}
-Reynolds, A.
-\newblock Truncated L{\'e}vy walks are expected beyond the scale of data
-  collection when correlated random walks embody observed movement patterns.
-\newblock {\em Journal of The Royal Society Interface} {\bf 2012}, {\em
-  9},~528--534.
+Reynolds, A., 2012.
+Truncated L{\'e}vy walks are expected beyond the scale of data collection when correlated random walks embody observed movement patterns.
+{\em Journal of The Royal Society Interface}, {\em
+  9}, pp. 528--534.
 
 \bibitem{zhao2015explaining}
-Zhao, K., Musolesi, M., Hui, P., Rao, W., Tarkoma, S.
-\newblock Explaining the power-law distribution of human mobility through
-  transportation modality decomposition.
-\newblock {\em Scientific reports} {\bf 2015}, {\em 5}.
+Zhao, K., Musolesi, M., Hui, P., Rao, W., Tarkoma, S., 2015. Explaining the power-law distribution of human mobility through transportation modality decomposition. {\em Scientific reports}, {\em 5}.
 

### 2016-10-19 Multi-scale_Mobility_Pattern_CEUS/template-num.tex
jia you jia you

@@
 
-\title{Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns}
+\title{An empirical study of the multi-scale spatiotemporal Twitter user mobility patterns}
 
@@
 \begin{abstract}
-% Text of abstract
+Understanding human mobility patterns is of great importance for urban planning, traffic management, and even marketing campaign.
+However, the capability of capturing detailed human movements with fine-grained spatial and temporal granularity is still limited.
+In this study, we extracted high-resolution mobility data from a collection of over 1.3 billion geo-located tweets.
+Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access, the dataset is collected from publicly accessible Twitter data streams.
+In this paper, we performed an empirical study of the multi-scale spatiotemporal Twitter user mobility patterns in the contiguous United States during the year 2014.
+
+Our approach included a scalable visual-analytics framework to deliver efficiency and scalability in filtering large volume of geo-located tweets, modeling and generating space-time user trajectories, and summarizing multi-scale spatiotemporal user mobility patterns.
+
+We performed a set of statistical analysis to understand Twitter user mobility patterns across multi-level spatial scales and temporal ranges.
+In particular, Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals revealed multi-scale or multi-modal Twitter user mobility patterns.
+By further studying such mobility patterns in different temporal ranges, we identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
 \end{abstract}
@@
 \begin{keyword}
-% keywords here, in the form: keyword \sep keyword
-
-% PACS codes here, in the form: \PACS code \sep code
-\PACS 
+Geo-located tweets, mobility patterns, multi-scale spatiotemporal analysis, distance decay
 \end{keyword}
@@
 % main text
-\section{}
-\label{}
+\section{Introduction}
+%\label{}
+Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\cite{belik2011natural}.
+Earlier research efforts relied on low-resolution mobility data to understand human mobility patterns, such as using census records to study human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
+However, such mobility data do not provide detailed human movements with fine-grained spatial and temporal granularity, which are usually aggregated and therefore are limited to capture mobility patterns of individuals~\cite{gonzalez2008understanding,Jurdak2015}.
+In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, emerging as a new mobility data source, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints in the form of real-world user trails and footprints~\cite{thatcher2014living}.
+A significant advantage of utilizing LBSM data streams as proxies for studying human mobility patterns is the large spatial coverage.
+For instance, researchers have used geo-located tweets for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible for other mobility datasets (e.g., GPS traces and mobile phone call records).
+Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}, the publicly available LBSM data streams offer unique opportunities for conducting reproducible and comparative scientific findings across different geographical regions.\\
+
+Many recent studies have adopted LBSM data streams to study human mobility patterns.
+For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects in the collective user movements~\cite{gonzalez2008understanding}, which were used to reveal different travel modes~\cite{Jurdak2015}, travel demands~\cite{wu2014intra,hasan2013understanding}, and the impact of social connections~\cite{cho2011friendship}.
+These studies have provided strong supports for using LBSM data as proxies for studying mobility patterns of individuals and valuable insights into human mobility dynamics.
+However, the variations of movements in different spatial scales and temporal ranges are neglected in these studies, where the measurements of distances are either fixed in a certain time range or to a specific geographic region.
+For instances, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national levels) are lacking.
+Such insights are critical to advance our understandings of the collective mobility patterns for various applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
+On the other hand, while the high-resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data-intensive challenges for developing multi-scale spatiotemporal analysis approaches to dealing with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales~\cite{tsou2015}.
+
+In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
+The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from January 1 to December 31, 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
+To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
+This framework is implemented based on high-performance distributed computing environment using Apache Hadoop (http://hadoop.apache.org/), which is an open source software framework to enable distributed processing of large datasets across computing clusters.
+Enabled by this framework, we have performed a set of statistical analysis to understand multi-scale spatiotemporal Twitter user mobility patterns. 
+We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions.
+In particular, Twitter user mobility patterns measured by user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
+By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
+In addition, our approach provides an interactive 3D virtual globe web mapping interface to enable exploratory geo-visual analytics for understanding the detailed Twitter user movement flows within a given spatial scale and time window.\\
+
+The remainder of this paper is organized as follows.
+Section 2 describes the related work in the context of studying mobility patterns using LBSM data, in particular, the geo-located Twitter data.
+We focus on research challenges in using visual-analytics methods to enable multi-scale spatiotemporal analysis with massive movement datasets, including data management, multi-level spatiotemporal user trajectory modeling and visualization.
+Section 3 details the processes for extracting, aggregating and summarizing multi-level spatiotemporal Twitter user mobility patterns.
+Section 4 presents the case study of performing visual-analytics for seeking multi-scale spatiotemporal Twitter mobility patterns in the continuous United States of the year 2014.
+Section 5 concludes the paper.
+
+\section{Mobility Patterns in Location Based Social Media data}
+\subsection{Geo-located Twitter Data for Studying Large-scale User Movements}
+To understand detailed mobility patterns of individuals, the capability to capture human movements with fine-grained spatial and temporal granularity is critical.
+In this connection, using GPS trackers tends to produce, to date, the most accurate records of individuals' movements regarding the accuracy of recorded user locations and update frequency~\cite{zheng2008understanding}.
+However, such data are often limited in spatial scale (e.g., within a specific city or region) from a small group of people, for example, 226 and 182 volunteers participated in collecting such mobility data in~\cite{rhee2011levy} and~\cite{zheng2010geolife} respectively.
+Other than tracking people directly, the vehicle-based GPS traces are often tied to specific vehicles (e.g. taxi), which are only accessible for a certain group of people~\cite{kung2014exploring}.
+
+Another approach from the literatures for studying human mobility is using mobile phone call data, such as Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with an accuracy in the order of kilometers~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
+Such a dataset can cover relatively large spatial scale~\cite{becker2013human,sobolevsky2013delineating} (e.g., national level) and a large portion of the population in the study region~\cite{kung2014exploring}.
+However, due to the concerns of infringement on individual privacy, mobile phone call data are not publicly accessible at all.
+Even such data were obtained in the mentioned studies, they came from various service providers covering different groups of users.
+These issues limit the capability for conducting reproducible scientific findings for mobility research, such as validating or extending the existing discoveries.
+
+In this connection, it becomes increasingly popular for researchers to exploit the publicly accessible mobility data captured from today's pervasive Location Based Social Media (LBSM) platforms (e.g., Foursquare and Twitter).
+LBSM enables users to attach their current location as a geo-tag to the message they post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
+A Big Data scenario emerges when millions social media users constantly post messages.
+In this study, geo-located Twitter data are chosen as a source for studying detailed mobility patterns.
+Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
+It provides a publicly accessible streaming API for easy data access~\cite{twitterAPI}.
+Indeed, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.
+
+However, it is worth noting that there are some limitations and complexities in directly using LBSM data for studying human mobility patterns.
+For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place.
+Although geo-located tweets tend to provide geo-locations with high position resolution as aforementioned~\cite{Jurdak2015}, the information regarding the quality of the geo-locations is absent in each tweet.
+This will contribute to the uncertainties in calculating the distance of Twitter user movements, especially in densely built environments.   
+There is also a potential mismatch regarding the representativeness of the overall population since not all people use social media or send geo-located messages~\cite{kung2014exploring}, the demographic information of the Twitter users cannot be easily identified.
+The derived mobility patterns may lead to an over or under-representation of the real-world human mobility patterns.
+Many studies started to look into the demographic information of LBSM data, in particular Twitter data~\cite{mitchell2013geography,longley2015geotemporal}.
+Although the used methods are still arguable, these issues certainly require us to pose stricter criteria in understanding human mobility patterns using geo-located Twitter data.
+On the other hand, geo-located Twitter dataset presents some unique advantages that make it a valuable proxy for studying human mobility patterns.
+For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\cite{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\cite{hawelka2014geo}, which is almost impossible for other mobility datasets.
+More importantly, by continuously monitoring the geo-located Twitter data streams with large volume of detailed and frequently updated spatiotemporal records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements), which is one of the motivations for this study.
 

### 2016-10-23 urban_boundaries_gb_ijgis_submission_r3/IJGIS/Paper.tex
author names

--- 2016-10-12 urban_boundaries_gb_ijgis_submission_r2/IJGIS/Paper.tex
@@
 
-%\doi{10.1080/1365881YYxxxxxxxx}
-%\issn{1362-3087} \issnp{1365-8816} \jvol{00} \jnum{00} \jyear{2009} %\jmonth{February}
+% \doi{10.1080/1365881YYxxxxxxxx}
+% \issn{1362-3087} \issnp{1365-8816} \jvol{00} \jnum{00} \jyear{2016} \jmonth{October}
 
-%\markboth{Taylor \& Francis and I.T. Consultant}{International Journal of Geographical Information Science}
+% \markboth{Taylor \& Francis and I.T. Consultant}{International Journal of Geographical Information Science}
 
 \articletype{RESEARCH ARTICLE}
-\title{{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data} }
+\title{{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}}
+
+\author{Junjun Yin$^{1,2,3}$, Soliman Aiman$^{1,4}$, Dandong Yin$^{1,2,3}$ and Shaowen Wang$^{1,2,3,4}$$^{\ast}$\thanks{$^\ast$Corresponding author. Email: shaowen@illinois.edu
+\vspace{6pt}}\\\vspace{6pt}  $^{1}${\em{CyberGIS Center for Advanced Digitial and Spatial Studies}};
+$^{2}${\em{CyberInfrastructure and Geospatial Information Laboratory}};
+$^{3}${\em{Department of Geography and Geographic Information Science}};
+$^{4}${\em{National Center for Supercomputing Applications}};{\em{University of Illinois at Urbana-Champaign, IL, 61801, U.S.A.}}
+\\\vspace{6pt}\received{v2.0 released October 2016}}
 \maketitle
@@
 Existing urban boundaries are usually defined by government agencies for political and administrative purposes.
-However, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter-regional activities.
+However, it is not clear whether the boundaries truly reflect human interactions with urban space in intra- and inter-regional activities.
 Defining urban boundaries which consider socio-economic relationships and citizen commute patterns is important for many aspects of urban planning.
-In this study, we presented a method to redraw urban boundaries based upon human interactions with the physical space.
-Specifically, we depicted the urban boundaries of Great Britain using a mobility network of Twitter user spatial interactions that was inferred from over 69 million geo-located Twitter messages.
+In this study, we presented a method to redraw urban boundaries based upon human interactions with physical space.
+Specifically, we depicted the urban boundaries of Great Britain using a mobility network of Twitter user spatial interactions that was inferred from over 69 million geo-located Tweets.
 We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
 The results of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas, which provide a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
-The technique was applied to both national (Great Britain) and municipal scales (the London metropolis).
+The method was applied to both national (Great Britain) and municipal scales (the London metropolis).
 While our results corresponded well with the administrative boundaries, many unexpected and interesting boundaries were identified.
 More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
-This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
+This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides new insights into the interactions between human activity and urban space.
 \newline
@@
 A suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interaction among the nodes~\citep{lancichinetti2009}.
-Different social and physical human interactions were considered to establish the edges of the network connecting the nodes.
+Different social and spatial human interactions were considered to establish the edges of the network connecting the nodes.
 For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in Great Britain~\citep{ratti2010}.
@@
 
-A common outcome observed in the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
+A common finding from the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
 A general consensus is that those geographically cohesive areas are instances of the effects on spatial proximity, where the interaction strength between two urban regions decreases as the geographical distance between them increases~\citep{fotheringham1981}.
@@
 \begin{center}
-\includegraphics[width=.8\linewidth]{./figure/S2_twitter_density_Fig_1}
+\includegraphics[width=.9\linewidth]{./figure/S2_twitter_density_Fig_1}
 \caption{{\bf The spatial coverage of collected geo-located Tweets in Great Britain (left) and London (right).} Each point corresponds to an individual geo-located tweet collected for this study.
@@
 \end{figure}
+
 The original location information embedded in the geo-tag is given in units of latitude and longitude.
@@
 \begin{figure}[ht]
-\includegraphics[width=1.0\linewidth]{./figure/S3_visitation}
-\caption{ \bfseries{Cumulative distribution of the number of locations visited by each Twitter user during different timespan}}
+\begin{center}
+\includegraphics[width=0.9\linewidth]{./figure/S3_visitation}
+\caption{\bfseries{Cumulative distribution of the number of locations visited by each Twitter user during different timespan}}
 \label{S3_Fig}
+\end{center}
 \end{figure}
@@
 Coherent geographic regions were identified as individual fishnet cells showing more internal user movement compared to user movements across the cell boundaries to neighboring cells.
-To help readers that are not familiar with the geographic context in Great Britain better interpret the derived boundaries,
-we had added two additional layers (i.e., locations of airport fields and population-wighted-centroids of workplace zones in the Great Britain) in the background of the figures.
+To help readers who are not familiar with the geographic context in Great Britain better interpret the derived boundaries, two additional layers (i.e., locations of airport fields and population-wighted-centroids of workplace zones in the Great Britain) are added in the background of the figures.
 Fig.~\ref{S5_Fig} presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4 km, greater than 10 km, and using all available displacements together compared to the administrative boundaries of Great Britain.
@@
 
-\begin{figure}[ht]
+\begin{figure}
 \begin{center}
@@
 
-\begin{figure}[ht]
+\begin{figure}
 \begin{center}
-\includegraphics[width=0.9\linewidth]{./figure/S7_london}
+\includegraphics[width=0.7\linewidth]{./figure/S7_london}
 \caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs ($L(M)=8.1$)}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.
@@
 
-%\clearpage
 \section{Discussion}
@@
 \section{Conclusion}
-In this study, we presented a method that connected human mobility research with the delineation of the non-administrative anthropographic urban boundaries in Great Britain using a mobility network of Twitter user spatial interactions.
-In contrast to administrative urban boundaries, our ``bottom-up" approach imposed a virtual fishnet over the islands of Great Britain to partition the space.
+In this study, we described a method that connected human mobility research with the delineation of the non-administrative anthropographic urban boundaries in Great Britain using a mobility network of Twitter user spatial interactions.
+In contrast to administrative urban boundaries, our ``bottom-up" approach constructed a virtual fishnet over the islands of Great Britain to partition the space.
 By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell-size of 10 km at the national level and 1 km for the greater London region.
@@
 By performing a statistical analysis of Twitter user mobility patterns in Great Britain, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
-Identifying the connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in Great Britain.
+Identifying the connected regions at each of these distance ranges revealed hierarchical boundaries of  the urban space in Great Britain.
 
-The power of using Twitter user mobility to delineate non-administrative anthropographic boundaries is the ability to redraw the city at different mobility ranges inferred objectively from the collective mobility patterns.
-Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect the human interactions with the geographical space.
+The power of using Twitter user mobility to delineate non-administrative anthropographic boundaries enables urban representation at different mobility ranges inferred objectively from the collective mobility patterns.
+Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect human interactions with the geographical space.
 More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
-This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activities and urban space.
-A final remark from this study for future studies is that geographical distance plays an important role in affecting human mobility patterns and the strength of human spatial interactions across space.
-Our approach can be considered to assist in understanding human spatial interactions from the mobility perspective, which is applicable for detailed geo-located Twitter data in different countries, as well as future mobility datasets with detailed location information of individuals and large spatial coverage.
-%\subsection{Acknowledgements}
+This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, gaining new insights into the interactions between human activities and urban space.
+A final remark from this study for future work is that geographical distance plays an important role in affecting human mobility patterns and the strength of human spatial interactions across space.
+Our approach can be considered to assist in understanding human spatial interactions from the mobility perspective, which is applicable based on detailed geo-located Twitter data in many countries, as well as future mobility datasets with detailed location information of individuals and large spatial coverage.
+
+\subsection*{Acknowledgements}
+xx
 

### 2016-10-25 Multi-scale_Mobility_Pattern_CEUS/ijgi-148112-can be published.tex
temp

--- 2016-10-17 ijgi-148112-for proofreading/ijgi-148112-can be published.tex
@@
 The authors would like to thank the four anonymous reviewers of IJGI for their constructive comments that better shaped the paper.
-Junjun Yin would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
+Junjun Yin, Yizhao Gao and Shaowen Wang would like to thank the funding support from the U.S. National Science Foundation under grant numbers: xx1, xx2, and xx3.
 Zhenhong Du would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.

### 2016-10-26 ijgi-148112-for proofreading/ijgi-148112-can be published_correction.tex
try

--- 2016-10-17 ijgi-148112-for proofreading/ijgi-148112-can be published_origin.tex
@@
 $^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
-$^{2}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn\\
-$^{3}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA}
+$^{3}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
+$^{2}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn}
 

### 2016-10-27 ijgi-148112-for proofreading/ijgi-148112-can be published_correction.tex
draft

@@
 % Authors, for the paper (add full first names)
-\Author{Junjun Yin $^{1,3}$ and Zhenhong Du $^{2,3,*}$}
+\Author{Junjun Yin $^{1,2}$, Yizhao Gao $^{1,2}$, Zhenhong Du $^{2,3}$ and Shaowen Wang $^{1,2,*}$}
 % Authors, for metadata in PDF
-\AuthorNames{Junjun Yin and Zhenhong Du}
+\AuthorNames{Junjun Yin, Yizhao Gao, Zhenhong Du and Shaowen Wang}
 
@@
 \address{%
-$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
-$^{3}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
-$^{2}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn}
+$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu, ygao29@illinois.edu, shaowen@illinois.edu\\
+$^{2}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
+$^{3}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn}
 
 % Contact information of the corresponding author
-\corres{Correspondence: duzhenhong@zju.edu.cn; Tel.: +86-138-1919-2989}
+\corres{Correspondence: shaowen@illinois.edu}
 
@@
 Note that the original location information embedded in each geo-located tweet is given in units of latitude and longitude, the distance is calculated by the great-circle distance between two points on a sphere with the haversine formula.
-Finally, we used the geographic boundaries of the continuous United States (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details is presented in the following section.
+Finally, we used the geographic boundaries of the continuous United States (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details are presented in the following section.
 Based on these reinforcements, the dataset contains 1,052,861,000 tweets and 4,559,205 unique users.
@@
 Finally, the reducers generate two data outputs: (1) reconstructed space-time Twitter user trajectories at each spatial level (2) movement flows in the form of in and out movement flux between the spatial units.
-The movement flows are stored in the database for interactive explorations in the 3D web mapping interface, whereas the re-constructed trajectories can be further processed to produce distance measures at different spatial scales, which is illustrated as fellows:
+The movement flows are stored in the database for interactive explorations in the 3D web mapping interface, whereas the re-constructed trajectories can be further processed to produce distance measures at different spatial scales, which is illustrated as follows:
 \newline
@@
 
-The probability distribution of radius of gyrations of individuals at the national level (Figure~\ref{fig:gyration}a) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10~m$ from [10 m, 50 m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50 m, 30 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30 km].
+The probability distribution of radius of gyrations of individuals at the national level (Figure~\ref{fig:gyration}a) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10~m$ from [10 m, 50 m], $ P(r_{g}) \sim \beta\lambda_{2}{r_{g}}^{\beta-1}e^{-\lambda^{1}({r_{g}}^\beta-{r_{g}}_{min}^\beta)}, {r_{g}}_{min}=50~m$ from [50 m, 30 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30 km].
 In particular, the radius of gyration between 50 m and 30 km can be further approximately by two power law distributions with a cutting point at 6 km (Figure~\ref{fig:gyration}b), which suggest two main types of spatial coverage of from the collected Twitter users in the continuous United States.
@@
 The fluctuations in the tails of the distributions indicate that long distance radius of gyrations (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern, which means the increase or decrease of long distance movement activities in the corresponding time period.
-However, it is worthy noting that the overall trends in the Twitter user mobility patterns revealed by radius of gyrations are still consistent.
+However, it is worth noting that the overall trends in the Twitter user mobility patterns revealed by radius of gyrations are still consistent.
 

### 2016-11-03 ijgi-148112-for proofreading/ijgi-148112-can be published_correction.tex
updates

@@
 The authors would like to thank the four anonymous reviewers of IJGI for their constructive comments that better shaped the paper.
-Junjun Yin would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
+Junjun Yin, Yizhao Gao and Shaowen Wang would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
 Zhenhong Du would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Junjun Yin conceived and designed the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin and Zhenhong Du wrote the paper.}
+\authorcontributions{Shaowen Wang conceived the idea; Junjun Yin and Yizhao Gao designed the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin, Yizhao Gao, Zhenhong Du and Shaowen Wang wrote the paper.}
 

### 2016-11-04 ijgi-148112-for proofreading/ijgi-148112-can be published_correction.tex
to be done today

--- 2016-10-27 ijgi-148112-for proofreading/ijgi-148112-can be published_correction.tex
@@
 % Authors, for the paper (add full first names)
-\Author{Junjun Yin $^{1,2}$, Yizhao Gao $^{1,2}$, Zhenhong Du $^{2,3}$ and Shaowen Wang $^{1,2,*}$}
+\Author{Junjun Yin $^{1,2}$, Yizhao Gao $^{1,2}$, Zhenhong Du $^{2,4}$ and Shaowen Wang $^{1,2,3,*}$}
 % Authors, for metadata in PDF
@@
 $^{2}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
-$^{3}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn}
+$^{3}$ \quad National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
+$^{4}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn}
 
@@
 We performed a set of statistical analysis to understand Twitter user mobility patterns across multi-level spatial scales and temporal ranges.
-In particular, Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals revealed multi-scale or multi-modal Twitter user mobility patterns.
-By further studying such mobility patterns in different temporal ranges, we identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
-At the same time, our approach provides a geo-visualization unit with an interactive 3D virtual globe web mapping interface for exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements.}
+In particular, Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals revealed multi-scale or multi-modal representation of the patterns.
+By further examining such mobility patterns in different temporal ranges, we identified both consistency and seasonal fluctuations of a distance decay effect.
+At the same time, our approach provides a geo-visualization component with an interactive 3D virtual globe and associated web mapping interface for exploratory analysis of the multi-level spatiotemporal movement patterns.}
 
 % Keywords
-\keyword{Geo-located tweets, mobility patterns, multi-scale spatiotemporal analysis, scalable visual-analytics framework}
+\keyword{Geo-located social media, human mobility, multi-scale spatiotemporal analysis, scalable visual-analytics}
 \begin{document}
@@
 \section{Introduction}
-Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and even the spatial spread of epidemic diseases~\cite{belik2011natural}.
-Earlier research efforts relied on low-resolution mobility data to understand human mobility patterns, such as using census records to study human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
+Understanding human mobility patterns is of great importance for a broad range of applications, such as urban planning~\cite{zheng2008understanding}, traffic management~\cite{jiang2009characterizing}, and controlling epidemic diseases~\cite{belik2011natural}.
+Earlier research efforts relied on low-resolution mobility data to understand human mobility patterns, such as using census records to study human migration patterns~\cite{greenwood1985human}, or designing surveys to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.
 However, such mobility data do not provide detailed human movements with fine-grained spatial and temporal granularity, which are usually aggregated and therefore are limited to capture mobility patterns of individuals~\cite{gonzalez2008understanding,Jurdak2015}.
-In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, emerging as a new mobility data source, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints in the form of real-world user trails and footprints~\cite{thatcher2014living}.
+In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, emerging as a new mobility data source, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer conterminous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints in the form of real-world user trails and footprints~\cite{thatcher2014living}.
 A significant advantage of utilizing LBSM data streams as proxies for studying human mobility patterns is the large spatial coverage.
 For instance, researchers have used geo-located tweets for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible for other mobility datasets (e.g., GPS traces and mobile phone call records).
-Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}, the publicly available LBSM data streams offer unique opportunities for conducting reproducible and comparative scientific findings across different geographic regions.
+While accessing individual-level human mobility data, such as the mobile phone call records, often raise privacy concerns~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}, open data are provided by LBSM data streams.
 
-Many recent studies have adopted LBSM data streams to study human mobility patterns.
+Many recent studies have adopted LBSM data streams to study human mobility.
 For example, they modeled and extracted trajectories of individuals and performed statistical analysis focusing on the distance decay effects in the collective user movements~\cite{gonzalez2008understanding}, which were used to reveal different travel modes~\cite{Jurdak2015}, travel demands~\cite{wu2014intra,hasan2013understanding}, and the impact of social connections~\cite{cho2011friendship}.
-These studies have provided strong supports for using LBSM data as proxies for studying mobility patterns of individuals and valuable insights into human mobility dynamics.
-However, the variations of movements in different spatial scales and temporal ranges are neglected in these studies, where the measurements of distances are either fixed in a certain time range or to a specific geographic region.
-For instances, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national levels) are lacking.
-Such insights are critical to advance our understandings of the collective mobility patterns for various applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
-On the other hand, while the high-resolution spatiotemporal records from LBSM present unique research opportunities in this direction, the inherited large data volume poses significant data-intensive challenges for developing multi-scale spatiotemporal analysis approaches to dealing with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales~\cite{tsou2015}.
+These studies have provided strong supports for using LBSM data as proxies for studying mobility patterns of individuals and important insights into human mobility dynamics.
+However, the variations of movements across different spatial scales and temporal ranges are not adequately addressed in these studies, where the measurements of distances are either fixed in a certain time range or to a specific geographic region.
+For instance, the examinations on whether there are temporal (e.g., monthly or seasonal) changes within the movements or how the observed mobility patterns vary across different spatial scales (e.g., intra- or inter city or national levels) are lacking for depth.
+However, such insights are critical to advance our understanding of the collective mobility patterns for various applications, such as examining the mobility patterns across different cities~\cite{noulas2012tale}, the spread patterns of disease~\cite{balcan2009multiscale, tamerius2011global} and touristic activities~\cite{hawelka2014geo}.
+On the other hand, while the high-resolution spatiotemporal records from LBSM present unique research opportunities in this regard, the inherent large data volume poses significant data-intensive challenges for developing multi-scale spatiotemporal analysis approaches to dealing with the complexities in filtering movements of individuals, modeling and aggregating user trajectories at multiple spatial and temporal scales~\cite{tsou2015}.
 
-In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
+In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the conterminous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
 The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from 1st January to 31st December 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
@@
 Section 3 details the processes for extracting, aggregating and summarizing multi-level spatiotemporal Twitter user mobility patterns.
-Section 4 presents the case study of performing visual-analytics for seeking multi-scale spatiotemporal Twitter mobility patterns in the continuous United States of the year 2014.
+Section 4 presents the case study of performing visual-analytics for seeking multi-scale spatiotemporal Twitter mobility patterns in the conterminous United States of the year 2014.
 Section 5 concludes the paper.
@@
 
-\section{Materials and Methods}
+\section{Data and Methods}
 \subsection{Geo-located Twitter Data}
-Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at.
-In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
-To ensure complete coverage over the continuous United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
-The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2 GB in size) collected per day.
-We have collected more than 1.3 billion geo-located tweets from 1 January to 31 December 2014 with 6,147,430 Twitter users and 1 TB in file size.
+Each geo-located tweet is appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at.
+In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within the box.
+To ensure complete coverage over the conterminous United States, we implemented a crawler that selects the North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
+The crawler was constantly running with over 2 million geo-located raw tweets ($\sim$2 GB in size) collected per day.
+We have collected more than 1.3 billion geo-located tweets from 1 January to 31 December 2014 with 6,147,430 Twitter users and 1 TB in data size.
 
 In particular, this data collection of the year 2014 was originally used to map the spatial spread of flu in North America during the time period~\cite{padmanabhan2014flumapper}.
-As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages in the dataset~\cite{black2012twitter}; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
+As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps.
+We first removed duplicated messages in the dataset~\cite{black2012twitter}, and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
 In this case, we adopted the speed limit value as 240 m/s used in~\cite{Jurdak2015}, where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
 Note that the original location information embedded in each geo-located tweet is given in units of latitude and longitude, the distance is calculated by the great-circle distance between two points on a sphere with the haversine formula.
-Finally, we used the geographic boundaries of the continuous United States (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details are presented in the following section.
+Finally, we used the geographic boundaries of the conterminous United States (excluding Alaska and Hawaii) to further restrict the remaining tweets, where the technical details are presented in the following section.
 Based on these reinforcements, the dataset contains 1,052,861,000 tweets and 4,559,205 unique users.
@@
 To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
-The scalable visual-analytics framework consists of two main units: (1) Data processing unit: a distributed computing environment using Apache Hadoop for modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing the movements at multiple spatiotemporal scales.
-(2) Geo-visualization unit: an interactive 3D virtual globe web mapping interface for exploratory geo-visual analytics to understand detailed Twitter user movement flows across different spatial scales and temporal ranges.
+The scalable visual-analytics framework consists of two main components: (1) Data processing: a distributed computing environment using Apache Hadoop for modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing the movements at multiple spatiotemporal scales.
+(2) Geo-visualization: an interactive 3D virtual globe web mapping interface for exploratory geo-visual analytics to understand detailed Twitter user movement flows across different spatial scales and temporal ranges.
 
@@
 An overall system architecture of the framework is shown in Figure~\ref{fig:overall_archi}.
-The details regarding the function and implementation of each unit are presented in the next sections.
+The details regarding the function and implementation of each component are presented in the next sections.
 
@@
 Each raw geo-located tweet contains multiple fields of information, such as the created time, country, language code, and location, etc.
-To construct a space-time trajectory from the data collection, we are interested in the following fields: \textit{user ID, location, timestamp}, which can be represented by a tuple $\left\langle id, loc, t\right\rangle$, where \textit{id} is a unique string representing a Twitter user's id; \textit{loc} is the recorded location of the message represented as a pair of projected coordinates $\left\langle x, y\right\rangle$;
+To construct a space-time trajectory from the dataset, we are interested in the following fields: \textit{user ID, location, timestamp}, which can be represented by a tuple $\left\langle id, loc, t\right\rangle$, where \textit{id} is a unique string representing a Twitter user's id; \textit{loc} is the recorded location of the message represented as a pair of projected coordinates $\left\langle x, y\right\rangle$;
 and \textit{t} is the timestamp of when the message was posted; A Twitter user's space-time trajectory is defined as follows.
@@
 Based on this definition for modeling the space-time Twitter user trajectories, we converted the process of extracting trajectories from the raw geo-located Twitter data as a MapReduce task.
-Specifically, each mapper utilizes the unique user id as a key to prepares the records that belong to the same user and send them to reducer.
-Once the reducers receive the $\langle key, value\rangle$ pairs, a Twitter user's space-time trajectory is formed by the sorting the locations in chronological order while considering the speed limit.
+Specifically, each mapper utilizes the unique user id as a key to prepare the records that belong to the same user and send them to a reducer.
+Once the reducers receive the $\langle key, value\rangle$ pairs, a Twitter user's space-time trajectory is formed by sorting the locations in chronological order while considering the speed limit.
 \newline
@@
 \noindent\textbf{Definition 2.
-visitation behavior, displacement and radius of gyration:} \emph{As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers the frequency of a user visiting different locations within a specific time frame.
+Visitation behavior, displacement and radius of gyration:} \emph{As each space-time Twitter user trajectory records all the locations a user has visited, the visitation behavior refers to the frequency of a user visiting different locations within a specific time frame.
 This metric provides an overall assessment regarding the diversity and similarity in the collective mobility pattern}~\cite{gao2012exploring}.
 
-In particular, the measurements of displacements and radius of gyrations of individuals are two popular metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
+In particular, the measurements of displacements and radius of gyrations of individuals are two key metrics to investigate and quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
 The displacement refers to an individual's re-allocation across the geographic space measured in distance, i.e., $distance (loc_{i} - loc_{i-1})$.
-It is not equivalent to a ``trip'' took by an individual, for instance, even the time interval between two recorded locations is one month, it will still count as a displacement.
-By studying the collective displacements from a group people, it helps to identify the distance bounds associated with different travel modes~\cite{Jurdak2015} and to quantitatively differentiate the mobility patterns from random walks~\cite{brockmann2006scaling}.
+It is not equivalent to a ``trip'' taken by an individual, for instance, even the time interval between two recorded locations is one month, it is still counted as a displacement.
+By studying the collective displacements from a group users, it helps to identify the distance bounds associated with different travel modes~\cite{Jurdak2015} and to quantitatively differentiate the mobility patterns from random walks~\cite{brockmann2006scaling}.
 On the other hand, radius of gyration (donated as $r_{g}$) is a metric to distinguish mobility patterns of individuals~\cite{gonzalez2008understanding}, which is defined as follows.
@@
 Note that both displacements and radius of gyrations are measured by ``crow's fly distance'' in this study (i.e., the direct great-circle distance between two recorded locations).
-Since these metrics are based on the generated trajectories, by breaking and aggregating the trajectories in multiple spatial scales and temporal ranges, it enables performing multi-scale spatiotemporal analysis on these measurements and studying the corresponding mobility patterns.
+Since these metrics are based on the generated trajectories, by aggregating the trajectories across multiple spatial scales and temporal ranges, multi-scale spatiotemporal analysis can be performed  to examine the corresponding mobility patterns.
 
 \subsection{Multi-level spatiotemporal trajectory aggregation}
-An important strategy for visual-analytics methods to deal with massive movement datasets is performing spatial aggregations to provide different levels-of-detail~\cite{andrienko2007designing,andrienko2007visual}.
-It is similar to the map generation approach that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest~\cite{buttenfield1991map}.
-To enable aggregating Twitter trajectories into multiple spatial scales, we have extended the hierarchical space-time cube model developed in~\cite{cao2014scalable}, where we partitioned the geographic space of the continuous United States into 10 hierarchical spatial layers and each space-time cube is created with a fixed time window of a week interval.
-Specifically, the state boundaries of the continuous United States are treated as the base layer (i.e.
+An important strategy for visual-analytics methods to deal with massive movement datasets is spatial aggregations with different levels-of-detail~\cite{andrienko2007designing,andrienko2007visual}.
+It is similar to map generalization that when a user is interacting with a map interface, the details of visualization should be adaptive to a user's area-of-interest and associated spatial scale~\cite{buttenfield1991map}.
+To enable aggregating Twitter trajectories into multiple spatial scales, we have extended the hierarchical space-time cube model developed in~\cite{cao2014scalable}, where we partitioned the geographic space of the conterminous United States into 10 hierarchical spatial layers and each space-time cube is created with a fixed time window of a week interval.
+Specifically, the state boundaries of the conterminous United States are treated as the base layer (i.e.
 level 0) for aggregating state-level Twitter user movements, Alaska and Hawaii are excluded for the consideration of better visualization effects in the mapping interface of the framework.
-We then created an hierarchical fishnet by diving the study region into regular cells, where the finest level (level 10) consists 1 km $\times$ 1 km cells.
-Such a cell size is consistent with the spatial resolution in landscan (http://web.ornl.gov/sci/landscan) product for measuring the global population density.
+We then created a hierarchical fishnet by diving the study region into regular cells, where the finest level (level 10) consists 1 km $\times$ 1 km cells.
+Such a cell size is consistent with the spatial resolution in LandScan (http://web.ornl.gov/sci/landscan) product for measuring the global population density.
 In our case, the cell width/height for level i-1 is twice of the size in level i.
-Figure~\ref{fig:multilevel} illustrates an hierarchical fishnet spatial units for mapping multi-level Twitter user movements.
-Note that any predefined geographic boundaries can be used and appended in this framework to show different level-of-detailed movements (e.g., national-level and census-tract level), in our case, we replaced the level 8 fishnet layer with the US county boundaries.
+Figure~\ref{fig:multilevel} illustrates a hierarchical fishnet spatial unit for mapping multi-level Twitter user movements.
+Note that any predefined geographic boundaries can be used and appended in this framework to show movements with different level-of-details (e.g., national-level and census-tract level), in our case, we replaced the level 8 fishnet layer with the US county boundaries.
 
 To perform a multi-level spatial aggregation of the Twitter user trajectories using hierarchical spatial layers, each location in a user's trajectory is redistributed to the corresponding spatial units.
-A MapReduce algorithm for the spatial aggregation is implemented, where the ID of unit in each spatial layer (e.g., polygon in state and country layer and cell in the rest) is treated as key in the at the map stage.
-It performs a ``point-in-polygon'' geospatial operation to determine which polygon the point belongs to.
-If the location does not belong to any polygon, it will be dropped, which is how we used the geographic boundaries of the continuous United States to filer the raw tweet collection that initially covered the North America and kept the ``domestic'' ones.
-To optimize the ``point-in-polygon'' determination without comparing the location with every polygon in the spatial layer, we also created a Quad-Tree~\cite{samet1984quadtree} for each spatial layer to speed up the process.
-Finally, the reducers generate two data outputs: (1) reconstructed space-time Twitter user trajectories at each spatial level (2) movement flows in the form of in and out movement flux between the spatial units.
-The movement flows are stored in the database for interactive explorations in the 3D web mapping interface, whereas the re-constructed trajectories can be further processed to produce distance measures at different spatial scales, which is illustrated as follows:
+A MapReduce algorithm for the spatial aggregation is implemented, where the unit ID in each spatial layer (e.g., polygon in state and country layer and cell in the rest) is treated as the key in the at the Map stage.
+It performs a ``point-in-polygon'' operation to determine which polygon the point belongs to.
+If the location does not belong to any polygon, it will be dropped, which is how we used the geographic boundaries of the conterminous United States to filer the raw tweet collection that initially covered the North America and kept the ``domestic'' ones.
+To optimize the ``point-in-polygon'' process without comparing the location with every polygon in the spatial layer, we also created a quadtree~\cite{samet1984quadtree} for each spatial layer to speed up the process.
+Finally, the reducers generate two data outputs: (1) reconstructed space-time Twitter user trajectories at each spatial level, and (2) movement flows in the form of in and out movement flux between the spatial units.
+The movement flows are stored in the database for interactive explorations via the 3D web mapping interface, whereas the re-constructed trajectories can be further processed to produce distance measures at different spatial scales, which is illustrated as follows:
 \newline
@@
 \includegraphics[width=0.6\linewidth]{./figures/multilevel}
-\caption{Hierarchical spatial layers for aggregating movements in different level-of-details.}
+\caption{Hierarchical spatial layers for aggregating movements with different level-of-details.}
 \label{fig:multilevel}
@@
 \subsection{Spatiotemporal Twitter User Mobility Patterns}
-The situation of using geo-located tweets as proxies to infer people's movements is complex as users' tweeting behavior can be significantly different from one to another, in particular, the frequency and time-interval between two consecutive tweets.
+Using geo-located tweets as proxies to infer people's movements is complex as users' tweeting behavior can be significantly different from one to another, in particular, the frequency and time-interval between two consecutive tweets.
 For example, some people may tweet once a day while others do more; some people may tweet regularly while others do not.  
@@
 Many studies have carried out data collection within a certain time period (e.g., a year in our case).
-However, as the geo-located tweets were collected in a continuous fashion, it is necessary to examine the sensitivity regarding these behaviors to ensure we are not just capturing a random snapshot from the whole data streams.
+However, as the geo-located tweets were collected in a continuous fashion, it is necessary to examine the sensitivity regarding such behavior to ensure we are not just capturing a random snapshot from the whole data streams.
 
-In this study, we have analyzed the cumulative distribution of the frequency Twitter users visiting different locations in the year 2014 (and every month), which uses the methods developed in~\cite{clauset2009power}.
+In this study, we have analyzed the cumulative distribution of the frequency of Twitter users visiting different locations in the year 2014 (and every month), which uses the methods developed in~\cite{clauset2009power}.
 The frequency is summarized based on the trajectories of individuals extracted from a monthly time span.
 Note that different groups of Twitter users may exist in each month. 
-It appears that the distribution of the collective Twitter user visitation behaviors in the year 2014 follows a two-tiered power law distributions (shown in Figure~\ref{fig:visitation}.
+It appears that the distribution of the collective Twitter user visitation behavior in the year 2014 follows a two-tiered power law distribution (shown in Figure~\ref{fig:visitation}.
 The majority (the front part) of the distribution follows a truncated power-law distribution $p(x)\sim x^{-\alpha}e^{-\lambda x}$, where $x$ is the number of visited locations and the $\alpha$ value is 1.32.
@@
 \includegraphics[width=1.0\linewidth]{./figures/visitation}
-\caption{Two-tier power law distribution of the collective Twitter user visitation behaviors.}
+\caption{Two-tier power law distribution of the collective Twitter user visitation behavior.}
 \label{fig:visitation}
@@
 As it is aforementioned, the measurements of displacements and radius of gyrations of individuals are two popular metrics to quantify the distance decay effects in the collective mobility patterns~\cite{gonzalez2008understanding}.
-In this case, we first gathered the displacements from all the collected Twitter users in the continuous United States in the year 2014, where those Twitter users with only one geo-located tweet were filtered out.
+In this case, we first gathered the displacements from all the collected Twitter users in the conterminous United States in the year 2014, where those Twitter users with only one geo-located tweet were filtered out.
 To investigate the mobility patterns of individuals, we also derived the accumulated displacements and the radius of gyrations of each individual Twitter user based on the corresponding space-time trajectories over the one year period.
-Note that both displacements and radius of gyrations were calculated by the direct great-circle distance ($d$) between two consecutively recorded locations in a user's trajectory.
+Note that both displacements and radius of gyrations were calculated based on the direct great-circle distance ($d$) between two consecutively recorded locations in a user's trajectory.
 
@@
 In addition, the displacement in the distance bound from 100 m and 80 km in Figure~\ref{fig:displacement}b can be further approximately by two power-law distributions with a cutting point at 5 km (53$\%$ distances are less than 5 km and 40$\%$ distances between 5 km and 80 km), which indicates two different travel modes, such as inter- or intra-city movements.
-Overall, the fitting functions with different distance bounds suggest the existence of multi-scale or multi-modal mobility patterns~\cite{Jurdak2015} of the Twitter users in the continuous United States, for example, the displacements larger than 80 km could be related to inter-state travels and stronger distance decay effects are observed in longer distance travels.
+Overall, the fitting functions with different distance bounds suggest the existence of multi-scale or multi-modal mobility patterns~\cite{Jurdak2015} of the Twitter users in the conterminous United States, for example, the displacements larger than 80 km could be related to inter-state travels and stronger distance decay effects are observed in longer distance travels.
 
 The probability distribution of radius of gyrations of individuals at the national level (Figure~\ref{fig:gyration}a) is approximated by $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10~m$ from [10 m, 50 m], $ P(r_{g}) \sim \beta\lambda_{2}{r_{g}}^{\beta-1}e^{-\lambda^{1}({r_{g}}^\beta-{r_{g}}_{min}^\beta)}, {r_{g}}_{min}=50~m$ from [50 m, 30 km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [$>$ 30 km].
-In particular, the radius of gyration between 50 m and 30 km can be further approximately by two power law distributions with a cutting point at 6 km (Figure~\ref{fig:gyration}b), which suggest two main types of spatial coverage of from the collected Twitter users in the continuous United States.
+In particular, the radius of gyration between 50 m and 30 km can be further approximately by two power law distributions with a cutting point at 6 km (Figure~\ref{fig:gyration}b), which suggest two main types of spatial coverage of from the collected Twitter users in the conterminous United States.
 The distribution shows that around $10\%$ the tweet population has a radius of gyration less than 50 meters, which indicates those twitter users mostly tweet at a particular place, such as home or office;  around 60$\%$ of the population has a radius of gyration less than 30 km, which indicates that most of the collected Twitter user movements are ``short'' distances, e.g., within a city locale.
@@
 \includegraphics[width=1.0\linewidth]{./figures/displacement}
-\caption{({\bf a}) The probability distribution of the collective Twitter user displacements P(d); ({\bf b}) the distance between [100 m, 80 km] is approximated by a double power-law functions; ({\bf c}) The probability distribution of the accumulated displacements of individual Twitter users P(d); ({\bf d}) The probability distribution of the accumulated displacements of individual Twitter users in 3 different months.}
+\caption{({\bf a}) The probability distribution of the collective Twitter user displacements P(d); ({\bf b}) the distance between [100 m, 80 km] is approximated by a double power-law function; ({\bf c}) The probability distribution of the accumulated displacements of individual Twitter users P(d); ({\bf d}) The probability distribution of the accumulated displacements of individual Twitter users in 3 different months.}
 
@@
 \includegraphics[width=1.0\linewidth]{./figures/gyration2}
-\caption{ ({\bf a}) The probability distribution of radius of gyration of individual Twitter users P($r_{g}$) at the national level; ({\bf b}) the distance between [50 m, 30 km] is approximated by a double power-law functions; ({\bf c}) P($r_{g}$) at the state level (Illinois and California); ({\bf d}) P($r_{g}$) for Chicago city.}
+\caption{ ({\bf a}) The probability distribution of radius of gyration of individual Twitter users P($r_{g}$) at the national level; ({\bf b}) the distance between [50 m, 30 km] is approximated by a double power-law function; ({\bf c}) P($r_{g}$) at the state level (Illinois and California); ({\bf d}) P($r_{g}$) for Chicago city.}
 \label{fig:gyration}
@@
 For example, users can perform comparative studies of Twitter user movements in different cities by simply rotating the globe. 
-More importantly, this mapping interface can be easily customized and extended to accommodate future geo-located Twitter data collection with larger spatial coverages.
+More importantly, this mapping interface can be easily customized and extended to accommodate future geo-located Twitter data collection with larger spatial coverage.
 The source code of the visual-analytics framework in this paper is available upon request.
@@
 \includegraphics[width=0.8\linewidth]{./figures/Chicago}
-\caption{The top 20$\%$ movement flows around Chicago city.}
+\caption{The top 20$\%$ movement flows around Chicago.}
 \label{fig:chicago}
@@
 \includegraphics[width=0.8\linewidth]{./figures/Chicago_airport}
-\caption{The top 20$\%$ movement flows between O'Hare International Airport and the city center of Chicago city.}
+\caption{The top 20$\%$ movement flows between the O'Hare International Airport and the city center of Chicago.}
 \label{fig:Chicago_airport}
@@
 \section{Conclusions}
-In this study, we have used large volume of geo-located tweets to study Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the continuous United States during the year 2014.
-To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-scale spatiotemporal Twitter user mobility patterns.
-This framework is implemented on high-performance distributed computing environment using Apache Hadoop.
-It provides efficiency in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
-For example, we have included an experiment for illustrating the processing time regarding generating Twitter user trajectories across different time span in the supplement material.
+In this study, we have used massive geo-located tweets to study mobility patterns of Twitter users across multi-level spatial scales and temporal ranges in the conterminous United States during the year of 2014.
+To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for exploring multi-scale spatiotemporal patterns of Twitter user mobility.
+This framework is implemented on a high-performance distributed computing environment using the Apache Hadoop.
+It achieves efficiency in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.
+For example, we have included an experiment for illustrating the processing time regarding generating Twitter user trajectories across different time spans in the supplement material.
 
-With this framework, we have found some interesting Twitter user mobility patterns, both statistically and visually.
+With this framework, interesting Twitter user mobility patterns were revealed, both statistically and visually.
 We studied the collective Twitter user visiting behavior regarding the frequency of Twitter users visiting different locations, which was fitted by a two-tier power-law distribution function.
-The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model, which has also been identified in many human mobility studies using different mobility data.
-The similarities among the cumulative distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which provides supports that we are not just capturing a random snapshot of the whole data stream.
+The two-tier power law distribution indicates that the collective behavior of Twitter users visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model, which has also been identified in many human mobility studies using different mobility data.
+The similarities among the cumulative distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which suggests that we are not just capturing a random snapshot of the whole data stream.
 
@@
 These distributions can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function.
-In particular, distance bounds between different fitting functions in displacement distribution reveals the existence of multi-scale or multi-modal mobility patterns of the Twitter users, whereas the distribution of radius of gyration reveals different groups of Twitter users with different types of spatial coverages at multiple spatial scales.
+In particular, distance bounds between different fitting functions in displacement distribution reveals the existence of multi-scale or multi-modal mobility patterns of the Twitter users, whereas the distribution of radius of gyration reveals different groups of Twitter users with different types of spatial coverage at multiple spatial scales.
 We further studied these mobility patterns in different temporal ranges to investigate the temporal changes in the mobility patterns. 
-We found that the accumulated displacements are almost identical in different months, while the long distance radius of gyration (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern.
+We found that the accumulated displacements are identical to a large degree in different months, while the long distance radius of gyration (i.e., above 30 km) will experiences more seasonal changes in the Twitter user mobility pattern.
 
 Finally, it is worth noting that at the current stage the geo-located Twitter data is not able to generalize to the entire population.
-As the demographic information of the Twitter users cannot be easily identified, the results derived in this study may not reflect a complete real-world image of human movements, which should be carefully considered in future studies.
-Nevertheless, the Twitter user movements provide clear supports to reveal the distance decay effects in human mobility research, which is observed in multiple spatial and temporal scales.
-Due to the large sample size, it is difficult to generalize the mobility pattern found at national level to entire population, city-level mobility pattern may provide better insights for investigating mobility dynamics.
-For example, the results of radius of gyration in Chicago exhibit similar pattern found in larger spatial scale, and with inputs of other mobility dataset that are often available at city-level, such as taxi trip records and mobile phone call data, there is a potential to synthesize these different sources of information and therefore provide a more complete image for understanding human mobility patterns.
-On the other hand, as we have discussed in this paper that geo-located Twitter data show the advantages regarding the easy data accessibility, the large spatial coverage and massive sample size, our approach took advantage of such data source to understand the mobility patterns across multiple spatial scales and temporal ranges.
-Also, our approach can be applied to the setting of other countries, which can be used to carry out comparative studies regarding spatiotemporal Twitter user mobility patterns.
+As the demographic information of the Twitter users cannot be easily obtained, the results produced by this study may not reflect a complete real-world image of human movements, which should further be investigated in future studies.
+Nevertheless, the Twitter user movements provide evident supports to reveal the distance decay effects in human mobility research, which is observed across multiple spatial and temporal scales.
+Due to the large sample size, it is difficult to generalize the mobility pattern found at the national level to entire population.
+But city-level mobility patterns may provide better insights into mobility dynamics.
+For example, the results of the radius of gyration in Chicago exhibit similar patterns found at larger spatial scale.
+With inputs of other mobility datasets that are often available at city-level, such as taxi trip records and mobile phone call data, there is an opportunity to synthesize these different sources of information and thus provide holistic understanding of human mobility patterns.
+On the other hand, as we have discussed in this paper that geo-located Twitter data show the advantages regarding the open data accessibility, the large spatial coverage, and massive sample size, our approach took advantage of such data source to understand the mobility patterns across multiple spatial scales and temporal ranges.
+Also, our approach can be applied to other regions, which may be used to carry out comparative studies regarding spatiotemporal patterns of Twitter user mobility.
 
@@
 \acknowledgments{
-The authors would like to thank the four anonymous reviewers of IJGI for their constructive comments that better shaped the paper.
-Junjun Yin would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
+The authors would like to thank the four anonymous reviewers of IJGI for their constructive comments that better shaped the paper, and are grateful for insightful inputs to the early stage of this research received from Yan Liu and Kiumars Soltani in the CyberInfrastructure and Geospatial Information Laboratory at the University of Illinois at Urbana-Champaign.
+This material is based in part upon work supported by the U.S.
+National Science Foundation (NSF) under grant numbers: 1354329 and 1443080.
+Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of NSF.
 Zhenhong Du would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Junjun Yin conceived and designed the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin and Zhenhong Du wrote the paper.}
+\authorcontributions{Shaowen Wang conceived the ideas; Junjun Yin and Yizhao Gao conducted the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin, Yizhao Gao, Zhenhong Du and Shaowen Wang wrote the paper.}
 
@@
 \conflictofinterests{The authors declare no conflict of interest.
-The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results.}
+The funding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results.}
 

### 2016-11-04 ijgi-148112-for proofreading/ijgi-148112-can be published_correction.tex
round 2 version 1

@@
 Regarding the concerns of infringement on individual privacy, such as the mobile phone call records with restricted access, the dataset is collected from publicly accessible Twitter data streams.
-In this paper, we employed a visual-analytics approach to studying multi-scale spatiotemporal Twitter user mobility patterns in the contiguous United States during the year 2014.
+In this paper, we employed a visual-analytics approach to studying multi-scale spatiotemporal Twitter user mobility patterns in the conterminous United States during the year 2014.
 Our approach included a scalable visual-analytics framework to deliver efficiency and scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-scale spatiotemporal user mobility patterns.
@@
 In this paper, we have employed a visual-analytics approach to exploring the Twitter user mobility patterns across multi-level spatial scales and temporal ranges in the conterminous United States (i.e., excluding Alaska and Hawaii) during the year 2014.
-The mobility data is extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from 1st January to 31st December 2014 over North America with over 6 million Twitter users and over 1 TB in file size.
-To address the data-intensive challenge embedded in this dataset, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
-This framework is implemented based on high-performance distributed computing environment using Apache Hadoop (http://hadoop.apache.org/), which is an open source software framework to enable distributed processing of large datasets across computing clusters.
-Enabled by this framework, we have performed a set of statistical analysis to understand multi-scale spatiotemporal Twitter user mobility patterns. 
-We have modeled the frequency of Twitter users visiting different locations to study the collective user visiting behaviors, where we have identified temporal similarities in the distributions.
-In particular, Twitter user mobility patterns measured by user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
-By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
+The mobility data are extracted from over 1.3 billion geo-located Twitter messages (i.e., tweets) from 1st January to 31st December 2014 over North America with over 6 million Twitter users and over 1 TB in data size.
+To handle this large volume of geo-located tweets, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets.
+This framework is implemented based on a high-performance distributed computing environment using the Apache Hadoop (http://hadoop.apache.org/, an open source software tool for distributed processing of large datasets across computing clusters).
+Enabled by this framework, we have performed a set of statistical analysis to understand multi-scale spatiotemporal patterns of Twitter user mobility, and modeled the frequency of Twitter users visiting different locations to study the collective user visiting behavior.
+
+Twitter user mobility patterns measured by user displacements and radius of gyrations of individuals~\cite{gonzalez2008understanding} have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns and multiple travel modes~\cite{Jurdak2015}.
+By further examining such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
 In addition, our approach provides an interactive 3D virtual globe web mapping interface to enable exploratory geo-visual analytics for understanding the detailed Twitter user movement flows within a given spatial scale and time window.
@@
 Section 2 describes the related work in the context of studying mobility patterns using LBSM data, in particular, the geo-located Twitter data.
-We focus on research challenges in using visual-analytics methods to enable multi-scale spatiotemporal analysis with massive movement datasets, including data management, multi-level spatiotemporal user trajectory modeling and visualization.
+We focus on research challenges in using visual-analytics methods to enable multi-scale spatiotemporal analysis of massive movement datasets, including data management, multi-level spatiotemporal user trajectory modeling and visualization.
 Section 3 details the processes for extracting, aggregating and summarizing multi-level spatiotemporal Twitter user mobility patterns.
-Section 4 presents the case study of performing visual-analytics for seeking multi-scale spatiotemporal Twitter mobility patterns in the conterminous United States of the year 2014.
+Section 4 presents the case study of performing visual-analytics for seeking multi-scale spatiotemporal Twitter mobility patterns in the conterminous United States for the year 2014.
 Section 5 concludes the paper.
@@
 
-Another approach from the literatures for studying human mobility is using mobile phone call data, such as Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with an accuracy in the order of kilometers~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
+Another approach to studying human mobility is using mobile phone call data, such as Call Detail Records (CDR), where the locations of mobile users are estimated by cell tower triangulation with accuracy in the order of kilometers~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}.
 Such a dataset can cover relatively large spatial scale~\cite{becker2013human,sobolevsky2013delineating} (e.g., national level) and a large portion of the population in the study region~\cite{kung2014exploring}.
 However, due to the concerns of infringement on individual privacy, mobile phone call data are not publicly accessible at all.
-Even such data were obtained in the mentioned studies, they came from various service providers covering different groups of users.
+Even such data were obtained in the aforementioned studies; they came from various service providers covering different groups of users.
 These issues limit the capability for conducting reproducible scientific findings for mobility research, such as validating or extending the existing discoveries.
@@
 LBSM enables users to attach their current location as a geo-tag to the message they post, which is derived from either the GPS or Wi-Fi positioning with a high position resolution down to 10 meters~\cite{Jurdak2015}.
-A Big Data scenario emerges when millions social media users constantly post messages.
+A Big Data scenario emerges when millions of social media users constantly post messages.
 In this study, geo-located Twitter data are chosen as a source for studying detailed mobility patterns.
-Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
+Twitter is one of the most popular platforms and has been actively used in many countries.
 It provides a publicly accessible streaming API for easy data access~\cite{twitterAPI}.
-Indeed, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.
 
-However, it is worth noting that there are some limitations and complexities in directly using LBSM data for studying human mobility patterns.
+However, it is worth noting that there are limitations and complexities in directly using LBSM data for studying human mobility patterns.
 For example, comparing to GPS traces, the update frequency of an individual's location varies depending on when a user is posting a new geo-located message or check-in at a new place.
@@
 Although the used methods are still arguable, these issues certainly require us to pose stricter criteria in understanding human mobility patterns using geo-located Twitter data.
-On the other hand, geo-located Twitter dataset presents some unique advantages that make it a valuable proxy for studying human mobility patterns.
+On the other hand, geo-located Twitter data present some unique advantages that make it a valuable proxy for studying human mobility patterns.
 For example, the high-resolution location information enables to identify multiple travel modes in user mobility patterns~\cite{Jurdak2015}; the large spatial coverage enables to study global mobility patterns~\cite{hawelka2014geo}, which is almost impossible for other mobility datasets.
-More importantly, by continuously monitoring the geo-located Twitter data streams with large volume of detailed and frequently updated spatiotemporal records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal gratuity (e.g., weekly, monthly, and seasonal movements), which is one of the motivations for this study.
+More importantly, by continuously monitoring the geo-located Twitter data streams with large volume of detailed and frequently updated spatiotemporal records of Twitter users, it offers a great deal of potential for studying mobility patterns of large groups of individuals at different spatial scales (e.g., movements across cities, states or even countries) and temporal granularity (e.g., weekly, monthly, and seasonal movements), which is a key motivation for this study.
 
 \subsection{Data-intensive Challenges for Multi-scale Geo-visual Analytics}
-Mobility data are essentially a collection of spatiotemporal records of people re-allocating across the geographic space.
+Human mobility data are essentially a collection of spatiotemporal records of people re-allocating across geographic space.
 To study mobility patterns of individuals, a space-time trajectory of each individual user should be modeled and constructed to quantify the collective movements over space and time.
-Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of user displacements and radius of gyrations of individuals, to study the mobility dynamics.
-Indeed, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\cite{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal ranges.
+Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of user displacements and radius of gyrations of individuals, to study mobility dynamics.
+Space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\cite{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal ranges.
 For example, a geo-visualization approach was used to study human activity patterns, where user trajectories were mapped in a 3D space ordered by timestamps in the third dimension~\cite{kwan2004geovisualization}.
@@
 In this regard, visual-analytics methods are proposed to better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\cite{andrienko2007designing,andrienko2007visual}.
-Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\cite{andrienko2007designing}.
+Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to group and divide individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\cite{andrienko2007designing}.
 Employing visual-analytics methods dealing with massive movement datasets is not only beneficial for optimizing visualizations but also provides a great deal of flexibilities for performing statistical analysis in seeking mobility patterns with different level of spatiotemporal details.
 
-However, in the context of studying mobility patterns using large volume of geo-located Twitter data, the inherited large data volume poses significant data intensive challenges for visual-analytics methods to scale with both the data volume and the computational requirements (e.g., movement extraction and trajectory modeling)~\cite{cao2014scalable}.
+However, in the context of studying mobility patterns using geo-located Twitter data, the inherent large data volume poses significant data intensive challenges for visual-analytics methods to scale with both the data volume and the computational requirements (e.g., movement extraction and trajectory modeling)~\cite{cao2014scalable}.
 In particular, in our study, 1.3 billion geo-located tweets were collected with over 1 TB in file size.
 To construct a space-time trajectory of an individual, it is necessary to go through the massive dataset to sort and update the trajectory whenever a new location is found.
-Such a task is already computationally demanding, let along breaking the trajectories to construct space-time cube with multiple spatial scale and temporal ranges.
+Such a task is already computationally demanding, let alone breaking the trajectories to construct space-time cube with multiple spatial scale and temporal ranges.
 Indeed, developing a multi-scale spatiotemporal analysis approach is identified as one of the research challenges for dealing with social media Big Data~\cite{tsou2015}.
-To address the data-intensive challenges, there is a need to develop a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
+To resolve the data-intensive challenges, there is a need to develop a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
 

### 2016-12-09 ijgi-148112-for proofreading/ijgi-148112-can be published_application.tex
have no idea

--- 2016-11-04 ijgi-148112-for proofreading/ijgi-148112-can be published_correction.tex
@@
 \makeatother 
-\articlenumber{x}
-\doinum{10.3390/------}
-\pubvolume{xx}
+\articlenumber{187}
+\doinum{10.3390/ijgi5100187}
+\pubvolume{5}
 \pubyear{2016}
@@
 \externaleditor{Academic Editors: Marguerite Madden and Wolfgang Kainz}
-\history{Received: 15 August 2016; Accepted: 28 September 2016; Published: date}
+\history{Received: 15 August 2016; Accepted: 28 September 2016; Published: 10 October 2016}
 %------------------------------------------------------------------
@@
 % Authors, for the paper (add full first names)
-\Author{Junjun Yin $^{1,2}$, Yizhao Gao $^{1,2}$, Zhenhong Du $^{2,4}$ and Shaowen Wang $^{1,2,3,*}$}
+\Author{Junjun Yin $^{1,2}$ and Zhenhong Du $^{3,*}$}
 % Authors, for metadata in PDF
-\AuthorNames{Junjun Yin, Yizhao Gao, Zhenhong Du and Shaowen Wang}
+\AuthorNames{Junjun Yin and Zhenhong Du}
 
@@
 \address{%
-$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu, ygao29@illinois.edu, shaowen@illinois.edu\\
+$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
 $^{2}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
-$^{3}$ \quad National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
-$^{4}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn}
+$^{3}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn}
 
 % Contact information of the corresponding author
-\corres{Correspondence: shaowen@illinois.edu}
+\corres{Correspondence:duzhenhong@zju.edu.cn; Tel.: +86-138-1919-2989}
 
@@
 \acknowledgments{
-The authors would like to thank the four anonymous reviewers of IJGI for their constructive comments that better shaped the paper, and are grateful for insightful inputs to the early stage of this research received from Yan Liu and Kiumars Soltani in the CyberInfrastructure and Geospatial Information Laboratory at the University of Illinois at Urbana-Champaign.
-This material is based in part upon work supported by the U.S.
-National Science Foundation (NSF) under grant numbers: 1354329 and 1443080.
-Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of NSF.
+The authors would like to thank the four anonymous reviewers of IJGI for their constructive comments that better shaped the paper.
+Junjun Yin would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
 Zhenhong Du would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Shaowen Wang conceived the ideas; Junjun Yin and Yizhao Gao conducted the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin, Yizhao Gao, Zhenhong Du and Shaowen Wang wrote the paper.}
+\authorcontributions{Junjun Yin conceived and designed the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin and Zhenhong Du wrote the paper.}
 

### 2016-12-22 semantic_decomposition_of_twitter_user_locations/paper.tex
temp
try
Speed up

@@
 % \author~\thanks{yinjunjun@gmail.com]{Junjun Yin}
-\author{Junjun Yin~\thanks{jyn@illinois.edu}}
-\affil[1]{Department of Geography and Geographic Information Science}
-\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
+\author{Junjun Yin~\thanks{jyin@psu.edu}}
+\affil[1]{Population Research Institute}
+\affil[ ]{The Pennslyvania State University, State College, 16801, PA, USA}
 \renewcommand\Authands{ and }
@@
 \section{Introduction}
+
 With the advancements in mobile technology, the location information 

### 2016-12-22 sq_mobility/sq_mobility_twitter.tex
hurry up experiments
edits
Speed up

@@
 \author[1,+]{Junjun  Yin}
-\author[1,2,+]{Myeonghun Jeong}
-\author[2,3,*]{Zhenhong Du}
-\affil[1]{Department of Geography and Geographic Information Science}
-\affil[2]{CyberGIS Center for Advanced Digitial and Spatial Studies}
-\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
-\affil[3]{Zhejiang University}
-\affil[*]{duzhenhong.zju@gmail.com}
+% \author[1,2,+]{Myeonghun Jeong}
+% \author[2,3,*]{Zhenhong Du}
+\affil[1]{Population Research Institute}
+\affil[ ]{The Pennslyvania State University, State College, PA, 16801, USA}
+% \affil[2]{CyberGIS Center for Advanced Digitial and Spatial Studies}
+% \affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
+% \affil[3]{Zhejiang University}
+% \affil[*]{duzhenhong.zju@gmail.com}
 \affil[+]{these authors contributed equally to this work}
@@
 \begin{abstract}
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
-Example Abstract.
-Abstract must be under 200 words and not include subheadings or citations.
+Location Based Social Media provides 
 \end{abstract}
@@
 
+\section*{Author contributions statement}
+J.Y. conceived the experiment(s),  J.Y. and M.J. conducted the experiment(s), J.Y., M.J. and D.Z. analysed the results.  All authors reviewed the manuscript.
+
 \bibliography{ref}

### 2016-12-27 semantic_decomposition_of_twitter_user_locations/paper.tex
test

@@
-\documentclass[a4paper,11pt]{article}
+\documentclass[a4paper, 11pt]{article}
+\usepackage{authblk}
+\usepackage[round, sort, numbers, authoryear]{natbib}
+\usepackage{regexpatch}
+\usepackage{graphicx}
+\graphicspath{ {/figures/} }
+\usepackage[section]{placeins}
+\usepackage{setspace}
 \usepackage[margin=1in]{geometry}
-\usepackage{lastpage,fancyhdr,graphicx}
-\graphicspath{ {/figure/} }
-\usepackage{authblk}
+\usepackage[]{algorithm2e}
+\usepackage{caption}
+\usepackage{subcaption}
+\date{}
+
+\usepackage{lineno}
 
@@
 % \author~\thanks{yinjunjun@gmail.com]{Junjun Yin}
-\author{Junjun Yin~\thanks{jyin@psu.edu}}
+\author[1,~\thanks{Corresponding author: jyin@psu.edu}]{Junjun Yin}
 \affil[1]{Population Research Institute}
-\affil[ ]{The Pennslyvania State University, State College, 16801, PA, USA}
+\affil[ ]{The Pennsylvania State University, State College, 16801, PA, USA}
 \renewcommand\Authands{ and }
@@
 Today's pervasive Location Based Social Media provide abundant user-generated geographic information
-In this paper, we present a geographical information system (GIS) based data synthesis approch to understanding semantic decompositions of Twitter user locations.
+In this paper, we present a geographical information system (GIS) based data synthesis approche to understanding semantic decompositions of Twitter user locations.
 Specifically, we implemented a
@@
 \section{Introduction}
+
+xx~\citep{yin2016exploring}
 
@@
 \section{Methods and Materials}
+
 \subsection{Geo-located Twitter Data}
@@
 \bibliography{ref}
-
 \end{document}

### 2017-01-11 MovePattern_IJGI/ijgi-148112-for proofreading/oo.tex
Clean up

--- 2016-10-17 ijgi-148112-for proofreading/ijgi-148112-can be published_origin.tex
@@
 Compared to other LBSM platforms, Twitter is one of the most popular platforms and is been actively used in many countries.
-It provides a publicly accessible streaming API for easy data access~\cite{twitterAPI}.
+It provides a publicly accessible streaming API (https://dev.twitter.com/streaming/overview) for easy data access.
 Indeed, many other LBSM data can be collected from the data streams, such as Foursquare check-in data~\cite{cranshaw2012livehoods,hasan2013understanding}.
@@
 In particular, this data collection of the year 2014 was originally used to map the spatial spread of flu in North America during the time period~\cite{padmanabhan2014flumapper}.
-As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages in the dataset~\cite{black2012twitter}; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
+
+As a social media account is not equal to a real person in the physical world~\cite{tsou2015}, to ensure the data quality, the collected raw tweets were further filtered by the following steps: We first removed duplicated messages (https://support.twitter.com/articles/18311-the-twitter-rules) in the dataset; and then we removed non-human users based on the heuristic of unusual relocating speed discussed in~\cite{hawelka2014geo,Jurdak2015}.
 In this case, we adopted the speed limit value as 240 m/s used in~\cite{Jurdak2015}, where we examined all the consecutive locations of each user and excluded those with relocating speed over the limit.
@@
 We tested the overall distribution of the movement flows (in the form of weighted in-degree and out-degree of a graph, where each state is treated as a node) among different states in the year 2014.
-We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states (Figure~\ref{fig:state_flow}).
+We found that the probability distribution of Twitter user movement flows of visiting different states follows a log-normal distribution: $p(x)\sim \frac{1}{x}exp[-\frac{(lnx - \mu)^{2}}{2\sigma^{2}}]$, which suggests the flux of Twitter user movements among the states are highly skewed and dominated by a few states.
 It indicates that the Twitter population is not proportional to account the movement flux between the states, which may provide some insights for other researchers in studying social-economical aspects of the migration dynamics.
@@
 \newblock Understanding mobility based on GPS data.
-\newblock  Proceedings of the 10th international conference on Ubiquitous
-  computing. ACM,  2008, pp. 312--321.
+\newblock  In Proceedings of the 10th International Conference on Ubiquitous
+  Computing, Seoul, South Korea, 21--24 September 2008.
 
@@
 \newblock Characterizing the human mobility pattern in a large street network.
-\newblock {\em Physical Review E} {\bf 2009}, {\em 80},~021136.
+\newblock {\em Phys. Rev. E} {\bf 2009}, doi:10.1103/PhysRevE.80.021136.
 
@@
   diseases.
-\newblock {\em Physical Review X} {\bf 2011}, {\em 1},~011001.
+\newblock {\em Phys. Rev. X} {\bf 2011}, doi:10.1103/PhysRevX.1.011001.
 
@@
 \newblock Human migration: Theory, models, and empirical studies.
-\newblock {\em Journal of regional Science} {\bf 1985}, {\em 25},~521--544.
+\newblock {\em J. Reg. Sci.} {\bf 1985}, {\em 25},~521--544.
 
@@
 Jurdak, R.; Zhao, K.; Liu, J.; AbouJaoude, M.; Cameron, M.; Newth, D.
-\newblock Understanding Human Mobility from Twitter.
-\newblock {\em PLoS ONE} {\bf 2015}, {\em 10},~e0131469.
+\newblock Understanding human mobility from twitter.
+\newblock {\em PLoS One} {\bf 2015}, doi:10.1371/journal.pone.0131469.
 
@@
 \newblock On the levy-walk nature of human mobility.
-\newblock {\em IEEE/ACM transactions on networking (TON)} {\bf 2011}, {\em
+\newblock {\em IEEE/ACM Trans. Netw.} {\bf 2011}, {\em
   19},~630--643.
@@
   data of mobile networks.
-\newblock {\em Journal of Urban Technology} {\bf 2010}, {\em 17},~41--60.
+\newblock {\em J. Urban Technol.} {\bf 2010}, {\em 17},~41--60.
 
@@
   phone data.
-\newblock {\em PloS one} {\bf 2014}, {\em 9},~e96180.
+\newblock {\em PloS One} {\bf 2014}, doi:10.1371/journal.pone.0096180.
 
@@
   of spatial big data.
-\newblock {\em International Journal of Communication} {\bf 2014}, {\em
+\newblock {\em Int. J. Commun.} {\bf 2014}, {\em
   8},~1765--1783.
@@
 \newblock Geo-located Twitter as proxy for global mobility patterns.
-\newblock {\em Cartography and Geographic Information Science} {\bf 2014}, {\em
+\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2014}, {\em
   41},~260--271.
@@
 Giannotti, F.; Pedreschi, D.
-\newblock {\em Mobility, data mining and privacy: Geographic knowledge
-  discovery}; Springer Science \& Business Media,  2008.
+\newblock {\em Mobility, Data Mining and Privacy: Geographic Knowledge
+  Discovery}; Springer Science \& Business Media: Berlin, Germany,  2008.
 
@@
 Crampton, J.W.
-\newblock Collect it all: national security, Big Data and governance.
-\newblock {\em GeoJournal} {\bf 2014}, pp. 1--13.
+\newblock Collect it all: National security, Big Data and governance.
+\newblock {\em GeoJournal} {\bf 2014}, {\em 9}, 1--13.
 
@@
   social media check-in data.
-\newblock {\em PloS one} {\bf 2014}, {\em 9},~e97010.
+\newblock {\em PLoS one} {\bf 2014}, doi:10.1371/journal.pone.0097010.
 
@@
   large-scale location-based data from online social media.
-\newblock  Proceedings of the 2nd ACM SIGKDD international workshop on urban
-  computing. ACM,  2013, p.~6.
+\newblock  In Proceedings of the 2nd ACM SIGKDD International Workshop on Urban
+  Computing, Chicago, IL, USA, 11--14 August 2013.
 
@@
 Cho, E.; Myers, S.A.; Leskovec, J.
-\newblock Friendship and mobility: user movement in location-based social
+\newblock Friendship and mobility: User movement in location-based social
   networks.
-\newblock  Proceedings of the 17th ACM SIGKDD international conference on
-  Knowledge discovery and data mining. ACM,  2011, pp. 1082--1090.
+\newblock  In Proceedings of the 17th ACM SIGKDD International Conference on
+  Knowledge Discovery and Data Mining, San Diego, CA, USA, 21--24 August 2011.
 
@@
 Noulas, A.; Scellato, S.; Lambiotte, R.; Pontil, M.; Mascolo, C.
-\newblock A tale of many cities: universal patterns in human urban mobility.
-\newblock {\em PloS one} {\bf 2012}, {\em 7},~e37027.
+\newblock A tale of many cities: Universal patterns in human urban mobility.
+\newblock {\em PLoS One} {\bf 2012}, doi:10.1371/journal.pone.0037027.
 
@@
   diseases.
-\newblock {\em Proceedings of the National Academy of Sciences} {\bf 2009},
+\newblock {\em Proc. Nat. Acad. Sci.} {\bf 2009},
   {\em 106},~21484--21489.
@@
 Tamerius, J.; Nelson, M.I.; Zhou, S.Z.; Viboud, C.; Miller, M.A.; Alonso, W.J.
-\newblock Global influenza seasonality: reconciling patterns across temperate
+\newblock Global influenza seasonality: Reconciling patterns across temperate
   and tropical regions.
-\newblock {\em Environmental health perspectives} {\bf 2011}, {\em 119},~439.
+\newblock {\em Environ. Health Perspect.} {\bf 2011}, {\em 119},~439--445.
 
@@
   Data.
-\newblock {\em Cartography and Geographic Information Science} {\bf 2015}, {\em
+\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2015}, {\em
   42},~70--74.
@@
 Zheng, Y.; Xie, X.; Ma, W.Y.
-\newblock GeoLife: A Collaborative Social Networking Service among User,
-  Location and Trajectory. {\bf 2010}.
+\newblock GeoLife: A collaborative social networking service among user,
+  location and trajectory. {\em IEEE Data(base) Eng. Bulletin} {\bf 2010}, {\em 33}, 32--39.
 
@@
 \newblock Human mobility characterization from cellular network data.
-\newblock {\em Communications of the ACM} {\bf 2013}, {\em 56},~74--82.
+\newblock {\em Commun. ACM} {\bf 2013}, {\em 56},~74--82.
 
@@
   in an extensive set of countries.
-\newblock {\em PLoS One} {\bf 2013}, {\em 8},~e81707.
-
-\bibitem[Twitter(2016)]{twitterAPI}
-Twitter.
-\newblock Twitter streaming API.
-\newblock {\em available from: https://dev.twitter.com/streaming/overview} {\bf
-  2016}.
+\newblock {\em PLoS One} {\bf 2013}, doi:10.1371/journal.pone.0081707.
 
@@
 Cranshaw, J.; Schwartz, R.; Hong, J.I.; Sadeh, N.M.
-\newblock The Livehoods Project: Utilizing Social Media to Understand the
-  Dynamics of a City.
-\newblock  ICWSM,  2012.
+\newblock The livehoods project: Utilizing social media to understand the
+  dynamics of a city.
+\newblock  In Proceedings of the ICWSM 2012, Dublin, Ireland, 4--8 June 2012.
 
@@
 \newblock The geography of happiness: Connecting twitter sentiment and
-  expression, demographics, and objective characteristics of place {\bf 2013}.
+  expression, demographics, and objective characteristics of place. {\em PLoS One} {\bf 2013}, doi:10.1371/journal.pone.0064417.
 
@@
   et~al.]{longley2015geotemporal}
-Longley, P.A.; Adnan, M.; Lansley, G.; others.
+Longley, P.A.; Adnan, M.; Lansley, G.
 \newblock The geotemporal demographics of Twitter usage.
-\newblock {\em Environment and Planning A} {\bf 2015}, {\em 47},~465--484.
+\newblock {\em Environ. Plan. A} {\bf 2015}, {\em 47},~465--484.
 
@@
   et~al.]{hagerstrand1985time}
-H{\"a}gerstrand, T.; others.
-\newblock Time-geography: focus on the corporeality of man, society, and
+H{\"a}gerstrand, T.
+\newblock Time-geography: Focus on the corporeality of man, society, and
   environment.
-\newblock {\em The science and praxis of complexity} {\bf 1985}, pp. 193--216.
+\newblock In {\em The Science and Praxis of Complexity}; United Nations University: Montpellier, France, 1985; pp. 193--216.
 
@@
 Kwan, M.P.; Lee, J.
-\newblock Geovisualization of human activity patterns using 3D GIS: a
-  time-geographic approach.
-\newblock {\em Spatially integrated social science} {\bf 2004}, {\em 27}.
+\newblock Geovisualization of human activity patterns using 3D GIS: A
+  time-geographic approach. In 
+\newblock {\em Spatially Integrated Social Science: Examples in Best Practice}; Michael, F.G., Donald, G.J. Eds.; Oxford University Press: Oxford, MI, USA, 2003; Volume 3, pp. 27--51.
 
@@
   movement data.
-\newblock {\em Cartographica: The International Journal for Geographic
-  Information and Geovisualization} {\bf 2007}, {\em 42},~117--138.
+\newblock {\em Cartogr. Int. J. Geogr.
+  Inf. Geovis.} {\bf 2007}, {\em 42},~117--138.
 
@@
 \newblock Research challenges in geovisualization.
-\newblock {\em Cartography and Geographic Information Science} {\bf 2001}, {\em
+\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2001}, {\em
   28},~3--12.
@@
 MacEachren, A.M.
-\newblock {\em How maps work: representation, visualization, and design};
-  Guilford Press,  2004.
+\newblock {\em How Maps Work: Representation, Visualization, and Design};
+  Guilford Press: New York, NY, USA, 2004.
 
@@
 \newblock Visual analytics tools for analysis of movement data.
-\newblock {\em ACM SIGKDD Explorations Newsletter} {\bf 2007}, {\em 9},~38--46.
+\newblock {\em ACM SIGKDD Explor. Newsl.} {\bf 2007}, {\em 9},~38--46.
 
@@
   social media data.
-\newblock {\em Computers, Environment and Urban Systems} {\bf 2015}, {\em
-  51},~70--82.
+\newblock {\em Comput. Environ. Urban Syst.} {\bf 2015}, {\em 51}, 70--82.
 
@@
   location-based social media.
-\newblock {\em Concurrency and Computation: Practice and Experience} {\bf
-  2014}.
-
-\bibitem[Black \em{et~al.}(2012)Black, Mascaro, Gallagher, and
-  Goggins]{black2012twitter}
-Black, A.; Mascaro, C.; Gallagher, M.; Goggins, S.P.
-\newblock Twitter zombie: Architecture for capturing, socially transforming and
-  analyzing the Twittersphere.
-\newblock  Proceedings of the 17th ACM international conference on Supporting
-  group work. ACM,  2012, pp. 229--238.
+\newblock {\em Concurr. Comput. Pract. Exp.} {\bf
+  2014}, doi:10.1002/cpe.3287.
 
@@
 \newblock The hadoop distributed file system.
-\newblock  Mass Storage Systems and Technologies (MSST), 2010 IEEE 26th
-  Symposium on. IEEE,  2010, pp. 1--10.
+\newblock  {\em Mass Storage Syst. Technol.}  {\bf 2010}, doi:10.1109/MSST.2010.5496972.
 
@@
 Dean, J.; Ghemawat, S.
-\newblock MapReduce: simplified data processing on large clusters.
-\newblock {\em Communications of the ACM} {\bf 2008}, {\em 51},~107--113.
+\newblock MapReduce: Simplified data processing on large clusters.
+\newblock {\em Commun. ACM} {\bf 2008}, {\em 51},~107--113.
 
@@
 Gao, H.; Tang, J.; Liu, H.
-\newblock Exploring Social-Historical Ties on Location-Based Social Networks.
-\newblock  ICWSM,  2012.
+\newblock Exploring social-historical ties on location-based social networks.
+\newblock In Proceedings of the ICWSM 2012, Dublin, Ireland, 4--8 June 2012.
 
@@
 Buttenfield, B.P.; McMaster, R.B.
-\newblock {\em Map Generalization: Making rules for knowledge representation};
-  Longman Scientific \& Technical New York,  1991.
+\newblock {\em Map Generalization: Making Rules for Knowledge Representation};
+  Longman Scientific \& Technical: New York, NY, USA, 1991.
 
@@
 \newblock The quadtree and related hierarchical data structures.
-\newblock {\em ACM Computing Surveys (CSUR)} {\bf 1984}, {\em 16},~187--260.
+\newblock {\em ACM Comput. Surv. (CSUR)} {\bf 1984}, {\em 16},~187--260.
 
@@
 \newblock Power-law distributions in empirical data.
-\newblock {\em SIAM review} {\bf 2009}, {\em 51},~661--703.
+\newblock {\em SIAM Rev.} {\bf 2009}, {\em 51},~661--703.
 
@@
   collection when correlated random walks embody observed movement patterns.
-\newblock {\em Journal of The Royal Society Interface} {\bf 2012}, {\em
+\newblock {\em J. Royal Soc. Int.} {\bf 2012}, {\em
   9},~528--534.
@@
   transportation modality decomposition.
-\newblock {\em Scientific reports} {\bf 2015}, {\em 5}.
+\newblock {\em Sci. Rep.} {\bf 2015}, doi:10.1038/srep09136.
 
@@
   education.
-\newblock {\em Concurrency and Computation: Practice and Experience} {\bf
-  2014}.
+\newblock {\em Sci. Gatew. Workshops 2013} {\bf
+  2014}, doi:10.1002/cpe.3256.
 

### 2017-01-11 urban_spatial_interaction/urban_boundaries_gb/Twitter_Urban_Boundary.edits.tex
Clean up

--- 2016-01-16 urban_boundaries_gb/Twitter_Urban_Boundary.edits.tex
@@
 \end{flushleft}
-% Please keep the abstract below 300 words
 \section*{Abstract}
@@
 We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
-The result of strongly connected urban regions, or communities, in the network space yield geographically cohesive, non-overlapping urban areas that delineate the non-administrative anthropographic urban boundaries of Great Britain.
-The technique was applied at the national scale (Great Britain) and the municipal scale (the London metropolis). 
+The result of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas that provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
+The technique was applied to both national scale (Great Britain) and municipal scale (the London metropolis). 
 While our results corresponded well to the administrative boundaries, many unexpected and interesting boundaries were identified.
@@
 Urban environments are conceptualized as spaces that are recreated and formed by human activities~\cite{schliephake}.
-A fundamental question when using the administrative, ``top-down'', approach for defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
-These interactions can take the form of trade, commerce, social connections, and political activity.
+A fundamental question when using the administrative, ``top-down'', approach to defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
+These interactions can take the form of trade, commerce, social connections, and political activity across the borders.
 Urban boundaries that respect the human interaction space can be very import to city planning, traffic management and resource allocation~\cite{lynch1960,jiang2015,liu2015,long2015}.
-Many studies adopt a ``bottom-up'' approach to urban boundary delineation; where the geographic space is partitioned into small units and each unit is modeled as a node within a network structure.
+Many studies adopt a ``bottom-up'' approach to urban boundary delineation, where the geographic space is partitioned into small units and each unit is modeled as a node within a network structure.
 A suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interaction among the nodes~\cite{lancichinetti2009}.
 Different social and physical human interactions were considered to establish the edges of the network connecting the nodes.
-For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in the United Kingdom~\cite{ratti2010}.
-% does ratti or sobolevsky argue the following... who are "the authors"?
-Extending the previous method to different countries~\cite{sobolevsky2013}, the authors argue, yields cohesive geographic divisions that mark the socio-economic boundaries. 
-% I think these citations should expand to include the author's names, not just [9].
-While~\cite{kallus2015} use social ties of Twitter users to identify cohesive regions for different countries across the world, the authors found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.
+For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in Great Britain~\cite{ratti2010}.
+Extending the previous method to different countries~\cite{sobolevsky2013}, the authors argue that this method yields cohesive geographic divisions that follow the socio-economic boundaries.
+While other researchers use social ties of Twitter users to identify cohesive regions for different countries across the world~\cite{kallus2015}, they found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.
 
-In this study, we describe a novel approach to delineate urban boundaries based on the movements of 
+In this study, we describe a novel approach to delineating urban boundaries based on the movements of 
 Twitter users extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
@@
 We argue here that Twitter user mobility patterns provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation. 
-A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in the United Kingdom.
-In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity 
-% I think UK calls them postal codes and not zip codes
-that is limited to the postal code level~\cite{thiemann}.  % everything has sparsity at some scale...
+A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in Great Britain.
+In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity that is limited to the postal code level~\cite{thiemann}.
 
-We delineated the geography of urban boundaries in the United Kingdom by imposing a virtual fishnet over the British Isles. % Great Britain is, itself, an island.
+We delineated the geography of urban boundaries in Great Britain by imposing a virtual fishnet over the islands of Great Britain.
 Twitter user movements were used to establish the connections between the fishnet's cells to form a connectivity network, where each cell acts as a node within the network.
@@
 The map equation algorithm was selected to avoid the inherent resolution problem~\cite{fortunato2007} of the common modularity maximization method~\cite{newman2006}. 
-We found that the collective mobility patterns of Twitter users in the United Kingdom are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points.
-The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in the United Kingdom.
+We found that the collective mobility patterns of Twitter users in Great Britain are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points.
+The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of the urban space in Great Britain.
 Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. 
-It provides a new understanding of the interaction between human activity and urban structures.
+It provides a new understanding of the interactions between human activity and urban structures.
 
@@
 This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two recorded locations is one month.
-To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the British Isles.
+To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the islands of Great Britain.
 Twitter user movements were then used to establish the connectivity between fishnet cells to form a connectivity network where each cell is considered a node within the network. 
-Finally, by detecting strongly connected clusters in the network space using community detection methods~\cite{coscia2011}, we are able to reveal urban boundaries within the geographic space. 
+Finally, by detecting strongly connected clusters in the network space using community detection methods~\cite{coscia2011}, we were able to reveal urban boundaries within the geographic space. 
 An overview of the approach is illustrated in Fig.~\ref{S1_Fig} and the details are presented in the following sections.
@@
 For this study, geo-located tweets were collected using the Twitter Streaming API (\url{https://dev.twitter.com/streaming/overview}) by supplying a geographical bounding box to retrieve all the  geo-located tweets within an area of interest.
-% is it the entire UK or the British Isles? It is not Great Britain.
-To ensure complete coverage of the United Kingdom, we set the bounding box to the British Isles using the lower left and upper right coordinates (49.497, -14.854), (61.186, 2.637) respectively.
-This does include part of France.
-% ireland is part of the british isles
-We implemented a data crawler to continuously collect 7-months of data (June $1^{st}$ -- December $31^{st}$, 2014) resulting in over 101.8 million tweets with a total data volume of 60 GB which we restrict to 69 million based on a process outlined below.
+To ensure complete coverage of Great Britain, we set the bounding box to the British Isles using the lower left and upper right coordinates (49.497, -14.854), (61.186, 2.637) respectively.
+This does include the whole of Ireland part of France.
+We implemented a data crawler to continuously collect 7-months of data (June $1^{st}$ -- December $31^{st}$, 2014) resulting in over 101.8 million tweets with a total data volume of 60 GB, which we restrict to 69 million based on a process outlined below.
 To showcase the overall spatial coverage of the collected geo-located tweets, a density map of the tweet locations in British Isles for July 2014 is shown in Fig.~\ref{S2_Fig}.
-The collected point visualization reveals the geography of cities. Notice the clusters with higher densities of tweets that correspond to the locations of major cities.
+The collected point visualization reveals the geography of cities.
+Notice the clusters with higher densities of tweets correspond to the locations of major cities.
 
@@
 Because the original location information embedded in the geo-tag is given in units of latitude and longitude, we projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations.
-Finally, we used the geographical boundary of the United Kingdom, which is derived from Office for National Statistics (ONS) of UK (\url{http://www.ons.gov.uk/ons}), to further restrict the remaining tweets to be ``domestic".
+Finally, we used the geographical boundary of Great Britain, which is derived from Office for National Statistics (ONS) of UK (\url{http://www.ons.gov.uk/ons}), to further restrict the remaining tweets to be ``domestic".
 Based on these restrictions, the filtered dataset for the following study contains 69,847,497 tweets made by 1,153,891 twitter users.
@@
 Some urban regions are more strongly connected to each other than other urban regions.
-Therefore, this study connects urban regions when a twitter user begins in one region and ends in another region.
-These connections can be represented by an origin-destination (OD) matrix based on the collective Twitter user displacement within the dataset.
-This OD matrix is essentially a mathematical representation of a weighted directed graph $G\equiv\langle V, E_{w}\rangle$ where $V$ is a set of spatial nodes corresponding to the underlying urban regions and $E_{w}$ is a set of edges representing the connections between a pair of nodes and the corresponding weights that are assigned to the accumulated volume of Twitter user movement.
+Therefore, this study connects urban regions when a twitter user's movement begins in one region and ends in another region.
+These connections can be represented by an origin-destination (OD) matrix based on the collective Twitter user displacements within the dataset.
+This OD matrix is essentially a mathematical representation of a weighted directed graph $G\equiv\langle V, E_{w}\rangle$, where $V$ is a set of spatial nodes corresponding to the underlying urban regions and $E_{w}$ is a set of edges representing the connections between a pair of nodes and the corresponding weights are assigned by the accumulated volume of Twitter user movements.
 
-To build our spatial network at the kingdom level, we had to determine the basic units to serve as spatial nodes of the connectivity network of urban regions.
+To build our spatial network at a national level, we had to determine the basic units to serve as spatial nodes of the connectivity network of urban regions.
 Previous studies have suggested equi-distant spatial tessellation to generate nodes, which uses voronoi polygons to partition the space based on the collected points~\cite{rinzivillo2012,zhong2014}. 
@@
 These patterns include: the number of visited locations per user,  the collective user displacements, and the radius of gyration of individuals in order to identify natural breaks in user travel patterns.
-We then used these natural breaks within the mobility patterns to partition the geographic space of the United Kingdom into fine-grained cells and established the connectivity among these cells to redraw non-administrative anthropographic urban boundaries.
+We then used these natural breaks within the mobility patterns to partition the geographic space of Great Britain into fine-grained cells and established the connectivity among these cells to redraw non-administrative anthropographic urban boundaries.
 
@@
 For example, the region of Wales appears to consist of three communities as found in the connectivity of both phone calls and long distance movements. 
-However, the regions extracted from the mobility network seems to be more spatially consistent with minimal spatial gaps compared to the partitions extracted from land-line call networks in the United Kingcom~\cite{ratti2010}.
+However, the regions extracted from the mobility network seems to be more spatially consistent with minimal spatial gaps compared to the partitions extracted from land-line call networks in Great Britain~\cite{ratti2010}.
 
@@
 \section*{Conclusion}
-In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
-In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the British Isles to partition the space.
-Then by studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell size of 10 km to quantify the spatial coverage of the majority of Twitter users in the United Kingdom.
+In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
+In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the islands of Great Britain to partition the space.
+By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell size of 10 km to quantify the spatial coverage of the majority of Twitter users in Great Britain.
 Twitter user movements were used to establish a connectivity network of the fishnet cells.
 Then we applied the map equation algorithm to partition the network and associated geographic regions.
-The strongly connected communities within the network space yields geographically cohesive, non-overlapping urban areas that provides a clear delineation of the urban boundaries of the United Kingdom.
-By performing a statistical analysis of Twitter user mobility patterns in the United Kingdom, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
+The strongly connected communities within the network space yields geographically cohesive, non-overlapping urban areas that provides a clear delineation of the urban boundaries in Great Britain.
+By performing a statistical analysis of Twitter user mobility patterns in Great Britain, in particular the distribution of collective Twitter user displacements, we found multi-scale and multi-modal urban movements that were divided into several distance ranges starting from short intra-city to inter-city movements with clear destination points.
 Identifying the connected regions at each of these distance ranges yielded hierarchical boundaries of  the urban space in Great Britain.
 
-The use of Twitter user mobility to delineate non-administrative anthropographic boundaries enables the researcher to redraw the city at different mobility ranges.
+The power of using Twitter user mobility to delineate non-administrative anthropographic boundaries is the ability to redraw the city at different mobility ranges inferred objectively from the collective mobility patterns.
 Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect the human interaction space.
-This study defines non-administrative anthropographic boundaries by investigating human mobility, which could assist in resource allocation, political campaigns and urban planning.
+This study provides a first step in connecting human mobility research with defining non-administrative anthropographic boundaries, which could assist in resource allocation, political campaigns and urban planning.
 However, the geo-located twitter data is not able to generalize to the entire population; therefore, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
@@
 \section*{Acknowledgments}
-The authors would like to thank Dr. Kun Zhao and Dr. Raja Jurdak from CSIRO, Australia for their suggestions in generating Figure 1 in this paper. 
+The authors would like to thank Dr. Kun Zhao and Dr. Raja Jurdak from CSIRO, Australia for their suggestions in generating Figure 4 in this paper.
 The research was supported from National Science Foundation grants No. xx ...
@@
 \bibitem{kallus2015}
-Kallus Z, Barankai N, Szüle J, Vattay G., 2015 Spatial Fingerprints of Community Structure in Human Interaction Network for an Extensive Set of Large-Scale Regions.
+Kallus Z, Barankai N, Szüle J, Vattay G., 2015.
+Spatial Fingerprints of Community Structure in Human Interaction Network for an Extensive Set of Large-Scale Regions.
 PLoS ONE 10(5): e0126713.

### 2017-01-11 urban_spatial_interaction/urban_boundaries_gb_IJGIS/IJGIS/Paper_version_1.tex
Clean up

--- 2016-08-02 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
@@
 \articletype{RESEARCH ARTICLE}
+
+%\title{{\itshape The geography of urban boundaries in Great Britain from the mobility network of Twitter user spatial interactions} }
+%\title{{\itshape Depict the geography of urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data} }
 \title{{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data} }
@@
 \begin{abstract}
-Existing urban boundaries are usually defined by government agencies for political and administrative purposes.
-However, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter-regional activities.
-Defining urban boundaries which consider socio-economic relationships and citizen commute patterns is important for many aspects of urban planning.
-In this study, we presented a method to redraw urban boundaries based upon human interactions with the physical space.
-Specifically, we depicted the urban boundaries of Great Britain using a mobility network of Twitter user spatial interactions that was inferred from over 69 million geo-located Twitter messages.
+Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter-regional activities.
+Defining urban boundaries with considerations of socio-economic relationships and citizen commute patterns is important for many aspects in urban planning.
+In this study, we presented a method to redraw urban boundaries based upon human interaction with the physical space.
+Specifically, we depicted the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million geo-located Twitter messages.
 We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
@@
 
-A common outcome observed in the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
-A general consensus is that those geographically cohesive areas are instances of the effects on spatial proximity, where the interaction strength between two urban regions decreases as the geographical distance between them increases~\citep{fotheringham1981}.
+A common outcome observed from the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
+The general consensus is that those geographically cohesive areas are instances of spatial proximity effects, where the interaction strength between two urban regions decreases as the geographical distance between them increases~\citep{fotheringham1981}.
 In particular, spatial proximity is closely related to Tobler's First Law of Geography: ``\textit{everything is related to everything else, but near things are more related than distant things}''~\citep{miller2004}.
-While it is perhaps intuitively logical, few research efforts, which seek to quantitatively understand and explain how the spatial interactions shape the forms of connected geographical areas (i.e., urban boundaries), have been carried out.
+While it is intuitively logical, few research efforts were further carried out to quantitatively understand and explain how the spatial interactions shape the forms of connected geographical areas (i.e., urban boundaries).
 One of the major reasons is that geographical distance may affect the interaction strength, it is not an explicitly expressed constraint in the ``virtual'' human interactions, such as social ties or phone call initiation.
@@
 The well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas. 
-Our study provides a first-step in connecting human mobility research with the delineation of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. 
-This provides a new understanding of the interactions between human activities and urban space.
+Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. 
+This provides a new understanding of the interactions between human activity and urban structures.
 
@@
 \section{Materials and Methods}
+%\subsection{Overview}
+%In this research, we use large-scale Twitter user spatial interactions inferred from the collective mobility patterns of Twitter users to delineate urban boundaries in Great Britain.
+%A Twitter user's movement is defined here as the individual's geographic relocation or displacement~\citep{gonzalez2008}.
+%This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two consecutive recorded locations is one month.
+%To identify the clusters of urban regional connectedness using large-scale Twitter data, we first imposed a virtual fishnet over the islands of Great Britain.
+%Twitter user movements were then used to establish the connectivity between fishnet cells to form a connectivity network where each cell is considered a node within the network. 
+%Finally, by detecting strongly connected clusters in the network space using community detection methods~\citep{coscia2011}, we were able to reveal urban boundaries within the geographic space. 
+%An overview of the approach is illustrated in Fig.~\ref{S1_Fig} and the details are presented in the following sections. 
+%
+%\begin{figure}[ht]
+%\begin{center}
+%\includegraphics[width=1\linewidth]{./figure/S1_overview_Fig_2}
+%\caption{\bfseries{An overview for delineating urban boundaries from Twitter user movements}}
+%\label{S1_Fig}
+%\end{center}
+%\end{figure}
+
 \subsection{Geo-located Twitter Data and Data Processing}
@@
 \end{figure}
-The original location information embedded in the geo-tag is given in units of latitude and longitude.
-We examined the \textit{``geo"} attribute in each raw tweet and kept the one with location information derived from GPS receiver (with high resolution) rather than from geocoding process~\citep{jurdak2015}.
-We projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations. 
+Because the original location information embedded in the geo-tag is given in units of latitude and longitude, we projected the points into the British National Grid (EPSG: 27700) coordinate system to reduce the complexity of the required distance calculations.
 We used the geographical boundary of Great Britain, which is derived from Office for National Statistics (ONS) of UK ({\tt{http://www.ons.gov.uk/ons}}), to further restrict the remaining tweets to be ``domestic".
@@
 To reduce the effects of tweets from non-human users, the raw tweets were further filtered using the following steps.
-First we removed the duplicated messages from the dataset.
+First we removed the duplicated messages in the dataset.
 We then removed non-human users based on unusual relocation speed \citep{hawelka,jurdak2015}. 
-We then examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold of 240 m/s as used by \citep{jurdak2015}.
+We examined all of the consecutive locations of each user and excluded those with relocating speeds in excess of the threshold of 240 m/s as used by \citep{jurdak2015}.
 Finally, to reflect the spatial interactions of residents rather than tourists, we further impose a condition that the time interval between a user's first and last recorded tweets should be more than 30 days.
@@
 This is not equivalent to a ``trip" taken by an individual, because, displacement includes situations when the time interval between two consecutive recorded locations is one month.
-To identify the clusters of urban regional connectedness, Twitter user movements are used to establish a connectivity network, where two urban regions connect when a Twitter user's movement begins in one and ends in another.
+To identify the clusters of urban regional connectedness, Twitter user movements are used to establish a connectivity network, where two urban region connects when a twitter user's movement begins in one and ends in another.
 These connections can be represented by an origin-destination (OD) matrix based on the collective Twitter user displacements within the dataset.
@@
 However, equi-distant tessellation decreases the spatial resolution of aggregated geo-located tweets, because the location information is usually derived from the embedded GPS within mobile devices and tends to provide greater accuracy~\citep{sakaki2010,zandbergen2009}.
-Another approach is to partition the space into a grid of spatial pixels~\citep{liuPopMobility,ratti2010}.
+Another popular approach is to partition the space into a grid of spatial pixels~\citep{liuPopMobility,ratti2010}.
 However, the size of the cell can potentially lead to biases due to the Modifiable Area Unit Problem (MAUP)~\citep{openshaw1984,wong2009}, where different choices of unit size can lead to significant variant findings.
 To compare our investigation with the findings of similar studies, and avoid subjectively deciding the cell size, we performed statistical analysis of Twitter user mobility patterns in Great Britain and measured the distribution of collective Twitter user displacements and the radius of gyrations of individuals \citep{gonzalez2008,jurdak2015}.
-The radius of gyration is a metric to distinguish mobility patterns of individuals~\citep{gonzalez2008}, which is defined as Eq. \eqref{eq:1}:
+The radius of gyration is a metric to distinguish mobility patterns of individuals~\citep{gonzalez2008}, which is defined as Eq. \eqref{eq:2}:
 
-\begin{equation} \label{eq:1}
+\begin{equation} \label{eq:2}
 r_{g} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(p_{i} -  p_{centroid})^{2}}, \textrm{where}\hspace{1ex} p_{centroid} = \frac{1}{n}\sum_{i=1}^{n}p_{i}
@@
 
-\noindent This measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
+\noindent It measures the accumulated distances of deviation from the center of mass of an individual user's trajectory, where $p_{i}$ is one of the user's locations and $p_{centroid}$ is the center of mass of the user's trajectory.
 By examining the probability distributions of the radius of gyration, also known as the spatial dispersal kernel $P(r_g)$~\citep{brockmann2006}, we chose 10 km as the cell size at the national level of Great Britain (Fig.~\ref{S4_Fig} - c, with details shown in the next section).
@@
 \subsection{Community structure of the network of spatial interactions}
-Based on the derived mobility network of spatial interactions, which is a directed weighted graph, we further determined clusters of strongly connected spatial nodes, known as communities, in the graph space.
+Based on the derived mobility network of spatial interactions, which is a directed weighted graph, we further determined clusters of strongly connected spatial nodes, known as communities, in the graph space~\citep{coscia2011}.
 There are a variety of community detection algorithms that produce different results depending the definition of community within the network~\citep{coscia2011}.
@@
 It identifies communities by minimizing the expected description length of the trajectory of a random walker, which is shown below:
-\begin{equation} \label{eq:2}
+\begin{equation} \label{eq:1}
 L(M)=qH(Q) + \sum_{i=1}^{m} p_{i}H(p_{i})
 \end{equation}
-In Eq.\eqref{eq:2}, $L(M)$ consists of two terms: qH(Q) is the entropy of the movement among clusters and $ \sum_{i=1}^{m} p_{i}H(p_{i})$ is the entropy of movement within clusters. 
-Specifically, q is the probability that a random walker jumps from one cluster to another, while $p_i$ is the probability of the in-cluster movement of cluster i.
-This algorithm can be intuitively tailored to describe strongly connected clusters of urban regions based on Twitter user movement.
+In Eq. \eqref{eq:1} , $L(M)$ consists of two terms: qH(Q) is the entropy of the movement among clusters and $ \sum_{i=1}^{m} p_{i}H(p_{i})$ is the entropy of movement within clusters. 
+To be more specific, q is the probability that a random walker jumps from one cluster to another, while $p_i$ is the probability of the in-cluster movement of cluster i.
+In this regard, this algorithm can be intuitively tailored to describe strongly connected clusters of urban regions based on Twitter user movement.
 The detailed literatures and implementations of Infomap can be found on this website ({\tt{http://mapequation.org}}).
-Note that Infomap is capable of performing multi-level community detection~\citep{domenico2015}, but we only use this algorithm to produce our most detailed community structures in order to examine groups of strongly connected urban regions.
+Note that Infomap is capable of performing multi-level community detection~\citep{domenico2015}, but we only use the algorithm to produce our most detailed community structures
+to examine groups of strongly connected urban regions.
 
 \subsection{Distance decay effects with a gravity model}
-As mentioned above, the clusters of urban regions in the form of communities in the network space often yield geographically cohesive urban areas. 
+As it is mentioned above, the clusters of urban regions in the form of communities in the network space often yield geographically cohesive urban areas. 
 This phenomenon is speculated to be related to the distance decay effects, where the interaction strength between two urban regions decreases as the geographical distance between them increases.
@@
 \eqref{eq:3}, where $<T_{ij}>$ and $d_{ij}$ denote the interaction from i to j and distance between two places, $K$ is a constant, and $P_{i}$ and $P_{j}$ are the population size of place $i$ and $j$ respectively.
-The interaction strength decreasing with respect to increasing geographic distance is expressed by the distance decay function, $f(d_{ij})$, where the parameter $\beta$ reveals the distance impact on interaction strength.
-A greater $\beta$ indicates stronger decay and the interaction strength is more influenced by distance~\citep{liu2014}.
+The interaction strength decreases with respect to the geographic distance is expressed by the distance decay function, $f(d_{ij})$, where the parameter $\beta$ reveals the distance impact on interaction strength.
+A greater $\beta$ indicates faster decay effects and the interaction strength is more influenced by distance~\citep{liu2014}.
 While it is suggested that population size may be an accurate indicator to describe the repulsion or attractiveness between places, the gravity model is usually fit by using observed interaction strength and the distance between geographical entities~\citep{liu2014}.
@@
 The majority of the data follow a truncated power-law distribution $P(X\geq x)\sim x^{-\alpha}e^{-\lambda x}$, where $\alpha = 1.24, \lambda =0.00132$; and the tail part (less than 2$\%$ of the whole population) follows a power-law distribution  $P(X \geq x)\sim x^{-\alpha}$ with $\alpha$ value is 3.2.
-The distribution was found to be consistent over each month examined (June to December, 2014), which has a slight offset in the truncated power-law distribution (the mean $\alpha$ value is 1.26 $ \pm$ with a 0.05 $\sigma$ and the mean $\lambda$ value as 0.00134 $ \pm$  with a 0.0002 $\sigma$).
+The distribution was found to be consistent over all individual months examined (June to December, 2014), which has a slight offset in the truncated power-law distribution (the mean $\alpha$ value is 1.26 $ \pm$ with a 0.05 $\sigma$ and the mean $\lambda$ value as 0.00134 $ \pm$  with a 0.0002 $\sigma$).
 
 The two-tier power law distribution indicates that the collective behavior of Twitter users visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk (a random walk) model~\citep{rhee2011,reynolds2012}, which has also been identified in many human mobility studies using different mobility data~\citep{zhao2015}.
-The similarity among the distributions suggests that the mobility data collected from geo-located tweets is temporally stable, at least at monthly intervals, which indicates that our approach using Twitter user mobility to delineate urban boundaries is viable.
+The similarity among the distributions suggests that the mobility data collected from geo-located tweets is temporally stable, at least at the monthly interval, which indicates that our approach using Twitter user mobility to delineate urban boundaries is viable.
 In addition, the L\'{e}vy Walk model reveals the diversity regarding the number of visited locations per user, which indicates a level of ``randomness'' in Twitter user movement across space. 
@@
 The probability distributions of the collective user displacement $P(d)$ and radius of gyration $P(r_g)$ are presented in Fig.~\ref{S4_Fig}, where the fitting method for identifying different distance ranges is derived from~\citep{jurdak2015}.
-The probability distribution of the collective displacements can be approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10m, 70m] (accounting for 3$\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [70m, 70km] (93$\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 70km] (4$\%$ of the population).
+The probability distribution of the collective displacements can be approximated by $P(d) \sim \lambda_{1} e^{-\lambda_{1}(d - d_{min})}, d_{min}=10m$ from [10m, 70m] (accounting for 3 $\%$ of the population),  $ P(d) \sim \beta\lambda_{1}d^{\beta-1}e^{-\lambda^{1}(d^\beta-d_{min}^\beta)}, d_{min} = 100m$ from [70m, 70km] (93 $\%$ of the population), and $P(d) \sim {d}^{-\alpha}$ [$>$ 70km] (4 $\%$ of the population).
 The displacement distance between 70m and 100km can be further approximated by two power law distributions with a cut-off point at 4km (55$\%$ distances are less than 4km and 40$\%$ distances between 4km and 100km), which indicates the urban movement captured by the geo-located Twitter data to reveal two different modes: inter-city and intra-city movement.
@@
 Further, we analyzed the distribution of radius of gyration to understand the movement from the point of view of individual Twitter users rather than separate displacements.
-The distribution of the radius of gyration of Twitter users in Great Britain can be approximated through a combination of three functions: $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10m$ from [10 m, 30m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50m, 10km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [10km, 100km], where these three functions account for 92$\%$ of all the users.
+The distribution of the radius of gyration can be approximated through a combination of three functions: $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}, {r_{g}}_{min}=10m$ from [10 m, 30m], $P(r_{g}) \sim \lambda_{2} e^{-\lambda_{2}(r_{g} - {r_{g}}_{min})}$ from [50m, 10km], and $P(r_{g}) \sim {r_{g}}^{-\alpha}$ [10km, 100km], where these three functions account for 92$\%$ of all the users.
 This suggests that there are three primary types of users that: (1) tend to stay at one location or at nearby locations when they tweet, or (2) tend to move at the intra-city scale when they tweet, or (3)  tend to exhibit a large spatial coverage.
@@
 These findings are consistent with the findings in the literature on human mobility, where the radius of gyration of human movement is bounded to different distance ranges~\citep{brockmann2006,gonzalez2008}.
-In particular, the distribution of the radius of gyration of Twitter users over the greater London region can be fitted by similar functions.
-However, as it reflects intra-city level mobility patterns, there is no distinct distance range to indicate large spatial coverage.
 The distance-decay effects found in both user displacements and the radius of gyration shows evidence of spatial proximity in Twitter user movement. 
@@
 \begin{figure}[ht]
-\includegraphics[width=1.0\linewidth]{./figure/S4_radius_displacement_3}
-\caption{{\bf The probability distribution of Twitter user displacements and radius of gyration:} (a) $P(d)$ is approximated by an exponential, a stretched-exponential and a power-law function (b) the distance between [70m, 70km] is approximated by a double power-law functions (c) $P(r_g)$ of Great Britain is approximated by the combination of an exponential, a stretched-exponential and a power-law function.
-(d) $P(r_g)$ of London is approximated an exponential and a stretched-exponential function.
+\includegraphics[width=0.9\linewidth]{./figure/S4_radius_displacement}
+\caption{{\bf The probability distribution of Twitter user displacements and radius of gyration:} (a) $P(d)$ is approximated by an exponential, a stretched-exponential and a power-law function (b) the distance between [70m, 70km] is approximated by a double power-law functions (c) $P(r_g)$ is approximated by the combination of an exponential, a stretched-exponential and a power-law function.
 (The green patch shows the distance range)}
@@
 \subsection{Redrawing Great Britain's Urban Boundaries}
-The mobility network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells, where 10 km is the distinct geographic distance for separating two main groups of Twitter users in terms of the spatial coverage (i.e., radius of gyration) in Great Britain (see Fig.~\ref{S4_Fig} - c).
+The mobility network of Twitter user spatial interaction was constructed by nodes representing 10 km by 10 km fishnet cells, where 10 km is the distinct geographic distance for separating two main groups of Twitter users in terms of the spatial coverage (i.e., radius of gyration) in Great Britain.
 The cells of the fishnet act as proxies to represent individuals' spatial coverage areas to focus more on the inter-connectivity among cells and identify strongly connected cell clusters.
@@
 Fig.~\ref{S5_Fig}  presents the delineated urban boundaries based on Twitter user displacement distance less than 4 km, greater than 4km, greater than 10 km, and using all available displacements together compared to the administrative boundaries of Great Britain.
-One clear observation in both the coarse and fine delineations is that most of the geographic divisions are centered around big urban cores with relatively high populations.
+One clear observation across the coarse and fine delineations is that most of the geographic divisions are centered around big urban cores with relatively high populations.
 These results are expected given that most of the tweets originate in urban centers.
@@
 \includegraphics[width=0.9\linewidth]{./figure/S5_community}
-\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) all displacements with $L(M)= 7.8$.
-(b) displacements longer than 10 km ($L(M)=8.5$) (c) displacements shorter than 4 km ($L(M)=4.5$) (d) and displacements longer than 4 km ($L(M)=8.1$).The partition of space was done using a 10 km fishnet for the directed displacements from and to each cell.
+\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) displacements longer than 10 km (b) displacements shorter than 4 km (c) and displacements longer than 4 km (d) The partition of space was done using a 10 km fishnet to map the directed displacements from and to each cell.
 Each color represents a unique community with more Twitter users displacements among the cells compared to others.
-Major cities (urban audit functional areas) and NUTS are displayed as labels.}
+Major cities (urban audit functional areas) and NUTS are displayed in black.}
 \label{S5_Fig}
@@
 A more detailed study was conducted over the greater London region revealing the intra-city spatial interaction patterns.
-Since the captured Twitter user movements were on intra-city level (in comparison to the national level in Fig.~\ref{S4_Fig}-c), there was no distinct distance range to separate Twitter user spatial coverage in terms of radius of gyration (see Fig.~\ref{S4_Fig}-d).
-We chose 1-km cell size as referred from the related literature~\citep{liu2015}, which suggested 1-km cell size is detailed enough to depict urban structures.
-The spatial partitions derived from a fine grid of 1km used all available Twitter user trips without any restriction on trip distances yields geographic boundaries comparable to some of London's boroughs  (Fig.~\ref{S7_Fig}).
+The spatial partitions derived from a fine grid of 1km using all available Twitter user trips without any restriction on trip distances yields geographic boundaries comparable to some of London's boroughs  (Fig.~\ref{S7_Fig}).
 However, some areas are shown to be more cohesive and display greater spatial interactions across the administrative boundaries, for instance, central London.
@@
 \includegraphics[width=0.7\linewidth]{./figure/S7_london}
-\caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs ($L(M)=8.1$)}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.
+\caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.
 Each unique color represents a different non-administrative anthropographic region.
-Notice that some remote regions like the airport (light purple region in south of Hillingdon) share the same class with downtown because it is well connected despite the geographic separation.}
+Notice that some remote regions like the airport (light green region in south of Hillingdon) share the same class with downtown because it is well connected despite the geographic separation.}
 \label{S7_Fig}
@@
 
-\subsection{Distance decay effects with a gravity model}
+\subsection{Explaining the Distance decay effects with the gravity model}
 The results of strongly connected urban regions in the form of communities in the mobility network of Twitter user spatial interactions yield geographically cohesive, non-overlapping urban areas. 
 While it provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain, the reasons on why they are geographically cohesive and non-overlapping or why the boundaries stop/emerge at certain spatial extent that leads to different size of the urban areas are not clear.
-As the depicted urban boundaries exhibit a strong instance of spatial proximity, a gravity model is employed (Eq.
+As the depicted urban boundaries exhibit a strong instance of spatial proximity, the gravity model is employed (Eq.
 \eqref{eq:3}) to explain how distance decay effects found in the mobility patterns affect the interaction strength among non-administrative anthropographic urban areas.
@@
 This confirms that the depicted urban areas are results of spatial proximity effects, where the strength of human (in this case, Twitter user) spatial interaction between two urban regions decreases as the geographic distance between them increases.
-More importantly, since we have used a mobility network to delineate the boundaries, the distance decay effects are well related and explained by the distance decay parameters found in the underlying mobility patterns.
+More importantly, since we have used a mobility network to delineate the boundaries, the distance decay effects are well related and explained by the underlying mobility patterns.
 In return, the well fitted gravity model provides support that the depicted urban areas are not random artifacts but indeed reflect how people move across geographic regions.
@@
 
-%\clearpage
-\section{Discussion}
-It is worth noting that constructing a mobility network of spatial interaction using geo-located Twitter data has some potential concerns to limit the results from this study.
-First, the geo-located Twitter data is not able to generalize to the entire population.
-As the demographic information of the Twitter users cannot be easily identified, the results of delineated urban boundaries may not reflect a complete real-world image from human movements. 
-The demographics of Twitter users in this study can be an under/over-representation of the all overall population in Great Britain.
-Related studies have been carried out to examine the demographic information in geo-located Twitter data~\citep{steiger2015,luo2016,huang2016}, which should be carefully considered in future studies.
-Second, regarding the concern of spatial sparseness of geo-located Twitter data~\citep{steiger2015}, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
-To investigate whether this limited the ability to capture the connections made through Twitter user movements between urban regions, we visualized the flows of Twitter user movements using the method mentioned in~\citep{rae2009}(see Supplement Materials section 1).
-The outcome showed that the Twitter user movements in this study connected most urban areas in Great Britain and clearly exhibited long and short distance movements, where was essential for investigating the connection strength between urban regions.
-Third, since the collective radius of gyration was used to determine the cell-size in the network, we examined the temporal stability for the measurement in the geo-located Twitter data.
-The probability distributions of the radius of gyration for Twitter users in the Great Britain are verified to be consistent across different monthly time span, (see Supplement Materials section 2), which indicates the stability of using such measurements in this study.
-Finally, as the geo-located Twitter data offers easy data accessibility, the methods in this study can be reproduced for other countries. 
-Along with the large sample size and spatial coverage, geo-located Twitter data demonstrated its applicability for this study.
-
-A major component in this study was imposing a virtual fishnet to partition the geographic space over Great Britain.
-We should be aware that using different approaches to partitioning the space will produce different mobility networks, and can potentially lead 
-to different delineations of the urban boundaries.
-Indeed, we had used the ward divisions as spatial units for aggregating Twitter user movements, which is the finest administrative boundaries of Great Britain (see Supplement Materials section 3).
-Without looking into the details of the results, the derived communities in the network space are similar to the ones from using fishnet approach.
-The strongly connected communities also yield geographically cohesive, non-overlapping urban areas.
-However, as the ward division is still defined by administrative purpose, the polygonal units tend to be geographically continuous.
-It causes problems to aggregate regions that do not have Twitter coverage into certain clusters.
-Aggregating Twitter user movements at the ward level also imposes more apparent concerns of the mismatch of the overall population, where less populated areas were overly represented and connected into large areas.
-These are the reasons why we chose a virtual fishnet approach for this study.
-
-As it is discussed above, we chose 10 km as the cell-size of the fishnet at national level in this study.
-We also carried out an experiment by arbitrarily setting the cell-size to 5 km at the national level (see Supplement Materials section 4).
-Note that the cell-size could be set to any value, such as 4.9 km or 5.1 km.
-The fishnet with smaller cell-size (i.e., 5 km) produced more and smaller strongly-connected communities within the network space.
-It indicates that the spatial resolution of the fishnet cells does affect the outcome from the community detection method employed in this study, where fishnet with smaller cell-size leads to more discrete and locally connected (i.e., smaller) clusters of urban areas.
-Such an effect can be explained by the probability distributions of the radius of gyrations of individual Twitter users.
-The probability of distance that deviates from a user's center location decays with a stretched-exponential function from [50m, 10km], which means the movements from Twitter users with smaller spatial coverage dominate the delineation of the connected urban areas.
-To avoid arbitrarily deciding the cell-size, we studied the probability distributions of the radius of gyrations of individual Twitter users and selected 10-km as the cell-size, which is the distinct geographic distance for separating two main groups of Twitter users in terms of their spatial coverage at the national level.
-In addition, this choice enabled us to focus on the inter-connections among different urban regions with less attention to movements around a user's neighborhood (i.e., within 10 km radius), such as home or work places.
-
-To apply the map equation algorithm, the mobility network should be organized as a weighted and directed graph, on which we confirmed an undirected graph cannot lead to a meaningful result (see Supplement Materials section 4).
-Since we used different physical movement ranges of users in delineating the urban boundaries, the description length $L(M)$ appeared to get larger when longer movement distances were used, which corresponded to less and larger geographically cohesive, non-overlapping urban areas.
-We believed that different movement ranges of users changed the weights of this graph and affected the interaction strength between two fishnet cells.
-As we have illustrated that the geographically cohesive, non-overlapping urban areas were instances of spatial proximity effects, where the gravity model model employed suggested the interaction strength between two fishnet cells decreases as the geographical distance increases, the longer movement distances were used, the larger $L(M)$ the map equation algorithm produces.
-
-\section{Conclusion}
-In this study, we presented a method that connected human mobility research with the delineation of the non-administrative anthropographic urban boundaries in Great Britain using a mobility network of Twitter user spatial interactions.
-In contrast to administrative urban boundaries, our ``bottom-up" approach imposed a virtual fishnet over the islands of Great Britain to partition the space.
-By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell-size of 10 km at the national level and 1 km for the greater London region.
+\clearpage
+\section{Conclusion and Discussion}
+In this study, we delineated the non-administrative anthropographic urban boundaries in Great Britain using a network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
+In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the islands of Great Britain to partition the space.
+By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell size of 10 km to quantify the spatial coverage of the majority of Twitter users in Great Britain.
 Twitter user movements were used to establish a connectivity network of the fishnet cells.
@@
 The power of using Twitter user mobility to delineate non-administrative anthropographic boundaries is the ability to redraw the city at different mobility ranges inferred objectively from the collective mobility patterns.
-Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect the human interactions with the geographical space.
-More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
-This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activities and urban space.
-A final remark from this study for future studies is that geographical distance plays an important role in affecting human mobility patterns and the strength of human spatial interactions across space.
-Our approach can be considered to assist in understanding human spatial interactions from the mobility perspective, which is applicable for detailed geo-located Twitter data in different countries, as well as future mobility datasets with detailed location information of individuals and large spatial coverage.
+Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect the human interaction space.
+This study provides a first step in connecting human mobility research with defining non-administrative anthropographic boundaries, which could assist in resource allocation, political campaigns and urban planning.
+However, the geo-located twitter data is not able to generalize to the entire population; therefore, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
+Yet, our approach is still applicable when more detailed mobility data is available.
+
+%Talk about interplay between human mobility 
+%The purpose of trip
+%contextualizing
+
 %\subsection{Acknowledgements}
@@
 \markboth{}{International Journal of Geographical Information Science}
+
 \bibitem[\protect\citeauthoryear{Blanford {\itshape{et~al.}}}{2015}]{blanford2015}
@@
 Fotheringham, A.S., 1981. Spatial structure and distance-decay parameters. Annals of the Association of American Geographers, 71(3), pp.425-436.
+
+%\bibitem[\protect\citeauthoryear{Frank {\itshape{et~al.}}}{2013}]{frank2013}
+%Frank, M.R., Mitchell, L., Dodds, P.S. and Danforth, C.M., 2013. Happiness and the patterns of life: A study of geolocated tweets. Scientific reports, 3.
 
@@
 2178-2199.
+
 \end{thebibliography}
+
 \bibliographystyle{tGIS}
+%\bibliography{Twitter_Urban_Boundary}
+
 \label{lastpage}

### 2017-01-11 urban_spatial_interaction/urban_boundaries_gb_IJGIS/IJGIS/Paper_version_2.tex
Clean up

--- 2016-08-02 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
@@
 \includegraphics[width=0.9\linewidth]{./figure/S5_community}
-\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) all displacements with $L(M)= 7.8$.
-(b) displacements longer than 10 km ($L(M)=8.5$) (c) displacements shorter than 4 km ($L(M)=4.5$) (d) and displacements longer than 4 km ($L(M)=8.1$).The partition of space was done using a 10 km fishnet for the directed displacements from and to each cell.
+\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) all displacements with $L = 7.8$.
+(b) displacements longer than 10 km ($L=8.5$) (c) displacements shorter than 4 km ($L=4.5$) (d) and displacements longer than 4 km ($L=8.1$).The partition of space was done using a 10 km fishnet to map the directed displacements from and to each cell.
 Each color represents a unique community with more Twitter users displacements among the cells compared to others.
@@
 \includegraphics[width=0.7\linewidth]{./figure/S7_london}
-\caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs ($L(M)=8.1$)}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.
+\caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs ($L=8.1$)}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.
 Each unique color represents a different non-administrative anthropographic region.
@@
 \section{Discussion}
-It is worth noting that constructing a mobility network of spatial interaction using geo-located Twitter data has some potential concerns to limit the results from this study.
+It is worth noting that constructing a mobility network of spatial interaction using geo-located Twitter data has some potential concerns.
 First, the geo-located Twitter data is not able to generalize to the entire population.
-As the demographic information of the Twitter users cannot be easily identified, the results of delineated urban boundaries may not reflect a complete real-world image from human movements. 
-The demographics of Twitter users in this study can be an under/over-representation of the all overall population in Great Britain.
-Related studies have been carried out to examine the demographic information in geo-located Twitter data~\citep{steiger2015,luo2016,huang2016}, which should be carefully considered in future studies.
-Second, regarding the concern of spatial sparseness of geo-located Twitter data~\citep{steiger2015}, the urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
-To investigate whether this limited the ability to capture the connections made through Twitter user movements between urban regions, we visualized the flows of Twitter user movements using the method mentioned in~\citep{rae2009}(see Supplement Materials section 1).
-The outcome showed that the Twitter user movements in this study connected most urban areas in Great Britain and clearly exhibited long and short distance movements, where was essential for investigating the connection strength between urban regions.
-Third, since the collective radius of gyration was used to determine the cell-size in the network, we examined the temporal stability for the measurement in the geo-located Twitter data.
-The probability distributions of the radius of gyration for Twitter users in the Great Britain are verified to be consistent across different monthly time span, (see Supplement Materials section 2), which indicates the stability of using such measurements in this study.
-Finally, as the geo-located Twitter data offers easy data accessibility, the methods in this study can be reproduced for other countries. 
-Along with the large sample size and spatial coverage, geo-located Twitter data demonstrated its applicability for this study.
+The demographic information of the Twitter users cannot be easily identified, the result of delineated urban boundaries may not reflect a complete real-world image from human movements.
+The urban regions that do not have any, or limited, Twitter coverage can be missed during the delineation process.
+Related studies have been carried out to examine the demographic information in geo-located Twitter data~\citep{steiger2015,luo2016}, which should be considered in future studies.
+Nevertheless, since this study focus on the connections made through Twitter user movements between urban regions, we visualized the mobility flux of Twitter user movements using the method mentioned in~\citep{rae2009}(see Supplement Materials section 1).
+The outcome showed that the Twitter user movements in this study connect most urban areas in Great Britain and clearly exhibited long and short distance movements.
+In this connection, geo-located Twitter data demonstrated its applicability for this study, along with the large spatial coverage and easy data accessibility as mentioned above.
+In addition,
 
-A major component in this study was imposing a virtual fishnet to partition the geographic space over Great Britain.
-We should be aware that using different approaches to partitioning the space will produce different mobility networks, and can potentially lead 
-to different delineations of the urban boundaries.
-Indeed, we had used the ward divisions as spatial units for aggregating Twitter user movements, which is the finest administrative boundaries of Great Britain (see Supplement Materials section 3).
-Without looking into the details of the results, the derived communities in the network space are similar to the ones from using fishnet approach.
-The strongly connected communities also yield geographically cohesive, non-overlapping urban areas.
-However, as the ward division is still defined by administrative purpose, the polygonal units tend to be geographically continuous.
-It causes problems to aggregate regions that do not have Twitter coverage into certain clusters.
-Aggregating Twitter user movements at the ward level also imposes more apparent concerns of the mismatch of the overall population, where less populated areas were overly represented and connected into large areas.
-These are the reasons why we chose a virtual fishnet approach for this study.
+The probability distributions of the radius of gyration for Twitter users in the Great Britain are verified to be consistent across different monthly time span, (see Supplement Materials section 1), which indicates the stability of using such measurements in this study.
 
-As it is discussed above, we chose 10 km as the cell-size of the fishnet at national level in this study.
-We also carried out an experiment by arbitrarily setting the cell-size to 5 km at the national level (see Supplement Materials section 4).
-Note that the cell-size could be set to any value, such as 4.9 km or 5.1 km.
-The fishnet with smaller cell-size (i.e., 5 km) produced more and smaller strongly-connected communities within the network space.
-It indicates that the spatial resolution of the fishnet cells does affect the outcome from the community detection method employed in this study, where fishnet with smaller cell-size leads to more discrete and locally connected (i.e., smaller) clusters of urban areas.
-Such an effect can be explained by the probability distributions of the radius of gyrations of individual Twitter users.
-The probability of distance that deviates from a user's center location decays with a stretched-exponential function from [50m, 10km], which means the movements from Twitter users with smaller spatial coverage dominate the delineation of the connected urban areas.
-To avoid arbitrarily deciding the cell-size, we studied the probability distributions of the radius of gyrations of individual Twitter users and selected 10-km as the cell-size, which is the distinct geographic distance for separating two main groups of Twitter users in terms of their spatial coverage at the national level.
-In addition, this choice enabled us to focus on the inter-connections among different urban regions with less attention to movements around a user's neighborhood (i.e., within 10 km radius), such as home or work places.
-
-To apply the map equation algorithm, the mobility network should be organized as a weighted and directed graph, on which we confirmed an undirected graph cannot lead to a meaningful result (see Supplement Materials section 4).
-Since we used different physical movement ranges of users in delineating the urban boundaries, the description length $L(M)$ appeared to get larger when longer movement distances were used, which corresponded to less and larger geographically cohesive, non-overlapping urban areas.
-We believed that different movement ranges of users changed the weights of this graph and affected the interaction strength between two fishnet cells.
-As we have illustrated that the geographically cohesive, non-overlapping urban areas were instances of spatial proximity effects, where the gravity model model employed suggested the interaction strength between two fishnet cells decreases as the geographical distance increases, the longer movement distances were used, the larger $L(M)$ the map equation algorithm produces.
+Yet, our approach is still applicable when more detailed mobility data is available.
 
 \section{Conclusion}
-In this study, we presented a method that connected human mobility research with the delineation of the non-administrative anthropographic urban boundaries in Great Britain using a mobility network of Twitter user spatial interactions.
-In contrast to administrative urban boundaries, our ``bottom-up" approach imposed a virtual fishnet over the islands of Great Britain to partition the space.
-By studying the probability distributions of the radius of gyrations of individual Twitters users, we selected a cell-size of 10 km at the national level and 1 km for the greater London region.
+In this study, we presented a method to delineate the non-administrative anthropographic urban boundaries in Great Britain using a mobility network of Twitter user spatial interactions, which were inferred from the collective Twitter user movement data extracted from more than 69 million Twitter messages.
+In contrast to administrative urban boundaries, our ``bottom-up" approach imposes a virtual fishnet over the islands of Great Britain to partition the space.
+To avoid deciding the cell size arbitrarily, we studied the probability distributions of the radius of gyrations of individual Twitters users and selected 10-km as the cell size, which is the distinct geographic distance for separating two main groups of Twitter users in terms of their spatial coverage at the national level.
+In addition, this choice enables us to focus on the inter-connections among different urban regions with less attention to movements around a user's neighborhood (i.e., within 10 km radius), such as home or work places.
+
 Twitter user movements were used to establish a connectivity network of the fishnet cells.
@@
 The power of using Twitter user mobility to delineate non-administrative anthropographic boundaries is the ability to redraw the city at different mobility ranges inferred objectively from the collective mobility patterns.
-Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect the human interactions with the geographical space.
-More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
-This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activities and urban space.
-A final remark from this study for future studies is that geographical distance plays an important role in affecting human mobility patterns and the strength of human spatial interactions across space.
-Our approach can be considered to assist in understanding human spatial interactions from the mobility perspective, which is applicable for detailed geo-located Twitter data in different countries, as well as future mobility datasets with detailed location information of individuals and large spatial coverage.
+Urban boundaries redrawn based on Twitter user movement represent physical commutes rather than social ties or phone call initiation to reflect the human interaction space.
+This study provides a first step in connecting human mobility research with defining non-administrative anthropographic boundaries, which could assist in resource allocation, political campaigns and urban planning.
+One final remark from this study is that we
+
 %\subsection{Acknowledgements}

### 2017-01-11 urban_spatial_interaction/urban_boundaries_gb_ijgis_submission_r2/IJGIS/Paper.tex
Clean up

--- 2016-10-23 urban_boundaries_gb_ijgis_submission_r3/IJGIS/Paper.tex
@@
 
-% \doi{10.1080/1365881YYxxxxxxxx}
-% \issn{1362-3087} \issnp{1365-8816} \jvol{00} \jnum{00} \jyear{2016} \jmonth{October}
+%\doi{10.1080/1365881YYxxxxxxxx}
+%\issn{1362-3087} \issnp{1365-8816} \jvol{00} \jnum{00} \jyear{2009} %\jmonth{February}
 
-% \markboth{Taylor \& Francis and I.T. Consultant}{International Journal of Geographical Information Science}
+%\markboth{Taylor \& Francis and I.T. Consultant}{International Journal of Geographical Information Science}
 
 \articletype{RESEARCH ARTICLE}
-\title{{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}}
-
-\author{Junjun Yin$^{1,2,3}$, Soliman Aiman$^{1,4}$, Dandong Yin$^{1,2,3}$ and Shaowen Wang$^{1,2,3,4}$$^{\ast}$\thanks{$^\ast$Corresponding author. Email: shaowen@illinois.edu
-\vspace{6pt}}\\\vspace{6pt}  $^{1}${\em{CyberGIS Center for Advanced Digitial and Spatial Studies}};
-$^{2}${\em{CyberInfrastructure and Geospatial Information Laboratory}};
-$^{3}${\em{Department of Geography and Geographic Information Science}};
-$^{4}${\em{National Center for Supercomputing Applications}};{\em{University of Illinois at Urbana-Champaign, IL, 61801, U.S.A.}}
-\\\vspace{6pt}\received{v2.0 released October 2016}}
+\title{{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data} }
 \maketitle
@@
 \begin{center}
-\includegraphics[width=.9\linewidth]{./figure/S2_twitter_density_Fig_1}
+\includegraphics[width=.8\linewidth]{./figure/S2_twitter_density_Fig_1}
 \caption{{\bf The spatial coverage of collected geo-located Tweets in Great Britain (left) and London (right).} Each point corresponds to an individual geo-located tweet collected for this study.
@@
 \end{figure}
-
 The original location information embedded in the geo-tag is given in units of latitude and longitude.
@@
 \begin{figure}[ht]
-\begin{center}
-\includegraphics[width=0.9\linewidth]{./figure/S3_visitation}
-\caption{\bfseries{Cumulative distribution of the number of locations visited by each Twitter user during different timespan}}
+\includegraphics[width=1.0\linewidth]{./figure/S3_visitation}
+\caption{ \bfseries{Cumulative distribution of the number of locations visited by each Twitter user during different timespan}}
 \label{S3_Fig}
-\end{center}
 \end{figure}
@@
 
-\begin{figure}
+\begin{figure}[ht]
 \begin{center}
@@
 
-\begin{figure}
+\begin{figure}[ht]
 \begin{center}
-\includegraphics[width=0.7\linewidth]{./figure/S7_london}
+\includegraphics[width=0.9\linewidth]{./figure/S7_london}
 \caption{{\bf Non-administrative anthropographic boundaries inferred from collective Twitter user displacements in the city of London compared to the boundaries of London boroughs ($L(M)=8.1$)}  A fine fishnet of 1 km cells were used to identify the detailed connectivity patterns based on all the Twitter user displacements in the area.
@@
 
+%\clearpage
 \section{Discussion}
@@
 Our approach can be considered to assist in understanding human spatial interactions from the mobility perspective, which is applicable based on detailed geo-located Twitter data in many countries, as well as future mobility datasets with detailed location information of individuals and large spatial coverage.
-
-\subsection*{Acknowledgements}
-xx
+%\subsection{Acknowledgements}
 

### 2017-01-18 semantic_decomposition_of_twitter_user_locations/paper.tex
edits

@@
 \title{A tale of two cities: A GIS based data synthesis approach to understanding semantic decompositions of Twitter user locations}
-% \author~\thanks{yinjunjun@gmail.com]{Junjun Yin}
-\author[1,~\thanks{Corresponding author: jyin@psu.edu}]{Junjun Yin}
-\affil[1]{Population Research Institute}
+\author[1~\thanks{Corresponding author: jyin@psu.edu}]{Junjun Yin}
+\affil[ ]{Social Science Research Institute}
 \affil[ ]{The Pennsylvania State University, State College, 16801, PA, USA}
@@
 \section*{Abstract}
+Human mobility is as complex human behavior, by its nature difficulty to study, confounded by human variability.
+
+With the advancement positioning technology, the
+
 Today's pervasive Location Based Social Media provide abundant user-generated geographic information
-In this paper, we present a geographical information system (GIS) based data synthesis approche to understanding semantic decompositions of Twitter user locations.
+In this paper, we present a geographical information system (GIS) based data synthesis approach to understanding semantic decompositions of Twitter user locations.
 Specifically, we implemented a
@@
 \section{Related Work}
+yy~\cite{yin2017depicting}
 
-\section{Methods and Materials}
+\section{Data and Methods}
 

### 2018-05-28 GIScience_2018/giscience_r2/giscience/giscience2018.tex
revision

\documentclass[a4paper,UKenglish]{lipics-v2018}
%This is a template for producing LIPIcs articles. 
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
% for section-numbered lemmas etc., use "numberwithinsect"

\usepackage{microtype}%if unwanted, comment out or use option "draft"

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

%My packages
%\usepackage{amsthm}

%\theoremstyle{definition}
%\newtheorem{definition}{Definition}[section]

%\nolinenumbers
\bibliographystyle{plainurl}% the recommended bibstyle

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\title{Robust Estimation and Comparison of Origin-Destination Flows with Data Depth}\footnote{A full version of the paper is available at \cite{DBLP:journals/cacm/Knuth74}, \url{XXX}}}
\title{Outlier Detection and Comparison of Origin-Destination Flows using Data Depth}
\titlerunning{Outlier Detection and Comparison of Origin-Destination Flows using Data Depth} %optional, in case that the title is too long; the running title should fit into the top page column

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author{Myeong-Hun Jeong}{Department of Civil Engineering, Chosun University, Gwangju, Republic of Korea}{mhjeong@chosun.ac.kr}{[orcid]}{[funding]}
\author{Junjun Yin}{Social Science Research Institute; Institute for CyberScience, Penn State University, PA, USA}{jyin@psu.edu}{[0000-0002-4196-2439]}{[This work used the Extreme Science and Engineering Discovery Environment (XSEDE), which is supported by National Science Foundation grant number ACI-1548562]}
\author{Shaowen Wang}{Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, IL, USA}{shaowen@illinois.edu}{[orcid]}{[funding]}

\authorrunning{M.-H. Jeong, J. Yin and S. Wang} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

\Copyright{Myeong-Hun Jeong, Junjun Yin, and Shaowen Wang}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

%\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation".

\subjclass{Computing methodologies $\rightarrow$ Anomaly detection}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm . E.g., cite as "General and reference $\rightarrow$ General literature" or \ccsdesc[100]{General and reference~General literature}.

\keywords{OD Analysis, Trajectory Data Mining, Data Depth, Outliers Detection}% mandatory: Please provide 1-5 keywords

\category{}%optional, e.g. invited paper

\relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website

\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...

\funding{}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

\acknowledgements{I want to thank \dots}%optional
% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{Stephan Winter, Amy Griffin, and Monika Sester}
\EventNoEds{3}
\EventLongTitle{10th International Conference on Geographic Information Science (GIScience 2018)}
\EventShortTitle{GIScience 2018}
\EventAcronym{GIScience}
\EventYear{2018}
\EventDate{August 28--31, 2017}
\EventLocation{Melbourne, Australia}
\EventLogo{}
\SeriesVolume{114}
\ArticleNo{6} % “New number” (=<article-no>) goes here!
% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\begin{abstract}
Advances in location-aware technology have resulted in the generation of  a huge volume of trajectory data. Origin-destination (OD) trajectories provide rich information on urban flow and transport demand. This study presents a new methodology to detect OD flows outliers and conduct hypothesis testing between two OD flows in terms of the variations of spatial extent, that is, spread. The proposed method is based on data depth, which measures the centrality and outlyingness of a point with respect to a given dataset in $\mathbb{R}^d$. Based on the center-outward ordering property, the proposed method analyzes the underlying characteristics of OD flows, such as location, outlyingness, and  spread. The ability of the proposed method to detect OD anomalies is compared with that of the Mahalanobis distance approach, and an F-test is used to verify the difference in scale. Empirical evaluation has demonstrated that the proposed method effectively identifies  OD flows outliers in an interactive way. Furthermore, the proposed method  can provide new perspectives by considering the overall structure of data when comparing two different OD flows in terms of scale.

 \end{abstract}

\section{Introduction}
With the rapid rise in ubiquity of geolocation-aware sensors, knowledge discovery is greatly enhanced by extracting and mining interesting patterns from spatiotemporal big data in various domains.
Location-acquisition technologies generate large volumes of movement data, which are used to track people, animals, vehicles, and even natural phenomena.
Such data help us better model moving objects and reveal hidden patterns that are important to urban planning \cite{mazimpaka15AGILE}, urban human mobility \cite{yin2017depicting,kwan1998space}, the sustainability of urban systems \cite{alberti2003integrating,chen13Percom}, the environment \cite{devarakonda13SIGKDD}, and public security and safety \cite{buchin14JOSIS}.
%Importantly, trajectory mining leads to solutions for addressing important research problems in different fields, such as urban planning \cite{mazimpaka15AGILE}, transportation \cite{chen13Percom}, environment \cite{devarakonda13SIGKDD}, and public security and safety \cite{buchin14JOSIS}.

This paper presents a new algorithm which estimates origination-destination (OD) flow anomalies and conducts hypothesis testing between two sets of different OD flows. In this study,  the OD flow data is a subset of trajectory data, which records the origin and destination of each movement while ignoring the actual trajectory route \cite{guo14IEEETVCG}.  
The algorithm was applied to OD flows derived from extracted origin and destination data in a dataset describing New York City taxi trips, in which each record contained the origin and destination of each trip, without intermediate locations of the actual routes.

In recent years, researchers have investigated a variety of approaches to trajectory data mining.
Most contemporary trajectory mining methods can be classified into four categories: clustering, classification, frequent/group pattern mining, and outlier detection \cite{mazimpaka16JOSIS,zheng15ACMTIST}. These techniques can be used independently or combinatorially for trajectory mining applications. This study focuses on outlier detection of OD flows. Outlier detection attempts to identify trajectories that do not follow the typical flows of trajectory datasets that characterizes the connectivity between regions \cite{mazimpaka16JOSIS}. Euclidean distance is employed by  \cite{fontes13GeoInfo,lee08ICDE} to find outlier patterns from trajectories. Studies by \cite{pan13ACMGIS,liu12IJGIS} question the Euclidean distance approach because of the loss of local features and unavailability when external factors, such as topography, land cover or weather condition,   affect the trajectories. In their research,  \cite{pan13ACMGIS,liu12IJGIS} addresses this by using robust distance measurements, i.e., Mahalanobis distance \cite{pan13ACMGIS} and relative distance \cite{liu12IJGIS}. Instead of using distance or density, anomalous trajectories are detected by exploiting comparisons of the structural features of each trajectory segment \cite{yuan11JCIS} and an isolation tree of trajectories  \cite{zhang11UC}.
Most of the above methods are related to trajectory data analysis, and thus, it is reasonable to extend the application of these approaches to the identification of OD flow anomalies. 
To overcome the sensitivity of Euclidean distance-based approaches to non-normal distributed data and the difficulty of selecting parameters for anomaly detection techniques based on distance or density, this study employs robust statistics, such as data depth, to detect OD flow outliers.

% Although most methods mentioned above are related to trajectory data analysis, it is reasonable to extend these approaches to identify  OD flows anomaly. Thus, this study employs robust statistics such as data depth to detect robustly OD flow outliers because Euclidean distance-based approaches are sensitive to non-normal distributed data and it is hard to choose  parameters for anomaly detection techniques based on distance or density.   
%  because  Euclidean distance-based approaches are sensitive to non-normal distribution of data sets.

%In a similar fashion, this study considers the center regions of OD flows with data depth in order to robustly detect the OD flows outliers.

%In addition, visual analytics such as flow mapping is a common approach to analyze OD flow data. Visual representations of massive movement data enables comprehensive exploration of data and results in understanding complex flow trends.

Flow mapping, a type of visual analytics, is a common approach to analyzing OD flow data. Visual representations of massive movement data facilitate comprehensive exploration of data, in turn enabling perception and understanding complex flow trends.
Aggregation and generalization of movement data are frequently utilized to resolve visual clutter \cite{guo14IEEETVCG}.  %\cite{andrienko08VAST,adrienko11IEEETVCG,guo14IEEETVCG}
While visual analytics can help to extract inherent patterns from massive data, it is difficult to quantitatively compare two sets of different OD flows based on a hypothesis testing.
In other words, it is complicated to comprehend how two OD flows differ and, more importantly, the magnitude of the difference, using a test of statistical significance.  Recently published articles employ multidimensional spatial scan statistics  \cite{Gao17IJGIS} and  local Ripley’s K-function \cite{tao16GA} to identify clusters of  flow data based on statistical significance tests. Thus, this paper applies bivariate hypothesis testing methods based on data depth to understand the difference between two OD flow datasets in terms of the amount of spatial extent.

It is worth noting that flow mapping approaches frequently suffer from the modifiable areal unit problem (MAUP).Essentially, MAUP is the influence of different aggregations determined by location on the presentation of coherent patterns.  Kernel-based flow estimation and smoothing are used to overcome different spatial resolutions \cite{guo14IEEETVCG}. 
Instead of attempting to find the best areal unit by which to partition urban space and aggregates the OD flows, this study adopted the established traffic analysis  zones of New York City as base unit. That said, the proposed method can be adapted to other implementation of areal units. In this study, New York City taxi trip data includes the origin and destination within traffic analysis zones, while ignoring the intermediate locations of the actual routes.
It is not necessary to reconstruct individual movements for flow estimation (see \cite{duckham16ICGIS}).

In summary, this paper presents a new algorithm which conducts outlier detection as well as hypothesis testing on OD flow data extracted from a trajectory dataset. Our approach investigates the central regions of OD flows, based on data depth, to detect OD flow anomalies and conduct hypothesis testing between two different OD flow datasets. We believe that our method for analyzing taxi trip data has the potential to aid administrative authorities in understanding crowd patterns, in turn improving urban planning activities such as determining transportation investments.

The remainder of this paper is organized as follows: Section \ref{sec:methods} overviews how to detect OD flow outliers and conduct  hypothesis testing between two different OD flow datasets using the concept of data depth. 
Experimental design and the evaluation of the proposed method are presented in Section \ref{sec:experiments}. 
These results are discussed in Section \ref{sec:discussion}. 
Section 5 concludes this paper with a summary and future perspectives.

%With the rapid rise in ubiquity of geo-tagged sensors, knowledge discovery power is enhanced by extracting interesting patterns from spatiotemporal big data in various domains. In particular, the location-acquisition technologies generate large volumes of movement data such as people, animals, vehicles and natural phenomena. These big movement data help us understand moving objects, and discover the hidden patterns. Thus, trajectory mining leads to solutions for important research problems in different fields such as urban planning \cite{mazimpaka15AGILE}, transportation \cite{chen13Percom}, environment \cite{devarakonda13SIGKDD}, and public security and safety \cite{buchin14JOSIS}.
%
%This paper presents a new algorithm which not only estimates origination-destination (OD)'s flows anomaly but also conducts hypothesis testing between two different OD flows. This paper utilizes a New York City Taxi data set that has the origin and destination of each movement without the whole actual trajectory routes. The analysis of digital footprints obtained from taxi data has a crucial role in  understanding crowd patterns and planning urban and transportation investments in administrative authorities.

%In recent years, researchers have investigated a variety of approaches to trajectory data mining. There are generally four categories that classify trajectory mining methods: clustering, classification, frequent/group pattern mining, and outlier detection \cite{mazimpaka16JOSIS,zheng15ACMTIST}. These techniques can be used independently or combinatorially for trajectory mining application problems. 
%
%In particular, this study focuses on outlier detection of OD flows. Outlier detection aims to find trajectories that do not follow the typical flow of trajectory data sets for characterizing the connectivity between regions \cite{mazimpaka16JOSIS}. \cite{fontes13GeoInfo,lee08ICDE} use Euclidean distance to find outlier patterns from trajectories.  \cite{pan13ACMGIS,liu12IJGIS} raise the questions of Euclidean distance approach due to the loss of local features and unavailability when external factors affect the trajectories (e.g., topography, land cover or weather condition).  \cite{pan13ACMGIS,liu12IJGIS} addresses this by using robust distance measurements (i.e., Mahalanobis distance \cite{pan13ACMGIS} and relative distance  \cite{liu12IJGIS}). Further, structural features  \cite{yuan11JCIS} and a data-induced random tree  \cite{zhang11UC} are exploited to detect anomalous trajectories instead of using distance or density. In a similar fashion, this study considers the center regions of OD flows with data depth in order to robustly detect the trajectory outliers. 
%
%
%
%In addition, visual analytics are a common approach to analyze OD flow data. Visual representation of massive movement data enables comprehensive exploration of data and results in understanding complex flow trends. Aggregation and generalization of movement data are frequently utilized \cite{andrienko08VAST,adrienko11IEEETVCG,guo14IEEETVCG}. While visual analytics can help to extract inherent patterns from massive data, it is difficult to compare two different OD flows based on a hypothesis testing. In other words, it is complicated to comprehend how two OD flows differ and by how much. This paper uses bivariate hypothesis testing methods based on data depth to understand how different two OD flow data sets are in terms of the amount of spatial extent. % and a shift in location. 
%
%
%Further, flow mapping approaches frequently suffer from the modifiable area unit problem (MAUP). For instance, it is not guaranteed that different aggregations via location can present coherent patterns. Kernel-based flow estimation and smoothing are used to overcome different spatial resolution \cite{guo14IEEETVCG}. This study uses traffic analysis zones in New York City as a base unit. Thus, it does not consider MAUP problem. In addition, New York City Taxi data includes the origin and destination within traffic analysis zones, which ignores the actual trajectory route. It is not necessary to reconstruct individual movements for flow estimation (see \cite{duckham16ICGIS}).
%
%In summary, this paper presents a new algorithm which conducts outlier detection as well as a hypothesis testing from OD flows data. Our approach investigates the central regions of  OD flows based on data depth to detect OD flows anomaly and conduct a hypothesis testing between two different OD flow data sets. 
%
%In the remainder of this paper, Section \ref{sec:methods} overviews how to detect OD flows outliers and conduct  a hypothesis testing between two different OD flows with the concept of data depth. Experimental design and the evaluation of the proposed method are presented in Section \ref{sec:experiments}. These results are discussed in Section \ref{sec:discussion}. Section \ref{sec:conclusions} concludes with a summary and future perspectives.

\section{Methods}
\label{sec:methods}
%We further develop a set of well thought out techniques to improve the performance.

\subsection{Data Depth}
Data depth measures the centrality of a point with regard to a given dataset in $\mathbb{R}^d$.  Originally developed by \cite{tukey75ICM}, the notion of data depth (i.e., halfspace depth) generalizes the univariate concept of ranking to multivariate data. Halfspace depth represents how deeply a point is located within a given dataset by ordering all points according to their degree of centrality.

Generally, the halfspace depth (HD) of point $x$ in  $\mathbb{R}^d$ is defined as the minimum probability, $P$ on  $\mathbb{R}^d$, associated with any closed halfspace containing $x$ \cite{liu00AS}. 
\begin{equation*}\label{eq:hd}
HD(x;P) = inf\{P(H): \text{H is a closed halfspace}, x \in H\}\text{, } x \in \mathbb{R}^d.
\end{equation*}

For the univariate case, all values less than or equal (greater than or equal) to $x$ form a closed halfspace. All values less (greater) than $x$ are an open halfspace. The smallest probability associated with two closed halfspaces developed by $x$ is the halfspace depth of  point $x$.
In Figure \ref{fig:hd_uni}, the probability of values less than or equal to 4 is  $2/7$ and the probability of values greater than or equal to 4 is $6/7$. Thus, the halfspace depth of 4 is $2/7$, which is the minimum probability carried by any closed halfspace containing 4. Furthermore, as the sample median, 14 has the largest halfspace depth. Note that, the polluted point inflates the standard error of the sample mean, thereby distorting the view of the data.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{images/depth_uni.eps}
	\caption{Robustness of halfspace depth for the univariate case}
	\label{fig:hd_uni}	
\end{figure}

Similarly, the halfspace depth of $x$ for the bivariate case is defined by the minimal number of data points in any closed halfspace, which is determined by a hyperplane through $x$ \cite{rousseeuw96RSS}. In Figure \ref{fig:hd_bi}, the solid line through $x$ is rotated by $180^{\circ}$. The halfspace depth of $x$ is determined by the smallest portion of data separated by such a hyperplane. For example, the halfspace depth of $x$ is $3/13$, as determined by the dotted line. However, the halfspace depth of $x$ determined by the solid line is  $4/13$. Thus, the halfspace depth of $x$ is $3/13$, which is the minimal number of data points in any closed halfspace through $x$.

\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{images/depth_bi.eps}
	\caption{Halfspace depth for the bivariate case}
	\label{fig:hd_bi}	
\end{figure}

The property of halfspace depth is a center-outward ordering of points in  $\mathbb{R}^d$ and is affine invariant \cite{Mosler13book}. These features make halfspace depth useful tool in nonparametric inference, which leads to various applications such as data classification and cluster analysis
\cite{lange14fSP,jeong16acmgis}. There are multiple approaches to calculating data depth, including halfspace depth \cite{rousseeuw96RSS}, projection depth \cite{wilcox03CSSC}, and simplicial depth \cite{liu90AS}. While the computational complexity of the projection approach is $\mathcal{O}(n^2)$ (where $n$ is the number of points), the computational complexity of simplicial depth is $\mathcal{O}(n^3)$. This can significantly increase execution time when $n$ is large. Thus, this paper uses the more efficient method proposed by \cite{rousseeuw96RSS}, in which the computation complexity for both approaches is $\mathcal{O}(n\log{}n)$.

\subsection{OD Flow Outlier Detection Based on Depth}
The center-outward ordering in data depth is closely related to the detection of outliers. The upper level sets of data depth in $\mathbb{R}^2$ form the central regions. The most central region can be regarded as a median. Conversely, the lower level sets of data depth, which coincide with larger distances from the center, can be regarded as outlyingness. This concept was utilized by \cite{rousseeuw99AS,aplpackR} to generate bag plots, which are analogous to one-dimensional box plots based on data depth. This paper uses the bag plot to identify the outliers of OD flows. Before explaining the method of outlier detection, we first introduce a basic definition of OD flow.

%\theoremstyle{definition}
%\begin{definition}{Point.}
%	A point $p$ is a tuple $(o,d,t)$, where $o$ and $d$  are the origin and destination ID of  traffic analysis zones and $t$ is the time when the destination ID is recorded.
%\end{definition}
%
%
%\begin{definition}{Trajectory.}
%	A trajectory $TR$ is a list of points $(p_1, p_2, p_3,...,p_n)$, where $p_i = (o_i,d_i,t_i)$ and $t_1<t_2<t_3<...<t_n$.
%\end{definition}

\begin{definition}{Origin-destination (OD) flow.}
	The OD flow $OD_i = (o_i,d_i,c_i,ts_i, te_i)$ is the number of trips from the origin ID to destination ID of traffic analysis zones between the start time ($ts_i$) and the end time ($te_i$), where $ts_i<te_i$.
\end{definition}

Based on this basic definitions, Figure \ref{fig:bagplot_0521_0701} depicts bag plots representing the OD flows of New York City taxi data collected on May 21, 2014 and July 1, 2014. We exploited taxi data on May 21, 2014 because the National September 11 Memorial Museum and Pavilion was opened to the public on this date. We randomly selected another data on July 1, 2014.  In Figure \ref{fig:OD_0521}, the deepest depth of OD flows, depth median, is represented by a star symbol. This point is surrounded by  a dark blue bag, which contains the half of OD flows. This region is regarded as a central region of OD flows. The OD flows in the bag are the dominant patterns.  Magnifying the bag by a factor of three, relative to depth median, constructs a fence, as indicated by the light-blue area. The fence is comparable to the whiskers of a one-dimensional boxplot. The OD flows outside the fence, represented by red circles, are outliers. Every OD pair is represented by a point in Figure \ref{fig:bagplot_0521_0701}. The x-axis indicates the counts of forward OD flows (e.g., the number of OD flows from origin ID $2$ to destination  ID $10$), and the y-axis indicates the counts of reverse OD flows (e.g., the number of OD flows from origin ID $10$ to destination  ID $2$) in Figure \ref{fig:OD_0521}.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/OD_0521.eps}
		\caption{May 21 2014}
		\label{fig:OD_0521}
	\end{subfigure}
	\hfill %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/OD_0701.eps}
		\caption{July 1 2014}
		\label{fig:OD_0721}
	\end{subfigure}
    \hfill
	\begin{subfigure}[b]{0.49\textwidth}
	\includegraphics[width=\textwidth]{images/OD_0701_0521.eps}
	\caption{Combination of May 21 and July 1}
	\label{fig:OD_0721_0521}
	\end{subfigure}
    \hfill
	\begin{subfigure}[b]{0.49\textwidth}
	\includegraphics[width=\textwidth]{images/Outliers_high_0701_0521.eps}
	\caption{Detection of outliers with high volume of trips}
	\label{fig:OD_outliers_high}
    \end{subfigure}
	\begin{subfigure}[b]{0.53\textwidth}
	\includegraphics[width=\textwidth]{images/Outliers_rare_0701_0521.eps}
	\caption{Relative outliers detection}
	\label{fig:OD_outliers_rare}
    \end{subfigure}
	\caption{Outliers detection of OD flows using a bag plot}\label{fig:bagplot_0521_0701}	
\end{figure}

The bag plot presents the data using the following attributes: location is represented by the depth median; spread or the spatial extent of bag; correlation or the orientation of the bag; and skewness, as represented by the shape of the bag and the fence \cite{rousseeuw99AS}.  In Figure \ref{fig:OD_0521}, we observe that some forward OD flows have higher counts than their paired reverse OD flows. We also note the relatively linear correlation between forward OD flows and reverse OD flows and the skewness of forward (reverse) OD flows.

It is also possible to detect the outliers of OD flows of two different time stamps. In Figure \ref{fig:OD_0721_0521}, we visualize the OD flows recorded on two different days.
Comparing the two sets of OD flows not only indicates the central region of OD flows, it also distinguishes the significantly  different OD flows.

 %Therefore, we can not only see where is the central region of OD flows, but also differentiate which OD flows are significantly different by comparing two sets of different OD flows.

The OD flows in high activity areas of a city are more likely to have large trip volumes. We use set operations to detect such outliers. We regard OD flows on July 1  as the control dataset ($control$); OD flows on May 21 as test dataset ($test$); and the combination of two OD flows as combination dataset ($combination$) in Figure \ref{fig:bagplot_0521_0701}. Then we can calculate the intersection of three outliers sets ($control \cap test \cap combination$), which are represented as rectangle symbols in Figure \ref{fig:OD_outliers_high}.

In addition, it is interesting to detect the outliers of OD flows which are typical patterns at time $t_1$ and atypical behavior at time $t_2$.  We define the union of points in the bag, the central region, at time $t_1$ and $t_2$. Then we calculate the intersection of two sets, the outliers of the combination set and the previous union set. These outliers are represented as triangle symbols in Figure \ref{fig:OD_outliers_rare}. These outliers are typical OD flows at time $t_1$, located in the central regions in the bag plot. When we consider two OD flows together, they become unusual OD flows, some have more trips and some have less trips,  relative to the control dataset. Thus, we can detect and treat outliers interactively based on data depth.

% we regard OD flows on July 01 ($t_1$) as control data set($control$) and OD flows on May 21 ($t_2$) as test data set ($test$). From the combination of two OD flows set ($combination$, see Figure \ref{fig:OD_0721_0521}), we calculate the interaction of the combination of two OD flows set and the test data set ($B = \{combination \cap test\}$). We also calculate the difference between the combination of two OD flows set and the control data set ($A = \{combination - control\}$) . Finally, we can detect the outliers of OD flows based on the difference between two sets $A$ and  $B$ ($C = \{A - B\}$). The triangles indicate these outliers in Figure \ref{fig:OD_outliers}.

\subsection{OD Flow Comparisons Based on Depth}
Data depth can compare bivariate data from two independent groups. A t-test can be used to compare  means from two independent groups. For example, the t-test reveals whether the means of two OD flows are different at two different temporal ranges. However, it is also worth examining how groups differ in terms of scale, which is also referred to as spread. Comparisons of central regions in data depth evaluate the marginal distribution, thereby considering the overall structure of the data \cite{wilcox03MBR}.

Let $X$ and $Y$ be the random variables having distributions F and G for two independent groups. The quality index proposed by \cite{liu93JASA} is the probability that the depth of $Y$ is greater than or equal to depth of $X$.

\begin{equation*}
Q(F,G) = P[D(X;F) \leq D(Y;F)],
\end{equation*}

where $P$ is the probability and $D(X;F)$ is the depth of randomly sampled observations according from distribution $F$.  The range of $Q$, as presented by \cite{liu93JASA}, is $[0,1]$ and $Q(F,G) = 0.5$ if and only if $F = G$. If $Q < 0.5$  or if $Q > 0.5$, the scale increases or decreases from  $F$ to $G$.   Therefore, it is possible to detect differences in scale using a bootstrap method.

Let $X_1,...,X_a$ be a random sample from $F$, and $Y_1,...,Y_b$ be a random sample from $G$. The estimate of $Q(F,G)$ is calculated as shown below.

\begin{equation*}
\hat{Q}(F,G) =\frac{1}{b} \sum_{i=1}^{b} R(Y_i;F_a),
\end{equation*}

where $R(Y_i;F_a)$ indicates the proportion of $X_j$ which has $D(X_j;F_a) \leq D(Y_i;F_a)$. Similarly, the estimate of $Q(G,F)$ can be defined as follows:

\begin{equation*}
\hat{Q}(G,F) =\frac{1}{a} \sum_{i=1}^{a} R(X_i;G_b).
\end{equation*}

Bootstrap samples are obtained by resampling from the two groups ($F$ and $G$). Under the null hypothesis ($H_0: Q(F,G) = Q(G,F)$), the difference of the resulting bootstrap estimates is $Q^*(F,G) - Q^*(G,F)$. Thus, if the confidence interval of $Q(F,G) - Q(G,F)$ does not contain zero, we can reject the null hypothesis, $H_0$ \cite{liu93JASA,wilcox03MBR}.

\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{images/com_mar_0329.eps}
	\caption{Central regions of two OD flows: $\circ$ indicates the OD flows for Saturday, March 29 2014 and * indicates the OD flows for a list of Saturdays; blue line presents the central region of the OD flows for the list of Saturdays and red dotted line presents the central region of the OD flows on March 29.}
	\label{fig:com_mar_0329}	
\end{figure}

For ease of understanding, Figure \ref{fig:com_mar_0329} presents the central regions of two OD flows. One dataset is OD flows for Saturday, March 29, 2014, and the other dataset includes multiple Saturdays, those of March  1, 8, 15, 22, and April 5. At 552,064 taxi trips, the day of March 29 had the highest number of taxi trips for the year of 2014. The dataset for the other five Saturdays comprised 2,621,703 taxi trips. The bootstrap method reveals that the confidence interval is 0.0247 and 0.0596. This confidence interval does not include zero, thus rejecting the $H_0$ null hypothesis. This indicates that the amount of scale is significantly changed between two OD flow datasets. Furthermore,  the OD flows from the group of Saturdays is nested within the OD flows corresponding to March 29. This additional perspective was based on data depth comparisons.

The bootstrap method is a time consuming process. For this study,  we generate $2,000$ bootstrap samples. To improve the execution efficiency of the bootstrap computation, we distributed the work across multiple nodes and cores by implementing an embarrassingly parallel R code. 
% Thus, we can effectively improve  execution efficiency.
% investigate resource pressures between serial and parallel approaches in the following section.

\section{Experiments}
\label{sec:experiments}

\subsection{Data}
This study uses New York City taxi data collected in 2014 to evaluate the effectiveness of the proposed approach.
Figure \ref{fig:taxizone} presents traffic analysis zones in New York City which indicate the origin and the destination IDs of the OD flows. A traffic analysis zone (TAZ) is the most commonly adopted basic geographic unit in transportation planning models. The geographic areas of TAZ are delineated by transportation officials for tabulating traffic-related data. The size of TAZ varies because it accounts the underlying population in each zone, which consists of one or more census blocks, block groups, or census tracts. The shapes of the TAZs in this study are derived from the cartographic boundary shapefiles developed by the U.S. Census Bureau in conjunction with the 2010 census (https://www2.census.gov/geo/tiger/TIGER2010/TAZ/2010/). Considering the TAZs are particularly useful for journey-to-work and place-of-work statistics, we employed them as the basic units for accounting the taxi trips. 
Figure \ref{fig:ODflows} shows OD flows on July 1. Red lines indicate the dominant OD flows.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/taxizone.eps}
		\caption{2,250 traffic analysis zones in New York City}
		\label{fig:taxizone}
	\end{subfigure}
	\hfill %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/July1st_pic2.eps}
		\caption{OD flows on July 1 2014}
		\label{fig:ODflows}
	\end{subfigure}
	\caption{Experimental data: New York City taxi data}\label{fig:taxi_data}	
\end{figure}

As a case study, this paper examined OD flows recorded on weekdays and weekends in June 2014. The weekday dataset includes taxi trajectories collected on June 3, 10, 17, and 24, and represents 1,721,655 taxi trips. The weekend dataset includes taxi trajectories collected on June 8, 15, 22, and 29, and describes 1,593,480.

\subsection{Procedure}

The performance of the proposed method was compared with alternative methods. Trajectory anomaly detection based on Mahalanobis distance \cite{pan13ACMGIS}  was used to evaluate the performance of outlier detection by the proposed method. The Mahalanobis distance is distinguished from Euclidean distance by its consideration of the correlations of the data, in this case, the two OD flow datasets. According to \cite{pan13ACMGIS}, the anomaly detection threshold can be defined as follows:

\begin{equation*}
d_M(OD_{t_1}, \mu_{[t_0,t_1)}) \geq 3\cdot \sqrt{\frac{1}{N}\sum_{t \in [t_0,t_1)} (OD_{t} - \mu_{[t_0,t_1)})^2} .
\end{equation*}

where $OD_{t_1}$ is the current OD flow, and $\mu_{[t_0,t_1)}$ is the median of all OD flows during $[t_0,t_1)$. In addition, we visualized the results in order to compare them and make the difference easier to understand. The difference of scale was evaluated using  standard statistics, such as F-test, to compare the variance of two datasets.

For data cleaning process, this study used Hadoop with Pig. We developed a Hadoop program to handle the large volume of data, which was composed of 173 million taxi trip records, remove trips with invalid OD coordinates, and assign each OD locations into the corresponding traffic analysis zone.  
To implement the OD flow outlier detection, this study used R. The computing environment used Amazon Web Service and the Bridges supercomputer at the Pittsburgh Supercomputing Center. This study only evaluated OD flows more than 10 trips, as the low trip number OD flows could have distorted the view of the data. All the code will be released as open source (the link to the code will added later and currently is available upon request).

 %Further, we used OD flows that have more than 10 trips. It is reasonable to remove the majority of low number of OD flows, which may distort the view of the data. All the code will be released as open source (the link to the code will added later and currently is available upon request).

%With regard to data cleaning process, this study used Hadoop with Pig. R was used to implement the code in Amazon Web Service  and Bridges supercomputer resources. Further, we used OD flows that have more than 10 trips. It is reasonable to remove the majority of low number of OD flows, which may distort the view of the data.

%Data cleaning process

\subsection{Case study: weekdays vs weekends}
\subsubsection{Outlier Detection}
The bag plots presented OD flow outliers on weekdays and weekends in Figures \ref{fig:weekdays_bag} and \ref{fig:weekends_bag}, respectively. The outliers are detected by considering forward OD flows and reverse OD flows together.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/OD_weekdays.eps}
		\caption{Bag plot on weekdays}
		\label{fig:weekdays_bag}
	\end{subfigure}
	\hfill %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/OD_weekends.eps}
		\caption{Bag plot on weekends}
		\label{fig:weekends_bag}
	\end{subfigure}
	\caption{Outliers detection of OD flows: X-axis indicates forward OD flows counts and Y-axis indicates reverse OD flows counts.}\label{fig:week_weekends_bag}	
\end{figure}

To find the difference between two datasets, we considered two forward OD flows together with the bag plot. Then, we identified the outliers OD flows in Figure \ref{fig:weekdays_high}. The outliers with rectangle symbols indicate OD flows with large volumes of taxi trips during weekdays and weekends. Figure \ref{fig:weekdays_high_map} depicts these outliers are superimposed on a map with red lines. The yellow lines represent the other OD flows, excluding the large volume OD flows on weekdays and weekends.

This case clearly demonstrates that most OD flows occurred in three broad areas: within Manhattan, between the center of Manhattan and the two major airports (J.F.K International Airport and LaGuardia Airport), and between the two airports.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/Outliers_high_weekdays_weekends.eps}
		\caption{OD flows with high volume of trips}
		\label{fig:weekdays_high}
	\end{subfigure}
	\hfill %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/outliers2_high_weekdays_weekends.eps}
		\caption{OD flow map with high volume of trips}
		\label{fig:weekdays_high_map}
	\end{subfigure}
	\caption{Outliers with high volume of trips on weekdays and weekends: Rectangles in Figure \ref{fig:weekdays_high} coincide with red lines in Figure \ref{fig:weekdays_high_map}. }\label{fig:weekdays_high_OD_map}	
\end{figure}

In addition, we investigated abnormal weekend OD flows that are typical weekday OD flows. These abnormal weekend OD flows exhibited substantial variance in number of taxi trips relative to their weekday counterparts. Figure \ref{fig:weekdays_rare} presents these OD flows outliers with triangle symbols. In Figure \ref{fig:weekdays_rare_map}, red lines indicate the substantial increases in weekend trip volumes. Conversely, blue lines indicate the decreases in trip volume. Figure \ref{fig:weekdays_rare_map} reveals that OD flows between the center of Manhattan and the two airports or between the two airports were not significantly different during weekdays and weekends. However, we did observe some meaningful decrease in OD flows during the weekends in business district, as depicted by the blue lines in Figure \ref{fig:weekdays_rare_map}.

%  decreased significantly during weekdays and weekends (e.g., left-side blue OD flows in business district in Figure \ref{fig:weekdays_rare_map}).

%These OD flows are represented on a map with red lines in Figure \ref{fig:weekdays_rare_map}.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/Outliers_rare_weekdays_weekends.eps}
		\caption{Relative OD flows outliers}
		\label{fig:weekdays_rare}
	\end{subfigure}
	\hfill %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/outliers_rare2_weekdays_weekends.eps}
		\caption{OD flow map for relative OD flows outliers}
		\label{fig:weekdays_rare_map}
	\end{subfigure}
	\caption{Relative OD flows outliers on weekdays and weekends: Triangles in Figure \ref{fig:weekdays_rare} coincide with red and blue lines in Figure \ref{fig:weekdays_rare_map}. }\label{fig:weekdays_rare_OD_map}	
\end{figure}

We also detected outlier OD flows using Mahalanobis distance. The results are presented in Figure \ref{fig:week_ends_MD}. 
Far fewer outlier OD flows were detected using  Mahalanobis distance than by the proposed approach. The Mahalanobis method only considers the forward OD flows of the two datasets. It identified OD flow outliers with high volume of trips  because Mahalanobis distance considers the correlations between two OD flows. Thus, Mahalanobis distance is more likely to identify outliers when two OD flows have large trip volumes. In fact, the OD flows outliers from Mahalanobis distance are a subset of the outliers identified by the proposed method, as depicted in Figure \ref{fig:weekdays_high_map}. Furthermore, the Mahalanobis distance approach could not detect the outliers detected by the proposed approach in Figure \ref{fig:weekdays_rare_OD_map} because the Mahalanobis distance approach cannot compare two flows to evaluate significant increases or decreases.

%which OD flows significantly decrease or increase by comparing two OD flows.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/out_weekdays_weekends_md2_outlier.eps}
	\end{subfigure}
	\caption{Outlier OD flows on weekdays and weekends based on Mahalanobis distance. }\label{fig:week_ends_MD}	
\end{figure}

\subsubsection{Comparisons in scale}
We further investigated how two OD flows differ. Our approach is sensitive to the difference in scale. Hypothesis testing  of differences between two central regions in Figure \ref{fig:OD_comparisons} inadvertently revealed that the confidence interval was -0.0277 and 0.0157, which includes zero. Thus, failing to reject the null hypothesis. The two central regions were similar in terms of the spread.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.7\textwidth}
		\includegraphics[width=\textwidth]{images/com_weekdays_weekends.eps}
	\end{subfigure}
	\caption{OD flows comparisons based on data depth: $\circ$ indicates the OD flows on weekdays and * indicates the OD flows on weekends; blue line presents the central region of the OD flows for the weekdays and red dotted line presents the central region of the OD flows on weekends. }\label{fig:OD_comparisons}	
\end{figure}

Interestingly, the standard statistic F-test was significant, $F(9530,7637) =1.1786$, $p \leq 0.05$. The variances of two groups were significantly different. This result directly opposed that of the proposed approach.

%\subsection{Scalability}
%
%\begin{figure}
%	\centering
%	\begin{subfigure}[b]{0.7\textwidth}
%		\includegraphics[width=\textwidth]{images/scalability.eps}
%	\end{subfigure}
%	\caption{Measure of time reduction. }\label{fig:scalability}	
%\end{figure}

\section{Discussion}
\label{sec:discussion}
The results demonstrate that the proposed method effectively identifies outlier OD flows based on data depth. It is also possible to detect outlier OD flows by querying with conditional clauses, such as which outlier OD flows always have high trip volumes during time $t_1$ and time $t_2$.

As an alternative method, the state-of-the-art Mahalanobis distance approach  detected similar outlier OD flows. However, the number of outliers detected was different. This occurred because our OD flows data had heavy tail distributions, that is, many of the OD flows with a long distance from the depth median depicted in Figure \ref{fig:weekdays_rare}. Mahalanobis distance is known to be inadequate when the underlying data have heavy tail distributions \cite{wilcox12Book}. Thus, the presence of outliers may mask the detection of other outliers in Mahalanobis distance approach. Furthermore, it can only detect OD flow outliers with high numbers of trips during time $t_1$ and time $t_2$. It is difficult to detect OD flows outliers that have different properties, such as substantial differences in the number of trips when comparing with time $t_1$ and time $t_2$.

In terms of the difference in spread, our approach used a bootstrap method to compare the central regions of data depth. This approach investigated the difference in scale as well as the structure of data. It can provide information how deeply points from group 1, OD flows at $t_1$, tend to be located within group 2, OD flows at $t_2$. General statistics such as F-test only provide their difference in variation and do not further specify how groups differ.

Interestingly, the F-test results revealed a statistically significant difference in terms of variation of OD flows on weekdays and weekends. Our approach showed no statistically significant differences. The difference may be caused by the sensitivity of F-test to non-normality  \cite{Field12book}, which increases the Type-I error rate. Conversely, data depth makes no assumptions about the distributions of the underlying dataset.

%when the sample size is large, small differences in group differences can produce a F test is significant. 
%
%This F-test is known to be extremely sensitive to non-normality,

\section{Conclusions and Future Work}
\label{sec:conclusions}

This paper provides a new methodology for identifying outlier OD flows and the difference in scale between two different OD flows at $t_1$ and $t_2$. The proposed method is based on the concept of data depth. Data depth is robust statistics, which is suited to non-Gaussian distribution of the underlying datasets. Compared with standard statistics, this approach enhances understanding of the differences and the magnitude of the differences between tow OD flows.

 %adds different perspective how two OD flows differ and by how much.

This study made no attempt to consider geographic contexts such as locational circumstances or surrounding environment in understanding OD flows. Ultimately, further investigation should focus on integrating the analysis of OD flows with geographic context. Such an effort will lead to knowledge discovery and understanding the dynamics of urban flow.

%
%the bag gives an idea of the shape of the majority of the data cloud.
%how to generalize: point-based approach.
%
%Tukey's depth makes no assumptions about the distribution from which observations are randomly sampled.  
%
%
%Outliers can be identified and treated in an interactive way.
%
%Multivariate depth statistics are particularly suited to analyze non-
%Gaussian or, more general, non-elliptical distributions in Rd . Without
%In inference, tests for
%goodness of fit and homogeneity regarding location, scale and symmetry are based
%on depth statistics

%\subparagraph*{Acknowledgements.}

%%
%% Bibliography
%%

%% Please use bibtex,

\bibliography{giscience2018}

\end{document}

### 2018-05-30 GIScience_2018/giscience_r2/giscience/giscience2018.tex
add

@@
 Origin-destination (OD) trajectories provide rich information on urban flow and transport demand.
-This study presents a new methodology to detect OD flows outliers and conduct hypothesis testing between two OD flows in terms of the variations of spatial extent, that is, spread.
+This study presents a new methodology to detect OD flow outliers and conduct hypothesis testing between two OD flows in terms of the variations of spatial extent, namely, spread.
 The proposed method is based on data depth, which measures the centrality and outlyingness of a point with respect to a given dataset in $\mathbb{R}^d$.
@@
 
-It is worth noting that flow mapping approaches frequently suffer from the modifiable areal unit problem (MAUP).Essentially, MAUP is the influence of different aggregations determined by location on the presentation of coherent patterns.
+It is worth noting that flow mapping approaches frequently suffer from the modifiable areal unit problem (MAUP). 
+Essentially, MAUP is the influence of different aggregations determined by location on the presentation of coherent patterns.
 Kernel-based flow estimation and smoothing are used to overcome different spatial resolutions \cite{guo14IEEETVCG}. 
@@
 
-The bag plot presents the data using the following attributes: location is represented by the depth median; spread or the spatial extent of bag; correlation or the orientation of the bag; and skewness, as represented by the shape of the bag and the fence \cite{rousseeuw99AS}.
+The bag plot presents the data using the following attributes:location is represented by the depth median; spread or the spatial extent of bag; correlation or the orientation of the bag; and skewness, as represented by the shape of the bag and the fence \cite{rousseeuw99AS}.
 In Figure \ref{fig:OD_0521}, we observe that some forward OD flows have higher counts than their paired reverse OD flows.
@@
 
-It is also possible to detect the outliers of OD flows of two different time stamps. In Figure \ref{fig:OD_0721_0521}, we visualize the OD flows recorded on two different days.
+It is also possible to detect the outliers of OD flows of two different time stamps.
+In Figure \ref{fig:OD_0721_0521}, we visualize the OD flows recorded on two separated days.
 Comparing the two sets of OD flows not only indicates the central region of OD flows, it also distinguishes the significantly different OD flows.
@@
 where $P$ is the probability and $D(X;F)$ is the depth of randomly sampled observations according from distribution $F$.
-The range of $Q$, as presented by \cite{liu93JASA}, is $[0,1]$ and $Q(F,G) = 0.5$ if and only if $F = G$.
-If $Q < 0.5$  or if $Q > 0.5$, the scale increases or decreases from  $F$ to $G$.
+The range of $Q$, as presented by \cite{liu93JASA}, is $[0,1]$ and $Q(F,G) = 0.5$ if and only if $F = G$. If $Q < 0.5$  or if $Q > 0.5$, the scale increases or decreases from  $F$ to $G$.
 Therefore, it is possible to detect differences in scale using a bootstrap method.
 
-Let $X_1,...,X_a$ be a random sample from $F$, and $Y_1,...,Y_b$ be a random sample from $G$. The estimate of $Q(F,G)$ is calculated as shown below.
+Let $X_1,...,X_a$ be a random sample from $F$, and $Y_1,...,Y_b$ be a random sample from $G$.
+The estimate of $Q(F,G)$ is calculated as shown below.
 
@@
 
-where $R(Y_i;F_a)$ indicates the proportion of $X_j$ which has $D(X_j;F_a) \leq D(Y_i;F_a)$. Similarly, the estimate of $Q(G,F)$ can be defined as follows:
+where $R(Y_i;F_a)$ indicates the proportion of $X_j$ which has $D(X_j;F_a) \leq D(Y_i;F_a)$.
+Similarly, the estimate of $Q(G,F)$ can be defined as follows:
 
@@
 This indicates that the amount of scale is significantly changed between two OD flow datasets.
-Furthermore,  the OD flows from the group of Saturdays is nested within the OD flows corresponding to March 29.
-This additional perspective was based on data depth comparisons.
+Furthermore, the OD flows from the group of Saturdays is nested within the OD flows corresponding to March 29. This additional perspective was based on data depth comparisons.
 
@@
 Considering the TAZs are particularly useful for journey-to-work and place-of-work statistics, we employed them as the basic units for accounting the taxi trips. 
-Figure \ref{fig:ODflows} shows OD flows on July 1. Red lines indicate the dominant OD flows.
+Figure \ref{fig:ODflows} shows OD flows on July 1.
+Red lines indicate the dominant OD flows.
 
@@
 For data cleaning process, this study used Hadoop with Pig.
-We developed a Hadoop program to handle the large volume of data, which was composed of 173 million taxi trip records, remove trips with invalid OD coordinates, and assign each OD locations into the corresponding traffic analysis zone.
+We developed a Hadoop program to handle the large data volume, which was composed of 173 million taxi trip records, remove trips with invalid OD coordinates, and assign each OD locations into the corresponding traffic analysis zone.
 To implement the OD flow outlier detection, this study used R.
@@
 Figure \ref{fig:weekdays_rare} presents these OD flows outliers with triangle symbols.
-In Figure \ref{fig:weekdays_rare_map}, red lines indicate the substantial increases in weekend trip volumes.
-Conversely, blue lines indicate the decreases in trip volume.
+In Figure \ref{fig:weekdays_rare_map}, red lines indicate the substantial increases in weekend trip volumes. Conversely, blue lines indicate the decreases in trip volume.
 Figure \ref{fig:weekdays_rare_map} reveals that OD flows between the center of Manhattan and the two airports or between the two airports were not significantly different during weekdays and weekends.
@@
 This study made no attempt to consider geographic contexts such as locational circumstances or surrounding environment in understanding OD flows. 
-Ultimately, further investigation should focus on integrating the analysis of OD flows with geographic context.
+Further investigation will focus on integrating the analysis of OD flows with geographic context.
 Such an effort will lead to knowledge discovery and understanding the dynamics of urban flow.

### 2018-05-30 GIScience_2018/giscience_r2/giscience/giscience2018.tex
cc

@@
 \begin{abstract}
-Advances in location-aware technology have resulted in the generation of a huge volume of trajectory data.
+Advances in location-aware technology have lead to the generation of a huge volume of trajectory data.
 Origin-destination (OD) trajectories provide rich information on urban flow and transport demand.
@@
 Figure \ref{fig:weekdays_rare} presents these OD flows outliers with triangle symbols.
-In Figure \ref{fig:weekdays_rare_map}, red lines indicate the substantial increases in weekend trip volumes. Conversely, blue lines indicate the decreases in trip volume.
+In Figure \ref{fig:weekdays_rare_map}, red lines indicate the substantial increases in weekend trip volumes.
+Conversely, blue lines indicate the decreases in trip volume.
 Figure \ref{fig:weekdays_rare_map} reveals that OD flows between the center of Manhattan and the two airports or between the two airports were not significantly different during weekdays and weekends.
@@
 
-As an alternative method, the state-of-the-art Mahalanobis distance approach detected similar outlier OD flows.
+As an alternative method, the state-of-the-art Mahalanobis distance-based approach detected similar outlier OD flows.
 However, the number of outliers detected was different.
 This occurred because our OD flows data had heavy tail distributions, that is, many of the OD flows with a long distance from the depth median depicted in Figure \ref{fig:weekdays_rare}. 
-Mahalanobis distance is known to be inadequate when the underlying data have heavy tail distributions \cite{wilcox12Book}.
+Mahalanobis distance is known to be inadequate when the underlying data have heavy tailed distributions \cite{wilcox12Book}. 
 Thus, the presence of outliers may mask the detection of other outliers in Mahalanobis distance approach.
@@
 Data depth is robust statistics, which is suited to non-Gaussian distribution of the underlying datasets.
-Compared with standard statistics, this approach enhances understanding of the differences and the magnitude of the differences between tow OD flows.
+Compared with standard statistics, this approach enhances understanding of the differences and the magnitude of the differences between two OD flows.
 
@@
 
-This study made no attempt to consider geographic contexts such as locational circumstances or surrounding environment in understanding OD flows. 
-Further investigation will focus on integrating the analysis of OD flows with geographic context.
-Such an effort will lead to knowledge discovery and understanding the dynamics of urban flow.
+This study made no attempt to incorporate geographic contexts such as locational circumstances or surrounding environment in understanding OD flows. 
+Further investigations will focus on integrating the analysis of OD flows with geographic context.
+Such an effort will lead to knowledge discovery and better understandings regarding the dynamics of urban flow.
 

### 2018-05-31 GIScience_2018/giscience_r2/giscience_r2/giscience2018.tex
Jun's version

--- 2018-05-30 GIScience_2018/giscience_r2/giscience/giscience2018.tex
@@
 \begin{abstract}
-Advances in location-aware technology have lead to the generation of a huge volume of trajectory data.
+Advances in location-aware technology have led to the generation of a huge volume of trajectory data.
 Origin-destination (OD) trajectories provide rich information on urban flow and transport demand.
@@
 Such data help us better model moving objects and reveal hidden patterns that are important to urban planning \cite{mazimpaka15AGILE}, urban human mobility \cite{yin2017depicting,kwan1998space}, the sustainability of urban systems \cite{alberti2003integrating,chen13Percom}, the environment \cite{devarakonda13SIGKDD}, and public security and safety \cite{buchin14JOSIS}.
-%Importantly, trajectory mining leads to solutions for addressing important research problems in different fields, such as urban planning \cite{mazimpaka15AGILE}, transportation \cite{chen13Percom}, environment \cite{devarakonda13SIGKDD}, and public security and safety \cite{buchin14JOSIS}.
 
-This paper presents a new algorithm which estimates origination-destination (OD) flow anomalies and conducts hypothesis testing between two sets of different OD flows.
-In this study, the OD flow data is a subset of trajectory data, which records the origin and destination of each movement while ignoring the actual trajectory route \cite{guo14IEEETVCG}.
-The algorithm was applied to OD flows derived from extracted origin and destination data in a dataset describing New York City taxi trips, in which each record contained the origin and destination of each trip, without intermediate locations of the actual routes.
+This paper presents a new algorithm which identifies origination-destination (OD) flow anomalies and conducts hypothesis testing between two sets of different OD flows.
+In this study, the OD flow data is a subset of trajectory data, which records the origin and destination of each movement while ignoring the exact trajectory route \cite{guo14IEEETVCG}.
+The algorithm was applied to OD flows derived from the New York City taxi trip records, in which each record contained the origin and destination of each trip without intermediate locations of the actual routes.
 
@@
 Euclidean distance is employed by \cite{fontes13GeoInfo,lee08ICDE} to find outlier patterns from trajectories.
-Studies by \cite{pan13ACMGIS,liu12IJGIS} question the Euclidean distance approach because of the loss of local features and unavailability when external factors, such as topography, land cover or weather condition, affect the trajectories.
+Studies by \cite{pan13ACMGIS,liu12IJGIS} question the Euclidean distance approach because of the loss of local features and unavailability when external factors, such as topography, land cover or weather condition, may affect the trajectories.
 In their research, \cite{pan13ACMGIS,liu12IJGIS} addresses this by using robust distance measurements, i.e., Mahalanobis distance \cite{pan13ACMGIS} and relative distance \cite{liu12IJGIS}.
 Instead of using distance or density, anomalous trajectories are detected by exploiting comparisons of the structural features of each trajectory segment \cite{yuan11JCIS} and an isolation tree of trajectories \cite{zhang11UC}.
-Most of the above methods are related to trajectory data analysis, and thus, it is reasonable to extend the application of these approaches to the identification of OD flow anomalies. 
-To overcome the sensitivity of Euclidean distance-based approaches to non-normal distributed data and the difficulty of selecting parameters for anomaly detection techniques based on distance or density, this study employs robust statistics, such as data depth, to detect OD flow outliers.
+Most of the above methods are related to trajectory data analysis.
+In this connection, it is reasonable to extend the application of these approaches to the identification of OD flow anomalies. 
+To overcome the sensitivity of Euclidean distance-based approaches to data with non-normal distributions and the difficulty of selecting parameters for anomaly detection techniques based on distance or density, this study employs robust statistics, specifically data depth, to detect OD flow outliers.
 
-% Although most methods mentioned above are related to trajectory data analysis, it is reasonable to extend these approaches to identify  OD flows anomaly.
-Thus, this study employs robust statistics such as data depth to detect robustly OD flow outliers because Euclidean distance-based approaches are sensitive to non-normal distributed data and it is hard to choose  parameters for anomaly detection techniques based on distance or density.
-%  because  Euclidean distance-based approaches are sensitive to non-normal distribution of data sets.
-
-%In a similar fashion, this study considers the center regions of OD flows with data depth in order to robustly detect the OD flows outliers.
-
-%In addition, visual analytics such as flow mapping is a common approach to analyze OD flow data.
-Visual representations of massive movement data enables comprehensive exploration of data and results in understanding complex flow trends.
-
-Flow mapping, a type of visual analytics, is a common approach to analyzing OD flow data.
+Flow mapping, as a type of visual analytics, is a common approach to analyzing OD flow data.
 Visual representations of massive movement data facilitate comprehensive exploration of data, in turn enabling perception and understanding complex flow trends.
-Aggregation and generalization of movement data are frequently utilized to resolve visual clutter \cite{guo14IEEETVCG}. %\cite{andrienko08VAST,adrienko11IEEETVCG,guo14IEEETVCG}
+Aggregation and generalization of movement data are frequently utilized to resolve visual clutter \cite{guo14IEEETVCG,yin2016exploring}.
 While visual analytics can help to extract inherent patterns from massive data, it is difficult to quantitatively compare two sets of different OD flows based on a hypothesis testing.
 In other words, it is complicated to comprehend how two OD flows differ and, more importantly, the magnitude of the difference, using a test of statistical significance.
-Recently published articles employ multidimensional spatial scan statistics \cite{Gao17IJGIS} and local Ripley’s K-function \cite{tao16GA} to identify clusters of flow data based on statistical significance tests.
-Thus, this paper applies bivariate hypothesis testing methods based on data depth to understand the difference between two OD flow datasets in terms of the amount of spatial extent.
+Recently literatures employ multidimensional spatial scan statistics \cite{Gao17IJGIS} and local Ripley’s K-function \cite{tao16GA} to identify clusters of flow data based on statistical significance tests.
+This paper applies bivariate hypothesis testing methods based on data depth to understand the difference between two OD flow datasets in terms of the amount of spatial extent.
 
@@
 Kernel-based flow estimation and smoothing are used to overcome different spatial resolutions \cite{guo14IEEETVCG}. 
-Instead of attempting to find the best areal unit by which to partition urban space and aggregates the OD flows, this study adopted the established traffic analysis zones of New York City as base unit.
+Instead of attempting to find the best areal unit by which to partition urban space and aggregates the OD flows, this study adopted the established traffic analysis zones of New York City as the base units.
 That said, the proposed method can be adapted to other implementation of areal units.
-In this study, New York City taxi trip data includes the origin and destination within traffic analysis zones, while ignoring the intermediate locations of the actual routes.
-It is not necessary to reconstruct individual movements for flow estimation (see \cite{duckham16ICGIS}).
+In this study, New York City taxi trip data include the origin and destination within traffic analysis zones, while ignoring the intermediate locations of the actual routes.
+Note that it is not necessary to reconstruct individual movements for flow estimation (see \cite{duckham16ICGIS}).
 
@@
 Our approach investigates the central regions of OD flows, based on data depth, to detect OD flow anomalies and conduct hypothesis testing between two different OD flow datasets.
-We believe that our method for analyzing taxi trip data has the potential to aid administrative authorities in understanding crowd patterns, in turn improving urban planning activities such as determining transportation investments.
+We believe that our method for analyzing taxi trip data has the potential to aid administrative authorities in understanding crowd patterns and improving urban planning activities such as determining transportation investments.
 
@@
 Experimental design and the evaluation of the proposed method are presented in Section \ref{sec:experiments}. 
-These results are discussed in Section \ref{sec:discussion}. 
+The results are discussed in Section \ref{sec:discussion}. 
 Section 5 concludes this paper with a summary and future perspectives.
-
-%With the rapid rise in ubiquity of geo-tagged sensors, knowledge discovery power is enhanced by extracting interesting patterns from spatiotemporal big data in various domains.
-In particular, the location-acquisition technologies generate large volumes of movement data such as people, animals, vehicles and natural phenomena.
-These big movement data help us understand moving objects, and discover the hidden patterns.
-Thus, trajectory mining leads to solutions for important research problems in different fields such as urban planning \cite{mazimpaka15AGILE}, transportation \cite{chen13Percom}, environment \cite{devarakonda13SIGKDD}, and public security and safety \cite{buchin14JOSIS}.
-%
-%This paper presents a new algorithm which not only estimates origination-destination (OD)'s flows anomaly but also conducts hypothesis testing between two different OD flows.
-This paper utilizes a New York City Taxi data set that has the origin and destination of each movement without the whole actual trajectory routes.
-The analysis of digital footprints obtained from taxi data has a crucial role in  understanding crowd patterns and planning urban and transportation investments in administrative authorities.
-
-%In recent years, researchers have investigated a variety of approaches to trajectory data mining.
-There are generally four categories that classify trajectory mining methods: clustering, classification, frequent/group pattern mining, and outlier detection \cite{mazimpaka16JOSIS,zheng15ACMTIST}.
-These techniques can be used independently or combinatorially for trajectory mining application problems.
-%
-%In particular, this study focuses on outlier detection of OD flows.
-Outlier detection aims to find trajectories that do not follow the typical flow of trajectory data sets for characterizing the connectivity between regions \cite{mazimpaka16JOSIS}.
-\cite{fontes13GeoInfo,lee08ICDE} use Euclidean distance to find outlier patterns from trajectories.
-\cite{pan13ACMGIS,liu12IJGIS} raise the questions of Euclidean distance approach due to the loss of local features and unavailability when external factors affect the trajectories (e.g., topography, land cover or weather condition).
-\cite{pan13ACMGIS,liu12IJGIS} addresses this by using robust distance measurements (i.e., Mahalanobis distance \cite{pan13ACMGIS} and relative distance  \cite{liu12IJGIS}).
-Further, structural features  \cite{yuan11JCIS} and a data-induced random tree  \cite{zhang11UC} are exploited to detect anomalous trajectories instead of using distance or density.
-In a similar fashion, this study considers the center regions of OD flows with data depth in order to robustly detect the trajectory outliers.
-%
-%
-%
-%In addition, visual analytics are a common approach to analyze OD flow data.
-Visual representation of massive movement data enables comprehensive exploration of data and results in understanding complex flow trends.
-Aggregation and generalization of movement data are frequently utilized \cite{andrienko08VAST,adrienko11IEEETVCG,guo14IEEETVCG}.
-While visual analytics can help to extract inherent patterns from massive data, it is difficult to compare two different OD flows based on a hypothesis testing.
-In other words, it is complicated to comprehend how two OD flows differ and by how much.
-This paper uses bivariate hypothesis testing methods based on data depth to understand how different two OD flow data sets are in terms of the amount of spatial extent.
-% and a shift in location.
-%
-%
-%Further, flow mapping approaches frequently suffer from the modifiable area unit problem (MAUP).
-For instance, it is not guaranteed that different aggregations via location can present coherent patterns.
-Kernel-based flow estimation and smoothing are used to overcome different spatial resolution \cite{guo14IEEETVCG}.
-This study uses traffic analysis zones in New York City as a base unit.
-Thus, it does not consider MAUP problem.
-In addition, New York City Taxi data includes the origin and destination within traffic analysis zones, which ignores the actual trajectory route.
-It is not necessary to reconstruct individual movements for flow estimation (see \cite{duckham16ICGIS}).
-%
-%In summary, this paper presents a new algorithm which conducts outlier detection as well as a hypothesis testing from OD flows data.
-Our approach investigates the central regions of  OD flows based on data depth to detect OD flows anomaly and conduct a hypothesis testing between two different OD flow data sets.
-%
-%In the remainder of this paper, Section \ref{sec:methods} overviews how to detect OD flows outliers and conduct  a hypothesis testing between two different OD flows with the concept of data depth.
-Experimental design and the evaluation of the proposed method are presented in Section \ref{sec:experiments}.
-These results are discussed in Section \ref{sec:discussion}.
-Section \ref{sec:conclusions} concludes with a summary and future perspectives.
 
@@
 \label{sec:methods}
-%We further develop a set of well thought out techniques to improve the performance.
 
@@
 Furthermore, as the sample median, 14 has the largest halfspace depth.
-Note that, the polluted point inflates the standard error of the sample mean, thereby distorting the view of the data.
+Note that the polluted point inflates the standard error of the sample mean, thereby distorting the view of the data.
 
@@
 In Figure \ref{fig:hd_bi}, the solid line through $x$ is rotated by $180^{\circ}$.
-The halfspace depth of $x$ is determined by the smallest portion of data separated by such a hyperplane.
-For example, the halfspace depth of $x$ is $3/13$, as determined by the dotted line.
+The halfspace depth of $x$ is determined by the smallest portion of data separated by such a hyperplane. For example, the halfspace depth of $x$ is $3/13$, as determined by the dotted line.
 However, the halfspace depth of $x$ determined by the solid line is  $4/13$.
-Thus, the halfspace depth of $x$ is $3/13$, which is the minimal number of data points in any closed halfspace through $x$.
+Therefore, the halfspace depth of $x$ is $3/13$, which is the minimal number of data points in any closed halfspace through $x$.
 
@@
 The property of halfspace depth is a center-outward ordering of points in $\mathbb{R}^d$ and is affine invariant \cite{Mosler13book}.
-These features make halfspace depth useful tool in nonparametric inference, which leads to various applications such as data classification and cluster analysis
-\cite{lange14fSP,jeong16acmgis}.
+These features make halfspace depth a useful tool in nonparametric inference, which leads to various applications such as data classification and cluster analysis \cite{lange14fSP,jeong16acmgis}.
 There are multiple approaches to calculating data depth, including halfspace depth \cite{rousseeuw96RSS}, projection depth \cite{wilcox03CSSC}, and simplicial depth \cite{liu90AS}.
@@
 
-%\theoremstyle{definition}
-%\begin{definition}{Point.}
-%	A point $p$ is a tuple $(o,d,t)$, where $o$ and $d$  are the origin and destination ID of  traffic analysis zones and $t$ is the time when the destination ID is recorded.
-%\end{definition}
-%
-%
-%\begin{definition}{Trajectory.}
-%	A trajectory $TR$ is a list of points $(p_1, p_2, p_3,...,p_n)$, where $p_i = (o_i,d_i,t_i)$ and $t_1<t_2<t_3<...<t_n$.
-%\end{definition}
-
 \begin{definition}{Origin-destination (OD) flow.}
@@
 
-Based on this basic definitions, Figure \ref{fig:bagplot_0521_0701} depicts bag plots representing the OD flows of New York City taxi data collected on May 21, 2014 and July 1, 2014.
+Based on this basic definition, Figure \ref{fig:bagplot_0521_0701} depicts bag plots representing the OD flows of New York City taxi data collected on May 21, 2014 and July 1, 2014.
 We exploited taxi data on May 21, 2014 because the National September 11 Memorial Museum and Pavilion was opened to the public on this date.
-We randomly selected another data on July 1, 2014.
+We also randomly selected another data on July 1, 2014.
 In Figure \ref{fig:OD_0521}, the deepest depth of OD flows, depth median, is represented by a star symbol.
 This point is surrounded by a dark blue bag, which contains the half of OD flows.
-This region is regarded as a central region of OD flows.
+This region is regarded as a central region of the OD flows.
 The OD flows in the bag are the dominant patterns.
@@
 
-The bag plot presents the data using the following attributes:location is represented by the depth median; spread or the spatial extent of bag; correlation or the orientation of the bag; and skewness, as represented by the shape of the bag and the fence \cite{rousseeuw99AS}.
+The bag plot presents the data using the following attributes: location is represented by the depth median; spread or the spatial extent of bag; correlation or the orientation of the bag; and skewness, as represented by the shape of the bag and the fence \cite{rousseeuw99AS}.
 In Figure \ref{fig:OD_0521}, we observe that some forward OD flows have higher counts than their paired reverse OD flows.
@@
 
- %Therefore, we can not only see where is the central region of OD flows, but also differentiate which OD flows are significantly different by comparing two sets of different OD flows.
-
-The OD flows in high activity areas of a city are more likely to have large trip volumes.
+The OD flows in high activity areas of the city are more likely to have large trip volumes.
 We use set operations to detect such outliers.
@@
 
-In addition, it is interesting to detect the outliers of OD flows which are typical patterns at time $t_1$ and atypical behavior at time $t_2$.
+In addition, it is interesting to detect the outliers of OD flows which are typical patterns at time $t_1$ but atypical behaviors at time $t_2$.
 We define the union of points in the bag, the central region, at time $t_1$ and $t_2$.
-Then we calculate the intersection of two sets, the outliers of the combination set and the previous union set.
+Then we calculate the intersection of two sets: the outliers of the combination set and the previous union set.
 These outliers are represented as triangle symbols in Figure \ref{fig:OD_outliers_rare}.
@@
 Thus, we can detect and treat outliers interactively based on data depth.
-
-% we regard OD flows on July 01 ($t_1$) as control data set($control$) and OD flows on May 21 ($t_2$) as test data set ($test$).
-From the combination of two OD flows set ($combination$, see Figure \ref{fig:OD_0721_0521}), we calculate the interaction of the combination of two OD flows set and the test data set ($B = \{combination \cap test\}$).
-We also calculate the difference between the combination of two OD flows set and the control data set ($A = \{combination - control\}$) .
-Finally, we can detect the outliers of OD flows based on the difference between two sets $A$ and  $B$ ($C = \{A - B\}$).
-The triangles indicate these outliers in Figure \ref{fig:OD_outliers}.
 
@@
 Under the null hypothesis ($H_0: Q(F,G) = Q(G,F)$), the difference of the resulting bootstrap estimates is $Q^*(F,G) - Q^*(G,F)$.
-Thus, if the confidence interval of $Q(F,G) - Q(G,F)$ does not contain zero, we can reject the null hypothesis, $H_0$ \cite{liu93JASA,wilcox03MBR}.
+Therefore, if the confidence interval of $Q(F,G) - Q(G,F)$ does not contain zero, we can reject the null hypothesis, $H_0$ \cite{liu93JASA,wilcox03MBR}.
 
@@
 
-For ease of understanding, Figure \ref{fig:com_mar_0329} presents the central regions of two OD flows.
+For the ease of understanding, Figure \ref{fig:com_mar_0329} presents the central regions of two OD flows.
 One dataset is OD flows for Saturday, March 29, 2014, and the other dataset includes multiple Saturdays, those of March 1, 8, 15, 22, and April 5.
@@
 This indicates that the amount of scale is significantly changed between two OD flow datasets.
-Furthermore, the OD flows from the group of Saturdays is nested within the OD flows corresponding to March 29. This additional perspective was based on data depth comparisons.
+Furthermore, the OD flows from the group of Saturdays are nested within the OD flows corresponding to March 29. This additional perspective is based on data depth comparisons.
 
@@
 For this study, we generate $2,000$ bootstrap samples.
-To improve the execution efficiency of the bootstrap computation, we distributed the work across multiple nodes and cores by implementing an embarrassingly parallel R code. 
-% Thus, we can effectively improve  execution efficiency.
-% investigate resource pressures between serial and parallel approaches in the following section.
+To improve the execution efficiency of the bootstrap computation, we distributed the work across multiple computing nodes and cores by implementing an embarrassingly parallel R code.
 
@@
 	\end{subfigure}
-	\hfill %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 	%(or a blank line to force the subfigure onto a new line)
+	\hfill
 	\begin{subfigure}[b]{0.49\textwidth}
@@
 This study only evaluated OD flows more than 10 trips, as the low trip number OD flows could have distorted the view of the data.
-All the code will be released as open source (the link to the code will added later and currently is available upon request).
-
- %Further, we used OD flows that have more than 10 trips.
-It is reasonable to remove the majority of low number of OD flows, which may distort the view of the data.
-All the code will be released as open source (the link to the code will added later and currently is available upon request).
-
-%With regard to data cleaning process, this study used Hadoop with Pig.
-R was used to implement the code in Amazon Web Service  and Bridges supercomputer resources.
-Further, we used OD flows that have more than 10 trips.
-It is reasonable to remove the majority of low number of OD flows, which may distort the view of the data.
-
-%Data cleaning process
+All the code will be released as open source (the link to the code is available upon request).
 
@@
 
-%  decreased significantly during weekdays and weekends (e.g., left-side blue OD flows in business district in Figure \ref{fig:weekdays_rare_map}).
-
-%These OD flows are represented on a map with red lines in Figure \ref{fig:weekdays_rare_map}.
-
 \begin{figure}
@@
 
-We also detected outlier OD flows using Mahalanobis distance. The results are presented in Figure \ref{fig:week_ends_MD}. 
+We also detected outlier OD flows using Mahalanobis distance.
+The results are presented in Figure \ref{fig:week_ends_MD}. 
 Far fewer outlier OD flows were detected using Mahalanobis distance than by the proposed approach.
@@
 Furthermore, the Mahalanobis distance approach could not detect the outliers detected by the proposed approach in Figure \ref{fig:weekdays_rare_OD_map} because the Mahalanobis distance approach cannot compare two flows to evaluate significant increases or decreases.
-
-%which OD flows significantly decrease or increase by comparing two OD flows.
 
@@
 Our approach is sensitive to the difference in scale.
-Hypothesis testing of differences between two central regions in Figure \ref{fig:OD_comparisons} inadvertently revealed that the confidence interval was -0.0277 and 0.0157, which includes zero.
-Thus, failing to reject the null hypothesis.
-The two central regions were similar in terms of the spread.
+Hypothesis testing of the differences between two central regions in Figure \ref{fig:OD_comparisons} inadvertently revealed that the confidence interval was -0.0277 and 0.0157, which included zero.
+Therefore, it failed to reject the null hypothesis, which indicated the two central regions were similar in terms of the spread.
 
@@
 This result directly opposed that of the proposed approach.
-
-%\subsection{Scalability}
-%
-%\begin{figure}
-%	\centering
-%	\begin{subfigure}[b]{0.7\textwidth}
-%		\includegraphics[width=\textwidth]{images/scalability.eps}
-%	\end{subfigure}
-%	\caption{Measure of time reduction. }\label{fig:scalability}	
-%\end{figure}
 
@@
 
-%when the sample size is large, small differences in group differences can produce a F test is significant. 
-%
-%This F-test is known to be extremely sensitive to non-normality,
-
 \section{Conclusions and Future Work}
@@
 
-This paper provides a new methodology for identifying outlier OD flows and the difference in scale between two different OD flows at $t_1$ and $t_2$.
+This paper provides a new methodology for identifying outlier OD flows and detecting the difference in scale between two different OD flows at $t_1$ and $t_2$.
 The proposed method is based on the concept of data depth.
-Data depth is robust statistics, which is suited to non-Gaussian distribution of the underlying datasets.
+Data depth is robust statistics, which is suited to datasets with the underlying distribution being non-Gaussian.
 Compared with standard statistics, this approach enhances understanding of the differences and the magnitude of the differences between two OD flows.
 
- %adds different perspective how two OD flows differ and by how much.
-
-This study made no attempt to incorporate geographic contexts such as locational circumstances or surrounding environment in understanding OD flows. 
+The current study made no attempt to incorporate geographic contexts, such as locational circumstances or surrounding environment, in differentiating the OD flows. 
 Further investigations will focus on integrating the analysis of OD flows with geographic context.
-Such an effort will lead to knowledge discovery and better understandings regarding the dynamics of urban flow.
-
-%
-%the bag gives an idea of the shape of the majority of the data cloud.
-%how to generalize: point-based approach.
-%
-%Tukey's depth makes no assumptions about the distribution from which observations are randomly sampled.  
-%
-%
-%Outliers can be identified and treated in an interactive way.
-%
-%Multivariate depth statistics are particularly suited to analyze non-
-%Gaussian or, more general, non-elliptical distributions in Rd . Without
-%In inference, tests for
-%goodness of fit and homogeneity regarding location, scale and symmetry are based
-%on depth statistics
-
-%\subparagraph*{Acknowledgements.}
+Such an effort will lead to knowledge discovery and better understandings regarding the dynamics in urban flows.
 

### 2018-05-31 GIScience_2018/giscience_r2/giscience_r2/giscience2018_origional.tex
Jun's version

--- 2018-05-28 GIScience_2018/giscience_r2/giscience/giscience2018.tex
@@
 \author{Myeong-Hun Jeong}{Department of Civil Engineering, Chosun University, Gwangju, Republic of Korea}{mhjeong@chosun.ac.kr}{[orcid]}{[funding]}
-\author{Junjun Yin}{Social Science Research Institute; Institute for CyberScience, Penn State University, PA, USA}{jyin@psu.edu}{[0000-0002-4196-2439]}{[This work used the Extreme Science and Engineering Discovery Environment (XSEDE), which is supported by National Science Foundation grant number ACI-1548562]}
+\author{Junjun Yin}{Social Science Research Institute; Institute for CyberScience, Penn State University, PA, USA}{jyin@psu.edu}{[orcid]}{[funding]}
 \author{Shaowen Wang}{Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, IL, USA}{shaowen@illinois.edu}{[orcid]}{[funding]}

### 2018-10-09 giscience_1/giscience2018.tex
xx

\documentclass[a4paper,UKenglish]{lipics-v2016}
%This is a template for producing LIPIcs articles. 
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
% for section-numbered lemmas etc., use "numberwithinsect"

\usepackage{microtype}%if unwanted, comment out or use option "draft"

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

%My packages
%\usepackage{amsthm}

%\theoremstyle{definition}
%\newtheorem{definition}{Definition}[section]

\bibliographystyle{plainurl}% the recommended bibstyle

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\title{Robust Estimation and Comparison of Origin-Destination Flows with Data Depth}\footnote{A full version of the paper is available at \cite{DBLP:journals/cacm/Knuth74}, \url{XXX}}}
\title{Outliers Detection and Comparison of Origin-Destination Flows with Data Depth}
\titlerunning{Outliers Detection and Comparison of Origin-Destination Flows with Data Depth} %optional, in case that the title is too long; the running title should fit into the top page column

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{Myeong-Hun Jeong}
\author[2]{Junjun Yin}
\author[3]{Shaowen Wang}
\affil[1]{Department of Civil Engineering,  Gwangju, Republic of Korea\\
  \texttt{mhjeong@chosun.ac.kr}}
\affil[2]{Social Science Research Institute, Penn State University, PA, USA\\
  \texttt{jyin@psu.edu}}
\affil[3]{Departmet of Geography and Geographic Information Science, the University of Illinois at Urbana-Champaign, IL, USA\\
	\texttt{shaowen@illinois.edu}}
\authorrunning{M.-H. Jeong, J. Yin and S. Wang} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

\Copyright{Myeong-Hun Jeong, Junjun Yin, and Shaowen Wang}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
\keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Acces}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\begin{abstract}
Abstract

 \end{abstract}

\section{Introduction}

With the rapid rise in ubiquity of geo-tagged sensors, knowledge discovery power is enhanced by extracting interesting patterns from spatiotemporal big data in various domains. In particular, the location-acquisition technologies generate large volumes of movement data such as people, animals, vehicles and natural phenomena. These big movement data help us understand moving objects, and discover the hidden patterns. Thus, trajectory mining leads to solutions for important research problems in different fields such as urban planning \cite{mazimpaka15AGILE}, transportation \cite{chen13Percom}, environment \cite{devarakonda13SIGKDD}, and public security and safety \cite{buchin14JOSIS}.

This paper presents a new algorithm which not only estimates origination-destination (OD)'s flows anomaly but also conducts hypothesis testing between two different OD flows. This paper utilizes a New York City Taxi data set that has the origin and destination of each movement without the whole actual trajectory routes. The analysis of digital footprints obtained from taxi data has a crucial role in  understanding crowd patterns and planning urban and transportation investments in administrative authorities.

In recent years, researchers have investigated a variety of approaches to trajectory data mining. There are generally four categories that classify trajectory mining methods: clustering, classification, frequent/group pattern mining, and outlier detection \cite{mazimpaka16JOSIS,zheng15ACMTIST}. These techniques can be used independently or combinatorially for trajectory mining application problems.

In particular, this study focuses on outlier detection of OD flows. Outlier detection aims to find trajectories that do not follow the typical flow of trajectory data sets for characterizing the connectivity between regions \cite{mazimpaka16JOSIS}. \cite{fontes13GeoInfo,lee08ICDE} use Euclidean distance to find outlier patterns from trajectories.  \cite{pan13ACMGIS,liu12IJGIS} raise the questions of Euclidean distance approach due to the loss of local features and unavailability when external factors affect the trajectories (e.g., topography, land cover or weather condition).  \cite{pan13ACMGIS,liu12IJGIS} addresses this by using robust distance measurements (i.e., Mahalanobis distance \cite{pan13ACMGIS} and relative distance  \cite{liu12IJGIS}). Further, structural features  \cite{yuan11JCIS} and a data-induced random tree  \cite{zhang11UC} are exploited to detect anomalous trajectories instead of using distance or density. In a similar fashion, this study considers the center regions of OD flows with data depth in order to robustly detect the trajectory outliers.

In addition, visual analytics are a common approach to analyze OD flow data. Visual representation of massive movement data enables comprehensive exploration of data and results in understanding complex flow trends. Aggregation and generalization of movement data are frequently utilized \cite{andrienko08VAST,adrienko11IEEETVCG,guo14IEEETVCG}. While visual analytics can help to extract inherent patterns from massive data, it is difficult to compare two different OD flows based on a hypothesis testing. In other words, it is complicated to comprehend how two OD flows differ and by how much. This paper uses bivariate hypothesis testing methods based on data depth to understand how different two OD flow data sets are in terms of the amount of spatial extent and a shift in location.

Further, flow mapping approaches frequently suffer from the modifiable area unit problem (MAUP). For instance, it is not guaranteed that different aggregations via location can present coherent patterns. Kernel-based flow estimation and smoothing are used to overcome different spatial resolution \cite{guo14IEEETVCG}. This study uses traffic analysis zones in New York City as a base unit. Thus, it does not consider MAUP problem. In addition, New York City Taxi data includes the origin and destination within traffic analysis zones, which ignores the actual trajectory route. It is not necessary to reconstruct individual movements for flow estimation (see \cite{duckham16ICGIS}).

In summary, this paper presents a new algorithm which conducts outlier detection as well as a hypothesis testing from OD flows data. Our approach investigates the central regions of  OD flows based on data depth to detect OD flows anomaly and conduct a hypothesis testing between two different OD flow data sets.

In the remainder of this paper, Section \ref{sec:methods} overviews how to detect OD flows outliers and conduct  a hypothesis testing between two different OD flows with the concept of data depth. Experimental design and the evaluation of the algorithm are presented in Section \ref{sec:experiments}. These results are discussed in Section \ref{sec:discussion}. Section 5 concludes with a summary and future perspectives.

%However these approaches take into account whole trajectories or sections of trajectories based on applications. This study focuses on OD flow data, which ignores the actual trajectory route. Additionally, it is not necessary to reconstruct individual movements for flow estimation (see \cite{duckham16ICGIS}). Further, this study considers spatial association of OD flow patterns with data depth to detect trajectory outliers. However, this study focuses on OD flow data, which ignores the actual trajectory route. The methods mentioned above consider the whole trajectory route. Further, New York City Taxi data have obivious  
%Clustering techniques are used to analyze the moving objects such as daily travel in a city and cyclone tracks \cite{rinzivillo12KI,gaffney07CD}. Human mobility is represented as a network with clustering technique \cite{liu09CUPUM}.

%Trajectory pattern mining.//
%clustering//
%Outliers//
%
%
%Trajectory clustering can be applied on either whole trajectories or sections of trajectories
%depending on the goal of analysis and the similarity function applied. For example, if
%the similarity function is defined as similar origin and similar destination, the trajectories
%can be clustered as a whole because the route followed is not important.
%
%
%visualization//
%
%Statistical testing//
%
%MAUP problems, uncertainty//
%
%make no attempt to 
%
%
%The  rapid growth of geospatial data results in enhancing knowledge discovery power by extracting interesting patterns from big data in various domains. There are many mining and analysis methodologies to extract new insights from observed data. In particular, this paper investigates spatio-temporal pattern maps that enable hypothesis testing to understand how groups differ and by how much. 
%
%In addition, our approach provides a method to comparing two independent groups based on data depth. The typical KDE can not provide its statistically significant difference between two different density maps. This study provides how different two data sets are in terms of the amount of scale and a shift in location. These features provide an interesting and useful perspective when trying to characterize how group differ. 
%However, the current study is specifically designed to deal with the entire area between two data sets. It is necessary to expand our approach to investigate local variations. Further, work might also test and compare with alternatives such as a spatial scan. 
%
%Our approach can take into account the overall structure of the data. This method can contribute to gaining a better understanding of data in a variety of applications such as influenza spread map or radiation level changes.
%
%The rapid growth of geospatial data can result in enhancing knowledge discovery power by
%extracting interesting patterns from big data in various domains. The identification of statistically significant hot spots has become a key problem that numerous businesses and organizations are attempting to solve. There are many spatial data mining and analysis methodologies to extract unusual patterns of data. This paper proposes a new spatiotemporal hypothesis testing using data depth. This study investigates how much two independent data sets are different in terms of the amount of spatial extent and a shift in location. These features provide an interesting and useful perspective when trying to characterize how groups differ. The experimental comparison with the leading state-of-the-art alternatives demonstrates that the proposed algorithm can not only take into account the overall structure of the data such as hot spots of drop-off locations in the New York City Taxi data, but also conducts statistical hypothesis testing. This method can contribute to gaining a better understanding of data in a variety of applications.

\section{Methods}
\label{sec:methods}
%We further develop a set of well thought out techniques to improve the performance.

\subsection{Data Depth}
Data depth measures the centrality of a point with regard to a given data sets in $\mathbb{R}^d$.  The notion of data depth (i.e., Tukey's halfspace depth) is originally developed by \cite{tukey75ICM}, which generalizes the univariate concept of ranking to multivariate data. It presents how deeply a point is located within a given data sets by ordering their degree of centrality.

In general, the halfspace depth (HD) of a point $x$ in  $\mathbb{R}^d$ is defined as the minimum probability, $P$ on  $\mathbb{R}^d$, associated with any closed halfspace containing $x$ \cite{liu00AS}. 
\begin{equation*}\label{eq:hd}
HD(x;P) = inf\{P(H): \text{H a closed halfspace}, x \in H\}\text{, } x \in \mathbb{R}^d.
\end{equation*}

For the univariate case, all values less than or equal (greater than or equal) to $x$ form a closed halfspace. 
In Figure \ref{fig:hd_uni}, the probability of values less than or equal to 4 is  $2/7$ and the probability greater than or equal to 4 is $6/7$. The halfspace depth of 4 is $2/7$ which is the minimum probability carried by any closed halfspace containing 4. Further, 14 has the largest halfspace depth, which is the usual sample median. However, the polluted point inflates the standard error of the sample mean, thereby giving a distorted view of the data.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{images/depth_uni.eps}
	\caption{Robustness of halfspace depth for the univariate case}
	\label{fig:hd_uni}	
\end{figure}

In a similar fashion, the halfspace depth of $x$ for the bivariate case is defined as the minimal number of data points in any closed halfspace, determined by a hyperplane through $x$ \cite{rousseeuw96RSS}. For example, the line through $x$ is rotated by $180^{\circ}$ in Figure \ref{fig:hd_bi}. The halfspace depth of $x$ is determined by the smallest portion of data that are separated by such a hyperplane (e.g.,  the halfspace depth of $x$ is $3/13$, determined by the dotted line).

\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{images/depth_bi.eps}
	\caption{Halfspace depth for the bivariate case}
	\label{fig:hd_bi}	
\end{figure}

The property of halfspace depth is a center-outward ordering of points in  $\mathbb{R}^d$ and affine invariant \cite{Mosler13book}. These features serve as a useful tool in nonparametric inference, which lead to various applications such as data classification and clustering analysis
\cite{lange14fSP,jeong16acmgis}. There are a couple of approaches to calculate data depth: halfspace detpth \cite{rousseeuw96RSS}, projection depth \cite{wilcox03CSSC}, and simplicial depth \cite{liu90AS}. While the computational complexity of the projection approach is $\mathcal{O}(n^2)$ (where $n$ is the number of points), the computational complexity of simplicial depth is $\mathcal{O}(n^3)$. This can significantly increase execution time when $n$ is large. Thus, this paper uses the halfspace depth fuction proposed by \cite{rousseeuw96RSS} of which computation complexity is $\mathcal{O}(n\log{}n)$.

\subsection{OD Trajectory Outlier Detection Based on Depth}
The center-outward ordering in data depth is closely related to the detection of outliers. The upper level sets of data depth in $\mathbb{R}^2$ form the central regions. The most central region can be regarded as a median. Conversely, the lower level sets of data depth, coincide with large distance from the center, can be regarded as outlyingness. \cite{rousseeuw99AS,aplpackR} utilizes this concept to generate a bag plot, which is analogous to the one-dimensional box plot based on data depth. This paper uses the bag plot in order to identify the outliers of OD flows. Before explaining the method of outliers detection, we define a couple of definitions.

%\theoremstyle{definition}
\begin{definition}{Point.}
	A point $p$ is a tuple $(o,d,t)$, where $o$ and $d$  are the origin and destination ID of  traffic analysis zones and $t$ is the time when the destination ID is recorded.
\end{definition}

\begin{definition}{Trajectory.}
	A trajectory $TR$ is a list of points $(p_1, p_2, p_3,...,p_n)$, where $p_i = (o_i,d_i,t_i)$ and $t_1<t_2<t_3<...<t_n$.
\end{definition}

\begin{definition}{OD flow.}
	A OD flow $OD$ is a sum of subset of trajectory $TR$. $OD = (OD_1, OD_2, OD_3,...,OD_k)$, where $OD_i = (o_i,d_i,c_i,ts_i, te_i)$, where $c_i$ is the count of the same origin ID ($o_i$) and destination ID ($d_i$) between the start time ($ts_i$) and the end time ($te_i$), $ts_i<te_i$.
\end{definition}

Based on these basic definitions, we plot the OD flows of New York City Taxi data (May 21 and July 01 2014) using a bag plot in Figure \ref{fig:bagplot_0521_0701}. In Figure \ref{fig:OD_0521}, the deepest depth of OD flows (i.e., depth median) is represented as a star symbol. This point is surrounded by a bag, which contains the half of OD flows (dark blue area). Magnifying the bag by a factor of 3 relative to depth median constructs a fence (light blue area). The fence is comparable with whiskers in an one-dimensional boxplot. The OD flows outside the fence are outliers (red color circles). The x-axis indicates the counts of forward OD flows and the y-axis indicates  the counts of reverse OD flows in Figure \ref{fig:OD_0521}. We can similarly present the bag plot of July 01 2014 in Figure \ref{fig:OD_0721}.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/OD_0521.eps}
		\caption{May 21 2014}
		\label{fig:OD_0521}
	\end{subfigure}
	\hfill %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/OD_0701.eps}
		\caption{July 01 2014}
		\label{fig:OD_0721}
	\end{subfigure}
    \hfill
	\begin{subfigure}[b]{0.49\textwidth}
	\includegraphics[width=\textwidth]{images/OD_0701_0521.eps}
	\caption{Combination of May 21 and July 01}
	\label{fig:OD_0721_0521}
	\end{subfigure}
    \hfill
	\begin{subfigure}[b]{0.49\textwidth}
	\includegraphics[width=\textwidth]{images/Outliers_high_0701_0521.eps}
	\caption{Detection of outliers for high volume of trips}
	\label{fig:OD_outliers_high}
    \end{subfigure}
	\begin{subfigure}[b]{0.53\textwidth}
	\includegraphics[width=\textwidth]{images/Outliers_rare_0701_0521.eps}
	\caption{Detection of outliers for atypical OD flow patterns}
	\label{fig:OD_outliers_rare}
    \end{subfigure}
	\caption{Outliers detection of OD flows using a bag plot}\label{fig:bagplot_0521_0701}	
\end{figure}

The bag plot is able to present the location (the depth median), spread (the size of bag), correlation (the orientation of the bag), and skewness (the shape of the bag and the fence) of data \cite{rousseeuw99AS}. For example, we can see which forward OD flows have higher counts compared with reverse OD flows; the relatively linear correlation between forward OD flows and reverse OD flows; and the skewness of forward (reverse) OD flows in Figure \ref{fig:OD_0521}.

In addition, it is possible to detect the outliers of OD flows of two different time stamps. In Figure \ref{fig:OD_0721_0521}, we visualize the OD flows of two different days. Thus, we can not only see where is the central region of OD flows, but also differentiate which OD flows are significantly different compared with two different OD flows.

Further, the OD flows of high active areas in a city are more likely to have large volume of trips. We use set operations to detect such outliers. For example, we regard OD flows on July 01  as control data set ($control$); OD flows on May 21 as test data set ($test$); and the combination of two OD flows as combination data set ($combination$) in Figure \ref{fig:bagplot_0521_0701}. Then we can calculate the intersection of three outliers sets ($control \cap test \cap combination$), which are represented as rectangle symbols in Figure \ref{fig:OD_outliers_high}.

In addition, it is interesting to detect the outliers of OD flows which are typical patterns at time $t_1$ and atypical behavior at time $t_2$.  For example, we define the union of points in the bag at time $t_1$ and $t_2$. Then we can calculate the intersection of two sets: the outliers of combination set and the previous union set. These outliers are represented as triangle symbols in Figure \ref{fig:OD_outliers_rare}. For example, these outliers are typical OD flows at time $t_1$ which are located in the central regions in the bag plot. When we consider two OD flows together, they become unusual OD flows (e.g., some have more trips and some have less trips compared with the control data set). Thus, we can detect and treat outliers in an interactive way based on data depth.

% we regard OD flows on July 01 ($t_1$) as control data set($control$) and OD flows on May 21 ($t_2$) as test data set ($test$). From the combination of two OD flows set ($combination$, see Figure \ref{fig:OD_0721_0521}), we calculate the interaction of the combination of two OD flows set and the test data set ($B = \{combination \cap test\}$). We also calculate the difference between the combination of two OD flows set and the control data set ($A = \{combination - control\}$) . Finally, we can detect the outliers of OD flows based on the difference between two sets $A$ and  $B$ ($C = \{A - B\}$). The triangles indicate these outliers in Figure \ref{fig:OD_outliers}.

\subsection{OD Trajectory Comparisons Based on Depth}
Data depth can compare bivariate data related with two independent groups \cite{liu93JASA}. A t-test can be used to compare two means from independent groups. For example, the t-test reveals whether two OD flows' means  are different at two different time stamps. However, it is worth examining how groups differ in terms of scale. The comparisons of central regions in data depth compare the marginal distribution, thereby considering the overall structure of the data \cite{wilcox03MBR}.

Let $X$ and $Y$ be the random variables having distributions F and G for two independent groups. The quality index proposed by \cite{liu93JASA} is the probability that the depth of $Y$ is greater than or equal to depth of $X$.

\begin{equation*}
Q(F,G) = P[D(X;F) \leq D(Y;F)],
\end{equation*}

where $P$ is the probability and $D(X;F)$ is the depth of a randomly sampled observations according with the distribution $F$. \cite{liu93JASA} presents the range of $Q$ is $[0,1]$ and $Q(F,G) = 0.5$ if and only if $F = G$. If $Q < 0.5$  or $Q > 0.5$, a scale increases or decreases from  $F$ to $G$.   It is therefore possible to detect differences in scale based on a bootstrap method.

Let $X_1,...,X_a$ be a random sample from $F$, and $Y_1,...,Y_b$ be a random sample from $G$. The estimate of $Q(F,G)$ is as below.

\begin{equation*}
\hat{Q}(F,G) =\frac{1}{b} \sum_{i=1}^{b} R(Y_i;F_a),
\end{equation*}

where $R(Y_i;F_a)$ indicates the proportion of $X_j$ which has $D(X_j;F_a) \leq D(Y_i;F_a)$. Similarly, the estimate of $Q(G,F)$ can be defined as below.

\begin{equation*}
\hat{Q}(G,F) =\frac{1}{a} \sum_{i=1}^{a} R(X_i;G_b).
\end{equation*}

Bootstrap samples are obtained by resampling from the two groups ($F$ and $G$). Under the null hypothesis ($H_0: Q(F,G) = Q(G,F)$), the difference of the resulting bootstrap estimates is $Q^*(F,G) - Q^*(G,F)$. Thus, if the confidence interval of $Q(F,G) - Q(G,F)$ does not contain zero, we can reject the null hypothesis, $H_0$ \cite{liu93JASA,wilcox03MBR}.

\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{images/com_mar_0329.eps}
	\caption{Central regions of two OD flows: $\circ$ indicates the OD flows for Saturday, March 29 2014 and * indicates the OD flows for a list of Saturdays; blue line presents the central region of the OD flows for the list of Saturdays and red dotted line presents the central region of the OD flows on March 29.}
	\label{fig:com_mar_0329}	
\end{figure}

For ease of understanding, Figure \ref{fig:com_mar_0329} presents the central regions of two OD flows. One data set is OD flows for Saturday, March 29 2014 and the other is Saturday data sets which include March  1, 8, 15, 22, and April 5. March 29 has the highest number of taxi trips of the year (i.e., 552,064 taxi trips).  The data set for the list of Saturdays has 2,621,703 taxi trips. The bootstrap method reveals that the confidence interval is 0.02467486 and 0.0595938. This confidence interval does not include zero, which results in rejecting the $H_0$. This means that the amount of scale is significantly changed between two OD flows.

In addition, it is apparent that the bootstrap method is a time consuming process. We generate $2,000$ bootstrap samples. In order to scale up the bootstrap computation, we spread work across multiple nodes and cores by implementing an embarrassingly parallel R code.  Thus, we investigate resource pressures between serial and parallel approaches in the following section.

\section{Experiments}
\label{sec:experiments}

\subsection{Data}
This study uses New York City Taxi data in 2014 to evaluate the effectiveness of the proposed approach.
Figure \ref{fig:taxizone} presents taxi analysis zones in New York City which indicates the origin and the destination IDs of OD flows. Figure \ref{fig:ODflows} shows OD flows on July 01.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/taxizone.eps}
		\caption{2,250 taxi analysis zone in New York City}
		\label{fig:taxizone}
	\end{subfigure}
	\hfill %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/July1st_pic2.png}
		\caption{OD flows on July 01 2014}
		\label{fig:ODflows}
	\end{subfigure}
	\caption{Experimental data: New York City Taxi data}\label{fig:taxi_data}	
\end{figure}

As a case study, this study used OD trips for the comparison between weekdays and weekends in June. The weekdays data set includes taxi trajectories on June 3, 10, 17, and 24. There are 1,721,655 taxi trips. The weekends data set includes taxi trajectories on June 8, 15, 22, and 29.  Its taxi trips are 1,593,480.

\subsection{Procedure}

The performance of the proposed method was compared with alternative methods. Trajectories anomalies detection, based on Mahalanobis distance \cite{pan13ACMSigspatial},  was used to compare the performance of outliers detection. The Mahalanobis distance considers the correlations of the data (e.g., two OD flows), which distinguishes it from Euclidean distance. According to \cite{pan13ACMSigspatial}, the anomaly detection threshold can be defined as below.

\begin{equation*}
d_M(OD_{t_1}, \mu_{[t_0,t_1)}) \geq 3\cdot \sqrt{\frac{1}{N}\sum_{t \in [t_0,t_1)} (OD_{t} - \mu_{[t_0,t_1)})^2} .
\end{equation*}

where $OD_{t_1}$ is the current OD flow, and $\mu_{[t_0,t_1)}$ is the median of all OD flows during $[t_0,t_1)$. In addition, we visualized the results in order to compare them and make the difference easier to understand. In terms of the difference of scale, we used standard statistics such as F-test to compare the variance of two groups.

With regard to data cleaning process, this study used Hadoop with Pig. R was used to implement the code in Amazon Web Service  and Bridges supercomputer resources. Further, we used OD flows that have more than 10 trips. It is reasonable to remove the majority of low number of OD flows, which may distort the view of the data.

%Data cleaning process

\subsection{Case study: weekdays vs weekends}
\subsubsection{Outlier Detection}
The bag plot presented OD flow outliers on weekdays and weekends separately in Figure \ref{fig:week_weekends_bag}. The outliers are detected by considering forward OD flows and reverse OD flow together.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/OD_weekdays.eps}
		\caption{Bag plot on weekdays}
		\label{fig:weekdays_bag}
	\end{subfigure}
	\hfill %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/OD_weekends.eps}
		\caption{Bag plot on weekends}
		\label{fig:weekends_bag}
	\end{subfigure}
	\caption{Outliers detection of OD flows: X-axis indicates forward OD flows counts and Y-axis indicates reverse OD flows counts.}\label{fig:week_weekends_bag}	
\end{figure}

In order to find the difference between two data sets, we considered two forward OD flows together with the bag plot. Then we found the outliers of OD flows in Figure \ref{fig:weekdays_high}. In particular, the outliers with rectangle symbols indicates that these OD flows have high volume of taxi trips during weekdays and weekends. These outliers are superimposed on a map with red lines in Figure \ref{fig:weekdays_high_map}. The yellow lines presents OD flows except the high volume of OD flows on weekends.

As this case very clearly demonstrated, the majority of OD flows occurred in broadly two places: within Manhattan, and between the center of Manhattan and two airports (i.e., J.F.K International airport and LaGuardia airport).

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/Outliers_high_weekdays_weekends.eps}
		\caption{High volume of OD flows}
		\label{fig:weekdays_high}
	\end{subfigure}
	\hfill %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/outliers2_high_weekdays_weekends.png}
		\caption{OD flow map for high volume of OD flows}
		\label{fig:weekdays_high_map}
	\end{subfigure}
	\caption{Outliers with high volume of trips on weekdays and weekends: Rectangles in Figure \ref{fig:weekdays_high} coincide with red lines in Figure \ref{fig:weekdays_high_map}. }\label{fig:weekdays_high_OD_map}	
\end{figure}

In addition, we investigated which OD flows are abnormal on weekends. They are typical OD flows on weekdays. These OD flows can have more taxi trips or less taxi trips compared with the OD flows on weekdays. Figure \ref{fig:weekdays_rare} presents these OD outliers with triangle symbols. These OD flows are represented on a map with red lines in Figure \ref{fig:weekdays_rare_map}.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/Outliers_rare_weekdays_weekends.eps}
		\caption{Relative OD outliers}
		\label{fig:weekdays_rare}
	\end{subfigure}
	\hfill %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/outliers_rare_weekdays_weekends.png}
		\caption{OD flow map for relative OD outliers}
		\label{fig:weekdays_rare_map}
	\end{subfigure}
	\caption{Relative OD outliers on weekdays and weekends: Triangles in Figure \ref{fig:weekdays_rare} coincide with red lines in Figure \ref{fig:weekdays_rare_map}. }\label{fig:weekdays_rare_OD_map}	
\end{figure}

Further, we detected OD outliers with Mahalanobis distance. The results are presented in Figure \ref{fig:week_ends_MD}. The number of OD outliers are very small compared with our approach. In particular, this method only considers forward OD flows with two data sets. It identified OD outliers with high volume of trips  because Mahalanobis distance takes into account the correlations between two OD flows. It is more likely to be outliers when two OD flows have high volume of trips. In fact, the OD outliers from Mahalanobis distance are the subset of them from our methods in Figure \ref{fig:weekdays_high_map}.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{images/out_weekdays_weekends_md2_outlier.png}
	\end{subfigure}
	\caption{OD outliers on weekdays and weekends based on Mahalanobis distance. }\label{fig:week_ends_MD}	
\end{figure}

\subsubsection{Comparisons in scale}
We further investigated how two OD flows differ. Our approach is sensitive to the difference in scale. The hypothesis testing whether two central regions in Figure \ref{fig:OD_comparisons} are different by chance revealed that the confidence interval was -0.02769909 and 0.01573812, which includes zero. Thus, it failed to reject the null hypothesis. They were the same in terms of the spread.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.7\textwidth}
		\includegraphics[width=\textwidth]{images/com_weekdays_weekends.eps}
	\end{subfigure}
	\caption{OD flows comparisons based on data depth: $\circ$ indicates the OD flows on weekdays and * indicates the OD flows on weekends; blue line presents the central region of the OD flows for the weekdays and red dotted line presents the central region of the OD flows on weekends. }\label{fig:OD_comparisons}	
\end{figure}

Interestingly, the standard statistic such as  F-test was significant, $F(9530,7637) =1.1786$, $p \leq 0.05$. The variances of two groups were significantly different. This is the opposite result compared with our approach.

\subsection{Scalability}

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.7\textwidth}
		\includegraphics[width=\textwidth]{images/scalability.eps}
	\end{subfigure}
	\caption{Measure of time reduction. }\label{fig:scalability}	
\end{figure}

\section{Discussion}
\label{sec:discussion}
when the sample size is large, small differences in group differences can produce a F test is significant.

This F-test is known to be extremely sensitive to non-normality,

\section{Conclusions and Future Work}
\label{sec:conclusions}
%the bag gives an idea of the shape of the majority of the data cloud.
%how to generalize: point-based approach.
%
%Tukey's depth makes no assumptions about the distribution from which observations are randomly sampled.  
%
%
%Outliers can be identified and treated in an interactive way.
%
%Multivariate depth statistics are particularly suited to analyze non-
%Gaussian or, more general, non-elliptical distributions in Rd . Without
%In inference, tests for
%goodness of fit and homogeneity regarding location, scale and symmetry are based
%on depth statistics

\subparagraph*{Acknowledgements.}

%%
%% Bibliography
%%

%% Please use bibtex,

\bibliography{giscience2018}

\end{document}

### 2018-10-09 giscience_1/giscience2018_new.tex
xx

--- 2018-10-09 giscience_1/giscience2018.tex
@@
 \author[3]{Shaowen Wang}
-\affil[1]{Department of Civil Engineering,  Gwangju, Republic of Korea\\
+\affil[1]{Department of Civil Engineering, Chosun University, Gwangju, Republic of Korea\\
   \texttt{mhjeong@chosun.ac.kr}}
-\affil[2]{Social Science Research Institute, Penn State University, PA, USA\\
+\affil[2]{Social Science Research Institute; Institute for CyberScience, Penn State University, PA, USA\\
   \texttt{jyin@psu.edu}}
-\affil[3]{Departmet of Geography and Geographic Information Science, the University of Illinois at Urbana-Champaign, IL, USA\\
+\affil[3]{Departmet of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, IL, USA\\
 	\texttt{shaowen@illinois.edu}}
@@
 \section{Introduction}
-
-With the rapid rise in ubiquity of geo-tagged sensors, knowledge discovery power is enhanced by extracting interesting patterns from spatiotemporal big data in various domains.
-In particular, the location-acquisition technologies generate large volumes of movement data such as people, animals, vehicles and natural phenomena.
-These big movement data help us understand moving objects, and discover the hidden patterns.
-Thus, trajectory mining leads to solutions for important research problems in different fields such as urban planning \cite{mazimpaka15AGILE}, transportation \cite{chen13Percom}, environment \cite{devarakonda13SIGKDD}, and public security and safety \cite{buchin14JOSIS}.
-
-This paper presents a new algorithm which not only estimates origination-destination (OD)'s flows anomaly but also conducts hypothesis testing between two different OD flows.
-This paper utilizes a New York City Taxi data set that has the origin and destination of each movement without the whole actual trajectory routes.
-The analysis of digital footprints obtained from taxi data has a crucial role in  understanding crowd patterns and planning urban and transportation investments in administrative authorities.
+With the rapid rise in ubiquity of geolocation-aware sensors, knowledge discovery is greatly enhanced by extracting and mining interesting patterns from spatiotemporal Big Data in various domains.
+In particular, the location-acquisition technologies generate large volumes of movement data, which were used to track people, animals, vehicles, and even natural phenomena.
+Such data help us better model moving objects and reveal hidden patterns that are important to urban planning and its applications in characterizing urban human mobility \cite{jiang2012discovering}, accessibility of the activity space \cite{kwan1998space}, and sustainability of the urban systems \cite{alberti2003integrating}.
+Importantly, trajectory mining leads to solutions for addressing important research problems in different fields, such as urban planning \cite{mazimpaka15AGILE}, transportation \cite{chen13Percom}, environment \cite{devarakonda13SIGKDD}, and public security and safety \cite{buchin14JOSIS}.
+This paper presents a new algorithm which not only estimates origination-destination (OD)'s flows anomaly but also conducts hypothesis testing between two sets of different OD flows.
+The algorithm is applied on the New York City taxi data set, where each record contains the origin and destination of each trip (without intermediate locations of the actual routes).
+We believe the our methods for analyzing taxi trip data has a promising application in understanding crowd patterns and planning urban and transportation investments by the administrative authorities.
 
 In recent years, researchers have investigated a variety of approaches to trajectory data mining.
-There are generally four categories that classify trajectory mining methods: clustering, classification, frequent/group pattern mining, and outlier detection \cite{mazimpaka16JOSIS,zheng15ACMTIST}.
-These techniques can be used independently or combinatorially for trajectory mining application problems.
-
-In particular, this study focuses on outlier detection of OD flows.
+In general, the contemporary trajectory mining methods can be classified into four categories: clustering, classification, frequent/group pattern mining, and outlier detection \cite{mazimpaka16JOSIS,zheng15ACMTIST}.
+These techniques can be used independently or combinatorially for trajectory mining applications.
+For this study, we focus on outlier detection of OD flows.
 Outlier detection aims to find trajectories that do not follow the typical flow of trajectory data sets for characterizing the connectivity between regions \cite{mazimpaka16JOSIS}.
@@
 
-In addition, visual analytics are a common approach to analyze OD flow data.
+In addition, utilizing visual analytics is a common approach to analyze OD flow data.
 Visual representation of massive movement data enables comprehensive exploration of data and results in understanding complex flow trends.
 Aggregation and generalization of movement data are frequently utilized \cite{andrienko08VAST,adrienko11IEEETVCG,guo14IEEETVCG}.
-While visual analytics can help to extract inherent patterns from massive data, it is difficult to compare two different OD flows based on a hypothesis testing.
-In other words, it is complicated to comprehend how two OD flows differ and by how much.
-This paper uses bivariate hypothesis testing methods based on data depth to understand how different two OD flow data sets are in terms of the amount of spatial extent and a shift in location.
+While visual analytics can help to extract inherent patterns from massive data, it is difficult to quantatively compare two sets of different OD flows based on a hypothesis testing.
+In other words, it is complicated to comprehend how two OD flows differ and, more importantly, by how much.
+In this light, this paper uses bivariate hypothesis testing methods based on data depth to understand how different two OD flow data sets are in terms of the amount of spatial extent and a shift in location.
 
-Further, flow mapping approaches frequently suffer from the modifiable area unit problem (MAUP).
+It is worthy noting that flow mapping approaches frequently suffer from the modifiable areal unit problem (MAUP).
 For instance, it is not guaranteed that different aggregations via location can present coherent patterns.
 Kernel-based flow estimation and smoothing are used to overcome different spatial resolution \cite{guo14IEEETVCG}. 
-This study uses traffic analysis zones in New York City as a base unit.
-Thus, it does not consider MAUP problem.
-In addition, New York City Taxi data includes the origin and destination within traffic analysis zones, which ignores the actual trajectory route.
+Instead of focusing on finding the best areal unit to partioning the urban space and aggregating the OD flows, this study chooses traffic analysis zones in New York City as a base unit.
+However, the mothods can be adapted to other choices of areal units.
+In addition, New York City taxi trip data include the origin and destination within traffic analysis zones, which ignores the intermediate locations of the actual routes.
 It is not necessary to reconstruct individual movements for flow estimation (see \cite{duckham16ICGIS}).
@@
 Our approach investigates the central regions of OD flows based on data depth to detect OD flows anomaly and conduct a hypothesis testing between two different OD flow data sets.
-
-In the remainder of this paper, Section \ref{sec:methods} overviews how to detect OD flows outliers and conduct  a hypothesis testing between two different OD flows with the concept of data depth.
+The remainder of this paper is organized as follows: Section \ref{sec:methods} overviews how to detect OD flows outliers and conduct  a hypothesis testing between two different OD flows with the concept of data depth.
 Experimental design and the evaluation of the algorithm are presented in Section \ref{sec:experiments}. 
@@
 The notion of data depth (i.e., Tukey's halfspace depth) is originally developed by \cite{tukey75ICM}, which generalizes the univariate concept of ranking to multivariate data.
-It presents how deeply a point is located within a given data sets by ordering their degree of centrality.
-
+It reveals how deeply a point is located within a given data set by ordering their degree of centrality. 
 In general, the halfspace depth (HD) of a point $x$ in  $\mathbb{R}^d$ is defined as the minimum probability, $P$ on  $\mathbb{R}^d$, associated with any closed halfspace containing $x$ \cite{liu00AS}.
@@
 In Figure \ref{fig:hd_uni}, the probability of values less than or equal to 4 is  $2/7$ and the probability greater than or equal to 4 is $6/7$. 
-The halfspace depth of 4 is $2/7$ which is the minimum probability carried by any closed halfspace containing 4.
+The halfspace depth of 4 is $2/7$, which is the minimum probability carried by any closed halfspace containing 4. 
 Further, 14 has the largest halfspace depth, which is the usual sample median. 
@@
 
-In a similar fashion, the halfspace depth of $x$ for the bivariate case is defined as the minimal number of data points in any closed halfspace, determined by a hyperplane through $x$ \cite{rousseeuw96RSS}.
+In a similar fashion, the halfspace depth of $x$ for the bivariate case is defined as the minimal number of data points in any closed halfspace, which is determined by a hyperplane through $x$ \cite{rousseeuw96RSS}.
 For example, the line through $x$ is rotated by $180^{\circ}$ in Figure \ref{fig:hd_bi}.
@@
 
-\subsection{OD Trajectory Outlier Detection Based on Depth}
+\subsection{OD Flow Outlier Detection Based on Depth}
 The center-outward ordering in data depth is closely related to the detection of outliers.
@@
 This paper uses the bag plot in order to identify the outliers of OD flows. 
-Before explaining the method of outliers detection, we define a couple of definitions.
+Before explaining the method of outliers detection, we first introduce a couple of definitions.
 
@@
 The bag plot is able to present the location (the depth median), spread (the size of bag), correlation (the orientation of the bag), and skewness (the shape of the bag and the fence) of data \cite{rousseeuw99AS}.
-For example, we can see which forward OD flows have higher counts compared with reverse OD flows; the relatively linear correlation between forward OD flows and reverse OD flows; and the skewness of forward (reverse) OD flows in Figure \ref{fig:OD_0521}.
+For example, we can see which forward OD flows have higher counts compared to the reverse OD flows; the relatively linear correlation between forward OD flows and reverse OD flows; and the skewness of forward (reverse) OD flows in Figure \ref{fig:OD_0521}.
 
@@
 In Figure \ref{fig:OD_0721_0521}, we visualize the OD flows of two different days.
-Thus, we can not only see where is the central region of OD flows, but also differentiate which OD flows are significantly different compared with two different OD flows.
+Therefore, we can not only see where is the central region of OD flows, but also differentiate which OD flows are significantly different compared with two different OD flows.
 
@@
 We use set operations to detect such outliers.
-For example, we regard OD flows on July 01  as control data set ($control$); OD flows on May 21 as test data set ($test$); and the combination of two OD flows as combination data set ($combination$) in Figure \ref{fig:bagplot_0521_0701}.
+For example, we regard OD flows on July 1  as control data set ($control$); OD flows on May 21 as test data set ($test$); and the combination of two OD flows as combination data set ($combination$) in Figure \ref{fig:bagplot_0521_0701}.
 Then we can calculate the intersection of three outliers sets ($control \cap test \cap combination$), which are represented as rectangle symbols in Figure \ref{fig:OD_outliers_high}.
@@
 
-\subsection{OD Trajectory Comparisons Based on Depth}
+\subsection{OD Flow Comparisons Based on Depth}
 Data depth can compare bivariate data related with two independent groups \cite{liu93JASA}. 
-A t-test can be used to compare two means from independent groups.
-For example, the t-test reveals whether two OD flows' means  are different at two different time stamps.
+A t-test can be used to compare means from two independent groups.
+For example, the t-test reveals whether two OD flows' means are different at two different temporal ranges.
 However, it is worth examining how groups differ in terms of scale.

### 2018-10-09 giscience_v2/giscience/giscience2018.tex
xx

--- 2018-10-09 giscience_1/giscience2018_new.tex
@@
 E.g., cite as "F.1.1 Models of Computation".
-\keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
+\keywords{OD Analysis, Trajectory Data Mining, Data Depth, Outliers Detection}% mandatory: Please provide 1-5 keywords
 % Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{abstract}
-Abstract
+The advances in location-aware technologies have generated a huge volume of trajectory data.
+In particular, Origin-Destination (OD) trajectories provide rich information to understand urban flow and transport demand.
+This study presents a new methodology to detect OD flows outliers and conduct hypothesis testing between two OD flows in terms of the variations of spatial extent (i.e., spread).
+The proposed method is based on data depth, which measures the centrality and outlyingness of a point with respect to a given data set in $\mathbb{R}^d$.
+Based on the center-outward ordering property, it is possible to analyze the underlying OD flows characteristics such as location, outlyingness, and  spread.
+The proposed method is compared with Mahalanobis distance approach to detect OD anomalies, and F-test to identify the difference in scale.
+Empirical evaluation has demonstrated that the proposed method can identify OD flows outliers in an interactive way.
+Further, it can provide new perspectives by considering the overall structure of data when comparing two different OD flows in scale.
 
@@
 \section{Introduction}
-With the rapid rise in ubiquity of geolocation-aware sensors, knowledge discovery is greatly enhanced by extracting and mining interesting patterns from spatiotemporal Big Data in various domains.
-In particular, the location-acquisition technologies generate large volumes of movement data, which were used to track people, animals, vehicles, and even natural phenomena.
-Such data help us better model moving objects and reveal hidden patterns that are important to urban planning and its applications in characterizing urban human mobility \cite{jiang2012discovering}, accessibility of the activity space \cite{kwan1998space}, and sustainability of the urban systems \cite{alberti2003integrating}.
+With the rapid rise in ubiquity of geolocation-aware sensors, knowledge discovery is greatly enhanced by extracting and mining interesting patterns from spatiotemporal big data in various domains.
+In particular, the location-acquisition technologies generate large volumes of movement data, which are used to track people, animals, vehicles, and even natural phenomena.
+Such data help us better model moving objects and reveal hidden patterns that are important to urban planning and its applications in characterizing urban human mobility \cite{yin2017depicting}, accessibility of the activity space \cite{kwan1998space}, and sustainability of the urban systems \cite{alberti2003integrating}.
 Importantly, trajectory mining leads to solutions for addressing important research problems in different fields, such as urban planning \cite{mazimpaka15AGILE}, transportation \cite{chen13Percom}, environment \cite{devarakonda13SIGKDD}, and public security and safety \cite{buchin14JOSIS}.
+
 This paper presents a new algorithm which not only estimates origination-destination (OD)'s flows anomaly but also conducts hypothesis testing between two sets of different OD flows.
 The algorithm is applied on the New York City taxi data set, where each record contains the origin and destination of each trip (without intermediate locations of the actual routes).
-We believe the our methods for analyzing taxi trip data has a promising application in understanding crowd patterns and planning urban and transportation investments by the administrative authorities.
+We believe that our methods for analyzing taxi trip data have a promising application in understanding crowd patterns, and planning urban and transportation investments by the administrative authorities.
 
@@
 \cite{pan13ACMGIS,liu12IJGIS} raise the questions of Euclidean distance approach due to the loss of local features and unavailability when external factors affect the trajectories (e.g., topography, land cover or weather condition).
-\cite{pan13ACMGIS,liu12IJGIS} addresses this by using robust distance measurements (i.e., Mahalanobis distance \cite{pan13ACMGIS} and relative distance \cite{liu12IJGIS}).
+\cite{pan13ACMGIS,liu12IJGIS} addresses this issue by using robust distance measurements (i.e., Mahalanobis distance \cite{pan13ACMGIS} and relative distance \cite{liu12IJGIS}).
 Further, structural features \cite{yuan11JCIS} and a data-induced random tree \cite{zhang11UC} are exploited to detect anomalous trajectories instead of using distance or density.
-In a similar fashion, this study considers the center regions of OD flows with data depth in order to robustly detect the trajectory outliers.
+In a similar fashion, this study considers the center regions of OD flows with data depth in order to robustly detect the OD flow outliers.
 
@@
 Aggregation and generalization of movement data are frequently utilized \cite{andrienko08VAST,adrienko11IEEETVCG,guo14IEEETVCG}.
-While visual analytics can help to extract inherent patterns from massive data, it is difficult to quantatively compare two sets of different OD flows based on a hypothesis testing.
+While visual analytics can help extract inherent patterns from massive data, it is difficult to quantitatively compare two sets of different OD flows based on a hypothesis testing.
 In other words, it is complicated to comprehend how two OD flows differ and, more importantly, by how much.
-In this light, this paper uses bivariate hypothesis testing methods based on data depth to understand how different two OD flow data sets are in terms of the amount of spatial extent and a shift in location.
+In this light, this paper uses bivariate hypothesis testing methods based on data depth to understand how different two OD flow data sets are in terms of the amount of spatial extent.
 
-It is worthy noting that flow mapping approaches frequently suffer from the modifiable areal unit problem (MAUP).
+It is worth noting that flow mapping approaches frequently suffer from the modifiable areal unit problem (MAUP).
 For instance, it is not guaranteed that different aggregations via location can present coherent patterns.
 Kernel-based flow estimation and smoothing are used to overcome different spatial resolution \cite{guo14IEEETVCG}. 
-Instead of focusing on finding the best areal unit to partioning the urban space and aggregating the OD flows, this study chooses traffic analysis zones in New York City as a base unit.
-However, the mothods can be adapted to other choices of areal units.
-In addition, New York City taxi trip data include the origin and destination within traffic analysis zones, which ignores the intermediate locations of the actual routes.
+Instead of focusing on finding the best areal unit to partitioning the urban space and aggregating the OD flows, this study chooses traffic analysis zones in New York City as a base unit.
+However, the method can be adapted to other choices of areal units.
+In this study, New York City taxi trip data include the origin and destination within traffic analysis zones, which ignores the intermediate locations of the actual routes.
 It is not necessary to reconstruct individual movements for flow estimation (see \cite{duckham16ICGIS}).
@@
 In summary, this paper presents a new algorithm which conducts outlier detection as well as a hypothesis testing from OD flows data.
-Our approach investigates the central regions of OD flows based on data depth to detect OD flows anomaly and conduct a hypothesis testing between two different OD flow data sets.
+Our approach investigates the central regions of OD flows, based on data depth, to detect OD flows anomaly and conduct a hypothesis testing between two different OD flow data sets.
 The remainder of this paper is organized as follows: Section \ref{sec:methods} overviews how to detect OD flows outliers and conduct  a hypothesis testing between two different OD flows with the concept of data depth.
-Experimental design and the evaluation of the algorithm are presented in Section \ref{sec:experiments}. 
+Experimental design and the evaluation of the methods are presented in Section \ref{sec:experiments}. 
 These results are discussed in Section \ref{sec:discussion}. 
@@
 
-%However these approaches take into account whole trajectories or sections of trajectories based on applications.
-This study focuses on OD flow data, which ignores the actual trajectory route.
-Additionally, it is not necessary to reconstruct individual movements for flow estimation (see \cite{duckham16ICGIS}).
-Further, this study considers spatial association of OD flow patterns with data depth to detect trajectory outliers.
-However, this study focuses on OD flow data, which ignores the actual trajectory route.
-The methods mentioned above consider the whole trajectory route.
-Further, New York City Taxi data have obivious
-%Clustering techniques are used to analyze the moving objects such as daily travel in a city and cyclone tracks \cite{rinzivillo12KI,gaffney07CD}.
-Human mobility is represented as a network with clustering technique \cite{liu09CUPUM}.
+%With the rapid rise in ubiquity of geo-tagged sensors, knowledge discovery power is enhanced by extracting interesting patterns from spatiotemporal big data in various domains.
+In particular, the location-acquisition technologies generate large volumes of movement data such as people, animals, vehicles and natural phenomena.
+These big movement data help us understand moving objects, and discover the hidden patterns.
+Thus, trajectory mining leads to solutions for important research problems in different fields such as urban planning \cite{mazimpaka15AGILE}, transportation \cite{chen13Percom}, environment \cite{devarakonda13SIGKDD}, and public security and safety \cite{buchin14JOSIS}.
+%
+%This paper presents a new algorithm which not only estimates origination-destination (OD)'s flows anomaly but also conducts hypothesis testing between two different OD flows.
+This paper utilizes a New York City Taxi data set that has the origin and destination of each movement without the whole actual trajectory routes.
+The analysis of digital footprints obtained from taxi data has a crucial role in  understanding crowd patterns and planning urban and transportation investments in administrative authorities.
 
-%Trajectory pattern mining.//
-%clustering//
-%Outliers//
+%In recent years, researchers have investigated a variety of approaches to trajectory data mining.
+There are generally four categories that classify trajectory mining methods: clustering, classification, frequent/group pattern mining, and outlier detection \cite{mazimpaka16JOSIS,zheng15ACMTIST}.
+These techniques can be used independently or combinatorially for trajectory mining application problems.
+%
+%In particular, this study focuses on outlier detection of OD flows.
+Outlier detection aims to find trajectories that do not follow the typical flow of trajectory data sets for characterizing the connectivity between regions \cite{mazimpaka16JOSIS}.
+\cite{fontes13GeoInfo,lee08ICDE} use Euclidean distance to find outlier patterns from trajectories.
+\cite{pan13ACMGIS,liu12IJGIS} raise the questions of Euclidean distance approach due to the loss of local features and unavailability when external factors affect the trajectories (e.g., topography, land cover or weather condition).
+\cite{pan13ACMGIS,liu12IJGIS} addresses this by using robust distance measurements (i.e., Mahalanobis distance \cite{pan13ACMGIS} and relative distance  \cite{liu12IJGIS}).
+Further, structural features  \cite{yuan11JCIS} and a data-induced random tree  \cite{zhang11UC} are exploited to detect anomalous trajectories instead of using distance or density.
+In a similar fashion, this study considers the center regions of OD flows with data depth in order to robustly detect the trajectory outliers.
 %
 %
-%Trajectory clustering can be applied on either whole trajectories or sections of trajectories
-%depending on the goal of analysis and the similarity function applied. For example, if
-%the similarity function is defined as similar origin and similar destination, the trajectories
-%can be clustered as a whole because the route followed is not important.
+%
+%In addition, visual analytics are a common approach to analyze OD flow data.
+Visual representation of massive movement data enables comprehensive exploration of data and results in understanding complex flow trends.
+Aggregation and generalization of movement data are frequently utilized \cite{andrienko08VAST,adrienko11IEEETVCG,guo14IEEETVCG}.
+While visual analytics can help to extract inherent patterns from massive data, it is difficult to compare two different OD flows based on a hypothesis testing.
+In other words, it is complicated to comprehend how two OD flows differ and by how much.
+This paper uses bivariate hypothesis testing methods based on data depth to understand how different two OD flow data sets are in terms of the amount of spatial extent.
+% and a shift in location.
 %
 %
-%visualization//
+%Further, flow mapping approaches frequently suffer from the modifiable area unit problem (MAUP).
+For instance, it is not guaranteed that different aggregations via location can present coherent patterns.
+Kernel-based flow estimation and smoothing are used to overcome different spatial resolution \cite{guo14IEEETVCG}.
+This study uses traffic analysis zones in New York City as a base unit.
+Thus, it does not consider MAUP problem.
+In addition, New York City Taxi data includes the origin and destination within traffic analysis zones, which ignores the actual trajectory route.
+It is not necessary to reconstruct individual movements for flow estimation (see \cite{duckham16ICGIS}).
 %
-%Statistical testing//
+%In summary, this paper presents a new algorithm which conducts outlier detection as well as a hypothesis testing from OD flows data.
+Our approach investigates the central regions of  OD flows based on data depth to detect OD flows anomaly and conduct a hypothesis testing between two different OD flow data sets.
 %
-%MAUP problems, uncertainty//
-%
-%make no attempt to 
-%
-%
-%The  rapid growth of geospatial data results in enhancing knowledge discovery power by extracting interesting patterns from big data in various domains.
-There are many mining and analysis methodologies to extract new insights from observed data.
-In particular, this paper investigates spatio-temporal pattern maps that enable hypothesis testing to understand how groups differ and by how much.
-%
-%In addition, our approach provides a method to comparing two independent groups based on data depth.
-The typical KDE can not provide its statistically significant difference between two different density maps.
-This study provides how different two data sets are in terms of the amount of scale and a shift in location.
-These features provide an interesting and useful perspective when trying to characterize how group differ.
-%However, the current study is specifically designed to deal with the entire area between two data sets.
-It is necessary to expand our approach to investigate local variations.
-Further, work might also test and compare with alternatives such as a spatial scan.
-%
-%Our approach can take into account the overall structure of the data.
-This method can contribute to gaining a better understanding of data in a variety of applications such as influenza spread map or radiation level changes.
-%
-%The rapid growth of geospatial data can result in enhancing knowledge discovery power by
-%extracting interesting patterns from big data in various domains.
-The identification of statistically significant hot spots has become a key problem that numerous businesses and organizations are attempting to solve.
-There are many spatial data mining and analysis methodologies to extract unusual patterns of data.
-This paper proposes a new spatiotemporal hypothesis testing using data depth.
-This study investigates how much two independent data sets are different in terms of the amount of spatial extent and a shift in location.
-These features provide an interesting and useful perspective when trying to characterize how groups differ.
-The experimental comparison with the leading state-of-the-art alternatives demonstrates that the proposed algorithm can not only take into account the overall structure of the data such as hot spots of drop-off locations in the New York City Taxi data, but also conducts statistical hypothesis testing.
-This method can contribute to gaining a better understanding of data in a variety of applications.
+%In the remainder of this paper, Section \ref{sec:methods} overviews how to detect OD flows outliers and conduct  a hypothesis testing between two different OD flows with the concept of data depth.
+Experimental design and the evaluation of the proposed method are presented in Section \ref{sec:experiments}.
+These results are discussed in Section \ref{sec:discussion}.
+Section \ref{sec:conclusions} concludes with a summary and future perspectives.
 
@@
 The notion of data depth (i.e., Tukey's halfspace depth) is originally developed by \cite{tukey75ICM}, which generalizes the univariate concept of ranking to multivariate data.
-It reveals how deeply a point is located within a given data set by ordering their degree of centrality. 
+It presents how deeply a point is located within a given data set by ordering their degree of centrality.
+
 In general, the halfspace depth (HD) of a point $x$ in $\mathbb{R}^d$ is defined as the minimum probability, $P$ on $\mathbb{R}^d$, associated with any closed halfspace containing $x$ \cite{liu00AS}. 
 \begin{equation*}\label{eq:hd}
-HD(x;P) = inf\{P(H): \text{H a closed halfspace}, x \in H\}\text{, } x \in \mathbb{R}^d.
+HD(x;P) = inf\{P(H): \text{H is a closed halfspace}, x \in H\}\text{, } x \in \mathbb{R}^d.
 \end{equation*}
@@
 \cite{lange14fSP,jeong16acmgis}.
-There are a couple of approaches to calculate data depth: halfspace detpth \cite{rousseeuw96RSS}, projection depth \cite{wilcox03CSSC}, and simplicial depth \cite{liu90AS}.
+There are a couple of approaches to calculate data depth: halfspace depth \cite{rousseeuw96RSS}, projection depth \cite{wilcox03CSSC}, and simplicial depth \cite{liu90AS}.
 While the computational complexity of the projection approach is $\mathcal{O}(n^2)$ (where $n$ is the number of points), the computational complexity of simplicial depth is $\mathcal{O}(n^3)$.
 This can significantly increase execution time when $n$ is large.
-Thus, this paper uses the halfspace depth fuction proposed by \cite{rousseeuw96RSS} of which computation complexity is $\mathcal{O}(n\log{}n)$.
+Thus, this paper uses the halfspace depth function proposed by \cite{rousseeuw96RSS} of which computation complexity is $\mathcal{O}(n\log{}n)$.
 
-\subsection{OD Flow Outlier Detection Based on Depth}
+\subsection{OD Trajectory Outlier Detection Based on Depth}
 The center-outward ordering in data depth is closely related to the detection of outliers.
@@
 
-Based on these basic definitions, we plot the OD flows of New York City Taxi data (May 21 and July 01 2014) using a bag plot in Figure \ref{fig:bagplot_0521_0701}.
+Based on these basic definitions, we plot the OD flows of New York City Taxi data (May 21 and July 1 2014) using a bag plot in Figure \ref{fig:bagplot_0521_0701}.
 In Figure \ref{fig:OD_0521}, the deepest depth of OD flows (i.e., depth median) is represented as a star symbol.
@@
 The x-axis indicates the counts of forward OD flows and the y-axis indicates  the counts of reverse OD flows in Figure \ref{fig:OD_0521}.
-We can similarly present the bag plot of July 01 2014 in Figure \ref{fig:OD_0721}.
+We can similarly present the bag plot of July 1 2014 in Figure \ref{fig:OD_0721}.
 
@@
 		\includegraphics[width=\textwidth]{images/OD_0701.eps}
-		\caption{July 01 2014}
+		\caption{July 1 2014}
 		\label{fig:OD_0721}
@@
 	\includegraphics[width=\textwidth]{images/OD_0701_0521.eps}
-	\caption{Combination of May 21 and July 01}
+	\caption{Combination of May 21 and July 1}
 	\label{fig:OD_0721_0521}
@@
 	\includegraphics[width=\textwidth]{images/Outliers_high_0701_0521.eps}
-	\caption{Detection of outliers for high volume of trips}
+	\caption{Detection of outliers with high volume of trips}
 	\label{fig:OD_outliers_high}
@@
 	\includegraphics[width=\textwidth]{images/Outliers_rare_0701_0521.eps}
-	\caption{Detection of outliers for atypical OD flow patterns}
+	\caption{Relative outliers detection}
 	\label{fig:OD_outliers_rare}
@@
 
-The bag plot is able to present the location (the depth median), spread (the size of bag), correlation (the orientation of the bag), and skewness (the shape of the bag and the fence) of data \cite{rousseeuw99AS}.
+The bag plot is able to present the location (the depth median), spread (the spatial extent of bag), correlation (the orientation of the bag), and skewness (the shape of the bag and the fence) of data \cite{rousseeuw99AS}.
 For example, we can see which forward OD flows have higher counts compared to the reverse OD flows; the relatively linear correlation between forward OD flows and reverse OD flows; and the skewness of forward (reverse) OD flows in Figure \ref{fig:OD_0521}.
@@
 
-\subsection{OD Flow Comparisons Based on Depth}
-Data depth can compare bivariate data related with two independent groups \cite{liu93JASA}. 
+\subsection{OD Trajectory Comparisons Based on Depth}
+Data depth can compare bivariate data related with two independent groups.
 A t-test can be used to compare  means from two independent groups.
 For example, the t-test reveals whether two OD flows' means  are different at two different temporal ranges.
-However, it is worth examining how groups differ in terms of scale.
+However, it is worth examining how groups differ in terms of scale (spread).
 The comparisons of central regions in data depth compare the marginal distribution, thereby considering the overall structure of the data \cite{wilcox03MBR}.
@@
 For ease of understanding, Figure \ref{fig:com_mar_0329} presents the central regions of two OD flows.
-One data set is OD flows for Saturday, March 29 2014 and the other is Saturday data sets which include March  1, 8, 15, 22, and April 5.
+One data set is OD flows for Saturday, March 29 2014 and the other is  the data set of Saturdays which include March  1, 8, 15, 22, and April 5.
 March 29 has the highest number of taxi trips of the year (i.e., 552,064 taxi trips).
@@
 This means that the amount of scale is significantly changed between two OD flows.
+Further, it is possible to see the OD flows from a list of Saturdays is nested within the OD flows corresponding to March 29.
+This is additional perspective based on data depth comparisons.
 
@@
 We generate $2,000$ bootstrap samples.
-In order to scale up the bootstrap computation, we spread work across multiple nodes and cores by implementing an embarrassingly parallel R code.
-Thus, we investigate resource pressures between serial and parallel approaches in the following section.
+In order to scale up the bootstrap computation, we distribute work across multiple nodes and cores by implementing an embarrassingly parallel R code.
+Thus, we can effectively improve execution efficiency.
+% investigate resource pressures between serial and parallel approaches in the following section.
 
@@
 This study uses New York City Taxi data in 2014 to evaluate the effectiveness of the proposed approach.
-Figure \ref{fig:taxizone} presents taxi analysis zones in New York City which indicates the origin and the destination IDs of OD flows. Figure \ref{fig:ODflows} shows OD flows on July 01.
+Figure \ref{fig:taxizone} presents taxi analysis zones in New York City which indicate the origin and the destination IDs of OD flows.
+Figure \ref{fig:ODflows} shows OD flows on July 1.
+Red lines indicate the dominated OD flows.
 
@@
 		\includegraphics[width=\textwidth]{images/taxizone.eps}
-		\caption{2,250 taxi analysis zone in New York City}
+		\caption{2,250 taxi analysis zones in New York City}
 		\label{fig:taxizone}
@@
 		\includegraphics[width=\textwidth]{images/July1st_pic2.png}
-		\caption{OD flows on July 01 2014}
+		\caption{OD flows on July 1 2014}
 		\label{fig:ODflows}
@@
 
-As a case study, this study used OD trips for the comparison between weekdays and weekends in June.
+As a case study, this study used OD flows during weekdays and weekends in June, 2014.
 The weekdays data set includes taxi trajectories on June 3, 10, 17, and 24.
@@
 \subsection{Procedure}
-
 The performance of the proposed method was compared with alternative methods.
-Trajectories anomalies detection, based on Mahalanobis distance \cite{pan13ACMSigspatial},  was used to compare the performance of outliers detection.
+Trajectories anomalies detection, based on Mahalanobis distance \cite{pan13ACMGIS},  was used to compare the performance of outliers detection.
 The Mahalanobis distance considers the correlations of the data (e.g., two OD flows), which distinguishes it from Euclidean distance.
-According to \cite{pan13ACMSigspatial}, the anomaly detection threshold can be defined as below.
+According to \cite{pan13ACMGIS}, the anomaly detection threshold can be defined as below.
 
@@
 With regard to data cleaning process, this study used Hadoop with Pig.
-R was used to implement the code in Amazon Web Service  and Bridges supercomputer resources.
+We have developed a Hadoop program to handle the large volume of data (~173 million taxi trip records), remove trips with invalid OD coordinates, and assign each OD locations into the corresponding traffic analysis zone.
+R was used to implement the OD flow outlier detection.
+The computing environment uses Amazon Web Service and Bridges supercomputer at the Pittsburgh Supercomputing Center.
 Further, we used OD flows that have more than 10 trips.
 It is reasonable to remove the majority of low number of OD flows, which may distort the view of the data.
+All the code will be released as open source (the link to the code will added later and currently is available upon request).
 
@@
 The bag plot presented OD flow outliers on weekdays and weekends separately in Figure \ref{fig:week_weekends_bag}.
-The outliers are detected by considering forward OD flows and reverse OD flow together.
+The outliers are detected by considering forward OD flows and reverse OD flows together.
 
@@
 Then we found the outliers of OD flows in Figure \ref{fig:weekdays_high}.
-In particular, the outliers with rectangle symbols indicates that these OD flows have high volume of taxi trips during weekdays and weekends.
+In particular, the outliers with rectangle symbols indicate that these OD flows have high volume of taxi trips during weekdays and weekends.
 These outliers are superimposed on a map with red lines in Figure \ref{fig:weekdays_high_map}.
-The yellow lines presents OD flows except the high volume of OD flows on weekends.
+The yellow lines present OD flows except the high volume of OD flows on weekends.
 
@@
 In addition, we investigated which OD flows are abnormal on weekends.
-They are typical OD flows on weekdays.
-These OD flows can have more taxi trips or less taxi trips compared with the OD flows on weekdays.
-Figure \ref{fig:weekdays_rare} presents these OD outliers with triangle symbols.
+However, they are typical OD flows on weekdays.
+These OD flows can have significantly more taxi trips or less taxi trips compared with the OD flows on weekdays.
+Figure \ref{fig:weekdays_rare} presents these OD flows outliers with triangle symbols.
 These OD flows are represented on a map with red lines in Figure \ref{fig:weekdays_rare_map}.
@@
 		\includegraphics[width=\textwidth]{images/Outliers_rare_weekdays_weekends.eps}
-		\caption{Relative OD outliers}
+		\caption{Relative OD flows outliers}
 		\label{fig:weekdays_rare}
@@
 	\begin{subfigure}[b]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{images/outliers_rare_weekdays_weekends.png}
-		\caption{OD flow map for relative OD outliers}
+		\includegraphics[width=\textwidth]{images/outliers_rare2_weekdays_weekends.eps}
+		\caption{OD flow map for relative OD flows outliers}
 		\label{fig:weekdays_rare_map}
 	\end{subfigure}
-	\caption{Relative OD outliers on weekdays and weekends: Triangles in Figure \ref{fig:weekdays_rare} coincide with red lines in Figure \ref{fig:weekdays_rare_map}. }\label{fig:weekdays_rare_OD_map}	
+	\caption{Relative OD flows outliers on weekdays and weekends: Triangles in Figure \ref{fig:weekdays_rare} coincide with red lines in Figure \ref{fig:weekdays_rare_map}.
+}\label{fig:weekdays_rare_OD_map}
 \end{figure}
 
-Further, we detected OD outliers with Mahalanobis distance.
+Further, we detected OD flows outliers with Mahalanobis distance.
 The results are presented in Figure \ref{fig:week_ends_MD}.
-The number of OD outliers are very small compared with our approach.
+The number of OD flows outliers are very small compared with our approach.
 In particular, this method only considers forward OD flows with two data sets.
-It identified OD outliers with high volume of trips  because Mahalanobis distance takes into account the correlations between two OD flows.
+It identified OD flows outliers with high volume of trips  because Mahalanobis distance takes into account the correlations between two OD flows.
 It is more likely to be outliers when two OD flows have high volume of trips.
-In fact, the OD outliers from Mahalanobis distance are the subset of them from our methods in Figure \ref{fig:weekdays_high_map}.
+In fact, the OD flows outliers from Mahalanobis distance are the subset of them from our methods in Figure \ref{fig:weekdays_high_map}.
 
@@
 	\begin{subfigure}[b]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{images/out_weekdays_weekends_md2_outlier.png}
+		\includegraphics[width=\textwidth]{images/out_weekdays_weekends_md2_outlier.eps}
 	\end{subfigure}
-	\caption{OD outliers on weekdays and weekends based on Mahalanobis distance. }\label{fig:week_ends_MD}	
+	\caption{OD flows outliers on weekdays and weekends based on Mahalanobis distance. }\label{fig:week_ends_MD}	
 \end{figure}
@@
 
-\subsection{Scalability}
-
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.7\textwidth}
-		\includegraphics[width=\textwidth]{images/scalability.eps}
-	\end{subfigure}
-	\caption{Measure of time reduction. }\label{fig:scalability}	
-\end{figure}
+%\subsection{Scalability}
+%
+%\begin{figure}
+%	\centering
+%	\begin{subfigure}[b]{0.7\textwidth}
+%		\includegraphics[width=\textwidth]{images/scalability.eps}
+%	\end{subfigure}
+%	\caption{Measure of time reduction. }\label{fig:scalability}	
+%\end{figure}
 
@@
 \label{sec:discussion}
-when the sample size is large, small differences in group differences can produce a F test is significant.
+Our results demonstrate that the proposed method can identify OD flows outliers interactively, based on data depth.
+It is possible to detect OD flows outliers by querying with conditional clauses (e.g., which OD flows outliers have always high volume of trips during time $t_1$ and time $t_2$?).
 
-This F-test is known to be extremely sensitive to non-normality,
+The state-of-the-art Mahalanobis distance approach as an alternative method detects similar OD flows outliers.
+However, the number of outliers is quite different.
+The reason behind it is that our OD flows data has heavy tail distributions (e.g., there are a lot of OD flows with a long distance from the depth median in Figure \ref{fig:weekdays_rare}).
+Mahalanobis distance is well known to be unsatisfactory when the underlying data has heavy tail distributions \cite{wilcox12Book}.
+Thus, the very presence of outliers may mask the outliers detection in Mahalanobis distance approach.
+Further, it can only detect OD flows outliers that have high number of trips during time $t_1$ and time $t_2$.
+It is difficult to detect OD flows outliers that have different properties (e.g., which OD flows outliers have significantly high number of trips compared with time $t_1$ and time $t_2$?
+).
+
+In terms of the difference in spread, our approach uses a bootstrap method to compare the central regions of data depth.
+This approach can  investigate not only the difference in scale, but also the structure of data.
+It can provide information how deeply points from group 1 (e.g., OD flows at $t_1$) tend to be located within group 2 (e.g., OD flows at $t_2$).
+General statistics such as F-test only provide their difference in variation.
+However, it does not give how groups differ.
+
+Interestingly, F-test presents there are statistically significant difference in terms of variation for the OD flows on weekdays and weekends.
+However, our approach shows there are no statistically significant differences.
+The difference may be caused by the sensitivity of F-test to non-normality  \cite{Field12book}, which increases the Type-I error rate.
+Conversely, data depth has no assumptions about the distributions of the underlying data set.
+
+%when the sample size is large, small differences in group differences can produce a F test is significant. 
+%
+%This F-test is known to be extremely sensitive to non-normality,
 
@@
 \label{sec:conclusions}
+
+This paper provides a new methodology for identifying OD flows outliers and the difference in scale between two different OD flows at $t_1$ and $t_2$.
+The method is based on the concept of data depth.
+Data depth is robust statistics, which is suited to non-Gaussian distribution of the underlying data sets.
+Compared with standard statistics, it adds different perspective how two OD flows differ and by how much.
+
+However, this study makes no attempt to consider geographic context such as locational circumstances or surrounding environment for understanding OD flows.
+Ultimately, further investigation should focus on integrating the analysis of OD flows with geographic context.
+Such an effort will lead to knowledge discovery for understanding the dynamics of urban flow.
+
+%
 %the bag gives an idea of the shape of the majority of the data cloud.

### 2018-10-09 giscience_v2/giscience/giscience2018_old.tex
xx

--- 2018-10-09 giscience_v2/giscience/giscience2018.tex
@@
 \author[3]{Shaowen Wang}
-\affil[1]{Department of Civil Engineering, Chosun University, Gwangju, Republic of Korea\\
+\affil[1]{Department of Civil Engineering,  Gwangju, Republic of Korea\\
   \texttt{mhjeong@chosun.ac.kr}}
-\affil[2]{Social Science Research Institute; Institute for CyberScience, Penn State University, PA, USA\\
+\affil[2]{Social Science Research Institute, Penn State University, PA, USA\\
   \texttt{jyin@psu.edu}}
-\affil[3]{Departmet of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, IL, USA\\
+\affil[3]{Department of Geography and Geographic Information Science, the University of Illinois at Urbana-Champaign, IL, USA\\
 	\texttt{shaowen@illinois.edu}}
@@
 In particular, Origin-Destination (OD) trajectories provide rich information to understand urban flow and transport demand.
-This study presents a new methodology to detect OD flows outliers and conduct hypothesis testing between two OD flows in terms of the variations of spatial extent (i.e., spread).
+This study presents a new methodology to detect OD flows outliers and conduct hypothesis testing between two OD flows in terms of spread.
 The proposed method is based on data depth, which measures the centrality and outlyingness of a point with respect to a given data set in $\mathbb{R}^d$.
@@
 In particular, the location-acquisition technologies generate large volumes of movement data, which are used to track people, animals, vehicles, and even natural phenomena.
-Such data help us better model moving objects and reveal hidden patterns that are important to urban planning and its applications in characterizing urban human mobility \cite{yin2017depicting}, accessibility of the activity space \cite{kwan1998space}, and sustainability of the urban systems \cite{alberti2003integrating}.
+Such data help us better model moving objects and reveal hidden patterns that are important to urban planning and its applications in characterizing urban human mobility \cite{jiang2012discovering}, accessibility of the activity space \cite{kwan1998space}, and sustainability of the urban systems \cite{alberti2003integrating}.
 Importantly, trajectory mining leads to solutions for addressing important research problems in different fields, such as urban planning \cite{mazimpaka15AGILE}, transportation \cite{chen13Percom}, environment \cite{devarakonda13SIGKDD}, and public security and safety \cite{buchin14JOSIS}.
@@
 \cite{pan13ACMGIS,liu12IJGIS} raise the questions of Euclidean distance approach due to the loss of local features and unavailability when external factors affect the trajectories (e.g., topography, land cover or weather condition).
-\cite{pan13ACMGIS,liu12IJGIS} addresses this issue by using robust distance measurements (i.e., Mahalanobis distance \cite{pan13ACMGIS} and relative distance \cite{liu12IJGIS}).
+\cite{pan13ACMGIS,liu12IJGIS} addresses this by using robust distance measurements (i.e., Mahalanobis distance \cite{pan13ACMGIS} and relative distance \cite{liu12IJGIS}).
 Further, structural features \cite{yuan11JCIS} and a data-induced random tree  \cite{zhang11UC} are exploited to detect anomalous trajectories instead of using distance or density.
-In a similar fashion, this study considers the center regions of OD flows with data depth in order to robustly detect the OD flow outliers.
+In a similar fashion, this study considers the center regions of OD flows with data depth in order to robustly detect the trajectory outliers.
 
@@
 Aggregation and generalization of movement data are frequently utilized \cite{andrienko08VAST,adrienko11IEEETVCG,guo14IEEETVCG}.
-While visual analytics can help extract inherent patterns from massive data, it is difficult to quantitatively compare two sets of different OD flows based on a hypothesis testing.
+While visual analytics can help to extract inherent patterns from massive data, it is difficult to quantitatively compare two sets of different OD flows based on a hypothesis testing.
 In other words, it is complicated to comprehend how two OD flows differ and, more importantly, by how much.
@@
 However, the method can be adapted to other choices of areal units.
-In this study, New York City taxi trip data include the origin and destination within traffic analysis zones, which ignores the intermediate locations of the actual routes.
+In addition, New York City taxi trip data include the origin and destination within traffic analysis zones, which ignores the intermediate locations of the actual routes.
 It is not necessary to reconstruct individual movements for flow estimation (see \cite{duckham16ICGIS}).
@@
 
-The bag plot is able to present the location (the depth median), spread (the spatial extent of bag), correlation (the orientation of the bag), and skewness (the shape of the bag and the fence) of data \cite{rousseeuw99AS}.
+The bag plot is able to present the location (the depth median), spread (the size of bag), correlation (the orientation of the bag), and skewness (the shape of the bag and the fence) of data \cite{rousseeuw99AS}.
 For example, we can see which forward OD flows have higher counts compared to the reverse OD flows; the relatively linear correlation between forward OD flows and reverse OD flows; and the skewness of forward (reverse) OD flows in Figure \ref{fig:OD_0521}.
@@
 We generate $2,000$ bootstrap samples.
-In order to scale up the bootstrap computation, we distribute work across multiple nodes and cores by implementing an embarrassingly parallel R code.
-Thus, we can effectively improve execution efficiency.
+In order to scale up the bootstrap computation, we spread work across multiple nodes and cores by implementing an embarrassingly parallel R code.
+Thus, we can effectively improve  execution times.
 % investigate resource pressures between serial and parallel approaches in the following section.
@@
 
-As a case study, this study used OD flows during weekdays and weekends in June, 2014.
+As a case study, this study used OD flows during weekdays and weekends in June.
 The weekdays data set includes taxi trajectories on June 3, 10, 17, and 24.
@@
 \subsection{Procedure}
+
 The performance of the proposed method was compared with alternative methods.
@@
 With regard to data cleaning process, this study used Hadoop with Pig.
-We have developed a Hadoop program to handle the large volume of data (~173 million taxi trip records), remove trips with invalid OD coordinates, and assign each OD locations into the corresponding traffic analysis zone.
-R was used to implement the OD flow outlier detection.
-The computing environment uses Amazon Web Service and Bridges supercomputer at the Pittsburgh Supercomputing Center.
+R was used to implement the code in Amazon Web Service  and Bridges supercomputer resources.
 Further, we used OD flows that have more than 10 trips.
 It is reasonable to remove the majority of low number of OD flows, which may distort the view of the data.
-All the code will be released as open source (the link to the code will added later and currently is available upon request).
 
@@
 	\begin{subfigure}[b]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{images/outliers_rare2_weekdays_weekends.eps}
+		\includegraphics[width=\textwidth]{images/outliers_rare_weekdays_weekends.png}
 		\caption{OD flow map for relative OD flows outliers}
@@
 	\begin{subfigure}[b]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{images/out_weekdays_weekends_md2_outlier.eps}
+		\includegraphics[width=\textwidth]{images/out_weekdays_weekends_md2_outlier.png}
 	\end{subfigure}
